### 2016-12-14 doc/paper/paper.tex
Added first version of the paper

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{algorithmic}
\usepackage[linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{ltblue}{rgb}{0,0.4,0.4}
\definecolor{dkblue}{rgb}{0,0.1,0.6}
\definecolor{dkgreen}{rgb}{0,0.4,0}
\definecolor{dkviolet}{rgb}{0.3,0,0.5}
\definecolor{dkred}{rgb}{0.5,0,0}

\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
\definecolor{orange}{rgb}{1,0.45,0.13}		
\definecolor{olive}{rgb}{0.17,0.59,0.20}
\definecolor{brown}{rgb}{0.69,0.31,0.31}
\definecolor{purple}{rgb}{0.38,0.18,0.81}
\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
\definecolor{lightred}{rgb}{1,0.4,0.5}
% CSS
\lstdefinelanguage{CSS}{
  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},	
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]",
  alsoletter={:},
  alsodigit={-}
}

% JavaScript
\lstdefinelanguage{JavaScript}{
  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
  morecomment=[s]{/*}{*/},
  morecomment=[l]//,
  morestring=[b]",
  morestring=[b]'
}

\lstdefinelanguage{HTML5}{
  language=html,
  sensitive=true,	
  alsoletter={<>=-},	
  morecomment=[s]{<!-}{-->},
  tag=[s],
  otherkeywords={
  % General
  >,
  % Standard tags
  <!DOCTYPE,
  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
  % body
  </body, <body,
  % Divs
  </div, <div, </div>, 
  % Paragraphs
  </p, <p, </p>,
  % scripts
  </script, <script,
  % More tags...
  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
  },
  ndkeywords={
  % General
  =,
  % HTML attributes
  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
  % SVG attributes
  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
  % properties
  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
  % CSS3 properties
  transform:, -moz-transform:, -webkit-transform:,
  animation:, -webkit-animation:,
  transition:,  transition-duration:, transition-property:, transition-timing-function:,
  }
}

\lstdefinestyle{htmlcssjs} {%
  % General design
  backgroundcolor=\color{editorGray},
  basicstyle={\scriptsize\ttfamily},   
  frame=tb,
  % line-numbers
  xleftmargin={0.75cm},
  numbers=left,
  stepnumber=1,
  firstnumber=1,
  numberfirstline=true,	
  % Code design
  identifierstyle=\color{black},
  keywordstyle=\color{blue}\bfseries,
  ndkeywordstyle=\color{editorGreen}\bfseries,
  stringstyle=\color{editorOcher}\ttfamily,
  commentstyle=\color{brown}\ttfamily,
  % Code
  language=JavaScript,
  alsolanguage=HTML5,
  alsodigit={.:;},	
  tabsize=2,
  showtabs=false,
  showspaces=false,
  showstringspaces=false,
  extendedchars=true,
  breaklines=true,
  escapechar=|c
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\listfiles % used to output the versions of all files being used by the latex

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Search-Based Test Data Generation for JavaScript Functions on DOM}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1}

\author{
  \alignauthor Alexander Elyasov, Wishnu Prasetya, Jurriaan Hage\\ 
  \affaddr{Utrecht University, The Netherlands}\\
  \email{\{a.elyasov,s.w.b.prasetya,j.hage\}@uu.nl}
}

\maketitle
\begin{abstract}

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
TODO
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{ACM proceedings; \LaTeX; text tagging}

\section{Introduction}
\label{sec.intro}
Recent empirical study of client-side JavaScript bugs~\cite{frolin:TSE16} has shown that 68\% of faults are DOM related.

Another empirical work~\cite{richards2010analysis}.

%% --------------------------------------------------------------------
\section{Motivating Example}
\label{sec.example}
%% --------------------------------------------------------------------

\begin{figure}[t]
  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
/*t dom */
function safeAdd() {
  var iframe = document.createElement("iframe");
  var whereto = document.getElementById("debug");
  var frameid = document.getElementById("frame");
  iframe.setAttribute("id", "frame");
  if (frameid) { 
    iframe.removeChild(frameid.childNodes[0]); |c \label{lbl:error} |c
    // frameid.parentNode.removeChild(frameid); |c \label{lbl:correction} |c
  } else { whereto.appendChild(iframe); } }  
  \end{lstlisting}
  \caption{Motivating Example}
  \label{fig..safeAdd.js}
\end{figure}

\begin{figure}[t]
  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
<html>
  <body>
    <div id="frame"></div>
    <div id="debug"></div>
  </body>
</html>
  \end{lstlisting}

  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
<html>
  <body>
    <div id="debug"></div>
  </body>
</html>
\end{lstlisting}  
\caption{Motivating Example}
\label{fig.safeAdd.html}
\end{figure}

\begin{figure}[t]
  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
/*t dom */
function revealAll() {
 for(var row=0; row<2; row++){
  for(var col=0; col<2; col++){
   var obj = document.getElementById('square_'+row+'_'+col);
   var spans = obj.getElementsByTagName('SPAN');
   spans[0].style.display='';
   spans[1].style.display='none';
   spans[1].style.color='#000000'; } } }
  \end{lstlisting}
  \caption{Motivating Example}
  \label{fig.revealAll.js}
\end{figure}

%% --------------------------------------------------------------------
\section{Test Generation Framework}
\label{sec.framework}
%% --------------------------------------------------------------------

\begin{figure}
  \centering 
  \begin{sequencediagram}[font=\scriptsize]
    \newinst{user}{User}
    \newinst{server}{Server}
    \newinst{validator}{Validator}
    \newinst{client}{Client}

    \begin{call}{user}{file.js + config}{server}{\textbf{end}}
      \begin{call}{server}{Initialize(file.js, config)}{server}{cfg, branches, cinfo, ifun, sig}
      \end{call}

      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
      \end{call}

      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
      \end{call}

      \begin{sdblock}{Genetic Loop}{$\text{branch} \in \text{branches}'$}
        \begin{sdblock}{Random Loop}{errors > 0}
          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
          \end{call}
        \end{sdblock}

        \begin{sdblock}{Fitness Loop}{(fitness $\neq$ 0) $\vee$ gen.limit}

          \begin{sdblock}{Evaluation Loop}{p $\in$ pop}
            \begin{call}{server}{POST /genetic \{p\}}{client}{response}
            \end{call}

            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
            \end{callself}
          \end{sdblock}

          \begin{sdblock}{Crossover Loop}{errors > 0}
            \begin{call}{server}{cross = Crossover(pop)}{validator}{errors}
            \end{call}
          \end{sdblock}

          \begin{sdblock}{Mutation Loop}{errors > 0}
            \begin{call}{server}{mut=Mutation(cinfo, pop)}{validator}{errors}
            \end{call}
          \end{sdblock}
        \end{sdblock}
        \mess{server}{}{user}
      \end{sdblock}
    \end{call}
  \end{sequencediagram}
  \caption{Architecture of the test generation framework}
  \label{fig.framework.architect} 
\end{figure}

\begin{algorithm}[!t]
  \caption{Initialization Phase}
  \label{alg.init}
  \algsetup{linenosize=\tiny}
  \scriptsize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Input{
    $fun.js$ is a JS file with FUT and type annotation
  }
  \Output{
    tuple with $(cfg, branches, cinfo)$
  }
  \Fn{$Initialize(fun.js)$}{
    $(ast, sig) \longleftarrow ParseFunAndSig(fun.js)$\;
    $ast' \longleftarrow TransAST(ast)$\;
    $cfg \longleftarrow BuildCFG(ast')$\;
    $branches \longleftarrow GetBranches(ast')$\;
    $cinfo \longleftarrow GetConstInfo(ast')$\;
    $ifun \longleftarrow Instrument(ast')$\;
    $Send(POST, /init, \{ifun, sig\})$\;
    \Return{$(cfg, branches, cinfo)$}
  }
\end{algorithm}

\begin{algorithm}[!t]
  \caption{Genetic Phase}
  \label{alg.init}
  \algsetup{linenosize=\tiny}
  \scriptsize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Fn{$Genetic(b_N, cfg, cinfo, config)$}{
    $(size_P, size_A, size_G, rate_C, rate_M) \longleftarrow Read(config)$\;
    $archive \longleftarrow \emptyset$\;
    $i \longleftarrow 0 $\;
    $pop \longleftarrow Random(cinfo, size_P)$\;
    \Repeat{$isPerfect(f^*) \vee i > size_G $}{
      $scoredPop \longleftarrow \emptyset$\;
      \ForAll{$p \in pop$}{
        $(tr, d_B, d_L, consts) \longleftarrow Send(POST, /genetic, \{p\})$\;
        \tcp{evaluate $ifun(p: sig)$}
        $(f, p) \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\;
        $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
        $cinfo \longleftarrow consts \cup cinfo$\;
      }
      $combo \longleftarrow scoredPop \cup archive$\;
      $cross \longleftarrow Crossover(combo, rate_C)$\;
      $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\;
      $pop \longleftarrow cross \cup mut$\;
      $archive \longleftarrow GetBest(combo, size_A)$\;
      $(f^*, p^*) \longleftarrow head(archive)$\;
      $i \longleftarrow i + 1$\;
    }
    \Return{$(f^*, p^*)$} 
  }
\end{algorithm}

The general structure of the JavaScript test generation framework is depicted in Figure~\ref{fig.framework.architect}. It consists of three main components

\subsection{Initialization Phase}
\label{sub.sec.init.phase}

\subsection{Genetic Phase}
\label{sub.sec.genetic.phase}

The heart of our test data generation framework is its genetic phase. The main workflow of the underlying genetic algorithm (GA) is quite standard~\cite{poli2008field}. First, random population is generated. Then, this population is evaluated against given fitness function. If perfectly fitted candidate is found or the budget is exhausted, the algorithm terminates and reports the best candidate so far. Otherwise it enters an iterative phase where after a selections procedure some candidates are crossed over and others are mutated. Afterwards a new population is formed and the evaluation repeats.

In order to instantiate genetic algorithm for a particular problem, its user has to define all the aforementioned operations specific for the problem in question. Since GAs have been commonly used for generation of test data for primitive types such as integers and strings~\cite{paper_on_search-based_test_case_generation}, we skip their definitions and rather focus or the interesting case, namely, HTML generation.

\subsubsection{Random HTML Generation}
\label{sub.sub.sec.random.html}

We want to generate HTML as it is specified by WHATWG\footnote{\url{https://html.spec.whatwg.org}}. HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web. Recent HTML5 standard defines more than hundred of tags and attributes which both have to comply with extremely complex logic to constitute a syntactically valid HTML. Browsers are usually tolerant to syntactic errors in HTML. They will silently fix them and display the page anyway.

In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML. This was a challenge on its own because, as we have mentioned early, the complexity of HTML and lack of formal specification. Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs the library\footnote{\url{https://hackage.haskell.org/package/QuickCheck}} to define an \texttt{Arbitrary} instance for the \texttt{Html} data type. With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} highlights that definition. Data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) describes the internal state of \texttt{Html} during generation. The state is composed of the following components:
\begin{itemize}
\item \texttt{depth} and \texttt{degree} specify maximum depth and node degree of HTML respectively
\item \texttt{ctx} is the current value of the HTML content model stack 
\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
\item \texttt{tags}, \texttt{ids} and \texttt{classes} are predefined sets of HTML elements which are given preference in the generation process.  
\end{itemize}
Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}). Each HTML tag should be defined as a value of type \texttt{GenHtmlState}. Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} show an example of content generation for the \texttt{<html>} tag. According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag. First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively). Then, if depth is equal to zero, we just return some string constant (line~\ref{ref.generateHTML.returnString}). Otherwise, we update the state with the depth decreased by one, generate new content for \texttt{head} and \texttt{body}, and return their combination (lines~\ref{ref.generateHTML.updateState}, \ref{ref.generateHTML.newHead}, \ref{ref.generateHTML.newBody} and \ref{ref.generateHTML.end} respectively).

\begin{figure}[t]
  \begin{haskell}
instance Arbitrary Html where
  arbitrary = evalStateT generateHTML defaultState

generateHTML :: GenHtmlState |c \label{ref.generateHTML.begin} |c
generateHTML = do
  state <- get |c \label{ref.generateHTML.getState} |c   
  let d = getDepth state |c \label{ref.generateHTML.getDepth} |c
  if d == 0
  then lift \dollar return \dollar toHtml "HTML" |c \label{ref.generateHTML.returnString} |c
  else do put state{depth = d - 1} |c \label{ref.generateHTML.updateState} |c
           head <- generateHEAD |c \label{ref.generateHTML.newHead} |c
           body <- generateBODY |c \label{ref.generateHTML.newBody} |c
           lift\dollar return \dollar docTypeHtml \dollar head >> body |c \label{ref.generateHTML.end} |c

data Tag = HTML | HEAD | BODY | ...
type Context = CFlow | CMetadata | ...
data HtmlState = |c \label{ref.HtmlState.begin} |c
  HtmlState { depth      :: Int 
             , degree    :: Int    
             , ctx       :: Stack Context 
             , tagFreq   :: [(Int, Tag)] 
             , tags      :: [Tag]
             , ids       :: [String]
             , classes   :: [String] } |c \label{ref.HtmlState.end} |c
type GenState s = StateT s Gen |c \label{ref.GenState} |c
type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
  \end{haskell}
  \caption{\texttt{Arbitrary} instance for \texttt{Html} data type}
  \label{fig.html.arb.def}
\end{figure}

\subsubsection{Genetic HTML Operations}
\label{sub.sub.sec.genetic.oper}

In essence, HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels. Therefore crossover and mutations are defined similar to those concepts for the expression trees in genetic programming.

\textbf{HTML Crossover} takes two HTML trees, randomly picks a node in each tree, and returns the first tree with a sub-tree swapped from the second tree.

\textbf{HTML Mutations} are of three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}. \emph{NewTree} simply generate a new tree based on the given state of constant pool. \emph{DropTree} mutation selects a node in a tree and drops the sub-tree starting from that node. \emph{ShuffleAttributes} for a given tree and an attribute type, re-assigns the attributes of the specified type on that tree. Currently we instantiated the \emph{ShuffleAttributes} mutation for only for two types of attributes \emph{class} and \emph{id}, which gave us it total four variations for mutation. Each time a mutation is performed the type is chosen uniformly. In the future we consider experiment with assigning some priorities to curtain mutations.

\subsubsection{Fitness Function}
\label{sub.sub.sec.fitness.fun}

%% --------------------------------------------------------------------
\section{Empirical Evaluation}
\label{sec.evaluation}
%% --------------------------------------------------------------------

\begin{description}
\item[\textbf{Q1}] How often \emph{validator} rejects generated HTML in case of the random and genetic (mutation and crossover) phases. This question characterizes potential performance issues that can occur in the generation.     
\end{description}

\subsection{Case Studies}
\label{sub.sec.case.studies}

Consider examples from: \cite{artemis2011}, \cite{dom2011}...

%% --------------------------------------------------------------------
\section{Related Work}
\label{sec:related.work}
%% --------------------------------------------------------------------

\subsection{Search-Based Test Case Generation}
\label{sub.sec.search.based}

\subsection{Static Analysis of JavaScript}
\label{sub.sec.js.static.anal}

Static analysis is a powerful technique commonly used as solid alternative for program testing. In fact both techniques can benefit from one another. For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence. Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation. In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API. Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
\cite{jquery2014}

\subsection{Whole Web Application Testing}
\label{sub.sec.web.app.test}

Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application. It discoverers new tests by generating sequences of executable events and monitoring they effect on the state of the application. \cite{ail2013}

\subsection{JavaScript Unit Testing}
\label{sub.sec.js.unit.test}

Generating fixture for JavaScript unit tests by means of concolic execution~\cite{amin:ase15}. Inference of UI oracles to complement JS unit tests~\cite{icst16}.

\subsection{Misc JavaScript Testing Techniques}
\label{sub.sec.misc.test.tech}

Discover patterns from bug fixes and imposing them as potential bugs in the future~\cite{quinn:fse16}.

\section{Conclusion}
\label{sec:concl}
1 page.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%

%\balancecolumns

\end{document}

### 2016-12-14 doc/paper/paper.tex
work in progress

@@
 \usepackage{lsthaskell}
+\usepackage{xspace}
 \usepackage{algorithmic}
-\usepackage[linesnumbered, ruled]{algorithm2e} % language for algorithm description
+\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
 \hypersetup{
@@
 \listfiles % used to output the versions of all files being used by the latex
+
+\newcommand{\Server}{\emph{Server}\xspace}
+\newcommand{\Client}{\emph{Client}\xspace}
+\newcommand{\User}{\emph{User}\xspace}
+\newcommand{\Validator}{\emph{Validator}\xspace}
 
@@
 %% --------------------------------------------------------------------
+The general workflow of our JavaScript test generation framework is represented as a sequence diagram in Figure~\ref{fig.framework.architect}.
+The diagram consists of four interacting components: \User, \Server\, \Validator and \Client, where \Server is the main one.
+It performs all preparatory steps (\emph{Initialization Phase}) as well as controls the data generation (\emph{Genetic Phase}).
+These two phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
+
+Every request sent to \Validator\footnote{\url{https://validator.w3.org/nu/}} with an HTML document as the body triggers a response containing the list of syntactic errors in that document.
+\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JavaScript code.
+It relies on the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to simulate calls to native DOM.
+
+Let us get a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
+First, \User provides JS file (\emph{file.js}) that contains the function under test (FUT) together with its type and a configuration file \emph{config}.
+These data are processed by the \Server in the \emph{Initialization Phase}.
+As an output we get a tuple with the following information about FUT: control flow graph (\emph{cfg}), list of branches (\emph{branches}), static information about the program's constants (\emph{cinfo}), instrumented version of the original program (\emph{ifun}) and the function's signature (\emph{sig}).
+\Server sends a \texttt{POST} request to the \Client to store \emph{ifun} and \emph{sig}.
+Second, \Server asks \User to select a branch(s) that has to be covered by the execution of FUT.
+For each branch our framework triggers the \emph{Genetic Phase (Loop)}.
+Inside of this phase it starts with a randomly generated population (\emph{Random Loop}), and continues to improve it until earthier perfect value is found or generation limit is reached.
+Each candidate in the population has to be evaluated.
+\Client parses the candidate according the know signature, invokes \emph{ifun} on the result, collects some information along the execution and sends it back to \Server, where the final fitness value is computed for that candidate (\emph{Evaluation Loop}).
+New population is the formed as joint result of the \emph{Crossover} and \emph{Mutation Loop}.
+At the end of the \emph{Fitness Loop} the best candidate with the best fitness value is reported to \User.
+After exhausting all branches \emph{Genetic Loop} terminates.
 
@@
     \newinst{server}{Server}
-    \newinst{validator}{Validator}
+    \newinst[1]{validator}{Validator}
     \newinst{client}{Client}
@@
     \begin{call}{user}{file.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(file.js, config)}{server}{cfg, branches, cinfo, ifun, sig}
+      \begin{call}{server}{Initialize(file.js, config)}{server}{(cfg, branches, cinfo, ifun, sig)}
       \end{call}
@@
 
-      \begin{sdblock}{Genetic Loop}{$\text{branch} \in \text{branches}'$}
+      \begin{sdblock}{Genetic Loop}{\hspace{2mm}$\text{branch} \in \text{branches}'$}
         \begin{sdblock}{Random Loop}{errors > 0}
@@
           \end{call}
+          \prelevel
         \end{sdblock}
@@
           \begin{sdblock}{Evaluation Loop}{p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response}
+            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
             \end{call}
@@
             \end{callself}
+            \prelevel
           \end{sdblock}
@@
             \end{call}
+            \prelevel
           \end{sdblock}
@@
           \begin{sdblock}{Mutation Loop}{errors > 0}
-            \begin{call}{server}{mut=Mutation(cinfo, pop)}{validator}{errors}
+            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
             \end{call}
+            \prelevel
           \end{sdblock}
+
+          \begin{callself}{server}{cross $\cup$ mut}{pop}
+          \end{callself}
+          \prelevel
         \end{sdblock}
-        \mess{server}{}{user}
+        \mess{server}{best fitness}{user}
+
       \end{sdblock}
@@
   \end{sequencediagram}
-  \caption{Architecture of the test generation framework}
+  \caption{Architecture of the test framework}
   \label{fig.framework.architect} 
@@
 
-\begin{algorithm}[!t]
+\begin{algorithm}[t!]
   \caption{Initialization Phase}
@@
   \Fn{$Initialize(fun.js)$}{
-    $(ast, sig) \longleftarrow ParseFunAndSig(fun.js)$\;
+
+    $(ast, sig) \longleftarrow ParseFunAndSig(fun.js)$\label{alg1.parse.fun.sig}\;
     $ast' \longleftarrow TransAST(ast)$\;
@@
   \caption{Genetic Phase}
-  \label{alg.init}
+  \label{alg.gen}
   \algsetup{linenosize=\tiny}
@@
 \end{algorithm}
-
-The general structure of the JavaScript test generation framework is depicted in Figure~\ref{fig.framework.architect}. It consists of three main components
 

### 2016-12-15 doc/paper/paper.tex
described Init phase and started Genetic one

@@
   % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
+  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article, </span, <span, </span> 
   },
@@
   \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
 function safeAdd() {
@@
   \end{lstlisting}
-  \caption{Motivating Example}
-  \label{fig..safeAdd.js}
-\end{figure}
 
-\begin{figure}[t]
   \begin{lstlisting}[style=htmlcssjs, language=HTML5]
@@
 \end{lstlisting}    
-\caption{Motivating Example}
-\label{fig.safeAdd.html}
+  \caption{Stackoverflow Example}
+  \label{fig..safeAdd.js}
 \end{figure}
@@
   \end{lstlisting}
-  \caption{Motivating Example}
+
+  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
+<html>
+  <body>
+    <div id="square_0_0">
+      <span></span><span></span>
+    </div>
+    <div id="square_0_1">
+      <span></span><span></span>
+    </div>
+    <div id="square_1_0">
+      <span></span><span></span>
+    </div>
+    <div id="square_1_1">
+      <span></span><span></span>
+    </div>
+  </body>
+</html>
+  \end{lstlisting}  
+  \caption{Sudoku Example}
   \label{fig.revealAll.js}
@@
 %% --------------------------------------------------------------------
-The general workflow of our JavaScript test generation framework is represented as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of four interacting components: \User, \Server\, \Validator and \Client, where \Server is the main one.
-It performs all preparatory steps (\emph{Initialization Phase}) as well as controls the data generation (\emph{Genetic Phase}).
-These two phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Every request sent to \Validator\footnote{\url{https://validator.w3.org/nu/}} with an HTML document as the body triggers a response containing the list of syntactic errors in that document.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JavaScript code.
-It relies on the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to simulate calls to native DOM.
-
-Let us get a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-First, \User provides JS file (\emph{file.js}) that contains the function under test (FUT) together with its type and a configuration file \emph{config}.
-These data are processed by the \Server in the \emph{Initialization Phase}.
-As an output we get a tuple with the following information about FUT: control flow graph (\emph{cfg}), list of branches (\emph{branches}), static information about the program's constants (\emph{cinfo}), instrumented version of the original program (\emph{ifun}) and the function's signature (\emph{sig}).
-\Server sends a \texttt{POST} request to the \Client to store \emph{ifun} and \emph{sig}.
-Second, \Server asks \User to select a branch(s) that has to be covered by the execution of FUT.
-For each branch our framework triggers the \emph{Genetic Phase (Loop)}.
-Inside of this phase it starts with a randomly generated population (\emph{Random Loop}), and continues to improve it until earthier perfect value is found or generation limit is reached.
-Each candidate in the population has to be evaluated.
-\Client parses the candidate according the know signature, invokes \emph{ifun} on the result, collects some information along the execution and sends it back to \Server, where the final fitness value is computed for that candidate (\emph{Evaluation Loop}).
-New population is the formed as joint result of the \emph{Crossover} and \emph{Mutation Loop}.
-At the end of the \emph{Fitness Loop} the best candidate with the best fitness value is reported to \User.
-After exhausting all branches \emph{Genetic Loop} terminates.
 
@@
 
-    \begin{call}{user}{file.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(file.js, config)}{server}{(cfg, branches, cinfo, ifun, sig)}
+    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
+      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
       \end{call}
@@
 
+Given JS function $f$ and some set of its branches $B_f$, the purpose of our testing framework is to generate input arguments for $f$ that trigger executions covering all branches in $B_f$.
+The general workflow of the test generation process is represented as a sequence diagram in Figure~\ref{fig.framework.architect}.
+The diagram consists of four interacting components: \User, \Server\, \Validator and \Client.
+\Server is the key one.
+It performs all preparatory steps (\emph{Initialization Phase}) as well as controls the data generation (\emph{Genetic Phase}).
+These two phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
+Every request sent to \Validator\footnote{\url{https://validator.w3.org/nu/}} with an HTML document as the body triggers a response containing the list of syntactic errors in that document.
+\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JavaScript code.
+It relies on the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library simulating calls to native DOM.
+
+Let us get a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
+First, \User provides JS file \emph{fun.js} that defines the function under test (FUT) \emph{fun} annotated with its type.
+Additionally, user supplies a configuration file \emph{config} that parameterizes some settings related to the genetic algorithm, random generation, logging etc.
+These data are processed by \Server in the \emph{Initialization Phase}.
+As an output we get a tuple with the following information about $fun$: control flow graph (\emph{cfg}), list of branches (\emph{branches}), static information about constants (\emph{cinfo}), instrumented function (\emph{ifun}) and the function's signature (\emph{sig}).
+\Server sends a \texttt{POST} request to the \Client to store \emph{ifun} and \emph{sig}.
+Second, \Server asks \User to select a branch(s) that has to be covered by the execution of \emph{fun}.
+For each branch our framework enters the \emph{Genetic Loop}.
+Inside of this phase it starts with a randomly generated population (\emph{Random Loop}), and continues to optimize it until earthier perfect fitness is found or generation limit is exceeded.
+Each candidate in the population has to be evaluated (\emph{Evaluation Loop}).
+To do so \Client parses the candidate according the known signature \emph{sig}, invokes \emph{ifun} on the result, collects some information along the execution and sends it back to \Server, where the final fitness value is computed for the candidate.
+New population is formed as the joint result of the \emph{Crossover} and \emph{Mutation Loop}.
+These two loops together with the \emph{Random} one are performed in conversation with \Validator.
+It forces to proceed generation until no more errors are present in the data.
+At the end of the \emph{Fitness Loop} the best candidate with the best fitness value are reported back to \User.
+After exploring all branches \emph{Genetic Loop} terminates.
+
+\subsection{Initialization Phase}
+\label{sub.sec.init.phase}
+
 \begin{algorithm}[t!]
@@
   \Output{
-    tuple with $(cfg, branches, cinfo)$
+    tuple with $(cfg, branches, cinfo, ifun, sig)$
   }
@@
 
-    $(ast, sig) \longleftarrow ParseFunAndSig(fun.js)$\label{alg1.parse.fun.sig}\;
-    $ast' \longleftarrow TransAST(ast)$\;
-    $cfg \longleftarrow BuildCFG(ast')$\;
-    $branches \longleftarrow GetBranches(ast')$\;
-    $cinfo \longleftarrow GetConstInfo(ast')$\;
-    $ifun \longleftarrow Instrument(ast')$\;
-    $Send(POST, /init, \{ifun, sig\})$\;
-    \Return{$(cfg, branches, cinfo)$}
+    $(ast, sig) \longleftarrow ParseFunAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
+    $cinfo \longleftarrow GetConstInfo(ast)$\label{alg.init.collect.info}\;
+    $ast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
+    $cfg \longleftarrow BuildCFG(ast)$\label{alg.init.build.cfg}\;
+    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
+    $ifun \longleftarrow Instrument(ast)$\label{alg.init.instr}\;
+    \Return{$(cfg, branches, cinfo, ifun, sig)$}
     }
 \end{algorithm}
+
+The goal of the \emph{Initialization Phase} is to prepare FUT for the follow up \emph{Genetic Phase}.
+The main steps of the initialization are illustrated in Algorithm~\ref{alg.init}.
+Given the file \emph{fun.js} as an input, we separately parse the function and its signature in line~\ref{alg.init.parse.fun.sig}.
+Currently our framework recognizes signatures composed of four primitive types such as \texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string} and a newly introduced type \texttt{dom}.
+To facilitate random generation in the \emph{Genetic Phase} we statically analyze the FUT to collect useful data about potential string and numeric constants (line~\ref{alg.init.collect.info}).
+Moreover, we track calls to such browser API methods as \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, \texttt{getElementsByName}, which gives us information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} respectively.
+Knowing this data significantly increases our chances to produce a desired test input.
+Sometimes it is necessary to normalize FUT before applying instrumentation (line~\ref{alg.init.transform.ast}), e.g.
+we transform \emph{if-then} branches to \emph{if-then-else}.
+After the normalization we can build CFG (line~\ref{alg.init.build.cfg}) and get all branches (line~\ref{alg.init.get.branches}).
+The final step is to instrument \emph{fun} (line~\ref{alg.init.instr}) in order to collect some run-time data such as execution trace, branch and loop distances, and constants.
+This data will be required for fitness evaluation (Section~\ref{sub.sub.sec.fitness.fun}) and updating of \emph{cinfo}.
+
+\subsection{Genetic Phase}
+\label{sub.sec.genetic.phase}
 
@@
   \SetKwProg{Fn}{Function}{}{}
-  \Fn{$Genetic(b_N, cfg, cinfo, config)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M) \longleftarrow Read(config)$\;
-    $archive \longleftarrow \emptyset$\;
-    $i \longleftarrow 0 $\;
-    $pop \longleftarrow Random(cinfo, size_P)$\;
-    \Repeat{$isPerfect(f^*) \vee i > size_G $}{
+  \Input{
+    $b_N$ is target branch, $cfg$ is control-flow graph\\
+    $cinfo$ is constant info, $config$ is configuration file\\
+    $ifun$ instrumented JS function, $sig$ type signature
+  }
+  \Output{
+     element $p^*$ on which the best fitness $f^*$ is achieved  
+  }
+  \Fn{$Genetic(b_N, cfg, cinfo, config, ifun, sig)$}{
+    $(size_P, size_A, size_G, rate_C, rate_M) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
+    $archive \longleftarrow \emptyset$; $i \longleftarrow 0 $\label{alg.gen.arch.init}\;
+    $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
+    \Repeat{$isPerfect(f^*) \vee i > size_G $}{\label{alg.gen.loop.begin}
       $scoredPop \longleftarrow \emptyset$\;
       \ForAll{$p \in pop$}{
-        $(tr, d_B, d_L, consts) \longleftarrow Send(POST, /genetic, \{p\})$\;
-        \tcp{evaluate $ifun(p: sig)$}
+        $args \longleftarrow MakeArguments(p, sig)$\;
+        $(tr, d_B, d_L, consts) \longleftarrow ifun(args)$\;
         $(f, p) \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\;
@@
       $i \longleftarrow i + 1$\;
-    }
+    }\label{alg.gen.loop.end}
     \Return{$(f^*, p^*)$} 
@@
 
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
+The heart of our test data generation framework is in the \emph{Genetic Phase}.
+The main workflow of the underlying genetic algorithm (GA) is quite standard~\cite{poli2008field}, and with some adaptations presented in Algorithm~\ref{alg.gen}.
+We start with the reading of the \emph{config} file in line~\ref{alg.gen.read.config}.
+As a result we get information about the number of elements in a population ($size_P$), size of the archive ($size_A$), number of generations ($size_G$) and respectively crossover ($rate_C$) and mutation ($rate_M$) rates.
+\emph{Archive} has the size of  $size_A$ and stores the most fitted candidates observed so far.
+It is empty in the beginning of the evolution (line~\ref{alg.gen.arch.init}).
+First population of $size_P$ is randomly generated (line~\ref{alg.gen.random.gen}) based on the values passed through the \emph{cinfo}.
+Inside of the loop (lines~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}) we are trying optimize the ....
 
-\subsection{Genetic Phase}
-\label{sub.sec.genetic.phase}
-
-The heart of our test data generation framework is its genetic phase.
-The main workflow of the underlying genetic algorithm (GA) is quite standard~\cite{poli2008field}.
-First, random population is generated.
 Then, this population is evaluated against given fitness function.
-If perfectly fitted candidate is found or the budget is exhausted, the algorithm terminates and reports the best candidate so far.
+If the perfectly fitted candidate is found or the budget is exhausted, the algorithm terminates and reports the best candidate so far.
 Otherwise it enters an iterative phase where after a selections procedure some candidates are crossed over and others are mutated.
@@
 This question characterizes potential performance issues that can occur in the generation.
+\item[\textbf{Q2}] Efficiency (compare with random)  
 \end{description}

### 2016-12-17 doc/paper/paper.tex
described Genetic Algorithm

@@
       $scoredPop \longleftarrow \emptyset$\;
-      \ForAll{$p \in pop$}{
-        $args \longleftarrow MakeArguments(p, sig)$\;
-        $(tr, d_B, d_L, consts) \longleftarrow ifun(args)$\;
-        $(f, p) \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\;
+      \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
+        $args \longleftarrow MakeArguments(p, sig)$\label{alg.gen.make.args}\;
+        $(tr, d_B, d_L, consts) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
+        $f \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
         $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        $cinfo \longleftarrow consts \cup cinfo$\;
+        $cinfo \longleftarrow consts \cup cinfo$\label{alg.gen.eval.end}\;
       }
-      $combo \longleftarrow scoredPop \cup archive$\;
-      $cross \longleftarrow Crossover(combo, rate_C)$\;
-      $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\;
-      $pop \longleftarrow cross \cup mut$\;
-      $archive \longleftarrow GetBest(combo, size_A)$\;
-      $(f^*, p^*) \longleftarrow head(archive)$\;
+      $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
+      $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
+      $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
+      $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
+      $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
+      $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
       $i \longleftarrow i + 1$\;
     }\label{alg.gen.loop.end}
-    \Return{$(f^*, p^*)$} 
+    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
   }
@@
 The heart of our test data generation framework is in the \emph{Genetic Phase}.
-The main workflow of the underlying genetic algorithm (GA) is quite standard~\cite{poli2008field}, and with some adaptations presented in Algorithm~\ref{alg.gen}.
-We start with the reading of the \emph{config} file in line~\ref{alg.gen.read.config}.
-As a result we get information about the number of elements in a population ($size_P$), size of the archive ($size_A$), number of generations ($size_G$) and respectively crossover ($rate_C$) and mutation ($rate_M$) rates.
-\emph{Archive} has the size of  $size_A$ and stores the most fitted candidates observed so far.
+The main workflow of the underlying genetic algorithm (GA) is quite standard~\cite{poli2008field}, and with some adjustments is presented in Algorithm~\ref{alg.gen}.
+First, we read the \emph{config} file in line~\ref{alg.gen.read.config}.
+As a result, we get information about the number of elements in a population ($size_P$), size of the archive ($size_A$), number of generations ($size_G$) and respectively crossover ($rate_C$) and mutation ($rate_M$) rates.
+\emph{Archive} has the capacity of $size_A$ elements and stores the most fitted candidates observed so far.
 It is empty in the beginning of the evolution (line~\ref{alg.gen.arch.init}).
-First population of $size_P$ is randomly generated (line~\ref{alg.gen.random.gen}) based on the values passed through the \emph{cinfo}.
-Inside of the loop (lines~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}) we are trying optimize the ....
-
-Then, this population is evaluated against given fitness function.
-If the perfectly fitted candidate is found or the budget is exhausted, the algorithm terminates and reports the best candidate so far.
-Otherwise it enters an iterative phase where after a selections procedure some candidates are crossed over and others are mutated.
-Afterwards a new population is formed and the evaluation repeats.
+The first population consisting of $size_P$ elements is randomly constructed from the elements in \emph{cinfo} (line~\ref{alg.gen.random.gen}).
+Inside of the loop (lines~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}) we are evolving the population until either the perfect fitness is found or the generation limit $size_G$ is reached.
+But first step in this loop is to score the current population~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
+Each candidate in the population has to be converted to an argument list by coercing it to a respective type according to the signature $sig$ (line~\ref{alg.gen.make.args}).
+Calling the instrumented function $ifun$ on those arguments (line~\ref{alg.gen.call.ifun}), we get 4-tuple consisting of the execution trace ($tr$), the branch distances ($d_B$), the loop distances ($d_L$) and the new set of constants ($consts$) collected at the run time.
+The next step is actually to evaluate the fitness value of the given candidate (line~\ref{alg.gen.eval}).
+Collected constants $consts$ are added to the existing constants info $cinfo$ (line~\ref{alg.gen.eval.end}).
+Eventually the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) and is used for the crossover (line~\ref{alg.gen.cross}) and mutation steps (line~\ref{alg.gen.mut}).
+The rates specify the distribution in which the respective operations are applied to produce the new population (line~\ref{alg.gen.new.pop}).
+Scored population together with the current archive are sorted based on the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
+On top of the archive we have the most fitted candidate observed over the course of all iterations (line~\ref{alg.gen.archive.head}).
+The fitness value of that element defines if perfect candidate is found (line~\ref{alg.gen.loop.end}) and it is return at the end of the algorithm (line~\ref{alg.gen.return}).
 
@@
 
+Success of any search-based algorithm heavily depends on the choice of the fitness function (FF) that guides the search process. In our case FF is defined on CFG of the program.
+
+\[
+\mathcal{F}(n) = ...
+\]
+
 %% --------------------------------------------------------------------
@@
 
-\subsection{Static Analysis of JavaScript}
+\subsection{Static and Dynamic Analysis of JavaScript}
 \label{sub.sec.js.static.anal}
@@
 
+ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
+
+Jalangi is dynamic analysis framework for JavaScript \cite{sen2013jalangi}.
+
+Dynamic type inconsistency analysis (implemented on top Jalangi) for JavaScript\cite{pradel2015typedevil}.
+
+Salable dynamic analysis framework for JS based on shadow executions~\cite{create_citation}.
+
+Information-flow security for JS~\cite{hedin2012information}.
+
 \subsection{Whole Web Application Testing}
@@
 
+Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
+
+Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
+
+Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
+
+Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
+
+DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
+
+\subsection{Formal Techniques}
+\label{sub.sec.formal}
+
+Modeling and reasoning about DOM events~\cite{lerner2012modeling}.
+
 \subsection{JavaScript Unit Testing}
@@
 Generating fixture for JavaScript unit tests by means of concolic execution~\cite{amin:ase15}. Inference of UI oracles to complement JS unit tests~\cite{icst16}.
+
+JS unit test generation by means of symbolic execution~\cite{tanida2014automatic}.
+
+Flycatcher~\cite{deautomatic}
 

### 2016-12-17 Genetic/MutationJS.hs

@@ -59,7 +59,7 @@ mutateHtml_newRandom :: JSCPool -> IO ByteString
 mutateHtml_newRandom pool = do
   let logger  = rootLoggerName
       setPool = removeDuplicates pool
-  noticeM logger $ "Constant pool data: " ++ (show setPool)
+  debugM logger $ "Constant pool data: " ++ (show setPool)
   debugM rootLoggerName $ "Mutation: generate new html:"
   genRandomDom $ getJSDoms setPool
 
@@ -71,7 +71,7 @@ mutateHtml_reassignIds pool html = do
       tagIds  = getJSIds setPool
       plain_html = removeAttributeFromDocument "id" $ bytestring2document html
   debugM rootLoggerName $ "Mutate element:\n" ++ (prettyHtmlByteString html)    
-  noticeM logger $ "Constant pool data: " ++ (show setPool)
+  debugM logger $ "Constant pool data: " ++ (show setPool)
   new_html <- liftM document2bytestring $ assignIdsToDocumentRandomly tagIds plain_html
   debugM rootLoggerName $ "Mutation result: re-assign ids:\n" ++ (prettyHtmlByteString new_html)
   setCondBreakPoint
@@ -85,7 +85,7 @@ mutateHtml_reassignClasses pool html = do
       tagClasses = getJSClasses setPool
       plain_html = removeAttributeFromDocument "class" $ bytestring2document html
   debugM rootLoggerName $ "Mutate element:\n" ++ (prettyHtmlByteString html)    
-  noticeM logger $ "Constant pool data: " ++ (show setPool)
+  debugM logger $ "Constant pool data: " ++ (show setPool)
   new_html <- liftM document2bytestring $ assignClassesToDocumentRandomly tagClasses plain_html
   debugM rootLoggerName $ "Mutation result: re-assign classes:\n" ++ (prettyHtmlByteString new_html)
   setCondBreakPoint

### 2016-12-17 Genetic/RandomJS.hs

@@ -19,7 +19,7 @@ import Util.Debug (setCondBreakPoint)
 genRandomVal :: JSCPool -> JSType -> IO JSArg
 genRandomVal pool tp = do
   debugM rootLoggerName  $ "Generating random value of type: " ++ (show tp)
-  noticeM rootLoggerName $ "Constant pool data: " ++ (show pool)
+  debugM rootLoggerName $ "Constant pool data: " ++ (show pool)
   debugM rootLoggerName $ "Generated random value is:"
   genRandomVal' pool tp
 

### 2016-12-17 Genetic/ScoreJS.hs

@@ -60,11 +60,11 @@ fitnessScore tg@(Target cfg loc@(from, to, _))  jargs = do
                  then return 0
                  else computeFitness cfg (map2IntMap loops_) to trace_ distances_
   -- infoM logger $ "Computing approach level for the location: " ++ (show exitLoc) ++ " along the path: " ++ (show trace_)
-  -- fitnessVal2 <- computeFitness cfg exitLoc trace_ distances_
+  fitnessVal2 <- computeFitness cfg (map2IntMap loops_) (-1) trace_ distances_
   -- fitnessVal2 <- return $ fromIntegral $ distanceToExit cfg trace_
   -- infoM logger $ "FitnessVal2: " ++ (show fitnessVal2)
-  -- let fitnessVal = fitnessVal1 + 0.001 * fitnessVal2
-  let fitnessVal = fitnessVal1
+  let fitnessVal = fitnessVal1 + 0.001 * fitnessVal2
+  -- let fitnessVal = fitnessVal1
   noticeM logger $ "Final Fitness value is equal to: " ++ (show fitnessVal)
 
   setCondBreakPoint

### 2016-12-17 JS/geneticServerES6.js

@@ -9,8 +9,8 @@ const _          = require('underscore');
 const instrument = require("./instrumentLib.js");
 const winston    = require('winston');
 
-// winston.level = 'info';
-winston.level = 'debug';
+winston.level = 'info';
+// winston.level = 'debug';
 winston.remove(winston.transports.Console);
 winston.add(winston.transports.Console, {'timestamp': () => (new Date()).toJSON()});
 

### 2016-12-17 examples/apps/sudoku/revealAll.js

@@ -6,8 +6,7 @@ function test() {
       var spans = obj.getElementsByTagName('SPAN');
       spans[0].style.display='';
       spans[1].style.display='none';
-      // spans[1].style.color='#000000';
+      spans[1].style.color='#000000';
     }
   }
-  gameFinished=true;
 }

### 2016-12-19 doc/paper/paper.tex
minor changes

@@
 \[
-\mathcal{F}(n) = ...
+\mathcal{F}(n) = 
+\]
+
+\[
+\mathcal{F}^*(n) = \mathcal{F}(n) + \lambda * \mathcal{F}(n_e)
 \]
@@
 
+For the purpose of validation we selected two classes of programs.
+The first class only includes JS programs composed of the primitive types.
+The programs in the second class additionally accept arguments of the DOM type.
+We collected those program from several researches in the field of web application analysis, and JS in particular.
+Moreover, we introduced few other subjects found in open source such as \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}}.
+
 Consider examples from: \cite{artemis2011}, \cite{dom2011}...
+
+\subsection{Limitations}
+\label{sub.sec.eval.limit}
+
+Our framework imposes certain constraints on the structure of JS programs:
+\begin{itemize}
+\item no inter-procedural function calls
+\item no recursion  
+\end{itemize}
 

### 2016-12-19 Analysis/CFG/Util.hs
integer GA generation

@@ -177,7 +177,8 @@ expr2objFun (PrefixExpr l prOp ex)         =
                       BoolLit _ _               -> expr2objFun $ propogateNeg ex
                       PrefixExpr _ PrefixLNot _ -> expr2objFun $ propogateNeg ex
                       InfixExpr _ _ _ _         -> expr2objFun $ propogateNeg ex
-                      _                         -> CallExpr def (VarRef def (Id def distanceNegZero)) [ex] 
+                      _                         -> CallExpr def (VarRef def (Id def distanceNegZero)) [ex]
+expr2objFun (CallExpr l  ex exs)           = VarRef def (Id def failureConst)
 -- expr2objFun (UnaryAssignExpr l unAsOp val) = undefined
 -- expr2objFun (CondExpr l ex1 ex2 ex3)       = undefined
 -- expr2objFun (AssignExpr l asOp val ex)     = undefined
@@ -262,10 +263,10 @@ evalLoopTree (Leaf _) = 1
 
 list2LoopTree ::  LoopIterationMap -> GPath -> LoopTree
 list2LoopTree _ [] = error "list2LoopTree: loop can't be empty"
-list2LoopTree iterMap (head:body) =
+list2LoopTree iterMap path@(head:body) =
   case (IntMap.lookup head iterMap) of
    Just iterN -> Node iterN head (map Leaf body)
-   Nothing    -> error "list2LoopTree: there is no info about max iteration number for given loop"
+   Nothing    -> trace ("no info about loop: " ++ (show head)) $ Node 10 head (map Leaf body)  
 
 buildLoopMaxSizeMap :: Gr NLab ELab -> LoopIterationMap -> LoopMaxSizeMap
 buildLoopMaxSizeMap gr iterMap =

### 2016-12-19 JS/geneticServerES6.js

@@ -9,8 +9,8 @@ const _          = require('underscore');
 const instrument = require("./instrumentLib.js");
 const winston    = require('winston');
 
-winston.level = 'info';
-// winston.level = 'debug';
+// winston.level = 'info';
+winston.level = 'debug';
 winston.remove(winston.transports.Console);
 winston.add(winston.transports.Console, {'timestamp': () => (new Date()).toJSON()});
 

### 2016-12-19 Main.hs

@@ -89,15 +89,18 @@ main = do
   -- | Instrument and statically analize JS program
   (jsFile:_) <- getArgs
   debugM logger $ "JavaScript file given for the analysis: " ++ (show jsFile)
-  jsFun <- liftM transfromJS $ parseFromFile jsFile
-  jsSig <- parseJSSignature jsFile
+  jsFileContent <- parseFromFile jsFile
+  jsSig <- parseJSSignature jsFile  
   debugM logger $ "JS function signature: " ++ (show jsSig)
-  let jsLabFun@(Script l jsLabStms) = fst $ flip runState 0 $ assignUniqueIdsSt jsFun
-      jsFunCFG      = uncurry mkGraph $ enrichCollectedEdges jsLabStms
+  let jsFun         = transfromJS jsFileContent               
+      (Script l (jsLabFun':jsLabStms)) = fst $ flip runState 0 $ assignUniqueIdsSt jsFun
+      jsLabFun      = Script l [jsLabFun'] 
+      jsFunCFG      = uncurry mkGraph $ enrichCollectedEdges [jsLabFun']
       branches      = getAllBranches jsFunCFG
       labBranches   = zip [1..] branches
       constPool     = collectConstantInfoJS jsLabFun
-      jsLabFunInstr = instrScript jsLabFun
+      jsLabFunInstr@(Script _ [jsLabFunInstrStmt]) = instrScript jsLabFun
+      jsLabFunInstrFile = Script l (jsLabFunInstrStmt:jsLabStms)
   noticeM logger "The function has the following CFG:\n"
   system $ "echo " ++ (show $ showDot $ fglToDotString jsFunCFG) ++ " | graph-easy --as_ascii"
   noticeM logger $ "Instrumented version of the analysed function:\n" ++ (show $ JSP.prettyPrint jsLabFunInstr)
@@ -114,7 +117,7 @@ main = do
                         , requestHeaders = [(CI.mk "Content-Type", "text/html;charset=UTF-8")]
                         , requestBody = RequestBodyLBS
                                         $ encode
-                                        $ InitData (T.pack $ show $ JSP.prettyPrint jsLabFunInstr)
+                                        $ InitData (T.pack $ show $ JSP.prettyPrint jsLabFunInstrFile)
                                         $ map (T.pack . show) jsSig
                         }
   initResp <- httpLbs reqInit man

### 2017-11-05 python/evaluation.py
Added missing generation for genetic with 5 iterations before restart

@@ -51,7 +51,7 @@ case_studies = [
     # bingbong + "doPaddlePower.js",  # -
     # bingbong + "drawLevel.js",      # -
     # bingbong + "goPing.js",
-    bingbong + "initBricks.js",     # -
+    # bingbong + "initBricks.js",     # -
 
     # burncanvas + "do_draw.js",      # -
     # burncanvas + "modify_region.js",
@@ -59,7 +59,7 @@ case_studies = [
     # csjs + "luhn-algorithm.js",
     # csjs + "quicksort_partition.js",
 
-    # mathjs + "probability_gamma.js"  # +
+    mathjs + "probability_gamma.js"  # +
 ]
 
 eval_type = sys.argv[1]

### 2017-11-05 doc/icse2018/icse2018.tex
Added new version of the papper.

--- 2016-12-19 doc/paper/paper.tex
@@
-% This is "sig-alternate.tex" V2.1 April 2013
-% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
-%
-% This example file demonstrates the use of the 'sig-alternate.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to ACM Conference Proceedings WHO DO NOT WISH TO
-% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
-% The 'sig-alternate.cls' file will produce a similar-looking,
-% albeit, 'tighter' paper resulting in, invariably, fewer pages.
-%
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V2.5) produces:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) NO page numbers
-%
-% as against the acm_proc_article-sp.cls file which
-% DOES NOT produce 1) thru' 3) above.
-%
-% Using 'sig-alternate.cls' you have control, however, from within
-% the source .tex file, over both the CopyrightYear
-% (defaulted to 200X) and the ACM Copyright Data
-% (defaulted to X-XXXXX-XX-X/XX/XX).
-% e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
-% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
-%
-% ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% ================= IF YOU HAVE QUESTIONS =======================
-% Questions regarding the SIGS styles, SIGS policies and
-% procedures, Conferences etc. should be sent to
-% Adrienne Griscti (griscti@acm.org)
-%
-% Technical questions _only_ to
-% Gerald Murray (murray@hq.acm.org)
-% ===============================================================
-%
-% For tracking purposes - this is V2.0 - May 2012
+\documentclass[sigconf]{acmart}
 
-\documentclass{sig-alternate}
+\usepackage{booktabs} % For formal tables
 \usepackage{tikz}
@@
 \usepackage{algorithmic}
+\usepackage{longtable}
+\usepackage{longtable}
 \usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
@@
 \newcommand{\Validator}{\emph{Validator}\xspace}
-
-\begin{document}
+\newcommand{\thenBr}{\text{then}}
+\newcommand{\elseBr}{\text{else}}
+\newcommand{\inFor}{\text{inFor}}
+\newcommand{\inWhile}{\text{inWhile}}
 
 % Copyright
-\setcopyright{acmcopyright}
+%\setcopyright{none}
+%\setcopyright{acmcopyright}
 %\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
+\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
 % DOI
-\doi{10.475/123_4}
+\acmDOI{10.475/123_4}
 
 % ISBN
-\isbn{123-4567-24-567/08/06}
+\acmISBN{123-4567-24-567/08/06}
 
 %Conference
-\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
+  Paso, Texas USA} 
+\acmYear{1997}
+\copyrightyear{2016}
 
-\acmPrice{\$15.00}
+\acmPrice{15.00}
 
-%
-% --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
+\begin{document}
+\title{Search-Based Test Data Generation for JavaScript Functions with DOM}
 
-\title{Search-Based Test Data Generation for JavaScript Functions on DOM}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
+%% \author{
+%%   \alignauthor Alexander Elyasov, Wishnu Prasetya, Jurriaan Hage\\ 
+%%   \affaddr{Utrecht University, The Netherlands}\\
+%%   \email{\{a.elyasov,s.w.b.prasetya,j.hage\}@uu.nl}
+%% }
 
-\numberofauthors{1}
+\author{Alexander Elyasov}
+\affiliation{%
+  \institution{Utrecht University}
+  \city{Utrecht} 
+  \country{The Netherlands} 
+}
+\email{a.elyasov@uu.nl}
 
-\author{
-  \alignauthor Alexander Elyasov, Wishnu Prasetya, Jurriaan Hage\\ 
-  \affaddr{Utrecht University, The Netherlands}\\
-  \email{\{a.elyasov,s.w.b.prasetya,j.hage\}@uu.nl}
+\author{Wishnu Prasetya}
+\affiliation{%
+  \institution{Utrecht University}
+  \city{Utrecht} 
+  \country{The Netherlands} 
 }
+\email{s.w.b.prasetya@uu.nl}
 
-\maketitle
+\author{Jurriaan Hage}
+\affiliation{%
+  \institution{Utrecht University}
+  \city{Utrecht} 
+  \country{The Netherlands} 
+}
+\email{j.hage@uu.nl}
+
 \begin{abstract}
-
+This paper provides a sample of a \LaTeX\ document which conforms,
+somewhat loosely, to the formatting guidelines for
+ACM SIG Proceedings.\footnote{This is an abstract footnote}
 \end{abstract}
@@
 
-\printccsdesc
+\keywords{ACM proceedings, \LaTeX, text tagging}
 
-% We no longer use \terms command
-%\terms{Theory}
-
-\keywords{ACM proceedings; \LaTeX; text tagging}
+\maketitle
 
@@
 
-Success of any search-based algorithm heavily depends on the choice of the fitness function (FF) that guides the search process. In our case FF is defined on CFG of the program.
+Success of any search-based algorithm heavily relies on the choice of the fitness function (FF) that guides the evolution process.
+Our search target is a specific branch of the program under test that we want to cover by generating a valid input data.
+The input is \emph{valid} only if the program normally terminates on it, i.e.
+without premature exception.
+Thus, our search target is an ordered pair of CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node of the program.
+FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and the normalized \emph{branch distance}\cite{arcuri2010does}.
+\[
+\mathcal{F}(n) = \text{Approach Level} + \alpha({\text{Branch Distance}})
+\]
+
+Therefore, the resulted FF ($\mathcal{F}^*$) is an ordered pair of the FFs of the respective nodes.
 
 \[
-\mathcal{F}(n) = 
-\]
-
-\[
-\mathcal{F}^*(n) = \mathcal{F}(n) + \lambda * \mathcal{F}(n_e)
+\mathcal{F}^*(n_b, n_x) = (\mathcal{F}(n_b), \mathcal{F}(n_x))
 \]
@@
 
+To report on cyclomatic complexity we use \emph{jshint}\footnote{http://jshint.com/} (we can also use this tool\footnote{http://jsmeter.info/})
+
+\begin{table*}
+  \caption{Summary of the case studies}
+  \label{tbl.case.studies}
+  %\resizebox{\textwidth}{!}{
+    \footnotesize
+  \begin{tabular}{l|l|l|r|r|r|c|c|c|c}
+    \toprule
+    \textbf{case-study} & \textbf{function} & \textbf{type} & \textbf{\#BR} & \textbf{\#LOC} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
+    \midrule
+    sudoku     & helpMe & (dom,int,int) & & & & + & + & + & - \\
+    sudoku     & isGameFinished & (dom) & & & & + & + & + & + \\
+    sudoku     & newGame & (dom)        & & & & + & + & + & + \\
+    sudoku     & revealAll & (dom)      & & & & + & + & + & - \\
+    sudoku     & shuffleBoard & (dom)   & & & & + & - & + & - \\
+    \midrule
+    phormer    & toggleInfo & (dom,string) & & & & + & + & - & - \\
+    \midrule
+    hotel RS   & isValidCard & ([int]) & & & & - & - & - & - \\
+    hotel RS   & isValidMasterCard & ([int])  & & & & - & - & - & - \\
+    \midrule
+    apophis    & initShields & (dom,[int],int,int) & & & & + & + & - & -\\
+    \midrule
+    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & & & & + & + & - & - \\
+    bingbong   & initBricks & (dom,[int],int,int) & & & & + & + & - & - \\
+    \midrule
+    burncanvas & do\_draw & (int,int,int,int,int,int,int) & & & & - & - & - & - \\
+    \midrule
+    mathjs     & probability\_gamma & (float) & & & & - & - & - & - \\
+    \bottomrule
+  \end{tabular}
+%}
+\end{table*}
+
+\begin{table*}
+  \caption{Statistics for genetic and random algorithms}
+  \label{tbl.stats}
+  \resizebox{\textwidth}{!}{
+    \footnotesize
+    \begin{tabular}{l|rrrr|rrrr|rrrr|rrrr|r|r|r|r|r|r}
+      \toprule
+      \textbf{name}     & $\bar{x}_R$ & $\bar{x}_G$ & $\bar{x}_{G5}$ & $\bar{x}_{G10}$ & $m_R$ & $m_G$ & $m_{G5}$ & $m_{G10}$ & $\min_R$ & $\min_G$ & $\min_{G5}$ & $\min_{G10}$ & $\max_R$ & $\max_G$ & $\max_{G5}$ & $\max_{G10}$ & \textbf{R-G} & \textbf{R-G5} & \textbf{R-G10} & \textbf{G-G5} & \textbf{G-G10} & \textbf{G5-G10}\\
+      \toprule
+      helpMe          &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
+    $(3,4,\inFor)$    & 3.94        & 7.94        & 10.22          & 11.7          & 3     & 3.5   & 7       & 7       & 1        & 1        & 1          & 1           & 16       & 31      & 63         & 124 & & & & & & \\
+    $(5,6,\thenBr)$   & 3.7         & 13.08       & 9.2            & 9.6           & 3     & 7     & 5       & 5.5     & 1        & 1        & 1          & 1           & 14       & 95      & 44         & 105 & & & & & & \\
+    $(5,15,\elseBr)$  & 118.64      & 30.14       & 34.12          & 31.68         & 119.5 & 23    & 28.5    & 22      & 4        & 4        & 3          & 1           & 199      & 97      & 167        & 114 & & & & & & \\
+    $(9,10,\thenBr)$  & 105.12      & 17.82       & 21.98          & 21.8          & 83.5  & 17    & 17.5    & 18      & 18       & 1        & 2          & 6           & 199      & 53      & 78         & 77  & & & & & & \\
+    $(9,14,\elseBr$   & 4.28        & 5.06        & 8.14           & 9.56          & 2.5   & 5     & 4       & 4       & 1        & 1        & 1          & 1           & 17       & 20      & 49         & 74  & & & & & & \\
+    \midrule
+    isGameFinished    &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
+    %% $(5,6,\inFor)$    & 0.02        & 0.1         & 0.12           & 0.1           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 2       & 2          & 2   \\
+    $(7,8,\thenBr)$   & 75.18       & 40.54       & 18.86          & 14.66         & 35.5  & 7     & 8       & 11      & 0        & 0        & 0          & 0           & 199      & 199     & 199        & 82  & & & & & & \\
+    %% $(7,15,\elseBr)$  & 0           & 0.06        & 0.04           & 0.08          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 0        & 2       & 1          & 2   \\
+    $(10,11,\thenBr)$ & 199         & 35.74       & 21.56          & 24.36         & 199   & 10    & 10      & 9       & 199      & 1        & 1          & 1           & 199      & 199     & 199        & 199 & & & & & & \\
+    $(10,14,\elseBr)$ & 69.62       & 56.32       & 28.74          & 31.92         & 23.5  & 10    & 16.5    & 18      & 1        & 0        & 0          & 0           & 199      & 199     & 199        & 199 & & & & & & \\
+    \midrule
+    newGame           &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
+    %% $(4,5,\inFor)$    & 0.04        & 0.12        & 0.1            & 0             & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 2       & 1          & 0 \\
+    $(6,7,\thenBr)$   & 21.54       & 10.48       & 9.92           & 8.34          & 15    & 7.5   & 7.5     & 7       & 0        & 0        & 0          & 0           & 97       & 53      & 30         & 35 & & & & & & \\
+    %% $(6,12,\elseBr)$  & 0.06        & 0.14        & 0.1            & 0.04          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 3       & 2          & 1\\
+    \midrule
+    revealAll         &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
+    $(2,3,\inFor)$    & 31.78       & 24.84       & 34.94          & 28.04         & 24    & 23    & 29      & 22.5    & 4        & 7        & 7          & 10          & 106      & 57      & 129        & 75 & & & & & & \\
+    $(4,5,\inFor)$    & 46.12       & 26.22       & 30.1           & 27.64         & 34    & 19    & 26.5    & 22      & 5        & 9        & 9          & 6           & 199      & 78      & 71         & 90 & & & & & & \\
+    \midrule
+    shuffleBoard      &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
+    %% $(5,6,\inWhile)$  & 0.36        & 0.32        & 0.24           & 0.48          & 0     & 0     & 0.24    & 0       & 0        & 0        & 0          & 0           & 4        & 3       & 2          & 0\\
+    $(13,14,\thenBr)$ & 6.38        & 7.7         & 8.72           & 7.86          & 4     & 4     & 8.72    & 4       & 0        & 0        & 0          & 0           & 22       & 67      & 64         & 38 & & & & & & \\
+    $(17,18,\thenBr)$ & 5.66        & 11.86       & 16.96          & 17.72         & 3.5   & 5.5   & 16.96   & 3.5     & 0        & 0        & 0          & 0           & 33       & 133     & 86         & 118 & & & & & & \\
+    %% $(21,22,\inFor)$  & 199         & 199         & 199            & 199           & 199   & 199   & 199     & 199     & 0        & 0        & 0          & 0           & 199      & 199     & 199        & 199\\
+    \midrule
+    \midrule
+    toggleInfo        &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
+    $(2,3,\thenBr)$   & 1.58        & 1.12        & 1.1            & 1             & 1     & 1     & 1       & 1       & 0        & 0        & 0          & 0           & 11       & 4       & 3          & 3 & & & & & & \\
+    $(6,7,\thenBr)$   & 1.48        & 9.9         & 17             & 15.3          & 1     & 2     & 4       & 4       & 0        & 0        & 0          & 0           & 8        & 125     & 143        & 136 & & & & & & \\
+    \midrule
+    \midrule
+    isValidCard       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
+    $(3,6,\elseBr)$   & 199         & 2.98        & 3              & 2.82          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 5          & 4 & & & & & & \\
+    $(7,8,\inFor)$    & 199         & 2.92        & 3.04           & 2.96          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 4          & 5 & & & & & & \\
+    $(10,11,\thenBr)$ & 199         & 3           & 2.86           & 3.06          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
+    $(10,13,\elseBr)$ & 199         & 2.84        & 2.98           & 3.04          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
+    $(14,15,\inFor)$  & 199         & 3.02        & 2.92           & 2.94          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
+    \midrule
+    isValidMasterCard & \multicolumn{16}{l}{} \\ 
+    $(2,3,\thenBr)$   & 199         & 11.04       & 12.08          & 11.42         & 199   & 10    & 12      & 12      & 199      & 4        & 5          & 5           & 199      & 27      & 32         & 23 & & & & & & \\
+    %% isValidVISA       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
+    %% $(2,3,\thenBr)$   & 199         & 6.54        & 6.38           & 6.48          & 199   & 6     & 6       & 6       & 199      & 4        & 3          & 4           & 199      &  14     & 16         & 18  \\
+    \midrule
+    \midrule
+    initShields       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
+    $(2,3,\inFor)$    & 5           & 5.32        & 5.28           & 5.26          & 5     & 5     & 5       & 5       & 5        & 5        & 5          & 5           & 5        & 6       & 7          & 7 & & & & & & \\
+    \midrule
+    \midrule
+    brickJiggler      &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
+    $(2,3,\thenBr)$   & 5.22        & 5.34        & 5.68           & 5.3           & 5     & 4     & 4       & 4       & 1        & 2        & 1          & 1           & 18       & 39      & 20         & 20 & & & & & & \\
+    doPaddlePower     &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
+    %% $(5,8,\elseBr)$   & 0.14        & 0.4         & 0.14           & 0.28          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 5       & 3          & 5 \\
+    $(10,11,\thenBr)$ & 17.96       & 193.14      & 47.18          & 42.5          & 14.5  & 199   & 17      & 21      & 0        & 3        & 0          & 0           & 53       & 199     & 199        & 199 & & & & & & \\
+    %% drawLevel         &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
+    %% $(5,6,\thenBr)$   & 0.18        & 0.16        & 0.14           & 0.2           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 2        & 3       & 5          & 5 \\
+    %% $(8,9,\inFor)$    & 0.1         & 0.16        & 0.34           & 0.3           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 3        & 5       & 5          & 5 \\
+    %% $(10,11,\thenBr)$ & 0.64        & 1.26        & 0.98           & 0.8           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 3        & 7       & 7          & 8 \\
+    %% $(10,13,\elseBr)$ & 0.06        & 0.22        & 0.3            & 0.2           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 3       & 7          & 3 \\
+    %% $(14,15,\inFor)$  & 0.08        & 0.34        & 0.3            & 0.36          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 7       & 4          & 6 \\
+    \midrule
+    initBricks        &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
+    $(6,7,\thenBr)$   & 1.5         & 3           & 2.6            & 2.74          & 1     & 4     & 2       & 2       & 1        & 1        & 1          & 1           & 5        & 5       & 5          & 5 & & & & & & \\
+    $(6,10,\elseBr)$  & 29.82       & 5.98        & 5.28           & 7.1           & 13.5  & 5     & 5       & 5       & 1        & 1        & 1          & 1           & 199      & 14      & 13         & 24 & & & & & & \\
+    $(11,12,\thenBr)$ & 162.28      & 18.36       & 27.58          & 25.26         & 199   & 13    & 16.5    & 16      & 2        & 5        & 4          & 4           & 199      & 56      & 71         & 77 & & & & & & \\
+    $(11,15,\elseBr)$ & 32.44       & 5.9         & 6.02           & 8.1           & 17    & 5     & 6       & 5       & 1        & 1        & 1          & 1           & 199      & 16      & 28         & 55 & & & & & & \\
+    $(16,17,\thenBr)$ & 164.06      & 25.14       & 37.48          & 28.64         & 199   & 16    & 12.5    & 16      & 4        & 4        & 1          & 2           & 199      & 199     & 199        & 112 & & & & & & \\
+    $(16,20,\elseBr)$ & 57.22       & 8.32        & 12.2           & 10.92         & 23.5  & 6     & 5       & 7       & 1        & 1        & 1          & 1           & 199      & 62      & 68         & 86 & & & & & & \\
+    $(21,22,\thenBr)$ & 152.56      & 19.38       & 30.92          & 40.12         & 199   & 13    & 12.5    & 16      & 1        & 1        & 2          & 2           & 199      & 199     & 117        & 149 & & & & & & \\
+    $(21,25,\elseBr)$ & 56.34       & 6.88        & 11.56          & 12.82         & 24.5  & 6     & 6       & 6.5     & 2        & 2        & 1          & 1           & 199      & 22      & 91         & 80 & & & & & & \\
+    $(29,30,\thenBr)$ & 147.66      & 102.66      & 91             & 96.48         & 199   & 65    & 69.5    & 73      & 2        & 5        & 5          & 5           & 199      & 199     & 199        & 199& & & & & & \\
+    $(29,37,\elseBr)$ & 1.46        & 2.5         & 2.52           & 2.78          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 5        & 6       & 5          & 5 & & & & & & \\
+    $(38,39,\thenBr)$ & 145.72      & 108.1       & 94.46          & 89.2          & 184   & 84    & 74.5    & 46.5    & 16       & 4        & 11         & 4           & 199      & 199     & 199        & 199& & & & & & \\
+    $(38,46,\elseBr)$ & 1.42        & 2.5         & 2.7            & 2.5           & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 6       & 6          & 5 & & & & & & \\
+    $(47,48,\thenBr)$ & 141.5       & 121         & 112.16         & 108.1         & 185.5 & 199   & 118     & 125.5   & 2        & 5        & 5          & 6           & 199      & 199     & 199        & 199 & & & & & & \\
+    $(47,55,\elseBr)$ & 1.54        & 2.44        & 2.5            & 2.46          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 4        & 5       & 5          & 5 & & & & & & \\
+    $(56,57,\thenBr)$ & 111.98      & 96.62       & 94.8           & 90.16         & 108   & 48.5  & 113     & 48      & 3        & 5        & 5          & 4           & 199      & 199     & 199        & 199 & & & & & & \\
+    $(56,64,\elseBr)$ & 1.52        & 2.66        & 2.96           & 2.48          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 5       & 13         & 5 & & & & & & \\
+    $(69,70,\thenBr)$ & 1.42        & 2.64        & 2.8            & 2.52          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 6       & 7          & 6 & & & & & & \\
+    $(69,71,\elseBr)$ & 74.98       & 102.98      & 54.82          & 55.42         & 39.5  & 93.5  & 20      & 26      & 1        & 2        & 1          & 1           & 199      & 199     & 199        & 199 & & & & & & \\
+    \midrule
+    \midrule
+    do\_draw           &             &            &               &                &       &       &         &         &           &          &           &             &          &          &           & & & & & & & \\
+    $(6,7,\thenBr)$    & 8.88        & 6.67       & 6.4           & 5.84           & 6.5   & 7     & 7       & 6       & 0         & 0        & 0         & 0           & 43       & 13       & 16        & 14 & & & & & & \\
+    $(6,12,\elseBr)$   & 12.58       & 5.56       & 5.88          & 5.62           & 9     & 5     & 6       & 6       & 0         & 0        & 0         & 0           & 53       & 17       & 14        & 15 & & & & & & \\
+    $(8,11,\elseBr)$   & 131.86      & 18.78      & 24.16         & 19.34          & 143   & 15.5  & 22      & 18      & 6         & 4        & 6         & 5           & 199      & 65       & 53        & 46 & & & & & &\\
+    %% $(24,27,\elseBr)$  & 0.02        & 0.08       & 0.18          & 0.06           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 1        & 3        & 5         & 3\\
+    %% $(36,39,\elseBr)$  & 0.32        & 0.7        & 0.52          & 0.12           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 4        & 7        & 7         & 2\\
+    %% $(40,43,\elseBr)$  & 0.1         & 0.1        & 0.52          & 0.34           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 1        & 2        & 6         & 12\\
+    $(44,45,\thenBr)$  & 76.1        & 149.16     & 32.14         & 42.8           & 56    & 199   & 26.5    & 38.5    & 3         & 3        & 0         & 1           & 199      & 199      & 199       & 199 & & & & & & \\
+    $(48,49,\thenBr)$  & 36.6        & 114.42     & 29.42         & 31.32          & 25    & 135.5 & 27.5    & 33      & 0         & 0        & 0         & 0           & 185      & 199      & 124       & 41 & & & & & & \\
+    \midrule
+    \midrule
+    probability\_gamma &             &            &               &                &       &       &         &         &           &          &           &             &          &          &           &  & & & & & & \\
+    $(4,5,\thenBr)$    & 195.58      & 1.02       & 1             & 1.06           & 199   & 1     & 1       & 1.06    & 28        & 1        & 1         & 1           & 199      & 2        & 1         & 2 & & & & & & \\
+    $(6,7,\thenBr)$    & 195.2       & 1.14       & 1.29          & 1.28           & 199   & 1     & 1       & 1.28    & 21        & 1        & 1         & 1           & 199      & 3        & 3         & 4 & & & & & & \\
+    $(6,9,\elseBr)$    & 199         & 1.42       & 1.39          & 1.46           & 199   & 1     & 1       & 1.46    & 199       & 1        & 1         & 1           & 199      & 4        & 4         & 4 & & & & & & \\
+    $(10,11,\thenBr)$  & 199         & 60.92      & 61.51         & 60.22          & 199   & 61    & 61      & 60.22   & 199       & 45       & 50        & 48          & 199      & 72       & 76        & 76 & & & & & & \\
+    $(10,13,\elseBr)$  & 199         & 1.24       & 1.19          & 1.22           & 199   & 1     & 1       & 1.22    & 199       & 1        & 1         & 1           & 199      & 2        & 3         & 3 & & & & & & \\
+    $(16,17,\inWhile)$ & 199         & 1.46       & 1.7           & 1.76           & 199   & 1     & 1       & 1.76    & 199       & 1        & 1         & 1           & 199      & 3        & 6         & 8 & & & & & & \\
+    $(20,21,\thenBr)$  & 199         & 5.38       & 4.85          & 6.32           & 199   & 5     & 4       & 6.32    & 199       & 1        & 1         & 1           & 199      & 14       & 14        & 25 & & & & & & \\
+    $(20,23,\elseBr)$  & 199         & 1.54       & 1.37          & 1.28           & 199   & 1     & 1       & 1.28    & 199       & 1        & 1         & 1           & 199      & 4        & 4         & 3 & & & & & & \\
+    $(30,31,\thenBr)$  & 199         & 51.44      &               & 51.96          & 199   & 52    &         & 51.96   & 199       & 42       &           & 42          & 199      & 62       &           & 62 & & & & & & \\
+    $(34,35,\thenBr)$  & 199         & 22.66      &               & 23.32          & 199   & 23    &         & 23.32   & 199       & 13       &           & 16          & 199      & 29       &           & 28 & & & & & & \\
+    \bottomrule
+    \end{tabular}
+}
+\end{table*}
+
 \subsection{Limitations}
@@
 \label{sub.sec.search.based}
+
+\cite{wegener2001evolutionary} evolutionary test generation for structural coverage.
+
+\cite{tonella2004evolutionary} evolutionary testing of classes
+
+\cite{wappler2005using} evolutionary testing of object-oriented software.
+
+\cite{wappler2006evolutionary} uses strongly-typed genetic programming and deals with the runtime exceptions.
+
+\cite{lakhotia2007multi} multi-objective search-based test data generation
+
+\cite{cao2009search} multi-path search-based test data generation
+
+\cite{awedikian2009mc} MC/DC test input generation
+
+\cite{shahbazi2016black} generation of string test data
+
+\cite{fraser2012mutation} mutation-driven generation of unit tests and oracles
+
+\cite{havrikov2014xmlmate} XMLMate: evolutionary XML test generation.
+
+\cite{mcminn2004search} seminal survey of search-based test data generation techniques.
+
+\cite{mcminn2011search} recent overview of search-based testing.
+
+\cite{mairhofer2011search} search-based testing for dynamic languages (Ruby)
+
+\cite{baars2011symbolic} combines dynamic analysis with symbolic information to improve search-based testing
+
+\cite{alshahwan2011automated} automated web application testing using search based software techniques.
+
+\cite{ma2015grt} guided random testing
+
+\cite{mao2016sapienz} Multi-objective automated testing for Android application
 
@@
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-
-%\balancecolumns
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{icse2018.bib}
 

### 2017-11-15 doc/icse2018/icse2018.tex
Provided motivation example. Working on an evaluation.

@@
   morecomment=[s]{<!-}{-->},
+  morestring=[b]'
   tag=[s],
@@
   % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article, </span, <span, </span> 
+  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
   },
@@
   transition:,  transition-duration:, transition-property:, transition-timing-function:,
+  }
+}
+
+\lstdefinelanguage{HTML5}{
+  language=html,
+  tagstyle=\color{blue},
+  markfirstintag=true,
+  sensitive=true,
+  alsoletter={<>=-},	
+  morecomment=[s]{<!--}{-->},
+  % tag=[s],
+  %% morestring=[b]'',
+  morestring=[b]',
+  ndkeywords={
+    % General
+    =,
+    % HTML attributes
+    id=, class= 
   }
@@
   \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function safeAdd() {
-  var iframe = document.createElement("iframe");
-  var whereto = document.getElementById("debug");
-  var frameid = document.getElementById("frame");
-  iframe.setAttribute("id", "frame");
-  if (frameid) { 
-    iframe.removeChild(frameid.childNodes[0]); |c \label{lbl:error} |c
-    // frameid.parentNode.removeChild(frameid); |c \label{lbl:correction} |c
-  } else { whereto.appendChild(iframe); } }  
+/*t dom */
+function isGameFinished() {
+  var obj = document.getElementById('sudoku'); |c \label{isGameFinished.getSudoku} |c
+  var subDivs = obj.getElementsByTagName('DIV'); |c \label{isGameFinished.getDivs} |c
+  var allOk = true;
+  for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
+    if (subDivs[no].className.indexOf('sudokuSquare') >= 0 |c \label{isGameFinished.if1.begin} |c 
+        && !subDivs[no].style.backgroundColor) { 
+      var spans = subDivs[no].getElementsByTagName('SPAN');
+      if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
+        allOk = false; |c \label{isGameFinished.unfinished} |c
+        break;
+      } |c \label{isGameFinished.if2.end} |c
+    } |c \label{isGameFinished.if1.end} |c
+  } |c \label{isGameFinished.inFor.end} |c
+  if (allOk) { |c \label{isGameFinished.if3.begin} |c 
+    console.log('Congratulations! You did it'); |c \label{isGameFinished.finished} |c
+  } |c \label{isGameFinished.if3.end} |c
+}
 \end{lstlisting}
+  \caption{JS function \texttt{isGameFinished.js} from sudoku}
+  \label{code.newGame}
 
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<html>
-  <body>
-    <div id="frame"></div>
-    <div id="debug"></div>
-  </body>
-</html>
-  \end{lstlisting}
-
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<html>
-  <body>
-    <div id="debug"></div>
-  </body>
-</html>
-\end{lstlisting}    
-  \caption{Stackoverflow Example}
-  \label{fig..safeAdd.js}
 \end{figure}
@@
 \begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
-function revealAll() {
- for(var row=0; row<2; row++){
-  for(var col=0; col<2; col++){
-   var obj = document.getElementById('square_'+row+'_'+col);
-   var spans = obj.getElementsByTagName('SPAN');
-   spans[0].style.display='';
-   spans[1].style.display='none';
-   spans[1].style.color='#000000'; } } }
-  \end{lstlisting}
-
   \begin{lstlisting}[style=htmlcssjs, language=HTML5]
+<!-- T1 covers: (6,15), (16,17) -->
 <html>
   <body>
-    <div id="square_0_0">
-      <span></span><span></span>
+    <div id='sudoku'></div>
+</body>
+</html>
+
+<!-- T2 covers: (6,7), (7,14), (16,17) -->
+<html>
+  <body>
+    <div id='sudoku'>
+      <div></div>
     </div>
-    <div id="square_0_1">
-      <span></span><span></span>
+  </body>
+</html>
+
+<!-- T3 covers: (6,7), (7,9), (10,13), (16,17) -->
+<html>
+  <body>
+    <div id='sudoku'>
+      <div class='sudokuSquare'>
+        <span></span>
+        <span></span>
       </div>
-    <div id="square_1_0">
-      <span></span><span></span>
     </div>
-    <div id="square_1_1">
-      <span></span><span></span>
+  </body>
+</html>
+
+<!-- T4 covers: (6,7), (7,9), (10,11), (16,18) -->
+<html>
+  <body>
+    <div id='sudoku'>
+      <div class='sudokuSquare'>
+        <span></span>
+        <span>TEST</span>
+      </div>
     </div>
@@
   \end{lstlisting}
-  \caption{Sudoku Example}
-  \label{fig.revealAll.js}
+  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
+  \label{fig.isGameFinished.tests}
 \end{figure}
+
+Let us consider JS function \texttt{isGameFinished} in Figure~\ref{code.newGame} taken from the web application game \emph{sudoku}~\ref{ref.sudoku}.
+This function checks if a sudoku solution entered by the user is valid.
+First, it finds the game field element (line~\ref{isGameFinished.getSudoku}), retrieves all child divs (line~\ref{isGameFinished.getDivs}), and iterates over that collection.
+Each div element which corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) consists of two span elements.
+One contains a user input, and another one, which is hidden at the moment, stores the expected value for the sudoku square.
+Once, it finds a square where two values are not equal (line~\ref{isGameFinished.if2.begin}) to each other, the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise (line~\ref{isGameFinished.finished}).
+
+Suppose now that we would like to (unit) test this function in isolation to the rest of the application source code.
+We aim to maximize branch coverage as a common testing criteria~\cite{why_is_common}.
+That is for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we have to construct a test input which passes the branch and normally exists the function.
+JS function has \emph{explicit} input arguments (none is our case), but it can also has \emph{implicit} arguments such as DOM state.
+As assume that DOM is the only global JS object that can be referred from the body of FUT.
+So in order to test our function we have to construct appropriate DOM objects as test inputs.
+
+%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
+
+Figure~\ref{fig.isGameFinished.tests} presents four tests that together provide full coverage of the FUT.
+Let us look at how to construct the test that covers branch $(10,11)$.
+Line~\ref{isGameFinished.getSudoku} expects DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
+In order to enter the for-loop on line~{isGameFinished.inFor.begin}, this element should have at least one child of the type $div$.
+The condition of the first $if$ (line~\ref{isGameFinished.if1.begin}) requires the div to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle and have no background color.
+The last if-condition (line~\ref{isGameFinished.if2.begin}) expects that the div has two \emph{span} elements whose \emph{innerHtml} values are not equal.
+$T4$ in Figure~\ref{fig.isGameFinished.tests} shows a concrete example of DOM that meets all the conditions above.
+
+As we have just seen even for such a relatively simple example, the construction of the test input is a far from trivial procedure because it requires deep understanding the program's semantics.
+In practice, web developers often have to deal with the gazillion of the JS frameworks and libraries freely available on the GitHub.
+This code is commonly untested and poorly documented.
+At the same time, unit testing is the most fundamental and easiest to provide level of testing.
+It greatly saves developers from the unexpected regression and creates a safety belt around the application.
 
@@
 
-\begin{description}
-\item[\textbf{Q1}] How often \emph{validator} rejects generated HTML in case of the random and genetic (mutation and crossover) phases.
-This question characterizes potential performance issues that can occur in the generation.
-\item[\textbf{Q2}] Efficiency (compare with random)  
-\end{description}
+In order to evaluation the feasibility of practical adoption of our genetic test generation framework, we carried out empirical validation on a set of case studies.
+Table~\ref{tbl.gen.config} shows summary of configuration parameters for both random and genetic instances of our framework.
+As a baseline we implemented random test generation strategy.
+It is similar to the genetic one except that it won't performing crossover and mutation.
+Hence, it also benefits from initial static analysis and follow up dynamic constant propagation.
+In addition, we experimented with two different sizes (5 and 10) for genetic restart in case of archive convergence.
+
+\begin{table}
+  \caption{Genetic Algorithm Configurations}
+  \label{tbl.gen.config}
+    \footnotesize
+  \begin{tabular}{l|r|r}
+    \toprule
+    \textbf{Parameter Name} & \textbf{Random} & \textbf{Genetic} \\
+    \midrule
+    Population size                   & 50  & 50 \\
+    Archive size                      & 1   & 25 \\
+    Maximum number of generations     & 200 & 200 \\
+    Crossover rate                    & 0   & 0.5 \\
+    Mutation rate                     & 0   & 0.5 \\
+    Restart after archive convergence & -   & - (5,10) \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 
-For the purpose of validation we selected two classes of programs.
-The first class only includes JS programs composed of the primitive types.
-The programs in the second class additionally accept arguments of the DOM type.
-We collected those program from several researches in the field of web application analysis, and JS in particular.
-Moreover, we introduced few other subjects found in open source such as \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}}.
+Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the web.
+They all are greatly vary in size, complexity and coding style.
+Moreover, many popular JS web-frameworks, including jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach for DOM manipulation to vanilla-like JS.
+Therefore, search for appropriate case-studies requires careful inspection of the application source code, which is often time consuming and labor intensive process.
+These factors significantly complicate the choice of suitable evaluation subjects.
+Therefore, we decided to form our experimental data set from two related research works \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
+Moreover, we introduced two additional subjects found in open source \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}}.
+For each case study application, we identified several JS functions which were suitable for our test generation framework.
+Our evaluation set includes both primitive and manipulating with DOM JS functions.
+
+Table~\ref{tbl.case.studies} presents generic quantitative characteristics of the selected functions such as the number of branches (\textbf{\#BR}), lines of code (\textbf{\#LOC}) and cyclomatic complexity (\textbf{CC}).
+The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
 
@@
     \midrule
-    mathjs     & probability\_gamma & (float) & & & & - & - & - & - \\
+    mathjs     & prob\_gamma & (float) & & & & - & - & - & - \\
     \bottomrule
@@
 \end{table*}
+
+\subsection{Research Questions}
+\label{sub.sec.research.questions}
+
+\begin{description}
+\item[\textbf{Q1}] What is the performance of our test generation framework?
+\item[\textbf{Q2}] How does genetic version perform against the random one?
+\item[\textbf{Q3}] How does the restart of genetic algorithm after the archive convergence enhance the performance? 
+\end{description}
 
@@
       \toprule
-      \textbf{name}     & $\bar{x}_R$ & $\bar{x}_G$ & $\bar{x}_{G5}$ & $\bar{x}_{G10}$ & $m_R$ & $m_G$ & $m_{G5}$ & $m_{G10}$ & $\min_R$ & $\min_G$ & $\min_{G5}$ & $\min_{G10}$ & $\max_R$ & $\max_G$ & $\max_{G5}$ & $\max_{G10}$ & \textbf{R-G} & \textbf{R-G5} & \textbf{R-G10} & \textbf{G-G5} & \textbf{G-G10} & \textbf{G5-G10}\\
+      \textbf{name}     & $\bar{x}_R$ & $\bar{x}_G$ & $\bar{x}_{G5}$ & $\bar{x}_{G10}$ & $m_R$ & $m_G$ & $m_{G5}$ & $m_{G10}$ & $\min_R$ & $\min_G$ & $\min_{G5}$ & $\min_{G10}$ & $\max_R$ & $\max_G$ & $\max_{G5}$ & $\max_{G10}$ & \textbf{G-R} & \textbf{G5-R} & \textbf{G10-R} & \textbf{G5-G} & \textbf{G10-G} & \textbf{G10-G5}\\
       \toprule
@@
     \midrule
-    probability\_gamma &             &            &               &                &       &       &         &         &           &          &           &             &          &          &           &  & & & & & & \\
+    prob\_gamma &             &            &               &                &       &       &         &         &           &          &           &             &          &          &           &  & & & & & & \\
     $(4,5,\thenBr)$    & 195.58      & 1.02       & 1             & 1.06           & 199   & 1     & 1       & 1.06    & 28        & 1        & 1         & 1           & 199      & 2        & 1         & 2 & & & & & & \\
@@
     $(20,23,\elseBr)$  & 199         & 1.54       & 1.37          & 1.28           & 199   & 1     & 1       & 1.28    & 199       & 1        & 1         & 1           & 199      & 4        & 4         & 3 & & & & & & \\
-    $(30,31,\thenBr)$  & 199         & 51.44      &               & 51.96          & 199   & 52    &         & 51.96   & 199       & 42       &           & 42          & 199      & 62       &           & 62 & & & & & & \\
-    $(34,35,\thenBr)$  & 199         & 22.66      &               & 23.32          & 199   & 23    &         & 23.32   & 199       & 13       &           & 16          & 199      & 29       &           & 28 & & & & & & \\
+    $(30,31,\thenBr)$  & 199         & 51.44      & 52            & 51.96          & 199   & 52    & 51.66   & 51.96   & 199       & 42       & 41        & 42          & 199      & 62       & 61        & 62 & & & & & & \\
+    $(34,35,\thenBr)$  & 199         & 22.66      & 23            & 23.32          & 199   & 23    & 23.32   & 23.32   & 199       & 13       & 15        & 16          & 199      & 29       & 33        & 28 & & & & & & \\
     \bottomrule

### 2017-11-15 evaluation/confix/sudoku/tests_isGameFinished.js

@@ -4,7 +4,7 @@ let doc, window, document;
 
 let dom1 = "<!DOCTYPE HTML><html><head><title>Test</title></head><body><div id='sudoku'></div></body></html>";
 
-let dom2 = "<!DOCTYPE HTML><html><head><title>Test</title></head><body><div id='sudoku'></div></body></html>";
+let dom2 = "<!DOCTYPE HTML><html><head><title>Test</title></head><body><div id='sudoku'><div></div></div></body></html>";
 
 let dom3 = "<!DOCTYPE HTML><html><head><title>Test</title></head><body><div id='sudoku'><div class='sudokuSquare'><span></span><span></span></div></div></body></html>";
 
@@ -45,16 +45,16 @@ function runTest(fun, dom, args = []) {
     Reflect.apply(fun, this, args);
 }
 
-// all branches: (1,8), (1,2), (2,3), (2,7), (4,5), (4,6), (8,9), (8,10)
+// all branches: *(1,8), *(1,2), *(2,3), *(2,7), *(4,5), *(4,6), *(8,9), (8,10)
 
-// cover branch (1,8), (8,9); path = [1,8,9,10]
+// cover branch *(1,8), *(8,9); path = [1,8,9,10]
 runTest(isGameFinished, dom1);
 
-// cover branch (1,2); path = [1,2,7,8,9,10]
+// cover branch *(1,2), (2,7), (8,9); path = [1,2,7,8,9,10]
 runTest(isGameFinished, dom2);
 
-// cover branch (2,3), (4,6); path = [1,2,3,4,6,7,8,9,10]
+// cover branch *(2,3), *(4,6), (8,9); path = [1,2,3,4,6,7,8,9,10]
 runTest(isGameFinished, dom3);
 
-// cover branch (4,5); path = [1,2,3,4,5,8,10]
+// cover branch (1,2), (2,3), *(4,5), *(8, 10); path = [1,2,3,4,5,8,10]
 runTest(isGameFinished, dom4);

### 2017-11-15 doc/icse2018/icse2018.tex
Uncommented boolean flag branch in isGameFinished example.

@@
 
-Table~\ref{tbl.case.studies} presents generic quantitative characteristics of the selected functions such as the number of branches (\textbf{\#BR}), lines of code (\textbf{\#LOC}) and cyclomatic complexity (\textbf{CC}).
+Table~\ref{tbl.case.studies} presents common quantitative characteristics of the selected functions such as the number of branches (\textbf{\#BR}), lines of code (\textbf{\#LOC}) and cyclomatic complexity (\textbf{CC}).
 The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.

### 2017-11-15 evaluation/confix/sudoku/final_isGameFinished.js

@@ -12,7 +12,7 @@ function test() {
             }
         }
     }
-    // if (allOk) {
-    //     console.log('Congratulations! You did it');
-    // }
+    if (allOk) {
+        console.log('Congratulations! You did it');
+    }
 }

### 2017-12-05 python/evaluation.py
Re-done initBricks example

@@ -24,7 +24,7 @@ out_folder = "./evaluation/result"
 case_studies = [
     # # sudoku + "getPossibleNumbers.js",
     # sudoku + "helpMe.js",          # +
-    sudoku + "isGameFinished.js"     # +
+    # sudoku + "isGameFinished.js"     # +
     # sudoku + "newGame.js",         # +
     # sudoku + "revealAll.js",       # +
     # # sudoku + "showCell.js",
@@ -51,7 +51,7 @@ case_studies = [
     # bingbong + "doPaddlePower.js",  # -
     # bingbong + "drawLevel.js",      # -
     # bingbong + "goPing.js",
-    # bingbong + "initBricks.js",     # -
+    bingbong + "initBricks.js",     # -
 
     # burncanvas + "do_draw.js",      # -
     # burncanvas + "modify_region.js",

### 2017-12-05 doc/icse2018/icse2018.tex

@@
   \label{code.newGame}
-
+\end{figure}
+
+\begin{figure}[t]
+  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
+function isGameFinished() {
+  trace.push(2);
+  var obj = document.getElementById("sudoku");
+  trace.push(3);
+  var subDivs = obj.getElementsByTagName("DIV");
+  trace.push(4);
+  var allOk = true;
+  loopMap[5] = function () {
+    var no = 0;
+    if (subDivs.length || subDivs.length == 0) {
+      return Math.abs(no - subDivs.length);
+    }
+    return 1;
+  }();
+  for (var no = 0; no < subDivs.length; no++) {
+    trace.push(5);
+    trace.push(6);
+    trace.push(7);
+    if (subDivs[no].className.indexOf("sudokuSquare") >= 0 &&
+        !subDivs[no].style.backgroundColor) {
+      trace.push(8);
+      branchDistance.push({ 
+        label: 7, 
+        distance: Math.min(
+          abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + _K_,
+          absZero(subDivs[no].style.backgroundColor))
+      });
+      trace.push(9);
+      var spans = subDivs[no].getElementsByTagName("SPAN");
+      trace.push(10);
+      if (spans[0].innerHTML != spans[1].innerHTML) {
+      trace.push(11);
+      branchDistance.push({
+        label: 10,
+        distance: abs(spans[0].innerHTML, spans[1].innerHTML)
+      });
+      trace.push(12);
+      allOk = false;
+      break;
+      } else {
+        trace.push(14);
+        branchDistance.push({label: 10,distance: _K_});
+      }
+    } else {
+      trace.push(15);
+      branchDistance.push({
+        label: 7,
+        distance: abs(subDivs[no].className.indexOf("sudokuSquare"), 0) +
+                  absNegZero(subDivs[no].style.backgroundColor)
+      });
+    }
+  }
+  trace.push(5);
+  trace.push(16);
+  if (allOk) {
+    trace.push(17);
+    branchDistance.push({label: 16, distance: absNegZero(allOk)});
+    trace.push(18);
+    console.log("Congratulations! You did it");
+  } else {
+    trace.push(19);
+    branchDistance.push({label: 16 ,distance: absZero(allOk)});
+  }
+  trace.push(-1);
+}
+\end{lstlisting}
+  \caption{Instrumented version of the function \texttt{isGameFinished.js} }
+  \label{code.isGameFinished.instr}
 \end{figure}
@@
     \footnotesize
-  \begin{tabular}{l|l|l|r|r|r|c|c|c|c}
+  \begin{tabular}{l|l|l|r|r|r|r|c|c|c|c}
     \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type} & \textbf{\#BR} & \textbf{\#LOC} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \midrule
-    sudoku     & helpMe & (dom,int,int) & & & & + & + & + & - \\
-    sudoku     & isGameFinished & (dom) & & & & + & + & + & + \\
-    sudoku     & newGame & (dom)        & & & & + & + & + & + \\
-    sudoku     & revealAll & (dom)      & & & & + & + & + & - \\
-    sudoku     & shuffleBoard & (dom)   & & & & + & - & + & - \\
-    \midrule
-    phormer    & toggleInfo & (dom,string) & & & & + & + & - & - \\
-    \midrule
-    hotel RS   & isValidCard & ([int]) & & & & - & - & - & - \\
-    hotel RS   & isValidMasterCard & ([int])  & & & & - & - & - & - \\
-    \midrule
-    apophis    & initShields & (dom,[int],int,int) & & & & + & + & - & -\\
-    \midrule
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & & & & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int) & & & & + & + & - & - \\
-    \midrule
-    burncanvas & do\_draw & (int,int,int,int,int,int,int) & & & & - & - & - & - \\
-    \midrule
-    mathjs     & prob\_gamma & (float) & & & & - & - & - & - \\
+    \textbf{case-study} & \textbf{function} & \textbf{type} & \textbf{\#LOC} & \textbf{\#BR} & \textbf{\#D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
+    \midrule
+    sudoku     & helpMe & (dom,int,int)                                   & 15 & 2  & 3 & 3  & + & + & + & - \\
+    sudoku     & isGameFinished & (dom)                                   & 17 & 4  & 3 & 5  & + & + & + & + \\
+    sudoku     & newGame & (dom)                                          & 12 & 1  & 2 & 2  & + & + & + & + \\
+    sudoku     & revealAll & (dom)                                        & 14 & 0  & 2 & 1  & + & + & + & - \\
+    sudoku     & showCell & (dom)                                         &    &    &   &    &   &   &   & \\
+    sudoku     & shuffleBoard & (dom)                                     & 26 & 2  & 3 & 3  & + & - & + & - \\
+    sudoku     & switchLevel & (dom,bool)                                 &    &    &   &    &   &   &   & \\
+    \midrule
+    phormer    & toggleInfo & (dom,string)                                & 15 & 3  & 1 & 4  & + & + & - & - \\
+    phormer    & update & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &    &   &    &   &   &   & \\
+    phormer    & updateIndic & (dom,bool)                                 &    &    &   &    &   &   &   & \\
+    \midrule
+    hotelRS    & RequiredField & (dom,[string])                           &    &    &   &    &   &   &   & \\
+    hotel RS   & isValidCard & ([int])                                    & 20 & 2  & 2 & 5  & - & - & - & - \\
+    hotel RS   & isValidMasterCard & ([int])                              & 6  & 4  & 1 & 7  & - & - & - & - \\
+    hotelRS    & isValidVISA & ([int])                                    &    &    &   &    &   &   &   & \\
+    hotelRS    & validateNumber & (dom,string)                            &    &    &   &    &   &   &   & \\
+    \midrule
+    apophis    & doRain & (dom,string,int,int,int,int,int,int)            &    &    &   &    &   &   &   & \\
+    apophis    & drawShields & (dom,[int])                                &    &    &   &    &   &   &   & \\
+    apophis    & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) &    &    &   &    &   &   &   & \\
+    apophis    & getReady & (dom,int,int,int,int,int,int)                 &    &    &   &    &   &   &   & \\
+    apophis    & initShields & (dom,[int],int,int)                        & 8  & 0  & 1 & 1  & + & + & - & -\\
+    \midrule
+    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
+    bingbong   & initBricks & (dom,[int],int,int)                         & 63 & 12 & 4 & 13 & + & + & - & - \\
+    bingbong   & doPaddlePower & (dom,int,int)                            &    &    &   &    &   &   &   & \\
+    bingbong   & drawLevel & (dom,int,int,int,int)                        &    &    &   &    &   &   &   & \\
+    bingbong   & goPing & (dom,int,int,int)                               &    &    &   &    &   &   &   & \\
+    \midrule
+    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 39 & 12 & 2 & 14 & - & - & - & - \\
+    \midrule
+    cs-in-js   & luhn-algorithm & (string,bool)                           &    &    &   &    &   &   &   & \\
+    cs-in-js   & quicksort-partition & ([int],int,int)                    &    &    &   &    &   &   &   & \\ 
+    \midrule
+    mathjs     & prob\_gamma & (float)                                    & 56 & 8  & 2 & 16 & - & - & - & - \\
     \bottomrule
@@
       helpMe          &                 &               &               &               &             &           &             &           &           &          &            &             &           &           &            & & & & & & & \\
-    $(3,4,\inFor)$    & 3.94        & 7.94        & 10.22          & 11.7          & 3     & 3.5   & 7       & 7       & 1        & 1        & 1          & 1           & 16       & 31      & 63         & 124 & & & & & & \\
-    $(5,6,\thenBr)$   & 3.7         & 13.08       & 9.2            & 9.6           & 3     & 7     & 5       & 5.5     & 1        & 1        & 1          & 1           & 14       & 95      & 44         & 105 & & & & & & \\
-    $(5,15,\elseBr)$  & 118.64      & 30.14       & 34.12          & 31.68         & 119.5 & 23    & 28.5    & 22      & 4        & 4        & 3          & 1           & 199      & 97      & 167        & 114 & & & & & & \\
-    $(9,10,\thenBr)$  & 105.12      & 17.82       & 21.98          & 21.8          & 83.5  & 17    & 17.5    & 18      & 18       & 1        & 2          & 6           & 199      & 53      & 78         & 77  & & & & & & \\
-    $(9,14,\elseBr$   & 4.28        & 5.06        & 8.14           & 9.56          & 2.5   & 5     & 4       & 4       & 1        & 1        & 1          & 1           & 17       & 20      & 49         & 74  & & & & & & \\
+    $(3,4,\inFor)$    & 3.94 (5.34)     & 7.94 (6.24)   & 10.22  (8.48) & 11.7 (9.32)   & 3 (4)       & 3.5 (3)   & 7 (6)       & 7 (6)     & 1 (1)     & 1 (1)    & 1 (1)      & 1 (2)       & 16 (21)   & 31 (23)   & 63 (48)    & 124 (84) & & & & & & \\
+    $(5,6,\thenBr)$   & 3.7 (5.74)      & 13.08 (9.86)  &   9.2  (7.76) & 9.6 (8.06)    & 3 (5)       & 7 (5.5)   & 5 (4)       & 5.5 (5)   & 1 (2)     & 1 (1)    & 1 (1)      & 1 (1)       & 14 (28)   & 95 (68)   & 44 (38)    & 105 (89) & & & & & & \\
+    $(5,15,\elseBr)$  & 118.64 (151.48) & 30.14 (27.08) & 34.12  (32.7) & 31.68 (31.92) & 119.5 (156) & 23 (20.5) & 28.5 (28.5) & 22 (23.5) & 4 (6)     & 4 (3)    & 3 (3)      & 1 (2)       & 199 (294) & 97 (99)   & 167 (156)  & 114 (130) & & & & & & \\
+    $(9,10,\thenBr)$  & 105.12 (124.26) & 17.82 (15.58) & 21.98 (21.66) & 21.8 (21.9)   & 83.5 (101)  & 17 (14)   & 17.5 (17)   & 18 (17)   & 18 (23)   & 1 (1)    & 2 (2)      & 6 (6)       & 199 (245) & 53 (51)   & 78 (83)    & 77  (86) & & & & & & \\
+    $(9,14,\elseBr$   & 4.28 (6.18)     & 5.06 (4.42)   &  8.14 (7.74)  & 9.56 (9.48)   & 2.5 (4)     & 5 (4)     & 4 (4)       & 4 (4)     & 1 (1)     & 1 (1)    & 1 (1)      & 1 (1)       & 17 (21)   & 20 (17)   & 49 (43)    & 74  (79) & & & & & & \\
     \midrule
     isGameFinished      &               &               &               &               &             &           &             &           &           &          &            &             &           &           &            & & & & & & & \\
-    %% $(5,6,\inFor)$    & 0.02        & 0.1         & 0.12           & 0.1           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 2       & 2          & 2   \\
-    $(7,8,\thenBr)$   & 75.18       & 40.54       & 18.86          & 14.66         & 35.5  & 7     & 8       & 11      & 0        & 0        & 0          & 0           & 199      & 199     & 199        & 82  & & & & & & \\
-    %% $(7,15,\elseBr)$  & 0           & 0.06        & 0.04           & 0.08          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 0        & 2       & 1          & 2   \\
-    $(10,11,\thenBr)$ & 199         & 35.74       & 21.56          & 24.36         & 199   & 10    & 10      & 9       & 199      & 1        & 1          & 1           & 199      & 199     & 199        & 199 & & & & & & \\
-    $(10,14,\elseBr)$ & 69.62       & 56.32       & 28.74          & 31.92         & 23.5  & 10    & 16.5    & 18      & 1        & 0        & 0          & 0           & 199      & 199     & 199        & 199 & & & & & & \\
+    %% $(5,6,\inFor)$   & 0.02 (0)      & 0.1 (0.88)    & 0.12 (0.94)   & 0.1 (0.94)    & 0 (1)       & 0 (1)     & 0 (1)       & 0 (1)     & 0 (0)     & 0 (0)    & 0 (0)      & 0 (0)       & 1 (2)     & 2 (3)     & 2 (3)      & 2 (3)  \\
+    $(7,8,\thenBr)$     & 75.18 (63.68) & 40.54 (40.32) & 18.86 (19.62) & 14.66 (15.62) & 35.5 (29.5) & 7 (7.5)   & 8 (9.5)     & 11 (12.5) & 0 (0)     & 0 (0)    & 0 (1)      & 0 (1)       & 199 (191) & 199 (225) & 199 (196)  & 82 (77) & & & & & & \\
+    %% $(7,15,\elseBr)$ & 0 (0.98)      & 0.06 (0.82)   & 0.04 (0.84)   & 0.08 (0.9)    & 0 (1)       & 0 (1)     & 0 (1)       & 0 (1)     & 0 (0)     & 0 (0)    & 0 (0)      & 0 (0)       & 0 (3)     & 2 (3)     & 1 (2)      & 2 (3)  \\
+    $(10,11,\thenBr)$   & 199 (166.32)  & 35.74 (36.6)  & 21.56 (22.5)  & 24.36 (26.44) & 199 (167)   & 10 (10)   & 10 (10.5)   & 9 (11)    & 199 (141) & 1 (2)    & 1 (1)      & 2 (3)       & 199 (191) & 199 (220) & 199 (217)  & 199 (224) & & & & & & \\
+    $(10,14,\elseBr)$   & 69.62 (59.28) & 56.32 (56.44) & 28.74 (31.78) & 31.92 (33.58) & 23.5 (21)   & 10 (10.5) & 16.5 (17)   & 18 (17.5) & 1 (1)     & 0 (0)    & 0 (1)      & 0 (1)       & 199 (186) & 199 (217) & 199 (258)  & 199 (206) & & & & & & \\
     \midrule
     newGame             &               &              &                &               &             &           &             &           &           &          &            &             &          &            &            & & & & & & & \\
-    %% $(4,5,\inFor)$    & 0.04        & 0.12        & 0.1            & 0             & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 2       & 1          & 0 \\
-    $(6,7,\thenBr)$   & 21.54       & 10.48       & 9.92           & 8.34          & 15    & 7.5   & 7.5     & 7       & 0        & 0        & 0          & 0           & 97       & 53      & 30         & 35 & & & & & & \\
-    %% $(6,12,\elseBr)$  & 0.06        & 0.14        & 0.1            & 0.04          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 3       & 2          & 1\\
+    %% $(4,5,\inFor)$   & 0.04 (0.9)    & 0.12 (0.66)  & 0.1 (0.84)     & 0 (0.86)      & 0 (1)       & 0 (1)     & 0 (1)       & 0 (1)     & 0 (0)     & 0 (0)    & 0 (0)      & 0 (0)       & 1 (2)    & 2 (2)      & 1 (2)      & 0 (1) \\
+    $(6,7,\thenBr)$     & 21.54 (16.58) & 10.48 (9.78) & 9.92 (10.24)   & 8.34 (8.84)   & 15 (11.5)   & 7.5 (7)   & 7.5 (8)     & 7 (8)     & 0 (1)     & 0 (1)    & 0 (1)      & 0 (0)       & 97 (67)  & 53 (47)    & 30 (34)    & 35 (31) & & & & & & \\
+    %% $(6,12,\elseBr)$ & 0.06 (0.78)   & 0.14 (0.84)  & 0.1 (0.86)     & 0.04 (0.8)    & 0 (1)       & 0 (1)     & 0 (1)       & 0 (1)     & 0 (0)     & 0 (0)    & 0 (0)      & 0 (0)       & 1 (2)    & 3 (4)      & 2 (3)      & 1 (2) \\
     \midrule
     revealAll           &               &               &               &               &             &           &             &           &           &          &            &             &          &            &            & \\
-    $(2,3,\inFor)$    & 31.78       & 24.84       & 34.94          & 28.04         & 24    & 23    & 29      & 22.5    & 4        & 7        & 7          & 10          & 106      & 57      & 129        & 75 & & & & & & \\
-    $(4,5,\inFor)$    & 46.12       & 26.22       & 30.1           & 27.64         & 34    & 19    & 26.5    & 22      & 5        & 9        & 9          & 6           & 199      & 78      & 71         & 90 & & & & & & \\
-    \midrule
-    shuffleBoard      &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
-    %% $(5,6,\inWhile)$  & 0.36        & 0.32        & 0.24           & 0.48          & 0     & 0     & 0.24    & 0       & 0        & 0        & 0          & 0           & 4        & 3       & 2          & 0\\
-    $(13,14,\thenBr)$ & 6.38        & 7.7         & 8.72           & 7.86          & 4     & 4     & 8.72    & 4       & 0        & 0        & 0          & 0           & 22       & 67      & 64         & 38 & & & & & & \\
-    $(17,18,\thenBr)$ & 5.66        & 11.86       & 16.96          & 17.72         & 3.5   & 5.5   & 16.96   & 3.5     & 0        & 0        & 0          & 0           & 33       & 133     & 86         & 118 & & & & & & \\
-    %% $(21,22,\inFor)$  & 199         & 199         & 199            & 199           & 199   & 199   & 199     & 199     & 0        & 0        & 0          & 0           & 199      & 199     & 199        & 199\\
-    \midrule
-    \midrule
-    toggleInfo        &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
-    $(2,3,\thenBr)$   & 1.58        & 1.12        & 1.1            & 1             & 1     & 1     & 1       & 1       & 0        & 0        & 0          & 0           & 11       & 4       & 3          & 3 & & & & & & \\
-    $(6,7,\thenBr)$   & 1.48        & 9.9         & 17             & 15.3          & 1     & 2     & 4       & 4       & 0        & 0        & 0          & 0           & 8        & 125     & 143        & 136 & & & & & & \\
+    $(2,3,\inFor)$      & 31.78 (27.78) & 24.84 (26.7)  & 34.94 (39.34) & 28.04 (32.58) & 24 (20)     & 23 (24)   & 29 (30.5)   & 22.5 (27) & 4 (3)     & 7 (7)    & 7 (7)      & 10 (11)     & 106 (89) & 57 (64)    & 129 (148)  & 75 (100) & & & & & & \\
+    $(4,5,\inFor)$      & 46.12 (41.42) & 26.22 (28.56) & 30.1 (33.02)  & 27.64 (31.46) & 34 (30)     & 19 (20)   & 26.5 (28)   & 22 (25.5) & 5 (5)     & 9 (9)    & 9 (9)      & 6 (5)       & 199 (172)& 78 (89)    & 71 (78)    & 90 (102) & & & & & & \\
+    \midrule
+    shuffleBoard         &              &              &               &               &             &             &            &           &           &           &           &           &           &           &           &           & & & & & & \\
+    %% $(3,4,\inFor)$    & 0 (1.6)      & 0 (1.36)     & 0 (1.52)      & 0 (1.42)      & 0 (2)       & 0 (1)       & 0 (2)      & 0 (1)     & 0 (1)     & 0 (1)     & 0 (1)     & 0 (1)     & 0 (3)     & 0 (2)     & 0 (2)     & 0 (2 )    & & & & & & \\
+    %% $(5,6,\inWhile)$  & 0.36 (2.94)  & 0.32 (2.6)   & 0.24 (2.58)   & 0.38 (2.88)   & 0 (2)       & 0 (2)       & 0 (2)      & 0 (2)     & 0 (1)     & 0 (1)     & 0 (1)     & 0 (1)     & 4 (11)    & 3 (8)     & 2 (6)     & 5 (15)    & & & & & & \\
+    %% $(10,11,\inFor)$  & 0 (1.88)     & 0 (1.4)      & 0 (1.64)      & 0 (1.58)      & 0 (2)       & 0 (1)       & 0 (2)      & 0 (2)     & 0 (2)     & 0 (1)     & 0 (1)     & 0 (1)     & 0 (3)     & 0 (2)     & 0 (2)     & 0 (2)     & & & & & & \\
+    $(13,14,\thenBr)$    & 6.38 (13.6)  & 7.7 (13.88)  & 8.72 (17.7)   & 7.86 (15.78)  & 4 (9.5)     & 4 (8.5)     & 4 (8.5)    & 5 (9.5)   & 0 (1)     & 0 (1)     & 0 (1)     & 0 (1)     & 22 (44)   & 67 (103)  & 64 (126)  & 38 (78)   & & & & & & \\
+    % $(13,16,\elseBr)$  & 0 (1.52)     & 0 (1.4)      & 0 (1.68)      & 0 (1.5)       & 0 (1.5)     & 0 (1)       & 0 (2)      & 0 (1.5)   & 0 (1)     & 0 (1)     & 0 (1)     & 0 (1)     & 0 (3)     & 0 (2)     & 0 (2)     & 0 (2)     & & & & & & \\
+    $(17,18,\thenBr)$    & 5.66 (13.76) & 11.86 (23.7) & 16.96 (39.58) & 15.02 (34.04) & 3.5 (10)    & 4 (10)      & 5.5 (12.5) & 5 (1)     & 0 (1)     & 0 (2)     & 0 (2)     & 0 (2)     & 33 (73)   & 133 (248) & 86 (180)  & 118 (248) & & & & & & \\
+    %% $(17,20,\elseBr)$ & 0 (2.06)     & 0 (1.84)     & 0 (1.72)      & 0 (1.8)       & 0 (2)       & 0 (2)       & 0 (2)      & 0 (2)     & 0 (1)     & 0 (1)     & 0 (1)     & 0 (1)     &  0 (4)    & 0 (2)     & 0 (2)     & 0 (2)     & & & & & & \\
+    %% $(21,22,\inFor)$  & 199 (373.2)  & 199 (275.1)  & 199 (305.16)  & 199 (299.84)  & 199 (372.5) & 199 (273.5) & 199 (307)  & 199 (302) & 199 (334) & 199 (242) & 199 (260) & 199 (255) & 199 (427) & 199 (322) & 199 (396) & 199 (325) & & & & & & \\
+    \midrule
+    \midrule
+    toggleInfo        &             &             &            &              &         &       &         &       &       &       &       &       &         &           &           &           & & & & & & \\
+    $(2,3,\thenBr)$   & 1.58 (2.32) & 1.12 (1.64) & 1.1 (1.7)  & 1 (1.46)     & 1 (1.5) & 1 (2) & 1 (2)   & 1 (1) & 0 (0) & 0 (0) & 0 (0) & 0 (0) & 11 (11) & 4 (4)     & 3 (4)     & 3 (3)     & & & & & & \\
+    %% $(2,5,\elseBr)$   & 0 (0.86)    & 0 (0.84)    & 0 (0.86)   & 0 (0.8)      & 0 (1)   & 0 (1) & 0 (1)   & 0 (1) & 0 (0) & 0 (0) & 0 (0) & 0 (0) & 0 (2)   & 0 (1)     & 0 (1)     & 0 (1)     & & & & & & \\
+    $(6,7,\thenBr)$   & 1.48 (2.1)  & 9.9 (8.7)   & 17 (14.92) & 15.3 (12.34) & 1 (2)   & 2 (3) & 4 (3.5) & 4 (3) & 0 (0) & 0 (0) & 0 (0) & 0 (0) & 8 (8)   & 125 (112) & 143 (132) & 136 (101) & & & & & & \\
+    %% $(6,13,\elseBr)$  & 0 (0.84)    & 0 (0.72)    &  0 (0.82)  & 0 (0.8)      & 0 (1)   & 0 (1) & 0 (1)   & 0 (1) & 0 (0) & 0 (0) & 0 (0) & 0 (0) & 0 (1)   & 0 (1)     & 0 (1)     & 0 (1)     & & & & & & \\
     \midrule
@@
     isValidCard       &              &             &             &             &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
-    $(3,6,\elseBr)$   & 199         & 2.98        & 3              & 2.82          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 5          & 4 & & & & & & \\
-    $(7,8,\inFor)$    & 199         & 2.92        & 3.04           & 2.96          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 4          & 5 & & & & & & \\
-    $(10,11,\thenBr)$ & 199         & 3           & 2.86           & 3.06          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
-    $(10,13,\elseBr)$ & 199         & 2.84        & 2.98           & 3.04          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
-    $(14,15,\inFor)$  & 199         & 3.02        & 2.92           & 2.94          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
+    $(3,4,\thenBr)$   & 0 (0.54)     & 0 (0.3)     & 0 (0.46)    & 0 (0.46)    & 0 (1)
+    $(3,6,\elseBr)$   & 199 (102.98) & 2.98 (1.52) & 3 (1.4)     & 2.82 (1.56) & 199 (102.5)   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 5          & 4 & & & & & & \\
+    $(7,8,\inFor)$    & 199 (102.38) & 2.92 (1.44) & 3.04 (1.6)  & 2.96 (1.58) & 199 (103)  & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 4          & 5 & & & & & & \\
+    $(10,11,\thenBr)$ & 199 (101.44) & 3 (1.56)    & 2.86 (1.48) & 3.06 (1.7)  & 199 (102)  & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
+    $(10,13,\elseBr)$ & 199 (104.66) & 2.84 (1.38) & 2.98 (1.54) & 3.04 (1.62) & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
+    $(14,15,\inFor)$  & 199 (101.66) & 3.02 (1.6)  & 2.92 (1.48) & 2.94 (1.5)  & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
     \midrule

### 2017-12-14 doc/icse2018/icse2018.tex
Finished datda summary
Working on the paper

--- 2017-11-15 doc/icse2018/icse2018.tex
@@
 
+\usepackage{syntax}
 \usepackage{booktabs} % For formal tables
@@
 \usepackage{longtable}
-\usepackage{longtable}
+\usepackage{pgfplots}
 \usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
@@
 %Conference
-\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
-  Paso, Texas USA} 
+\acmConference[ISSTA'18]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{July 2018}{Amsterdam, The Netherlands} 
 \acmYear{1997}
@@
 Suppose now that we would like to (unit) test this function in isolation to the rest of the application source code.
-We aim to maximize branch coverage as a common testing criteria~\cite{why_is_common}.
+We aim to maximize branch coverage as a common testing criteria~\cite{why.this.common}.
 That is for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we have to construct a test input which passes the branch and normally exists the function.
@@
 
-\begin{figure}
+\begin{figure}[t!]
   \centering 
-  \begin{sequencediagram}[font=\scriptsize]
-    \newinst{user}{User}
-    \newinst{server}{Server}
-    \newinst[1]{validator}{Validator}
-    \newinst{client}{Client}
+  \begin{sequencediagram}[font=\footnotesize]
+
+    \renewcommand\unitfactor{0.5}
+    \newinst{user}{\textbf{User}}
+    \newinst{server}{\textbf{Server}}
+    \newinst[1]{validator}{\textbf{Validator}}
+    \newinst{client}{\textbf{Client}}
 
@@
 
-      \begin{sdblock}{Genetic Loop}{\hspace{2mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{Random Loop}{errors > 0}
+      \begin{sdblock}{\textbf{Genetic Loop}}{\hspace{2mm}$\text{branch} \in \text{branches}'$}
+        \begin{sdblock}{\textbf{Random Loop}}{errors > 0}
           \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
@@
 
-        \begin{sdblock}{Fitness Loop}{(fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{Evaluation Loop}{p $\in$ pop}
+        \begin{sdblock}{\textbf{Fitness Loop}}{(fitness $\neq$ 0) $\vee$ gen.limit}
+
+          \begin{sdblock}{\textbf{Evaluation Loop}}{p $\in$ pop}
             \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
@@
 
-          \begin{sdblock}{Crossover Loop}{errors > 0}
-            \begin{call}{server}{cross = Crossover(pop)}{validator}{errors}
+          \begin{sdblock}{\textbf{Crossover Loop}}{errors > 0}
+            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
             \end{call}
@@
 
-          \begin{sdblock}{Mutation Loop}{errors > 0}
+          \begin{sdblock}{\textbf{Mutation Loop}}{errors > 0}
             \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
@@
 
-          \begin{callself}{server}{cross $\cup$ mut}{pop}
+          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
           \end{callself}
@@
 
-Given JS function $f$ and some set of its branches $B_f$, the purpose of our testing framework is to generate input arguments for $f$ that trigger executions covering all branches in $B_f$.
-The general workflow of the test generation process is represented as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of four interacting components: \User, \Server\, \Validator and \Client.
-\Server is the key one.
-It performs all preparatory steps (\emph{Initialization Phase}) as well as controls the data generation (\emph{Genetic Phase}).
-These two phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-Every request sent to \Validator\footnote{\url{https://validator.w3.org/nu/}} with an HTML document as the body triggers a response containing the list of syntactic errors in that document.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JavaScript code.
-It relies on the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library simulating calls to native DOM.
-
-Let us get a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-First, \User provides JS file \emph{fun.js} that defines the function under test (FUT) \emph{fun} annotated with its type.
-Additionally, user supplies a configuration file \emph{config} that parameterizes some settings related to the genetic algorithm, random generation, logging etc.
-These data are processed by \Server in the \emph{Initialization Phase}.
-As an output we get a tuple with the following information about $fun$: control flow graph (\emph{cfg}), list of branches (\emph{branches}), static information about constants (\emph{cinfo}), instrumented function (\emph{ifun}) and the function's signature (\emph{sig}).
-\Server sends a \texttt{POST} request to the \Client to store \emph{ifun} and \emph{sig}.
-Second, \Server asks \User to select a branch(s) that has to be covered by the execution of \emph{fun}.
-For each branch our framework enters the \emph{Genetic Loop}.
-Inside of this phase it starts with a randomly generated population (\emph{Random Loop}), and continues to optimize it until earthier perfect fitness is found or generation limit is exceeded.
-Each candidate in the population has to be evaluated (\emph{Evaluation Loop}).
-To do so \Client parses the candidate according the known signature \emph{sig}, invokes \emph{ifun} on the result, collects some information along the execution and sends it back to \Server, where the final fitness value is computed for the candidate.
-New population is formed as the joint result of the \emph{Crossover} and \emph{Mutation Loop}.
-These two loops together with the \emph{Random} one are performed in conversation with \Validator.
-It forces to proceed generation until no more errors are present in the data.
-At the end of the \emph{Fitness Loop} the best candidate with the best fitness value are reported back to \User.
-After exploring all branches \emph{Genetic Loop} terminates.
+Given JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
+We implemented such a framework as a client-server application which uses under the hood genetic test generation engine.
+The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
+The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
+\Server is the key component of the whole framework.
+It is responsible for the \emph{Initialization Phase} and test data generation in the \emph{Genetic Phase}.
+Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
+Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactical correctness and reports back the set of identified errors.
+\Server rejects the document if any errors were revealed and repeats the current step until the generated document has no errors anymore.
+\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
+We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate native browser API calls.
+
+Let us give a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
+As an input to our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with the type signature.
+Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random data generation, genetic phase, logging etc.
+Experimentally, we have found an optimal set of input configurations that was used across all the experimental subjects in Section~\ref{sec.evaluation}.
+The received data is processed by \Server during the \emph{Initialization Phase}.
+At the end of it we get the following information back: the control flow graph (\emph{cfg}) of \emph{fun}, the list of its branches (\emph{branches}), the \emph{fun}'s  constant (\emph{cinfo}) info, the instrumented version \emph{ifun} of \emph{fun}, and the \emph{fun}'s signature (\emph{sig}).
+\Server sends a \texttt{POST} request to the \Client to store there \emph{ifun} and \emph{sig}.
+Depending on the chosen execution mode, the \Server either asks the \User to select the target branch or covers all branches one by one in a fixed order.
+For each branch our framework enters the \emph{Genetic Loop (Phase)}.
+Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve the population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
+the limit of generation attempts is reached.
+Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
+It matches the candidate $p$ according the known type signature \emph{sig} and invokes the instrumented JS function \emph{ifun(p)}.
+The execution trace along with some collected information are sent back to the \Server, where the final fitness value is computed.
+The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
+If an HTML document is produced during one the genetic phases, it has to be approved by the \Validator first.
+At the end of the \emph{Fitness Loop} the candidate with the ``best'' fitness value is reported back to the \User.
+Once all branches are exercised, the algorithm reaches the end.
+In the follow up two sections we elaborate on the details of each individual component of our test generation framework.
 
@@
   \SetKwProg{Fn}{Function}{}{}
-  \Input{
-    $fun.js$ is a JS file with FUT and type annotation
-  }
-  \Output{
-    tuple with $(cfg, branches, cinfo, ifun, sig)$
-  }
+  \Input{JS file $fun.js$ with FUT and type annotation }
+  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
   \Fn{$Initialize(fun.js)$}{
 
-    $(ast, sig) \longleftarrow ParseFunAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstInfo(ast)$\label{alg.init.collect.info}\;
-    $ast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $cfg \longleftarrow BuildCFG(ast)$\label{alg.init.build.cfg}\;
+    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
+    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
+    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
+    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
+    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
     $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    $ifun \longleftarrow Instrument(ast)$\label{alg.init.instr}\;
     \Return{$(cfg, branches, cinfo, ifun, sig)$}
@@
 
-The goal of the \emph{Initialization Phase} is to prepare FUT for the follow up \emph{Genetic Phase}.
+During the \emph{Initialization Phase} we analyze FUN and collect data necessary for the consecutive genetic testing phase.
 The main steps of the initialization are illustrated in Algorithm~\ref{alg.init}.
-Given the file \emph{fun.js} as an input, we separately parse the function and its signature in line~\ref{alg.init.parse.fun.sig}.
-Currently our framework recognizes signatures composed of four primitive types such as \texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string} and a newly introduced type \texttt{dom}.
-To facilitate random generation in the \emph{Genetic Phase} we statically analyze the FUT to collect useful data about potential string and numeric constants (line~\ref{alg.init.collect.info}).
-Moreover, we track calls to such browser API methods as \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, \texttt{getElementsByName}, which gives us information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} respectively.
-Knowing this data significantly increases our chances to produce a desired test input.
-Sometimes it is necessary to normalize FUT before applying instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-we transform \emph{if-then} branches to \emph{if-then-else}.
-After the normalization we can build CFG (line~\ref{alg.init.build.cfg}) and get all branches (line~\ref{alg.init.get.branches}).
-The final step is to instrument \emph{fun} (line~\ref{alg.init.instr}) in order to collect some run-time data such as execution trace, branch and loop distances, and constants.
-This data will be required for fitness evaluation (Section~\ref{sub.sub.sec.fitness.fun}) and updating of \emph{cinfo}.
+Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
+In order to maximize the chances of generating the fittest candidate in the genetic phase, we perform a static analysis of the FUT with the purpose to collect constant info in line~\ref{alg.init.collect.info}.
+Such constants include string and numeric literals as well as the arguments to the following DOM API methods:
+\begin{itemize}
+\item \texttt{getElementsByTagName}
+\item \texttt{getElementById}
+\item \texttt{getElementsByClassName}
+\item \texttt{getElementsByName}
+\end{itemize}
+which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} used in the FUT.
+Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
+we need to transform \emph{if-then} branches into \emph{if-then-else}.
+We need to instrument the FUT (line~\ref{alg.init.instr}) in order be able to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants.
+Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure.
+The last two steps are to construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
+
+\subsubsection{Supported Types}
+\label{sub.sec.sup.types}
+
+\begin{figure}[t]
+\setlength{\grammarparsep}{3pt}
+\small
+\begin{grammar}
+
+<JS Type Annotation> ::= /*t <Signature> */
+
+<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
+
+<DOM> ::= \texttt{dom}
+
+<Type Signature> ::= <Type> | <Type> : <Type Signature>
+
+<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
+
+<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
+
+<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
+\end{grammar}
+\caption{Grammar of supported JS type annotations}
+\label{fig.js.type.annot}
+\end{figure}
+
+The grammar of JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
+Each type annotation is a signature surrounded with a specialized JS type comment (\texttt{/*t...*/}).
+We distinguish two between kinds of signatures those who refer to the global DOM and ``ordinary'' JS type signatures.
+Functions with a DOM signature expect a \texttt{dom} argument being passed as the first implicit parameter to the function call.
+Ordinary JS signature is a non-zero sequence of JS types.
+The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
 
@@
   \Input{
-    $b_N$ is target branch, $cfg$ is control-flow graph\\
-    $cinfo$ is constant info, $config$ is configuration file\\
-    $ifun$ instrumented JS function, $sig$ type signature
+    $config$ is a GA configuration file\\
+    $b_n$ is a target branch of FUT\\
+    $(cfg, branches, cinfo, ifun, sig)$ output of Algorithm~\ref{alg.init}
   }
   \Output{
-     element $p^*$ on which the best fitness $f^*$ is achieved  
-  }
-  \Fn{$Genetic(b_N, cfg, cinfo, config, ifun, sig)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
-    $archive \longleftarrow \emptyset$; $i \longleftarrow 0 $\label{alg.gen.arch.init}\;
+     $(f^*, p^*)$ the best population candidate and its fitness score
+  }
+  \Fn{$Genetic(b_n, cfg, cinfo, config, ifun, sig)$}{
+    $(size_P, size_A, size_G, rate_C, rate_M,size_{H}) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
+    $target \longleftarrow b_n$\label{alg.gen.init.target}\; 
+    $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
+    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
+      $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\; 
+      $history \longleftarrow \emptyset$\label{alg.gen.init.history}\; 
       $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
-    \Repeat{$isPerfect(f^*) \vee i > size_G $}{\label{alg.gen.loop.begin}
+      \Repeat{$isPerfect(f^*) \vee historyConverged \vee (i > size_G)$}{\label{alg.gen.loop.begin}
         $scoredPop \longleftarrow \emptyset$\;
+        $history \longleftarrow history \cup archive$\;
         \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
-        $args \longleftarrow MakeArguments(p, sig)$\label{alg.gen.make.args}\;
-        $(tr, d_B, d_L, consts) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
-        $f \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
+          $args \longleftarrow CoerceArguments(p, sig)$\label{alg.gen.make.args}\;
+          $(tr, d_B, d_L, dyncinfo) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
+          $f \longleftarrow Score(target, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
+          $cinfo \longleftarrow cinfo \cup dyncinfo$\label{alg.gen.eval.end}\;
           $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        $cinfo \longleftarrow consts \cup cinfo$\label{alg.gen.eval.end}\;
         }
@@
         $i \longleftarrow i + 1$\;
+        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
       }\label{alg.gen.loop.end}
+      $target \longleftarrow NewTarget(branches, b_n)$\label{alg.gen.new.target}\;
+    }\label{alg.gen.converged.loop.end}
     \Return{$(f^*, p^*)$}\label{alg.gen.return} 
@@
 The heart of our test data generation framework is in the \emph{Genetic Phase}.
-The main workflow of the underlying genetic algorithm (GA) is quite standard~\cite{poli2008field}, and with some adjustments is presented in Algorithm~\ref{alg.gen}.
-First, we read the \emph{config} file in line~\ref{alg.gen.read.config}.
-As a result, we get information about the number of elements in a population ($size_P$), size of the archive ($size_A$), number of generations ($size_G$) and respectively crossover ($rate_C$) and mutation ($rate_M$) rates.
-\emph{Archive} has the capacity of $size_A$ elements and stores the most fitted candidates observed so far.
-It is empty in the beginning of the evolution (line~\ref{alg.gen.arch.init}).
-The first population consisting of $size_P$ elements is randomly constructed from the elements in \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-Inside of the loop (lines~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}) we are evolving the population until either the perfect fitness is found or the generation limit $size_G$ is reached.
-But first step in this loop is to score the current population~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
-Each candidate in the population has to be converted to an argument list by coercing it to a respective type according to the signature $sig$ (line~\ref{alg.gen.make.args}).
-Calling the instrumented function $ifun$ on those arguments (line~\ref{alg.gen.call.ifun}), we get 4-tuple consisting of the execution trace ($tr$), the branch distances ($d_B$), the loop distances ($d_L$) and the new set of constants ($consts$) collected at the run time.
-The next step is actually to evaluate the fitness value of the given candidate (line~\ref{alg.gen.eval}).
-Collected constants $consts$ are added to the existing constants info $cinfo$ (line~\ref{alg.gen.eval.end}).
-Eventually the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) and is used for the crossover (line~\ref{alg.gen.cross}) and mutation steps (line~\ref{alg.gen.mut}).
-The rates specify the distribution in which the respective operations are applied to produce the new population (line~\ref{alg.gen.new.pop}).
-Scored population together with the current archive are sorted based on the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-On top of the archive we have the most fitted candidate observed over the course of all iterations (line~\ref{alg.gen.archive.head}).
-The fitness value of that element defines if perfect candidate is found (line~\ref{alg.gen.loop.end}) and it is return at the end of the algorithm (line~\ref{alg.gen.return}).
-
-In order to instantiate genetic algorithm for a particular problem, its user has to define all the aforementioned operations specific for the problem in question.
-Since GAs have been commonly used for generation of test data for primitive types such as integers and strings~\cite{paper_on_search-based_test_case_generation}, we skip their definitions and rather focus or the interesting case, namely, HTML generation.
+The main workflow of the underlying genetic algorithm (GA) is, though, being fairly standard~\cite{poli2008field} but has been extended with the concept of \emph{archive convergence} (Algorithm~\ref{alg.gen}).
+We get as an input a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and the tuple of parameters computed by Algorithm~\ref{alg.init}.
+The output consists of the ``best'' fitness score $f^*$ achieved on the population candidate $p^*$.
+
+First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: 
+%% \begin{itemize}
+%% \item $size_P$ is the size of the genetic population
+%% \item $size_A$ is the size of the genetic archive
+%% \item $size_G$ is the total number of the genetic iterations
+%% \item $rate_C$ is a crossover rate
+%% \item $rate_M$ is a mutation rate
+%% \item $size_H$ is a history window size
+%% \end{itemize}
+a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
+We set the initial target to $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ to 0 (line~\ref{alg.gen.iter.count}).
+Until the history of archives has not converged or the limit of the generations has not been reached, we are initializing the genetic search of the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}).
+An \emph{archive} stores the most fitted population candidates observed so far.
+It is empty in the beginning of the evolution (line~\ref{alg.gen.arch.init}) as well as the history of archives \emph{history} (line~\ref{alg.gen.init.history}).
+The first population of $size_P$ elements is randomly generated out of the constants taken from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
+Then, in loop lines~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either the perfect candidate is found or the history of archives is converged or the generation limit $size_G$ is reached.
+But the first step in this loop is scoring the current population~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
+Each candidate of the population represents a concrete argument list of the FUT so it has to be coerced with respect to the type signature $sig$ (line~\ref{alg.gen.make.args}).
+After calling the instrumented function \emph{ifun} on $args$ (line~\ref{alg.gen.call.ifun}), we get 4-tuple consisting of an execution trace ($tr$), the sets of branch ($d_B$) and loop distances ($d_L$), and dynamic constant info (\emph{dyncinfo}) collected at the run-time.
+The next step is actually scoring the fitness value for the given population candidate (line~\ref{alg.gen.eval}).
+Collected constants \emph{dyncinfo} are merged with existing constant pool (line~\ref{alg.gen.eval.end}).
+Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) and it is used for the crossover (line~\ref{alg.gen.cross}) and mutation steps (line~\ref{alg.gen.mut}).
+The rates specify the proportion in with two operation contribute the formation of the new population (line~\ref{alg.gen.new.pop}).
+The scored population together with the current archive are sorted by the fitness value, and the best $size_A$ elements form a new archive (line~\ref{alg.gen.new.archive}).
+The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}).
+The fitness value of that element defines if a perfect candidate is found (line~\ref{alg.gen.loop.end}).
+Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}).
+
+In some cases, when we do get enough guidance from the fitness function, the genetic algorithm converges to a local minimum~\cite{ga.flag.problem.or.survey}.
+For example, if one branch is dominated by another, the coverage of the former branch depends on the coverage of the latter.
+Unless this relation is captured by the branch condition on the former branch, the respective fitness function does not reflect on the branch dependency.
+In this situation, we find ourselves being trapped on a flat space, with a small unreliable chance to escape.
+In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
+If during a certain history window, the fitness values of the respective archives converge to a fixed point, we restart the genetic search and redefine the search target.
+At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we compute the convergence condition of the fitness values in the first $size_H$ archives taken from the history.
+If the fitness has converged (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new target.
+It consists of the original branch $b_n$ prefixed with a branch $b \in branches$ which our branch depends on (line~\ref{alg.gen.new.target}).
+Every time genetic search converges, we produce a new partial path by eventually covering all possible executions leading to $b_n$.
+In practice, we limit this process by the target of length two.
+
+In the rest of this section, we elaborate on the technical details of the genetic algorithm such as random generation in Section~\ref{sub.sub.sec.random.html}, mutation and crossover in Section~\ref{sub.sub.sec.genetic.oper}, and fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
+Our primary focus in those sections will be on the generation and transformation of the HTML documents.
+Table~\ref{} descries how similar operations are implemented for primitive and array JS types.
+
+\begin{table}
+  \caption{Genetic Operation for JS types}
+  \label{tbl.gen.oper.js.types}
+    \footnotesize
+  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
+    \toprule
+    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
+    \midrule
+    Random & Bool & choose at random \{\texttt{true}, \texttt{false}\} \\
+    Random & Int  & with 80\% probability choose an integer from [-10, 10], or with 20\% from integer constants\\
+    Random & Float & with 80\% probability choose an float from [-10.0, 10.0], or with 20\% from float constants\\
+    Random & String & with 80\% probability make a random string up to length five composed characters \texttt{[a-zA-Z0-9]}, or with 20\% from string constants\\
+    Random & Array & make a random array of a respective type upto length five\\
+    \midrule
+    Crossover & Bool   & pick at random one out of two given boolean \\
+    Crossover & Int    & pick at random one out of two given integers\\
+    Crossover & Float  & pick at random one out of two given floats\\
+    Crossover & String & choose independently crossover point for each string, swap ends, and pick result at random\\
+    Crossover & Array & similar crossover operator as for strings\\
+    \midrule
+    Mutation & Bool & Flip the boolean constant\\
+    Mutation & Int  & Generate a new integer value, on increase (decrease) by 1 or 10 the given one\\
+    Mutation & Float  & Generate a new float value, on increase (decrease) by 0.1, 1 or 10 the given one\\
+    Mutation & String & Generate an new string values, remove a random character in a string, or replace a successor (predecessor) a random character\\
+    Mutation & Array & Mutate a random element in array according to its type\\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 
-In order to evaluation the feasibility of practical adoption of our genetic test generation framework, we carried out empirical validation on a set of case studies.
-Table~\ref{tbl.gen.config} shows summary of configuration parameters for both random and genetic instances of our framework.
+In order to evaluate practical feasibility of the test framework adoption, we conducted an empirical validation on a set of case studies.
+Table~\ref{tbl.gen.config} gives summary of configuration parameters for both random and genetic instances of our framework.
 As a baseline we implemented random test generation strategy.
@@
     Mutation rate                     & 0   & 0.5 \\
-    Restart after archive convergence & -   & - (5,10) \\
+    History window size               & 200 & 5/10/200 \\
     \bottomrule
@@
 
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the web.
-They all are greatly vary in size, complexity and coding style.
-Moreover, many popular JS web-frameworks, including jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach for DOM manipulation to vanilla-like JS.
-Therefore, search for appropriate case-studies requires careful inspection of the application source code, which is often time consuming and labor intensive process.
-These factors significantly complicate the choice of suitable evaluation subjects.
-Therefore, we decided to form our experimental data set from two related research works \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
-Moreover, we introduced two additional subjects found in open source \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}}.
-For each case study application, we identified several JS functions which were suitable for our test generation framework.
-Our evaluation set includes both primitive and manipulating with DOM JS functions.
+Being one of the most popular programming languages of modern time, there are ample open source JS projects on the Web.
+Being written with the help of countless number of specialized JS libraries, JS applications greatly vary in size, complexity and coding style.
+Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation.
+In order to choose suitable case-studies, we need to scrutinize the source code of the JS applications which is time consuming and labor intensive process.
+Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
+Both of these works address the problem of testing of JS application with the reference to the browser DOM.
+Since our testing framework is capable of dealing with the browserless imperative JS code as well, we introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}}.
+For each case-study application, we identified several JS functions that are suitable for our testing framework.
+In the end, our evaluation set included both primitive and DOM related JS functions.
 
@@
   %\resizebox{\textwidth}{!}{
-    \footnotesize
-  \begin{tabular}{l|l|l|r|r|r|c|c|c|c}
+    \scriptsize
+  \begin{tabular}{l|l|l|r|r|r|r|c|c|c|c}
     \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type} & \textbf{\#BR} & \textbf{\#LOC} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \midrule
-    sudoku     & helpMe & (dom,int,int) & & & & + & + & + & - \\
-    sudoku     & isGameFinished & (dom) & & & & + & + & + & + \\
-    sudoku     & newGame & (dom)        & & & & + & + & + & + \\
-    sudoku     & revealAll & (dom)      & & & & + & + & + & - \\
-    sudoku     & shuffleBoard & (dom)   & & & & + & - & + & - \\
-    \midrule
-    phormer    & toggleInfo & (dom,string) & & & & + & + & - & - \\
-    \midrule
-    hotel RS   & isValidCard & ([int]) & & & & - & - & - & - \\
-    hotel RS   & isValidMasterCard & ([int])  & & & & - & - & - & - \\
-    \midrule
-    apophis    & initShields & (dom,[int],int,int) & & & & + & + & - & -\\
-    \midrule
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & & & & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int) & & & & + & + & - & - \\
-    \midrule
-    burncanvas & do\_draw & (int,int,int,int,int,int,int) & & & & - & - & - & - \\
-    \midrule
-    mathjs     & prob\_gamma & (float) & & & & - & - & - & - \\
+    \textbf{case-study} & \textbf{function} & \textbf{type} & \textbf{\#LOC} & \textbf{\#BR} & \textbf{\#D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
+    \midrule
+    sudoku     & helpMe & (dom,int,int)                                   & 15 & 2  & 3 & 3  & + & + & + & - \\
+    sudoku     & isGameFinished & (dom)                                   & 17 & 4  & 3 & 5  & + & + & + & + \\
+    sudoku     & newGame & (dom)                                          & 12 & 1  & 2 & 2  & + & + & + & + \\
+    sudoku     & revealAll & (dom)                                        & 14 & 0  & 2 & 1  & + & + & + & - \\
+    sudoku     & showCell* & (dom)                                         &    &    &   &    &   &   &   & \\
+    sudoku     & shuffleBoard & (dom)                                     & 26 & 2  & 3 & 3  & + & - & + & - \\
+    sudoku     & switchLevel* & (dom,bool)                                 &    &    &   &    &   &   &   & \\
+    \midrule
+    phormer    & toggleInfo & (dom,string)                                & 15 & 3  & 1 & 4  & + & + & - & - \\
+    phormer    & update* & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &    &   &    &   &   &   & \\
+    phormer    & updateIndic* & (dom,bool)                                 &    &    &   &    &   &   &   & \\
+    \midrule
+    hotel RS    & RequiredField* & (dom,[string])                           &    &    &   &    &   &   &   & \\
+    hotel RS   & isValidCard & ([int])                                    & 20 & 2  & 2 & 5  & - & - & - & - \\
+    hotel RS   & isValidMasterCard & ([int])                              & 6  & 4  & 1 & 7  & - & - & - & - \\
+    hotel RS    & isValidVISA & ([int])                                    &    &    &   &    &   &   &   & \\
+    hotel RS    & validateNumber* & (dom,string)                            &    &    &   &    &   &   &   & \\
+    \midrule
+    apophis    & doRain* & (dom,string,int,int,int,int,int,int)            &    &    &   &    &   &   &   & \\
+    apophis    & drawShields* & (dom,[int])                                &    &    &   &    &   &   &   & \\
+    apophis    & fireMeteor* & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) &    &    &   &    &   &   &   & \\
+    apophis    & getReady* & (dom,int,int,int,int,int,int)                 &    &    &   &    &   &   &   & \\
+    apophis    & initShields & (dom,[int],int,int)                        & 8  & 0  & 1 & 1  & + & + & - & -\\
+    \midrule
+    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
+    bingbong   & initBricks & (dom,[int],int,int)                         & 63 & 12 & 4 & 13 & + & + & - & - \\
+    bingbong   & doPaddlePower & (dom,int,int)                            &    &    &   &    &   &   &   & \\
+    bingbong   & drawLevel* & (dom,int,int,int,int)                        &    &    &   &    &   &   &   & \\
+    bingbong   & goPing* & (dom,int,int,int)                               &    &    &   &    &   &   &   & \\
+    \midrule
+    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 39 & 12 & 2 & 14 & - & - & - & - \\
+    \midrule
+    cs-in-js   & luhn-algorithm* & (string,bool)                           &    &    &   &    &   &   &   & \\
+    cs-in-js   & quicksort-partition* & ([int],int,int)                    &    &    &   &    &   &   &   & \\ 
+    \midrule
+    mathjs     & prob\_gamma & (float)                                    & 56 & 8  & 2 & 16 & - & - & - & - \\
     \bottomrule
@@
 
+% \input{summary_statistics}
+
+\setlength\tabcolsep{2pt}
 \begin{table*}
@@
   \label{tbl.stats}
-  \resizebox{\textwidth}{!}{
-    \footnotesize
-    \begin{tabular}{l|rrrr|rrrr|rrrr|rrrr|r|r|r|r|r|r}
+  \scriptsize
+  %\resizebox{\textwidth}{!}{
+
+    \begin{tabular}{l|rrrr|rrrr|rrrr|rrrr|rrrrrr}
       \toprule
-      \textbf{name}     & $\bar{x}_R$ & $\bar{x}_G$ & $\bar{x}_{G5}$ & $\bar{x}_{G10}$ & $m_R$ & $m_G$ & $m_{G5}$ & $m_{G10}$ & $\min_R$ & $\min_G$ & $\min_{G5}$ & $\min_{G10}$ & $\max_R$ & $\max_G$ & $\max_{G5}$ & $\max_{G10}$ & \textbf{G-R} & \textbf{G5-R} & \textbf{G10-R} & \textbf{G5-G} & \textbf{G10-G} & \textbf{G10-G5}\\
+      \textbf{NAME}   & $\mathbf{\bar{x}_R}$     & $\mathbf{\bar{x}_G}$   & $\mathbf{\bar{x}_{G5}}$ & $\mathbf{\bar{x}_{G10}}$ & $\mathbf{m_R}$       & $\mathbf{m_G}$     & $\mathbf{m_{G5}}$     & $\mathbf{m_{G10}}$   & $\mathbf{mn_R}$  & $\mathbf{mn_G}$ & $\mathbf{mn_{G5}}$ & $\mathbf{mn_{G10}}$ & $\mathbf{mx_R}$  & $\mathbf{mx_G}$ & $\mathbf{mx_{G5}}$ & $\mathbf{mx_{G10}}$ & \textbf{R-G} & \textbf{R-G5} & \textbf{R-G10} & \textbf{G-G5} & \textbf{G-G10} & \textbf{G5-G10}\\
       \toprule
-      helpMe          &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
-    $(3,4,\inFor)$    & 3.94        & 7.94        & 10.22          & 11.7          & 3     & 3.5   & 7       & 7       & 1        & 1        & 1          & 1           & 16       & 31      & 63         & 124 & & & & & & \\
-    $(5,6,\thenBr)$   & 3.7         & 13.08       & 9.2            & 9.6           & 3     & 7     & 5       & 5.5     & 1        & 1        & 1          & 1           & 14       & 95      & 44         & 105 & & & & & & \\
-    $(5,15,\elseBr)$  & 118.64      & 30.14       & 34.12          & 31.68         & 119.5 & 23    & 28.5    & 22      & 4        & 4        & 3          & 1           & 199      & 97      & 167        & 114 & & & & & & \\
-    $(9,10,\thenBr)$  & 105.12      & 17.82       & 21.98          & 21.8          & 83.5  & 17    & 17.5    & 18      & 18       & 1        & 2          & 6           & 199      & 53      & 78         & 77  & & & & & & \\
-    $(9,14,\elseBr$   & 4.28        & 5.06        & 8.14           & 9.56          & 2.5   & 5     & 4       & 4       & 1        & 1        & 1          & 1           & 17       & 20      & 49         & 74  & & & & & & \\
-    \midrule
-    isGameFinished    &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
-    %% $(5,6,\inFor)$    & 0.02        & 0.1         & 0.12           & 0.1           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 2       & 2          & 2   \\
-    $(7,8,\thenBr)$   & 75.18       & 40.54       & 18.86          & 14.66         & 35.5  & 7     & 8       & 11      & 0        & 0        & 0          & 0           & 199      & 199     & 199        & 82  & & & & & & \\
-    %% $(7,15,\elseBr)$  & 0           & 0.06        & 0.04           & 0.08          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 0        & 2       & 1          & 2   \\
-    $(10,11,\thenBr)$ & 199         & 35.74       & 21.56          & 24.36         & 199   & 10    & 10      & 9       & 199      & 1        & 1          & 1           & 199      & 199     & 199        & 199 & & & & & & \\
-    $(10,14,\elseBr)$ & 69.62       & 56.32       & 28.74          & 31.92         & 23.5  & 10    & 16.5    & 18      & 1        & 0        & 0          & 0           & 199      & 199     & 199        & 199 & & & & & & \\
-    \midrule
-    newGame           &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
-    %% $(4,5,\inFor)$    & 0.04        & 0.12        & 0.1            & 0             & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 2       & 1          & 0 \\
-    $(6,7,\thenBr)$   & 21.54       & 10.48       & 9.92           & 8.34          & 15    & 7.5   & 7.5     & 7       & 0        & 0        & 0          & 0           & 97       & 53      & 30         & 35 & & & & & & \\
-    %% $(6,12,\elseBr)$  & 0.06        & 0.14        & 0.1            & 0.04          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 3       & 2          & 1\\
-    \midrule
-    revealAll         &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
-    $(2,3,\inFor)$    & 31.78       & 24.84       & 34.94          & 28.04         & 24    & 23    & 29      & 22.5    & 4        & 7        & 7          & 10          & 106      & 57      & 129        & 75 & & & & & & \\
-    $(4,5,\inFor)$    & 46.12       & 26.22       & 30.1           & 27.64         & 34    & 19    & 26.5    & 22      & 5        & 9        & 9          & 6           & 199      & 78      & 71         & 90 & & & & & & \\
-    \midrule
-    shuffleBoard      &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
-    %% $(5,6,\inWhile)$  & 0.36        & 0.32        & 0.24           & 0.48          & 0     & 0     & 0.24    & 0       & 0        & 0        & 0          & 0           & 4        & 3       & 2          & 0\\
-    $(13,14,\thenBr)$ & 6.38        & 7.7         & 8.72           & 7.86          & 4     & 4     & 8.72    & 4       & 0        & 0        & 0          & 0           & 22       & 67      & 64         & 38 & & & & & & \\
-    $(17,18,\thenBr)$ & 5.66        & 11.86       & 16.96          & 17.72         & 3.5   & 5.5   & 16.96   & 3.5     & 0        & 0        & 0          & 0           & 33       & 133     & 86         & 118 & & & & & & \\
-    %% $(21,22,\inFor)$  & 199         & 199         & 199            & 199           & 199   & 199   & 199     & 199     & 0        & 0        & 0          & 0           & 199      & 199     & 199        & 199\\
-    \midrule
-    \midrule
-    toggleInfo        &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
-    $(2,3,\thenBr)$   & 1.58        & 1.12        & 1.1            & 1             & 1     & 1     & 1       & 1       & 0        & 0        & 0          & 0           & 11       & 4       & 3          & 3 & & & & & & \\
-    $(6,7,\thenBr)$   & 1.48        & 9.9         & 17             & 15.3          & 1     & 2     & 4       & 4       & 0        & 0        & 0          & 0           & 8        & 125     & 143        & 136 & & & & & & \\
-    \midrule
-    \midrule
-    isValidCard       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
-    $(3,6,\elseBr)$   & 199         & 2.98        & 3              & 2.82          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 5          & 4 & & & & & & \\
-    $(7,8,\inFor)$    & 199         & 2.92        & 3.04           & 2.96          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 4          & 5 & & & & & & \\
-    $(10,11,\thenBr)$ & 199         & 3           & 2.86           & 3.06          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
-    $(10,13,\elseBr)$ & 199         & 2.84        & 2.98           & 3.04          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
-    $(14,15,\inFor)$  & 199         & 3.02        & 2.92           & 2.94          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
-    \midrule
-    isValidMasterCard & \multicolumn{16}{l}{} \\ 
-    $(2,3,\thenBr)$   & 199         & 11.04       & 12.08          & 11.42         & 199   & 10    & 12      & 12      & 199      & 4        & 5          & 5           & 199      & 27      & 32         & 23 & & & & & & \\
-    %% isValidVISA       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
-    %% $(2,3,\thenBr)$   & 199         & 6.54        & 6.38           & 6.48          & 199   & 6     & 6       & 6       & 199      & 4        & 3          & 4           & 199      &  14     & 16         & 18  \\
-    \midrule
-    \midrule
-    initShields       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
-    $(2,3,\inFor)$    & 5           & 5.32        & 5.28           & 5.26          & 5     & 5     & 5       & 5       & 5        & 5        & 5          & 5           & 5        & 6       & 7          & 7 & & & & & & \\
-    \midrule
-    \midrule
-    brickJiggler      &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
-    $(2,3,\thenBr)$   & 5.22        & 5.34        & 5.68           & 5.3           & 5     & 4     & 4       & 4       & 1        & 2        & 1          & 1           & 18       & 39      & 20         & 20 & & & & & & \\
-    doPaddlePower     &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
-    %% $(5,8,\elseBr)$   & 0.14        & 0.4         & 0.14           & 0.28          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 5       & 3          & 5 \\
-    $(10,11,\thenBr)$ & 17.96       & 193.14      & 47.18          & 42.5          & 14.5  & 199   & 17      & 21      & 0        & 3        & 0          & 0           & 53       & 199     & 199        & 199 & & & & & & \\
-    %% drawLevel         &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
-    %% $(5,6,\thenBr)$   & 0.18        & 0.16        & 0.14           & 0.2           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 2        & 3       & 5          & 5 \\
-    %% $(8,9,\inFor)$    & 0.1         & 0.16        & 0.34           & 0.3           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 3        & 5       & 5          & 5 \\
-    %% $(10,11,\thenBr)$ & 0.64        & 1.26        & 0.98           & 0.8           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 3        & 7       & 7          & 8 \\
-    %% $(10,13,\elseBr)$ & 0.06        & 0.22        & 0.3            & 0.2           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 3       & 7          & 3 \\
-    %% $(14,15,\inFor)$  & 0.08        & 0.34        & 0.3            & 0.36          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 7       & 4          & 6 \\
-    \midrule
-    initBricks        &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
-    $(6,7,\thenBr)$   & 1.5         & 3           & 2.6            & 2.74          & 1     & 4     & 2       & 2       & 1        & 1        & 1          & 1           & 5        & 5       & 5          & 5 & & & & & & \\
-    $(6,10,\elseBr)$  & 29.82       & 5.98        & 5.28           & 7.1           & 13.5  & 5     & 5       & 5       & 1        & 1        & 1          & 1           & 199      & 14      & 13         & 24 & & & & & & \\
-    $(11,12,\thenBr)$ & 162.28      & 18.36       & 27.58          & 25.26         & 199   & 13    & 16.5    & 16      & 2        & 5        & 4          & 4           & 199      & 56      & 71         & 77 & & & & & & \\
-    $(11,15,\elseBr)$ & 32.44       & 5.9         & 6.02           & 8.1           & 17    & 5     & 6       & 5       & 1        & 1        & 1          & 1           & 199      & 16      & 28         & 55 & & & & & & \\
-    $(16,17,\thenBr)$ & 164.06      & 25.14       & 37.48          & 28.64         & 199   & 16    & 12.5    & 16      & 4        & 4        & 1          & 2           & 199      & 199     & 199        & 112 & & & & & & \\
-    $(16,20,\elseBr)$ & 57.22       & 8.32        & 12.2           & 10.92         & 23.5  & 6     & 5       & 7       & 1        & 1        & 1          & 1           & 199      & 62      & 68         & 86 & & & & & & \\
-    $(21,22,\thenBr)$ & 152.56      & 19.38       & 30.92          & 40.12         & 199   & 13    & 12.5    & 16      & 1        & 1        & 2          & 2           & 199      & 199     & 117        & 149 & & & & & & \\
-    $(21,25,\elseBr)$ & 56.34       & 6.88        & 11.56          & 12.82         & 24.5  & 6     & 6       & 6.5     & 2        & 2        & 1          & 1           & 199      & 22      & 91         & 80 & & & & & & \\
-    $(29,30,\thenBr)$ & 147.66      & 102.66      & 91             & 96.48         & 199   & 65    & 69.5    & 73      & 2        & 5        & 5          & 5           & 199      & 199     & 199        & 199& & & & & & \\
-    $(29,37,\elseBr)$ & 1.46        & 2.5         & 2.52           & 2.78          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 5        & 6       & 5          & 5 & & & & & & \\
-    $(38,39,\thenBr)$ & 145.72      & 108.1       & 94.46          & 89.2          & 184   & 84    & 74.5    & 46.5    & 16       & 4        & 11         & 4           & 199      & 199     & 199        & 199& & & & & & \\
-    $(38,46,\elseBr)$ & 1.42        & 2.5         & 2.7            & 2.5           & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 6       & 6          & 5 & & & & & & \\
-    $(47,48,\thenBr)$ & 141.5       & 121         & 112.16         & 108.1         & 185.5 & 199   & 118     & 125.5   & 2        & 5        & 5          & 6           & 199      & 199     & 199        & 199 & & & & & & \\
-    $(47,55,\elseBr)$ & 1.54        & 2.44        & 2.5            & 2.46          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 4        & 5       & 5          & 5 & & & & & & \\
-    $(56,57,\thenBr)$ & 111.98      & 96.62       & 94.8           & 90.16         & 108   & 48.5  & 113     & 48      & 3        & 5        & 5          & 4           & 199      & 199     & 199        & 199 & & & & & & \\
-    $(56,64,\elseBr)$ & 1.52        & 2.66        & 2.96           & 2.48          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 5       & 13         & 5 & & & & & & \\
-    $(69,70,\thenBr)$ & 1.42        & 2.64        & 2.8            & 2.52          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 6       & 7          & 6 & & & & & & \\
-    $(69,71,\elseBr)$ & 74.98       & 102.98      & 54.82          & 55.42         & 39.5  & 93.5  & 20      & 26      & 1        & 2        & 1          & 1           & 199      & 199     & 199        & 199 & & & & & & \\
-    \midrule
-    \midrule
-    do\_draw           &             &            &               &                &       &       &         &         &           &          &           &             &          &          &           & & & & & & & \\
-    $(6,7,\thenBr)$    & 8.88        & 6.67       & 6.4           & 5.84           & 6.5   & 7     & 7       & 6       & 0         & 0        & 0         & 0           & 43       & 13       & 16        & 14 & & & & & & \\
-    $(6,12,\elseBr)$   & 12.58       & 5.56       & 5.88          & 5.62           & 9     & 5     & 6       & 6       & 0         & 0        & 0         & 0           & 53       & 17       & 14        & 15 & & & & & & \\
-    $(8,11,\elseBr)$   & 131.86      & 18.78      & 24.16         & 19.34          & 143   & 15.5  & 22      & 18      & 6         & 4        & 6         & 5           & 199      & 65       & 53        & 46 & & & & & &\\
-    %% $(24,27,\elseBr)$  & 0.02        & 0.08       & 0.18          & 0.06           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 1        & 3        & 5         & 3\\
-    %% $(36,39,\elseBr)$  & 0.32        & 0.7        & 0.52          & 0.12           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 4        & 7        & 7         & 2\\
-    %% $(40,43,\elseBr)$  & 0.1         & 0.1        & 0.52          & 0.34           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 1        & 2        & 6         & 12\\
-    $(44,45,\thenBr)$  & 76.1        & 149.16     & 32.14         & 42.8           & 56    & 199   & 26.5    & 38.5    & 3         & 3        & 0         & 1           & 199      & 199      & 199       & 199 & & & & & & \\
-    $(48,49,\thenBr)$  & 36.6        & 114.42     & 29.42         & 31.32          & 25    & 135.5 & 27.5    & 33      & 0         & 0        & 0         & 0           & 185      & 199      & 124       & 41 & & & & & & \\
-    \midrule
-    \midrule
-    prob\_gamma &             &            &               &                &       &       &         &         &           &          &           &             &          &          &           &  & & & & & & \\
-    $(4,5,\thenBr)$    & 195.58      & 1.02       & 1             & 1.06           & 199   & 1     & 1       & 1.06    & 28        & 1        & 1         & 1           & 199      & 2        & 1         & 2 & & & & & & \\
-    $(6,7,\thenBr)$    & 195.2       & 1.14       & 1.29          & 1.28           & 199   & 1     & 1       & 1.28    & 21        & 1        & 1         & 1           & 199      & 3        & 3         & 4 & & & & & & \\
-    $(6,9,\elseBr)$    & 199         & 1.42       & 1.39          & 1.46           & 199   & 1     & 1       & 1.46    & 199       & 1        & 1         & 1           & 199      & 4        & 4         & 4 & & & & & & \\
-    $(10,11,\thenBr)$  & 199         & 60.92      & 61.51         & 60.22          & 199   & 61    & 61      & 60.22   & 199       & 45       & 50        & 48          & 199      & 72       & 76        & 76 & & & & & & \\
-    $(10,13,\elseBr)$  & 199         & 1.24       & 1.19          & 1.22           & 199   & 1     & 1       & 1.22    & 199       & 1        & 1         & 1           & 199      & 2        & 3         & 3 & & & & & & \\
-    $(16,17,\inWhile)$ & 199         & 1.46       & 1.7           & 1.76           & 199   & 1     & 1       & 1.76    & 199       & 1        & 1         & 1           & 199      & 3        & 6         & 8 & & & & & & \\
-    $(20,21,\thenBr)$  & 199         & 5.38       & 4.85          & 6.32           & 199   & 5     & 4       & 6.32    & 199       & 1        & 1         & 1           & 199      & 14       & 14        & 25 & & & & & & \\
-    $(20,23,\elseBr)$  & 199         & 1.54       & 1.37          & 1.28           & 199   & 1     & 1       & 1.28    & 199       & 1        & 1         & 1           & 199      & 4        & 4         & 3 & & & & & & \\
-    $(30,31,\thenBr)$  & 199         & 51.44      & 52            & 51.96          & 199   & 52    & 51.66   & 51.96   & 199       & 42       & 41        & 42          & 199      & 62       & 61        & 62 & & & & & & \\
-    $(34,35,\thenBr)$  & 199         & 22.66      & 23            & 23.32          & 199   & 23    & 23.32   & 23.32   & 199       & 13       & 15        & 16          & 199      & 29       & 33        & 28 & & & & & & \\
+      \textbf{helpMe} & 293    & 63.18 & 78.34 & 80.68 & 270 & 47   & 59.5 &  55.5 & 33   & 7    & 8      & 12     & 609 & 258 & 368  & 468 & & & & & & \\
+    $(3,4,\inFor)$    & 5.34   & 6.24  & 8.48  & 9.32  & 4   &  3    & 6    &  6    & 1     & 1    & 1      & 2       & 21   &  23   &  48    & 84  & 0.57 & 0.41 & 0.39 & 0.38 &  0.37 & 0.47 \\
+    $(5,6,\thenBr)$   & 5.74   & 9.86  &  7.76  & 8.06  & 5   & 5.5  & 4    & 5    & 2     & 1    & 1      & 1       & 28   & 68   & 38    & 89  & 0.46 & 0.47 & 0.5  & 0.52 & 0.53 & 0.52 \\
+    $(5,15,\elseBr)$  & 151.48 & 27.08 & 32.7  & 31.92 & 156 & 20.5 & 28.5 & 23.5 & 6     & 3    & 3      & 2       & 294 & 99   & 156  & 130 & 0.87 & 0.85 & 0.86 & 0.42 & 0.48 &  0.55 \\
+    $(9,10,\thenBr)$  & 124.26 & 15.58 & 21.66 & 21.9  & 101 & 14   & 17   & 17   & 23   & 1    & 2      & 6       & 245 & 51   & 83    & 86  & 0.98 & 0.95 & 0.95 & 0.43 & 0.40 & 0.47 \\
+    $(9,14,\elseBr$   & 6.18   & 4.42  & 7.74  & 9.48  & 4 & 4 & 4 & 4 & 1 & 1 & 1 & 1 & 21 & 17 & 43 & 79 & 0.56 & 0.53 & 0.51 & 0.48 & 0.45 & 0.48 \\
+    \midrule
+    \textbf{isGameFinished}      & 290.26 & 135.06 & 75.68 & 77.48 & 219.5 & 30   & 39   & 43   & 142 & 2   &  3    & 5       & 573 & 668 & 676  & 513 &             &              &             &             &             &      \\
+    %% $(5,6,\inFor)$   & 0        & 0.88      & 0.94   & 0.94    & 1       & 1     & 1       & 1     & 0     & 0   & 0     & 0       & 2     & 3     & 3      & 3     & 0.53 & 0.5   & 0.5  & 0.48 & 0.47  & 0.5 \\
+    $(7,8,\thenBr)$     & 63.68   & 40.32   & 19.62 & 15.62 & 29.5 & 7.5   & 9.5     & 12.5 & 0     & 0   & 1     & 1       & 191 & 225 & 196  & 77   & 0.6  & 0.66   & 0.66 & 0.46 & 0.43 & 0.44  \\
+    %% $(7,15,\elseBr)$ & 0.98        & 0.82     & 0.84   & 0.9    & 1       & 1     & 1       & 1     & 0     & 0   & 0     & 0       & 3     & 3     & 2      & 3     & 0.57 & 0.55  & 0.54 & 0.48  & 0.46 & 0.48 \\
+    $(10,11,\thenBr)$   & 166.32*    & 36.6    & 22.5  & 26.44 & 167*   & 10   & 10.5   & 11    & 141 & 2   & 1     & 3       & 191 & 220 & 217  & 224 & 0.88 & 0.96  & 0.96 & 0.52 & 0.48 & 0.45 \\
+    $(10,14,\elseBr)$   & 59.28   & 56.44   & 31.78 & 33.58 & 21   & 10.5 & 17   & 17.5 & 1     & 0   & 1     & 1       & 186 & 217 & 258  & 206 & 0.55  & 0.57 & 0.55  & 0.48  &0.46 & 0.47 \\
+    \midrule
+    \textbf{newGame}             & 18.26 & 11.28 & 11.94  & 10.5   & 13.5   & 9   & 10    & 10   & 1      & 1    & 1      & 0       & 69  & 53    & 39    & 34 & & & & & & \\
+    %% $(4,5,\inFor)$   & 0.9    & 0.66   & 0.84     & 0.86      & 1       & 1     & 1       & 1     & 0     & 0    & 0      & 0       & 2    & 2      & 2      & 1   & 0.6  & 0.53 & 0.51 & 0.42  & 0.4 & 0.49 \\
+    $(6,7,\thenBr)$     & 16.58 & 9.78  & 10.24   & 8.84   & 11.5   & 7   & 8     & 8     & 1     & 1    & 1      & 0       & 67  & 47    & 34    & 31 & 0.64 & 0.6  & 0.65 & 0.44 & 0.5 & 0.56 \\
+    %% $(6,12,\elseBr)$ & 0.78   & 0.84   & 0.86     & 0.8    & 1       &  1     & 1       & 1     & 0     & 0    & 0      & 0       & 2    & 4      & 3      & 2   & 0.5   & 0.47 & 0.49 & 0.46 & 0.48 & 0.52 \\
+    \midrule
+    \textbf{revealAll}           & 69.2   & 55.26 & 70.34 & 64.04 & 50     & 44   & 58.5 & 52.5 &  8     & 16  & 16    & 16     & 261 & 153  & 226  & 202 & & & & & &\\
+    $(2,3,\inFor)$      & 27.78 & 26.7  & 39.34 & 32.58 & 20     & 24   & 30.5   & 27   & 3     & 7    & 7      & 11     & 89  & 64    & 148  & 100  & 0.45 & 0.37 & 0.39 & 0.39 & 0.43 & 0.55 \\
+    $(4,5,\inFor)$      & 41.42 & 28.56 & 33.02  & 31.46 & 30     & 20   & 28   & 25.5   & 5     & 9    & 9      & 5       & 172 & 89    & 78    & 102  & 0.62 & 0.53  & 0.55 & 0.39  & 0.37 & 0.53 \\
+    \midrule
+    \textbf{shuffleBoard}         & 410.56 & 321.28 & 371.58 & 358.84 & 401.5 & 299   & 338 & 321 & 342 & 250 & 268 & 263 & 568 & 689 & 716 & 674 & & & & & & \\
+    %% $(3,4,\inFor)$    & 1.6        & 1.36        & 1.52        & 1.42        & 2         & 1       & 2       & 1     & 1     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.61  & 0.54  & 0.58  & 0.42  & 0.47  & 0.55 \\
+    %% $(5,6,\inWhile)$  & 2.94    & 2.6      &  2.58     & 2.88     &  2         & 2       &  2       &  2     & 1     & 1     & 1     & 1     & 11    & 8     & 6     & 15    & 0.6  & 0.54 & 0.56 & 0.45  & 0.46  & 0.52 \\
+    %% $(10,11,\inFor)$  & 1.88       & 1.4         &  1.64        &  1.58        &  2         &  1       &  2       &  2     &  2     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.72  & 0.61  & 0.64  & 0.38  & 0.41  & 0.53 \\
+    $(13,14,\thenBr)$    & 13.6    & 13.88     &  17.7     &  15.78    & 9.5       &  8.5     &  8.5     &  9.5   & 1     & 1     & 1     & 1     & 44   & 103  & 126  & 78   & 0.58 & 0.52  & 0.53  & 0.46 & 0.46 & 0.51 \\
+    % $(13,16,\elseBr)$  & 1.52       & 1.4         & 1.68        & 1.5         &  1.5       &  1       &  2       & 1.5   & 1     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.55  & 0.42  & 0.51  & 0.36  & 0.45  & 0.59 \\
+    $(17,18,\thenBr)$    & 13.76   & 23.7    &  39.58   & 34.04   &  10      &  10      &  12.5  & 1     &  1     & 2     & 2     & 2     & 73   & 248 & 180  & 248 & 0.46 & 0.38 & 0.47 & 0.4  & 0.5   & 0.55 \\
+    %% $(17,20,\elseBr)$ & 2.06       & 1.84        & 1.72        & 1.8         &  2         & 2       &  2       &  2     & 1     & 1     & 1     & 1     &  4    & 2     & 2     & 2     & 0.59  & 0.64  & 0.61  & 0.56  & 0.52  & 0.46 \\
+    $(21,22,\inFor)$     & 373.2*    & 275.1*     & 305.16*    & 299.84*    & 372.5*   & 273.5* & 307*   & 302* & 334 & 242 & 260 & 255 & 427 & 322 & 396 & 325 & 1     & 0.99  & 1     & 0.15 & 0.16   & 0.58 \\
+    \midrule
+    \midrule
+    \textbf{toggleInfo}         & 6.12 & 11.9 & 18.3 & 15.4  & 5.5 & 7 & 7.5  & 6 & 0 & 0 & 0 & 0 & 22 & 118 & 138 & 106 & & & & & & \\
+    $(2,3,\thenBr)$    & 2.32 & 1.64  & 1.7   & 1.46     & 1.5 & 2 & 2   & 1 & 0 0 & 0 & 0 &  0 &  11 & 4     &  4     &  3     &  0.54  &  0.53 &  0.58 & 0.48  & 0.55 & 0.57 \\
+    %% $(2,5,\elseBr)$ & 0.86    & 0.84     & 0.86    & 0.8      & 1   & 1 & 1   & 1 & 0 & 0 & 0 & 0 & 2   &1     & 1     & 1     & 0.51  & 0.5   & 0.53  & 0.49  & 0.52  & 0.53 \\
+    $(6,7,\thenBr)$    & 2.1  & 8.7    & 14.92  & 12.34 & 2   & 3 & 3.5 & 3 & 0 & 0 & 0 & 0 & 8   & 112 & 132 & 101 & 0.37 & 0.29 & 0.36 & 0.42 & 0.48 & 0.55 \\
+    %% $(6,13,\elseBr)$& 0.84    & 0.72     & 0.82   & 0.8      & 1   & 1 & 1   & 1 & 0 & 0 & 0 & 0 & 1   & 1     & 1     & 1     &  0.56  &  0.51  & 0.52  & 0.45  & 0.46  & 0.51 \\
+    \midrule
+    \midrule
+    \textbf{isValidCard}       & 513.66 & 7.8 & 7.96 & 8.42 & 514   & 8 &  7 & 9.5 & 447 & 5 & 5 & 5 & 579 & 12 & 13 & 12  & & & & & & \\
+    %% $(3,4,\thenBr)$& 0.54     & 0.3     & 0.46    & 0.46     & 1       & 0  & 0  & 0    & 0     & 0  & 0  & 0  &  0     & 1   & 1   &  0 &  0.61 & 0.53 & 0.53 &  0.42 & 0.42 & 0.5 \\
+    $(3,6,\elseBr)$   & 102.98* & 1.52 & 1.4     & 1.56  &  102.5* & 2  &  1  & 2    &  87  &  1  &  1  &  1  &  116 &  2   &  3   &  3    &  1 &  1 &  1 & 0.49    & 0.5  & 0.43 \\
+    $(7,8,\inFor)$    & 102.38* & 1.44 & 1.6  & 1.58  & 103*   & 1  & 2  & 2    & 90  & 1  & 1  & 1  & 115 & 3   & 2   & 2    & 1 & 1 & 1 & 0.42 & 0.43 & 0.51 \\
+    $(10,11,\thenBr)$ & 101.44* & 1.56    & 1.48 & 1.7   & 102*   & 2  & 1  & 2    & 88  & 1  & 1  & 1  & 116 & 2   & 2   & 3    &  1 &  1 &  1 &  0.54 & 0.43 &  0.4 \\
+    $(10,13,\elseBr)$ & 104.66* & 1.38 & 1.54 & 1.62  & 106*   & 1  & 2  & 2    & 91  & 1  & 1  & 1  & 115 & 2   & 2   & 2    & 1 & 1 &  1 &  0.42 & 0.38 &  0.46 \\
+    $(14,15,\inFor)$  & 101.66* & 1.6  & 1.48 & 1.5   & 99.5*  & 2  & 1  & 1.5  & 91  & 1  & 1  & 1  & 117 & 2   & 3   & 2    & 1 & 1 &  1 &  0.56 &  0.55 & 0.48 \\
+    \midrule
+    %% \textbf{isValidMasterCard}  & 109.46 & 4.84 & 5.1  & 5.03 & 102.5 & 4 & 4.5 & 4 & 86 & 2 & 2 & 2 & 164 & 11 & 11 & 10 & & & & & & \\
+    %% $(2,3,\thenBr)$    & 108.98* & 4.5  & 4.64 & 4.6  & 102.5* & 4 & 4.5 & 4 & 86 & 2 & 2 & 2 & 162 & 10 & 10 & 9  & 1      & 1     & 1 & 0.47 & 0.49 & 0.51 \\
+    %% %% $(2,5,\elseBr)$ & 0.48     & 0.34     & 0.46   & 0.43     & 0       &  0  &  0    & 0  & 0    & 0 & 0 & 0 & 2     & 1   & 1   & 1   & 0.56 & 0.5 & 0.52 & 0.44 & 0.46 & 0.52 \\
+    \midrule
+    \textbf{isValidVISA}       & 97.54 & 3.06 & 3.04 & 3.04 & 95 & 3 & 3 & 2 &  89 & 2  & 1 & 1 & 140 & 6 & 7 & 7 & & & & & & \\
+    $(2,3,\thenBr)$   & 97.08* & 2.72 &  2.62 & 2.58 & 95* & 3 & 3 & 2 &  89 &  2 &  1 &  1 &  139 &  5 &  6 &  6 &  1 &  1 &  1 &  0.54 &  0.59 &  0.54 \\
+    %% $(2,5,\elseBr)$& 0.46    & 0.34    & 0.42    & 0.46    & 0    & 0 & 0 & 0 & 0    & 0 & 0 & 0 & 1     & 1  & 1  & 1  & 0.56 & 0.52 & 0.5 & 0.46 & 0.44 & 0.48 \\
+    \midrule
+    \midrule
+    \textbf{initShields}       & 5.8 & 3.76 & 3.9 & 3.7 & 5 & 4 & 4 & 3 & 3 & 3 & 3 & 3 & 10 & 5 & 5 & 5 & & & & & & \\
+    $(2,3,\inFor)$    & 5.8 & 3.76 & 3.9 & 3.7 & 5 & 4 & 4 & 3 & 3 & 3 & 3 & 3 & 10 & 5 & 5 & 5 & 0.83 & 0.8 & 0.84 & 0.45 & 0.53 & 0.58 \\
+    \midrule
+    \midrule
+    \textbf{brickJiggler}      & 9.74 & 4.68 & 4.98 & 4.28 &  8 & 4 &  4 & 3 & 2 & 3 & 2 & 2 & 28 & 20 & 12 & 12 &  & & & & &\\
+    $(2,3,\thenBr)$   & 8.46 & 3.54 & 3.66 &  3.2  &  7 &  3 & 3 & 2 & 2 & 2 &  1 & 1 & 25 & 18 & 10 & 10 & 0.83 & 0.81 & 0.85 & 0.48 & 0.56 & 0.57 \\
+    %% $(2,9,\elseBr)$& 1.28    & 1.14    & 1.32    & 1.08   & 1 & 1 & 1 & 1 & 0 & 1 & 1 & 1 & 3   & 2   & 2   & 2   & 0.51  & 0.45  & 0.53  & 0.41  & 0.53 & 0.62 \\
+    \midrule
+    \textbf{doPaddlePower}        & 17.64  & 134.54 & 36.4  & 29.58 & 15 & 140 & 14 & 16 &  1 &  3 &  0 &  1 &  51 &  160 &  157 &  144 & & & & & & \\
+    %% $(5,6,\thenBr)$   & 0.82      & 0.82        & 0.9       & 0.86      &  1     &  1     &  1   &  1   &  0 &  0 &  0 & 0   &  2   &  1     &  1     &  1     &  0.5   &  0.46  &  0.48 &  0.46  & 0.48 &  0.52 \\
+    %% $(5,8,\elseBr)$   & 0.9    & 1.04      & 0.82   & 0.74   & 1     &  1     &  1   &  1   &  0 &  0 &  0 & 0    &  3   &  4     &  2     &  3     &  0.47 &  0.52 &  0.56 &  0.54 &  0.59 &  0.55 \\
+    $(10,11,\thenBr)$    & 15.04 & 131.86 & 33.86 & 27.24  & 1 12 &  136* & 12 &  13 & 1 & 3 & 0 & 1 & 43 & 154 & 153 &  139 & 0.02 &  0.46 &  0.43 &  0.86 &  0.94 &  0.45 \\
+    %% $(10,13,\elseBr)$ & 0.88      & 0.82        & 0.82      &  0.74      &  1     &  1     &  1   &  1   &  0 &  0 &  0 & 0   &  3  &  1     &  1     &  1      &  0.251 &  0.51  &  0.55  & 0.5  &  0.54  &  0.54 \\
+
+    %% drawLevel         & 6.78 & 2.14 / 6.05 & 2.06 / 6.92 & 1.86 / 5.82 & 0 / 6 & 0 / 6 & 0 / 6 & 0 / 6 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 10 / 17 & 25 / 19 & 28 / 23 & 27 / 19 & & & & & \\
+    %% $(5,6,\thenBr)$   & 1.04 & 0.16 / 0.9  & 0.14 / 1.04 & 0.2 / 0.9   & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 2 / 2   & 3 / 2   & 5 / 4   & 5 / 3 & & & & & & \\
+    %% $(5,21,\elseBr)$  & 0.86    & 0 / 0.9     & 0 / 0.92    & 0 / 0.84    & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 2   & 0 / 2   & 0 / 1   & 0 / 1 & & & & & & \\
+    %% $(8,9,\inFor)$    & 1.04  & 0.16 / 0.89 & 0.34 / 1.1  & 0.3 / 1.06  & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 3 / 4   & 5 / 3   & 5 / 4   & 5 / 4 & & & & & & \\
+    %% $(10,11,\thenBr)$ & 1.52 & 1.26 / 1.48 & 0.98 / 1.62 & 0.8 / 1.1   & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 3 / 5   & 7 / 5   & 7 / 6   & 8 / 5 & & & & & & \\
+    %% $(10,13,\elseBr)$ & 1.2  & 0.22 / 0.86 & 0.3 / 1.14  & 0.2 / 0.98  & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 1 / 3   & 3 / 2   & 7 / 4   & 3 / 2 & & & & & & \\
+    %% $(14,15,\inFor)$  & 1.12 & 0.34 / 1.02 & 0.3 / 1.1   & 0.36 / 0.94 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 1 / 1   & 7 / 5   & 4 / 4   & 6 / 4 & & & & & & \\
+    \midrule
+    \textbf{initBricks}        & 2272.40  & 579.58 & 617    & 584.06 & 2379  & 474  & 517   & 414.5 & 90  & 60 & 64 & 59 & 4647 & 1612 & 1731 & 1653 & & & & & & \\
+    $(6,7,\thenBr)$   & 3.94     & 3.6    & 3.54   & 3.6    & 3     & 4    & 3     & 3     & 2   & 2  & 1  & 2  & 9    & 5    & 5    & 5    & 0.53 & 0.46 & 0.5  & 0.43 & 0.5  & 0.57 \\
+    $(6,10,\elseBr)$  & 50.56    & 6.16   & 6.32   & 7.68   & 23    & 6    & 6     & 6     & 3   & 2  & 2  & 3  & 370  & 10   & 14   & 23   & 0.87 & 0.83 & 0.83 & 0.34 & 0.4  & 0.56 \\
+    $(11,12,\thenBr)$ & 267.92   & 16.22  & 27.02  & 23.98  & 317*   & 11.5 & 16.5  & 15    & 5   & 6  & 6  & 5  & 366  & 48   & 67   & 78   & 0.93 & 0.91 & 0.91 & 0.41 & 0.41 & 0.47 \\
+    $(11,15,\elseBr)$ & 54.7     & 6.32   & 6.84   & 8.52   & 30    & 6    & 7     & 6     & 3   & 3  & 2  & 2  & 314  & 13   & 28   & 53   & 0.89 & 0.83 & 0.86 & 0.32 & 0.47 & 0.62 \\
+    $(16,17,\thenBr)$ & 272.82   & 23.36  & 38.68  & 28.08  & 324*   & 13.5 & 13    & 16    & 9   & 5  & 2  & 3  & 379  & 187  & 205  & 109  & 0.96 & 0.94 & 0.96 & 0.4  & 0.45 & 0.52 \\
+    $(16,20,\elseBr)$ & 95.9     & 8.16   & 13.3   & 11.06  & 40    & 6.5  & 6     & 7     & 3   & 3  & 2  & 3  & 367  & 50   & 70   & 83   & 0.89 & 0.8  & 0.86 & 0.36 & 0.46 & 0.6 \\
+    $(21,22,\thenBr)$ & 251.98   & 19.38  & 32.16  & 40.48  & 309.5* & 12.5 & 13.5  & 16.5  & 3   & 2  & 4  & 3  & 370  & 181  & 121  & 151  & 0.94 & 0.92 & 0.9  & 0.4  & 0.36 & 0.44 \\
+    $(21,25,\elseBr)$ & 93.62    & 7.08   & 12.72  & 13.12  & 41    & 6.5  & 7     & 7     & 5   & 3  & 3  & 3  & 371  & 20   & 99   & 81   & 0.94 & 0.84 & 0.87 & 0.32 & 0.42 & 0.59 \\
+    $(29,30,\thenBr)$ & 275.06   & 90.36  & 88.74  & 88.92  & 330*   & 57.5 & 69.5  & 70    & 5   & 5  & 6  & 5  & 413  & 208  & 204  & 201  & 0.82 & 0.88 & 0.88 & 0.46 & 0.5  & 0.54 \\
+    $(29,37,\elseBr)$ & 4.44     & 3.76   & 4      & 4.04   & 4     & 3    & 4     & 4     & 3   & 2  & 2  & 2  & 11   & 7    & 6    & 6    & 0.63 & 0.33 & 0.53 & 0.24 & 0.43 & 0.72 \\
+    $(38,39,\thenBr)$ & 266.76   & 93.96  & 95.88  & 86.26  & 328   & 66.5 & 82    & 44    & 30  & 5  & 11 & 5  & 410  & 208  & 217  & 214  & 0.87 & 0.82 & 0.88 & 0.41 & 0.54 & 0.62 \\
+    $(38,46,\elseBr)$ & 4.32     & 3.66   & 4.3    & 3.92   & 4     & 3.5  & 4     & 4     & 2   & 2  & 2  & 2  & 8    & 6    & 8    & 6    & 0.64 & 0.46 & 0.58 & 0.33 & 0.44 & 0.61 \\
+    $(47,48,\thenBr)$ & 264.56   & 108.44 & 115.74 & 108.1  & 335.5 & 141*  & 128   & 131   & 5   & 6  & 6  & 7  & 408  & 212  & 227  & 206  & 0.8  & 0.79 & 0.8  & 0.44 & 0.54 & 0.59 \\
+    $(47,55,\elseBr)$ & 4.52     & 3.74   & 4      & 3.92   & 4     & 3    & 4     & 4     & 2   & 2  & 2  & 2  & 9    & 6    & 6    & 6    & 0.66 & 0.44 & 0.61 & 0.31 & 0.46 & 0.65 \\
+    $(56,57,\thenBr)$ & 208.04   & 86.78  & 98.74  & 89.54  & 197.5 & 42.5 & 123.5 & 47    & 6   & 5  & 6  & 5  & 411  & 222  & 213  & 209  & 0.76 & 0.72 & 0.75 & 0.43 & 0.5  & 0.57 \\
+    $(56,64,\elseBr)$ & 4.48     & 3.82   & 4.38   & 3.94   & 4     & 3    & 4     & 4     & 2   & 2  & 2  & 2  & 7    & 5    & 15   & 6    & 0.64 & 0.51 & 0.61 & 0.39 & 0.47 & 0.59 \\
+    $(69,70,\thenBr)$ & 4.26     & 2.64   & 4.72   & 4.26   & 4     & 4    & 4     & 4     & 2   & 2  & 2  & 2  & 8    & 7    & 9    & 8    & 0.48 & 0.31 & 0.51 & 0.32 & 0.53 & 0.69 \\
+    $(69,71,\elseBr)$ & 144.52   & 92.14  & 55.92  & 54.64  & 80.5  & 83.5 & 22    & 26    & 3   & 3  & 3  & 3  & 416  & 217  & 217  & 208  & 0.57 & 0.71 & 0.68 & 0.65 & 0.61 & 0.46 \\
+    \midrule
+    \midrule
+    \textbf{do\_draw}             & 695.56 & 1064.82 & 346.64 & 347.42 & 625   & 1295  & 315  & 333.5  & 49 & 49 & 47 & 46 & 1772 & 1855 & 1453 & 1077 & & & & & & \\
+    %% $(2,3,\thenBr)$   & 2.42   & 2.48    & 2.44   & 2.38   & 2     & 2     & 2    & 2      & 2  & 2  & 2  & 2  & 3    & 4    & 3    & 3    & & & & & & \\
+    %% $(2,5,\elseBr)$   & 0.98   & 0.98    & 0.98   & 0.94   & 1     & 1     & 1    & 1      & 0  & 0  & 0  & 0  & 1    & 2    & 2    & 1    & & & & & & \\
+    $(6,7,\thenBr)$      & 23.62  & 23.74   & 21.66  & 19.82  & 18.5  & 25    & 23   & 20     & 2  & 2  & 2  & 2  & 103  & 46   & 50   & 15   & 0.41 & 0.45 & 0.5 & 0.55 & 0.62 & 0.57 \\
+    %% $(6,12,\elseBr)$  & 1.02   & 1       & 0.94   & 0.94   & 1     & 1     & 1    & 1      & 0  & 0  & 0  & 0  & 2    & 2    & 1    & 2    & & & & & & \\
+    $(8,9,\thenBr)$      & 32.2   & 19.58   & 20.12  & 19.3   & 23    & 17    & 20   & 20.5   & 2  & 2  & 2  & 0  & 124  & 54   & 45   & 47   & 0.63  & 0.6  & 0.62 & 0.47 & 0.49 & 0.5 \\
+    $(8,11,\elseBr)$     & 318.68 & 62.16   & 77.08  & 61.76  & 343   & 51    & 70.5 & 57     & 16 & 15 & 20 & 2  & 488  & 214  & 165  & 146  & 0.91  & 0.89 & 0.91 & 0.36 & 0.46 & 0.62\\
+    %% $(20,21,\thenBr)$ & 1.2    & 1.44    & 1.22   & 1.22   & 1     & 1     & 1    & 1      & 1  & 1  & 1  & 18 & 2    & 3    & 2    & 2    & & & & & &\\
+    %% $(20,23,\elseBr)$ & 2.52   & 2.58    & 2.46   & 2.46   & 3     & 2.5   & 2    & 2      & 2  & 2  & 2  & 1  & 3    & 4    & 3    & 3    & & & & & &\\
+    %% $(24,25,\thenBr)$ & 1.28   & 1.3     & 1.2    & 1.22   & 1     & 1     & 1    & 1      & 1  & 1  & 0  & 2  & 2    & 3    & 2    & 2    & & & & & &\\
+    %% $(24,27,\elseBr)$ & 2.52   & 2.94    & 3.02   & 2.66   & 2.5   & 3     & 3    & 2.5    & 2  & 2  & 2  & 1  & 4    & 12   & 17   & 11   \\
+    %% $(28,29,\thenBr)$ & 1.84   & 1.84    & 1.92   & 1.84   & 2     & 2     & 2    & 2      & 1  & 1  & 1  & 2  & 2    & 3    & 3    & 2    & & & & & &\\
+    %% $(28,31,\elseBr)$ & 1.94   & 1.94    & 1.9    & 1.94   & 2     & 2     & 2    & 2      & 1  & 1  & 1  & 1  & 3    & 3    & 3    & 3    & & & & & &\\
+    %% $(32,33,\thenBr)$ & 1.92   & 2.08    & 1.92   & 1.92   & 2     & 2     & 2    & 2      & 1  & 1  & 1  & 1  & 2    & 3    & 3    & 2    & & & & & &\\
+    %% $(32,35,\elseBr)$ & 1.9    & 2.04    & 1.9    & 1.86   & 2     & 2     & 2    & 2      & 1  & 1  & 1  & 1  & 3    & 3    & 3    & 2    & & & & & &\\
+    %% $(36,37,\thenBr)$ & 1.02   & 1.22    & 1      & 1.08   & 1     & 1     & 1    & 1      & 0  & 0  & 0  & 0  & 2    & 3    & 2    & 2    & & & & & &\\
+    %% $(36,39,\elseBr)$ & 3.4    & 4.8     & 4.14   & 2.98   & 3     & 3     & 3    & 3      & 2  & 2  & 2  & 2  & 12   & 24   & 24   & 8    \\
+    %% $(40,41,\thenBr)$ & 1.18   & 1.28    & 1.24   & 1.04   & 1     & 1     & 1    & 1      & 0  & 0  & 1  & 0  & 2    & 2    & 2    & 2    & & & & & &\\
+    %% $(40,43,\elseBr)$ & 2.86   & 3.04    & 4.12   & 3.76   & 3     & 3     & 3    & 3      & 2  & 2  & 2  & 2  & 5    & 9    & 20   & 40   \\
+    $(44,45,\thenBr)$    & 193.84 & 515.7   & 102.5  & 125.62 & 143.5 & 681*   & 83   & 111    & 10 & 12 & 3  & 6  & 518  & 718  & 657  & 645  & 0.16 & 0.65 & 0.58 & 0.9 & 0.89 & 0.24 \\
+    %% $(44,47,\elseBr)$ & 1.08   & 1.1     & 1.02   & 1.02   & 1     & 1     & 1    & 1      & 0  & 0  & 1  & 0  & 2    & 2    & 2    & 2    & & & & & & \\
+    $(48,49,\thenBr)$    & 97.12  & 410.58  & 92.86  & 90.58  & 68    & 491.5 & 90   & 96.5   & 3  & 2  & 3  & 3  & 487  & 739  & 442  & 135  & 0.24 & 0.43 & 0.4 & 0.74 & 0.74 & 0.41 \\
+    %% $(48,51,\elseBr)$ & 1.02   & 1       & 1      & 1.08   & 1     & 1     & 1    & 1      & 0  & 0  & 0  & 0  & 2    & 2    & 2    & 2    & & & & & & \\
+    \midrule
+    \midrule
+    \textbf{prob\_gamma}          & 701.78  & 84.88 & 82.56 & 81.98 & 710  & 84 & 79.5  & 80.5 & 484 & 55  & 52 & 52  & 799 & 119 & 121 & 122 & & & & & & \\
+    $(4,5,\thenBr)$      & 69.06   & 0.84  & 0.84  & 0.9   & 70.5* & 1  & 1     & 1    & 11  & 0   & 0  & 0   & 80  & 2   & 1   & 2   & 1 & 1 & 1 & 0.5 & 0.47 & 0.47 \\
+    %% $(4,25,\elseBr)$  & 0.3     & 0.4   & 0.4   & 0.36  & 0    & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
+    $(6,7,\thenBr)$      & 68.26   & 0.9   & 0.9   & 0.88  & 71*   & 1  & 1     & 1    & 8   & 0   & 0  & 0   & 77  & 2   & 2   & 2   & 1 &  1 & 1 & 0.5 & 0.51 & 0.51 \\
+    $(6,9,\elseBr)$      & 69.2*    & 1     & 0.92  & 0.98  & 69.5* & 1  & 1     & 1    & 57  & 0   & 0  & 0   & 76  & 4   & 2   & 2   & 1 & 1 & 1 & 0.52 & 0.49 & 0.47 \\
+    $(10,11,\thenBr)$    & 70.06*   & 41.58 & 39.66 & 39.44 & 72*   & 42 & 39.5  & 40   & 56  & 31  & 27 & 29  & 77  & 51  & 52  & 52  & 1 & 1 & 1 & 0.6 & 0.62  & 0.5 \\
+    $(10,13,\elseBr)$    & 70.4*    & 1.04  & 0.82  & 0.88  & 71*   & 1  & 1     & 1    & 59  & 0   & 0  & 0   & 79  & 2   & 2   & 2   & 1 & 1 & 1 & 0.6 & 0.57 & 0.47 \\
+    $(16,17,\inWhile)$   & 69.74*   & 1.1   & 1.06  & 1.08  & 70*   & 1  & 1     & 1    & 57  & 0   & 0  & 0   & 81  & 2   & 3   & 4   & 1 & 1 & 1 & 0.52 & 0.53 & 0.5 \\
+    $(20,21,\thenBr)$    & 69.8*    & 2.58  & 2.6   & 2.92  & 70*   & 2  & 2     & 2.5  & 58  & 1   & 0  & 0   & 78  & 6   & 9   & 11  & 1 & 1 & 1 & 0.56 & 0.48 & 0.43 \\
+    $(20,23,\elseBr)$    & 70.58*   & 0.9   & 0.94  & 0.88  & 71.5* & 1  & 1     & 1    & 57  & 0   & 0  & 0   & 79  & 3   & 2   & 2   & 1 & 1 & 1 & 0.46 & 0.49 & 0.5 \\
+    %% $(26,27,\thenBr)$ & 0.44    & 0.54  & 0.48  & 0.36  & 0    & 1  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 2   & 1   & & & & & & \\
+    %% $(26,29,\elseBr)$ & 0.34    & 0.38  & 0.38  & 0.4   & 0    & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
+    $(30,31,\thenBr)$    & 70.94*   & 22.56 & 22.3  & 21.88 & 72*   & 23 & 22    & 22   & 57  & 17  & 18 & 16  & 81  & 28  & 27  & 27  & 1 & 1 & 1 & 0.54 & 0.58 & 0.56 \\
+    %% $(30,33,\elseBr)$ & 0.5     & 0.36  & 0.32  & 0.46  & 0.5  & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
+    $(34,35,\thenBr)$    & 71.3*    & 9.9   & 10.18 & 9.8   & 72*   & 10 & 10    & 10   & 64  & 6   & 7  & 7   & 85  & 13  & 14  & 12  & 1 & 1 & 1 & 0.46 & 0.51 & 0.55 \\
+    %% $(34,41,\elseBr)$ & 0.48    & 0.46  & 0.34  & 0.42  & 0    & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
+    %% $(44,45,\inFor)$  & 0.38    & 0.34  & 0.42  & 0.34  & 0    & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
     \bottomrule
     \end{tabular}
-}
+%}
 \end{table*}
+
+% \input{summary_branch_coverage}
+
+\begin{figure}[t]
+\centering
+\begin{tikzpicture}[scale=0.7]
+\begin{axis}[
+    xlabel={Time budget per branch (seconds)},
+    ylabel={Number of covered branches},
+    xmin=0, xmax=150,
+    ymin=0, ymax=59,
+    xtick={0,5,10,30,60,90,120,150,180},
+    ytick={0,10,20,30,40,50},
+    legend pos=south east,
+    ymajorgrids=true,
+    grid style=dashed,
+]
+
+  \addplot[
+    color=blue,
+    mark=square,
+  ] coordinates {
+    (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
+  }; 
+  \addplot[
+    color=red,
+    mark=square,
+  ]  coordinates {
+    (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
+  };
+  \addplot[
+    color=green,
+    mark=square,
+  ]   coordinates {
+    (5,26) (10,35) (30,49) (60,51) (90,56) (120,56) (150,58)
+  };
+  \addplot[
+    color=yellow,
+    mark=square,
+  ]   coordinates {
+    (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,59)
+  };
+    \legend{R,G,G5,G10}
+
+\end{axis}
+\end{tikzpicture}
+\caption{Progress of the branch coverage given fix time budget per branch}
+\end{figure}
 
@@
 
-Salable dynamic analysis framework for JS based on shadow executions~\cite{create_citation}.
+Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
 

### 2017-12-14 python/analysis.py

@@ -18,7 +18,27 @@ def get_summary_report(csvs):
     result['max'] = merged_dataframes.max(axis=1)
     result['min'] = merged_dataframes.min(axis=1)
     result['median'] = merged_dataframes.median(axis=1)
-    return result
+    ## print merged_dataframes
+    return (merged_dataframes, result)
+
+
+def a12slow(lst1, lst2):
+    more = same = 0.0
+    for x in sorted(lst1):
+        for y in sorted(lst2):
+            if x == y:
+                same += 1
+            elif x > y:
+                more += 1
+    return (more + 0.5*same) / (len(lst1)*len(lst2))
+
+def mk_a12_df(df1, df2):
+    a12 = []
+    for index, row in df1.iterrows():
+        a12.append(a12slow(df1.iloc[index], df2.iloc[index]))
+    a12_df = pd.DataFrame(a12, columns=['a12'])
+    print a12_df
+    return a12_df
 
 
 def generateExcelReport(cs_name,
@@ -27,16 +47,25 @@ def generateExcelReport(cs_name,
                         genetic_converge5_csvs,
                         genetic_converge10_csvs,
                         genetic_converge20_csvs):
-    random_df = get_summary_report(random_csvs)
-    genetic_df = get_summary_report(genetic_csvs)
-    genetic_converge5_df = get_summary_report(genetic_converge5_csvs)
-    genetic_converge10_df = get_summary_report(genetic_converge10_csvs)
-    genetic_converge20_df = get_summary_report(genetic_converge20_csvs)
+    (mrandom_df, random_df) = get_summary_report(random_csvs)
+    (mgenetic_df, genetic_df) = get_summary_report(genetic_csvs)
+    (mgenetic_converge5_df, genetic_converge5_df) = get_summary_report(genetic_converge5_csvs)
+    (mgenetic_converge10_df, genetic_converge10_df) = get_summary_report(genetic_converge10_csvs)
+    (mgenetic_converge20_df, genetic_converge20_df) = get_summary_report(genetic_converge20_csvs)
+
+    rg_df = mk_a12_df(mrandom_df, mgenetic_df)
+    rg5_df = mk_a12_df(mrandom_df, mgenetic_converge5_df)
+    rg10_df = mk_a12_df(mrandom_df, mgenetic_converge10_df)
+    gg5_df = mk_a12_df(mgenetic_df, mgenetic_converge5_df)
[…]

### 2017-12-23 doc/icse2018/icse2018.tex
Explained research RQ2.
* doc/icse2018/icse2018.tex:

@@
 \usepackage{syntax}
+\usepackage{multirow}
 \usepackage{booktabs} % For formal tables
 \usepackage{tikz}
-\usetikzlibrary{arrows,shadows,positioning}
+\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
 \usepackage{pgf-umlsd}
@@
 \usepackage{longtable}
+\usepackage{subcaption}
 \usepackage{pgfplots}
+\pgfplotsset{compat=newest}
 \usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
@@
 \newcommand{\inFor}{\text{inFor}}
-\newcommand{\inWhile}{\text{inWhile}}
+\newcommand{\inWhile}{\text{while}}
+\newcommand{\un}[1]{\underline{#1}}
 
@@
     \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
-    \midrule
+    \hline
     Random & Bool & choose at random \{\texttt{true}, \texttt{false}\} \\
@@
     Random & Array & make a random array of a respective type upto length five\\
-    \midrule
+    \hline
     Crossover & Bool   & pick at random one out of two given boolean \\
@@
     Crossover & Array & similar crossover operator as for strings\\
-    \midrule
+    \hline
     Mutation & Bool & Flip the boolean constant\\
@@
 
-In order to evaluate practical feasibility of the test framework adoption, we conducted an empirical validation on a set of case studies.
-Table~\ref{tbl.gen.config} gives summary of configuration parameters for both random and genetic instances of our framework.
-As a baseline we implemented random test generation strategy.
-It is similar to the genetic one except that it won't performing crossover and mutation.
-Hence, it also benefits from initial static analysis and follow up dynamic constant propagation.
-In addition, we experimented with two different sizes (5 and 10) for genetic restart in case of archive convergence.
+In order to evaluate practical feasibility of the test framework adoption, we conducted an empirical validation on a set of case studies described in Section~\ref{sub.sec.case.studies}.
+All the experiments were performed in a batch mode on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
+We have created three different instances of our JS testing framework each is based a slight variation of the underlying genetic search algorithm.
+The first version is \emph{Random} ($R$), i.e.
+instead of applying crossover and mutation we regenerate new population from scratch.
+It worth to notice, that random version also benefits from both preliminary static analysis phase and dynamic constant propagation during fitness evaluation step.
+The second version is \emph{Genetic} ($G$) and it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
+The last version ($G10$) is based on the genetic algorithm~\ref{alg.gen} where search is restarted after the archive is converged within a given history window, which is equal to 10 in our case.
+Initially, we experimented with two different window sizes 5 and 10.
+On one hand, a smaller window size forces the GA to converge fast and early discover a potential flat space.
+On the other hand, it sometimes causes a premature convergence by not letting the right genetic combination to be triggered.
+We experimentally concluded that the window size 10 works best for our examples and present the rest of the analysis based on that result.
+Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three proposed test generation strategies.
+The choice of initial values is similar to other genetic testing frameworks, e.g.
+\emph{EvoSuite}~\cite{evosuite}.
 
@@
   \label{tbl.gen.config}
-    \footnotesize
-  \begin{tabular}{l|r|r}
+    \scriptsize
+  \begin{tabular}{l|r|r|r}
     \toprule
-    \textbf{Parameter Name} & \textbf{Random} & \textbf{Genetic} \\
-    \midrule
-    Population size                   & 50  & 50 \\
-    Archive size                      & 1   & 25 \\
-    Maximum number of generations     & 200 & 200 \\
-    Crossover rate                    & 0   & 0.5 \\
-    Mutation rate                     & 0   & 0.5 \\
-    History window size               & 200 & 5/10/200 \\
+    \textbf{Parameter Name} & \textbf{R} & \textbf{G} & \textbf{G10} \\
+    \hline
+    Population size                   & 50  & 50  & 50  \\
+    Archive size                      & 1   & 25  & 25  \\
+    Maximum number of generations     & 200 & 200 & 200 \\
+    Crossover rate                    & 0   & 0.5 & 0.5 \\
+    Mutation rate                     & 0   & 0.5 & 0.5 \\
+    History window size               & 200 & -   & 10  \\
     \bottomrule
@@
 
-Being one of the most popular programming languages of modern time, there are ample open source JS projects on the Web.
+Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
 Being written with the help of countless number of specialized JS libraries, JS applications greatly vary in size, complexity and coding style.
@@
 
-Table~\ref{tbl.case.studies} presents common quantitative characteristics of the selected functions such as the number of branches (\textbf{\#BR}), lines of code (\textbf{\#LOC}) and cyclomatic complexity (\textbf{CC}).
+Table~\ref{tbl.case.studies} presents some common quantitative characteristics for the selected case-studies.
+For each function of a case-study we reported the following metrics\footnote{\url{http://jsmeter.info/} is the measurement tool}: lines of code (\textbf{\#LOC}), number of branches (\textbf{\#BR}), depth (\textbf{\#D}), cyclomatic complexity (\textbf{CC}), halstead volume (\textbf{HV}) and maintainability index (\textbf{MI}).
 The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
 
-Consider examples from: \cite{artemis2011}, \cite{dom2011}...
-
-To report on cyclomatic complexity we use \emph{jshint}\footnote{http://jshint.com/} (we can also use this tool\footnote{http://jsmeter.info/})
-
-\begin{table*}
-  \caption{Summary of the case studies}
+\begin{table*}[t]
+  \caption{Summary of the Case-Studies}
   \label{tbl.case.studies}
@@
     \scriptsize
-  \begin{tabular}{l|l|l|r|r|r|r|c|c|c|c}
+  \begin{tabular}{l|c|l|l|r|r|r|r|r|r|c|c|c|c}
     \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type} & \textbf{\#LOC} & \textbf{\#BR} & \textbf{\#D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \midrule
-    sudoku     & helpMe & (dom,int,int)                                   & 15 & 2  & 3 & 3  & + & + & + & - \\
-    sudoku     & isGameFinished & (dom)                                   & 17 & 4  & 3 & 5  & + & + & + & + \\
-    sudoku     & newGame & (dom)                                          & 12 & 1  & 2 & 2  & + & + & + & + \\
-    sudoku     & revealAll & (dom)                                        & 14 & 0  & 2 & 1  & + & + & + & - \\
-    sudoku     & showCell* & (dom)                                         &    &    &   &    &   &   &   & \\
-    sudoku     & shuffleBoard & (dom)                                     & 26 & 2  & 3 & 3  & + & - & + & - \\
-    sudoku     & switchLevel* & (dom,bool)                                 &    &    &   &    &   &   &   & \\
-    \midrule
-    phormer    & toggleInfo & (dom,string)                                & 15 & 3  & 1 & 4  & + & + & - & - \\
-    phormer    & update* & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &    &   &    &   &   &   & \\
-    phormer    & updateIndic* & (dom,bool)                                 &    &    &   &    &   &   &   & \\
-    \midrule
-    hotel RS    & RequiredField* & (dom,[string])                           &    &    &   &    &   &   &   & \\
-    hotel RS   & isValidCard & ([int])                                    & 20 & 2  & 2 & 5  & - & - & - & - \\
-    hotel RS   & isValidMasterCard & ([int])                              & 6  & 4  & 1 & 7  & - & - & - & - \\
-    hotel RS    & isValidVISA & ([int])                                    &    &    &   &    &   &   &   & \\
-    hotel RS    & validateNumber* & (dom,string)                            &    &    &   &    &   &   &   & \\
-    \midrule
-    apophis    & doRain* & (dom,string,int,int,int,int,int,int)            &    &    &   &    &   &   &   & \\
-    apophis    & drawShields* & (dom,[int])                                &    &    &   &    &   &   &   & \\
-    apophis    & fireMeteor* & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) &    &    &   &    &   &   &   & \\
-    apophis    & getReady* & (dom,int,int,int,int,int,int)                 &    &    &   &    &   &   &   & \\
-    apophis    & initShields & (dom,[int],int,int)                        & 8  & 0  & 1 & 1  & + & + & - & -\\
-    \midrule
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int)                         & 63 & 12 & 4 & 13 & + & + & - & - \\
-    bingbong   & doPaddlePower & (dom,int,int)                            &    &    &   &    &   &   &   & \\
-    bingbong   & drawLevel* & (dom,int,int,int,int)                        &    &    &   &    &   &   &   & \\
-    bingbong   & goPing* & (dom,int,int,int)                               &    &    &   &    &   &   &   & \\
-    \midrule
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 39 & 12 & 2 & 14 & - & - & - & - \\
-    \midrule
-    cs-in-js   & luhn-algorithm* & (string,bool)                           &    &    &   &    &   &   &   & \\
-    cs-in-js   & quicksort-partition* & ([int],int,int)                    &    &    &   &    &   &   &   & \\ 
-    \midrule
-    mathjs     & prob\_gamma & (float)                                    & 56 & 8  & 2 & 16 & - & - & - & - \\
+    \textbf{case-study} & \textbf{?} & \textbf{function} & \textbf{type signature} & \textbf{\#LOC} & \textbf{\#BR} & \textbf{\#D} & \textbf{CC} & \textbf{HV} & \textbf{MI} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
+    \hline
+    sudoku     & + & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & 344 & 107.58 & + & + & + & - \\
+    sudoku     & + & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & 370 & 112.55 & + & + & + & + \\
+    sudoku     & + & newGame & (dom)           & 9  & 1 & 2 & 2 & 326 & 115.15 & + & + & + & + \\
+    sudoku     & + & revealAll & (dom)         & 8  & 0 & 2 & 1 & 312 & 117.44 & + & + & + & - \\
+    sudoku     & - & showCell & (dom)         & 8  & 0 & 0 & 1 & 232 & 118.46 & + & + & + & - \\
+    sudoku     & + & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & 555 & 97.9   & + & - & + & - \\
+    sudoku     & - & switchLevel & (dom,bool) & 10 & 1 & 2 & 2 & 257 & 114.26 & + & - & + & - \\
+    \hline
+    phormer    & + & toggleInfo & (dom,string)                                                      & 16 & 3 & 1 & 4 & 570  & 103.46 & + & + & - & - \\
+    phormer    & - & update & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) & 35 & 5 & 3 & 6 & 1190 & 87.804 & + & + & - & - \\
+    phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & 361  & 105    & + & + & - & - \\
+    \hline
+    hotel RS   & - & RequiredField & (dom,[string]) & 11 & 2 & 2 & 5 & 247  & 112.16 & + & + & - & - \\
+    hotel RS   & + & isValidCard & ([int])           & 17 & 2 & 2 & 5 & 351  & 103.91 & - & - & - & - \\
+    hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & 130  & 126.67 & - & - & - & - \\
+    hotel RS   & + & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & 104  & 124.71 & - & - & - & - \\
+    hotel RS   & - & validateNumber & (dom,string)  & 7  & 1 & 1 & 4 & 98.1 & 122.87 & + & + & - & - \\
+    \hline
+    apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & 242 & 114.1  & + & + & - & -\\
+    apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & 212 & 123.19 & + & + & - & - \\
+    apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & 539 & 104.70 & - & - & - & - \\
+    apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & 410 & 104.82 & + & + & - & - \\
+    apophis    & + & initShields & (dom,[int],int,int)                                               & 6  & 0 & 1 & 1 & 310 & 122.12 & + & + & - & -\\
+    \hline
+    bingbong   & + & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & 305  & 119.45 & + & + & - & - \\
+    bingbong   & + & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & 353  & 106.38 & + & + & - & - \\
+    bingbong   & + & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & 2380 & 72.594 & + & + & - & - \\
+    bingbong   & - & drawLevel & (dom,int,int,int,int)                       & 22 & 2  & 3 & 3  & 703  & 97.816 & + & + & - & - \\
+    bingbong   & - & goPing & (dom,int,int,int)                              & 12 & 2  & 2 & 3  & 268  & 110.93 & + & + & - & - \\
+    \hline
+    burncanvas & + & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & 583 & 86.214 & - & - & - & - \\
+    \hline
+    cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & 308 & 101.49 & -  & -  & - & - \\
+    cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & 309 & 101.38 & -  & -  & - & - \\ 
+    \hline
+    mathjs     & + & prob\_gamma & (float)                                    & 57 & 8  & 2 & 16 & 1370 & 77.121 & - & - & - & - \\
     \bottomrule
@@
 \begin{description}
-\item[\textbf{Q1}] What is the performance of our test generation framework?
-\item[\textbf{Q2}] How does genetic version perform against the random one?
-\item[\textbf{Q3}] How does the restart of genetic algorithm after the archive convergence enhance the performance? 
+\item[\textbf{RQ1:}] What is the performance of our test generation framework?
+Is there any difference in performance on examples with DOM and without?
+Which algorithm works best random, genetic or genetic with restart?
+\item[\textbf{RQ2:}] What is the cost of one iteration of each algorithm?
+\item[\textbf{RQ3:}] How does the branch coverage progress over time given a fixed budget per branch? 
 \end{description}
 
-% \input{summary_statistics}
-
-\setlength\tabcolsep{2pt}
-\begin{table*}
-  \caption{Statistics for genetic and random algorithms}
+\subsection{Results}
+\label{sub.sec.eval.results}
+
+\setlength\tabcolsep{0.8pt}
+\begin{table}[!t]
+  \caption{Performance statistics of branch coverage (in seconds) for four variations of the JS test generation framework}
   \label{tbl.stats}
     \scriptsize
-  %\resizebox{\textwidth}{!}{
-
-    \begin{tabular}{l|rrrr|rrrr|rrrr|rrrr|rrrrrr}
+    \begin{tabular}{lc|ccc|ccc|ccc|ccc|ccc}
       \toprule
-      \textbf{NAME}   & $\mathbf{\bar{x}_R}$     & $\mathbf{\bar{x}_G}$   & $\mathbf{\bar{x}_{G5}}$ & $\mathbf{\bar{x}_{G10}}$ & $\mathbf{m_R}$       & $\mathbf{m_G}$     & $\mathbf{m_{G5}}$     & $\mathbf{m_{G10}}$   & $\mathbf{mn_R}$  & $\mathbf{mn_G}$ & $\mathbf{mn_{G5}}$ & $\mathbf{mn_{G10}}$ & $\mathbf{mx_R}$  & $\mathbf{mx_G}$ & $\mathbf{mx_{G5}}$ & $\mathbf{mx_{G10}}$ & \textbf{R-G} & \textbf{R-G5} & \textbf{R-G10} & \textbf{G-G5} & \textbf{G-G10} & \textbf{G5-G10}\\
+      \multirow{2}{*}{\textbf{NAME}} & \multirow{2}{*}{\textbf{\#D}}         &  \multicolumn{3}{c|}{$m_r$} & \multicolumn{3}{c|}{$m_g$} & \multicolumn{3}{c|}{$m_{g10}$} & \multirow{2}{*}{$\frac{t_r}{t_g}$} &  \multirow{2}{*}{$\frac{t_r}{t_{g10}}$} & \multirow{2}{*}{$\frac{t_g}{t_{g10}}$}   & \multirow{2}{*}{$a_{rg}$} &  \multirow{2}{*}{$a_{rg10}$} & \multirow{2}{*}{$a_{gg10}$} \\
+      \cline{3-11}
+            &                & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
       \toprule
-      \textbf{helpMe} & 293    & 63.18 & 78.34 & 80.68 & 270 & 47   & 59.5 &  55.5 & 33   & 7    & 8      & 12     & 609 & 258 & 368  & 468 & & & & & & \\
-    $(3,4,\inFor)$    & 5.34   & 6.24  & 8.48  & 9.32  & 4   &  3    & 6    &  6    & 1     & 1    & 1      & 2       & 21   &  23   &  48    & 84  & 0.57 & 0.41 & 0.39 & 0.38 &  0.37 & 0.47 \\
-    $(5,6,\thenBr)$   & 5.74   & 9.86  &  7.76  & 8.06  & 5   & 5.5  & 4    & 5    & 2     & 1    & 1      & 1       & 28   & 68   & 38    & 89  & 0.46 & 0.47 & 0.5  & 0.52 & 0.53 & 0.52 \\
-    $(5,15,\elseBr)$  & 151.48 & 27.08 & 32.7  & 31.92 & 156 & 20.5 & 28.5 & 23.5 & 6     & 3    & 3      & 2       & 294 & 99   & 156  & 130 & 0.87 & 0.85 & 0.86 & 0.42 & 0.48 &  0.55 \\
-    $(9,10,\thenBr)$  & 124.26 & 15.58 & 21.66 & 21.9  & 101 & 14   & 17   & 17   & 23   & 1    & 2      & 6       & 245 & 51   & 83    & 86  & 0.98 & 0.95 & 0.95 & 0.43 & 0.40 & 0.47 \\
-    $(9,14,\elseBr$   & 6.18   & 4.42  & 7.74  & 9.48  & 4 & 4 & 4 & 4 & 1 & 1 & 1 & 1 & 21 & 17 & 43 & 79 & 0.56 & 0.53 & 0.51 & 0.48 & 0.45 & 0.48 \\
-    \midrule
-    \textbf{isGameFinished}      & 290.26 & 135.06 & 75.68 & 77.48 & 219.5 & 30   & 39   & 43   & 142 & 2   &  3    & 5       & 573 & 668 & 676  & 513 &             &              &             &             &             &      \\
-    %% $(5,6,\inFor)$   & 0        & 0.88      & 0.94   & 0.94    & 1       & 1     & 1       & 1     & 0     & 0   & 0     & 0       & 2     & 3     & 3      & 3     & 0.53 & 0.5   & 0.5  & 0.48 & 0.47  & 0.5 \\
-    $(7,8,\thenBr)$     & 63.68   & 40.32   & 19.62 & 15.62 & 29.5 & 7.5   & 9.5     & 12.5 & 0     & 0   & 1     & 1       & 191 & 225 & 196  & 77   & 0.6  & 0.66   & 0.66 & 0.46 & 0.43 & 0.44  \\
-    %% $(7,15,\elseBr)$ & 0.98        & 0.82     & 0.84   & 0.9    & 1       & 1     & 1       & 1     & 0     & 0   & 0     & 0       & 3     & 3     & 2      & 3     & 0.57 & 0.55  & 0.54 & 0.48  & 0.46 & 0.48 \\
-    $(10,11,\thenBr)$   & 166.32*    & 36.6    & 22.5  & 26.44 & 167*   & 10   & 10.5   & 11    & 141 & 2   & 1     & 3       & 191 & 220 & 217  & 224 & 0.88 & 0.96  & 0.96 & 0.52 & 0.48 & 0.45 \\
-    $(10,14,\elseBr)$   & 59.28   & 56.44   & 31.78 & 33.58 & 21   & 10.5 & 17   & 17.5 & 1     & 0   & 1     & 1       & 186 & 217 & 258  & 206 & 0.55  & 0.57 & 0.55  & 0.48  &0.46 & 0.47 \\
-    \midrule
-    \textbf{newGame}             & 18.26 & 11.28 & 11.94  & 10.5   & 13.5   & 9   & 10    & 10   & 1      & 1    & 1      & 0       & 69  & 53    & 39    & 34 & & & & & & \\
-    %% $(4,5,\inFor)$   & 0.9    & 0.66   & 0.84     & 0.86      & 1       & 1     & 1       & 1     & 0     & 0    & 0      & 0       & 2    & 2      & 2      & 1   & 0.6  & 0.53 & 0.51 & 0.42  & 0.4 & 0.49 \\
-    $(6,7,\thenBr)$     & 16.58 & 9.78  & 10.24   & 8.84   & 11.5   & 7   & 8     & 8     & 1     & 1    & 1      & 0       & 67  & 47    & 34    & 31 & 0.64 & 0.6  & 0.65 & 0.44 & 0.5 & 0.56 \\
-    %% $(6,12,\elseBr)$ & 0.78   & 0.84   & 0.86     & 0.8    & 1       &  1     & 1       & 1     & 0     & 0    & 0      & 0       & 2    & 4      & 3      & 2   & 0.5   & 0.47 & 0.49 & 0.46 & 0.48 & 0.52 \\
-    \midrule
-    \textbf{revealAll}           & 69.2   & 55.26 & 70.34 & 64.04 & 50     & 44   & 58.5 & 52.5 &  8     & 16  & 16    & 16     & 261 & 153  & 226  & 202 & & & & & &\\
-    $(2,3,\inFor)$      & 27.78 & 26.7  & 39.34 & 32.58 & 20     & 24   & 30.5   & 27   & 3     & 7    & 7      & 11     & 89  & 64    & 148  & 100  & 0.45 & 0.37 & 0.39 & 0.39 & 0.43 & 0.55 \\
-    $(4,5,\inFor)$      & 41.42 & 28.56 & 33.02  & 31.46 & 30     & 20   & 28   & 25.5   & 5     & 9    & 9      & 5       & 172 & 89    & 78    & 102  & 0.62 & 0.53  & 0.55 & 0.39  & 0.37 & 0.53 \\
-    \midrule
-    \textbf{shuffleBoard}         & 410.56 & 321.28 & 371.58 & 358.84 & 401.5 & 299   & 338 & 321 & 342 & 250 & 268 & 263 & 568 & 689 & 716 & 674 & & & & & & \\
-    %% $(3,4,\inFor)$    & 1.6        & 1.36        & 1.52        & 1.42        & 2         & 1       & 2       & 1     & 1     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.61  & 0.54  & 0.58  & 0.42  & 0.47  & 0.55 \\
-    %% $(5,6,\inWhile)$  & 2.94    & 2.6      &  2.58     & 2.88     &  2         & 2       &  2       &  2     & 1     & 1     & 1     & 1     & 11    & 8     & 6     & 15    & 0.6  & 0.54 & 0.56 & 0.45  & 0.46  & 0.52 \\
-    %% $(10,11,\inFor)$  & 1.88       & 1.4         &  1.64        &  1.58        &  2         &  1       &  2       &  2     &  2     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.72  & 0.61  & 0.64  & 0.38  & 0.41  & 0.53 \\
-    $(13,14,\thenBr)$    & 13.6    & 13.88     &  17.7     &  15.78    & 9.5       &  8.5     &  8.5     &  9.5   & 1     & 1     & 1     & 1     & 44   & 103  & 126  & 78   & 0.58 & 0.52  & 0.53  & 0.46 & 0.46 & 0.51 \\
-    % $(13,16,\elseBr)$  & 1.52       & 1.4         & 1.68        & 1.5         &  1.5       &  1       &  2       & 1.5   & 1     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.55  & 0.42  & 0.51  & 0.36  & 0.45  & 0.59 \\
-    $(17,18,\thenBr)$    & 13.76   & 23.7    &  39.58   & 34.04   &  10      &  10      &  12.5  & 1     &  1     & 2     & 2     & 2     & 73   & 248 & 180  & 248 & 0.46 & 0.38 & 0.47 & 0.4  & 0.5   & 0.55 \\
-    %% $(17,20,\elseBr)$ & 2.06       & 1.84        & 1.72        & 1.8         &  2         & 2       &  2       &  2     & 1     & 1     & 1     & 1     &  4    & 2     & 2     & 2     & 0.59  & 0.64  & 0.61  & 0.56  & 0.52  & 0.46 \\
-    $(21,22,\inFor)$     & 373.2*    & 275.1*     & 305.16*    & 299.84*    & 372.5*   & 273.5* & 307*   & 302* & 334 & 242 & 260 & 255 & 427 & 322 & 396 & 325 & 1     & 0.99  & 1     & 0.15 & 0.16   & 0.58 \\
-    \midrule
-    \midrule
-    \textbf{toggleInfo}         & 6.12 & 11.9 & 18.3 & 15.4  & 5.5 & 7 & 7.5  & 6 & 0 & 0 & 0 & 0 & 22 & 118 & 138 & 106 & & & & & & \\
-    $(2,3,\thenBr)$    & 2.32 & 1.64  & 1.7   & 1.46     & 1.5 & 2 & 2   & 1 & 0 0 & 0 & 0 &  0 &  11 & 4     &  4     &  3     &  0.54  &  0.53 &  0.58 & 0.48  & 0.55 & 0.57 \\
-    %% $(2,5,\elseBr)$ & 0.86    & 0.84     & 0.86    & 0.8      & 1   & 1 & 1   & 1 & 0 & 0 & 0 & 0 & 2   &1     & 1     & 1     & 0.51  & 0.5   & 0.53  & 0.49  & 0.52  & 0.53 \\
-    $(6,7,\thenBr)$    & 2.1  & 8.7    & 14.92  & 12.34 & 2   & 3 & 3.5 & 3 & 0 & 0 & 0 & 0 & 8   & 112 & 132 & 101 & 0.37 & 0.29 & 0.36 & 0.42 & 0.48 & 0.55 \\
-    %% $(6,13,\elseBr)$& 0.84    & 0.72     & 0.82   & 0.8      & 1   & 1 & 1   & 1 & 0 & 0 & 0 & 0 & 1   & 1     & 1     & 1     &  0.56  &  0.51  & 0.52  & 0.45  & 0.46  & 0.51 \\
-    \midrule
-    \midrule
-    \textbf{isValidCard}       & 513.66 & 7.8 & 7.96 & 8.42 & 514   & 8 &  7 & 9.5 & 447 & 5 & 5 & 5 & 579 & 12 & 13 & 12  & & & & & & \\
-    %% $(3,4,\thenBr)$& 0.54     & 0.3     & 0.46    & 0.46     & 1       & 0  & 0  & 0    & 0     & 0  & 0  & 0  &  0     & 1   & 1   &  0 &  0.61 & 0.53 & 0.53 &  0.42 & 0.42 & 0.5 \\
-    $(3,6,\elseBr)$   & 102.98* & 1.52 & 1.4     & 1.56  &  102.5* & 2  &  1  & 2    &  87  &  1  &  1  &  1  &  116 &  2   &  3   &  3    &  1 &  1 &  1 & 0.49    & 0.5  & 0.43 \\
-    $(7,8,\inFor)$    & 102.38* & 1.44 & 1.6  & 1.58  & 103*   & 1  & 2  & 2    & 90  & 1  & 1  & 1  & 115 & 3   & 2   & 2    & 1 & 1 & 1 & 0.42 & 0.43 & 0.51 \\
-    $(10,11,\thenBr)$ & 101.44* & 1.56    & 1.48 & 1.7   & 102*   & 2  & 1  & 2    & 88  & 1  & 1  & 1  & 116 & 2   & 2   & 3    &  1 &  1 &  1 &  0.54 & 0.43 &  0.4 \\
-    $(10,13,\elseBr)$ & 104.66* & 1.38 & 1.54 & 1.62  & 106*   & 1  & 2  & 2    & 91  & 1  & 1  & 1  & 115 & 2   & 2   & 2    & 1 & 1 &  1 &  0.42 & 0.38 &  0.46 \\
-    $(14,15,\inFor)$  & 101.66* & 1.6  & 1.48 & 1.5   & 99.5*  & 2  & 1  & 1.5  & 91  & 1  & 1  & 1  & 117 & 2   & 3   & 2    & 1 & 1 &  1 &  0.56 &  0.55 & 0.48 \\
-    \midrule
-    %% \textbf{isValidMasterCard}  & 109.46 & 4.84 & 5.1  & 5.03 & 102.5 & 4 & 4.5 & 4 & 86 & 2 & 2 & 2 & 164 & 11 & 11 & 10 & & & & & & \\
-    %% $(2,3,\thenBr)$    & 108.98* & 4.5  & 4.64 & 4.6  & 102.5* & 4 & 4.5 & 4 & 86 & 2 & 2 & 2 & 162 & 10 & 10 & 9  & 1      & 1     & 1 & 0.47 & 0.49 & 0.51 \\
-    %% %% $(2,5,\elseBr)$ & 0.48     & 0.34     & 0.46   & 0.43     & 0       &  0  &  0    & 0  & 0    & 0 & 0 & 0 & 2     & 1   & 1   & 1   & 0.56 & 0.5 & 0.52 & 0.44 & 0.46 & 0.52 \\
-    \midrule
-    \textbf{isValidVISA}       & 97.54 & 3.06 & 3.04 & 3.04 & 95 & 3 & 3 & 2 &  89 & 2  & 1 & 1 & 140 & 6 & 7 & 7 & & & & & & \\
-    $(2,3,\thenBr)$   & 97.08* & 2.72 &  2.62 & 2.58 & 95* & 3 & 3 & 2 &  89 &  2 &  1 &  1 &  139 &  5 &  6 &  6 &  1 &  1 &  1 &  0.54 &  0.59 &  0.54 \\
-    %% $(2,5,\elseBr)$& 0.46    & 0.34    & 0.42    & 0.46    & 0    & 0 & 0 & 0 & 0    & 0 & 0 & 0 & 1     & 1  & 1  & 1  & 0.56 & 0.52 & 0.5 & 0.46 & 0.44 & 0.48 \\
-    \midrule
-    \midrule
-    \textbf{initShields}       & 5.8 & 3.76 & 3.9 & 3.7 & 5 & 4 & 4 & 3 & 3 & 3 & 3 & 3 & 10 & 5 & 5 & 5 & & & & & & \\
-    $(2,3,\inFor)$    & 5.8 & 3.76 & 3.9 & 3.7 & 5 & 4 & 4 & 3 & 3 & 3 & 3 & 3 & 10 & 5 & 5 & 5 & 0.83 & 0.8 & 0.84 & 0.45 & 0.53 & 0.58 \\
-    \midrule
-    \midrule
-    \textbf{brickJiggler}      & 9.74 & 4.68 & 4.98 & 4.28 &  8 & 4 &  4 & 3 & 2 & 3 & 2 & 2 & 28 & 20 & 12 & 12 &  & & & & &\\
-    $(2,3,\thenBr)$   & 8.46 & 3.54 & 3.66 &  3.2  &  7 &  3 & 3 & 2 & 2 & 2 &  1 & 1 & 25 & 18 & 10 & 10 & 0.83 & 0.81 & 0.85 & 0.48 & 0.56 & 0.57 \\
-    %% $(2,9,\elseBr)$& 1.28    & 1.14    & 1.32    & 1.08   & 1 & 1 & 1 & 1 & 0 & 1 & 1 & 1 & 3   & 2   & 2   & 2   & 0.51  & 0.45  & 0.53  & 0.41  & 0.53 & 0.62 \\
-    \midrule
-    \textbf{doPaddlePower}        & 17.64  & 134.54 & 36.4  & 29.58 & 15 & 140 & 14 & 16 &  1 &  3 &  0 &  1 &  51 &  160 &  157 &  144 & & & & & & \\
-    %% $(5,6,\thenBr)$   & 0.82      & 0.82        & 0.9       & 0.86      &  1     &  1     &  1   &  1   &  0 &  0 &  0 & 0   &  2   &  1     &  1     &  1     &  0.5   &  0.46  &  0.48 &  0.46  & 0.48 &  0.52 \\
-    %% $(5,8,\elseBr)$   & 0.9    & 1.04      & 0.82   & 0.74   & 1     &  1     &  1   &  1   &  0 &  0 &  0 & 0    &  3   &  4     &  2     &  3     &  0.47 &  0.52 &  0.56 &  0.54 &  0.59 &  0.55 \\
-    $(10,11,\thenBr)$    & 15.04 & 131.86 & 33.86 & 27.24  & 1 12 &  136* & 12 &  13 & 1 & 3 & 0 & 1 & 43 & 154 & 153 &  139 & 0.02 &  0.46 &  0.43 &  0.86 &  0.94 &  0.45 \\
-    %% $(10,13,\elseBr)$ & 0.88      & 0.82        & 0.82      &  0.74      &  1     &  1     &  1   &  1   &  0 &  0 &  0 & 0   &  3  &  1     &  1     &  1      &  0.251 &  0.51  &  0.55  & 0.5  &  0.54  &  0.54 \\
-
-    %% drawLevel         & 6.78 & 2.14 / 6.05 & 2.06 / 6.92 & 1.86 / 5.82 & 0 / 6 & 0 / 6 & 0 / 6 & 0 / 6 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 10 / 17 & 25 / 19 & 28 / 23 & 27 / 19 & & & & & \\
-    %% $(5,6,\thenBr)$   & 1.04 & 0.16 / 0.9  & 0.14 / 1.04 & 0.2 / 0.9   & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 2 / 2   & 3 / 2   & 5 / 4   & 5 / 3 & & & & & & \\
-    %% $(5,21,\elseBr)$  & 0.86    & 0 / 0.9     & 0 / 0.92    & 0 / 0.84    & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 2   & 0 / 2   & 0 / 1   & 0 / 1 & & & & & & \\
-    %% $(8,9,\inFor)$    & 1.04  & 0.16 / 0.89 & 0.34 / 1.1  & 0.3 / 1.06  & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 3 / 4   & 5 / 3   & 5 / 4   & 5 / 4 & & & & & & \\
-    %% $(10,11,\thenBr)$ & 1.52 & 1.26 / 1.48 & 0.98 / 1.62 & 0.8 / 1.1   & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 3 / 5   & 7 / 5   & 7 / 6   & 8 / 5 & & & & & & \\
-    %% $(10,13,\elseBr)$ & 1.2  & 0.22 / 0.86 & 0.3 / 1.14  & 0.2 / 0.98  & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 1 / 3   & 3 / 2   & 7 / 4   & 3 / 2 & & & & & & \\
-    %% $(14,15,\inFor)$  & 1.12 & 0.34 / 1.02 & 0.3 / 1.1   & 0.36 / 0.94 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 1 & 0 / 0 & 0 / 0 & 0 / 0 & 0 / 0 & 1 / 1   & 7 / 5   & 4 / 4   & 6 / 4 & & & & & & \\
-    \midrule
-    \textbf{initBricks}        & 2272.40  & 579.58 & 617    & 584.06 & 2379  & 474  & 517   & 414.5 & 90  & 60 & 64 & 59 & 4647 & 1612 & 1731 & 1653 & & & & & & \\
-    $(6,7,\thenBr)$   & 3.94     & 3.6    & 3.54   & 3.6    & 3     & 4    & 3     & 3     & 2   & 2  & 1  & 2  & 9    & 5    & 5    & 5    & 0.53 & 0.46 & 0.5  & 0.43 & 0.5  & 0.57 \\
-    $(6,10,\elseBr)$  & 50.56    & 6.16   & 6.32   & 7.68   & 23    & 6    & 6     & 6     & 3   & 2  & 2  & 3  & 370  & 10   & 14   & 23   & 0.87 & 0.83 & 0.83 & 0.34 & 0.4  & 0.56 \\
-    $(11,12,\thenBr)$ & 267.92   & 16.22  & 27.02  & 23.98  & 317*   & 11.5 & 16.5  & 15    & 5   & 6  & 6  & 5  & 366  & 48   & 67   & 78   & 0.93 & 0.91 & 0.91 & 0.41 & 0.41 & 0.47 \\
-    $(11,15,\elseBr)$ & 54.7     & 6.32   & 6.84   & 8.52   & 30    & 6    & 7     & 6     & 3   & 3  & 2  & 2  & 314  & 13   & 28   & 53   & 0.89 & 0.83 & 0.86 & 0.32 & 0.47 & 0.62 \\
-    $(16,17,\thenBr)$ & 272.82   & 23.36  & 38.68  & 28.08  & 324*   & 13.5 & 13    & 16    & 9   & 5  & 2  & 3  & 379  & 187  & 205  & 109  & 0.96 & 0.94 & 0.96 & 0.4  & 0.45 & 0.52 \\
-    $(16,20,\elseBr)$ & 95.9     & 8.16   & 13.3   & 11.06  & 40    & 6.5  & 6     & 7     & 3   & 3  & 2  & 3  & 367  & 50   & 70   & 83   & 0.89 & 0.8  & 0.86 & 0.36 & 0.46 & 0.6 \\
-    $(21,22,\thenBr)$ & 251.98   & 19.38  & 32.16  & 40.48  & 309.5* & 12.5 & 13.5  & 16.5  & 3   & 2  & 4  & 3  & 370  & 181  & 121  & 151  & 0.94 & 0.92 & 0.9  & 0.4  & 0.36 & 0.44 \\
-    $(21,25,\elseBr)$ & 93.62    & 7.08   & 12.72  & 13.12  & 41    & 6.5  & 7     & 7     & 5   & 3  & 3  & 3  & 371  & 20   & 99   & 81   & 0.94 & 0.84 & 0.87 & 0.32 & 0.42 & 0.59 \\
-    $(29,30,\thenBr)$ & 275.06   & 90.36  & 88.74  & 88.92  & 330*   & 57.5 & 69.5  & 70    & 5   & 5  & 6  & 5  & 413  & 208  & 204  & 201  & 0.82 & 0.88 & 0.88 & 0.46 & 0.5  & 0.54 \\
-    $(29,37,\elseBr)$ & 4.44     & 3.76   & 4      & 4.04   & 4     & 3    & 4     & 4     & 3   & 2  & 2  & 2  & 11   & 7    & 6    & 6    & 0.63 & 0.33 & 0.53 & 0.24 & 0.43 & 0.72 \\
-    $(38,39,\thenBr)$ & 266.76   & 93.96  & 95.88  & 86.26  & 328   & 66.5 & 82    & 44    & 30  & 5  & 11 & 5  & 410  & 208  & 217  & 214  & 0.87 & 0.82 & 0.88 & 0.41 & 0.54 & 0.62 \\
-    $(38,46,\elseBr)$ & 4.32     & 3.66   & 4.3    & 3.92   & 4     & 3.5  & 4     & 4     & 2   & 2  & 2  & 2  & 8    & 6    & 8    & 6    & 0.64 & 0.46 & 0.58 & 0.33 & 0.44 & 0.61 \\
-    $(47,48,\thenBr)$ & 264.56   & 108.44 & 115.74 & 108.1  & 335.5 & 141*  & 128   & 131   & 5   & 6  & 6  & 7  & 408  & 212  & 227  & 206  & 0.8  & 0.79 & 0.8  & 0.44 & 0.54 & 0.59 \\
-    $(47,55,\elseBr)$ & 4.52     & 3.74   & 4      & 3.92   & 4     & 3    & 4     & 4     & 2   & 2  & 2  & 2  & 9    & 6    & 6    & 6    & 0.66 & 0.44 & 0.61 & 0.31 & 0.46 & 0.65 \\
-    $(56,57,\thenBr)$ & 208.04   & 86.78  & 98.74  & 89.54  & 197.5 & 42.5 & 123.5 & 47    & 6   & 5  & 6  & 5  & 411  & 222  & 213  & 209  & 0.76 & 0.72 & 0.75 & 0.43 & 0.5  & 0.57 \\
-    $(56,64,\elseBr)$ & 4.48     & 3.82   & 4.38   & 3.94   & 4     & 3    & 4     & 4     & 2   & 2  & 2  & 2  & 7    & 5    & 15   & 6    & 0.64 & 0.51 & 0.61 & 0.39 & 0.47 & 0.59 \\
-    $(69,70,\thenBr)$ & 4.26     & 2.64   & 4.72   & 4.26   & 4     & 4    & 4     & 4     & 2   & 2  & 2  & 2  & 8    & 7    & 9    & 8    & 0.48 & 0.31 & 0.51 & 0.32 & 0.53 & 0.69 \\
-    $(69,71,\elseBr)$ & 144.52   & 92.14  & 55.92  & 54.64  & 80.5  & 83.5 & 22    & 26    & 3   & 3  & 3  & 3  & 416  & 217  & 217  & 208  & 0.57 & 0.71 & 0.68 & 0.65 & 0.61 & 0.46 \\
-    \midrule
-    \midrule
-    \textbf{do\_draw}             & 695.56 & 1064.82 & 346.64 & 347.42 & 625   & 1295  & 315  & 333.5  & 49 & 49 & 47 & 46 & 1772 & 1855 & 1453 & 1077 & & & & & & \\
-    %% $(2,3,\thenBr)$   & 2.42   & 2.48    & 2.44   & 2.38   & 2     & 2     & 2    & 2      & 2  & 2  & 2  & 2  & 3    & 4    & 3    & 3    & & & & & & \\
-    %% $(2,5,\elseBr)$   & 0.98   & 0.98    & 0.98   & 0.94   & 1     & 1     & 1    & 1      & 0  & 0  & 0  & 0  & 1    & 2    & 2    & 1    & & & & & & \\
-    $(6,7,\thenBr)$      & 23.62  & 23.74   & 21.66  & 19.82  & 18.5  & 25    & 23   & 20     & 2  & 2  & 2  & 2  & 103  & 46   & 50   & 15   & 0.41 & 0.45 & 0.5 & 0.55 & 0.62 & 0.57 \\
-    %% $(6,12,\elseBr)$  & 1.02   & 1       & 0.94   & 0.94   & 1     & 1     & 1    & 1      & 0  & 0  & 0  & 0  & 2    & 2    & 1    & 2    & & & & & & \\
-    $(8,9,\thenBr)$      & 32.2   & 19.58   & 20.12  & 19.3   & 23    & 17    & 20   & 20.5   & 2  & 2  & 2  & 0  & 124  & 54   & 45   & 47   & 0.63  & 0.6  & 0.62 & 0.47 & 0.49 & 0.5 \\
-    $(8,11,\elseBr)$     & 318.68 & 62.16   & 77.08  & 61.76  & 343   & 51    & 70.5 & 57     & 16 & 15 & 20 & 2  & 488  & 214  & 165  & 146  & 0.91  & 0.89 & 0.91 & 0.36 & 0.46 & 0.62\\
-    %% $(20,21,\thenBr)$ & 1.2    & 1.44    & 1.22   & 1.22   & 1     & 1     & 1    & 1      & 1  & 1  & 1  & 18 & 2    & 3    & 2    & 2    & & & & & &\\
-    %% $(20,23,\elseBr)$ & 2.52   & 2.58    & 2.46   & 2.46   & 3     & 2.5   & 2    & 2      & 2  & 2  & 2  & 1  & 3    & 4    & 3    & 3    & & & & & &\\
-    %% $(24,25,\thenBr)$ & 1.28   & 1.3     & 1.2    & 1.22   & 1     & 1     & 1    & 1      & 1  & 1  & 0  & 2  & 2    & 3    & 2    & 2    & & & & & &\\
-    %% $(24,27,\elseBr)$ & 2.52   & 2.94    & 3.02   & 2.66   & 2.5   & 3     & 3    & 2.5    & 2  & 2  & 2  & 1  & 4    & 12   & 17   & 11   \\
-    %% $(28,29,\thenBr)$ & 1.84   & 1.84    & 1.92   & 1.84   & 2     & 2     & 2    & 2      & 1  & 1  & 1  & 2  & 2    & 3    & 3    & 2    & & & & & &\\
-    %% $(28,31,\elseBr)$ & 1.94   & 1.94    & 1.9    & 1.94   & 2     & 2     & 2    & 2      & 1  & 1  & 1  & 1  & 3    & 3    & 3    & 3    & & & & & &\\
-    %% $(32,33,\thenBr)$ & 1.92   & 2.08    & 1.92   & 1.92   & 2     & 2     & 2    & 2      & 1  & 1  & 1  & 1  & 2    & 3    & 3    & 2    & & & & & &\\
-    %% $(32,35,\elseBr)$ & 1.9    & 2.04    & 1.9    & 1.86   & 2     & 2     & 2    & 2      & 1  & 1  & 1  & 1  & 3    & 3    & 3    & 2    & & & & & &\\
-    %% $(36,37,\thenBr)$ & 1.02   & 1.22    & 1      & 1.08   & 1     & 1     & 1    & 1      & 0  & 0  & 0  & 0  & 2    & 3    & 2    & 2    & & & & & &\\
-    %% $(36,39,\elseBr)$ & 3.4    & 4.8     & 4.14   & 2.98   & 3     & 3     & 3    & 3      & 2  & 2  & 2  & 2  & 12   & 24   & 24   & 8    \\
-    %% $(40,41,\thenBr)$ & 1.18   & 1.28    & 1.24   & 1.04   & 1     & 1     & 1    & 1      & 0  & 0  & 1  & 0  & 2    & 2    & 2    & 2    & & & & & &\\
-    %% $(40,43,\elseBr)$ & 2.86   & 3.04    & 4.12   & 3.76   & 3     & 3     & 3    & 3      & 2  & 2  & 2  & 2  & 5    & 9    & 20   & 40   \\
-    $(44,45,\thenBr)$    & 193.84 & 515.7   & 102.5  & 125.62 & 143.5 & 681*   & 83   & 111    & 10 & 12 & 3  & 6  & 518  & 718  & 657  & 645  & 0.16 & 0.65 & 0.58 & 0.9 & 0.89 & 0.24 \\
-    %% $(44,47,\elseBr)$ & 1.08   & 1.1     & 1.02   & 1.02   & 1     & 1     & 1    & 1      & 0  & 0  & 1  & 0  & 2    & 2    & 2    & 2    & & & & & & \\
-    $(48,49,\thenBr)$    & 97.12  & 410.58  & 92.86  & 90.58  & 68    & 491.5 & 90   & 96.5   & 3  & 2  & 3  & 3  & 487  & 739  & 442  & 135  & 0.24 & 0.43 & 0.4 & 0.74 & 0.74 & 0.41 \\
-    %% $(48,51,\elseBr)$ & 1.02   & 1       & 1      & 1.08   & 1     & 1     & 1    & 1      & 0  & 0  & 0  & 0  & 2    & 2    & 2    & 2    & & & & & & \\
-    \midrule
-    \midrule
-    \textbf{prob\_gamma}          & 701.78  & 84.88 & 82.56 & 81.98 & 710  & 84 & 79.5  & 80.5 & 484 & 55  & 52 & 52  & 799 & 119 & 121 & 122 & & & & & & \\
-    $(4,5,\thenBr)$      & 69.06   & 0.84  & 0.84  & 0.9   & 70.5* & 1  & 1     & 1    & 11  & 0   & 0  & 0   & 80  & 2   & 1   & 2   & 1 & 1 & 1 & 0.5 & 0.47 & 0.47 \\
-    %% $(4,25,\elseBr)$  & 0.3     & 0.4   & 0.4   & 0.36  & 0    & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
-    $(6,7,\thenBr)$      & 68.26   & 0.9   & 0.9   & 0.88  & 71*   & 1  & 1     & 1    & 8   & 0   & 0  & 0   & 77  & 2   & 2   & 2   & 1 &  1 & 1 & 0.5 & 0.51 & 0.51 \\
-    $(6,9,\elseBr)$      & 69.2*    & 1     & 0.92  & 0.98  & 69.5* & 1  & 1     & 1    & 57  & 0   & 0  & 0   & 76  & 4   & 2   & 2   & 1 & 1 & 1 & 0.52 & 0.49 & 0.47 \\
-    $(10,11,\thenBr)$    & 70.06*   & 41.58 & 39.66 & 39.44 & 72*   & 42 & 39.5  & 40   & 56  & 31  & 27 & 29  & 77  & 51  & 52  & 52  & 1 & 1 & 1 & 0.6 & 0.62  & 0.5 \\
-    $(10,13,\elseBr)$    & 70.4*    & 1.04  & 0.82  & 0.88  & 71*   & 1  & 1     & 1    & 59  & 0   & 0  & 0   & 79  & 2   & 2   & 2   & 1 & 1 & 1 & 0.6 & 0.57 & 0.47 \\
-    $(16,17,\inWhile)$   & 69.74*   & 1.1   & 1.06  & 1.08  & 70*   & 1  & 1     & 1    & 57  & 0   & 0  & 0   & 81  & 2   & 3   & 4   & 1 & 1 & 1 & 0.52 & 0.53 & 0.5 \\
-    $(20,21,\thenBr)$    & 69.8*    & 2.58  & 2.6   & 2.92  & 70*   & 2  & 2     & 2.5  & 58  & 1   & 0  & 0   & 78  & 6   & 9   & 11  & 1 & 1 & 1 & 0.56 & 0.48 & 0.43 \\
-    $(20,23,\elseBr)$    & 70.58*   & 0.9   & 0.94  & 0.88  & 71.5* & 1  & 1     & 1    & 57  & 0   & 0  & 0   & 79  & 3   & 2   & 2   & 1 & 1 & 1 & 0.46 & 0.49 & 0.5 \\
-    %% $(26,27,\thenBr)$ & 0.44    & 0.54  & 0.48  & 0.36  & 0    & 1  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 2   & 1   & & & & & & \\
-    %% $(26,29,\elseBr)$ & 0.34    & 0.38  & 0.38  & 0.4   & 0    & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
-    $(30,31,\thenBr)$    & 70.94*   & 22.56 & 22.3  & 21.88 & 72*   & 23 & 22    & 22   & 57  & 17  & 18 & 16  & 81  & 28  & 27  & 27  & 1 & 1 & 1 & 0.54 & 0.58 & 0.56 \\
-    %% $(30,33,\elseBr)$ & 0.5     & 0.36  & 0.32  & 0.46  & 0.5  & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
-    $(34,35,\thenBr)$    & 71.3*    & 9.9   & 10.18 & 9.8   & 72*   & 10 & 10    & 10   & 64  & 6   & 7  & 7   & 85  & 13  & 14  & 12  & 1 & 1 & 1 & 0.46 & 0.51 & 0.55 \\
-    %% $(34,41,\elseBr)$ & 0.48    & 0.46  & 0.34  & 0.42  & 0    & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
-    %% $(44,45,\inFor)$  & 0.38    & 0.34  & 0.42  & 0.34  & 0    & 0  & 0     & 0    & 0   & 0   & 0  & 0   & 1   & 1   & 1   & 1   & & & & & & \\
+    \multicolumn{2}{l|}{\textbf{helpMe}*}     
+                                 & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
+    $(3,4,\inFor)$    & 1        & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & 0.57 & 0.39 & 0.37  \\
+    $(5,6,\thenBr)$   & 2        & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & 0.46 & 0.5  & 0.53  \\
+    $(5,15,\elseBr)$  & 2        & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & 0.48  \\
+    $(9,10,\thenBr)$  & 3        & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & 0.40  \\
+    $(9,14,\elseBr)$  & 3        & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & 0.56 & 0.51 & 0.45  \\
+    \hline                                                                                                          
+\multicolumn{2}{l|}{\textbf{isGameFinished}*} 
+                                 & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
+    $(7,8,\thenBr)$   & 2        & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & 0.6  & 0.66 & 0.43   \\
+    $(10,11,\thenBr)$ & 3        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & 0.48   \\
+    $(10,14,\elseBr)$ & 3        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & 0.55 & 0.55 & 0.46   \\
+    \hline
+    \multicolumn{2}{l|}{\textbf{newGame}*}   
+                                 & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
+    $(6,7,\thenBr)$   & 2        & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & 0.5  \\
+    \hline
+    \multicolumn{2}{l|}{\textbf{revealAll}*}  
+                                 & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
+    $(2,3,\inFor)$    & 1        & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & 0.45 & 0.39 &  0.43  \\
+    $(4,5,\inFor)$    & 2        & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & 0.55 &  0.37  \\
+    \hline
+\multicolumn{2}{l|}{\textbf{shuffleBoard}*}   
+                                 & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
+    $(13,14,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & 0.58 & 0.53 & 0.46  \\
+    $(17,18,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & 0.46 & 0.47 & 0.5   \\
+    \toprule
+\multicolumn{2}{l|}{\textbf{toggleInfo}*}     
+                                 & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
+    $(2,3,\thenBr)$   & 1        & 2        & 2    & 1         & 2  & 2 & 1                 & 2 & 1   & 0.5                & 1     & 2     & 2     & 0.54 & 0.58 & 0.55  \\
+    $(6,7,\thenBr)$   & 1        & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & 0.48  \\
+    \toprule
+\multicolumn{2}{l|}{\textbf{isValidCard}}        
+                                 & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
+    $(3,6,\elseBr)$   & 1        & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & 0.5   \\
+    $(7,8,\inFor)$    & 1        & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & 0.43  \\
+    $(10,11,\thenBr)$ & 2        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & 0.43  \\
+    $(10,13,\elseBr)$ & 2        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & 0.38  \\
+    $(14,15,\inFor)$  & 1        & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & 0.55  \\
+    \hline
+\multicolumn{2}{l|}{\textbf{isValidVISA}}        
+                                 & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
+    $(2,3,\thenBr)$   & 1        & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & 0.59  \\
+    \toprule
+\multicolumn{2}{l|}{\textbf{initShields}*}    
+                                 & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
+    $(2,3,\inFor)$    & 1        & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & 0.53  \\
+    \toprule
+\multicolumn{2}{l|}{\textbf{brickJiggler}*}   
+                                 & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
+    $(2,3,\thenBr)$   & 1        & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & 0.56  \\
+    \hline
+\multicolumn{2}{l|}{\textbf{doPaddlePower}*}  
+                                 & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
+    $(10,11,\thenBr)$ & 1        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & 0.43 & 0.94 \\
+    \hline
+\multicolumn{2}{l|}{\textbf{initBricks}*}     
+                                 & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
+    $(6,7,\thenBr)$   & 1        & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & 0.53 & 0.5  & 0.5   \\
+    $(6,10,\elseBr)$  & 1        & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & 0.4   \\
+    $(11,12,\thenBr)$ & 2        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & 0.41  \\
+    $(11,15,\elseBr)$ & 2        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & 0.47  \\
+    $(16,17,\thenBr)$ & 3        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & 0.45  \\
+    $(16,20,\elseBr)$ & 3        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & 0.46  \\
+    $(21,22,\thenBr)$ & 4        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
+    $(21,25,\elseBr)$ & 4        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & 0.42  \\
+    $(29,30,\thenBr)$ & 1        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & 0.5   \\
+    $(29,37,\elseBr)$ & 1        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.63 & 0.53 & 0.43  \\
+    $(38,39,\thenBr)$ & 2        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & 0.54  \\
+    $(38,46,\elseBr)$ & 2        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & 0.58 & 0.44  \\
+    $(47,48,\thenBr)$ & 3        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & 0.54  \\
+    $(47,55,\elseBr)$ & 3        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & 0.46  \\
+    $(56,57,\thenBr)$ & 4        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & 0.5   \\
+    $(56,64,\elseBr)$ & 4        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & 0.47  \\
+    $(69,70,\thenBr)$ & 1        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.48 & 0.51 & 0.53  \\
+    $(69,71,\elseBr)$ & 1        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & 0.57 & 0.68 & 0.61  \\
+    \toprule
+    \multicolumn{2}{l|}{\textbf{do\_draw}}       
+                                 & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
+    $(6,7,\thenBr)$   & 1        & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & 0.41 & 0.5  &  0.62 \\
+    $(8,9,\thenBr)$   & 2        & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  0.49 \\
+    $(8,11,\elseBr)$  & 2        & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  0.46 \\
+    $(44,45,\thenBr)$ & 1        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & 0.58 &  0.89 \\
+    $(48,49,\thenBr)$ & 1        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & 0.4  &  0.74 \\
+    \toprule
+\multicolumn{2}{l|}{\textbf{prob\_gamma}}        
+                                 & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
+    $(4,5,\thenBr)$   & 1        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  0.47  \\
+    $(6,7,\thenBr)$   & 2        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  0.51  \\
+    $(6,9,\elseBr)$   & 2        & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  0.49  \\
+    $(10,11,\thenBr)$ & 2        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  0.62  \\
+    $(10,13,\elseBr)$ & 2        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  0.57  \\
+    $(16,17,\inWhile)$& 2        & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  0.53  \\
+    $(20,21,\thenBr)$ & 2        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 & 0.48   \\
+    $(20,23,\elseBr)$ & 2        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  0.49  \\
+    $(30,31,\thenBr)$ & 1        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  0.58  \\
+    $(34,35,\thenBr)$ & 1        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  0.51  \\
     \bottomrule
     \end{tabular}
-%}
-\end{table*}
-
-% \input{summary_branch_coverage}
+\end{table}
+
+\paragraph{\textbf{RQ1 (performance).}} We would like to study the performance of the three variations of the testing framework: Random ($R$), Genetic ($G$) and Genetic with Restart ($G10$).
+To address this question, we applied our framework to all branches of each function in Table~\ref{tbl.case.studies}.
+Due to the probabilistic nature of the test generation process, the experiments has to be repeated 50 times to get statistically significant results.
+Our discussion completely excludes some functions in Table~\ref{tbl.case.studies} ($-$ sign in the $?$ column) as not presenting real challenge.
+Despite of it apparent complexity, like the function \emph{update}, in practice both random and genetic testing strategies take maximum upto two seconds to cover each branch.
+This gave us in total 14 functions, for which we present summary of performance statistics in Table~\ref{tbl.stats} for all three testing strategy.
+For the sake of space, we omitted from that table the branches whose average coverage time was less than one second.
+Functions suffixed with the start (*) symbol indicate reference to DOM.
+Column $D$ next to the branch shows its depth.
+We computed the following medians for each algorithm: the number of iterations ($i$), time in seconds ($t$), and their ratio ($t/i$).
+In the table, these values are grouped into three columns $m_r$, $m_g$ and $m_{g10}$, one per algorithm type $R$, $G$ and $G5$  respectively.
+Next group of columns $t_r/t_g$, $t_r/t_{g10}$ and $t_g/t_{g10}$ measures the relative performance of each pair of the testing strategies $(R,G)$, $(R,G10)$, and $(G,G10)$ respectively.
+
+The fact that the median of generation reached the upper limit of \underline{200} means the branch was never covered.
+With that budget in mind not all algorithms were always performing successfully.
+The main reason for the random generation to fail, e.g.
+the \emph{(10,11,then)} branch of the \emph{isGameFinished} function or any branch of the \emph{isValidCard} function, is the huge size of the search space and complete absence of any guidance.
+On the contrary, the genetic search may stuck on a flat space when the fitness function does not carry any information how to get out it, e.g.
+the branches \emph{(10,11,then)}, \emph{(40,48,then)} and \emph{(40,45,then)} of the functions \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw} respectively.
+(say why random give better performance in that case) Those examples motivated us to introduce the genetic algorithm with restart ($G5$), which is as our evaluation demonstrated not only provided a solution within given budget, but also outperformed random search.
+(Maybe discuss examples where $R$ outperformed $G5$)
+
+Table~\ref{tbl.stats} also shows accumulated statistics for each function as a whole (row in line with the function name).
+This gives us a way to compare  all three testing strategies with each other at the function level.
+Chart in Figure~\ref{fig.gen.time.comp} clearly illustrates how the median time varies per function for each algorithm.
+Across all 14 examples $G10$ indicated the best performance comparing to both $R$ and $G$.
+We observed only two cases (\emph{revealAll}) and (\emph{doPaddlePower}) where random testing gave a slightly better result by only 6\%.
+If we take in consideration only examples with the average execution time above 50 seconds, we can conclude that $G10$ was minimum 1.87 time (\emph{do_draw}) and maximum 51.4 (\emph{isValidCard}) time faster than $R$.
+At the same time, even plain genetic algorithm $G$ outperforms the random one $R$ in all examples except of two \emph{doPaddlePower} and \emph{initBricks} due to the reasons discussed early in this section.
+In cases of success, especially for some small examples such as \emph{newGame} and \emph{isValidCard}, the genetic algorithm was even able to beat $G5$ by upto 30\%.
+
+\paragraph{\textbf{RQ2 (cost).}} The cost of one test iteration is defined as the relation between the execution time and the number of generations, i.e.
+$t/i$ in Table~\ref{tbl.stats}.
+Figure~\ref{fig.get.cost} shows the comparison of various algorithms across all case-studies.
+
+\paragraph{\textbf{RQ3 (coverage).}} ...
 
@@
   \centering
-\begin{tikzpicture}[scale=0.7]
+  \begin{tikzpicture}[scale=0.8]
+    \begin{axis}[
+        every axis plot post/.style={/pgf/number format/fixed},
+        ybar,
+        ymin=0,ymax=950,
+        width=11cm,height=3.3cm,
+        bar width=3pt,
+        enlarge x limits=0.05,
+        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
+        legend cell align={left},
+        ylabel={time (sec.)},
+        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
+        xtick=data,
+        restrict y to domain*=0:1350, % Cut values off at 14
+        visualization depends on=rawy\as\rawy, % Save the unclipped values
+        after end axis/.code={ % Draw line indicating break
+          \draw [ultra thick, white, decoration={snake, amplitude=1pt}, decorate] (rel axis cs:0,1.05) -- (rel axis cs:1,1.05);
+        },
+        nodes near coords={%
+          \pgfmathprintnumber{\rawy}% Print unclipped values
+        },
+        every node near coord/.append style={rotate=90,anchor=west,font=\footnotesize},
+        % every node near coord/.append style={font=\footnotesize},
+        axis lines*=left,
+        clip=false,
+        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
+        y tick label style={font=\footnotesize}
+      ]
+      \addplot[fill=blue] coordinates {(helpMe*,270) (isGameFinished*,220) (newGame*,14) (revealAll*,50) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,514) (isValidVISA,95) (initShields*,5) (brickJiggler*,8) (doPaddlePower*,15)  (initBricks*,2379) (do\_draw,625) (prob\_gamma,710)};
+      \addplot[fill=red] coordinates {(helpMe*,47)  (isGameFinished*,30)  (newGame*,9)  (revealAll*,44) (shuffleBoard*,26) (toggleInfo*,7) (isValidCard,8)   (isValidVISA,3)  (initShields*,5) (brickJiggler*,4) (doPaddlePower*,140) (initBricks*,474) (do\_draw,1295) (prob\_gamma,84)};
+      \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
+      \legend{R,G,G10}
+    \end{axis}
+  \end{tikzpicture}
+  \caption{Overall test generation time per function.}
+  \label{fig.gen.time.comp}
+\end{figure}
+
+% \input{summary_statistics}
+
+\begin{figure}[t]
+  \begin{tikzpicture}[scale=0.8]
+    \begin{axis}[
+        every axis plot post/.style={/pgf/number format/fixed},
+        ybar,
+        ymin=0,ymax=4,
+        width=11cm,height=3.3cm,
+        bar width=3pt,
+        enlarge x limits=0.05,
+        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
+        legend cell align={left},
+        ylabel={time (sec.)},
+        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
+        xtick=data,
+        nodes near coords,
+        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
+        % every node near coord/.append style={font=\footnotesize},
+        axis lines*=left,
+        clip=false,
+        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
+        y tick label style={font=\footnotesize}
+      ]
+      \addplot[fill=blue] coordinates {(helpMe*,1.24) (isGameFinished*,0.83) (newGame*,0.78) (revealAll*,0.83) (shuffleBoard*,1.93) (toggleInfo*,1) (isValidCard,0.51) (isValidVISA,0.47) (initShields*,0.83) (brickJiggler*,1.14) (doPaddlePower*,0.79)  (initBricks*,1.68) (do\_draw,2.33) (prob\_gamma,0.35)};
+      \addplot[fill=red] coordinates {(helpMe*,0.77)  (isGameFinished*,0.94)  (newGame*,0.81)  (revealAll*,1) (shuffleBoard*,1.73) (toggleInfo*,1) (isValidCard,0.38)   (isValidVISA,0.38)  (initShields*,0.83) (brickJiggler*,0.67) (doPaddlePower*,0.69) (initBricks*,0.8) (do\_draw,3.38) (prob\_gamma,0.52)};
+      \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
+      \legend{R,G,G10}
+    \end{axis}
+  \end{tikzpicture}
+  \caption{Speed of test generation measured as $t/i$}
+    \label{fig.get.cost}
+\end{figure}
+
+\begin{figure}[t]
+  \begin{tikzpicture}[scale=0.8]
+    \begin{axis}[
+        every axis plot post/.style={/pgf/number format/fixed},
+        ybar,
+        ymin=0,ymax=135,
+        width=11cm,height=3.3cm,
+        bar width=3pt,
+        enlarge x limits=0.05,
+        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
+        legend cell align={left},
+        ylabel={time (sec.)},
+        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
+        xtick=data,
+        nodes near coords,
+        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
+        % every node near coord/.append style={font=\footnotesize},
+        axis lines*=left,
+        clip=false,
+        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
+        y tick label style={font=\footnotesize}
+      ]
+      \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
+
+      \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
+
+      \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
+      \legend{R,G,G10}
+    \end{axis}
+  \end{tikzpicture}
+  \caption{Average generation time per branch}
+    \label{fig:1}
+\end{figure}
+
+\begin{figure}[!t]
+  \begin{tikzpicture}[scale=0.5]
     \begin{axis}[
@@
         color=blue,
-    mark=square,
+        mark=square*,
       ] coordinates {
@@
         color=red,
-    mark=square,
+        mark=triangle*,
       ]  coordinates {
@@
       \addplot[
-    color=green,
-    mark=square,
-  ]   coordinates {
-    (5,26) (10,35) (30,49) (60,51) (90,56) (120,56) (150,58)
-  };
-  \addplot[
         color=yellow,
-    mark=square,
+        mark=*,
       ]   coordinates {
@@
       };
-    \legend{R,G,G5,G10}
+      \legend{R,G,G10}
 
@@
   \caption{Progress of the branch coverage given fix time budget per branch}
+    \label{fig:2}
 \end{figure}
+
+\section{Discussion}
+\label{sec.disc}
 
@@
 \end{itemize}
+
+\subsection{Threats to Validity}
+\label{sub.sec.thhreats}
 
@@
 
-\section{Conclusion}
+\section{Conclusions}
 \label{sec:concl}

### 2017-12-23 evaluation/confix/sudoku/final_isGameFinished.js

@@ -12,7 +12,7 @@ function test() {
             }
         }
     }
-    if (allOk) {
-        console.log('Congratulations! You did it');
-    }
+    // if (allOk) {
+    //     console.log('Congratulations! You did it');
+    // }
 }

### 2017-12-23 evaluation/confix/sudoku/final_shuffleBoard.js

@@ -21,9 +21,9 @@ function test(number1, number2) {
 	    }
         }
 
-        for (var n1 = 0; no < tmpObjects1.length; no++) {
-            tmpObjects1[n1].innerHTML = number2;
-            tmpObjects2[n1].innerHTML = number1;
-        }
+        // for (var n1 = 0; no < tmpObjects1.length; no++) {
+        //     tmpObjects1[n1].innerHTML = number2;
+        //     tmpObjects2[n1].innerHTML = number1;
+        // }
     }
 }

### 2017-12-23 evaluation/tsjs_dom_html/chrome/bingbong/final_initBricks.js

@@ -68,6 +68,6 @@ function test(i, myCenterH, brickV, brickH, brickStat, theLevelArt, levelData) {
     }
     i++;
     if (i <= 50) {
-        //window.setTimeout("initBricks(" + i + ");", 20);
+        window.setTimeout("initBricks(" + i + ");", 20);
     }
 }

### 2017-12-31 doc/icse2018/icse2018.tex
Working o RQ3.
* doc/icse2018/icse2018.tex:

@@
 
-\paragraph{\textbf{RQ2 (cost).}} The cost of one test iteration is defined as the relation between the execution time and the number of generations, i.e.
+\paragraph{\textbf{RQ2 (cost).}} The cost (time) of one iteration is defined as the relation between the execution time and the number of generations, i.e.
 $t/i$ in Table~\ref{tbl.stats}.
-Figure~\ref{fig.get.cost} shows the comparison of various algorithms across all case-studies.
-
-\paragraph{\textbf{RQ3 (coverage).}} ...
+Figure~\ref{fig.get.cost} shows the cost comparison of various algorithms across all case-studies.
+The execution time of one iteration depends on the population size, in case 50 candidates.
+Evaluation of a candidate results in an execution trace of a varying length.
+The length of an execution trace positively correlates with the computation cost of the fitness function.
+Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
+The \emph{do_draw} examples illustrates the latter case, it consists of 40 LOC and operates only with primitive type which do not case any exception.
+In our evaluation we observed that the iteration cost varied between 0.25 and 3.38 seconds.
+
+TODO: discuss why cost of one genetic iteration for \emph{do_draw} is higher than random.
+
+TODO: discuss if costs of $R$, $G$ and $G5$ vary between each other and why.
+
+\paragraph{\textbf{RQ3 (coverage).}} In this research question we want to compare how coverage progresses with the increase of budget assigned per branch.
+We chose the following budget categories: 5, 10, 30 etc.
+up to 150 seconds per branch.
+Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
+Eventually, it converges around 52\% coverage.
+Given 5 seconds per branch, both $G$ and $G10$ equally perform at the rate of 45\%.
+When the budget increases towards 10 seconds, $G$ slightly outperforms $G10$, 60\% against 63\% respectively.
+But when the budget rises to 30 seconds, $G10$ starts to transcend $G$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).
 
@@
         xmin=0, xmax=150,
-        ymin=0, ymax=59,
+        ymin=10, ymax=58,
         xtick={0,5,10,30,60,90,120,150,180},
@@
         ymajorgrids=true,
+        % xmajorgrids=true,
         grid style=dashed,
+        label style={font=\huge}
       ]
@@
       ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,59)
+        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
       };

### 2017-12-31 python/report.py

@@ -97,14 +97,14 @@ def printTarget(writer, target_stats):
 
 def outputCsvReport():
     inputfile = sys.argv[1]
-    print 'Analysing file:', inputfile
+    print('Analysing file:', inputfile)
     (input_path, input_base) = split(inputfile)
     input_name = splitext(input_base)[0]
     outputfile = join(input_path, input_name) + '.csv'
-    print 'Generating report:', outputfile
+    print('Generating report:', outputfile)
     with open(outputfile, 'w') as csvfile:
         report = processReport(inputfile)
-        print 'len', len(report)
+        print('len', len(report))
         header = ['brunch'] + range(1, len(report)+1)
         writer = csv.writer(csvfile, delimiter=';')
         writer.writerow(header)

### 2018-01-04 doc/icse2018/icse2018.tex
Working on introduction.

@@
 \label{sec.intro}
+
+According to the Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the firth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
+Such a tremendous ever increasing success of JS happens thanks to various language features including dynamic typing, native browser support (DOM).
+
+Say about popularity of JS applications including nodejs. Cite some works referring to challenges in testing.
+
+Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.
+
+Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.
+
+List current practices in testing and show where they fail. Make connection with DOM.
+
+The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit among the most used ones in the decreasing order of popularity.
+These frameworks support testing at different levels unit, integration and functional.
+The same survey also indicated relatively low satisfaction rate of the current state of JS testing tools, only 3.2 out of 5.
+As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
+But despite of this effort, test data generation stays a missing component not being properly addressed by any of the widely used testing frameworks.
+Research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
+
+Recent study of client-side JS bugs~\cite{ocariza2017study} has shown that majority (68\%) of JS faults are DOM-related and occur in the JS code itself. This fact indicates that a better
+
+Introduce search-based test generation.
+
 Recent empirical study of client-side JavaScript bugs~\cite{frolin:TSE16} has shown that 68\% of faults are DOM related.

### 2018-01-15 doc/icse2018/icse2018.tex
Another review round.

@@
 \usepackage{multirow}
+\usepackage{multicol}
 \usepackage{booktabs} % For formal tables
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings.\footnote{This is an abstract footnote}
+As of 2017 JavaScript language and Node.js platform continues to stay the most prevalent technologies voted by the developers in Stack Overflow survey. At the same time  
 \end{abstract}
@@
 According to the Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the firth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
-Such a tremendous ever increasing success of JS happens thanks to various language features including dynamic typing, native browser support (DOM).
-
-Say about popularity of JS applications including nodejs. Cite some works referring to challenges in testing.
-
-Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.
-
-Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.
-
-List current practices in testing and show where they fail. Make connection with DOM.
+It is used through all technology stack web, back-ends and mobile.
+Such a tremendous ever increasing JS success is happening thanks to extensive dynamic features of the language, JS permissiveness and native browser support.
+On the contrary, JS applications are error-prone~\cite{why}, hard to analyze~\cite{why} and test~\cite{why}.
+Therefore, it is not surprising that year over year we hear new stories\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}} about another critical bug being found in a web application by Facebook, Twitter etc.
+
+%% Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.
+
+%% Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.
 
@@
 Research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-
-Recent study of client-side JS bugs~\cite{ocariza2017study} has shown that majority (68\%) of JS faults are DOM-related and occur in the JS code itself. This fact indicates that a better
-
-Introduce search-based test generation.
-
-Recent empirical study of client-side JavaScript bugs~\cite{frolin:TSE16} has shown that 68\% of faults are DOM related.
+Recent study of client-side JS bugs~\cite{ocariza2017study} has shown that majority (68\%) of JS faults are DOM-related and occur in JS code itself.
+This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
+
+Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{paper}.
+In the recent years, some effort was done to apply search-based testing for dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been implemented for JavaScript.
+This circumstance motivated us to introduce a search-based test generation framework for JS with presence of DOM.
+Our work makes the following contributions:
+\begin{enumerate}
+\item JS search-based testing framework
+\item random HTML generation
+\item genetic with restart algorithm
+\item empirical evaluation 
+\end{enumerate}
+
+The paper is structured as follows:
 
@@
         break; 
-      } |c \label{isGameFinished.if2.end} |c
-    } |c \label{isGameFinished.if1.end} |c
-  } |c \label{isGameFinished.inFor.end} |c
-  if (allOk) { |c \label{isGameFinished.if3.begin} |c 
-    console.log('Congratulations! You did it'); |c \label{isGameFinished.finished} |c
-  } |c \label{isGameFinished.if3.end} |c
+      }
+    }
+  } |c \label{isGameFinished.outFor} |c
 }
@@
   \caption{JS function \texttt{isGameFinished.js} from sudoku}
-  \label{code.newGame}
+  \label{code.isGameFinished}
 \end{figure}
+
+\begin{figure}[t]
+  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
+<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
+<html>                        <html>
+ <body>                        <body>
+  <div id='sudoku'>             <div id='sudoku'>
+                                 <div></div>                           
+  </div>                        </div> 
+ </body>                       </body>    
+</html>                       </html>
+
+<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
+<html>                        <html>
+ <body>                        <body>
+  <div id='sudoku'>             <div id='sudoku'>
+   <div class='sudokuSquare'>    <div class='sudokuSquare'>
+    <span></span>                 <span></span> 
+    <span></span>                 <span>TEST</span>
+   </div>                        </div> 
+  </div>                        </div>
+ </body>                       </body>
+</html>                       </html>
+  \end{lstlisting}
+  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
+  \label{fig.isGameFinished.tests}
+\end{figure}
+
+Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from a web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
+This function checks the validity of a sudoku solution given by a user.
+First, we find a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
+Then, we collect all its child DIVs (line~\ref{isGameFinished.getDivs}).
+Each DIV element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) and consists of two SPANs.
+First span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
+Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
+Once, we find a square with two unequal SPAN values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
+
+Suppose now that we would like to unit test this function in isolation to the rest of the application.
+We aim to maximize the branch coverage as a common testing criteria~\cite{why.this.common}.
+That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
+JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
+We assume that DOM is the only global variable that can be referenced in the body of the FUT.
+So in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
+
+%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
+
+Figure~\ref{fig.isGameFinished.tests} presents four tests that together deliver the full coverage of the FUT.
+Let us look now at how following the structure of the FUT in Figure~\ref{code.isGameFinished}, we can construct the $T4$ test covering the $(10,11)$ branch.
+Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
+In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{DIV} tag.
+The first if-condition in line~\ref{isGameFinished.if1.begin} requires this $div$ to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle\ and also have no background color.
+The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the $div$ consists of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
+The resulted test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
+
+As we have just seen, even for such a relatively simple example, the construction procedure of a test input is far from trivial because it requires the deep understanding of the program semantics.
+In practice, web developers often have to deal with the gazillion of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
+At the same time, unit testing is the most fundamental level of testing and, at the same time, it is easiest to implement.
+It greatly saves the developers from unexpected regression and puts a safety belt around the application.
+
+%% --------------------------------------------------------------------
+\section{Test Generation Framework}
+\label{sec.framework}
+%% --------------------------------------------------------------------
+
+\begin{figure}[t!]
+  \centering 
+  \begin{sequencediagram}[font=\footnotesize]
+
+    \renewcommand\unitfactor{0.5}
+    \newinst{user}{\textbf{User}}
+    \newinst{server}{\textbf{Server}}
+    \newinst[1]{validator}{\textbf{Validator}}
+    \newinst{client}{\textbf{Client}}
+
+    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
+      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
+      \end{call}
+
+      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
+      \end{call}
+
+      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
+      \end{call}
+
+      \begin{sdblock}{\textbf{Genetic Loop}}{\hspace{2mm}$\text{branch} \in \text{branches}'$}
+        \begin{sdblock}{\textbf{Random Loop}}{errors > 0}
+          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
+          \end{call}
+          \prelevel
+        \end{sdblock}
+
+        \begin{sdblock}{\textbf{Fitness Loop}}{(fitness $\neq$ 0) $\vee$ gen.limit}
+
+          \begin{sdblock}{\textbf{Evaluation Loop}}{p $\in$ pop}
+            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
+            \end{call}
+
+            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
+            \end{callself}
+            \prelevel
+          \end{sdblock}
+
+          \begin{sdblock}{\textbf{Crossover Loop}}{errors > 0}
+            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
+            \end{call}
+            \prelevel
+          \end{sdblock}
+
+          \begin{sdblock}{\textbf{Mutation Loop}}{errors > 0}
+            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
+            \end{call}
+            \prelevel
+          \end{sdblock}
+
+          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
+          \end{callself}
+          \prelevel
+        \end{sdblock}
+        \mess{server}{best fitness}{user}
+
+      \end{sdblock}
+    \end{call}
+  \end{sequencediagram}
+  \caption{The architecture of the test framework}
+  \label{fig.framework.architect} 
+\end{figure}
+
+Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
+We implemented such a framework as a client-server application which under the hood uses the genetic engine for test generation.
+The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
+The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
+\Server is the key component of the whole framework.
+It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}.
+Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
+
+Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactic correctness and reports back the set of identified errors.
+\Server rejects the document if any errors were revealed and generates a new one until the generated document has no errors anymore.
+\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
+We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate the native browser API calls.
+
+Let us give a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
+As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with the type signature.
+Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random data generation, genetic phase, logging etc.
+Experimentally, we have found an optimal set of input configurations that was used across all experimental objects in Section~\ref{sec.evaluation}.
+This data is processed by the \Server during the \emph{Initialization Phase}.
+As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{ifun}, and the signature (\emph{sig}).
+\Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
+Depends on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
+For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
+Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
+the limit on the number of generation attempts.
+Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
+It matches the candidate $p$ according to the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
+The execution trace along with some supplementary information about the execution are sent back to the \Server, where the final \emph{fitness value} is computed.
+The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
+If a new HTML document is produced somewhere in the genetic phase, it has to be first approved by the \Validator.
+At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
+Once all the branches are exercised, the algorithm reaches the end.
+In the follow up two sections, we elaborate on the details of each individual phase of our test generation framework.
+
+\subsection{Initialization Phase}
+\label{sub.sec.init.phase}
+
+\begin{algorithm}[t!]
+  \caption{Initialization Phase}
+  \label{alg.init}
+  \algsetup{linenosize=\tiny}
+  \scriptsize
+  \DontPrintSemicolon
+  \SetAlgoVlined
+  \SetKwInOut{Input}{Input}
+  \SetKwInOut{Output}{Output}
+  \SetKwInOut{Require}{Require}
+  \SetKwProg{Fn}{Function}{}{}
+  \Input{JS file $fun.js$ with FUT and type annotation }
+  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
+  \Fn{$Initialize(fun.js)$}{
+
+    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
+    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
+    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
+    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
+    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
+    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
+    \Return{$(cfg, branches, cinfo, ifun, sig)$}
+    }
+\end{algorithm}
+
+During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing.
+The main steps of this phase are illustrated by Algorithm~\ref{alg.init}.
+Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
+In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info.
+Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods:
+\begin{multicols}{2}
+\footnotesize
+\begin{itemize}
+\item \texttt{getElementsByTagName}
+\item \texttt{getElementById}
+\item \texttt{getElementsByClassName}
+\item \texttt{getElementsByName}
+\end{itemize}
+\end{multicols}
+which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT.
+Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
+transform \emph{if-then} branches into \emph{if-then-else}.
+We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants.
+Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure.
+Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
+
+\subsubsection{Supported Types}
+\label{sub.sec.sup.types}
+
+\begin{figure}[t]
+\setlength{\grammarparsep}{3pt}
+\small
+\begin{grammar}
+
+<JS Type Annotation> ::= /*t <Signature> */
+
+<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
+
+<DOM> ::= \texttt{dom}
+
+<Type Signature> ::= <Type> | <Type> : <Type Signature>
+
+<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
+
+<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
+
+<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
+\end{grammar}
+\caption{Grammar of supported JS type annotations}
+\label{fig.js.type.annot}
+\end{figure}
+
+The grammar of the JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
+Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
+We distinguish between two kinds of signatures those which refer to the global DOM and the ``ordinary'' JS type signatures.
+The functions of the former signature expect some \texttt{dom} argument to be passed as the first implicit parameter for the function call.
+Whereas ordinary JS signature is a non-zero sequence of the JS types.
+The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
+
+\subsubsection{Instrumentation}
+\label{sub.sec.instrument}
+
+Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
+The global variable \emph{trace} in line~\ref{isGameFinished.instr.trace} is an array of labels corresponding to the sequence of executed program statements.
+All statements have to be traced because each one, in theory, can rise an exception.
+The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations for the consecutive for-loop.
+If no exact bound can be computed, we set it to one.
+The \texttt{branchDistance} map tracks the distances to the deviated branches according to the translation formulae~\cite{tracey1998automated}.
+
+TODO: maybe expand this section with the JS type casting for branch distance computation
 
@@
 function isGameFinished() {
-  trace.push(2);
+ trace.push(2); |c \label{isGameFinished.instr.trace} |c
  var obj = document.getElementById("sudoku");
@@
  var allOk = true;
-  loopMap[5] = function () {
+ loopMap[5] = function () { |c \label{isGameFinished.instr.loopMap} |c
    var no = 0;
@@
  }();
+ trace.push(5);
  for (var no = 0; no < subDivs.length; no++) {
-    trace.push(5);
   trace.push(6);
@@
     label: 7,
-        distance: abs(subDivs[no].className.indexOf("sudokuSquare"), 0) +
+    distance: 
+     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + 
      absNegZero(subDivs[no].style.backgroundColor)
@@
  trace.push(5);
-  trace.push(16);
-  if (allOk) {
-    trace.push(17);
-    branchDistance.push({label: 16, distance: absNegZero(allOk)});
-    trace.push(18);
-    console.log("Congratulations! You did it");
-  } else {
-    trace.push(19);
-    branchDistance.push({label: 16 ,distance: absZero(allOk)});
-  }
  trace.push(-1);
@@
 \end{lstlisting}
-  \caption{Instrumented version of the function \texttt{isGameFinished.js} }
+  \caption{Instrumented version of \texttt{isGameFinished.js} }
   \label{code.isGameFinished.instr}
 \end{figure}
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<!-- T1 covers: (6,15), (16,17) -->
-<html>
-  <body>
-    <div id='sudoku'></div>
-</body>
-</html>
-
-<!-- T2 covers: (6,7), (7,14), (16,17) -->
-<html>
-  <body>
-    <div id='sudoku'>
-      <div></div>
-    </div>
-  </body>
-</html>
-
-<!-- T3 covers: (6,7), (7,9), (10,13), (16,17) -->
-<html>
-  <body>
-    <div id='sudoku'>
-      <div class='sudokuSquare'>
-        <span></span>
-        <span></span>
-      </div>
-    </div>
-  </body>
-</html>
-
-<!-- T4 covers: (6,7), (7,9), (10,11), (16,18) -->
-<html>
-  <body>
-    <div id='sudoku'>
-      <div class='sudokuSquare'>
-        <span></span>
-        <span>TEST</span>
-      </div>
-    </div>
-  </body>
-</html>
-  \end{lstlisting}
-  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
-  \label{fig.isGameFinished.tests}
-\end{figure}
-
-Let us consider JS function \texttt{isGameFinished} in Figure~\ref{code.newGame} taken from the web application game \emph{sudoku}~\ref{ref.sudoku}.
-This function checks if a sudoku solution entered by the user is valid.
-First, it finds the game field element (line~\ref{isGameFinished.getSudoku}), retrieves all child divs (line~\ref{isGameFinished.getDivs}), and iterates over that collection.
-Each div element which corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) consists of two span elements.
-One contains a user input, and another one, which is hidden at the moment, stores the expected value for the sudoku square.
-Once, it finds a square where two values are not equal (line~\ref{isGameFinished.if2.begin}) to each other, the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise (line~\ref{isGameFinished.finished}).
-
-Suppose now that we would like to (unit) test this function in isolation to the rest of the application source code.
-We aim to maximize branch coverage as a common testing criteria~\cite{why.this.common}.
-That is for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we have to construct a test input which passes the branch and normally exists the function.
-JS function has \emph{explicit} input arguments (none is our case), but it can also has \emph{implicit} arguments such as DOM state.
-As assume that DOM is the only global JS object that can be referred from the body of FUT.
-So in order to test our function we have to construct appropriate DOM objects as test inputs.
-
-%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
-
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together provide full coverage of the FUT.
-Let us look at how to construct the test that covers branch $(10,11)$.
-Line~\ref{isGameFinished.getSudoku} expects DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop on line~{isGameFinished.inFor.begin}, this element should have at least one child of the type $div$.
-The condition of the first $if$ (line~\ref{isGameFinished.if1.begin}) requires the div to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle and have no background color.
-The last if-condition (line~\ref{isGameFinished.if2.begin}) expects that the div has two \emph{span} elements whose \emph{innerHtml} values are not equal.
-$T4$ in Figure~\ref{fig.isGameFinished.tests} shows a concrete example of DOM that meets all the conditions above.
-
-As we have just seen even for such a relatively simple example, the construction of the test input is a far from trivial procedure because it requires deep understanding the program's semantics.
-In practice, web developers often have to deal with the gazillion of the JS frameworks and libraries freely available on the GitHub.
-This code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental and easiest to provide level of testing.
-It greatly saves developers from the unexpected regression and creates a safety belt around the application.
-
-%% --------------------------------------------------------------------
-\section{Test Generation Framework}
-\label{sec.framework}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t!]
-  \centering 
-  \begin{sequencediagram}[font=\footnotesize]
-
-    \renewcommand\unitfactor{0.5}
-    \newinst{user}{\textbf{User}}
-    \newinst{server}{\textbf{Server}}
-    \newinst[1]{validator}{\textbf{Validator}}
-    \newinst{client}{\textbf{Client}}
-
-    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
-      \end{call}
-
-      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
-      \end{call}
-
-      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
-      \end{call}
-
-      \begin{sdblock}{\textbf{Genetic Loop}}{\hspace{2mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{errors > 0}
-          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
-          \end{call}
-          \prelevel
-        \end{sdblock}
-
-        \begin{sdblock}{\textbf{Fitness Loop}}{(fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
-            \end{call}
-
-            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
-            \end{callself}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Crossover Loop}}{errors > 0}
-            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Mutation Loop}}{errors > 0}
-            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
-          \end{callself}
-          \prelevel
-        \end{sdblock}
-        \mess{server}{best fitness}{user}
-
-      \end{sdblock}
-    \end{call}
-  \end{sequencediagram}
-  \caption{Architecture of the test framework}
-  \label{fig.framework.architect} 
-\end{figure}
-
-Given JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
-We implemented such a framework as a client-server application which uses under the hood genetic test generation engine.
-The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-\Server is the key component of the whole framework.
-It is responsible for the \emph{Initialization Phase} and test data generation in the \emph{Genetic Phase}.
-Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactical correctness and reports back the set of identified errors.
-\Server rejects the document if any errors were revealed and repeats the current step until the generated document has no errors anymore.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate native browser API calls.
-
-Let us give a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input to our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random data generation, genetic phase, logging etc.
-Experimentally, we have found an optimal set of input configurations that was used across all the experimental subjects in Section~\ref{sec.evaluation}.
-The received data is processed by \Server during the \emph{Initialization Phase}.
-At the end of it we get the following information back: the control flow graph (\emph{cfg}) of \emph{fun}, the list of its branches (\emph{branches}), the \emph{fun}'s  constant (\emph{cinfo}) info, the instrumented version \emph{ifun} of \emph{fun}, and the \emph{fun}'s signature (\emph{sig}).
-\Server sends a \texttt{POST} request to the \Client to store there \emph{ifun} and \emph{sig}.
-Depending on the chosen execution mode, the \Server either asks the \User to select the target branch or covers all branches one by one in a fixed order.
-For each branch our framework enters the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve the population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
-the limit of generation attempts is reached.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate $p$ according the known type signature \emph{sig} and invokes the instrumented JS function \emph{ifun(p)}.
-The execution trace along with some collected information are sent back to the \Server, where the final fitness value is computed.
-The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-If an HTML document is produced during one the genetic phases, it has to be approved by the \Validator first.
-At the end of the \emph{Fitness Loop} the candidate with the ``best'' fitness value is reported back to the \User.
-Once all branches are exercised, the algorithm reaches the end.
-In the follow up two sections we elaborate on the details of each individual component of our test generation framework.
-
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
-
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
-During the \emph{Initialization Phase} we analyze FUN and collect data necessary for the consecutive genetic testing phase.
-The main steps of the initialization are illustrated in Algorithm~\ref{alg.init}.
-Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate in the genetic phase, we perform a static analysis of the FUT with the purpose to collect constant info in line~\ref{alg.init.collect.info}.
-Such constants include string and numeric literals as well as the arguments to the following DOM API methods:
-\begin{itemize}
-\item \texttt{getElementsByTagName}
-\item \texttt{getElementById}
-\item \texttt{getElementsByClassName}
-\item \texttt{getElementsByName}
-\end{itemize}
-which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} used in the FUT.
-Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-we need to transform \emph{if-then} branches into \emph{if-then-else}.
-We need to instrument the FUT (line~\ref{alg.init.instr}) in order be able to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants.
-Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure.
-The last two steps are to construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
-
-\subsubsection{Supported Types}
-\label{sub.sec.sup.types}
-
-\begin{figure}[t]
-\setlength{\grammarparsep}{3pt}
-\small
-\begin{grammar}
-
-<JS Type Annotation> ::= /*t <Signature> */
-
-<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
-
-<DOM> ::= \texttt{dom}
-
-<Type Signature> ::= <Type> | <Type> : <Type Signature>
-
-<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
-
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
-
-<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
-\end{grammar}
-\caption{Grammar of supported JS type annotations}
-\label{fig.js.type.annot}
-\end{figure}
-
-The grammar of JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature surrounded with a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish two between kinds of signatures those who refer to the global DOM and ``ordinary'' JS type signatures.
-Functions with a DOM signature expect a \texttt{dom} argument being passed as the first implicit parameter to the function call.
-Ordinary JS signature is a non-zero sequence of JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
 
@@
     $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
+    $historyConverged \longleftarrow true$\;
     \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
@@
 The heart of our test data generation framework is in the \emph{Genetic Phase}.
-The main workflow of the underlying genetic algorithm (GA) is, though, being fairly standard~\cite{poli2008field} but has been extended with the concept of \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-We get as an input a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and the tuple of parameters computed by Algorithm~\ref{alg.init}.
-The output consists of the ``best'' fitness score $f^*$ achieved on the population candidate $p^*$.
-
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: 
-%% \begin{itemize}
-%% \item $size_P$ is the size of the genetic population
-%% \item $size_A$ is the size of the genetic archive
-%% \item $size_G$ is the total number of the genetic iterations
-%% \item $rate_C$ is a crossover rate
-%% \item $rate_M$ is a mutation rate
-%% \item $size_H$ is a history window size
-%% \end{itemize}
-a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We set the initial target to $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ to 0 (line~\ref{alg.gen.iter.count}).
-Until the history of archives has not converged or the limit of the generations has not been reached, we are initializing the genetic search of the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}).
-An \emph{archive} stores the most fitted population candidates observed so far.
-It is empty in the beginning of the evolution (line~\ref{alg.gen.arch.init}) as well as the history of archives \emph{history} (line~\ref{alg.gen.init.history}).
-The first population of $size_P$ elements is randomly generated out of the constants taken from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-Then, in loop lines~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either the perfect candidate is found or the history of archives is converged or the generation limit $size_G$ is reached.
-But the first step in this loop is scoring the current population~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
-Each candidate of the population represents a concrete argument list of the FUT so it has to be coerced with respect to the type signature $sig$ (line~\ref{alg.gen.make.args}).
-After calling the instrumented function \emph{ifun} on $args$ (line~\ref{alg.gen.call.ifun}), we get 4-tuple consisting of an execution trace ($tr$), the sets of branch ($d_B$) and loop distances ($d_L$), and dynamic constant info (\emph{dyncinfo}) collected at the run-time.
-The next step is actually scoring the fitness value for the given population candidate (line~\ref{alg.gen.eval}).
-Collected constants \emph{dyncinfo} are merged with existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) and it is used for the crossover (line~\ref{alg.gen.cross}) and mutation steps (line~\ref{alg.gen.mut}).
-The rates specify the proportion in with two operation contribute the formation of the new population (line~\ref{alg.gen.new.pop}).
-The scored population together with the current archive are sorted by the fitness value, and the best $size_A$ elements form a new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}).
+Though, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, but has been extended with the concept of the \emph{archive convergence} (Algorithm~\ref{alg.gen}).
+As an input, we take a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
+The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
+
+First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
+We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ equal to 0 (line~\ref{alg.gen.iter.count}).
+We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged or the generations limit has not been reached.
+The \emph{archive} variable stores the most fitted population candidates observed so far, and the \emph{history} variables records all archives during the generation process.
+These variables both are empty in the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
+
+The initial population has $size_P$ elements, and it is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
+In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found or the history has converged or the generation limit $size_G$ has been reached.
+But first, we need to score the current population lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
+Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
+Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
+Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
+This gives us 4-tuple consisting of an execution trace ($tr$), branch ($d_B$) and loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
+The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
+Collected dynamic constants \emph{dyncinfo} are merged with the existing constant pool (line~\ref{alg.gen.eval.end}).
+Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}).
+And the $combo$ is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
+Then, the scored population together with the current archive are sorted by the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
+The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
 The fitness value of that element defines if a perfect candidate is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}).
-
-In some cases, when we do get enough guidance from the fitness function, the genetic algorithm converges to a local minimum~\cite{ga.flag.problem.or.survey}.
-For example, if one branch is dominated by another, the coverage of the former branch depends on the coverage of the latter.
-Unless this relation is captured by the branch condition on the former branch, the respective fitness function does not reflect on the branch dependency.
-In this situation, we find ourselves being trapped on a flat space, with a small unreliable chance to escape.
+Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
+
+In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{ga.flag.problem.or.survey}.
+For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
+Unless this relation is encoded in the fitness function somehow, we can not learn about it occasionally.
+In such situation, we find ourselves being trapped on a flat space, with a small unreliable chance to escape.
 In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives converge to a fixed point, we restart the genetic search and redefine the search target.
-At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we compute the convergence condition of the fitness values in the first $size_H$ archives taken from the history.
-If the fitness has converged (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new target.
-It consists of the original branch $b_n$ prefixed with a branch $b \in branches$ which our branch depends on (line~\ref{alg.gen.new.target}).
-Every time genetic search converges, we produce a new partial path by eventually covering all possible executions leading to $b_n$.
-In practice, we limit this process by the target of length two.
-
-In the rest of this section, we elaborate on the technical details of the genetic algorithm such as random generation in Section~\ref{sub.sub.sec.random.html}, mutation and crossover in Section~\ref{sub.sub.sec.genetic.oper}, and fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our primary focus in those sections will be on the generation and transformation of the HTML documents.
-Table~\ref{} descries how similar operations are implemented for primitive and array JS types.
+If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
+At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
+If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
+It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
+Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
+In practice, we only consider the target extensions upto the length of two.
+
+The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
+In the rest of this section, we reveal the implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
+Our main focus in those sections is on the generation and transformation of HTML documents.
 
 \begin{table}
-  \caption{Genetic Operation for JS types}
+  \caption{Genetic Operation for the JS Types}
   \label{tbl.gen.oper.js.types}
@@
     Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random & Int  & with 80\% probability choose an integer from [-10, 10], or with 20\% from integer constants\\
-    Random & Float & with 80\% probability choose an float from [-10.0, 10.0], or with 20\% from float constants\\
-    Random & String & with 80\% probability make a random string up to length five composed characters \texttt{[a-zA-Z0-9]}, or with 20\% from string constants\\
-    Random & Array & make a random array of a respective type upto length five\\
-    \hline
-    Crossover & Bool   & pick at random one out of two given boolean \\
+    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
+    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
+    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
+    Random    & Array  & array of a respective type upto length five\\
+    \hline
+    Crossover & Bool   & pick at random one out of two given booleans \\
     Crossover & Int    & pick at random one out of two given integers\\
     Crossover & Float  & pick at random one out of two given floats\\
-    Crossover & String & choose independently crossover point for each string, swap ends, and pick result at random\\
+    Crossover & String & pick at random one out of two single point crossovers\\
     Crossover & Array  & similar crossover operator as for strings\\
     \hline
-    Mutation & Bool & Flip the boolean constant\\
-    Mutation & Int  & Generate a new integer value, on increase (decrease) by 1 or 10 the given one\\
-    Mutation & Float  & Generate a new float value, on increase (decrease) by 0.1, 1 or 10 the given one\\
-    Mutation & String & Generate an new string values, remove a random character in a string, or replace a successor (predecessor) a random character\\
+    Mutation  & Bool   & flip the boolean constant\\
+    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
+    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
+    Mutation  & String & random string, remove char or apply pred(suc) char\\
     Mutation  & Array  & Mutate a random element in array according to its type\\
@@
 \label{sub.sub.sec.random.html}
-
-We want to generate HTML as it is specified by WHATWG\footnote{\url{https://html.spec.whatwg.org}}.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-Recent HTML5 standard defines more than hundred of tags and attributes which both have to comply with extremely complex logic to constitute a syntactically valid HTML.
-Browsers are usually tolerant to syntactic errors in HTML.
-They will silently fix them and display the page anyway.
-
-In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because, as we have mentioned early, the complexity of HTML and lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs the library\footnote{\url{https://hackage.haskell.org/package/QuickCheck}} to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} highlights that definition.
-Data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) describes the internal state of \texttt{Html} during generation.
-The state is composed of the following components:
-\begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify maximum depth and node degree of HTML respectively
-\item \texttt{ctx} is the current value of the HTML content model stack 
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are predefined sets of HTML elements which are given preference in the generation process.  
-\end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag should be defined as a value of type \texttt{GenHtmlState}.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} show an example of content generation for the \texttt{<html>} tag.
-According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
-First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
-Then, if depth is equal to zero, we just return some string constant (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we update the state with the depth decreased by one, generate new content for \texttt{head} and \texttt{body}, and return their combination (lines~\ref{ref.generateHTML.updateState}, \ref{ref.generateHTML.newHead}, \ref{ref.generateHTML.newBody} and \ref{ref.generateHTML.end} respectively).
 
@@
   \end{haskell}
-  \caption{\texttt{Arbitrary} instance for \texttt{Html} data type}
+  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
   \label{fig.html.arb.def}
@@
 
+We want to generate HTML according to the WHATWG\footnote{\url{https://html.spec.whatwg.org}} specification.
+HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
+The recent HTML5 standard defines more than hundred of tags and attributes which both have to comply with extremely complex logic to constitute a syntactically valid HTML.
+Browsers are usually tolerant to syntactic errors in HTML.
+They will silently fix them and display the page anyway.
+
+In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
+This was a challenge on its own because, as we have mentioned early, the complexity of HTML and the lack of formal specification.
+Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
+With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} highlights that definition.
+The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) describes the internal state of \texttt{Html} in the generation.
+The state is composed of the following components:
+\begin{itemize}
+\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of HTML 
+\item \texttt{ctx} is the current value of the HTML content model stack 
+\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
+\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
+\end{itemize}
+Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
+Each HTML tag should be defined as the value of the \texttt{GenHtmlState} type.
+Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
+According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
+First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
+Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
+Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the new contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
+
 \subsubsection{Genetic HTML Operations}
@@
 In essence, HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore crossover and mutations are defined similar to those concepts for the expression trees in genetic programming.
-
-\textbf{HTML Crossover} takes two HTML trees, randomly picks a node in each tree, and returns the first tree with a sub-tree swapped from the second tree.
-
-\textbf{HTML Mutations} are of three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
-\emph{NewTree} simply generate a new tree based on the given state of constant pool.
-\emph{DropTree} mutation selects a node in a tree and drops the sub-tree starting from that node.
-\emph{ShuffleAttributes} for a given tree and an attribute type, re-assigns the attributes of the specified type on that tree.
-Currently we instantiated the \emph{ShuffleAttributes} mutation for only for two types of attributes \emph{class} and \emph{id}, which gave us it total four variations for mutation.
-Each time a mutation is performed the type is chosen uniformly.
-In the future we consider experiment with assigning some priorities to curtain mutations.
+Therefore, the crossover and mutations are defined similar to those operators for the \emph{expression trees} in genetic programming.
+
+\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
+
+\textbf{HTML Mutations} are of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
+The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
+The \emph{DropTree} mutation removes the whole sub-tree at a randomly chosen node.
+\emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
+Currently, we instantiated the \emph{ShuffleAttributes} mutation for only for tho types \emph{class} and \emph{id}.
+In total, this gives us four mutations to chose from in order to evolve an Html document.
 
@@
 
-Success of any search-based algorithm heavily relies on the choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the program under test that we want to cover by generating a valid input data.
-The input is \emph{valid} only if the program normally terminates on it, i.e.
+The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
+Our search target is a specific branch of the function under test that we want to cover by generating a valid input data.
+The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
 without premature exception.
-Thus, our search target is an ordered pair of CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node of the program.
-FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and the normalized \emph{branch distance}\cite{arcuri2010does}.
+Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
+FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
 \[
-\mathcal{F}(n) = \text{Approach Level} + \alpha({\text{Branch Distance}})
+\textit{fit}(n) = \text{approach level} +
+\begin{cases}
+ 1/2 * (\frac{\text{branch distance}}{1 + \text{branch distance}}) & \text{if no exception}\\
+ 1                                  &  \text{otherwise}
+\end{cases}
 \]
-
-Therefore, the resulted FF ($\mathcal{F}^*$) is an ordered pair of the FFs of the respective nodes.
-
+Final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
 \[
-\mathcal{F}^*(n_b, n_x) = (\mathcal{F}(n_b), \mathcal{F}(n_x))
+\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
 \]
+Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
+ \[
+\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
+\]
+
+The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
+the node caused the deviation.
+Since any node can potentially be exceptional, they all contribute to the approach level in addition to the conditional branches.
+Loops have to treated in a special way because we need to estimate the maximum number of iterations.
+In the case of for-loop, at run-time we can always provide an exact bound.
+For while-loops, we assume that it has to be passed at least once.
+The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
 
@@
 
-In order to evaluate practical feasibility of the test framework adoption, we conducted an empirical validation on a set of case studies described in Section~\ref{sub.sec.case.studies}.
-All the experiments were performed in a batch mode on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of our JS testing framework each is based a slight variation of the underlying genetic search algorithm.
-The first version is \emph{Random} ($R$), i.e.
-instead of applying crossover and mutation we regenerate new population from scratch.
-It worth to notice, that random version also benefits from both preliminary static analysis phase and dynamic constant propagation during fitness evaluation step.
-The second version is \emph{Genetic} ($G$) and it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version ($G10$) is based on the genetic algorithm~\ref{alg.gen} where search is restarted after the archive is converged within a given history window, which is equal to 10 in our case.
-Initially, we experimented with two different window sizes 5 and 10.
-On one hand, a smaller window size forces the GA to converge fast and early discover a potential flat space.
-On the other hand, it sometimes causes a premature convergence by not letting the right genetic combination to be triggered.
-We experimentally concluded that the window size 10 works best for our examples and present the rest of the analysis based on that result.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three proposed test generation strategies.
-The choice of initial values is similar to other genetic testing frameworks, e.g.
+In order to evaluate the feasibility of our test framework adoption in practice, we conducted an empirical evaluation on a set of case-studies described in Section~\ref{sub.sec.case.studies}.
+All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
+We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
+The first version, which play the role of our baseline, is \emph{Random} ($R$).
+Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
+It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
+The second version is \emph{Genetic}~($G$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
+The last version is the \emph{Genetic with Restart} ($G10$).
+It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
+On one hand, the smaller window size forces the GA to converge faster and early discovers the stagnation on a flat space.
+On the other hand, the small window can lead to a premature archive convergence, which prevents the right genetic combination from been triggered.
+We have experimented with two different windows of size 5 and 10.
+But since the latter one ($G10$) showed the best performance over all, we chose it to report in the paper.
+Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
+The initial setup for genetic algorithm is similar to other frameworks, e.g.
 \emph{EvoSuite}~\cite{evosuite}.
@@
     Mutation rate                     & 0   & 0.5 & 0.5 \\
-    History window size               & 200 & -   & 10  \\
+    History window size               & -   & -   & 10  \\
     \bottomrule
@@
 Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-Being written with the help of countless number of specialized JS libraries, JS applications greatly vary in size, complexity and coding style.
+JS applications are written with the help of countless number of specialized libraries, and greatly vary in size, complexity and coding style.
 Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation.
-In order to choose suitable case-studies, we need to scrutinize the source code of the JS applications which is time consuming and labor intensive process.
+Before selection, the source code of a potential case-study has to be scrutinized which is time consuming and labor intensive process.
 Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
 Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-Since our testing framework is capable of dealing with the browserless imperative JS code as well, we introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}}.
+We introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}} to increase the presence of primitive (browserless) JS code.
 For each case-study application, we identified several JS functions that are suitable for our testing framework.
@@
 
-Table~\ref{tbl.case.studies} presents some common quantitative characteristics for the selected case-studies.
-For each function of a case-study we reported the following metrics\footnote{\url{http://jsmeter.info/} is the measurement tool}: lines of code (\textbf{\#LOC}), number of branches (\textbf{\#BR}), depth (\textbf{\#D}), cyclomatic complexity (\textbf{CC}), halstead volume (\textbf{HV}) and maintainability index (\textbf{MI}).
+Table~\ref{tbl.case.studies} presents common quantitative characteristics for the selected case-studies.
+For each function, we reported the following metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code (\textbf{\#LOC}), number of branches (\textbf{\#BR}), depth (\textbf{\#D}), cyclomatic complexity (\textbf{CC}), halstead volume (\textbf{HV}) and maintainability index (\textbf{MI}).
 The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
@@
 
+\subsection{Future Work}
+\label{sub.sec.fut.work}
+
+We would like to open source our test generation framework and introduce a web service allowing developers to submit their JS code for automated testing.
+One benefit of such service from the perspective of future research is an ability to learn about programming style and the use of JS libraries.
+Being dynamic language, JS supports various programming styles, which is, as was widely admitted~\cite{paper}, hindrance the complete analysis of JS programs.
+By gathering feedback about JS programs on which our framework performed poorly, we can identify and prioritize language constructs and programming patterns that should be adequately addressed.
+Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process:
+\begin{enumerate}
+\item ability to assign static types to input parameters 
+\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
+\item no support for recursion
+\item doesn't perform inter-procedural analysis
+\item no support for JS frameworks
+\item no reference to global variables and functions
+\item limited support of DOM API     
+\end{enumerate}
+
 \subsection{Limitations}
@@
 Our framework imposes certain constraints on the structure of JS programs:
-\begin{itemize}
-\item no inter-procedural function calls
-\item no recursion  
-\end{itemize}
 

### 2018-01-23 doc/icse2018/icse2018.tex
Continue working on the paper. Test for measuring the significance.

@@
   \centering 
-  \begin{sequencediagram}[font=\footnotesize]
-
-    \renewcommand\unitfactor{0.5}
+  \begin{sequencediagram}[font=\scriptsize]
+
+    \renewcommand\unitfactor{0.35}
     \newinst{user}{\textbf{User}}
@@
 
-      \begin{sdblock}{\textbf{Genetic Loop}}{\hspace{2mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{errors > 0}
+      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
+        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
           \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
@@
 
-        \begin{sdblock}{\textbf{Fitness Loop}}{(fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{p $\in$ pop}
+        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}
+
+          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
             \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
@@
 
-          \begin{sdblock}{\textbf{Crossover Loop}}{errors > 0}
+          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
             \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
@@
 
-          \begin{sdblock}{\textbf{Mutation Loop}}{errors > 0}
+          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
             \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
@@
 Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
-We implemented such a framework as a client-server application which under the hood uses the genetic engine for test generation.
+Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses the genetic engine for test generation.
 The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
@@
 In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info.
-Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods:
-\begin{multicols}{2}
-\footnotesize
-\begin{itemize}
-\item \texttt{getElementsByTagName}
-\item \texttt{getElementById}
-\item \texttt{getElementsByClassName}
-\item \texttt{getElementsByName}
-\end{itemize}
-\end{multicols}
+Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName},
 which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT.
@@
 
+By carrying the evaluation, we would like to address the following research questions:
+\begin{description}
+\item[\textbf{RQ1 (performance):}] What is the performance of our test generation framework?
+Is there any difference in performance on examples with DOM and without?
+Which algorithm works best random, genetic or genetic with restart?
+\item[\textbf{RQ2 (cost):}] What is the cost of one iteration of each algorithm?
+\item[\textbf{RQ3 (coverage):}] How does the branch coverage progress over time given a fixed budget per branch?
+\item[\textbf{RQ4 (significance):}] What is statistical significance and effect size of our experimental results? 
+\end{description}
+
 \subsection{Case Studies}
@@
 
-\begin{table*}[t]
+\setlength\tabcolsep{0.6pt}
+\begin{table}[t]
   \caption{Summary of the Case-Studies}
@@
     \scriptsize
-  \begin{tabular}{l|c|l|l|r|r|r|r|r|r|c|c|c|c}
+  \begin{tabular}{l|l|p{3.1cm}|c|c|c|c|c|c|c|c}
     \toprule
-    \textbf{case-study} & \textbf{?} & \textbf{function} & \textbf{type signature} & \textbf{\#LOC} & \textbf{\#BR} & \textbf{\#D} & \textbf{CC} & \textbf{HV} & \textbf{MI} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & + & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & 344 & 107.58 & + & + & + & - \\
-    sudoku     & + & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & 370 & 112.55 & + & + & + & + \\
-    sudoku     & + & newGame & (dom)           & 9  & 1 & 2 & 2 & 326 & 115.15 & + & + & + & + \\
-    sudoku     & + & revealAll & (dom)         & 8  & 0 & 2 & 1 & 312 & 117.44 & + & + & + & - \\
-    sudoku     & - & showCell & (dom)         & 8  & 0 & 0 & 1 & 232 & 118.46 & + & + & + & - \\
-    sudoku     & + & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & 555 & 97.9   & + & - & + & - \\
-    sudoku     & - & switchLevel & (dom,bool) & 10 & 1 & 2 & 2 & 257 & 114.26 & + & - & + & - \\
-    \hline
-    phormer    & + & toggleInfo & (dom,string)                                                      & 16 & 3 & 1 & 4 & 570  & 103.46 & + & + & - & - \\
-    phormer    & - & update & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) & 35 & 5 & 3 & 6 & 1190 & 87.804 & + & + & - & - \\
-    phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & 361  & 105    & + & + & - & - \\
-    \hline
-    hotel RS   & - & RequiredField & (dom,[string]) & 11 & 2 & 2 & 5 & 247  & 112.16 & + & + & - & - \\
-    hotel RS   & + & isValidCard & ([int])           & 17 & 2 & 2 & 5 & 351  & 103.91 & - & - & - & - \\
-    hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & 130  & 126.67 & - & - & - & - \\
-    hotel RS   & + & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & 104  & 124.71 & - & - & - & - \\
-    hotel RS   & - & validateNumber & (dom,string)  & 7  & 1 & 1 & 4 & 98.1 & 122.87 & + & + & - & - \\
-    \hline
-    apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & 242 & 114.1  & + & + & - & -\\
-    apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & 212 & 123.19 & + & + & - & - \\
-    apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & 539 & 104.70 & - & - & - & - \\
-    apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & 410 & 104.82 & + & + & - & - \\
-    apophis    & + & initShields & (dom,[int],int,int)                                               & 6  & 0 & 1 & 1 & 310 & 122.12 & + & + & - & -\\
-    \hline
-    bingbong   & + & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & 305  & 119.45 & + & + & - & - \\
-    bingbong   & + & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & 353  & 106.38 & + & + & - & - \\
-    bingbong   & + & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & 2380 & 72.594 & + & + & - & - \\
-    bingbong   & - & drawLevel & (dom,int,int,int,int)                       & 22 & 2  & 3 & 3  & 703  & 97.816 & + & + & - & - \\
-    bingbong   & - & goPing & (dom,int,int,int)                              & 12 & 2  & 2 & 3  & 268  & 110.93 & + & + & - & - \\
-    \hline
-    burncanvas & + & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & 583 & 86.214 & - & - & - & - \\
-    \hline
-    cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & 308 & 101.49 & -  & -  & - & - \\
-    cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & 309 & 101.38 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & + & prob\_gamma & (float)                                    & 57 & 8  & 2 & 16 & 1370 & 77.121 & - & - & - & - \\
+    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
+    \hline
+    sudoku     & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
+    sudoku     & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & + & + & + & + \\
+    sudoku     & newGame & (dom)           & 9  & 1 & 2 & 2 & + & + & + & + \\
+    sudoku     & revealAll & (dom)         & 8  & 0 & 2 & 1 & + & + & + & - \\
+    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
+    sudoku     & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & + & - & + & - \\
+    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
+    \hline
+    phormer    & toggleInfo & (dom,string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
+    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
+    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
+    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
+    \hline
+    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
+    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
+    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
+    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
+    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
+    \hline
+    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
+    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
+    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
+    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
+    apophis    & initShields & (dom,[int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
+    \hline
+    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
+    bingbong   & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
+    bingbong   & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
+    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
+    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
+    \hline
+    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
+    %% \hline
+    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
+    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
+    \hline
+    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
     \bottomrule
@@
 %}
-\end{table*}
-
-\subsection{Research Questions}
-\label{sub.sec.research.questions}
-
-\begin{description}
-\item[\textbf{RQ1:}] What is the performance of our test generation framework?
-Is there any difference in performance on examples with DOM and without?
-Which algorithm works best random, genetic or genetic with restart?
-\item[\textbf{RQ2:}] What is the cost of one iteration of each algorithm?
-\item[\textbf{RQ3:}] How does the branch coverage progress over time given a fixed budget per branch? 
-\end{description}
+\end{table}
 
@@
       \toprule
-      \multirow{2}{*}{\textbf{NAME}} & \multirow{2}{*}{\textbf{\#D}}         &  \multicolumn{3}{c|}{$m_r$} & \multicolumn{3}{c|}{$m_g$} & \multicolumn{3}{c|}{$m_{g10}$} & \multirow{2}{*}{$\frac{t_r}{t_g}$} &  \multirow{2}{*}{$\frac{t_r}{t_{g10}}$} & \multirow{2}{*}{$\frac{t_g}{t_{g10}}$}   & \multirow{2}{*}{$a_{rg}$} &  \multirow{2}{*}{$a_{rg10}$} & \multirow{2}{*}{$a_{gg10}$} \\
+      \multirow{2}{*}{\textbf{NAME}} & \multirow{2}{*}{\textbf{\#D}}         &  \multicolumn{3}{c|}{$m_r$} & \multicolumn{3}{c|}{$m_g$} & \multicolumn{3}{c|}{$m_{g10}$} & \multirow{2}{*}{$\frac{t_r}{t_g}$} &  \multirow{2}{*}{$\frac{t_r}{t_{g10}}$} & \multirow{2}{*}{$\frac{t_g}{t_{g10}}$}   & \multirow{2}{*}{r/g} &  \multirow{2}{*}{r/g10} & \multirow{2}{*}{g/g10} \\
       \cline{3-11}
@@
                                  & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$    & 1        & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & 0.57 & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$   & 2        & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & 0.46 & 0.5  & 0.53  \\
-    $(5,15,\elseBr)$  & 2        & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & 0.48  \\
-    $(9,10,\thenBr)$  & 3        & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & 0.40  \\
-    $(9,14,\elseBr)$  & 3        & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & 0.56 & 0.51 & 0.45  \\
+    $(3,4,\inFor)$    & 1        & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
+    $(5,6,\thenBr)$   & 2        & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
+    $(5,15,\elseBr)$  & 2        & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
+    $(9,10,\thenBr)$  & 3        & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
+    $(9,14,\elseBr)$  & 3        & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
     \hline                                                                                                          
@@
                                  & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$   & 2        & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & 0.6  & 0.66 & 0.43   \\
-    $(10,11,\thenBr)$ & 3        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & 0.48   \\
-    $(10,14,\elseBr)$ & 3        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & 0.55 & 0.55 & 0.46   \\
+    $(7,8,\thenBr)$   & 2        & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
+    $(10,11,\thenBr)$ & 3        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
+    $(10,14,\elseBr)$ & 3        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
     \hline
@@
                                  & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$   & 2        & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & 0.5  \\
+    $(6,7,\thenBr)$   & 2        & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
     \hline
@@
                                  & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$    & 1        & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & 0.45 & 0.39 &  0.43  \\
-    $(4,5,\inFor)$    & 2        & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & 0.55 &  0.37  \\
+    $(2,3,\inFor)$    & 1        & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
+    $(4,5,\inFor)$    & 2        & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
     \hline
@@
                                  & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & 0.58 & 0.53 & 0.46  \\
-    $(17,18,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & 0.46 & 0.47 & 0.5   \\
+    $(13,14,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
+    $(17,18,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
     \toprule
@@
                                  & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(2,3,\thenBr)$   & 1        & 2        & 2    & 1         & 2  & 2 & 1                 & 2 & 1   & 0.5                & 1     & 2     & 2     & 0.54 & 0.58 & 0.55  \\
-    $(6,7,\thenBr)$   & 1        & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & 0.48  \\
+    $(2,3,\thenBr)$   & 1        & 2        & 2    & 1         & 2  & 2 & 1                 & 2 & 1   & 0.5                & 1     & 2     & 2     & - & - & -  \\
+    $(6,7,\thenBr)$   & 1        & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
     \toprule
@@
                                  & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$   & 1        & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & 0.5   \\
-    $(7,8,\inFor)$    & 1        & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & 0.43  \\
-    $(10,11,\thenBr)$ & 2        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & 0.43  \\
-    $(10,13,\elseBr)$ & 2        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & 0.38  \\
-    $(14,15,\inFor)$  & 1        & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & 0.55  \\
+    $(3,6,\elseBr)$   & 1        & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
+    $(7,8,\inFor)$    & 1        & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
+    $(10,11,\thenBr)$ & 2        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
+    $(10,13,\elseBr)$ & 2        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
+    $(14,15,\inFor)$  & 1        & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
     \hline
@@
                                  & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$   & 1        & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & 0.59  \\
+    $(2,3,\thenBr)$   & 1        & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
     \toprule
@@
                                  & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$    & 1        & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & 0.53  \\
+    $(2,3,\inFor)$    & 1        & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
     \toprule
@@
                                  & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$   & 1        & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & 0.56  \\
+    $(2,3,\thenBr)$   & 1        & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
     \hline
@@
                                  & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$ & 1        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & 0.43 & 0.94 \\
+    $(10,11,\thenBr)$ & 1        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
     \hline
@@
                                  & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$   & 1        & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & 0.53 & 0.5  & 0.5   \\
-    $(6,10,\elseBr)$  & 1        & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & 0.4   \\
-    $(11,12,\thenBr)$ & 2        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & 0.41  \\
-    $(11,15,\elseBr)$ & 2        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & 0.47  \\
-    $(16,17,\thenBr)$ & 3        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & 0.45  \\
-    $(16,20,\elseBr)$ & 3        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & 0.46  \\
+    $(6,7,\thenBr)$   & 1        & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
+    $(6,10,\elseBr)$  & 1        & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
+    $(11,12,\thenBr)$ & 2        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
+    $(11,15,\elseBr)$ & 2        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
+    $(16,17,\thenBr)$ & 3        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
+    $(16,20,\elseBr)$ & 3        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
     $(21,22,\thenBr)$ & 4        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$ & 4        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & 0.42  \\
-    $(29,30,\thenBr)$ & 1        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & 0.5   \\
-    $(29,37,\elseBr)$ & 1        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.63 & 0.53 & 0.43  \\
-    $(38,39,\thenBr)$ & 2        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & 0.54  \\
-    $(38,46,\elseBr)$ & 2        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & 0.58 & 0.44  \\
-    $(47,48,\thenBr)$ & 3        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & 0.54  \\
-    $(47,55,\elseBr)$ & 3        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & 0.46  \\
-    $(56,57,\thenBr)$ & 4        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & 0.5   \\
-    $(56,64,\elseBr)$ & 4        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & 0.47  \\
-    $(69,70,\thenBr)$ & 1        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.48 & 0.51 & 0.53  \\
-    $(69,71,\elseBr)$ & 1        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & 0.57 & 0.68 & 0.61  \\
+    $(21,25,\elseBr)$ & 4        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
+    $(29,30,\thenBr)$ & 1        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
+    $(29,37,\elseBr)$ & 1        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
+    $(38,39,\thenBr)$ & 2        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
+    $(38,46,\elseBr)$ & 2        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
+    $(47,48,\thenBr)$ & 3        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
+    $(47,55,\elseBr)$ & 3        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
+    $(56,57,\thenBr)$ & 4        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
+    $(56,64,\elseBr)$ & 4        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
+    $(69,70,\thenBr)$ & 1        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
+    $(69,71,\elseBr)$ & 1        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
     \toprule
@@
                                  & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$   & 1        & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & 0.41 & 0.5  &  0.62 \\
-    $(8,9,\thenBr)$   & 2        & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  0.49 \\
-    $(8,11,\elseBr)$  & 2        & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  0.46 \\
-    $(44,45,\thenBr)$ & 1        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & 0.58 &  0.89 \\
-    $(48,49,\thenBr)$ & 1        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & 0.4  &  0.74 \\
+    $(6,7,\thenBr)$   & 1        & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
+    $(8,9,\thenBr)$   & 2        & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
+    $(8,11,\elseBr)$  & 2        & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
+    $(44,45,\thenBr)$ & 1        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
+    $(48,49,\thenBr)$ & 1        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
     \toprule
@@
                                  & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$   & 1        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  0.47  \\
-    $(6,7,\thenBr)$   & 2        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  0.51  \\
-    $(6,9,\elseBr)$   & 2        & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  0.49  \\
-    $(10,11,\thenBr)$ & 2        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  0.62  \\
-    $(10,13,\elseBr)$ & 2        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  0.57  \\
-    $(16,17,\inWhile)$& 2        & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  0.53  \\
-    $(20,21,\thenBr)$ & 2        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 & 0.48   \\
-    $(20,23,\elseBr)$ & 2        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  0.49  \\
-    $(30,31,\thenBr)$ & 1        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  0.58  \\
-    $(34,35,\thenBr)$ & 1        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  0.51  \\
+    $(4,5,\thenBr)$   & 1        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
+    $(6,7,\thenBr)$   & 2        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
+    $(6,9,\elseBr)$   & 2        & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
+    $(10,11,\thenBr)$ & 2        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
+    $(10,13,\elseBr)$ & 2        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
+    $(16,17,\inWhile)$& 2        & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
+    $(20,21,\thenBr)$ & 2        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
+    $(20,23,\elseBr)$ & 2        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
+    $(30,31,\thenBr)$ & 1        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
+    $(34,35,\thenBr)$ & 1        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
     \bottomrule
@@
 But when the budget rises to 30 seconds, $G10$ starts to transcend $G$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).
+
+\paragraph{\textbf{RQ4 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} our the performance results.
+This analysis is based on the coverage time in 50 executions, produced by each test algorithm $R$, $G$ and $G10$.
+Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
+In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values, where it was significant (otherwise '-'), for all three pairs of the test algorithm: $R$ against $G$ ($r/g$), $R$ against $G10$ ($r/g10$), and $G$ against $G10$ ($g/g10$).
+Depends on the actually exceeded value, the effect size can be small (0.56), medium (0.64), and large (0.71).
+Both genetic versions ($G$ and $G10$) outperform random ($R$) with the large (medium and small) effect in 33 (37 and 39) subjects, respectively, out of total 57.
 
@@
 
+Multi-objective test suite generation. DOM reduction by means of hierarchical delta-debugging.
+
 \subsection{Limitations}

### 2018-01-23 python/analysis.py

@@ -1,6 +1,7 @@
 #!/usr/bin/python
 
 import pandas as pd
+from scipy.stats import mstats
 from glob import glob
 
 
@@ -37,8 +38,22 @@ def mk_a12_df(df1, df2):
     for index, row in df1.iterrows():
         a12.append(a12slow(df1.iloc[index], df2.iloc[index]))
     a12_df = pd.DataFrame(a12, columns=['a12'])
-    print(a12_df)
     return a12_df
+
+def mk_kruskal(df1, df2):
+    kruskal = []
+    for index, row in df1.iterrows():
+        if df1.iloc[index].isnull().values.any():
+            pval = 0
+        else:
+            if (df1.iloc[index].values == df2.iloc[index].values).all():
+                pval = 0
+            else:
+                args = [df1.iloc[index].values, df2.iloc[index].values]
+                pval = mstats.mannwhitneyu(*args).pvalue
+        kruskal.append(pval)
+    kruskal_df = pd.DataFrame(kruskal, columns=['kruskal'])
+    return kruskal_df
 
 
 def generateExcelReport(cs_name,
@@ -60,24 +75,31 @@ def generateExcelReport(cs_name,
     gg10_df = mk_a12_df(mgenetic_df, mgenetic_converge10_df)
     g5g10_df = mk_a12_df(mgenetic_converge5_df, mgenetic_converge10_df)
 
-    concat_result = pd.concat([genetic_df,
-                               genetic_converge5_df,
+    kruskal_rg   = mk_kruskal(mrandom_df, mgenetic_df)
+    kruskal_rg10 = mk_kruskal(mrandom_df, mgenetic_converge10_df)
+    kruskal_gg10 = mk_kruskal(mgenetic_df, mgenetic_converge10_df)
+
+    concat_result = pd.concat([random_df,
+                               genetic_df,
                                genetic_converge10_df,
-                               genetic_converge20_df,
-                               random_df,
-                               rg_df, rg5_df, rg10_df, gg5_df, gg10_df, g5g10_df],
+                               rg_df,
+                               rg10_df,
+                               gg10_df,
+                               kruskal_rg,
+                               kruskal_rg10,
+                               kruskal_gg10],
                               axis=1)
-    headers = ['gbrunch',
+    headers = ['rbrunch',
+               'rmean',
+               'rmax',
+               'rmin',
+               'rmedian',
+
+               'gbrunch',
                'gmean',
                'gmax',
                'gmin',
                'gmedian',
-
-               'g5brunch',
[…]

### 2018-01-25 doc/icse2018/icse2018.tex
Completed RQ1

@@
-\documentclass[sigconf]{acmart}
-
+\documentclass[sigconf,review, anonymous]{acmart}
+
+\usepackage{tablefootnote}
 \usepackage{syntax}
@@
 \usepackage{xspace}
+\usepackage{mdframed}
 \usepackage{algorithmic}
@@
 \newcommand{\un}[1]{\underline{#1}}
+\newcommand{\Random}{\mathbb{R}}
+\newcommand{\Genetic}{\mathbb{G}}
+\newcommand{\RGenetic}{\mathbb{G}_{10}}
 
@@
 %Conference
-\acmConference[ISSTA'18]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{July 2018}{Amsterdam, The Netherlands} 
+\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
 \acmYear{1997}
@@
 \affiliation{%
-  \institution{Utrecht University}
-  \city{Utrecht} 
-  \country{The Netherlands} 
+  \institution{Utrecht University, The Netherlands} 
 }
@@
 \affiliation{%
-  \institution{Utrecht University}
-  \city{Utrecht} 
-  \country{The Netherlands} 
+  \institution{Utrecht University, The Netherlands}
 }
@@
 \affiliation{%
-  \institution{Utrecht University}
-  \city{Utrecht} 
+  \institution{Utrecht University, The Netherlands}
   \country{The Netherlands} 
@@
 data HtmlState = |c \label{ref.HtmlState.begin} |c
-  HtmlState { depth      :: Int 
-             , degree    :: Int    
-             , ctx       :: Stack Context 
-             , tagFreq   :: [(Int, Tag)] 
-             , tags      :: [Tag]
-             , ids       :: [String]
+  HtmlState { depth    :: Int,           degree  :: Int    
+             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
+             , tags    :: [Tag],         ids     :: [String]
              , classes :: [String] } |c \label{ref.HtmlState.end} |c
@@
     \toprule
-    \textbf{Parameter Name} & \textbf{R} & \textbf{G} & \textbf{G10} \\
+    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
     \hline
@@
 
-Table~\ref{tbl.case.studies} presents common quantitative characteristics for the selected case-studies.
-For each function, we reported the following metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code (\textbf{\#LOC}), number of branches (\textbf{\#BR}), depth (\textbf{\#D}), cyclomatic complexity (\textbf{CC}), halstead volume (\textbf{HV}) and maintainability index (\textbf{MI}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
+For the sake of space, we chose to exclude from the follow up presentation the branches and functions which coverage time was less than two seconds.
+In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
+This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
+For each function, we reported the following software metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
+The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
+To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the aforementioned case studies with the results presented in Section~\ref{sub.sec.eval.results}.
 
@@
 
-\setlength\tabcolsep{0.8pt}
+\setlength\tabcolsep{.98pt}
 \begin{table}[!t]
-  \caption{Performance statistics of branch coverage (in seconds) for four variations of the JS test generation framework}
+  \caption{Branch coverage statistics for three variations of the JS test generation framework}
   \label{tbl.stats}
     \scriptsize
-    \begin{tabular}{lc|ccc|ccc|ccc|ccc|ccc}
+    \begin{tabular}{l|rrr|rrr|rrr|rrr|rrr}
       \toprule
-      \multirow{2}{*}{\textbf{NAME}} & \multirow{2}{*}{\textbf{\#D}}         &  \multicolumn{3}{c|}{$m_r$} & \multicolumn{3}{c|}{$m_g$} & \multicolumn{3}{c|}{$m_{g10}$} & \multirow{2}{*}{$\frac{t_r}{t_g}$} &  \multirow{2}{*}{$\frac{t_r}{t_{g10}}$} & \multirow{2}{*}{$\frac{t_g}{t_{g10}}$}   & \multirow{2}{*}{r/g} &  \multirow{2}{*}{r/g10} & \multirow{2}{*}{g/g10} \\
-      \cline{3-11}
-            &                & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \toprule
-    \multicolumn{2}{l|}{\textbf{helpMe}*}     
-                                 & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$    & 1        & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$   & 2        & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$  & 2        & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$  & 3        & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$  & 3        & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-\multicolumn{2}{l|}{\textbf{isGameFinished}*} 
-                                 & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$   & 2        & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$ & 3        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$ & 3        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \multicolumn{2}{l|}{\textbf{newGame}*}   
+      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
+      \cline{2-10} % \!:\!
+                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
+      \midrule
+    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
+    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
+    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
+    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
+    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
+    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
+    \hline                                                                                                          
+    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
+    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
+    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
+    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
+    \hline
+    \textbf{newGame}*   
                              & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$   & 2        & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \multicolumn{2}{l|}{\textbf{revealAll}*}  
+    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
+    \hline
+    \textbf{revealAll}*  
                              & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$    & 1        & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$    & 2        & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-\multicolumn{2}{l|}{\textbf{shuffleBoard}*}   
+    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
+    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
+    \hline
+    \textbf{shuffleBoard}*   
                              & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$ & 3        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \toprule
-\multicolumn{2}{l|}{\textbf{toggleInfo}*}     
-                                 & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(2,3,\thenBr)$   & 1        & 2        & 2    & 1         & 2  & 2 & 1                 & 2 & 1   & 0.5                & 1     & 2     & 2     & - & - & -  \\
-    $(6,7,\thenBr)$   & 1        & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \toprule
-\multicolumn{2}{l|}{\textbf{isValidCard}}        
-                                 & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$   & 1        & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$    & 1        & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$ & 2        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$ & 2        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$  & 1        & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-\multicolumn{2}{l|}{\textbf{isValidVISA}}        
-                                 & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$   & 1        & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \toprule
-\multicolumn{2}{l|}{\textbf{initShields}*}    
-                                 & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$    & 1        & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \toprule
-\multicolumn{2}{l|}{\textbf{brickJiggler}*}   
-                                 & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$   & 1        & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-\multicolumn{2}{l|}{\textbf{doPaddlePower}*}  
-                                 & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$ & 1        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-    \hline
-\multicolumn{2}{l|}{\textbf{initBricks}*}     
-                                 & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$   & 1        & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$  & 1        & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$ & 2        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$ & 2        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$ & 3        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$ & 3        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$ & 4        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$ & 4        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$ & 1        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$ & 1        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$ & 2        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$ & 2        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$ & 3        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$ & 3        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$ & 4        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$ & 4        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$ & 1        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$ & 1        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \toprule
-    \multicolumn{2}{l|}{\textbf{do\_draw}}       
-                                 & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$   & 1        & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$   & 2        & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$  & 2        & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$ & 1        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$ & 1        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \toprule
-\multicolumn{2}{l|}{\textbf{prob\_gamma}}        
-                                 & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$   & 1        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$   & 2        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$   & 2        & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$ & 2        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$ & 2        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$& 2        & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$ & 2        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$ & 2        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$ & 1        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$ & 1        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
+    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
+    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
+    \hline
+   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
+    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
+    \hline
+   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
+    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
+    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
+    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
+    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
+    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
+    \hline
+   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
+    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
+    \hline
+   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
+    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
+    \hline
+   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
+    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
+    \hline
+   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
+    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
+    \hline
+   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
+    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
+    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
+    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
+    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
+    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
+    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
+    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
+    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
+    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
+    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
+    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
+    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
+    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
+    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
+    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
+    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
+    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
+    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
+    \hline
+    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
+    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
+    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
+    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
+    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
+    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
+    \hline
+    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
+    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
+    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
+    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
+    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
+    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
+    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
+    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
+    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
+    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
+    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
+    \midrule
+    \textbf{TOTAL} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
     \bottomrule
@@
 
-\paragraph{\textbf{RQ1 (performance).}} We would like to study the performance of the three variations of the testing framework: Random ($R$), Genetic ($G$) and Genetic with Restart ($G10$).
-To address this question, we applied our framework to all branches of each function in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments has to be repeated 50 times to get statistically significant results.
-Our discussion completely excludes some functions in Table~\ref{tbl.case.studies} ($-$ sign in the $?$ column) as not presenting real challenge.
-Despite of it apparent complexity, like the function \emph{update}, in practice both random and genetic testing strategies take maximum upto two seconds to cover each branch.
-This gave us in total 14 functions, for which we present summary of performance statistics in Table~\ref{tbl.stats} for all three testing strategy.
-For the sake of space, we omitted from that table the branches whose average coverage time was less than one second.
-Functions suffixed with the start (*) symbol indicate reference to DOM.
-Column $D$ next to the branch shows its depth.
-We computed the following medians for each algorithm: the number of iterations ($i$), time in seconds ($t$), and their ratio ($t/i$).
-In the table, these values are grouped into three columns $m_r$, $m_g$ and $m_{g10}$, one per algorithm type $R$, $G$ and $G5$  respectively.
-Next group of columns $t_r/t_g$, $t_r/t_{g10}$ and $t_g/t_{g10}$ measures the relative performance of each pair of the testing strategies $(R,G)$, $(R,G10)$, and $(G,G10)$ respectively.
-
-The fact that the median of generation reached the upper limit of \underline{200} means the branch was never covered.
-With that budget in mind not all algorithms were always performing successfully.
-The main reason for the random generation to fail, e.g.
-the \emph{(10,11,then)} branch of the \emph{isGameFinished} function or any branch of the \emph{isValidCard} function, is the huge size of the search space and complete absence of any guidance.
-On the contrary, the genetic search may stuck on a flat space when the fitness function does not carry any information how to get out it, e.g.
-the branches \emph{(10,11,then)}, \emph{(40,48,then)} and \emph{(40,45,then)} of the functions \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw} respectively.
-(say why random give better performance in that case) Those examples motivated us to introduce the genetic algorithm with restart ($G5$), which is as our evaluation demonstrated not only provided a solution within given budget, but also outperformed random search.
-(Maybe discuss examples where $R$ outperformed $G5$)
-
-Table~\ref{tbl.stats} also shows accumulated statistics for each function as a whole (row in line with the function name).
-This gives us a way to compare  all three testing strategies with each other at the function level.
-Chart in Figure~\ref{fig.gen.time.comp} clearly illustrates how the median time varies per function for each algorithm.
-Across all 14 examples $G10$ indicated the best performance comparing to both $R$ and $G$.
-We observed only two cases (\emph{revealAll}) and (\emph{doPaddlePower}) where random testing gave a slightly better result by only 6\%.
-If we take in consideration only examples with the average execution time above 50 seconds, we can conclude that $G10$ was minimum 1.87 time (\emph{do_draw}) and maximum 51.4 (\emph{isValidCard}) time faster than $R$.
-At the same time, even plain genetic algorithm $G$ outperforms the random one $R$ in all examples except of two \emph{doPaddlePower} and \emph{initBricks} due to the reasons discussed early in this section.
-In cases of success, especially for some small examples such as \emph{newGame} and \emph{isValidCard}, the genetic algorithm was even able to beat $G5$ by upto 30\%.
-
-\paragraph{\textbf{RQ2 (cost).}} The cost (time) of one iteration is defined as the relation between the execution time and the number of generations, i.e.
-$t/i$ in Table~\ref{tbl.stats}.
-Figure~\ref{fig.get.cost} shows the cost comparison of various algorithms across all case-studies.
-The execution time of one iteration depends on the population size, in case 50 candidates.
-Evaluation of a candidate results in an execution trace of a varying length.
-The length of an execution trace positively correlates with the computation cost of the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-The \emph{do_draw} examples illustrates the latter case, it consists of 40 LOC and operates only with primitive type which do not case any exception.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.38 seconds.
-
-TODO: discuss why cost of one genetic iteration for \emph{do_draw} is higher than random.
-
-TODO: discuss if costs of $R$, $G$ and $G5$ vary between each other and why.
-
-\paragraph{\textbf{RQ3 (coverage).}} In this research question we want to compare how coverage progresses with the increase of budget assigned per branch.
-We chose the following budget categories: 5, 10, 30 etc.
-up to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $G$ and $G10$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $G$ slightly outperforms $G10$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $G10$ starts to transcend $G$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).
-
-\paragraph{\textbf{RQ4 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $R$, $G$ and $G10$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values, where it was significant (otherwise '-'), for all three pairs of the test algorithm: $R$ against $G$ ($r/g$), $R$ against $G10$ ($r/g10$), and $G$ against $G10$ ($g/g10$).
-Depends on the actually exceeded value, the effect size can be small (0.56), medium (0.64), and large (0.71).
-Both genetic versions ($G$ and $G10$) outperform random ($R$) with the large (medium and small) effect in 33 (37 and 39) subjects, respectively, out of total 57.
+\paragraph{\textbf{RQ1 (performance).}} First, we would like to study the performance of our test generation framework, including three test algorithms: Random ($\Random$), Genetic ($\Genetic$) and Genetic with Restart ($\RGenetic$).
+To address this question, we ran each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
+Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
+%% Functions suffixed with the start (*) symbol indicate reference to DOM.  Column $D$ next to the branch shows its depth. 
+Table~\ref{tbl.stats} contains results of our evaluation.
+For each algorithm, we computed the following median values per branch: the number of iterations ($i$), time in seconds ($t$), and their ratio ($t/i$).
+In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ according to the algorithm type $\Random$, $\Genetic$ and $\RGenetic$.
+Next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
+Inline with the function name, we also present accumulated statistics for the function as a whole.
+Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
+see the \emph{toggleInfo} function.
+At the bottom of the table, we included accumulated data throughout all functions.
+Let us structure the performance discussion according the three levels of abstraction total, function, and branch.
+
+Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
+That is, the underlined values in Table~\ref{tbl.stats}  ($\underline{200}$) indicate branches, which on average were not covered by the respective algorithms.
+The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
+branch $(10,11)$ of the \emph{isGameFinished} function.
+In the case of genetic approach~($\Genetic$), it may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
+We encountered three of such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
+Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines strengths of both algorithms genetic and random.
+It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness converges.
+As our evaluation has shown, $\RGenetic$ not only manged to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
+branch $(69,71)$ of the \emph{do_draw} function.
+
+Figure~\ref{fig.gen.time.branch} shows average generation time per branch for each algorithm.
+It took maximum upto 26.5 seconds for $\RGenetic$ to cover a branch.
+This upper bound may service as a rough estimate defining budget for testing a new function with our framework using $\RGenetic$.
+
+%% \setlength{\fboxsep}{2mm}
+%% \fbox{%
+%%   \parbox{8cm}{
+%%     Three testing strategies $\Random$, $\Genetic$ and $\RGenetic$ covered respectively 63\%, 95\% and 100\% of branches.
+%%   }
+%% }
+
+%% TODO: Maybe discuss examples where $\Random$ outperformed $\RGenetic$
+%% TODO: consider further branch discrimination
 
@@
       \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
-      \legend{R,G,G10}
+      \legend{$\Random$,$\Genetic$,$\RGenetic$}
     \end{axis}
@@
 
-% \input{summary_statistics}
+The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at a function level.
+There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%; and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
+In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
+According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are easy to test, and above 10 present a reasonable challenge.
+Three functions at the bottom of Table~\ref{tbl.case.studies}, \emph{initBricks}, \emph{do_daw} and \emph{prob_gamma} with the respective CC 13, 14 and 16 are of the latter category.
+Because of they complexity, they are recommended to test, but test construction, especially manual, can be difficult.
+For those functions, $\RGenetic$ managed to provide complete coverage, where other two algorithms failed, and did it in a shortest time.
+
+In total, $\RGenetic$ outperformed $\Random$ and $\Genetic$ by 4.66 and 2.05 times, respectively; and $\Genetic$ outperformed $\Random$ by 2.27 times.
+Moreover, $\RGenetic$ was not only the fastest, but also the most effective algorithm reaching 100\% of branch coverage, with $\Genetic$ coming second 95\%, and $\Random$ third 63\%.
+On average, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
+
+\begin{figure}[t]
+  \begin{tikzpicture}[scale=0.8]
+    \begin{axis}[
+        every axis plot post/.style={/pgf/number format/fixed},
+        ybar,
+        ymin=0,ymax=135,
+        width=11cm,height=3.3cm,
+        bar width=3pt,
+        enlarge x limits=0.05,
+        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
+        legend cell align={left},
+        ylabel={time (sec.)},
+        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
+        xtick=data,
+        nodes near coords,
+        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
+        % every node near coord/.append style={font=\footnotesize},
+        axis lines*=left,
+        clip=false,
+        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
+        y tick label style={font=\footnotesize}
+      ]
+      \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
+
+      \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
+
+      \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
+      \legend{$\Random$,$\Genetic$,$\RGenetic$}
+    \end{axis}
+  \end{tikzpicture}
+  \caption{Average generation time per branch}
+    \label{fig.gen.time.branch}
+\end{figure}
+
+\paragraph{\textbf{RQ2 (cost).}} This question is supposed to shed some light on the cost of one iteration of our framework.
+This information is useful when setting up the maximal generation limit.
+The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
+it measures time of one iteration.
+Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
+On one hand, the cost of one iteration depends on the population size, in our case 50 candidates.
+On the other hand, the cost also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
+....
+Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
+The \emph{do_draw} examples illustrates the latter case, it consists of 40 LOC and operates only with primitive type which do not case any exception.
+In our evaluation we observed that the iteration cost varied between 0.25 and 3.38 seconds.
 
@@
       \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
-      \legend{R,G,G10}
+      \legend{$\Random$,$\Genetic$,$\RGenetic$}
     \end{axis}
@@
 
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=135,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-      \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-      \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-      \legend{R,G,G10}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Average generation time per branch}
-    \label{fig:1}
-\end{figure}
+TODO: discuss why cost of one genetic iteration for \emph{do_draw} is higher than random.
+
+TODO: discuss if costs of $R$, $G$ and $G5$ vary between each other and why.
+
+\paragraph{\textbf{RQ3 (coverage).}} In this research question we want to compare how coverage progresses with the increase of budget assigned per branch.
+We chose the following budget categories: 5, 10, 30 etc.
+up to 150 seconds per branch.
+Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
+Eventually, it converges around 52\% coverage.
+Given 5 seconds per branch, both $G$ and $G10$ equally perform at the rate of 45\%.
+When the budget increases towards 10 seconds, $G$ slightly outperforms $G10$, 60\% against 63\% respectively.
+But when the budget rises to 30 seconds, $G10$ starts to transcend $G$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).
 
@@
       };
-      \legend{R,G,G10}
+      \legend{$\Random$,$\Genetic$,$\RGenetic$}
 
@@
 \end{figure}
+
+\paragraph{\textbf{RQ4 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} our the performance results.
+This analysis is based on the coverage time in 50 executions, produced by each test algorithm $R$, $G$ and $G10$.
+Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
+In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values, where it was significant (otherwise '-'), for all three pairs of the test algorithm: $R$ against $G$ ($r/g$), $R$ against $G10$ ($r/g10$), and $G$ against $G10$ ($g/g10$).
+Depends on the actually exceeded value, the effect size can be small (0.56), medium (0.64), and large (0.71).
+Both genetic versions ($G$ and $G10$) outperform random ($R$) with the large (medium and small) effect in 33 (37 and 39) subjects, respectively, out of total 57.
+
+% \input{summary_statistics}
 

### 2018-01-27 doc/icse2018/icse2018.tex
Finished introduction

@@
-\documentclass[sigconf,review, anonymous]{acmart}
+\documentclass[sigconf,review,anonymous]{acmart}
 
@@
 % Copyright
-%\setcopyright{none}
+\setcopyright{none}
 %\setcopyright{acmcopyright}
 %\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
+%\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
 % DOI
-\acmDOI{10.475/123_4}
+%\acmDOI{10.475/123_4}
 
 % ISBN
-\acmISBN{123-4567-24-567/08/06}
+%\acmISBN{123-4567-24-567/08/06}
 
@@
 \acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-\acmYear{1997}
-\copyrightyear{2016}
-
-\acmPrice{15.00}
+%% \acmYear{1997}                  
+%% \copyrightyear{2016}
+
+%% \acmPrice{15.00}
 
@@
 \title{Search-Based Test Data Generation for JavaScript Functions with DOM}
-
-%% \author{
-%%   \alignauthor Alexander Elyasov, Wishnu Prasetya, Jurriaan Hage\\ 
-%%   \affaddr{Utrecht University, The Netherlands}\\
-%%   \email{\{a.elyasov,s.w.b.prasetya,j.hage\}@uu.nl}
-%% }
 
@@
 \begin{abstract}
-As of 2017 JavaScript language and Node.js platform continues to stay the most prevalent technologies voted by the developers in Stack Overflow survey. At the same time  
+As of 2017 JavaScript and Node.js continue to stay the most prevalent technologies according to the Stack Overflow developers survey.
+Nevertheless, existing JS testing frameworks are still lacking any support for such a vital step in test automation as the generation of input data.
+To address this problem, we present a novel \textbf{J}avascript \textbf{E}volutionary-based testing framework with \textbf{D}OM as an \textbf{I}input, called \textbf{JEDI}.
+In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state.
+The \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage in our empirical evaluation with the average execution time 7.7 sec.
+per branch
 \end{abstract}
@@
 \begin{CCSXML}
-TODO 
+<ccs2012>
+<concept>
+<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
+<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011074.10011784</concept_id>
+<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
 \end{CCSXML}
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\ccsdesc[300]{Software and its engineering~Software testing and debugging}
+\ccsdesc[300]{Software and its engineering~Search-based software engineering}
+
+\keywords{JavaScript, search-based testing, branch coverage}
 
@@
 
-According to the Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the firth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
+According to a Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the fifth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
 It is used through all technology stack web, back-ends and mobile.
-Such a tremendous ever increasing JS success is happening thanks to extensive dynamic features of the language, JS permissiveness and native browser support.
-On the contrary, JS applications are error-prone~\cite{why}, hard to analyze~\cite{why} and test~\cite{why}.
-Therefore, it is not surprising that year over year we hear new stories\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}} about another critical bug being found in a web application by Facebook, Twitter etc.
+Such a tremendous ever increasing JS success is happening thanks to the extensive dynamic features of the language, JS permissiveness and native browser support.
+On the other hand, JS applications are error-prone~\cite{why}, hard to analyze~\cite{why} and test~\cite{why}.
+Therefore, it is not surprising that year after year we hear new stories\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}} about another critical bug being found in a web application by Facebook, Twitter etc.
 
@@
 
-The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit among the most used ones in the decreasing order of popularity.
-These frameworks support testing at different levels unit, integration and functional.
-The same survey also indicated relatively low satisfaction rate of the current state of JS testing tools, only 3.2 out of 5.
+The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
+These frameworks support testing at various levels: unit, integration and functional.
+The survey also indicated relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
 As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite of this effort, test data generation stays a missing component not being properly addressed by any of the widely used testing frameworks.
-Research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-Recent study of client-side JS bugs~\cite{ocariza2017study} has shown that majority (68\%) of JS faults are DOM-related and occur in JS code itself.
+But despite of this effort, test data generation continues to be not properly addressed by any of the widely used testing frameworks.
+The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
+A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of JS faults are DOM-related and occur in JS code, and not in HTML or CSS.
 This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
@@
 Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{paper}.
-In the recent years, some effort was done to apply search-based testing for dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been implemented for JavaScript.
-This circumstance motivated us to introduce a search-based test generation framework for JS with presence of DOM.
+In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript.
 Our work makes the following contributions:
 \begin{enumerate}
-\item JS search-based testing framework
-\item random HTML generation
-\item genetic with restart algorithm
-\item empirical evaluation 
+\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
+Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
+\item We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
+\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
+The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency...
 \end{enumerate}
 
-The paper is structured as follows:
+The paper is structured as follows: In Section~\ref{sec.example}, we present a motivating example illustrating the challenges of generating test data for JS.
+The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
+Section~\ref{sec.evaluation} present empirical validation, whereas Section~\ref{sec.disc} discusses future work and validity threats.
+We discuss related work in Section~\ref{sec:related.work} and conclude the paper in Section~\ref{sec:concl}.
 
@@
 We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which play the role of our baseline, is \emph{Random} ($R$).
+The first version, which play the role of our baseline, is \emph{Random} ($\Random$).
 Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
 It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($G$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is the \emph{Genetic with Restart} ($G10$).
+The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
+The last version is the \emph{Genetic with Restart} ($\RGenetic$).
 It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
@@
 We have experimented with two different windows of size 5 and 10.
-But since the latter one ($G10$) showed the best performance over all, we chose it to report in the paper.
+But since the latter one ($\RGenetic$) showed the best performance over all, we chose it to report in the paper.
 Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
@@
 \begin{description}
-\item[\textbf{RQ1 (performance):}] What is the performance of our test generation framework?
-Is there any difference in performance on examples with DOM and without?
-Which algorithm works best random, genetic or genetic with restart?
-\item[\textbf{RQ2 (cost):}] What is the cost of one iteration of each algorithm?
-\item[\textbf{RQ3 (coverage):}] How does the branch coverage progress over time given a fixed budget per branch?
-\item[\textbf{RQ4 (significance):}] What is statistical significance and effect size of our experimental results? 
+\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework? Which testing algorithm is the most effective?
+\item[\textbf{RQ2 (efficiency):}] How efficient our testing framework? And which algorithm is the most efficient?
+\item[\textbf{RQ3 (significance):}] What is statistical significance and effect size of our experimental results? 
 \end{description}
@@
 
-\paragraph{\textbf{RQ1 (performance).}} First, we would like to study the performance of our test generation framework, including three test algorithms: Random ($\Random$), Genetic ($\Genetic$) and Genetic with Restart ($\RGenetic$).
-To address this question, we ran each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
+To study the effectiveness and efficiency of our test generation framework, including three test algorithms Random ($\Random$), Genetic ($\Genetic$) and Genetic with Restart ($\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
 Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-%% Functions suffixed with the start (*) symbol indicate reference to DOM.  Column $D$ next to the branch shows its depth. 
 Table~\ref{tbl.stats} contains results of our evaluation.
@@
 At the bottom of the table, we included accumulated data throughout all functions.
-Let us structure the performance discussion according the three levels of abstraction total, function, and branch.
-
+
+\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
 Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-That is, the underlined values in Table~\ref{tbl.stats}  ($\underline{200}$) indicate branches, which on average were not covered by the respective algorithms.
+The values in Table~\ref{tbl.stats} highlighted as $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
 The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
@@
 
-Figure~\ref{fig.gen.time.branch} shows average generation time per branch for each algorithm.
-It took maximum upto 26.5 seconds for $\RGenetic$ to cover a branch.
-This upper bound may service as a rough estimate defining budget for testing a new function with our framework using $\RGenetic$.
+According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
+Three functions at the bottom of Table~\ref{tbl.case.studies}, \emph{initBricks}, \emph{do_daw} and \emph{prob_gamma} with the respective CC 13, 14 and 16 are of the latter category.
+Because of they complexity, they are recommended to test, but test construction, especially manual, can be difficult.
+For those functions, $\RGenetic$ managed to provide complete coverage, where other two algorithms failed, and did it in a shortest time.
+Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
+
+Additionally, we would like to investigate how the coverage progresses with the increase of budget assigned per branch.
+This experiment models different testing scenarios which are time depended.
+E.g.
+running tests inside IDE should be fast; as part of the CI cycle we may afford a large waiting time; regression testing over night may take hours.
+We define the following budget categories: 5, 10, 30, 60, 90, 120, 150.
+Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
+Eventually, it converges around 52\% coverage.
+Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
+When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
+But when the budget rises to 30 seconds, $\RGenetic$ starts to transcend $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).
+In conclusion, our recommendation is to use $\Genetic$ for rapid testing during development, and later towards integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
+
+\begin{figure}[!t]
+  \begin{tikzpicture}[scale=0.5]
+    \begin{axis}[
+        xlabel={Time budget per branch (seconds)},
+        ylabel={Number of covered branches},
+        xmin=0, xmax=150,
+        ymin=10, ymax=58,
+        xtick={0,5,10,30,60,90,120,150,180},
+        ytick={0,10,20,30,40,50},
+        legend pos=south east,
+        ymajorgrids=true,
+        % xmajorgrids=true,
+        grid style=dashed,
+        label style={font=\huge}
+      ]
+
+      \addplot[
+        color=blue,
+        mark=square*,
+      ] coordinates {
+        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
+      }; 
+      \addplot[
+        color=red,
+        mark=triangle*,
+      ]  coordinates {
+        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
+      };
+      \addplot[
+        color=yellow,
+        mark=*,
+      ]   coordinates {
+        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
+      };
+      \legend{$\Random$,$\Genetic$,$\RGenetic$}
+
+    \end{axis}
+  \end{tikzpicture}
+  \caption{Progress of the branch coverage given fix time budget per branch}
+    \label{fig:2}
+\end{figure}
+
+\paragraph{\textbf{RQ2 (efficiency).}} To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
+Based on this information, we suggest an estimate on the execution time of the testing framework.
 
@@
 
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at a function level.
-There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%; and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
+The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
+There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
 In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
-According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are easy to test, and above 10 present a reasonable challenge.
-Three functions at the bottom of Table~\ref{tbl.case.studies}, \emph{initBricks}, \emph{do_daw} and \emph{prob_gamma} with the respective CC 13, 14 and 16 are of the latter category.
-Because of they complexity, they are recommended to test, but test construction, especially manual, can be difficult.
-For those functions, $\RGenetic$ managed to provide complete coverage, where other two algorithms failed, and did it in a shortest time.
-
-In total, $\RGenetic$ outperformed $\Random$ and $\Genetic$ by 4.66 and 2.05 times, respectively; and $\Genetic$ outperformed $\Random$ by 2.27 times.
-Moreover, $\RGenetic$ was not only the fastest, but also the most effective algorithm reaching 100\% of branch coverage, with $\Genetic$ coming second 95\%, and $\Random$ third 63\%.
-On average, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
 
@@
 
-\paragraph{\textbf{RQ2 (cost).}} This question is supposed to shed some light on the cost of one iteration of our framework.
-This information is useful when setting up the maximal generation limit.
-The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures time of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On one hand, the cost of one iteration depends on the population size, in our case 50 candidates.
-On the other hand, the cost also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
-....
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-The \emph{do_draw} examples illustrates the latter case, it consists of 40 LOC and operates only with primitive type which do not case any exception.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.38 seconds.
+Figure~\ref{fig.gen.time.branch} shows average generation time per branch for each algorithm.
+It took maximum upto 26.5 seconds for $\RGenetic$ to cover a branch.
+This upper bound may service as a rough estimate defining budget for testing a new function with our framework using $\RGenetic$.
+
+In total, $\RGenetic$ outperformed $\Random$ and $\Genetic$ by 4.66 and 2.05 times, respectively; and $\Genetic$ outperformed $\Random$ by 2.27 times.
 
@@
 
+This question is supposed to shed some light on the cost of one iteration of our framework.
+This information is useful when setting up the maximal generation limit.
+The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
+it measures time of one iteration.
+Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
+On one hand, the cost of one iteration depends on the population size, in our case 50 candidates.
+On the other hand, the cost also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
+....
+Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
+The \emph{do_draw} examples illustrates the latter case, it consists of 40 LOC and operates only with primitive type which do not case any exception.
+In our evaluation we observed that the iteration cost varied between 0.25 and 3.38 seconds.
+On average, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
+
 TODO: discuss why cost of one genetic iteration for \emph{do_draw} is higher than random.
@@
 
-\paragraph{\textbf{RQ3 (coverage).}} In this research question we want to compare how coverage progresses with the increase of budget assigned per branch.
-We chose the following budget categories: 5, 10, 30 etc.
-up to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $G$ and $G10$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $G$ slightly outperforms $G10$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $G10$ starts to transcend $G$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).
-
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig:2}
-\end{figure}
-
-\paragraph{\textbf{RQ4 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} our the performance results.
+\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} our the performance results.
 This analysis is based on the coverage time in 50 executions, produced by each test algorithm $R$, $G$ and $G10$.

### 2018-01-28 doc/icse2018/icse2018.tex
Finished the RQ3

@@
 \begin{table}[!t]
-  \caption{Branch coverage statistics for three variations of the JS test generation framework}
+  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
   \label{tbl.stats}
     \scriptsize
-    \begin{tabular}{l|rrr|rrr|rrr|rrr|rrr}
+    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
       \toprule
@@
     $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-    \hline
+   \midrule
+    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
+    \bottomrule
    \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
@@
     \midrule
-    \textbf{TOTAL} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
+    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
+    %% \midrule
+    %% \midrule
+    \bottomrule
+    \bottomrule  
+    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
     \bottomrule
@@
 
-To study the effectiveness and efficiency of our test generation framework, including three test algorithms Random ($\Random$), Genetic ($\Genetic$) and Genetic with Restart ($\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
+To study the effectiveness and efficiency of our test generation framework, including three test algorithms Random~($\Random$), Genetic~($\Genetic$) and Genetic with Restart~($\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
 Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
 Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations ($i$), time in seconds ($t$), and their ratio ($t/i$).
+For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
 In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ according to the algorithm type $\Random$, $\Genetic$ and $\RGenetic$.
@@
 see the \emph{toggleInfo} function.
-At the bottom of the table, we included accumulated data throughout all functions.
+
+According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
+We call the functions of the first type ``simple'', and ``difficult'' otherwise.
+The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with the respective the CC 13, 14 and 16.
+Table~\ref{tbl.stats.sum} summarizes the total results of the experiment such as coverage, execution time per branch and significance.
+
+\begin{table}[!t]
+  \caption{Result Summary (L - large, M - medium, S - small)}
+  \label{tbl.stats.sum}
+    \footnotesize
+    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
+      \toprule
+      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
+      \cline{2-16}
+                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $\Random : \Genetic$} & \multicolumn{3}{p{1cm}|}{\hfil $\Random : \RGenetic$} & \multicolumn{3}{p{1cm}}{\hfil $\Genetic : \RGenetic$} \\
+      \cline{8-16}
+                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
+      \midrule
+      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
+      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
+      \midrule
+      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
+      \bottomrule
+    \end{tabular}
+\end{table}
 
@@
 Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines strengths of both algorithms genetic and random.
-It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness converges.
+It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
 As our evaluation has shown, $\RGenetic$ not only manged to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
-branch $(69,71)$ of the \emph{do_draw} function.
-
-According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
-Three functions at the bottom of Table~\ref{tbl.case.studies}, \emph{initBricks}, \emph{do_daw} and \emph{prob_gamma} with the respective CC 13, 14 and 16 are of the latter category.
-Because of they complexity, they are recommended to test, but test construction, especially manual, can be difficult.
-For those functions, $\RGenetic$ managed to provide complete coverage, where other two algorithms failed, and did it in a shortest time.
+branch $(69,71)$ of the \emph{initBricks} function.\\
+\setlength{\fboxsep}{1mm}
+\fbox{%
+  \parbox{8.2cm}{
 Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
-
-Additionally, we would like to investigate how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios which are time depended.
-E.g.
-running tests inside IDE should be fast; as part of the CI cycle we may afford a large waiting time; regression testing over night may take hours.
-We define the following budget categories: 5, 10, 30, 60, 90, 120, 150.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ starts to transcend $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).
-In conclusion, our recommendation is to use $\Genetic$ for rapid testing during development, and later towards integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
+  }
+}
 
@@
   \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig:2}
+    \label{fig.budget.progress}
 \end{figure}
+
+Additionally, we would like to investigate how the coverage progresses with the increase of budget assigned per branch.
+This experiment models different testing scenarios, used in practice, which are time depended.
+E.g.
+running tests inside IDE should be fast; as part of the CI cycle we may afford a large waiting time; regression testing over night may take hours.
+Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
+Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
+Eventually, it converges around 52\% coverage.
+Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
+When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
+But when the budget rises to 30 seconds, $\RGenetic$ starts to transcend $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
+\setlength{\fboxsep}{1mm}
+\fbox{%
+  \parbox{8.2cm}{
+Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
+  }
+}
 
@@
 Based on this information, we suggest an estimate on the execution time of the testing framework.
-
-%% \setlength{\fboxsep}{2mm}
-%% \fbox{%
-%%   \parbox{8cm}{
-%%     Three testing strategies $\Random$, $\Genetic$ and $\RGenetic$ covered respectively 63\%, 95\% and 100\% of branches.
-%%   }
-%% }
-
-%% TODO: Maybe discuss examples where $\Random$ outperformed $\RGenetic$
-%% TODO: consider further branch discrimination
+The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
+There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
+In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
 
@@
 
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=135,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-      \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-      \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Average generation time per branch}
-    \label{fig.gen.time.branch}
-\end{figure}
-
-Figure~\ref{fig.gen.time.branch} shows average generation time per branch for each algorithm.
-It took maximum upto 26.5 seconds for $\RGenetic$ to cover a branch.
-This upper bound may service as a rough estimate defining budget for testing a new function with our framework using $\RGenetic$.
-
-In total, $\RGenetic$ outperformed $\Random$ and $\Genetic$ by 4.66 and 2.05 times, respectively; and $\Genetic$ outperformed $\Random$ by 2.27 times.
+%% \begin{figure}[t]
+%%   \begin{tikzpicture}[scale=0.8]
+%%     \begin{axis}[
+%%         every axis plot post/.style={/pgf/number format/fixed},
+%%         ybar,
+%%         ymin=0,ymax=135,
+%%         width=11cm,height=3.3cm,
+%%         bar width=3pt,
+%%         enlarge x limits=0.05,
+%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
+%%         legend cell align={left},
+%%         ylabel={time (sec.)},
+%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
+%%         xtick=data,
+%%         nodes near coords,
+%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
+%%         % every node near coord/.append style={font=\footnotesize},
+%%         axis lines*=left,
+%%         clip=false,
+%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
+%%         y tick label style={font=\footnotesize}
+%%       ]
+%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
+
+%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
+
+%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
+%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
+%%     \end{axis}
+%%   \end{tikzpicture}
+%%   \caption{Average generation time per branch}
+%%     \label{fig.gen.time.branch}
+%% \end{figure}
+
+Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with the 7 and 25 seconds per branch.
+For simple functions, the $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
+In all categories, $\Random$ was much slower than both genetic alternatives.\\
+\setlength{\fboxsep}{1mm}
+\fbox{%
+  \parbox{8.2cm}{
+    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch 19, 39 and 88 seconds, respectively. 
+  }
+}
 
@@
 
-This question is supposed to shed some light on the cost of one iteration of our framework.
-This information is useful when setting up the maximal generation limit.
+Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
+This information is useful when configuring the maximal generation limit.
 The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures time of one iteration.
+it measures the speed of one iteration.
 Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On one hand, the cost of one iteration depends on the population size, in our case 50 candidates.
-On the other hand, the cost also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
-....
+On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
+On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
 Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-The \emph{do_draw} examples illustrates the latter case, it consists of 40 LOC and operates only with primitive type which do not case any exception.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.38 seconds.
-On average, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
-
-TODO: discuss why cost of one genetic iteration for \emph{do_draw} is higher than random.
-
-TODO: discuss if costs of $R$, $G$ and $G5$ vary between each other and why.
-
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $R$, $G$ and $G10$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values, where it was significant (otherwise '-'), for all three pairs of the test algorithm: $R$ against $G$ ($r/g$), $R$ against $G10$ ($r/g10$), and $G$ against $G10$ ($g/g10$).
-Depends on the actually exceeded value, the effect size can be small (0.56), medium (0.64), and large (0.71).
-Both genetic versions ($G$ and $G10$) outperform random ($R$) with the large (medium and small) effect in 33 (37 and 39) subjects, respectively, out of total 57.
+For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus not rising exceptions, and at the same time, it consists of 40 LOC.
+In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
+\setlength{\fboxsep}{1mm}
+\fbox{%
+  \parbox{8.2cm}{
+    Globally, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
+  }
+}
+
+\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
+This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
+Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
+In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
+For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs comparing to $\Genetic$.
+Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
+\setlength{\fboxsep}{1mm}
+\fbox{%
+  \parbox{8.2cm}{
+    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases globally and 67\% on the difficult functions.  
+  }
+}
 

### 2018-01-29 doc/icse2018/icse2018.tex
Working on Related work section

@@
 \usepackage{xspace}
+\usepackage{enumitem}
 \usepackage{mdframed}
@@
 \begin{document}
-\title{Search-Based Test Data Generation for JavaScript Functions with DOM}
+\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
 
@@
 In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state.
-The \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage in our empirical evaluation with the average execution time 7.7 sec.
-per branch
+We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
+ It has shown that the \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage on all experimental subjects with the average 19 seconds of execution time per branch.
 \end{abstract}
@@
 
-Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{paper}.
+Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{mao2016sapienz}.
 In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript.
 Our work makes the following contributions:
-\begin{enumerate}
+\begin{enumerate}[leftmargin=5mm]
 \item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
@@
 We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate the native browser API calls.
+
+\begin{algorithm}[t!]
+  \caption{Initialization Phase}
+  \label{alg.init}
+  \algsetup{linenosize=\tiny}
+  \scriptsize
+  \DontPrintSemicolon
+  \SetAlgoVlined
+  \SetKwInOut{Input}{Input}
+  \SetKwInOut{Output}{Output}
+  \SetKwInOut{Require}{Require}
+  \SetKwProg{Fn}{Function}{}{}
+  \Input{JS file $fun.js$ with FUT and type annotation }
+  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
+  \Fn{$Initialize(fun.js)$}{
+
+    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
+    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
+    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
+    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
+    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
+    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
+    \Return{$(cfg, branches, cinfo, ifun, sig)$}
+    }
+\end{algorithm}
 
@@
 
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
 During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing.
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
 \setlength{\grammarparsep}{3pt}
@@
 \end{figure}
+One assumption made in the paper is the availability of type signatures for JS functions.
+We believe in the legitimacy of such a request due to the following observations.
+First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity.
+Second, there has been an active work on the JS type inference done both in academia~\cite{paper} and industry, e.g.
+Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.
 
@@
 The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{evosuite}.
+\emph{EvoSuite}~\cite{fraser2011evosuite}.
 
@@
 \begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework? Which testing algorithm is the most effective?
-\item[\textbf{RQ2 (efficiency):}] How efficient our testing framework? And which algorithm is the most efficient?
-\item[\textbf{RQ3 (significance):}] What is statistical significance and effect size of our experimental results? 
+\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
+Which testing algorithm is the most effective?
+How the effectiveness changes with the budget per branch?
+\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost of one iteration?
+\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
 \end{description}
@@
       \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $\Random : \Genetic$} & \multicolumn{3}{p{1cm}|}{\hfil $\Random : \RGenetic$} & \multicolumn{3}{p{1cm}}{\hfil $\Genetic : \RGenetic$} \\
+                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
       \cline{8-16}
@@
 
-\paragraph{\textbf{RQ2 (efficiency).}} To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
+\paragraph{\textbf{RQ2 (efficiency).}}
+ To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
 Based on this information, we suggest an estimate on the execution time of the testing framework.
@@
 
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with the 7 and 25 seconds per branch.
-For simple functions, the $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
-In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch 19, 39 and 88 seconds, respectively. 
-  }
-}
-
 \begin{figure}[t]
@@
 
+%% \begin{figure}[t]
+%%   \begin{tikzpicture}[scale=0.8]
+%%     \begin{axis}[
+%%         every axis plot post/.style={/pgf/number format/fixed},
+%%         ybar,
+%%         ymin=0,ymax=135,
+%%         width=11cm,height=3.3cm,
+%%         bar width=3pt,
+%%         enlarge x limits=0.05,
+%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
+%%         legend cell align={left},
+%%         ylabel={time (sec.)},
+%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
+%%         xtick=data,
+%%         nodes near coords,
+%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
+%%         % every node near coord/.append style={font=\footnotesize},
+%%         axis lines*=left,
+%%         clip=false,
+%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
+%%         y tick label style={font=\footnotesize}
+%%       ]
+%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
+
+%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
+
+%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
+%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
+%%     \end{axis}
+%%   \end{tikzpicture}
+%%   \caption{Average generation time per branch}
+%%     \label{fig.gen.time.branch}
+%% \end{figure}
+
+Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with the 7 and 25 seconds per branch.
+For simple functions, the $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
+In all categories, $\Random$ was much slower than both genetic alternatives.\\
+\setlength{\fboxsep}{1mm}
+\fbox{%
+  \parbox{8.2cm}{
+    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch 19, 39 and 88 seconds, respectively. 
+  }
+}
+
 Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
@@
 
-% \input{summary_statistics}
+\paragraph{\textbf{Threats to Validity}}
+The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
+Though, the branch coverage is a common criteria used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
+Reaching a target branch is only part of the problem, we also need an oracle to discriminate the program's output.
+In this paper, we strike for so called ``natural'' oracles disseminating in exceptions.
+Using a stronger oracle for validation is future work.
+Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
+To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent unnecessary data explosion.
+Additional measure that could be taken is applying a minimization procedure, aka \emph{delta debugging}, to the GA result.
+
+Initial GA configuration introduces the threat to the \emph{internal validity} of our empirical evaluation.
+The parameters we used are quite standard for similar SBST frameworks, e.g.
+EvoSuite.
+Though, not reported in the paper, we performed preliminary assessment of various GA configurations, which confirmed our final decision.
+
+The threat of \emph{conclusion validity} can be affected by the GA stochastic nature.
+This risk was addressed by repeating the experiment 50 times and performing statistical analysis of the significance and effect size.
+We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
+
+The \emph{external validity} deals with the threat of generalization of our results due to manual selection of the experimental subjects.
+To mitigate this fact, we picked the subjects either from previously used in related research or found in open source.
+Of course, those subjects still have to met the constrains of our testing approach.
+So, further research is required in both increasing the power of our framework and extending the validation set.
 
@@
 
+There are several ways how to address the problem of input data generation for JS functions: static and dynamic analysis, symbolic execution, SBST, formal reasoning, the whole web application testing.
+
 \subsection{Search-Based Test Case Generation}
+
+Despite of the practical popularity of JavaScript, the only recorded in the literature attempt of adopting search-based testing for JS unit testing was done by Alshraideh~\cite{alshraideh2008complete}.
+It uses GA for branch and mutation coverage, but only deals with the limited input types booleans, integers and strings; and provides validation based on one trivial example --- \emph{the triangle program}.
+On the contrary, our work additionally supports array and DOM types, with suggest reasonable validation with the discussion of significance and effect size.
+Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
+
+One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
+Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage.
+That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage.
+Usually, such problems incur multi-objective optimization, e.g.
+coverage vs.
+test-suite length.
+
+In this paper we dealt with the generation and evolution of DOM which is an example of tree-like data structure.
+\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim to improve test coverage of the XML-aware Java programs.
+To generate random document, it may rely on existing XML schema, or generate document from scratch.
+In some sense, DOM specification can be thought of a complex XML schema, which is difficult to comply.
+One distinction of our approach is the use of program analysis for data generation.
+Both tools have similar philosophy for mutation and crossover.
+Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
+
+The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
+Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
+It performs static analysis to collect constant info and feed it to the random generation.
+We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution.
+Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
+
+Mobile
+
+Object-oriented: EvoSuite~\cite{fraser2011evosuite}
+
+Structural
+
+TODO: discuss multi-objective works and hyper-heuristics search
+
 \label{sub.sec.search.based}
@@
 
-\cite{havrikov2014xmlmate} XMLMate: evolutionary XML test generation.
-
 \cite{mcminn2004search} seminal survey of search-based test data generation techniques.
@@
 \cite{mcminn2011search} recent overview of search-based testing.
-
-\cite{mairhofer2011search} search-based testing for dynamic languages (Ruby)
 
@@
 
+NodEO, a multi-paradigm distributed evolutionary algorithm platform in JavaScript~\cite{merelo2014nodeo}.
+
 \section{Conclusions}

### 2018-01-30 doc/icse2018/icse2018.tex
Continue working on related work

@@
 
+\usepackage[inline]{enumitem}
 \usepackage{tablefootnote}
@@
 
-TODO: maybe expand this section with the JS type casting for branch distance computation
+%TODO: maybe expand this section with the JS type casting for branch distance computation
 
@@
 The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
+
+\subsubsection{Limitations}
+\label{sub.sub.sec.limit}
+
+Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
+\begin{enumerate}
+\item ability to assign static types to input parameters 
+\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
+\item no support for recursion
+\item doesn't perform inter-procedural analysis
+\item no support for JS frameworks
+\item no reference to global variables and functions
+\item limited support of DOM API     
+\end{enumerate}
 
@@
 
-\section{Discussion}
-\label{sec.disc}
-
-\subsection{Future Work}
-\label{sub.sec.fut.work}
-
-We would like to open source our test generation framework and introduce a web service allowing developers to submit their JS code for automated testing.
-One benefit of such service from the perspective of future research is an ability to learn about programming style and the use of JS libraries.
-Being dynamic language, JS supports various programming styles, which is, as was widely admitted~\cite{paper}, hindrance the complete analysis of JS programs.
-By gathering feedback about JS programs on which our framework performed poorly, we can identify and prioritize language constructs and programming patterns that should be adequately addressed.
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process:
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
-Multi-objective test suite generation. DOM reduction by means of hierarchical delta-debugging.
-
-\subsection{Limitations}
-\label{sub.sec.eval.limit}
-
-Our framework imposes certain constraints on the structure of JS programs:
-
-\subsection{Threats to Validity}
-\label{sub.sec.thhreats}
-
 %% --------------------------------------------------------------------
-\section{Related Work}
+\section{Related and Future Work}
 \label{sec:related.work}
@@
 
-There are several ways how to address the problem of input data generation for JS functions: static and dynamic analysis, symbolic execution, SBST, formal reasoning, the whole web application testing.
-
-\subsection{Search-Based Test Case Generation}
+The last two decades were fruitful in the amount of work dedicates to the analysis and web applications and JavaScript, in particular.
+The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the two recent surveys~\cite{andreasen2017survey, sun2017analysis}.
+Therefore, we would like to organize our discussion of related work around two main questions:
+\begin{enumerate*}
+\item test data generation for JS functions interacting with the DOM, and
+\item the application of search-based techniques for that problem.
+\end{enumerate*}
+
+\subsection{Test Data Generation for JavaScript}
+
+The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
+Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
+It performs static analysis to collect constant info and feed it to the random generation.
+We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution.
+Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
+
+\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing concolic testing or type inconsistency analysis~\cite{pradel2015typedevil}.
+It suffers from typical for the symbolic analysis problems such as the handing of arrays and loops.
+\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtains DOM fixtures for the FUT.
+Combined with Jalangi it can be used for both primitive and DOM test data generation.
+As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
+Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
+
+Static analysis is a powerful technique commonly used as solid alternative for program testing.
+In fact both techniques can benefit from one another.
+For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence.
+Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
+In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API.
+Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
+
+\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
+
+\subsection{Search-Based Test Data Generation}
 
@@
 
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect constant info and feed it to the random generation.
-We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-
 Mobile
@@
 
-\subsection{Static and Dynamic Analysis of JavaScript}
-\label{sub.sec.js.static.anal}
-
-Static analysis is a powerful technique commonly used as solid alternative for program testing.
-In fact both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
 \cite{jquery2014}

### 2018-01-30 doc/icse2018/icse2018.tex
Continue working on related work

@@
 First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity.
-Second, there has been an active work on the JS type inference done both in academia~\cite{paper} and industry, e.g.
+Second, there has been an active work on the JS type inference done both in academia~\cite{kristensen2017type} and industry, e.g.
 Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.
@@
 The last two decades were fruitful in the amount of work dedicates to the analysis and web applications and JavaScript, in particular.
-The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the two recent surveys~\cite{andreasen2017survey, sun2017analysis}.
+The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
 Therefore, we would like to organize our discussion of related work around two main questions:
@@
 Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
+More recently, Kristensen et al.~\cite{kristensen2017type} proposes to use feedback-directed random testing for generating TypeScript tests based on the provided type annotations.
 
@@
 Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
+Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS without the DOM interaction.
 
@@
 Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
+Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
+It discoverers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
+
+\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
+
+\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the JS \emph{Proxies} in order to collect type related information.
 
 \emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
+Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
+
+\cite{alshahwan2011automated} automated web application testing using search based software techniques.
+
+\cite{ma2015grt} guided random testing
+
+\cite{mao2016sapienz} Multi-objective automated testing for Android application
+
+\cite{jquery2014}
+
+ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
+
+Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
+
+Information-flow security for JS~\cite{hedin2012information}.
+
+Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
+
+Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
+
+Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
+
+Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
+
+DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
 
 \subsection{Search-Based Test Data Generation}
+\label{sub.sec.search.based}
 
@@
 Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage.
-That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization, e.g.
-coverage vs.
-test-suite length.
 
@@
 
-Mobile
-
-Object-oriented: EvoSuite~\cite{fraser2011evosuite}
-
-Structural
-
-TODO: discuss multi-objective works and hyper-heuristics search
-
-\label{sub.sec.search.based}
-
-\cite{wegener2001evolutionary} evolutionary test generation for structural coverage.
-
-\cite{tonella2004evolutionary} evolutionary testing of classes
-
-\cite{wappler2005using} evolutionary testing of object-oriented software.
-
-\cite{wappler2006evolutionary} uses strongly-typed genetic programming and deals with the runtime exceptions.
-
-\cite{lakhotia2007multi} multi-objective search-based test data generation
-
-\cite{cao2009search} multi-path search-based test data generation
-
-\cite{awedikian2009mc} MC/DC test input generation
-
-\cite{shahbazi2016black} generation of string test data
-
-\cite{fraser2012mutation} mutation-driven generation of unit tests and oracles
-
-\cite{mcminn2004search} seminal survey of search-based test data generation techniques.
-
-\cite{mcminn2011search} recent overview of search-based testing.
-
-\cite{baars2011symbolic} combines dynamic analysis with symbolic information to improve search-based testing
-
-\cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-\cite{ma2015grt} guided random testing
-
-\cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-\cite{jquery2014}
-
-ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-Jalangi is dynamic analysis framework for JavaScript \cite{sen2013jalangi}.
-
-Dynamic type inconsistency analysis (implemented on top Jalangi) for JavaScript\cite{pradel2015typedevil}.
-
-Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-Information-flow security for JS~\cite{hedin2012information}.
-
-\subsection{Whole Web Application Testing}
-\label{sub.sec.web.app.test}
-
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discoverers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-\cite{ail2013}
-
-Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Formal Techniques}
-\label{sub.sec.formal}
-
-Modeling and reasoning about DOM events~\cite{lerner2012modeling}.
-
-\subsection{JavaScript Unit Testing}
-\label{sub.sec.js.unit.test}
-
-Generating fixture for JavaScript unit tests by means of concolic execution~\cite{amin:ase15}. Inference of UI oracles to complement JS unit tests~\cite{icst16}.
-
-JS unit test generation by means of symbolic execution~\cite{tanida2014automatic}.
-
-Flycatcher~\cite{deautomatic}
-
-\subsection{Misc JavaScript Testing Techniques}
-\label{sub.sec.misc.test.tech}
-
-Discover patterns from bug fixes and imposing them as potential bugs in the future~\cite{quinn:fse16}.
-
-NodEO, a multi-paradigm distributed evolutionary algorithm platform in JavaScript~\cite{merelo2014nodeo}.
+Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of SBST research~\cite{mcminn2011search}.
+Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
+
+One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
+Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage.
+That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage.
+Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
+coverage vs.
+test-suite length.
+Another direction of future work is adjusting out tool for mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
+That would also help us to judge about the fault revealing ability of \emph{JEDI} based on the number of killed mutants.
+As we said early in this section, SBST techniques can benefit from symbolic analysis~\cite{baars2011symbolic}.
 
@@
 \label{sec:concl}
-1 page.
+This paper
 

### 2018-05-07 doc/icse2018/issta2018.tex
Working on issre 2018 revision.

--- 2018-01-30 doc/icse2018/icse2018.tex
@@
-\documentclass[sigconf,review,anonymous]{acmart}
+\documentclass[sigconf,review]{acmart}
 
@@
 
-\listfiles % used to output the versions of all files being used by the latex
+\listfiles % used to output the versions of all files being used by the late
 
@@
 %\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
+\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
   \institution{Utrecht University, The Netherlands}
-  \country{The Netherlands} 
 }
@@
 \begin{abstract}
-As of 2017 JavaScript and Node.js continue to stay the most prevalent technologies according to the Stack Overflow developers survey.
-Nevertheless, existing JS testing frameworks are still lacking any support for such a vital step in test automation as the generation of input data.
-To address this problem, we present a novel \textbf{J}avascript \textbf{E}volutionary-based testing framework with \textbf{D}OM as an \textbf{I}input, called \textbf{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state.
+The popularity of JavaScript is continuously growing.
+Together with HTML and CSS, it forms the core technology stack for web development.
+Because of the dynamic nature and complex interplay with HTML, JS applications are still error-prone and vulnerable.
+Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS applications interacting with the DOM has not yet been addressed.
+In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
+In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including the global DOM state.
 We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
- It has shown that the \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage on all experimental subjects with the average 19 seconds of execution time per branch.
+It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
 \end{abstract}
@@
 
+%% ------------------------------------------------------------------------
 \section{Introduction}
 \label{sec.intro}
-
-According to a Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the fifth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
-It is used through all technology stack web, back-ends and mobile.
-Such a tremendous ever increasing JS success is happening thanks to the extensive dynamic features of the language, JS permissiveness and native browser support.
-On the other hand, JS applications are error-prone~\cite{why}, hard to analyze~\cite{why} and test~\cite{why}.
-Therefore, it is not surprising that year after year we hear new stories\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}} about another critical bug being found in a web application by Facebook, Twitter etc.
-
-%% Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.
-
-%% Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.
-
-The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
-These frameworks support testing at various levels: unit, integration and functional.
-The survey also indicated relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
-As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite of this effort, test data generation continues to be not properly addressed by any of the widely used testing frameworks.
-The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of JS faults are DOM-related and occur in JS code, and not in HTML or CSS.
-This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
-Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{mao2016sapienz}.
-In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript.
-Our work makes the following contributions:
+%% ------------------------------------------------------------------------
+
+According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript has been recognized for the sixth time in row as the most commonly used programming language.
+It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million).
+Such an ever increasing JS success can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}.
+On the other hand, due to of implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}.
+Thus, it is not surprising that once in a while critical bugs manage to break through~\cite{bugstories2017} into the web applications by Facebook, Twitter etc.
+
+Systematic unit testing is basic and, at the same time, the most effective technique for improving software quality.
+In practice, there are numerous of JS frameworks --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc.
+--- intended to assist developers with the automation of various unit testing activities such as design, execution and monitoring.
+Despite the apparent abundance of the JS testing tools, the developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements.
+One of such areas is \emph{test data generation}.
+It pursues the goal of maximizing the test coverage by exercising the function under test (FUT) with different input parameters.
+Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.
+
+Generally, the problem of test data generation has been under an active study for the past three decades.
+In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the whole web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
+Out of those tools, only \emph{Confix} tries to construct a sufficient DOM fixture by translating native browser API calls into logical constraints.
+However, in the empirical evaluation~\cite{amin:ase15}, Confix only reached about 50\% in \emph{branch coverage} on the selected subjects.
+At the same time, search-based techniques have shown prominent results in achieving high branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications.
+But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of the search-based approach.
+In this paper we are breaching this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
+We can summarize our contributions as follows:
 \begin{enumerate}[leftmargin=5mm]
 \item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-\item We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency...
+Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
+\item Our test generation algorithm, called ``genetic with restart'', is trying to escape search plateau by restarting GA with a new target.
+Because the full-fledged JS data flow analysis~\cite{jang2009points} is hard to reach, the new target is chosen purely based on the preceding control flow behaviour in contrast with more popular techniques~\cite{ferguson1996chaining}.
+\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results.
+The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
+Moreover, we showed that on the selected subjects \emph{JEDI} outperforms \emph{Confix} ....
 \end{enumerate}
@@
 The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} present empirical validation, whereas Section~\ref{sec.disc} discusses future work and validity threats.
-We discuss related work in Section~\ref{sec:related.work} and conclude the paper in Section~\ref{sec:concl}.
-
-Another empirical work~\cite{richards2010analysis}.
+Section~\ref{sec.evaluation} presents empirical validation and indicates the validity threats.
+Related and future work are discussed in Section~\ref{sec:related.work}.
+Section~\ref{sec:concl} concludes the paper.
+
+%% The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
+These frameworks support testing at various levels: unit, integration and functional.
+The survey also indicated a relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
+As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
+But despite this effort, test data generation continues to be poorly addressed by any of the widely used testing frameworks.
+The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
+A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of web application faults are DOM-related and introduced in the JS code, and not in other components such as HTML or CSS.
+This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
 
@@
 
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from a web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
+Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
 This function checks the validity of a sudoku solution given by a user.
-First, we find a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
+First, we find the DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
 Then, we collect all its child DIVs (line~\ref{isGameFinished.getDivs}).
 Each DIV element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) and consists of two SPANs.
-First span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
+The first span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
 Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
@@
 Suppose now that we would like to unit test this function in isolation to the rest of the application.
-We aim to maximize the branch coverage as a common testing criteria~\cite{why.this.common}.
+We aim to maximize the branch coverage as a common testing criteria~\cite{zhu1997software}.
 That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
-We assume that DOM is the only global variable that can be referenced in the body of the FUT.
-So in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
+The JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
+Henceforth, we assume that DOM is the only global variable that is allowed to be referred to in the body of the FUT.
+In general, in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
 
@@
 
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together deliver the full coverage of the FUT.
+Figure~\ref{fig.isGameFinished.tests} presents four tests that together provide the full coverage of the FUT.
 Let us look now at how following the structure of the FUT in Figure~\ref{code.isGameFinished}, we can construct the $T4$ test covering the $(10,11)$ branch.
@@
 The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the $div$ consists of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
-The resulted test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
+The resulting test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
 
 As we have just seen, even for such a relatively simple example, the construction procedure of a test input is far from trivial because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with the gazillion of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and, at the same time, it is easiest to implement.
-It greatly saves the developers from unexpected regression and puts a safety belt around the application.
+In practice, web developers often have to deal with a large number of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
+At the same time, unit testing is the most fundamental level of testing and the easiest to implement.
+It saves the developers from unexpected regressions and often documents the desired behavior of a program.
 
@@
 
-Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses the genetic engine for test generation.
+Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $\mathbb{B}_f$.
+Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses a genetic engine for test generation.
 The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
 The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-\Server is the key component of the whole framework.
+The \Server is the key component of the  framework.
 It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}.
-Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
+Both phases will be covered in detail in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
 
 Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactic correctness and reports back the set of identified errors.
-\Server rejects the document if any errors were revealed and generates a new one until the generated document has no errors anymore.
+\Server rejects the document if any errors were revealed and generates a new one until the generated document has no more errors.
 \Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
@@
 
-Let us give a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random data generation, genetic phase, logging etc.
+Let us take a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
+As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with a type signature.
+Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random and genetic phases, logging etc.
 Experimentally, we have found an optimal set of input configurations that was used across all experimental objects in Section~\ref{sec.evaluation}.
 This data is processed by the \Server during the \emph{Initialization Phase}.
-As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{ifun}, and the signature (\emph{sig}).
-\Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
-Depends on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
+As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
+The \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
+Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
 For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
@@
 Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate $p$ according to the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
-The execution trace along with some supplementary information about the execution are sent back to the \Server, where the final \emph{fitness value} is computed.
+It matches the candidate $p$ with the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
+The execution trace along with some supplementary information about the execution are sent back to the \Server, where the \emph{fitness value} is computed.
 The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
@@
 At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are exercised, the algorithm reaches the end.
-In the follow up two sections, we elaborate on the details of each individual phase of our test generation framework.
+Once all the branches are covered, the algorithm reaches the end.
+Below, we elaborate on the details of each individual phase of our test generation framework.
 
@@
 
-During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing.
-The main steps of this phase are illustrated by Algorithm~\ref{alg.init}.
+During the \emph{Initialization Phase} we analyze the FUT in order to retrieve the data required for the subsequent genetic testing.
+The main steps of this phase are described in Algorithm~\ref{alg.init}.
 Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info.
-Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName},
-which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT.
-Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
+In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants.
+Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods: \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName}
+These methods provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the FUT.
+The next step is to normalize the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
 transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants.
-Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure.
+We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants.
+Upon the \emph{ifun} execution this information is gathered and fed back to the fitness evaluation procedure.
 Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
@@
 \setlength{\grammarparsep}{3pt}
-\small
+\footnotesize
 \begin{grammar}
@@
 Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures those which refer to the global DOM and the ``ordinary'' JS type signatures.
-The functions of the former signature expect some \texttt{dom} argument to be passed as the first implicit parameter for the function call.
-Whereas ordinary JS signature is a non-zero sequence of the JS types.
+We distinguish between two kinds of signatures: those which refer to the global DOM and ``ordinary'' JS type signatures.
+The functions with the former kind expect some \texttt{dom} argument to be passed as the first implicit parameter of the function call.
+Whereas ordinary JS signature is a non-empty sequence of the JS types.
 The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
@@
 The global variable \emph{trace} in line~\ref{isGameFinished.instr.trace} is an array of labels corresponding to the sequence of executed program statements.
-All statements have to be traced because each one, in theory, can rise an exception.
-The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations for the consecutive for-loop.
+All statements have to be traced because each one, in theory, can raise an exception.
+The \texttt{loopMap} map in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations of the respective for-loop.
 If no exact bound can be computed, we set it to one.
-The \texttt{branchDistance} map tracks the distances to the deviated branches according to the translation formulae~\cite{tracey1998automated}.
+The \texttt{branchDistance} map records the conditional distance~\cite{tracey1998automated} on the branch where the deviation from the target branch has happened.
 
@@
 The heart of our test data generation framework is in the \emph{Genetic Phase}.
-Though, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, but has been extended with the concept of the \emph{archive convergence} (Algorithm~\ref{alg.gen}).
+Although, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, it has been extended with the concept of  \emph{archive convergence} (Algorithm~\ref{alg.gen}).
 As an input, we take a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
@@
 We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ equal to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged or the generations limit has not been reached.
-The \emph{archive} variable stores the most fitted population candidates observed so far, and the \emph{history} variables records all archives during the generation process.
-These variables both are empty in the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
+We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged, or the generations limit has not been reached.
+The \emph{archive} variable stores the most fit population candidates observed so far, and the \emph{history} variable records all archives during the generation process.
+These variables both are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
 
 The initial population has $size_P$ elements, and it is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found or the history has converged or the generation limit $size_G$ has been reached.
-But first, we need to score the current population lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
+In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found, or the history has converged, or the generation limit $size_G$ has been reached.
+But first, we need to score the current population (lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}).
 Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
@@
 Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
-This gives us 4-tuple consisting of an execution trace ($tr$), branch ($d_B$) and loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
+This gives us a 4-tuple consisting of an execution trace ($tr$), branch ($d_B$), loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
 The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
 Collected dynamic constants \emph{dyncinfo} are merged with the existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}).
-And the $combo$ is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
+Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) in $combo$.
+And it is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
+Then, the scored population together with the current archive are sorted by fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
 The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
-The fitness value of that element defines if a perfect candidate is found (line~\ref{alg.gen.loop.end}).
+If $f^*$ is a \emph{perfect} candidate, the solution is found (line~\ref{alg.gen.loop.end}).
 Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
 
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{ga.flag.problem.or.survey}.
+In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{mcminn2004search}.
 For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it occasionally.
-In such situation, we find ourselves being trapped on a flat space, with a small unreliable chance to escape.
+Unless this relation is encoded in the fitness function somehow, we can not learn about it accidentally.
+In such a situation, we find ourselves being trapped on a flat space, with a small chance to escape.
 In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
@@
 Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
-In practice, we only consider the target extensions upto the length of two.
+In practice, we only consider extensions upto length two.
 
 The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
-In the rest of this section, we reveal the implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our main focus in those sections is on the generation and transformation of HTML documents.
+In the rest of this section, we provide implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and the fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
+Our main focus here is on the generation and transformation of HTML documents.
 
@@
 HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-The recent HTML5 standard defines more than hundred of tags and attributes which both have to comply with extremely complex logic to constitute a syntactically valid HTML.
+The recent HTML5 standard defines more than a hundred of tags and attributes which both have to comply with extremely complex logic to constitute  syntactically valid HTML.
 Browsers are usually tolerant to syntactic errors in HTML.
@@
 In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because, as we have mentioned early, the complexity of HTML and the lack of formal specification.
+This was a challenge on its own because the complexity of HTML and the lack of formal specification.
 Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} highlights that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) describes the internal state of \texttt{Html} in the generation.
+With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} shows that definition.
+The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) represents the internal state of \texttt{Html}.
 The state is composed of the following components:
 \begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of HTML 
+\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of the generated HTML 
 \item \texttt{ctx} is the current value of the HTML content model stack 
@@
 Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag should be defined as the value of the \texttt{GenHtmlState} type.
+Each HTML tag is the value of the \texttt{GenHtmlState} type.
 Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
@@
 Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the new contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
+Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
 
@@
 
-In essence, HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for the \emph{expression trees} in genetic programming.
+In essence, an HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
+Therefore, the crossover and mutations are defined similar to those operators for \emph{expression trees} in genetic programming.
 
@@
 
-\textbf{HTML Mutations} are of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
+\textbf{HTML Mutations} belong to one of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
 The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
@@
 \emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
-Currently, we instantiated the \emph{ShuffleAttributes} mutation for only for tho types \emph{class} and \emph{id}.
-In total, this gives us four mutations to chose from in order to evolve an Html document.
+Currently, we instantiated the \emph{ShuffleAttributes} mutation only for the types \emph{class} and \emph{id}.
+In total, this gives us four mutations to choose from in order to evolve an HTML document.
 
@@
 The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating a valid input data.
+Our search target is a specific branch of the function under test that we want to cover by generating valid input data.
 The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
@@
 Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
+The FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
 \[
@@
 \]
-Final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
+The final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
 \[
@@
 The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
-the node caused the deviation.
-Since any node can potentially be exceptional, they all contribute to the approach level in addition to the conditional branches.
-Loops have to treated in a special way because we need to estimate the maximum number of iterations.
-In the case of for-loop, at run-time we can always provide an exact bound.
+the node causing the deviation.
+Since any node can potentially be exceptional, they all contribute to the approach level, in addition to the conditional branches.
+Loops have to be treated in a special way because we need to estimate the maximum number of iterations.
+In the case of a for-loop, at run-time we can always provide an exact bound.
 For while-loops, we assume that it has to be passed at least once.
@@
 
-In order to evaluate the feasibility of our test framework adoption in practice, we conducted an empirical evaluation on a set of case-studies described in Section~\ref{sub.sec.case.studies}.
+In order to evaluate the feasibility of our test framework, we conducted an empirical evaluation on a set of case-studies (see Section~\ref{sub.sec.case.studies}).
 All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
 We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which play the role of our baseline, is \emph{Random} ($\Random$).
+The first version, which plays the role of our baseline, is \emph{Random} ($\Random$).
 Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
+It is important to note  that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
 The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is the \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On one hand, the smaller window size forces the GA to converge faster and early discovers the stagnation on a flat space.
-On the other hand, the small window can lead to a premature archive convergence, which prevents the right genetic combination from been triggered.
+The last version is \emph{Genetic with Restart} ($\RGenetic$).
+It is based on the genetic Algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
+On the one hand, the smaller window size forces the GA to converge faster and quickly discovers stagnation on a flat space.
+On the other hand, the small window can lead to premature archive convergence, which prevents the right genetic combination from being triggered.
 We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose it to report in the paper.
+But since the latter one ($\RGenetic$) showed the best performance over all, we chose to report only that case in the paper.
 Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
@@
 
-By carrying the evaluation, we would like to address the following research questions:
+By carrying the evaluation, we would like to answer the following research questions:
 \begin{description}
@@
 Which testing algorithm is the most effective?
-How the effectiveness changes with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost of one iteration?
+How does effectiveness change with the budget per branch?
+\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost per iteration?
 \item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
+\item[\textbf{RQ4 (comparison):}] What is the branch coverage of \emph{Confix}?
 \end{description}
@@
 Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless number of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation.
-Before selection, the source code of a potential case-study has to be scrutinized which is time consuming and labor intensive process.
+JS applications are written with the help of countless numbers of specialized libraries, and greatly vary in size, complexity and coding style.
+Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to native DOM manipulation.
+Before selection, the source code of a potential case-study has to be scrutinized which is a time consuming and labor intensive process.
 Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
 Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}} to increase the presence of primitive (browserless) JS code.
+We added additional case-study \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} to increase the presence of primitive (browserless) JS code.
 For each case-study application, we identified several JS functions that are suitable for our testing framework.
@@
 
-For the sake of space, we chose to exclude from the follow up presentation the branches and functions which coverage time was less than two seconds.
+For the sake of space, we chose to exclude from the following presentation the branches and functions the coverage time of which was less than two seconds.
 In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
@@
 The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the aforementioned case studies with the results presented in Section~\ref{sub.sec.eval.results}.
+To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the case studies in ~Table~\ref{tbl.case.studies}.
 
@@
 
-To study the effectiveness and efficiency of our test generation framework, including three test algorithms Random~($\Random$), Genetic~($\Genetic$) and Genetic with Restart~($\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
+To study the effectiveness and efficiency of our test generation framework ($\Random$, $\Genetic$ and $\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
 Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
@@
 For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
-In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ according to the algorithm type $\Random$, $\Genetic$ and $\RGenetic$.
-Next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-Inline with the function name, we also present accumulated statistics for the function as a whole.
+In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ one for each algorithm.
+The next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
+To the right of the function name, we also present accumulated statistics for the function as a whole.
 Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
@@
 
-According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
+According to the industry standard~\cite{bray1997c4}, functions with a CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
 We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with the respective the CC 13, 14 and 16.
-Table~\ref{tbl.stats.sum} summarizes the total results of the experiment such as coverage, execution time per branch and significance.
+The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with CC's of 13, 14 and 16 respectively.
+Table~\ref{tbl.stats.sum} summarizes the results of the experiment such as coverage, execution time per branch and significance.
 
@@
 Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The values in Table~\ref{tbl.stats} highlighted as $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
+The underlined values in Table~\ref{tbl.stats} like $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
 The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
 branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of genetic approach~($\Genetic$), it may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
-We encountered three of such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines strengths of both algorithms genetic and random.
+In the case of the genetic approach, $\Genetic$ may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
+We encountered three such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
+Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines the strengths of both $\Random$ and $\Genetic$.
 It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only manged to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
+As our evaluation has shown, $\RGenetic$ not only managed to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
 branch $(69,71)$ of the \emph{initBricks} function.\\
@@
 
-Additionally, we would like to investigate how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time depended.
+Additionally, we have investigated how the coverage progresses with the increase of budget assigned per branch.
+This experiment models different testing scenarios, used in practice, which are time dependent.
 E.g.
-running tests inside IDE should be fast; as part of the CI cycle we may afford a large waiting time; regression testing over night may take hours.
+running tests inside an IDE should be fast; as part of the CI cycle we may afford a larger waiting time; regression testing over night may take hours.
 Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
@@
 When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ starts to transcend $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
+But when the budget rises to 30 seconds, $\RGenetic$ overtakes $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
 \setlength{\fboxsep}{1mm}
@@
 The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
+There are two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
+In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum of 40\%~(\emph{newGame}) and a maximum of 510\%~(\emph{isValidCard}).
 
@@
 
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with the 7 and 25 seconds per branch.
-For simple functions, the $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
+Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with  7 and 25 seconds per branch.
+For simple functions, $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
 In all categories, $\Random$ was much slower than both genetic alternatives.\\
@@
   \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch 19, 39 and 88 seconds, respectively. 
+    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch of 19, 39 and 88 seconds, respectively. 
   }
@@
 On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
+On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost of the fitness function.
 Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus not rising exceptions, and at the same time, it consists of 40 LOC.
+For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus never rising exceptions, and at the same time, it consists of 40 LOC.
 In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
@@
   \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
+    Globally, one algorithm iteration took one second on average for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse 1.4 seconds.
   }
@@
 In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs comparing to $\Genetic$.
+For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs relative to $\Genetic$.
 Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
@@
   \parbox{8.2cm}{
-    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases globally and 67\% on the difficult functions.  
-  }
-}
+    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases generally across the board and 67\% on the difficult functions.  
+  }
+}
+
+\paragraph{\textbf{RQ4 (comparison).}} Authors of \emph{Confix}~\cite{amin:ase15} have proposed three test generation strategies: 
+\begin{enumerate*}[label=(\roman*)]
+  \item only use \emph{Confix},
+  \item combine with \emph{Jalangi}~\cite{sen2013jalangi}, and
+  \item combine with manual input. 
+\end{enumerate*}
+They reported a relative increase of 2\% and 19\% in branch coverage of the second and third strategies, respectively, over the first one. Even though,
+
+The mix with manual showed 19\% increase  the best result, it is not objectively suitable for the comparison with the fully automated technique, like \emph{JEDI}.
+Unfortunately, the open source version of the \emph{Confix} we found~\footnote{\url{confix}} online does not provide actual integration with \emph{Jalangi}.
+Neither, the paper~\cite{amin:ase15} highlights any technical details of the integration.
+Also it only gave 2\% of improvement relative to
 
@@
 The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Though, the branch coverage is a common criteria used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
-Reaching a target branch is only part of the problem, we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles disseminating in exceptions.
+Although, the branch coverage is a common criterion used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
+Reaching a target branch is only part of the problem: we also need an oracle to discriminate the program's output.
+In this paper, we strike for so called ``natural'' oracles leading to exceptions.
 Using a stronger oracle for validation is future work.
 Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent unnecessary data explosion.
-Additional measure that could be taken is applying a minimization procedure, aka \emph{delta debugging}, to the GA result.
-
-Initial GA configuration introduces the threat to the \emph{internal validity} of our empirical evaluation.
+To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent on unnecessary data explosion.
+Additional measures that could be applied is a minimization procedure, aka \emph{delta debugging}~\cite{misherghi2006hdd}, to the GA result.
+
+Initial GA configuration introduces a threat to the \emph{internal validity} of our empirical evaluation.
 The parameters we used are quite standard for similar SBST frameworks, e.g.
 EvoSuite.
-Though, not reported in the paper, we performed preliminary assessment of various GA configurations, which confirmed our final decision.
-
-The threat of \emph{conclusion validity} can be affected by the GA stochastic nature.
-This risk was addressed by repeating the experiment 50 times and performing statistical analysis of the significance and effect size.
+Although, not reported in the paper, we did perform a preliminary assessment of various GA configurations, which confirmed our final decision.
+
+The threat of \emph{conclusion validity} can be affected by the stochastic nature.
+This risk was addressed by repeating the experiment of GA 50 times and performing a statistical analysis of the significance and effect size.
 We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
 
-The \emph{external validity} deals with the threat of generalization of our results due to manual selection of the experimental subjects.
-To mitigate this fact, we picked the subjects either from previously used in related research or found in open source.
-Of course, those subjects still have to met the constrains of our testing approach.
+The \emph{external validity} deals with the threat of generalization of our results due to the manual selection of the experimental subjects.
+To mitigate this fact, we selected the subjects either from previous  related research or found in open source.
+Of course, those subjects still have to meet the constraints of our testing approach.
 So, further research is required in both increasing the power of our framework and extending the validation set.
@@
 
-The last two decades were fruitful in the amount of work dedicates to the analysis and web applications and JavaScript, in particular.
-The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around two main questions:
+The last two decades have been fruitful in the amount of work dedicates to the analysis of web applications and JavaScript, in particular.
+The state-of-the-art in this field including static and dynamic analysis of JS, as well as the test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
+Therefore, we would like to organize our discussion of related work around the two main questions:
 \begin{enumerate*}
@@
 Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect constant info and feed it to the random generation.
-We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution.
+It performs static analysis to collect info about constant and feeds this data to the random generation.
+In comparison, our approach is the genetic generation.
+Additionally, we not only rely on the static information but also perform dynamic analysis to collect the run-time data.
 Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} proposes to use feedback-directed random testing for generating TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing concolic testing or type inconsistency analysis~\cite{pradel2015typedevil}.
-It suffers from typical for the symbolic analysis problems such as the handing of arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtains DOM fixtures for the FUT.
-Combined with Jalangi it can be used for both primitive and DOM test data generation.
+More recently, Kristensen et al.~\cite{kristensen2017type} propose to use feedback-directed random testing for generation of TypeScript tests based on the provided type annotations.
+
+\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing \emph{concolic testing} or {type inconsistency} analysis~\cite{pradel2015typedevil}.
+It suffers from common for the symbolic analysis problems such reasoning about arrays and loops.
+\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtain DOM fixtures for the FUT.
+Combined with Jalangi, it can be used both for the generation of primitive data and DOM.
 As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
 Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as solid alternative for program testing.
-In fact both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence.
+Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS functions without the DOM interaction.
+
+Static analysis is a powerful technique commonly used as a solid alternative for program testing.
+In fact, both techniques can benefit from one another.
+For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information for identifying potential bugs or even guarantee their absence.
 Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API.
+In the follow-up work~\cite{dom2011}, they extended the analysis with the abstractions able reason about HTML DOM and browser API.
 Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
 Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discoverers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
+It discovers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
 
 \emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the JS \emph{Proxies} in order to collect type related information.
+\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the help the JS \emph{Proxies} in order to collect type related information.
 
@@
 
-\cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-\cite{ma2015grt} guided random testing
-
-\cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-\cite{jquery2014}
-
-ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-Information-flow security for JS~\cite{hedin2012information}.
-
-Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
+%% \cite{alshahwan2011automated} automated web application testing using search based software techniques.
+
+%% \cite{ma2015grt} guided random testing
+
+%% \cite{mao2016sapienz} Multi-objective automated testing for Android application
+
+%% \cite{jquery2014}
+
+%% ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
+
+%% Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
+
+%% Information-flow security for JS~\cite{hedin2012information}.
+
+%% Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
+
+%% Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
+
+%% Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
+
+%% Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
+
+%% DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
 
@@
 
-Despite of the practical popularity of JavaScript, the only recorded in the literature attempt of adopting search-based testing for JS unit testing was done by Alshraideh~\cite{alshraideh2008complete}.
-It uses GA for branch and mutation coverage, but only deals with the limited input types booleans, integers and strings; and provides validation based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports array and DOM types, with suggest reasonable validation with the discussion of significance and effect size.
+Despite of the practical popularity of JavaScript, we have only encountered one work by Alshraideh~\cite{alshraideh2008complete} attempting to apply SBST to JavaScript.
+It uses GA for test generation with the goal cover all branches or kill all mutants, but it only deals with the limited input types such as booleans, integers and strings; and the provided validation is only based on one trivial example --- \emph{the triangle program}.
+On the contrary, our work additionally supports \emph{array} and \emph{DOM}, and conducts reasonable empirical validation with the discussion of significance and effect size.
 Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
 
-In this paper we dealt with the generation and evolution of DOM which is an example of tree-like data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim to improve test coverage of the XML-aware Java programs.
-To generate random document, it may rely on existing XML schema, or generate document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, which is difficult to comply.
+In this paper we deal with the generation and evolution of DOM which is an example of \emph{tree-like} data structure.
+\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim of improving test coverage of the XML-aware Java programs.
+To generate a random document, it may either rely on the  existing XML schema, or generate the document from scratch.
+In some sense, DOM specification can be thought of a complex XML schema, with extensive validation requirements.
 One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for mutation and crossover.
+Both tools have similar philosophy for the mutation and crossover.
 Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
 
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of SBST research~\cite{mcminn2011search}.
+Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of the SBST research~\cite{mcminn2011search}.
 Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
@@
 One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage.
-That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage.
+Most of the time, instead of searching for a test reaching a particular branch, we would like to have the set of tests maximizing the program coverage.
+That is, our solution is a vector of candidates which has the best fitness score in terms of the branch coverage.
 Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
@@
 test-suite length.
-Another direction of future work is adjusting out tool for mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That would also help us to judge about the fault revealing ability of \emph{JEDI} based on the number of killed mutants.
-As we said early in this section, SBST techniques can benefit from symbolic analysis~\cite{baars2011symbolic}.
+Another direction of future work is re-targeting out tool towards mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
+That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.
+
+% -----------------------
+Our test generation strategy is \emph{goal-oriented}~\cite{korel1992dynamic}, i.e.
+it tries to find an execution leading to a goal (statement) regardless of a concrete path taken.
+We uses control flow graph to identify implicit dependencies between nodes.
+
+The \emph{chaining approach}~\cite{ferguson1996chaining} uses data dependency to form the sequences of statements preceding the execution of a search target. 
+% -----------------------
 
@@
 \label{sec:concl}
-This paper
+
+In this paper we have introduced a novel JS unit testing framework, called \emph{JEDI}, which uses search-based techniques for generating test data.
+Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
+We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
+Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
+The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
 

### 2018-05-11 doc/icse2018/issta2018.tex
Near final version of the issre 2018 paper

@@
 \newcommand{\RGenetic}{\mathbb{G}_{10}}
+\newcommand{\Confix}{\emph{Confix}}
+\newcommand{\Jalangi}{\emph{Jalangi}}
+\newcommand{\Jedi}{\emph{JEDI}}
 
@@
 Together with HTML and CSS, it forms the core technology stack for web development.
-Because of the dynamic nature and complex interplay with HTML, JS applications are still error-prone and vulnerable.
+Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable.
 Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS applications interacting with the DOM has not yet been addressed.
@@
   for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
-    if (subDivs[no].className.indexOf('sudokuSquare') >= 0 |c \label{isGameFinished.if1.begin} |c 
+    if (subDivs[no].className.indexOf('square') >= 0 |c \label{isGameFinished.if1.begin} |c 
         && !subDivs[no].style.backgroundColor) { 
@@
       if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
-        allOk = false; |c \label{isGameFinished.unfinished} |c
-        break; 
-      }
-    }
-  } |c \label{isGameFinished.outFor} |c
-}
+        allOk = false; //target |c \label{isGameFinished.unfinished} |c
+        break;}}}} |c \label{isGameFinished.outFor} |c
 \end{lstlisting}
@@
   <div id='sudoku'>             <div id='sudoku'>
-   <div class='sudokuSquare'>    <div class='sudokuSquare'>
+   <div class='square'>          <div class='square'>
     <span></span>                 <span></span> 
@@
 
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
-This function checks the validity of a sudoku solution given by a user.
-First, we find the DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, we collect all its child DIVs (line~\ref{isGameFinished.getDivs}).
-Each DIV element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) and consists of two SPANs.
-The first span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
+Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}~\cite{sudoku}.
+This function validates a sudoku solution given by a user.
+First, it finds a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
+Then, it collects all the child \emph{divs} (line~\ref{isGameFinished.getDivs}).
+Each \emph{div} element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}), and consists of two \emph{spans}.
+The first \emph{span} contains a user input, whereas the second one (hidden by default) stores an expected value for that sudoku square.
 Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal SPAN values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
+Once, we find a square with two unequal values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
 
@@
 That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-The JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
-Henceforth, we assume that DOM is the only global variable that is allowed to be referred to in the body of the FUT.
+A JS function can take \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as a DOM state.
 In general, in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
@@
 Figure~\ref{fig.isGameFinished.tests} presents four tests that together provide the full coverage of the FUT.
-Let us look now at how following the structure of the FUT in Figure~\ref{code.isGameFinished}, we can construct the $T4$ test covering the $(10,11)$ branch.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{DIV} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this $div$ to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the $div$ consists of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
-The resulting test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
-
-As we have just seen, even for such a relatively simple example, the construction procedure of a test input is far from trivial because it requires the deep understanding of the program semantics.
+Let us take a look at how to construct the \texttt{T4} test, which covers the branch $(10,11)$, by following the structure of the FUT.
+Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with an id \textquotesingle\texttt{sudoku}\textquotesingle.
+In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{div} tag.
+The first if-condition in line~\ref{isGameFinished.if1.begin} requires this \emph{div} to be of the class \textquotesingle\texttt{square}\textquotesingle\ and also have no background color.
+The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the \emph{div} consists of two \emph{span} elements whose \emph{innerHtml} values are not equal.
+The resulting test \texttt{T4} in Figure~\ref{fig.isGameFinished.tests} meets all the above conditions.
+
+As we have just observed, even for such a relatively simple example, the test data generation can be far from trivial procedure because it requires the deep understanding of the program semantics.
 In practice, web developers often have to deal with a large number of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
@@
   \centering 
+\tikzset{
+  % add this style to all tikzpicture environments
+  every picture/.append style={
+    % enable scaling of nodes
+    transform shape,
+    % set scale factor
+    scale=1
+  }
+}
   \begin{sequencediagram}[font=\scriptsize]
@@
 Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $\mathbb{B}_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses a genetic engine for test generation.
+Our JS testing framework, called \emph{JEDI}, is a client-server application, which uses under the hood a genetic engine, for test generation.
 The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
 The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-The \Server is the key component of the  framework.
-It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}.
-Both phases will be covered in detail in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactic correctness and reports back the set of identified errors.
-\Server rejects the document if any errors were revealed and generates a new one until the generated document has no more errors.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate the native browser API calls.
+The \Server is the key component of the  framework, responsible for the \emph{Initialization} and \emph{Genetic Phases}, covered in detail in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
+
+Each newly constructed HTML document has to be assessed by the \Validator~\cite{htmlvalidator} that checks its syntactic correctness and reports back any identified errors.
+The document generation process is repeated by the \Server until there are no errors revealed.
+\Client is a \emph{Node.js}~\cite{nodejs} application that is mainly responsible for the execution of the JS code.
+We use the \emph{jsdom}~\cite{jsdom} library to model the virtual DOM and simulate the native browser API calls.
 
@@
 Let us take a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with a type signature.
-Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random and genetic phases, logging etc.
-Experimentally, we have found an optimal set of input configurations that was used across all experimental objects in Section~\ref{sec.evaluation}.
-This data is processed by the \Server during the \emph{Initialization Phase}.
-As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
-The \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
+As an input for our testing framework, \User has to provide a JS file \emph{fun.js} that contains a FUT \emph{fun} annotated with the type signature.
+Additionally, \User specifies a configuration file \emph{config} that sets various control parameters for the random and genetic phases, logging etc.
+Experimentally, we have found an optimal configuration that was consistently used in the experimental evaluation in Section~\ref{sec.evaluation}.
+Once all the data are processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
+Then, the \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
 Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
+For each branch, our framework triggers the \emph{Genetic Loop (Phase)}.
+Inside of this phase, the framework begins with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criteria is achieved, e.g.
 the limit on the number of generation attempts.
+Any HTML document produced during the genetic phase has to be first approved by the \Validator.
 Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate $p$ with the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
-The execution trace along with some supplementary information about the execution are sent back to the \Server, where the \emph{fitness value} is computed.
-The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-If a new HTML document is produced somewhere in the genetic phase, it has to be first approved by the \Validator.
+It matches the candidate solution $p$ with the type signature \emph{sig}, and invokes the instrumented JS function as \emph{ifun(p)}.
+The execution trace along with some auxiliary information is sent back to the \Server, where the final \emph{fitness value} is computed.
+A new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
 At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are covered, the algorithm reaches the end.
+Once all the branches are covered, the algorithm terminates.
 Below, we elaborate on the details of each individual phase of our test generation framework.
@@
 
-During the \emph{Initialization Phase} we analyze the FUT in order to retrieve the data required for the subsequent genetic testing.
+During the \emph{Initialization Phase} we analyze the FUT in order to facilitate the subsequent genetic testing.
 The main steps of this phase are described in Algorithm~\ref{alg.init}.
 Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants.
-Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods: \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName}
+In order to maximize the chances of generating the fittest candidate, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants, e.g.
+numeric and string literals.
+Additionally, we monitor the calls to such DOM API methods as \texttt{getElementsByTagName}, \texttt{getElementById}, and \texttt{getElementsByClassName}.
 These methods provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the FUT.
@@
 transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants.
+We instrument the FUT (line~\ref{alg.init.instr}) for run-time data collection about the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants.
 Upon the \emph{ifun} execution this information is gathered and fed back to the fitness evaluation procedure.
@@
 \begin{grammar}
-
 <JS Type Annotation> ::= /*t <Signature> */
 
-<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
-
-<DOM> ::= \texttt{dom}
+<Signature> ::= \texttt{dom} : <Type Signature> | <Type Signature>
 
@@
 \end{figure}
-One assumption made in the paper is the availability of type signatures for JS functions.
-We believe in the legitimacy of such a request due to the following observations.
-First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity.
-Second, there has been an active work on the JS type inference done both in academia~\cite{kristensen2017type} and industry, e.g.
-Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.
-
-The grammar of the JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
+
+We assume the FUT is equipped with the type signature.
+The legitimacy of such a requirement can be confirmed by the popularity of \emph{TypeScript}~\cite{typescript}, and advances in the JS type inference \emph{Flow}~\cite{flow}.
+The supported grammar of type annotations is shown in Figure~\ref{fig.js.type.annot}.
 Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures: those which refer to the global DOM and ``ordinary'' JS type signatures.
-The functions with the former kind expect some \texttt{dom} argument to be passed as the first implicit parameter of the function call.
-Whereas ordinary JS signature is a non-empty sequence of the JS types.
+We distinguish between two kinds of signatures: with the reference to the global DOM and ``ordinary'' JS type signatures.
+The former kind expects the \texttt{dom} terminal to be in place of the first parameter of the function call.
+Whereas an ordinary JS signature is a non-empty sequence of the JS types.
 The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
@@
 Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \emph{trace} in line~\ref{isGameFinished.instr.trace} is an array of labels corresponding to the sequence of executed program statements.
-All statements have to be traced because each one, in theory, can raise an exception.
-The \texttt{loopMap} map in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations of the respective for-loop.
-If no exact bound can be computed, we set it to one.
-The \texttt{branchDistance} map records the conditional distance~\cite{tracey1998automated} on the branch where the deviation from the target branch has happened.
+The global variable \texttt{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT.
+We have to trace all the statements because each one, in theory, can rise an exception.
+The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} captures the upper bound for the number for-loop iterations.
+If the exact bound is unknown, it is set to one.
+The \texttt{branchDistance} variable, computed for the \emph{problem node}, contains the distance~\cite{tracey1998automated} from the target branch.
 
@@
 function isGameFinished() {
- trace.push(2); |c \label{isGameFinished.instr.trace} |c
- var obj = document.getElementById("sudoku");
- trace.push(3);
- var subDivs = obj.getElementsByTagName("DIV");
- trace.push(4);
+ trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
+ trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
  var allOk = true;
- loopMap[5] = function () { |c \label{isGameFinished.instr.loopMap} |c
+ loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
    var no = 0;
@@
      return Math.abs(no - subDivs.length);
-   }
-   return 1;
- }();
- trace.push(5);
+   }; return 1}();
+ trace.push(3);
  for (var no = 0; no < subDivs.length; no++) {
-  trace.push(6);
-  trace.push(7);
-  if (subDivs[no].className.indexOf("sudokuSquare") >= 0 &&
+  trace.push(4);
+  if (subDivs[no].className.indexOf("square") >= 0 &&
       !subDivs[no].style.backgroundColor) {
-   trace.push(8);
-   branchDistance.push({ 
-    label: 7, 
+   trace.push(5); branchDistance.push({ label: 3, 
     distance: Math.min(
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + _K_, 
+     abs(subDivs[no].className.indexOf("square"),0)+_K_ 
      absZero(subDivs[no].style.backgroundColor))
    });
-   trace.push(9);
-   var spans = subDivs[no].getElementsByTagName("SPAN");
-   trace.push(10);
+   trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
+   trace.push(7);
    if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(11);
-    branchDistance.push({
-     label: 10,
+    trace.push(8); branchDistance.push({ label: 7, 
      distance: abs(spans[0].innerHTML, spans[1].innerHTML)
     });
-    trace.push(12);
-    allOk = false;
-    break;
+    allOk = false; break;
    } else {
-     trace.push(14);
-     branchDistance.push({label: 10,distance: _K_});
+   trace.push(9);branchDistance.push({label:7,distance:_K_});
    }
   } else {
-   trace.push(15);
-   branchDistance.push({
-    label: 7,
+   trace.push(10); branchDistance.push({ label: 3,
     distance: 
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + 
+     abs(subDivs[no].className.indexOf("square"), 0) + 
      absNegZero(subDivs[no].style.backgroundColor)
-   });
-  }
- }
- trace.push(5);
+   });}}
  trace.push(-1);
@@
 Although, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, it has been extended with the concept of \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we take a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
+As an input, we specify a configuration file \emph{config}, a target branch $b_n$ of the FUT, and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
 The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
 
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ equal to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged, or the generations limit has not been reached.
-The \emph{archive} variable stores the most fit population candidates observed so far, and the \emph{history} variable records all archives during the generation process.
-These variables both are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
-
-The initial population has $size_P$ elements, and it is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found, or the history has converged, or the generation limit $size_G$ has been reached.
+First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) to retrieve the following GA settings: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
+We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ set to 0 (line~\ref{alg.gen.iter.count}).
+We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged, or the generations limit has not been exceeded.
+The \emph{archive} variable stores the most fit population candidates observed so far, and the \emph{history} variable records all the archives during the generation process.
+The two variables are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
+
+The initial population of $size_P$ is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
+In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate is found, or the history is converged, or the generation limit $size_G$ is reached.
 But first, we need to score the current population (lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}).
@@
 The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
-Collected dynamic constants \emph{dyncinfo} are merged with the existing constant pool (line~\ref{alg.gen.eval.end}).
+Collected dynamic constants \emph{dyncinfo} are merged into the existing constant pool (line~\ref{alg.gen.eval.end}).
 Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) in $combo$.
-And it is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
+It is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
 Then, the scored population together with the current archive are sorted by fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
@@
 
-We want to generate HTML according to the WHATWG\footnote{\url{https://html.spec.whatwg.org}} specification.
+We want to generate HTML according to the WHATWG~\cite{htmlspec} specification.
 HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
@@
 Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
+According to the specification~\cite{htmlspec}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
 First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
@@
 JS applications are written with the help of countless numbers of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to native DOM manipulation.
+Moreover, some popular JS web-frameworks, such as jQuery and React~\cite{todomvc}, offer an alternative approach to native DOM manipulation.
 Before selection, the source code of a potential case-study has to be scrutinized which is a time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
+Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011, tajsbenchmarks}.
 Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We added additional case-study \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} to increase the presence of primitive (browserless) JS code.
+We added additional case-study \emph{mathjs}~\cite{mathjs} to increase the presence of primitive (browserless) JS code.
 For each case-study application, we identified several JS functions that are suitable for our testing framework.
@@
 This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
+For each function, we reported the following software metrics~\cite{jsmeter} is the tool used for measuring JS code statistics: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
 The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
@@
 
-\setlength\tabcolsep{0.6pt}
-\begin{table}[t]
+\setlength\tabcolsep{1pt}
+\begin{table}[!t]
   \caption{Summary of the Case-Studies}
@@
     \scriptsize
-  \begin{tabular}{l|l|p{3.1cm}|c|c|c|c|c|c|c|c}
+  \begin{tabular}{l|l|p{2.7cm}|c|c|c|c|c|c|c|c}
     \toprule
@@
     \hline
-    sudoku     & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & (dom)           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & (dom)         & 8  & 0 & 2 & 1 & + & + & + & - \\
+    sudoku     & helpMe & (int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
+    sudoku     & isGameFinished & ()    & 10 & 3 & 3 & 4 & + & + & + & + \\
+    sudoku     & newGame & ()           & 9  & 1 & 2 & 2 & + & + & + & + \\
+    sudoku     & revealAll & ()         & 8  & 0 & 2 & 1 & + & + & + & - \\
     %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & + & - & + & - \\
+    sudoku     & shuffleBoard & (int,int)      & 23 & 2 & 3 & 3 & + & - & + & - \\
     %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
     \hline
-    phormer    & toggleInfo & (dom,string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
+    phormer    & toggleInfo & (string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
     %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
@@
     %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & (dom,[int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
+    apophis    & initShields & ([int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
+    \hline
+    bingbong   & brickJiggler & (int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
+    bingbong   & doPaddlePower & (int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
+    bingbong   & initBricks & ([int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
     %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
@@
 
-\paragraph{\textbf{RQ4 (comparison).}} Authors of \emph{Confix}~\cite{amin:ase15} have proposed three test generation strategies: 
+\paragraph{\textbf{RQ4 (comparison).}} Authors of \emph{Confix}~\cite{amin:ase15} have proposed three strategies for test generation based on: 
 \begin{enumerate*}[label=(\roman*)]
-  \item only use \emph{Confix},
-  \item combine with \emph{Jalangi}~\cite{sen2013jalangi}, and
-  \item combine with manual input. 
+  \item \emph{Confix} entirely,
+  \item combination with \emph{Jalangi}~\cite{sen2013jalangi}, and
+  \item combination with a manual input. 
 \end{enumerate*}
-They reported a relative increase of 2\% and 19\% in branch coverage of the second and third strategies, respectively, over the first one. Even though,
-
-The mix with manual showed 19\% increase  the best result, it is not objectively suitable for the comparison with the fully automated technique, like \emph{JEDI}.
-Unfortunately, the open source version of the \emph{Confix} we found~\footnote{\url{confix}} online does not provide actual integration with \emph{Jalangi}.
-Neither, the paper~\cite{amin:ase15} highlights any technical details of the integration.
-Also it only gave 2\% of improvement relative to
+They reported a relative increase of 2\% and 19\% in branch coverage of the second and third strategies, respectively, over the first one.
+Even though, the third strategy performed the best, due to a manually enhanced data set, it is not objectively comparable with a fully automated technique, like \emph{JEDI}.
+Unfortunately, the open source version of \emph{Confix} we found online~\cite{confixgit} does not support an actual integration with \emph{Jalangi}.
+Neither, the paper~\cite{amin:ase15} highlights any implementation details of it.
+Thus in our evaluation Figure~\ref{tbl.confix.compare}, we had to fall back on the plain \emph{Confix} test generation.
+\Jedi seeks for a normal program termination during test generation, which is a stronger coverage criterion in comparison with only reaching a target branch provided by \Confix.
+Although, \Confix performs much faster (under 10 seconds), it is unable to discover hard to cover branches especially in terms of strong coverage.
+
+\begin{table}[!t]
+  \caption{Evaluation of \emph{Confix} (\#BR - total branches, \#BRC weak/strong - covered branches with exceptional/normal termination)}
+  \label{tbl.confix.compare}
+    \footnotesize
+    \centering
+    \begin{tabular}{l|l|c|c|c|c|c}
+      \toprule
+      \textbf{case-study} & \textbf{function} & \textbf{\#BR} & \textbf{\#C (weak)} & \textbf{\#C strong} & \textbf{\#tests} & \textbf{time (sec.)} \\
+      \hline
+      sudoku & helpMe          & 5  & 4 (80\%)  & 4 (80\%)  & 2 & 5 \\
+      sudoku & isGameFinished  & 5  & 2 (40\%)  & 2 (40\%)  & 2 & 5 \\
+      sudoku & newGame         & 3  & 3 (100\%) & 3 (100\%) & 4 & 6 \\
+      sudoku & revealAll       & 2  & 2 (100\%) & 0 (0\%)   & 6 & 11 \\
+      sudoku & shuffleBoard    & 7  & 5 (71\%)  & 0 (0\%)   & 2 & 5  \\
+      \hline
+      phormer & toogleInfo     & 4  & 2 (50\%)  & 2 (50\%)  & 3 & 5 \\
+      \hline
+      apophis & initShields    & 1  & 0 (0\%)   & 0 (0\%)   & 1 & 6 \\
+      \hline
+      bingbong & brickJiggler  & 2  & 0 (0\%)   & 0 (0\%)   & 1  & 3 \\
+      bingbong & doPaddlePower & 4  & 2 (50\%)  & 2 (50\%)  & 1  & 4 \\
+      bingbong & initBricks    & 18 & 3 (17\%)  & 0 (0\%) & 1  & 3 \\
+      \bottomrule
+    \end{tabular}
+\end{table}
 

### 2018-05-11 doc/issre2018/evaluation.tex
Near final version of the issre 2018 paper

--- 2018-05-11 doc/icse2018/issta2018.tex
@@
-\documentclass[sigconf,review]{acmart}
-
-\usepackage[inline]{enumitem}
-\usepackage{tablefootnote}
-\usepackage{syntax}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{booktabs} % For formal tables
-\usepackage{tikz}
-\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
-\usepackage{pgf-umlsd}
-\usepackage{tikz-uml}
-\usepackage{hyperref}
-\usepackage{upquote}
-\usepackage{listings}
-\usepackage{lsthaskell}
-\usepackage{xspace}
-\usepackage{enumitem}
-\usepackage{mdframed}
-\usepackage{algorithmic}
-\usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{pgfplots}
-\pgfplotsset{compat=newest}
-\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = red, %Colour of internal links
-  citecolor    = green %Colour of citations
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\definecolor{ltblue}{rgb}{0,0.4,0.4}
-\definecolor{dkblue}{rgb}{0,0.1,0.6}
-\definecolor{dkgreen}{rgb}{0,0.4,0}
-\definecolor{dkviolet}{rgb}{0.3,0,0.5}
-\definecolor{dkred}{rgb}{0.5,0,0}
-
-\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
-%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
-\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
-\definecolor{orange}{rgb}{1,0.45,0.13}		
-\definecolor{olive}{rgb}{0.17,0.59,0.20}
-\definecolor{brown}{rgb}{0.69,0.31,0.31}
-\definecolor{purple}{rgb}{0.38,0.18,0.81}
-\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
-\definecolor{lightred}{rgb}{1,0.4,0.5}
-% CSS
-\lstdefinelanguage{CSS}{
-  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},
-  sensitive=true,
-  morecomment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  morestring=[b]',
-  morestring=[b]",
-  alsoletter={:},
-  alsodigit={-}
-}
-
-% JavaScript
-\lstdefinelanguage{JavaScript}{
-  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
-  morecomment=[s]{/*}{*/},
-  morecomment=[l]//,
-  morestring=[b]",
-  morestring=[b]'
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  sensitive=true,	
-  alsoletter={<>=-},	
-  morecomment=[s]{<!-}{-->},
-  morestring=[b]'
-  tag=[s],
-  otherkeywords={
-  % General
-  >,
-  % Standard tags
-	<!DOCTYPE,
-  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
-	% body
-	</body, <body,
-	% Divs
-	</div, <div, </div>, 
-	% Paragraphs
-	</p, <p, </p>,
-	% scripts
-	</script, <script,
-  % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
-  },
-  ndkeywords={
-  % General
-  =,
-  % HTML attributes
-  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
-  % SVG attributes
-  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
-  % properties
-  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
-	% CSS3 properties
-  transform:, -moz-transform:, -webkit-transform:,
-  animation:, -webkit-animation:,
-  transition:,  transition-duration:, transition-property:, transition-timing-function:,
-  }
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  tagstyle=\color{blue},
-  markfirstintag=true,
-  sensitive=true,
-  alsoletter={<>=-},	
-  morecomment=[s]{<!--}{-->},
-  % tag=[s],
-  %% morestring=[b]'',
-  morestring=[b]',
-  ndkeywords={
-    % General
-    =,
-    % HTML attributes
-    id=, class= 
-  }
-}
-
-\lstdefinestyle{htmlcssjs} {%
-  % General design
-  backgroundcolor=\color{editorGray},
-  basicstyle={\scriptsize\ttfamily},   
-  frame=tb,
-  % line-numbers
-  xleftmargin={0.75cm},
-  numbers=left,
-  stepnumber=1,
-  firstnumber=1,
-  numberfirstline=true,	
-  % Code design
-  identifierstyle=\color{black},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywordstyle=\color{editorGreen}\bfseries,
-  stringstyle=\color{editorOcher}\ttfamily,
-  commentstyle=\color{brown}\ttfamily,
-  % Code
-  language=JavaScript,
-  alsolanguage=HTML5,
-  alsodigit={.:;},	
-  tabsize=2,
-  showtabs=false,
-  showspaces=false,
-  showstringspaces=false,
-  extendedchars=true,
-  breaklines=true,
-  escapechar=|c
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\listfiles % used to output the versions of all files being used by the late
-
-\newcommand{\Server}{\emph{Server}\xspace}
-\newcommand{\Client}{\emph{Client}\xspace}
-\newcommand{\User}{\emph{User}\xspace}
-\newcommand{\Validator}{\emph{Validator}\xspace}
-\newcommand{\thenBr}{\text{then}}
-\newcommand{\elseBr}{\text{else}}
-\newcommand{\inFor}{\text{inFor}}
-\newcommand{\inWhile}{\text{while}}
-\newcommand{\un}[1]{\underline{#1}}
-\newcommand{\Random}{\mathbb{R}}
-\newcommand{\Genetic}{\mathbb{G}}
-\newcommand{\RGenetic}{\mathbb{G}_{10}}
-\newcommand{\Confix}{\emph{Confix}}
-\newcommand{\Jalangi}{\emph{Jalangi}}
-\newcommand{\Jedi}{\emph{JEDI}}
-
-% Copyright
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-%% \acmYear{1997}                  
-%% \copyrightyear{2016}
-
-%% \acmPrice{15.00}
-
-\begin{document}
-\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
-
-\author{Alexander Elyasov}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands} 
-}
-\email{a.elyasov@uu.nl}
-
-\author{Wishnu Prasetya}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{s.w.b.prasetya@uu.nl}
-
-\author{Jurriaan Hage}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{j.hage@uu.nl}
-
-\begin{abstract}
-The popularity of JavaScript is continuously growing.
-Together with HTML and CSS, it forms the core technology stack for web development.
-Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable.
-Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS applications interacting with the DOM has not yet been addressed.
-In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including the global DOM state.
-We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
-It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Software and its engineering~Software testing and debugging}
-\ccsdesc[300]{Software and its engineering~Search-based software engineering}
-
-\keywords{JavaScript, search-based testing, branch coverage}
-
-\maketitle
-
-%% ------------------------------------------------------------------------
-\section{Introduction}
-\label{sec.intro}
-%% ------------------------------------------------------------------------
-
-According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript has been recognized for the sixth time in row as the most commonly used programming language.
-It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million).
-Such an ever increasing JS success can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}.
-On the other hand, due to of implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}.
-Thus, it is not surprising that once in a while critical bugs manage to break through~\cite{bugstories2017} into the web applications by Facebook, Twitter etc.
-
-Systematic unit testing is basic and, at the same time, the most effective technique for improving software quality.
-In practice, there are numerous of JS frameworks --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc.
---- intended to assist developers with the automation of various unit testing activities such as design, execution and monitoring.
-Despite the apparent abundance of the JS testing tools, the developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements.
-One of such areas is \emph{test data generation}.
-It pursues the goal of maximizing the test coverage by exercising the function under test (FUT) with different input parameters.
-Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.
-
-Generally, the problem of test data generation has been under an active study for the past three decades.
-In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the whole web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
-Out of those tools, only \emph{Confix} tries to construct a sufficient DOM fixture by translating native browser API calls into logical constraints.
-However, in the empirical evaluation~\cite{amin:ase15}, Confix only reached about 50\% in \emph{branch coverage} on the selected subjects.
-At the same time, search-based techniques have shown prominent results in achieving high branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications.
-But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of the search-based approach.
-In this paper we are breaching this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-We can summarize our contributions as follows:
-\begin{enumerate}[leftmargin=5mm]
-\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
-\item Our test generation algorithm, called ``genetic with restart'', is trying to escape search plateau by restarting GA with a new target.
-Because the full-fledged JS data flow analysis~\cite{jang2009points} is hard to reach, the new target is chosen purely based on the preceding control flow behaviour in contrast with more popular techniques~\cite{ferguson1996chaining}.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
-Moreover, we showed that on the selected subjects \emph{JEDI} outperforms \emph{Confix} ....
-\end{enumerate}
-
-The paper is structured as follows: In Section~\ref{sec.example}, we present a motivating example illustrating the challenges of generating test data for JS.
-The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} presents empirical validation and indicates the validity threats.
-Related and future work are discussed in Section~\ref{sec:related.work}.
-Section~\ref{sec:concl} concludes the paper.
-
-%% The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
-These frameworks support testing at various levels: unit, integration and functional.
-The survey also indicated a relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
-As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite this effort, test data generation continues to be poorly addressed by any of the widely used testing frameworks.
-The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of web application faults are DOM-related and introduced in the JS code, and not in other components such as HTML or CSS.
-This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
-%% --------------------------------------------------------------------
-\section{Motivating Example}
-\label{sec.example}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
-function isGameFinished() {
-  var obj = document.getElementById('sudoku'); |c \label{isGameFinished.getSudoku} |c
-  var subDivs = obj.getElementsByTagName('DIV'); |c \label{isGameFinished.getDivs} |c
-  var allOk = true;
-  for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
-    if (subDivs[no].className.indexOf('square') >= 0 |c \label{isGameFinished.if1.begin} |c 
-        && !subDivs[no].style.backgroundColor) { 
-      var spans = subDivs[no].getElementsByTagName('SPAN');
-      if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
-        allOk = false; //target |c \label{isGameFinished.unfinished} |c
-        break;}}}} |c \label{isGameFinished.outFor} |c
-\end{lstlisting}
-  \caption{JS function \texttt{isGameFinished.js} from sudoku}
-  \label{code.isGameFinished}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-                                 <div></div>                           
-  </div>                        </div> 
- </body>                       </body>    
-</html>                       </html>
-
-<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-   <div class='square'>          <div class='square'>
-    <span></span>                 <span></span> 
-    <span></span>                 <span>TEST</span>
-   </div>                        </div> 
-  </div>                        </div>
- </body>                       </body>
-</html>                       </html>
-  \end{lstlisting}
-  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
-  \label{fig.isGameFinished.tests}
-\end{figure}
-
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}~\cite{sudoku}.
-This function validates a sudoku solution given by a user.
-First, it finds a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, it collects all the child \emph{divs} (line~\ref{isGameFinished.getDivs}).
-Each \emph{div} element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}), and consists of two \emph{spans}.
-The first \emph{span} contains a user input, whereas the second one (hidden by default) stores an expected value for that sudoku square.
-Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
-
-Suppose now that we would like to unit test this function in isolation to the rest of the application.
-We aim to maximize the branch coverage as a common testing criteria~\cite{zhu1997software}.
-That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-A JS function can take \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as a DOM state.
-In general, in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
-
-%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
-
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together provide the full coverage of the FUT.
-Let us take a look at how to construct the \texttt{T4} test, which covers the branch $(10,11)$, by following the structure of the FUT.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with an id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{div} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this \emph{div} to be of the class \textquotesingle\texttt{square}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the \emph{div} consists of two \emph{span} elements whose \emph{innerHtml} values are not equal.
-The resulting test \texttt{T4} in Figure~\ref{fig.isGameFinished.tests} meets all the above conditions.
-
-As we have just observed, even for such a relatively simple example, the test data generation can be far from trivial procedure because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with a large number of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and the easiest to implement.
-It saves the developers from unexpected regressions and often documents the desired behavior of a program.
-
-%% --------------------------------------------------------------------
-\section{Test Generation Framework}
-\label{sec.framework}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t!]
-  \centering 
-\tikzset{
-  % add this style to all tikzpicture environments
-  every picture/.append style={
-    % enable scaling of nodes
-    transform shape,
-    % set scale factor
-    scale=1
-  }
-}
-  \begin{sequencediagram}[font=\scriptsize]
-
-    \renewcommand\unitfactor{0.35}
-    \newinst{user}{\textbf{User}}
-    \newinst{server}{\textbf{Server}}
-    \newinst[1]{validator}{\textbf{Validator}}
-    \newinst{client}{\textbf{Client}}
-
-    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
-      \end{call}
-
-      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
-      \end{call}
-
-      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
-      \end{call}
-
-      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
-          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
-          \end{call}
-          \prelevel
-        \end{sdblock}
-
-        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
-            \end{call}
-
-            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
-            \end{callself}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
-          \end{callself}
-          \prelevel
-        \end{sdblock}
-        \mess{server}{best fitness}{user}
-
-      \end{sdblock}
-    \end{call}
-  \end{sequencediagram}
-  \caption{The architecture of the test framework}
-  \label{fig.framework.architect} 
-\end{figure}
-
-Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $\mathbb{B}_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application, which uses under the hood a genetic engine, for test generation.
-The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-The \Server is the key component of the  framework, responsible for the \emph{Initialization} and \emph{Genetic Phases}, covered in detail in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Each newly constructed HTML document has to be assessed by the \Validator~\cite{htmlvalidator} that checks its syntactic correctness and reports back any identified errors.
-The document generation process is repeated by the \Server until there are no errors revealed.
-\Client is a \emph{Node.js}~\cite{nodejs} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}~\cite{jsdom} library to model the virtual DOM and simulate the native browser API calls.
-
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
-Let us take a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide a JS file \emph{fun.js} that contains a FUT \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that sets various control parameters for the random and genetic phases, logging etc.
-Experimentally, we have found an optimal configuration that was consistently used in the experimental evaluation in Section~\ref{sec.evaluation}.
-Once all the data are processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
-Then, the \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
-Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework triggers the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework begins with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criteria is achieved, e.g.
-the limit on the number of generation attempts.
-Any HTML document produced during the genetic phase has to be first approved by the \Validator.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate solution $p$ with the type signature \emph{sig}, and invokes the instrumented JS function as \emph{ifun(p)}.
-The execution trace along with some auxiliary information is sent back to the \Server, where the final \emph{fitness value} is computed.
-A new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are covered, the algorithm terminates.
-Below, we elaborate on the details of each individual phase of our test generation framework.
-
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
-
-During the \emph{Initialization Phase} we analyze the FUT in order to facilitate the subsequent genetic testing.
-The main steps of this phase are described in Algorithm~\ref{alg.init}.
-Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants, e.g.
-numeric and string literals.
-Additionally, we monitor the calls to such DOM API methods as \texttt{getElementsByTagName}, \texttt{getElementById}, and \texttt{getElementsByClassName}.
-These methods provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the FUT.
-The next step is to normalize the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) for run-time data collection about the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants.
-Upon the \emph{ifun} execution this information is gathered and fed back to the fitness evaluation procedure.
-Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
-
-\subsubsection{Supported Types}
-\label{sub.sec.sup.types}
-
-\begin{figure}[t!]
-\setlength{\grammarparsep}{3pt}
-\footnotesize
-\begin{grammar}
-<JS Type Annotation> ::= /*t <Signature> */
-
-<Signature> ::= \texttt{dom} : <Type Signature> | <Type Signature>
-
-<Type Signature> ::= <Type> | <Type> : <Type Signature>
-
-<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
-
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
-
-<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
-\end{grammar}
-\caption{Grammar of supported JS type annotations}
-\label{fig.js.type.annot}
-\end{figure}
-
-We assume the FUT is equipped with the type signature.
-The legitimacy of such a requirement can be confirmed by the popularity of \emph{TypeScript}~\cite{typescript}, and advances in the JS type inference \emph{Flow}~\cite{flow}.
-The supported grammar of type annotations is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures: with the reference to the global DOM and ``ordinary'' JS type signatures.
-The former kind expects the \texttt{dom} terminal to be in place of the first parameter of the function call.
-Whereas an ordinary JS signature is a non-empty sequence of the JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
-
-\subsubsection{Instrumentation}
-\label{sub.sec.instrument}
-
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \texttt{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT.
-We have to trace all the statements because each one, in theory, can rise an exception.
-The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} captures the upper bound for the number for-loop iterations.
-If the exact bound is unknown, it is set to one.
-The \texttt{branchDistance} variable, computed for the \emph{problem node}, contains the distance~\cite{tracey1998automated} from the target branch.
-
-%TODO: maybe expand this section with the JS type casting for branch distance computation
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function isGameFinished() {
- trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
- trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
- var allOk = true;
- loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
-   var no = 0;
-   if (subDivs.length || subDivs.length == 0) {
-     return Math.abs(no - subDivs.length);
-   }; return 1}();
- trace.push(3);
- for (var no = 0; no < subDivs.length; no++) {
-  trace.push(4);
-  if (subDivs[no].className.indexOf("square") >= 0 &&
-      !subDivs[no].style.backgroundColor) {
-   trace.push(5); branchDistance.push({ label: 3, 
-    distance: Math.min(
-     abs(subDivs[no].className.indexOf("square"),0)+_K_ 
-     absZero(subDivs[no].style.backgroundColor))
-   });
-   trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
-   trace.push(7);
-   if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(8); branchDistance.push({ label: 7, 
-     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-    });
-    allOk = false; break;
-   } else {
-   trace.push(9);branchDistance.push({label:7,distance:_K_});
-   }
-  } else {
-   trace.push(10); branchDistance.push({ label: 3,
-    distance: 
-     abs(subDivs[no].className.indexOf("square"), 0) + 
-     absNegZero(subDivs[no].style.backgroundColor)
-   });}}
- trace.push(-1);
-}
-\end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
-  \label{code.isGameFinished.instr}
-\end{figure}
-
-\subsection{Genetic Phase}
-\label{sub.sec.genetic.phase}
-
-\begin{algorithm}[!t]
-  \caption{Genetic Phase}
-  \label{alg.gen}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{
-    $config$ is a GA configuration file\\
-    $b_n$ is a target branch of FUT\\
-    $(cfg, branches, cinfo, ifun, sig)$ output of Algorithm~\ref{alg.init}
-  }
-  \Output{
-     $(f^*, p^*)$ the best population candidate and its fitness score
-  }
-  \Fn{$Genetic(b_n, cfg, cinfo, config, ifun, sig)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M,size_{H}) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
-    $target \longleftarrow b_n$\label{alg.gen.init.target}\; 
-    $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
-    $historyConverged \longleftarrow true$\;
-    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
-      $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\; 
-      $history \longleftarrow \emptyset$\label{alg.gen.init.history}\; 
-      $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
-      \Repeat{$isPerfect(f^*) \vee historyConverged \vee (i > size_G)$}{\label{alg.gen.loop.begin}
-        $scoredPop \longleftarrow \emptyset$\;
-        $history \longleftarrow history \cup archive$\;
-        \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
-          $args \longleftarrow CoerceArguments(p, sig)$\label{alg.gen.make.args}\;
-          $(tr, d_B, d_L, dyncinfo) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
-          $f \longleftarrow Score(target, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
-          $cinfo \longleftarrow cinfo \cup dyncinfo$\label{alg.gen.eval.end}\;
-          $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        }
-        $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
-        $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
-        $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
-        $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
-        $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
-        $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
-        $i \longleftarrow i + 1$\;
-        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
-      }\label{alg.gen.loop.end}
-      $target \longleftarrow NewTarget(branches, b_n)$\label{alg.gen.new.target}\;
-    }\label{alg.gen.converged.loop.end}
-    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
-  }
-\end{algorithm}
-
-The heart of our test data generation framework is in the \emph{Genetic Phase}.
-Although, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, it has been extended with the concept of \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we specify a configuration file \emph{config}, a target branch $b_n$ of the FUT, and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
-The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
-
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) to retrieve the following GA settings: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ set to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged, or the generations limit has not been exceeded.
-The \emph{archive} variable stores the most fit population candidates observed so far, and the \emph{history} variable records all the archives during the generation process.
-The two variables are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
-
-The initial population of $size_P$ is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate is found, or the history is converged, or the generation limit $size_G$ is reached.
-But first, we need to score the current population (lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}).
-Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
-Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
-Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
-This gives us a 4-tuple consisting of an execution trace ($tr$), branch ($d_B$), loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
-The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
-Collected dynamic constants \emph{dyncinfo} are merged into the existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) in $combo$.
-It is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
-If $f^*$ is a \emph{perfect} candidate, the solution is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
-
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{mcminn2004search}.
-For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it accidentally.
-In such a situation, we find ourselves being trapped on a flat space, with a small chance to escape.
-In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
-At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
-If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
-It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
-Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
-In practice, we only consider extensions upto length two.
-
-The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
-In the rest of this section, we provide implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and the fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our main focus here is on the generation and transformation of HTML documents.
-
-\begin{table}
-  \caption{Genetic Operation for the JS Types}
-  \label{tbl.gen.oper.js.types}
-    \footnotesize
-  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
-    \toprule
-    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
-    \hline
-    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
-    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
-    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
-    Random    & Array  & array of a respective type upto length five\\
-    \hline
-    Crossover & Bool   & pick at random one out of two given booleans \\
-    Crossover & Int    & pick at random one out of two given integers\\
-    Crossover & Float  & pick at random one out of two given floats\\
-    Crossover & String & pick at random one out of two single point crossovers\\
-    Crossover & Array  & similar crossover operator as for strings\\
-    \hline
-    Mutation  & Bool   & flip the boolean constant\\
-    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
-    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
-    Mutation  & String & random string, remove char or apply pred(suc) char\\
-    Mutation  & Array  & Mutate a random element in array according to its type\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsubsection{Random HTML Generation}
-\label{sub.sub.sec.random.html}
-
-\begin{figure}[t]
-  \begin{haskell}
-instance Arbitrary Html where
-  arbitrary = evalStateT generateHTML defaultState
-
-generateHTML :: GenHtmlState |c \label{ref.generateHTML.begin} |c
-generateHTML = do
-  state <- get |c \label{ref.generateHTML.getState} |c   
-  let d = getDepth state |c \label{ref.generateHTML.getDepth} |c
-  if d == 0
-  then lift \dollar return \dollar toHtml "HTML" |c \label{ref.generateHTML.returnString} |c
-  else do put state{depth = d - 1} |c \label{ref.generateHTML.updateState} |c
-           head <- generateHEAD |c \label{ref.generateHTML.newHead} |c
-           body <- generateBODY |c \label{ref.generateHTML.newBody} |c
-           lift\dollar return \dollar docTypeHtml \dollar head >> body |c \label{ref.generateHTML.end} |c
-
-data Tag = HTML | HEAD | BODY | ...
-type Context = CFlow | CMetadata | ...
-data HtmlState = |c \label{ref.HtmlState.begin} |c
-  HtmlState { depth    :: Int,           degree  :: Int    
-             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
-             , tags    :: [Tag],         ids     :: [String]
-             , classes :: [String] } |c \label{ref.HtmlState.end} |c
-type GenState s = StateT s Gen |c \label{ref.GenState} |c
-type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
-  \end{haskell}
-  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
-  \label{fig.html.arb.def}
-\end{figure}
-
-We want to generate HTML according to the WHATWG~\cite{htmlspec} specification.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-The recent HTML5 standard defines more than a hundred of tags and attributes which both have to comply with extremely complex logic to constitute  syntactically valid HTML.
-Browsers are usually tolerant to syntactic errors in HTML.
-They will silently fix them and display the page anyway.
-
-In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because the complexity of HTML and the lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} shows that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) represents the internal state of \texttt{Html}.
-The state is composed of the following components:
-\begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of the generated HTML 
-\item \texttt{ctx} is the current value of the HTML content model stack 
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
-\end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag is the value of the \texttt{GenHtmlState} type.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to the specification~\cite{htmlspec}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
-First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
-Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
-
-\subsubsection{Genetic HTML Operations}
-\label{sub.sub.sec.genetic.oper}
-
-In essence, an HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for \emph{expression trees} in genetic programming.
-
-\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
-
-\textbf{HTML Mutations} belong to one of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
-The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
-The \emph{DropTree} mutation removes the whole sub-tree at a randomly chosen node.
-\emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
-Currently, we instantiated the \emph{ShuffleAttributes} mutation only for the types \emph{class} and \emph{id}.
-In total, this gives us four mutations to choose from in order to evolve an HTML document.
-
-\subsubsection{Fitness Function}
-\label{sub.sub.sec.fitness.fun}
-
-The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating valid input data.
-The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
-without premature exception.
-Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-The FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
-\[
-\textit{fit}(n) = \text{approach level} +
-\begin{cases}
- 1/2 * (\frac{\text{branch distance}}{1 + \text{branch distance}}) & \text{if no exception}\\
- 1                                  &  \text{otherwise}
-\end{cases}
-\]
-The final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
-\[
-\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
-\]
-Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
- \[
-\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
-\]
-
-The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
-the node causing the deviation.
-Since any node can potentially be exceptional, they all contribute to the approach level, in addition to the conditional branches.
-Loops have to be treated in a special way because we need to estimate the maximum number of iterations.
-In the case of a for-loop, at run-time we can always provide an exact bound.
-For while-loops, we assume that it has to be passed at least once.
-The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
-
-\subsubsection{Limitations}
-\label{sub.sub.sec.limit}
-
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
 %% --------------------------------------------------------------------
@@
 
-In order to evaluate the feasibility of our test framework, we conducted an empirical evaluation on a set of case-studies (see Section~\ref{sub.sec.case.studies}).
-All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which plays the role of our baseline, is \emph{Random} ($\Random$).
-Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is important to note  that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic Algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On the one hand, the smaller window size forces the GA to converge faster and quickly discovers stagnation on a flat space.
-On the other hand, the small window can lead to premature archive convergence, which prevents the right genetic combination from being triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose to report only that case in the paper.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{fraser2011evosuite}.
-
-\begin{table}
+\begin{table}[!t]
   \caption{Genetic Algorithm Configurations}
@@
   \scriptsize
+  \centering
   \begin{tabular}{l|r|r|r}
@@
 
+In order to evaluate the feasibility of our test framework, we conducted an empirical study on a set of subjects (see Section~\ref{sub.sec.case.studies}).
+All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
+We have created three different instances of the JS testing framework --- each one is based on a slight variation of the underlying genetic algorithm.
+The first version, which plays the role of our baseline, is \emph{Random} ($\Random$).
+Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
+It is important to note  that the random version also benefits from both preliminary static analysis and dynamic constant propagation as part of the fitness evaluation.
+The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
+The last version is \emph{Genetic with Restart} ($\RGenetic$).
+It is based on the genetic Algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
+On the one hand, the smaller window size forces the GA to converge faster and quickly discovers stagnation.
+On the other hand, the small window can lead to premature archive convergence, which prevents the right genetic combination from being triggered.
+We have experimented with two different windows of size 5 and 10.
+But since the latter one ($\RGenetic$) showed the best performance over all, we chose to report only that case in the paper.
+Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
+The initial setup for genetic algorithm is similar to other frameworks, e.g.
+\emph{EvoSuite}~\cite{fraser2011evosuite}.
+
 By carrying the evaluation, we would like to answer the following research questions:
 \begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
-Which testing algorithm is the most effective?
-How does effectiveness change with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost per iteration?
-\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
+\item[\textbf{RQ1 (effectiveness):}] What is the branch coverage?
+ %% achieved by our testing framework? Which testing algorithm is the most effective? How does effectiveness change with the budget per branch?
+\item[\textbf{RQ2 (efficiency):}] What is the coverage time per branch?
+% What is the cost per iteration?
+\item[\textbf{RQ3 (significance):}] Are the results statistically significant?
+%% What is the statistical significance and effect size of our experimental results?
 \item[\textbf{RQ4 (comparison):}] What is the branch coverage of \emph{Confix}?
@@
 
+\input{table-case-studies}
+
 Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
 JS applications are written with the help of countless numbers of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React~\cite{todomvc}, offer an alternative approach to native DOM manipulation.
+Moreover, some popular JS web-frameworks, such as jQuery and React~\cite{todomvc}, implement their own API for DOM manipulation.
 Before selection, the source code of a potential case-study has to be scrutinized which is a time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011, tajsbenchmarks}.
+Therefore, we decided to primarily focus on the evaluation of the JS subjects already established in the related research such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011, tajsbenchmarks}.
 Both of these works address the problem of testing of JS application with the reference to the browser DOM.
@@
 
-For the sake of space, we chose to exclude from the following presentation the branches and functions the coverage time of which was less than two seconds.
+To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our framework on the case studies in Table~\ref{tbl.case.studies}.
+For the sake of space, we omitted from the following presentation the functions and branches with the coverage time less than two seconds.
 In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
 This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics~\cite{jsmeter} is the tool used for measuring JS code statistics: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the case studies in ~Table~\ref{tbl.case.studies}.
+For each function, we reported the following software metrics~\cite{jsmeter}: lines of code~(\textbf{loc}), number of conditions~(\textbf{c}), depth~(\textbf{d}), and cyclomatic complexity~(\textbf{cc}).
+The four rightmost columns \textbf{dom}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{DOM}, \emph{id}, \emph{tag} or \emph{class} respectively.
 
-\setlength\tabcolsep{1pt}
-\begin{table}[!t]
-  \caption{Summary of the Case-Studies}
-  \label{tbl.case.studies}
-  %\resizebox{\textwidth}{!}{
-    \scriptsize
-  \begin{tabular}{l|l|p{2.7cm}|c|c|c|c|c|c|c|c}
-    \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & helpMe & (int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & ()    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & ()           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & ()         & 8  & 0 & 2 & 1 & + & + & + & - \\
-    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (int,int)      & 23 & 2 & 3 & 3 & + & - & + & - \\
-    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
-    \hline
-    phormer    & toggleInfo & (string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
-    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
-    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
-    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
-    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
-    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
-    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
-    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
-    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
-    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
-    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & ([int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & ([int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
-    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
-    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
-    \hline
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
-    %% \hline
-    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
-    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
-    \bottomrule
-  \end{tabular}
-%}
-\end{table}
+\begin{figure*}[!t]
+\centering
+\begin{minipage}[c]{.43\linewidth}
+\centering
+\subfloat[Result Summary (L - large, M - medium, S - small)]{
+  \centering
+  \input{evaluation-summary-short}
+\label{tbl.stats.sum}
+}\\
+\subfloat[\emph{Confix} Evaluation: \textbf{\#BR} total branches, \textbf{\#C} covered branches]{
+  \centering
+  \input{evaluation-summary-confix}
+\label{tbl.confix.compare}
+}\\
+\subfloat[Branch Coverage Progress]{
+  \centering
+  \input{graph-coverage-progress}
+  \label{fig.budget.progress}
+}\\
+\begin{minipage}[c]{.6\linewidth}
+\subfloat[Time $t$]{
+  \centering
+  \input{graph-generation-time}
+  \label{fig.gen.time.comp}
+}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{.3\linewidth}
+\subfloat[Speed $t/i$]{
+  \centering
+  \input{graph-generation-speed}
+  \label{fig.get.cost}
+}
+\end{minipage}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{.55\linewidth}
+\subfloat[Test Generation Summary]{
+  \input{evaluation-summary-full}
+  \label{tbl.stats}
+}
+\end{minipage}
+\caption{Statistics of experimental results for $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
+\label{lab3}
+\end{figure*}
 
@@
 
-\setlength\tabcolsep{.98pt}
-\begin{table}[!t]
-  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
-  \label{tbl.stats}
-    \scriptsize
-    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
-      \toprule
-      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{2-10} % \!:\!
-                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \midrule
-    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \textbf{newGame}*   
-                             & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \textbf{revealAll}*  
-                             & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-    \textbf{shuffleBoard}*   
-                             & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \hline
-   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \hline
-   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \hline
-   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \hline
-   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-   \midrule
-    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
-    \bottomrule
-   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \hline
-    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \hline
-    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
-    \midrule
-    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
-    %% \midrule
-    %% \midrule
-    \bottomrule
-    \bottomrule  
-    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-To study the effectiveness and efficiency of our test generation framework ($\Random$, $\Genetic$ and $\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
+To study the effectiveness and efficiency of our test generation framework, we exercised each algorithm ($\Random$, $\Genetic$ and $\RGenetic$) against all branches of the functions in Table~\ref{tbl.case.studies}.
 Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
+Table~\ref{tbl.stats} summarizes the evaluation results.
+For each algorithm, we computed the following \emph{medians} per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
 In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ one for each algorithm.
 The next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-To the right of the function name, we also present accumulated statistics for the function as a whole.
-Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function.
+To the right of the function name, we also present accumulated statistics for the function as a whole\footnote{because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
+see the \emph{toggleInfo} function}
 
-According to the industry standard~\cite{bray1997c4}, functions with a CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
+According to the industry standard~\cite{bray1997c4}, functions with a CC below 10 are considered as easy to test, and above 10 are reasonably challenging.
 We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with CC's of 13, 14 and 16 respectively.
+The three functions \mbox{\emph{initBricks}}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with CC's of 13, 14 and 16 respectively.
 Table~\ref{tbl.stats.sum} summarizes the results of the experiment such as coverage, execution time per branch and significance.
 
-\begin{table}[!t]
-  \caption{Result Summary (L - large, M - medium, S - small)}
-  \label{tbl.stats.sum}
-    \footnotesize
-    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
-      \toprule
-      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
-      \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{8-16}
-                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
-      \midrule
-      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
-      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
-      \midrule
-      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
+\textbf{RQ1 (effectiveness)}: To answer this question, we measure the branch coverage achieved by each test generation algorithm.
 Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
 The underlined values in Table~\ref{tbl.stats} like $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
-The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
+The main reason for the random generation~($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
 branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of the genetic approach, $\Genetic$ may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
+In the case of the genetic approach~($\Genetic$), it  may get stuck at a plateau because the fitness function does not provide sufficient guidance, whereas $\Random$ could still escape the plateau by sheer luck.
 We encountered three such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines the strengths of both $\Random$ and $\Genetic$.
+They motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines the strengths of both $\Random$ and $\Genetic$.
 It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only managed to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
+As our evaluation has shown, $\RGenetic$ not only managed to outperform $\Random$ and cover the three problematic branches above, but it generally improved the results of $\Genetic$, e.g.
 branch $(69,71)$ of the \emph{initBricks} function.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
+\framebox{
+  \parbox[t][1.1cm]{0.95\linewidth}{
     Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
@@
 
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig.budget.progress}
-\end{figure}
-
 Additionally, we have investigated how the coverage progresses with the increase of budget assigned per branch.
@@
 E.g.
-running tests inside an IDE should be fast; as part of the CI cycle we may afford a larger waiting time; regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
+running tests inside an IDE should be fast; as part of the continuous integration we may afford a longer waiting time; and regression testing over night may take hours.
+Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across budget categories from 5 to 150 seconds per branch.
 Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
@@
 But when the budget rises to 30 seconds, $\RGenetic$ overtakes $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
+\framebox{
+  \parbox[t][0.7cm]{0.95\linewidth}{
+We suggest to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$.
   }
@@
 
-\paragraph{\textbf{RQ2 (efficiency).}}
- To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
-Based on this information, we suggest an estimate on the execution time of the testing framework.
+\textbf{RQ2 (efficiency):} To answer this question, we compare the actual execution time of our test generation algorithms.
 The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
@@
 
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=950,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        restrict y to domain*=0:1350, % Cut values off at 14
-        visualization depends on=rawy\as\rawy, % Save the unclipped values
-        after end axis/.code={ % Draw line indicating break
-          \draw [ultra thick, white, decoration={snake, amplitude=1pt}, decorate] (rel axis cs:0,1.05) -- (rel axis cs:1,1.05);
-        },
-        nodes near coords={%
-          \pgfmathprintnumber{\rawy}% Print unclipped values
-        },
-        every node near coord/.append style={rotate=90,anchor=west,font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,270) (isGameFinished*,220) (newGame*,14) (revealAll*,50) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,514) (isValidVISA,95) (initShields*,5) (brickJiggler*,8) (doPaddlePower*,15)  (initBricks*,2379) (do\_draw,625) (prob\_gamma,710)};
-      \addplot[fill=red] coordinates {(helpMe*,47)  (isGameFinished*,30)  (newGame*,9)  (revealAll*,44) (shuffleBoard*,26) (toggleInfo*,7) (isValidCard,8)   (isValidVISA,3)  (initShields*,5) (brickJiggler*,4) (doPaddlePower*,140) (initBricks*,474) (do\_draw,1295) (prob\_gamma,84)};
-      \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Overall test generation time per function.}
-  \label{fig.gen.time.comp}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=4,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,1.24) (isGameFinished*,0.83) (newGame*,0.78) (revealAll*,0.83) (shuffleBoard*,1.93) (toggleInfo*,1) (isValidCard,0.51) (isValidVISA,0.47) (initShields*,0.83) (brickJiggler*,1.14) (doPaddlePower*,0.79)  (initBricks*,1.68) (do\_draw,2.33) (prob\_gamma,0.35)};
-      \addplot[fill=red] coordinates {(helpMe*,0.77)  (isGameFinished*,0.94)  (newGame*,0.81)  (revealAll*,1) (shuffleBoard*,1.73) (toggleInfo*,1) (isValidCard,0.38)   (isValidVISA,0.38)  (initShields*,0.83) (brickJiggler*,0.67) (doPaddlePower*,0.69) (initBricks*,0.8) (do\_draw,3.38) (prob\_gamma,0.52)};
-      \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Speed of test generation measured as $t/i$}
-    \label{fig.get.cost}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
 Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with  7 and 25 seconds per branch.
-For simple functions, $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
+For simple functions, the $\Genetic$ performance was quite close to $\RGenetic$, only 9 seconds, but for difficult functions it was two times slower.
 In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch of 19, 39 and 88 seconds, respectively. 
+\framebox{
+  \parbox[t][0.7cm]{0.95\linewidth}{
+    $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch of 19, 39 and 88 seconds, respectively.
   }
@@
 
-Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
-This information is useful when configuring the maximal generation limit.
+Another question related to the efficiency is the computational cost of one iteration of each algorithm.
+It useful to know in order to choose the generation limit.
 The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
 it measures the speed of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost of the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus never rising exceptions, and at the same time, it consists of 40 LOC.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second on average for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse 1.4 seconds.
+Figure~\ref{fig.get.cost} presents the cost comparison for all three algorithms in our study.
+Among the factors impacting the iteration cost are the population size (50 candidates in our case) and the fitness evaluation of one candidate.
+The length of an execution trace correlates with the fitness evaluation.
+So, an exceptional program termination leads to short traces, whereas loops tend to produce longer traces.
+For example, the \emph{do_draw} function has long traces because it only operates with the primitive types thus never rising exceptions, and at the same time, it consists of 40 LOC.
+In our evaluation, the iteration cost varied between 0.25 and 3.59 seconds.\\
+\framebox{
+  \parbox[t][0.7cm]{0.95\linewidth}{
+    On average, one algorithm iteration took one second for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse 1.4 seconds.
   }
@@
 
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
+\textbf{RQ3 (significance):} Our testing framework is randomized by nature, therefore we need to conduct a statistical analysis to assess the \emph{significance} and \emph{effect size} of our results.
+This analysis is based on 50 executions produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
 Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
 In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs relative to $\Genetic$.
+Thus, the higher the value in the $_{\Genetic}^{\Random}$ column, indicates that $\Random$ is slower comparison with $\Genetic$.
 Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
+\framebox{
+  \parbox[t][0.65cm]{0.95\linewidth}{
     Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases generally across the board and 67\% on the difficult functions.
@@
 
-\paragraph{\textbf{RQ4 (comparison).}} Authors of \emph{Confix}~\cite{amin:ase15} have proposed three strategies for test generation based on: 
+\textbf{RQ4 (comparison):} We evaluated \Confix\ as the only available alternative for the generation of DOM fixtures.
+In \cite{amin:ase15} the authors have proposed three strategies for test generation based on:
 \begin{enumerate*}[label=(\roman*)]
   \item \emph{Confix} entirely,
-  \item combination with \emph{Jalangi}~\cite{sen2013jalangi}, and
-  \item combination with a manual input. 
+  \item \emph{Jalangi}~\cite{sen2013jalangi} combination, and
+  \item semi-manual approach.
 \end{enumerate*}
-They reported a relative increase of 2\% and 19\% in branch coverage of the second and third strategies, respectively, over the first one.
-Even though, the third strategy performed the best, due to a manually enhanced data set, it is not objectively comparable with a fully automated technique, like \emph{JEDI}.
-Unfortunately, the open source version of \emph{Confix} we found online~\cite{confixgit} does not support an actual integration with \emph{Jalangi}.
-Neither, the paper~\cite{amin:ase15} highlights any implementation details of it.
-Thus in our evaluation Figure~\ref{tbl.confix.compare}, we had to fall back on the plain \emph{Confix} test generation.
-\Jedi seeks for a normal program termination during test generation, which is a stronger coverage criterion in comparison with only reaching a target branch provided by \Confix.
-Although, \Confix performs much faster (under 10 seconds), it is unable to discover hard to cover branches especially in terms of strong coverage.
+Even though, the third strategy outperformed pure \Confix by 19\%, it is not suitable for an objective comparison with a fully automated technique, like \Jedi.
+On the other hand, the combination with \Jalangi could be used for the evaluation, but it only improved branch coverage by 2\%, and the \Confix version available online~\cite{confixgit} has no actual integration with \Jalangi.
+Thus we had to fall back on the plain \Confix test generation, results are present in Figure~\ref{tbl.confix.compare}.
+\Jedi seeks for a normal program termination during test generation, which is a stronger coverage criterion in comparison with only reaching a target branch provided by \Confix.\\
+\framebox{
+  \parbox[t][0.65cm]{0.95\linewidth}{
+Although, \Confix performs much faster (under 10 seconds), it is unable to reach hard to cover branches.
+  }
+}
 
-\begin{table}[!t]
-  \caption{Evaluation of \emph{Confix} (\#BR - total branches, \#BRC weak/strong - covered branches with exceptional/normal termination)}
-  \label{tbl.confix.compare}
-    \footnotesize
-    \centering
-    \begin{tabular}{l|l|c|c|c|c|c}
-      \toprule
-      \textbf{case-study} & \textbf{function} & \textbf{\#BR} & \textbf{\#C (weak)} & \textbf{\#C strong} & \textbf{\#tests} & \textbf{time (sec.)} \\
-      \hline
-      sudoku & helpMe          & 5  & 4 (80\%)  & 4 (80\%)  & 2 & 5 \\
-      sudoku & isGameFinished  & 5  & 2 (40\%)  & 2 (40\%)  & 2 & 5 \\
-      sudoku & newGame         & 3  & 3 (100\%) & 3 (100\%) & 4 & 6 \\
-      sudoku & revealAll       & 2  & 2 (100\%) & 0 (0\%)   & 6 & 11 \\
-      sudoku & shuffleBoard    & 7  & 5 (71\%)  & 0 (0\%)   & 2 & 5  \\
-      \hline
-      phormer & toogleInfo     & 4  & 2 (50\%)  & 2 (50\%)  & 3 & 5 \\
-      \hline
-      apophis & initShields    & 1  & 0 (0\%)   & 0 (0\%)   & 1 & 6 \\
-      \hline
-      bingbong & brickJiggler  & 2  & 0 (0\%)   & 0 (0\%)   & 1  & 3 \\
-      bingbong & doPaddlePower & 4  & 2 (50\%)  & 2 (50\%)  & 1  & 4 \\
-      bingbong & initBricks    & 18 & 3 (17\%)  & 0 (0\%) & 1  & 3 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{Threats to Validity}}
-The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Although, the branch coverage is a common criterion used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
+\textbf{Threats to Validity:}
+The \emph{construct validity} threat comes from the choice of measurements: branch coverage and execution time.
+Although, the branch coverage is a common criterion used in practice, the actual fault finding capability is a stronger indication of testing adequacy.
 Reaching a target branch is only part of the problem: we also need an oracle to discriminate the program's output.
@@
 So, further research is required in both increasing the power of our framework and extending the validation set.
-
-%% --------------------------------------------------------------------
-\section{Related and Future Work}
-\label{sec:related.work}
-%% --------------------------------------------------------------------
-
-The last two decades have been fruitful in the amount of work dedicates to the analysis of web applications and JavaScript, in particular.
-The state-of-the-art in this field including static and dynamic analysis of JS, as well as the test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around the two main questions:
-\begin{enumerate*}
-\item test data generation for JS functions interacting with the DOM, and
-\item the application of search-based techniques for that problem.
-\end{enumerate*}
-
-\subsection{Test Data Generation for JavaScript}
-
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect info about constant and feeds this data to the random generation.
-In comparison, our approach is the genetic generation.
-Additionally, we not only rely on the static information but also perform dynamic analysis to collect the run-time data.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} propose to use feedback-directed random testing for generation of TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing \emph{concolic testing} or {type inconsistency} analysis~\cite{pradel2015typedevil}.
-It suffers from common for the symbolic analysis problems such reasoning about arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtain DOM fixtures for the FUT.
-Combined with Jalangi, it can be used both for the generation of primitive data and DOM.
-As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
-Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS functions without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as a solid alternative for program testing.
-In fact, both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information for identifying potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011}, they extended the analysis with the abstractions able reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discovers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-
-\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the help the JS \emph{Proxies} in order to collect type related information.
-
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-
-%% \cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-%% \cite{ma2015grt} guided random testing
-
-%% \cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-%% \cite{jquery2014}
-
-%% ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-%% Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-%% Information-flow security for JS~\cite{hedin2012information}.
-
-%% Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-%% Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-%% Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-%% Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-%% DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Search-Based Test Data Generation}
-\label{sub.sec.search.based}
-
-Despite of the practical popularity of JavaScript, we have only encountered one work by Alshraideh~\cite{alshraideh2008complete} attempting to apply SBST to JavaScript.
-It uses GA for test generation with the goal cover all branches or kill all mutants, but it only deals with the limited input types such as booleans, integers and strings; and the provided validation is only based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports \emph{array} and \emph{DOM}, and conducts reasonable empirical validation with the discussion of significance and effect size.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-In this paper we deal with the generation and evolution of DOM which is an example of \emph{tree-like} data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim of improving test coverage of the XML-aware Java programs.
-To generate a random document, it may either rely on the  existing XML schema, or generate the document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, with extensive validation requirements.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for the mutation and crossover.
-Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
-
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of the SBST research~\cite{mcminn2011search}.
-Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a particular branch, we would like to have the set of tests maximizing the program coverage.
-That is, our solution is a vector of candidates which has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
-coverage vs.
-test-suite length.
-Another direction of future work is re-targeting out tool towards mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.
-
-% -----------------------
-Our test generation strategy is \emph{goal-oriented}~\cite{korel1992dynamic}, i.e.
-it tries to find an execution leading to a goal (statement) regardless of a concrete path taken.
-We uses control flow graph to identify implicit dependencies between nodes.
-
-The \emph{chaining approach}~\cite{ferguson1996chaining} uses data dependency to form the sequences of statements preceding the execution of a search target. 
-% -----------------------
-
-\section{Conclusions}
-\label{sec:concl}
-
-In this paper we have introduced a novel JS unit testing framework, called \emph{JEDI}, which uses search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{icse2018.bib}
-
-\end{document}

### 2018-05-11 doc/issre2018/example.tex
Near final version of the issre 2018 paper

--- 2018-05-11 doc/icse2018/issta2018.tex
@@
-\documentclass[sigconf,review]{acmart}
-
-\usepackage[inline]{enumitem}
-\usepackage{tablefootnote}
-\usepackage{syntax}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{booktabs} % For formal tables
-\usepackage{tikz}
-\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
-\usepackage{pgf-umlsd}
-\usepackage{tikz-uml}
-\usepackage{hyperref}
-\usepackage{upquote}
-\usepackage{listings}
-\usepackage{lsthaskell}
-\usepackage{xspace}
-\usepackage{enumitem}
-\usepackage{mdframed}
-\usepackage{algorithmic}
-\usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{pgfplots}
-\pgfplotsset{compat=newest}
-\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = red, %Colour of internal links
-  citecolor    = green %Colour of citations
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\definecolor{ltblue}{rgb}{0,0.4,0.4}
-\definecolor{dkblue}{rgb}{0,0.1,0.6}
-\definecolor{dkgreen}{rgb}{0,0.4,0}
-\definecolor{dkviolet}{rgb}{0.3,0,0.5}
-\definecolor{dkred}{rgb}{0.5,0,0}
-
-\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
-%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
-\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
-\definecolor{orange}{rgb}{1,0.45,0.13}		
-\definecolor{olive}{rgb}{0.17,0.59,0.20}
-\definecolor{brown}{rgb}{0.69,0.31,0.31}
-\definecolor{purple}{rgb}{0.38,0.18,0.81}
-\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
-\definecolor{lightred}{rgb}{1,0.4,0.5}
-% CSS
-\lstdefinelanguage{CSS}{
-  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},
-  sensitive=true,
-  morecomment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  morestring=[b]',
-  morestring=[b]",
-  alsoletter={:},
-  alsodigit={-}
-}
-
-% JavaScript
-\lstdefinelanguage{JavaScript}{
-  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
-  morecomment=[s]{/*}{*/},
-  morecomment=[l]//,
-  morestring=[b]",
-  morestring=[b]'
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  sensitive=true,	
-  alsoletter={<>=-},	
-  morecomment=[s]{<!-}{-->},
-  morestring=[b]'
-  tag=[s],
-  otherkeywords={
-  % General
-  >,
-  % Standard tags
-	<!DOCTYPE,
-  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
-	% body
-	</body, <body,
-	% Divs
-	</div, <div, </div>, 
-	% Paragraphs
-	</p, <p, </p>,
-	% scripts
-	</script, <script,
-  % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
-  },
-  ndkeywords={
-  % General
-  =,
-  % HTML attributes
-  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
-  % SVG attributes
-  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
-  % properties
-  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
-	% CSS3 properties
-  transform:, -moz-transform:, -webkit-transform:,
-  animation:, -webkit-animation:,
-  transition:,  transition-duration:, transition-property:, transition-timing-function:,
-  }
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  tagstyle=\color{blue},
-  markfirstintag=true,
-  sensitive=true,
-  alsoletter={<>=-},	
-  morecomment=[s]{<!--}{-->},
-  % tag=[s],
-  %% morestring=[b]'',
-  morestring=[b]',
-  ndkeywords={
-    % General
-    =,
-    % HTML attributes
-    id=, class= 
-  }
-}
-
-\lstdefinestyle{htmlcssjs} {%
-  % General design
-  backgroundcolor=\color{editorGray},
-  basicstyle={\scriptsize\ttfamily},   
-  frame=tb,
-  % line-numbers
-  xleftmargin={0.75cm},
-  numbers=left,
-  stepnumber=1,
-  firstnumber=1,
-  numberfirstline=true,	
-  % Code design
-  identifierstyle=\color{black},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywordstyle=\color{editorGreen}\bfseries,
-  stringstyle=\color{editorOcher}\ttfamily,
-  commentstyle=\color{brown}\ttfamily,
-  % Code
-  language=JavaScript,
-  alsolanguage=HTML5,
-  alsodigit={.:;},	
-  tabsize=2,
-  showtabs=false,
-  showspaces=false,
-  showstringspaces=false,
-  extendedchars=true,
-  breaklines=true,
-  escapechar=|c
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\listfiles % used to output the versions of all files being used by the late
-
-\newcommand{\Server}{\emph{Server}\xspace}
-\newcommand{\Client}{\emph{Client}\xspace}
-\newcommand{\User}{\emph{User}\xspace}
-\newcommand{\Validator}{\emph{Validator}\xspace}
-\newcommand{\thenBr}{\text{then}}
-\newcommand{\elseBr}{\text{else}}
-\newcommand{\inFor}{\text{inFor}}
-\newcommand{\inWhile}{\text{while}}
-\newcommand{\un}[1]{\underline{#1}}
-\newcommand{\Random}{\mathbb{R}}
-\newcommand{\Genetic}{\mathbb{G}}
-\newcommand{\RGenetic}{\mathbb{G}_{10}}
-\newcommand{\Confix}{\emph{Confix}}
-\newcommand{\Jalangi}{\emph{Jalangi}}
-\newcommand{\Jedi}{\emph{JEDI}}
-
-% Copyright
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-%% \acmYear{1997}                  
-%% \copyrightyear{2016}
-
-%% \acmPrice{15.00}
-
-\begin{document}
-\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
-
-\author{Alexander Elyasov}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands} 
-}
-\email{a.elyasov@uu.nl}
-
-\author{Wishnu Prasetya}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{s.w.b.prasetya@uu.nl}
-
-\author{Jurriaan Hage}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{j.hage@uu.nl}
-
-\begin{abstract}
-The popularity of JavaScript is continuously growing.
-Together with HTML and CSS, it forms the core technology stack for web development.
-Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable.
-Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS applications interacting with the DOM has not yet been addressed.
-In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including the global DOM state.
-We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
-It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Software and its engineering~Software testing and debugging}
-\ccsdesc[300]{Software and its engineering~Search-based software engineering}
-
-\keywords{JavaScript, search-based testing, branch coverage}
-
-\maketitle
-
-%% ------------------------------------------------------------------------
-\section{Introduction}
-\label{sec.intro}
-%% ------------------------------------------------------------------------
-
-According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript has been recognized for the sixth time in row as the most commonly used programming language.
-It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million).
-Such an ever increasing JS success can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}.
-On the other hand, due to of implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}.
-Thus, it is not surprising that once in a while critical bugs manage to break through~\cite{bugstories2017} into the web applications by Facebook, Twitter etc.
-
-Systematic unit testing is basic and, at the same time, the most effective technique for improving software quality.
-In practice, there are numerous of JS frameworks --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc.
---- intended to assist developers with the automation of various unit testing activities such as design, execution and monitoring.
-Despite the apparent abundance of the JS testing tools, the developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements.
-One of such areas is \emph{test data generation}.
-It pursues the goal of maximizing the test coverage by exercising the function under test (FUT) with different input parameters.
-Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.
-
-Generally, the problem of test data generation has been under an active study for the past three decades.
-In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the whole web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
-Out of those tools, only \emph{Confix} tries to construct a sufficient DOM fixture by translating native browser API calls into logical constraints.
-However, in the empirical evaluation~\cite{amin:ase15}, Confix only reached about 50\% in \emph{branch coverage} on the selected subjects.
-At the same time, search-based techniques have shown prominent results in achieving high branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications.
-But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of the search-based approach.
-In this paper we are breaching this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-We can summarize our contributions as follows:
-\begin{enumerate}[leftmargin=5mm]
-\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
-\item Our test generation algorithm, called ``genetic with restart'', is trying to escape search plateau by restarting GA with a new target.
-Because the full-fledged JS data flow analysis~\cite{jang2009points} is hard to reach, the new target is chosen purely based on the preceding control flow behaviour in contrast with more popular techniques~\cite{ferguson1996chaining}.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
-Moreover, we showed that on the selected subjects \emph{JEDI} outperforms \emph{Confix} ....
-\end{enumerate}
-
-The paper is structured as follows: In Section~\ref{sec.example}, we present a motivating example illustrating the challenges of generating test data for JS.
-The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} presents empirical validation and indicates the validity threats.
-Related and future work are discussed in Section~\ref{sec:related.work}.
-Section~\ref{sec:concl} concludes the paper.
-
-%% The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
-These frameworks support testing at various levels: unit, integration and functional.
-The survey also indicated a relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
-As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite this effort, test data generation continues to be poorly addressed by any of the widely used testing frameworks.
-The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of web application faults are DOM-related and introduced in the JS code, and not in other components such as HTML or CSS.
-This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
 %% --------------------------------------------------------------------
@@
 
-\begin{figure}[t]
+\begin{figure}[!t]
   \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
@@
 
-\begin{figure}[t]
+\begin{figure}[!t]
   \begin{lstlisting}[style=htmlcssjs, language=HTML5]
@@
 It saves the developers from unexpected regressions and often documents the desired behavior of a program.
-
-%% --------------------------------------------------------------------
-\section{Test Generation Framework}
-\label{sec.framework}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t!]
-  \centering 
-\tikzset{
-  % add this style to all tikzpicture environments
-  every picture/.append style={
-    % enable scaling of nodes
-    transform shape,
-    % set scale factor
-    scale=1
-  }
-}
-  \begin{sequencediagram}[font=\scriptsize]
-
-    \renewcommand\unitfactor{0.35}
-    \newinst{user}{\textbf{User}}
-    \newinst{server}{\textbf{Server}}
-    \newinst[1]{validator}{\textbf{Validator}}
-    \newinst{client}{\textbf{Client}}
-
-    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
-      \end{call}
-
-      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
-      \end{call}
-
-      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
-      \end{call}
-
-      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
-          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
-          \end{call}
-          \prelevel
-        \end{sdblock}
-
-        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
-            \end{call}
-
-            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
-            \end{callself}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
-          \end{callself}
-          \prelevel
-        \end{sdblock}
-        \mess{server}{best fitness}{user}
-
-      \end{sdblock}
-    \end{call}
-  \end{sequencediagram}
-  \caption{The architecture of the test framework}
-  \label{fig.framework.architect} 
-\end{figure}
-
-Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $\mathbb{B}_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application, which uses under the hood a genetic engine, for test generation.
-The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-The \Server is the key component of the  framework, responsible for the \emph{Initialization} and \emph{Genetic Phases}, covered in detail in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Each newly constructed HTML document has to be assessed by the \Validator~\cite{htmlvalidator} that checks its syntactic correctness and reports back any identified errors.
-The document generation process is repeated by the \Server until there are no errors revealed.
-\Client is a \emph{Node.js}~\cite{nodejs} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}~\cite{jsdom} library to model the virtual DOM and simulate the native browser API calls.
-
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
-Let us take a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide a JS file \emph{fun.js} that contains a FUT \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that sets various control parameters for the random and genetic phases, logging etc.
-Experimentally, we have found an optimal configuration that was consistently used in the experimental evaluation in Section~\ref{sec.evaluation}.
-Once all the data are processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
-Then, the \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
-Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework triggers the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework begins with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criteria is achieved, e.g.
-the limit on the number of generation attempts.
-Any HTML document produced during the genetic phase has to be first approved by the \Validator.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate solution $p$ with the type signature \emph{sig}, and invokes the instrumented JS function as \emph{ifun(p)}.
-The execution trace along with some auxiliary information is sent back to the \Server, where the final \emph{fitness value} is computed.
-A new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are covered, the algorithm terminates.
-Below, we elaborate on the details of each individual phase of our test generation framework.
-
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
-
-During the \emph{Initialization Phase} we analyze the FUT in order to facilitate the subsequent genetic testing.
-The main steps of this phase are described in Algorithm~\ref{alg.init}.
-Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants, e.g.
-numeric and string literals.
-Additionally, we monitor the calls to such DOM API methods as \texttt{getElementsByTagName}, \texttt{getElementById}, and \texttt{getElementsByClassName}.
-These methods provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the FUT.
-The next step is to normalize the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) for run-time data collection about the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants.
-Upon the \emph{ifun} execution this information is gathered and fed back to the fitness evaluation procedure.
-Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
-
-\subsubsection{Supported Types}
-\label{sub.sec.sup.types}
-
-\begin{figure}[t!]
-\setlength{\grammarparsep}{3pt}
-\footnotesize
-\begin{grammar}
-<JS Type Annotation> ::= /*t <Signature> */
-
-<Signature> ::= \texttt{dom} : <Type Signature> | <Type Signature>
-
-<Type Signature> ::= <Type> | <Type> : <Type Signature>
-
-<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
-
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
-
-<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
-\end{grammar}
-\caption{Grammar of supported JS type annotations}
-\label{fig.js.type.annot}
-\end{figure}
-
-We assume the FUT is equipped with the type signature.
-The legitimacy of such a requirement can be confirmed by the popularity of \emph{TypeScript}~\cite{typescript}, and advances in the JS type inference \emph{Flow}~\cite{flow}.
-The supported grammar of type annotations is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures: with the reference to the global DOM and ``ordinary'' JS type signatures.
-The former kind expects the \texttt{dom} terminal to be in place of the first parameter of the function call.
-Whereas an ordinary JS signature is a non-empty sequence of the JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
-
-\subsubsection{Instrumentation}
-\label{sub.sec.instrument}
-
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \texttt{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT.
-We have to trace all the statements because each one, in theory, can rise an exception.
-The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} captures the upper bound for the number for-loop iterations.
-If the exact bound is unknown, it is set to one.
-The \texttt{branchDistance} variable, computed for the \emph{problem node}, contains the distance~\cite{tracey1998automated} from the target branch.
-
-%TODO: maybe expand this section with the JS type casting for branch distance computation
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function isGameFinished() {
- trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
- trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
- var allOk = true;
- loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
-   var no = 0;
-   if (subDivs.length || subDivs.length == 0) {
-     return Math.abs(no - subDivs.length);
-   }; return 1}();
- trace.push(3);
- for (var no = 0; no < subDivs.length; no++) {
-  trace.push(4);
-  if (subDivs[no].className.indexOf("square") >= 0 &&
-      !subDivs[no].style.backgroundColor) {
-   trace.push(5); branchDistance.push({ label: 3, 
-    distance: Math.min(
-     abs(subDivs[no].className.indexOf("square"),0)+_K_ 
-     absZero(subDivs[no].style.backgroundColor))
-   });
-   trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
-   trace.push(7);
-   if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(8); branchDistance.push({ label: 7, 
-     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-    });
-    allOk = false; break;
-   } else {
-   trace.push(9);branchDistance.push({label:7,distance:_K_});
-   }
-  } else {
-   trace.push(10); branchDistance.push({ label: 3,
-    distance: 
-     abs(subDivs[no].className.indexOf("square"), 0) + 
-     absNegZero(subDivs[no].style.backgroundColor)
-   });}}
- trace.push(-1);
-}
-\end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
-  \label{code.isGameFinished.instr}
-\end{figure}
-
-\subsection{Genetic Phase}
-\label{sub.sec.genetic.phase}
-
-\begin{algorithm}[!t]
-  \caption{Genetic Phase}
-  \label{alg.gen}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{
-    $config$ is a GA configuration file\\
-    $b_n$ is a target branch of FUT\\
-    $(cfg, branches, cinfo, ifun, sig)$ output of Algorithm~\ref{alg.init}
-  }
-  \Output{
-     $(f^*, p^*)$ the best population candidate and its fitness score
-  }
-  \Fn{$Genetic(b_n, cfg, cinfo, config, ifun, sig)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M,size_{H}) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
-    $target \longleftarrow b_n$\label{alg.gen.init.target}\; 
-    $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
-    $historyConverged \longleftarrow true$\;
-    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
-      $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\; 
-      $history \longleftarrow \emptyset$\label{alg.gen.init.history}\; 
-      $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
-      \Repeat{$isPerfect(f^*) \vee historyConverged \vee (i > size_G)$}{\label{alg.gen.loop.begin}
-        $scoredPop \longleftarrow \emptyset$\;
-        $history \longleftarrow history \cup archive$\;
-        \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
-          $args \longleftarrow CoerceArguments(p, sig)$\label{alg.gen.make.args}\;
-          $(tr, d_B, d_L, dyncinfo) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
-          $f \longleftarrow Score(target, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
-          $cinfo \longleftarrow cinfo \cup dyncinfo$\label{alg.gen.eval.end}\;
-          $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        }
-        $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
-        $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
-        $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
-        $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
-        $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
-        $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
-        $i \longleftarrow i + 1$\;
-        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
-      }\label{alg.gen.loop.end}
-      $target \longleftarrow NewTarget(branches, b_n)$\label{alg.gen.new.target}\;
-    }\label{alg.gen.converged.loop.end}
-    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
-  }
-\end{algorithm}
-
-The heart of our test data generation framework is in the \emph{Genetic Phase}.
-Although, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, it has been extended with the concept of \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we specify a configuration file \emph{config}, a target branch $b_n$ of the FUT, and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
-The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
-
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) to retrieve the following GA settings: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ set to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged, or the generations limit has not been exceeded.
-The \emph{archive} variable stores the most fit population candidates observed so far, and the \emph{history} variable records all the archives during the generation process.
-The two variables are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
-
-The initial population of $size_P$ is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate is found, or the history is converged, or the generation limit $size_G$ is reached.
-But first, we need to score the current population (lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}).
-Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
-Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
-Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
-This gives us a 4-tuple consisting of an execution trace ($tr$), branch ($d_B$), loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
-The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
-Collected dynamic constants \emph{dyncinfo} are merged into the existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) in $combo$.
-It is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
-If $f^*$ is a \emph{perfect} candidate, the solution is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
-
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{mcminn2004search}.
-For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it accidentally.
-In such a situation, we find ourselves being trapped on a flat space, with a small chance to escape.
-In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
-At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
-If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
-It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
-Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
-In practice, we only consider extensions upto length two.
-
-The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
-In the rest of this section, we provide implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and the fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our main focus here is on the generation and transformation of HTML documents.
-
-\begin{table}
-  \caption{Genetic Operation for the JS Types}
-  \label{tbl.gen.oper.js.types}
-    \footnotesize
-  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
-    \toprule
-    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
-    \hline
-    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
-    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
-    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
-    Random    & Array  & array of a respective type upto length five\\
-    \hline
-    Crossover & Bool   & pick at random one out of two given booleans \\
-    Crossover & Int    & pick at random one out of two given integers\\
-    Crossover & Float  & pick at random one out of two given floats\\
-    Crossover & String & pick at random one out of two single point crossovers\\
-    Crossover & Array  & similar crossover operator as for strings\\
-    \hline
-    Mutation  & Bool   & flip the boolean constant\\
-    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
-    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
-    Mutation  & String & random string, remove char or apply pred(suc) char\\
-    Mutation  & Array  & Mutate a random element in array according to its type\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsubsection{Random HTML Generation}
-\label{sub.sub.sec.random.html}
-
-\begin{figure}[t]
-  \begin{haskell}
-instance Arbitrary Html where
-  arbitrary = evalStateT generateHTML defaultState
-
-generateHTML :: GenHtmlState |c \label{ref.generateHTML.begin} |c
-generateHTML = do
-  state <- get |c \label{ref.generateHTML.getState} |c   
-  let d = getDepth state |c \label{ref.generateHTML.getDepth} |c
-  if d == 0
-  then lift \dollar return \dollar toHtml "HTML" |c \label{ref.generateHTML.returnString} |c
-  else do put state{depth = d - 1} |c \label{ref.generateHTML.updateState} |c
-           head <- generateHEAD |c \label{ref.generateHTML.newHead} |c
-           body <- generateBODY |c \label{ref.generateHTML.newBody} |c
-           lift\dollar return \dollar docTypeHtml \dollar head >> body |c \label{ref.generateHTML.end} |c
-
-data Tag = HTML | HEAD | BODY | ...
-type Context = CFlow | CMetadata | ...
-data HtmlState = |c \label{ref.HtmlState.begin} |c
-  HtmlState { depth    :: Int,           degree  :: Int    
-             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
-             , tags    :: [Tag],         ids     :: [String]
-             , classes :: [String] } |c \label{ref.HtmlState.end} |c
-type GenState s = StateT s Gen |c \label{ref.GenState} |c
-type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
-  \end{haskell}
-  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
-  \label{fig.html.arb.def}
-\end{figure}
-
-We want to generate HTML according to the WHATWG~\cite{htmlspec} specification.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-The recent HTML5 standard defines more than a hundred of tags and attributes which both have to comply with extremely complex logic to constitute  syntactically valid HTML.
-Browsers are usually tolerant to syntactic errors in HTML.
-They will silently fix them and display the page anyway.
-
-In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because the complexity of HTML and the lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} shows that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) represents the internal state of \texttt{Html}.
-The state is composed of the following components:
-\begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of the generated HTML 
-\item \texttt{ctx} is the current value of the HTML content model stack 
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
-\end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag is the value of the \texttt{GenHtmlState} type.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to the specification~\cite{htmlspec}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
-First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
-Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
-
-\subsubsection{Genetic HTML Operations}
-\label{sub.sub.sec.genetic.oper}
-
-In essence, an HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for \emph{expression trees} in genetic programming.
-
-\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
-
-\textbf{HTML Mutations} belong to one of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
-The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
-The \emph{DropTree} mutation removes the whole sub-tree at a randomly chosen node.
-\emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
-Currently, we instantiated the \emph{ShuffleAttributes} mutation only for the types \emph{class} and \emph{id}.
-In total, this gives us four mutations to choose from in order to evolve an HTML document.
-
-\subsubsection{Fitness Function}
-\label{sub.sub.sec.fitness.fun}
-
-The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating valid input data.
-The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
-without premature exception.
-Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-The FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
-\[
-\textit{fit}(n) = \text{approach level} +
-\begin{cases}
- 1/2 * (\frac{\text{branch distance}}{1 + \text{branch distance}}) & \text{if no exception}\\
- 1                                  &  \text{otherwise}
-\end{cases}
-\]
-The final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
-\[
-\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
-\]
-Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
- \[
-\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
-\]
-
-The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
-the node causing the deviation.
-Since any node can potentially be exceptional, they all contribute to the approach level, in addition to the conditional branches.
-Loops have to be treated in a special way because we need to estimate the maximum number of iterations.
-In the case of a for-loop, at run-time we can always provide an exact bound.
-For while-loops, we assume that it has to be passed at least once.
-The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
-
-\subsubsection{Limitations}
-\label{sub.sub.sec.limit}
-
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
-%% --------------------------------------------------------------------
-\section{Empirical Evaluation}
-\label{sec.evaluation}
-%% --------------------------------------------------------------------
-
-In order to evaluate the feasibility of our test framework, we conducted an empirical evaluation on a set of case-studies (see Section~\ref{sub.sec.case.studies}).
-All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which plays the role of our baseline, is \emph{Random} ($\Random$).
-Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is important to note  that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic Algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On the one hand, the smaller window size forces the GA to converge faster and quickly discovers stagnation on a flat space.
-On the other hand, the small window can lead to premature archive convergence, which prevents the right genetic combination from being triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose to report only that case in the paper.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{fraser2011evosuite}.
-
-\begin{table}
-  \caption{Genetic Algorithm Configurations}
-  \label{tbl.gen.config}
-    \scriptsize
-  \begin{tabular}{l|r|r|r}
-    \toprule
-    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
-    \hline
-    Population size                   & 50  & 50  & 50  \\
-    Archive size                      & 1   & 25  & 25  \\
-    Maximum number of generations     & 200 & 200 & 200 \\
-    Crossover rate                    & 0   & 0.5 & 0.5 \\
-    Mutation rate                     & 0   & 0.5 & 0.5 \\
-    History window size               & -   & -   & 10  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-By carrying the evaluation, we would like to answer the following research questions:
-\begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
-Which testing algorithm is the most effective?
-How does effectiveness change with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost per iteration?
-\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
-\item[\textbf{RQ4 (comparison):}] What is the branch coverage of \emph{Confix}?
-\end{description}
-
-\subsection{Case Studies}
-\label{sub.sec.case.studies}
-
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless numbers of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React~\cite{todomvc}, offer an alternative approach to native DOM manipulation.
-Before selection, the source code of a potential case-study has to be scrutinized which is a time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011, tajsbenchmarks}.
-Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We added additional case-study \emph{mathjs}~\cite{mathjs} to increase the presence of primitive (browserless) JS code.
-For each case-study application, we identified several JS functions that are suitable for our testing framework.
-In the end, our evaluation set included both primitive and DOM related JS functions.
-
-For the sake of space, we chose to exclude from the following presentation the branches and functions the coverage time of which was less than two seconds.
-In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
-This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics~\cite{jsmeter} is the tool used for measuring JS code statistics: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the case studies in ~Table~\ref{tbl.case.studies}.
-
-\setlength\tabcolsep{1pt}
-\begin{table}[!t]
-  \caption{Summary of the Case-Studies}
-  \label{tbl.case.studies}
-  %\resizebox{\textwidth}{!}{
-    \scriptsize
-  \begin{tabular}{l|l|p{2.7cm}|c|c|c|c|c|c|c|c}
-    \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & helpMe & (int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & ()    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & ()           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & ()         & 8  & 0 & 2 & 1 & + & + & + & - \\
-    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (int,int)      & 23 & 2 & 3 & 3 & + & - & + & - \\
-    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
-    \hline
-    phormer    & toggleInfo & (string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
-    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
-    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
-    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
-    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
-    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
-    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
-    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
-    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
-    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
-    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & ([int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & ([int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
-    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
-    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
-    \hline
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
-    %% \hline
-    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
-    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
-    \bottomrule
-  \end{tabular}
-%}
-\end{table}
-
-\subsection{Results}
-\label{sub.sec.eval.results}
-
-\setlength\tabcolsep{.98pt}
-\begin{table}[!t]
-  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
-  \label{tbl.stats}
-    \scriptsize
-    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
-      \toprule
-      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{2-10} % \!:\!
-                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \midrule
-    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \textbf{newGame}*   
-                             & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \textbf{revealAll}*  
-                             & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-    \textbf{shuffleBoard}*   
-                             & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \hline
-   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \hline
-   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \hline
-   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \hline
-   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-   \midrule
-    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
-    \bottomrule
-   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \hline
-    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \hline
-    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
-    \midrule
-    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
-    %% \midrule
-    %% \midrule
-    \bottomrule
-    \bottomrule  
-    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-To study the effectiveness and efficiency of our test generation framework ($\Random$, $\Genetic$ and $\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
-In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ one for each algorithm.
-The next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-To the right of the function name, we also present accumulated statistics for the function as a whole.
-Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function.
-
-According to the industry standard~\cite{bray1997c4}, functions with a CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
-We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with CC's of 13, 14 and 16 respectively.
-Table~\ref{tbl.stats.sum} summarizes the results of the experiment such as coverage, execution time per branch and significance.
-
-\begin{table}[!t]
-  \caption{Result Summary (L - large, M - medium, S - small)}
-  \label{tbl.stats.sum}
-    \footnotesize
-    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
-      \toprule
-      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
-      \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{8-16}
-                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
-      \midrule
-      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
-      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
-      \midrule
-      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
-Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The underlined values in Table~\ref{tbl.stats} like $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
-The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
-branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of the genetic approach, $\Genetic$ may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
-We encountered three such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines the strengths of both $\Random$ and $\Genetic$.
-It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only managed to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
-branch $(69,71)$ of the \emph{initBricks} function.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
-  }
-}
-
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig.budget.progress}
-\end{figure}
-
-Additionally, we have investigated how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time dependent.
-E.g.
-running tests inside an IDE should be fast; as part of the CI cycle we may afford a larger waiting time; regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ overtakes $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
-  }
-}
-
-\paragraph{\textbf{RQ2 (efficiency).}}
- To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
-Based on this information, we suggest an estimate on the execution time of the testing framework.
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum of 40\%~(\emph{newGame}) and a maximum of 510\%~(\emph{isValidCard}).
-
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=950,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        restrict y to domain*=0:1350, % Cut values off at 14
-        visualization depends on=rawy\as\rawy, % Save the unclipped values
-        after end axis/.code={ % Draw line indicating break
-          \draw [ultra thick, white, decoration={snake, amplitude=1pt}, decorate] (rel axis cs:0,1.05) -- (rel axis cs:1,1.05);
-        },
-        nodes near coords={%
-          \pgfmathprintnumber{\rawy}% Print unclipped values
-        },
-        every node near coord/.append style={rotate=90,anchor=west,font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,270) (isGameFinished*,220) (newGame*,14) (revealAll*,50) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,514) (isValidVISA,95) (initShields*,5) (brickJiggler*,8) (doPaddlePower*,15)  (initBricks*,2379) (do\_draw,625) (prob\_gamma,710)};
-      \addplot[fill=red] coordinates {(helpMe*,47)  (isGameFinished*,30)  (newGame*,9)  (revealAll*,44) (shuffleBoard*,26) (toggleInfo*,7) (isValidCard,8)   (isValidVISA,3)  (initShields*,5) (brickJiggler*,4) (doPaddlePower*,140) (initBricks*,474) (do\_draw,1295) (prob\_gamma,84)};
-      \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Overall test generation time per function.}
-  \label{fig.gen.time.comp}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=4,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,1.24) (isGameFinished*,0.83) (newGame*,0.78) (revealAll*,0.83) (shuffleBoard*,1.93) (toggleInfo*,1) (isValidCard,0.51) (isValidVISA,0.47) (initShields*,0.83) (brickJiggler*,1.14) (doPaddlePower*,0.79)  (initBricks*,1.68) (do\_draw,2.33) (prob\_gamma,0.35)};
-      \addplot[fill=red] coordinates {(helpMe*,0.77)  (isGameFinished*,0.94)  (newGame*,0.81)  (revealAll*,1) (shuffleBoard*,1.73) (toggleInfo*,1) (isValidCard,0.38)   (isValidVISA,0.38)  (initShields*,0.83) (brickJiggler*,0.67) (doPaddlePower*,0.69) (initBricks*,0.8) (do\_draw,3.38) (prob\_gamma,0.52)};
-      \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Speed of test generation measured as $t/i$}
-    \label{fig.get.cost}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with  7 and 25 seconds per branch.
-For simple functions, $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
-In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch of 19, 39 and 88 seconds, respectively. 
-  }
-}
-
-Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
-This information is useful when configuring the maximal generation limit.
-The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures the speed of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost of the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus never rising exceptions, and at the same time, it consists of 40 LOC.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second on average for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse 1.4 seconds.
-  }
-}
-
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs relative to $\Genetic$.
-Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases generally across the board and 67\% on the difficult functions.  
-  }
-}
-
-\paragraph{\textbf{RQ4 (comparison).}} Authors of \emph{Confix}~\cite{amin:ase15} have proposed three strategies for test generation based on: 
-\begin{enumerate*}[label=(\roman*)]
-  \item \emph{Confix} entirely,
-  \item combination with \emph{Jalangi}~\cite{sen2013jalangi}, and
-  \item combination with a manual input. 
-\end{enumerate*}
-They reported a relative increase of 2\% and 19\% in branch coverage of the second and third strategies, respectively, over the first one.
-Even though, the third strategy performed the best, due to a manually enhanced data set, it is not objectively comparable with a fully automated technique, like \emph{JEDI}.
-Unfortunately, the open source version of \emph{Confix} we found online~\cite{confixgit} does not support an actual integration with \emph{Jalangi}.
-Neither, the paper~\cite{amin:ase15} highlights any implementation details of it.
-Thus in our evaluation Figure~\ref{tbl.confix.compare}, we had to fall back on the plain \emph{Confix} test generation.
-\Jedi seeks for a normal program termination during test generation, which is a stronger coverage criterion in comparison with only reaching a target branch provided by \Confix.
-Although, \Confix performs much faster (under 10 seconds), it is unable to discover hard to cover branches especially in terms of strong coverage.
-
-\begin{table}[!t]
-  \caption{Evaluation of \emph{Confix} (\#BR - total branches, \#BRC weak/strong - covered branches with exceptional/normal termination)}
-  \label{tbl.confix.compare}
-    \footnotesize
-    \centering
-    \begin{tabular}{l|l|c|c|c|c|c}
-      \toprule
-      \textbf{case-study} & \textbf{function} & \textbf{\#BR} & \textbf{\#C (weak)} & \textbf{\#C strong} & \textbf{\#tests} & \textbf{time (sec.)} \\
-      \hline
-      sudoku & helpMe          & 5  & 4 (80\%)  & 4 (80\%)  & 2 & 5 \\
-      sudoku & isGameFinished  & 5  & 2 (40\%)  & 2 (40\%)  & 2 & 5 \\
-      sudoku & newGame         & 3  & 3 (100\%) & 3 (100\%) & 4 & 6 \\
-      sudoku & revealAll       & 2  & 2 (100\%) & 0 (0\%)   & 6 & 11 \\
-      sudoku & shuffleBoard    & 7  & 5 (71\%)  & 0 (0\%)   & 2 & 5  \\
-      \hline
-      phormer & toogleInfo     & 4  & 2 (50\%)  & 2 (50\%)  & 3 & 5 \\
-      \hline
-      apophis & initShields    & 1  & 0 (0\%)   & 0 (0\%)   & 1 & 6 \\
-      \hline
-      bingbong & brickJiggler  & 2  & 0 (0\%)   & 0 (0\%)   & 1  & 3 \\
-      bingbong & doPaddlePower & 4  & 2 (50\%)  & 2 (50\%)  & 1  & 4 \\
-      bingbong & initBricks    & 18 & 3 (17\%)  & 0 (0\%) & 1  & 3 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{Threats to Validity}}
-The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Although, the branch coverage is a common criterion used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
-Reaching a target branch is only part of the problem: we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles leading to exceptions.
-Using a stronger oracle for validation is future work.
-Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent on unnecessary data explosion.
-Additional measures that could be applied is a minimization procedure, aka \emph{delta debugging}~\cite{misherghi2006hdd}, to the GA result.
-
-Initial GA configuration introduces a threat to the \emph{internal validity} of our empirical evaluation.
-The parameters we used are quite standard for similar SBST frameworks, e.g.
-EvoSuite.
-Although, not reported in the paper, we did perform a preliminary assessment of various GA configurations, which confirmed our final decision.
-
-The threat of \emph{conclusion validity} can be affected by the stochastic nature.
-This risk was addressed by repeating the experiment of GA 50 times and performing a statistical analysis of the significance and effect size.
-We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
-
-The \emph{external validity} deals with the threat of generalization of our results due to the manual selection of the experimental subjects.
-To mitigate this fact, we selected the subjects either from previous  related research or found in open source.
-Of course, those subjects still have to meet the constraints of our testing approach.
-So, further research is required in both increasing the power of our framework and extending the validation set.
-
-%% --------------------------------------------------------------------
-\section{Related and Future Work}
-\label{sec:related.work}
-%% --------------------------------------------------------------------
-
-The last two decades have been fruitful in the amount of work dedicates to the analysis of web applications and JavaScript, in particular.
-The state-of-the-art in this field including static and dynamic analysis of JS, as well as the test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around the two main questions:
-\begin{enumerate*}
-\item test data generation for JS functions interacting with the DOM, and
-\item the application of search-based techniques for that problem.
-\end{enumerate*}
-
-\subsection{Test Data Generation for JavaScript}
-
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect info about constant and feeds this data to the random generation.
-In comparison, our approach is the genetic generation.
-Additionally, we not only rely on the static information but also perform dynamic analysis to collect the run-time data.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} propose to use feedback-directed random testing for generation of TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing \emph{concolic testing} or {type inconsistency} analysis~\cite{pradel2015typedevil}.
-It suffers from common for the symbolic analysis problems such reasoning about arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtain DOM fixtures for the FUT.
-Combined with Jalangi, it can be used both for the generation of primitive data and DOM.
-As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
-Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS functions without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as a solid alternative for program testing.
-In fact, both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information for identifying potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011}, they extended the analysis with the abstractions able reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discovers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-
-\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the help the JS \emph{Proxies} in order to collect type related information.
-
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-
-%% \cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-%% \cite{ma2015grt} guided random testing
-
-%% \cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-%% \cite{jquery2014}
-
-%% ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-%% Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-%% Information-flow security for JS~\cite{hedin2012information}.
-
-%% Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-%% Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-%% Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-%% Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-%% DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Search-Based Test Data Generation}
-\label{sub.sec.search.based}
-
-Despite of the practical popularity of JavaScript, we have only encountered one work by Alshraideh~\cite{alshraideh2008complete} attempting to apply SBST to JavaScript.
-It uses GA for test generation with the goal cover all branches or kill all mutants, but it only deals with the limited input types such as booleans, integers and strings; and the provided validation is only based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports \emph{array} and \emph{DOM}, and conducts reasonable empirical validation with the discussion of significance and effect size.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-In this paper we deal with the generation and evolution of DOM which is an example of \emph{tree-like} data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim of improving test coverage of the XML-aware Java programs.
-To generate a random document, it may either rely on the  existing XML schema, or generate the document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, with extensive validation requirements.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for the mutation and crossover.
-Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
-
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of the SBST research~\cite{mcminn2011search}.
-Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a particular branch, we would like to have the set of tests maximizing the program coverage.
-That is, our solution is a vector of candidates which has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
-coverage vs.
-test-suite length.
-Another direction of future work is re-targeting out tool towards mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.
-
-% -----------------------
-Our test generation strategy is \emph{goal-oriented}~\cite{korel1992dynamic}, i.e.
-it tries to find an execution leading to a goal (statement) regardless of a concrete path taken.
-We uses control flow graph to identify implicit dependencies between nodes.
-
-The \emph{chaining approach}~\cite{ferguson1996chaining} uses data dependency to form the sequences of statements preceding the execution of a search target. 
-% -----------------------
-
-\section{Conclusions}
-\label{sec:concl}
-
-In this paper we have introduced a novel JS unit testing framework, called \emph{JEDI}, which uses search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{icse2018.bib}
-
-\end{document}

### 2018-05-11 doc/issre2018/framework.tex
Near final version of the issre 2018 paper

--- 2018-05-11 doc/icse2018/issta2018.tex
@@
-\documentclass[sigconf,review]{acmart}
-
-\usepackage[inline]{enumitem}
-\usepackage{tablefootnote}
-\usepackage{syntax}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{booktabs} % For formal tables
-\usepackage{tikz}
-\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
-\usepackage{pgf-umlsd}
-\usepackage{tikz-uml}
-\usepackage{hyperref}
-\usepackage{upquote}
-\usepackage{listings}
-\usepackage{lsthaskell}
-\usepackage{xspace}
-\usepackage{enumitem}
-\usepackage{mdframed}
-\usepackage{algorithmic}
-\usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{pgfplots}
-\pgfplotsset{compat=newest}
-\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = red, %Colour of internal links
-  citecolor    = green %Colour of citations
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\definecolor{ltblue}{rgb}{0,0.4,0.4}
-\definecolor{dkblue}{rgb}{0,0.1,0.6}
-\definecolor{dkgreen}{rgb}{0,0.4,0}
-\definecolor{dkviolet}{rgb}{0.3,0,0.5}
-\definecolor{dkred}{rgb}{0.5,0,0}
-
-\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
-%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
-\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
-\definecolor{orange}{rgb}{1,0.45,0.13}		
-\definecolor{olive}{rgb}{0.17,0.59,0.20}
-\definecolor{brown}{rgb}{0.69,0.31,0.31}
-\definecolor{purple}{rgb}{0.38,0.18,0.81}
-\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
-\definecolor{lightred}{rgb}{1,0.4,0.5}
-% CSS
-\lstdefinelanguage{CSS}{
-  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},
-  sensitive=true,
-  morecomment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  morestring=[b]',
-  morestring=[b]",
-  alsoletter={:},
-  alsodigit={-}
-}
-
-% JavaScript
-\lstdefinelanguage{JavaScript}{
-  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
-  morecomment=[s]{/*}{*/},
-  morecomment=[l]//,
-  morestring=[b]",
-  morestring=[b]'
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  sensitive=true,	
-  alsoletter={<>=-},	
-  morecomment=[s]{<!-}{-->},
-  morestring=[b]'
-  tag=[s],
-  otherkeywords={
-  % General
-  >,
-  % Standard tags
-	<!DOCTYPE,
-  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
-	% body
-	</body, <body,
-	% Divs
-	</div, <div, </div>, 
-	% Paragraphs
-	</p, <p, </p>,
-	% scripts
-	</script, <script,
-  % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
-  },
-  ndkeywords={
-  % General
-  =,
-  % HTML attributes
-  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
-  % SVG attributes
-  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
-  % properties
-  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
-	% CSS3 properties
-  transform:, -moz-transform:, -webkit-transform:,
-  animation:, -webkit-animation:,
-  transition:,  transition-duration:, transition-property:, transition-timing-function:,
-  }
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  tagstyle=\color{blue},
-  markfirstintag=true,
-  sensitive=true,
-  alsoletter={<>=-},	
-  morecomment=[s]{<!--}{-->},
-  % tag=[s],
-  %% morestring=[b]'',
-  morestring=[b]',
-  ndkeywords={
-    % General
-    =,
-    % HTML attributes
-    id=, class= 
-  }
-}
-
-\lstdefinestyle{htmlcssjs} {%
-  % General design
-  backgroundcolor=\color{editorGray},
-  basicstyle={\scriptsize\ttfamily},   
-  frame=tb,
-  % line-numbers
-  xleftmargin={0.75cm},
-  numbers=left,
-  stepnumber=1,
-  firstnumber=1,
-  numberfirstline=true,	
-  % Code design
-  identifierstyle=\color{black},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywordstyle=\color{editorGreen}\bfseries,
-  stringstyle=\color{editorOcher}\ttfamily,
-  commentstyle=\color{brown}\ttfamily,
-  % Code
-  language=JavaScript,
-  alsolanguage=HTML5,
-  alsodigit={.:;},	
-  tabsize=2,
-  showtabs=false,
-  showspaces=false,
-  showstringspaces=false,
-  extendedchars=true,
-  breaklines=true,
-  escapechar=|c
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\listfiles % used to output the versions of all files being used by the late
-
-\newcommand{\Server}{\emph{Server}\xspace}
-\newcommand{\Client}{\emph{Client}\xspace}
-\newcommand{\User}{\emph{User}\xspace}
-\newcommand{\Validator}{\emph{Validator}\xspace}
-\newcommand{\thenBr}{\text{then}}
-\newcommand{\elseBr}{\text{else}}
-\newcommand{\inFor}{\text{inFor}}
-\newcommand{\inWhile}{\text{while}}
-\newcommand{\un}[1]{\underline{#1}}
-\newcommand{\Random}{\mathbb{R}}
-\newcommand{\Genetic}{\mathbb{G}}
-\newcommand{\RGenetic}{\mathbb{G}_{10}}
-\newcommand{\Confix}{\emph{Confix}}
-\newcommand{\Jalangi}{\emph{Jalangi}}
-\newcommand{\Jedi}{\emph{JEDI}}
-
-% Copyright
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-%% \acmYear{1997}                  
-%% \copyrightyear{2016}
-
-%% \acmPrice{15.00}
-
-\begin{document}
-\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
-
-\author{Alexander Elyasov}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands} 
-}
-\email{a.elyasov@uu.nl}
-
-\author{Wishnu Prasetya}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{s.w.b.prasetya@uu.nl}
-
-\author{Jurriaan Hage}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{j.hage@uu.nl}
-
-\begin{abstract}
-The popularity of JavaScript is continuously growing.
-Together with HTML and CSS, it forms the core technology stack for web development.
-Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable.
-Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS applications interacting with the DOM has not yet been addressed.
-In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including the global DOM state.
-We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
-It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Software and its engineering~Software testing and debugging}
-\ccsdesc[300]{Software and its engineering~Search-based software engineering}
-
-\keywords{JavaScript, search-based testing, branch coverage}
-
-\maketitle
-
-%% ------------------------------------------------------------------------
-\section{Introduction}
-\label{sec.intro}
-%% ------------------------------------------------------------------------
-
-According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript has been recognized for the sixth time in row as the most commonly used programming language.
-It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million).
-Such an ever increasing JS success can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}.
-On the other hand, due to of implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}.
-Thus, it is not surprising that once in a while critical bugs manage to break through~\cite{bugstories2017} into the web applications by Facebook, Twitter etc.
-
-Systematic unit testing is basic and, at the same time, the most effective technique for improving software quality.
-In practice, there are numerous of JS frameworks --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc.
---- intended to assist developers with the automation of various unit testing activities such as design, execution and monitoring.
-Despite the apparent abundance of the JS testing tools, the developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements.
-One of such areas is \emph{test data generation}.
-It pursues the goal of maximizing the test coverage by exercising the function under test (FUT) with different input parameters.
-Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.
-
-Generally, the problem of test data generation has been under an active study for the past three decades.
-In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the whole web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
-Out of those tools, only \emph{Confix} tries to construct a sufficient DOM fixture by translating native browser API calls into logical constraints.
-However, in the empirical evaluation~\cite{amin:ase15}, Confix only reached about 50\% in \emph{branch coverage} on the selected subjects.
-At the same time, search-based techniques have shown prominent results in achieving high branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications.
-But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of the search-based approach.
-In this paper we are breaching this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-We can summarize our contributions as follows:
-\begin{enumerate}[leftmargin=5mm]
-\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
-\item Our test generation algorithm, called ``genetic with restart'', is trying to escape search plateau by restarting GA with a new target.
-Because the full-fledged JS data flow analysis~\cite{jang2009points} is hard to reach, the new target is chosen purely based on the preceding control flow behaviour in contrast with more popular techniques~\cite{ferguson1996chaining}.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
-Moreover, we showed that on the selected subjects \emph{JEDI} outperforms \emph{Confix} ....
-\end{enumerate}
-
-The paper is structured as follows: In Section~\ref{sec.example}, we present a motivating example illustrating the challenges of generating test data for JS.
-The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} presents empirical validation and indicates the validity threats.
-Related and future work are discussed in Section~\ref{sec:related.work}.
-Section~\ref{sec:concl} concludes the paper.
-
-%% The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
-These frameworks support testing at various levels: unit, integration and functional.
-The survey also indicated a relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
-As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite this effort, test data generation continues to be poorly addressed by any of the widely used testing frameworks.
-The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of web application faults are DOM-related and introduced in the JS code, and not in other components such as HTML or CSS.
-This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
-%% --------------------------------------------------------------------
-\section{Motivating Example}
-\label{sec.example}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
-function isGameFinished() {
-  var obj = document.getElementById('sudoku'); |c \label{isGameFinished.getSudoku} |c
-  var subDivs = obj.getElementsByTagName('DIV'); |c \label{isGameFinished.getDivs} |c
-  var allOk = true;
-  for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
-    if (subDivs[no].className.indexOf('square') >= 0 |c \label{isGameFinished.if1.begin} |c 
-        && !subDivs[no].style.backgroundColor) { 
-      var spans = subDivs[no].getElementsByTagName('SPAN');
-      if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
-        allOk = false; //target |c \label{isGameFinished.unfinished} |c
-        break;}}}} |c \label{isGameFinished.outFor} |c
-\end{lstlisting}
-  \caption{JS function \texttt{isGameFinished.js} from sudoku}
-  \label{code.isGameFinished}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-                                 <div></div>                           
-  </div>                        </div> 
- </body>                       </body>    
-</html>                       </html>
-
-<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-   <div class='square'>          <div class='square'>
-    <span></span>                 <span></span> 
-    <span></span>                 <span>TEST</span>
-   </div>                        </div> 
-  </div>                        </div>
- </body>                       </body>
-</html>                       </html>
-  \end{lstlisting}
-  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
-  \label{fig.isGameFinished.tests}
-\end{figure}
-
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}~\cite{sudoku}.
-This function validates a sudoku solution given by a user.
-First, it finds a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, it collects all the child \emph{divs} (line~\ref{isGameFinished.getDivs}).
-Each \emph{div} element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}), and consists of two \emph{spans}.
-The first \emph{span} contains a user input, whereas the second one (hidden by default) stores an expected value for that sudoku square.
-Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
-
-Suppose now that we would like to unit test this function in isolation to the rest of the application.
-We aim to maximize the branch coverage as a common testing criteria~\cite{zhu1997software}.
-That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-A JS function can take \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as a DOM state.
-In general, in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
-
-%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
-
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together provide the full coverage of the FUT.
-Let us take a look at how to construct the \texttt{T4} test, which covers the branch $(10,11)$, by following the structure of the FUT.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with an id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{div} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this \emph{div} to be of the class \textquotesingle\texttt{square}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the \emph{div} consists of two \emph{span} elements whose \emph{innerHtml} values are not equal.
-The resulting test \texttt{T4} in Figure~\ref{fig.isGameFinished.tests} meets all the above conditions.
-
-As we have just observed, even for such a relatively simple example, the test data generation can be far from trivial procedure because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with a large number of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and the easiest to implement.
-It saves the developers from unexpected regressions and often documents the desired behavior of a program.
-
 %% --------------------------------------------------------------------
@@
 
-\begin{figure}[t!]
+\begin{figure}[!t]
   \centering
@@
       \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
+        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors $>$ 0}
           \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
@@
 
-          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
+          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors $>$ 0}
             \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
@@
 
-          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
+          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors $>$ 0}
             \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
@@
 
-\begin{algorithm}[t!]
+\begin{algorithm}[!t]
   \caption{Initialization Phase}
@@
 
-\begin{figure}[t!]
+\begin{figure}[!t]
 \setlength{\grammarparsep}{3pt}
-\footnotesize
+\scriptsize
 \begin{grammar}
@@
 
-\subsubsection{Instrumentation}
-\label{sub.sec.instrument}
+%% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+%%        LEFT OUT DUE TO LACK OF SPACE
+%% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+%% \subsubsection{Instrumentation}
+%% \label{sub.sec.instrument}
 
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
+%% Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
 The global variable \texttt{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT.
@@
 
-%TODO: maybe expand this section with the JS type casting for branch distance computation
+%% %TODO: maybe expand this section with the JS type casting for branch distance computation
 
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function isGameFinished() {
- trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
- trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
- var allOk = true;
- loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
-   var no = 0;
-   if (subDivs.length || subDivs.length == 0) {
-     return Math.abs(no - subDivs.length);
-   }; return 1}();
- trace.push(3);
- for (var no = 0; no < subDivs.length; no++) {
-  trace.push(4);
-  if (subDivs[no].className.indexOf("square") >= 0 &&
-      !subDivs[no].style.backgroundColor) {
-   trace.push(5); branchDistance.push({ label: 3, 
-    distance: Math.min(
-     abs(subDivs[no].className.indexOf("square"),0)+_K_ 
-     absZero(subDivs[no].style.backgroundColor))
-   });
-   trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
-   trace.push(7);
-   if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(8); branchDistance.push({ label: 7, 
-     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-    });
-    allOk = false; break;
-   } else {
-   trace.push(9);branchDistance.push({label:7,distance:_K_});
-   }
-  } else {
-   trace.push(10); branchDistance.push({ label: 3,
-    distance: 
-     abs(subDivs[no].className.indexOf("square"), 0) + 
-     absNegZero(subDivs[no].style.backgroundColor)
-   });}}
- trace.push(-1);
-}
-\end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
-  \label{code.isGameFinished.instr}
-\end{figure}
+%% \begin{figure}[!t]
+%%   \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
+%% function isGameFinished() {
+%%  trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
+%%  trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
+%%  var allOk = true;
+%%  loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
+%%    var no = 0;
+%%    if (subDivs.length || subDivs.length == 0) {
+%%      return Math.abs(no - subDivs.length);
+%%    }; return 1}();
+%%  trace.push(3);
+%%  for (var no = 0; no < subDivs.length; no++) {
+%%   trace.push(4);
+%%   if (subDivs[no].className.indexOf("square") >= 0 &&
+%%       !subDivs[no].style.backgroundColor) {
+%%    trace.push(5); branchDistance.push({ label: 3,
+%%     distance: Math.min(
+%%      abs(subDivs[no].className.indexOf("square"),0)+_K_
+%%      absZero(subDivs[no].style.backgroundColor))
+%%    });
+%%    trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
+%%    trace.push(7);
+%%    if (spans[0].innerHTML != spans[1].innerHTML) {
+%%     trace.push(8); branchDistance.push({ label: 7,
+%%      distance: abs(spans[0].innerHTML, spans[1].innerHTML)
+%%     });
+%%     allOk = false; break;
+%%    } else {
+%%    trace.push(9);branchDistance.push({label:7,distance:_K_});
+%%    }
+%%   } else {
+%%    trace.push(10); branchDistance.push({ label: 3,
+%%     distance:
+%%      abs(subDivs[no].className.indexOf("square"), 0) +
+%%      absNegZero(subDivs[no].style.backgroundColor)
+%%    });}}
+%%  trace.push(-1);
+%% }
+%% \end{lstlisting}
+%%   \caption{Instrumented version of \texttt{isGameFinished.js} }
+%%   \label{code.isGameFinished.instr}
+%% \end{figure}
 
@@
 
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{mcminn2004search}.
-For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it accidentally.
-In such a situation, we find ourselves being trapped on a flat space, with a small chance to escape.
-In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
+However, ff during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
 At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
@@
 
+In some cases, we get insufficient guidance from a fitness function because the FUT contains \emph{flag variables}~\cite{baresel2004evolutionary}, nested predicates~\cite{mcminn2005testability}, or unstructured control flow~\cite{hierons2005branch}.
+Researches have devised several techniques, such as \emph{chaining approach}~\cite{ferguson1996chaining,mcminn2006evolutionary} and \emph{testability transformation}~\cite{korel2005data}, to overcome with these problems.
+The common idea behind of these techniques is to incorporate data dependency into the search.
+In our case, such an analysis for JS is hard to implement~\cite{jang2009points}.
+So we decided to build our search algorithm purely on the knowledge about control-flow dependencies.
+The downside of this idea is the lack of precision, i.e some of the node sequences are fruitless to tackle.
+Nevertheless, it was sufficient to find solutions for our experimental subjects.
+
 The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
@@
 
-\begin{table}
+\begin{table}[!t]
   \caption{Genetic Operation for the JS Types}
   \label{tbl.gen.oper.js.types}
-    \footnotesize
+  \scriptsize
+  \centering
   \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
@@
     Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
-    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
-    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
+    Random    & Int    & choose (4:1) at random [-10, 10] or constants\\
+    Random    & Float  & choose (4:1) at random [-10.0, 10.0] or constants\\
+    Random    & String & $>5$ chars from $\texttt{[a-zA-Z0-9]}$ or constants (4:1)\\
     Random    & Array  & array of a respective type upto length five\\
@@
 
-\begin{figure}[t]
+\begin{figure}[!t]
+  \centering
   \begin{haskell}
@@
 The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating valid input data.
-The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
-without premature exception.
-Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-The FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
-\[
-\textit{fit}(n) = \text{approach level} +
+Our search target is a specific branch of the FUT that we want to cover.
+As a dynamically typed language, JS does not statically guarantee for an object that its accessed field or method are defined.
+Thus, such a behaviour can only be known at run-time and will eventually result into an exception.
+We have to assume that every statement of the FUT can rise an exception leading to the deviation from the target.
+We consider a test input as \emph{valid} only if it leads the FUT to a \emph{normal termination}, i.e.
+avoids exceptions.
+This is a ``stronger'' coverage criterion to satisfy then just passing the target branch because it additionally requires to reach an exit.
+Therefore, our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
+The FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}~\cite{arcuri2010does}.
+\begin{equation}
+\footnotesize
+F(n) = \text{approach level} +
 \begin{cases}
@@
 \end{cases}
-\]
-The final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
-\[
-\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
-\]
+\end{equation}
+The final FF ($F^*$) is an ordered pair of the FFs of the respective nodes.
+\begin{equation}
+\footnotesize
+F^*(n_b, n_x) = (F(n_b), F(n_x))
+\end{equation}
 Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
- \[
-\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
-\]
+ \begin{equation}
+\footnotesize
+F^*(n_1, n_2, \ldots, n_k) = (F(n_1), F(n_2), \ldots, F(n_k))
+\end{equation}
 
-The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
+The approach level is an integer value that indicates how many statements separate the target from the \emph{problem node}, i.e.
 the node causing the deviation.
 Since any node can potentially be exceptional, they all contribute to the approach level, in addition to the conditional branches.
-Loops have to be treated in a special way because we need to estimate the maximum number of iterations.
-In the case of a for-loop, at run-time we can always provide an exact bound.
-For while-loops, we assume that it has to be passed at least once.
+If on the way to a target there is a loop, we have to estimate its size.
+For for-loops, we can always provide an exact bound at run-time.
+Whereas, for while-loops, we assume that the loop has to be passed at least once.
 The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
-
-\subsubsection{Limitations}
-\label{sub.sub.sec.limit}
-
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
-%% --------------------------------------------------------------------
-\section{Empirical Evaluation}
-\label{sec.evaluation}
-%% --------------------------------------------------------------------
-
-In order to evaluate the feasibility of our test framework, we conducted an empirical evaluation on a set of case-studies (see Section~\ref{sub.sec.case.studies}).
-All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which plays the role of our baseline, is \emph{Random} ($\Random$).
-Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is important to note  that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic Algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On the one hand, the smaller window size forces the GA to converge faster and quickly discovers stagnation on a flat space.
-On the other hand, the small window can lead to premature archive convergence, which prevents the right genetic combination from being triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose to report only that case in the paper.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{fraser2011evosuite}.
-
-\begin{table}
-  \caption{Genetic Algorithm Configurations}
-  \label{tbl.gen.config}
-    \scriptsize
-  \begin{tabular}{l|r|r|r}
-    \toprule
-    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
-    \hline
-    Population size                   & 50  & 50  & 50  \\
-    Archive size                      & 1   & 25  & 25  \\
-    Maximum number of generations     & 200 & 200 & 200 \\
-    Crossover rate                    & 0   & 0.5 & 0.5 \\
-    Mutation rate                     & 0   & 0.5 & 0.5 \\
-    History window size               & -   & -   & 10  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-By carrying the evaluation, we would like to answer the following research questions:
-\begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
-Which testing algorithm is the most effective?
-How does effectiveness change with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost per iteration?
-\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
-\item[\textbf{RQ4 (comparison):}] What is the branch coverage of \emph{Confix}?
-\end{description}
-
-\subsection{Case Studies}
-\label{sub.sec.case.studies}
-
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless numbers of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React~\cite{todomvc}, offer an alternative approach to native DOM manipulation.
-Before selection, the source code of a potential case-study has to be scrutinized which is a time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011, tajsbenchmarks}.
-Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We added additional case-study \emph{mathjs}~\cite{mathjs} to increase the presence of primitive (browserless) JS code.
-For each case-study application, we identified several JS functions that are suitable for our testing framework.
-In the end, our evaluation set included both primitive and DOM related JS functions.
-
-For the sake of space, we chose to exclude from the following presentation the branches and functions the coverage time of which was less than two seconds.
-In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
-This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics~\cite{jsmeter} is the tool used for measuring JS code statistics: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the case studies in ~Table~\ref{tbl.case.studies}.
-
-\setlength\tabcolsep{1pt}
-\begin{table}[!t]
-  \caption{Summary of the Case-Studies}
-  \label{tbl.case.studies}
-  %\resizebox{\textwidth}{!}{
-    \scriptsize
-  \begin{tabular}{l|l|p{2.7cm}|c|c|c|c|c|c|c|c}
-    \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & helpMe & (int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & ()    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & ()           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & ()         & 8  & 0 & 2 & 1 & + & + & + & - \\
-    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (int,int)      & 23 & 2 & 3 & 3 & + & - & + & - \\
-    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
-    \hline
-    phormer    & toggleInfo & (string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
-    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
-    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
-    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
-    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
-    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
-    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
-    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
-    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
-    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
-    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & ([int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & ([int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
-    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
-    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
-    \hline
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
-    %% \hline
-    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
-    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
-    \bottomrule
-  \end{tabular}
-%}
-\end{table}
-
-\subsection{Results}
-\label{sub.sec.eval.results}
-
-\setlength\tabcolsep{.98pt}
-\begin{table}[!t]
-  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
-  \label{tbl.stats}
-    \scriptsize
-    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
-      \toprule
-      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{2-10} % \!:\!
-                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \midrule
-    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \textbf{newGame}*   
-                             & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \textbf{revealAll}*  
-                             & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-    \textbf{shuffleBoard}*   
-                             & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \hline
-   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \hline
-   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \hline
-   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \hline
-   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-   \midrule
-    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
-    \bottomrule
-   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \hline
-    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \hline
-    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
-    \midrule
-    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
-    %% \midrule
-    %% \midrule
-    \bottomrule
-    \bottomrule  
-    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-To study the effectiveness and efficiency of our test generation framework ($\Random$, $\Genetic$ and $\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
-In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ one for each algorithm.
-The next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-To the right of the function name, we also present accumulated statistics for the function as a whole.
-Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function.
-
-According to the industry standard~\cite{bray1997c4}, functions with a CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
-We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with CC's of 13, 14 and 16 respectively.
-Table~\ref{tbl.stats.sum} summarizes the results of the experiment such as coverage, execution time per branch and significance.
-
-\begin{table}[!t]
-  \caption{Result Summary (L - large, M - medium, S - small)}
-  \label{tbl.stats.sum}
-    \footnotesize
-    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
-      \toprule
-      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
-      \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{8-16}
-                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
-      \midrule
-      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
-      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
-      \midrule
-      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
-Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The underlined values in Table~\ref{tbl.stats} like $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
-The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
-branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of the genetic approach, $\Genetic$ may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
-We encountered three such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines the strengths of both $\Random$ and $\Genetic$.
-It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only managed to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
-branch $(69,71)$ of the \emph{initBricks} function.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
-  }
-}
-
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig.budget.progress}
-\end{figure}
-
-Additionally, we have investigated how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time dependent.
-E.g.
-running tests inside an IDE should be fast; as part of the CI cycle we may afford a larger waiting time; regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ overtakes $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
-  }
-}
-
-\paragraph{\textbf{RQ2 (efficiency).}}
- To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
-Based on this information, we suggest an estimate on the execution time of the testing framework.
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum of 40\%~(\emph{newGame}) and a maximum of 510\%~(\emph{isValidCard}).
-
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=950,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        restrict y to domain*=0:1350, % Cut values off at 14
-        visualization depends on=rawy\as\rawy, % Save the unclipped values
-        after end axis/.code={ % Draw line indicating break
-          \draw [ultra thick, white, decoration={snake, amplitude=1pt}, decorate] (rel axis cs:0,1.05) -- (rel axis cs:1,1.05);
-        },
-        nodes near coords={%
-          \pgfmathprintnumber{\rawy}% Print unclipped values
-        },
-        every node near coord/.append style={rotate=90,anchor=west,font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,270) (isGameFinished*,220) (newGame*,14) (revealAll*,50) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,514) (isValidVISA,95) (initShields*,5) (brickJiggler*,8) (doPaddlePower*,15)  (initBricks*,2379) (do\_draw,625) (prob\_gamma,710)};
-      \addplot[fill=red] coordinates {(helpMe*,47)  (isGameFinished*,30)  (newGame*,9)  (revealAll*,44) (shuffleBoard*,26) (toggleInfo*,7) (isValidCard,8)   (isValidVISA,3)  (initShields*,5) (brickJiggler*,4) (doPaddlePower*,140) (initBricks*,474) (do\_draw,1295) (prob\_gamma,84)};
-      \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Overall test generation time per function.}
-  \label{fig.gen.time.comp}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=4,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,1.24) (isGameFinished*,0.83) (newGame*,0.78) (revealAll*,0.83) (shuffleBoard*,1.93) (toggleInfo*,1) (isValidCard,0.51) (isValidVISA,0.47) (initShields*,0.83) (brickJiggler*,1.14) (doPaddlePower*,0.79)  (initBricks*,1.68) (do\_draw,2.33) (prob\_gamma,0.35)};
-      \addplot[fill=red] coordinates {(helpMe*,0.77)  (isGameFinished*,0.94)  (newGame*,0.81)  (revealAll*,1) (shuffleBoard*,1.73) (toggleInfo*,1) (isValidCard,0.38)   (isValidVISA,0.38)  (initShields*,0.83) (brickJiggler*,0.67) (doPaddlePower*,0.69) (initBricks*,0.8) (do\_draw,3.38) (prob\_gamma,0.52)};
-      \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Speed of test generation measured as $t/i$}
-    \label{fig.get.cost}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with  7 and 25 seconds per branch.
-For simple functions, $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
-In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch of 19, 39 and 88 seconds, respectively. 
-  }
-}
-
-Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
-This information is useful when configuring the maximal generation limit.
-The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures the speed of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost of the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus never rising exceptions, and at the same time, it consists of 40 LOC.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second on average for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse 1.4 seconds.
-  }
-}
-
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs relative to $\Genetic$.
-Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases generally across the board and 67\% on the difficult functions.  
-  }
-}
-
-\paragraph{\textbf{RQ4 (comparison).}} Authors of \emph{Confix}~\cite{amin:ase15} have proposed three strategies for test generation based on: 
-\begin{enumerate*}[label=(\roman*)]
-  \item \emph{Confix} entirely,
-  \item combination with \emph{Jalangi}~\cite{sen2013jalangi}, and
-  \item combination with a manual input. 
-\end{enumerate*}
-They reported a relative increase of 2\% and 19\% in branch coverage of the second and third strategies, respectively, over the first one.
-Even though, the third strategy performed the best, due to a manually enhanced data set, it is not objectively comparable with a fully automated technique, like \emph{JEDI}.
-Unfortunately, the open source version of \emph{Confix} we found online~\cite{confixgit} does not support an actual integration with \emph{Jalangi}.
-Neither, the paper~\cite{amin:ase15} highlights any implementation details of it.
-Thus in our evaluation Figure~\ref{tbl.confix.compare}, we had to fall back on the plain \emph{Confix} test generation.
-\Jedi seeks for a normal program termination during test generation, which is a stronger coverage criterion in comparison with only reaching a target branch provided by \Confix.
-Although, \Confix performs much faster (under 10 seconds), it is unable to discover hard to cover branches especially in terms of strong coverage.
-
-\begin{table}[!t]
-  \caption{Evaluation of \emph{Confix} (\#BR - total branches, \#BRC weak/strong - covered branches with exceptional/normal termination)}
-  \label{tbl.confix.compare}
-    \footnotesize
-    \centering
-    \begin{tabular}{l|l|c|c|c|c|c}
-      \toprule
-      \textbf{case-study} & \textbf{function} & \textbf{\#BR} & \textbf{\#C (weak)} & \textbf{\#C strong} & \textbf{\#tests} & \textbf{time (sec.)} \\
-      \hline
-      sudoku & helpMe          & 5  & 4 (80\%)  & 4 (80\%)  & 2 & 5 \\
-      sudoku & isGameFinished  & 5  & 2 (40\%)  & 2 (40\%)  & 2 & 5 \\
-      sudoku & newGame         & 3  & 3 (100\%) & 3 (100\%) & 4 & 6 \\
-      sudoku & revealAll       & 2  & 2 (100\%) & 0 (0\%)   & 6 & 11 \\
-      sudoku & shuffleBoard    & 7  & 5 (71\%)  & 0 (0\%)   & 2 & 5  \\
-      \hline
-      phormer & toogleInfo     & 4  & 2 (50\%)  & 2 (50\%)  & 3 & 5 \\
-      \hline
-      apophis & initShields    & 1  & 0 (0\%)   & 0 (0\%)   & 1 & 6 \\
-      \hline
-      bingbong & brickJiggler  & 2  & 0 (0\%)   & 0 (0\%)   & 1  & 3 \\
-      bingbong & doPaddlePower & 4  & 2 (50\%)  & 2 (50\%)  & 1  & 4 \\
-      bingbong & initBricks    & 18 & 3 (17\%)  & 0 (0\%) & 1  & 3 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{Threats to Validity}}
-The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Although, the branch coverage is a common criterion used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
-Reaching a target branch is only part of the problem: we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles leading to exceptions.
-Using a stronger oracle for validation is future work.
-Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent on unnecessary data explosion.
-Additional measures that could be applied is a minimization procedure, aka \emph{delta debugging}~\cite{misherghi2006hdd}, to the GA result.
-
-Initial GA configuration introduces a threat to the \emph{internal validity} of our empirical evaluation.
-The parameters we used are quite standard for similar SBST frameworks, e.g.
-EvoSuite.
-Although, not reported in the paper, we did perform a preliminary assessment of various GA configurations, which confirmed our final decision.
-
-The threat of \emph{conclusion validity} can be affected by the stochastic nature.
-This risk was addressed by repeating the experiment of GA 50 times and performing a statistical analysis of the significance and effect size.
-We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
-
-The \emph{external validity} deals with the threat of generalization of our results due to the manual selection of the experimental subjects.
-To mitigate this fact, we selected the subjects either from previous  related research or found in open source.
-Of course, those subjects still have to meet the constraints of our testing approach.
-So, further research is required in both increasing the power of our framework and extending the validation set.
-
-%% --------------------------------------------------------------------
-\section{Related and Future Work}
-\label{sec:related.work}
-%% --------------------------------------------------------------------
-
-The last two decades have been fruitful in the amount of work dedicates to the analysis of web applications and JavaScript, in particular.
-The state-of-the-art in this field including static and dynamic analysis of JS, as well as the test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around the two main questions:
-\begin{enumerate*}
-\item test data generation for JS functions interacting with the DOM, and
-\item the application of search-based techniques for that problem.
-\end{enumerate*}
-
-\subsection{Test Data Generation for JavaScript}
-
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect info about constant and feeds this data to the random generation.
-In comparison, our approach is the genetic generation.
-Additionally, we not only rely on the static information but also perform dynamic analysis to collect the run-time data.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} propose to use feedback-directed random testing for generation of TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing \emph{concolic testing} or {type inconsistency} analysis~\cite{pradel2015typedevil}.
-It suffers from common for the symbolic analysis problems such reasoning about arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtain DOM fixtures for the FUT.
-Combined with Jalangi, it can be used both for the generation of primitive data and DOM.
-As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
-Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS functions without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as a solid alternative for program testing.
-In fact, both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information for identifying potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011}, they extended the analysis with the abstractions able reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discovers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-
-\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the help the JS \emph{Proxies} in order to collect type related information.
-
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-
-%% \cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-%% \cite{ma2015grt} guided random testing
-
-%% \cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-%% \cite{jquery2014}
-
-%% ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-%% Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-%% Information-flow security for JS~\cite{hedin2012information}.
-
-%% Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-%% Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-%% Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-%% Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-%% DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Search-Based Test Data Generation}
-\label{sub.sec.search.based}
-
-Despite of the practical popularity of JavaScript, we have only encountered one work by Alshraideh~\cite{alshraideh2008complete} attempting to apply SBST to JavaScript.
-It uses GA for test generation with the goal cover all branches or kill all mutants, but it only deals with the limited input types such as booleans, integers and strings; and the provided validation is only based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports \emph{array} and \emph{DOM}, and conducts reasonable empirical validation with the discussion of significance and effect size.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-In this paper we deal with the generation and evolution of DOM which is an example of \emph{tree-like} data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim of improving test coverage of the XML-aware Java programs.
-To generate a random document, it may either rely on the  existing XML schema, or generate the document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, with extensive validation requirements.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for the mutation and crossover.
-Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
-
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of the SBST research~\cite{mcminn2011search}.
-Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a particular branch, we would like to have the set of tests maximizing the program coverage.
-That is, our solution is a vector of candidates which has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
-coverage vs.
-test-suite length.
-Another direction of future work is re-targeting out tool towards mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.
-
-% -----------------------
-Our test generation strategy is \emph{goal-oriented}~\cite{korel1992dynamic}, i.e.
-it tries to find an execution leading to a goal (statement) regardless of a concrete path taken.
-We uses control flow graph to identify implicit dependencies between nodes.
-
-The \emph{chaining approach}~\cite{ferguson1996chaining} uses data dependency to form the sequences of statements preceding the execution of a search target. 
-% -----------------------
-
-\section{Conclusions}
-\label{sec:concl}
-
-In this paper we have introduced a novel JS unit testing framework, called \emph{JEDI}, which uses search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{icse2018.bib}
-
-\end{document}

### 2018-05-11 doc/issre2018/graph-generation-speed.tex
Near final version of the issre 2018 paper

--- 2018-01-30 doc/icse2018/icse2018.tex
@@
-\documentclass[sigconf,review,anonymous]{acmart}
-
-\usepackage[inline]{enumitem}
-\usepackage{tablefootnote}
-\usepackage{syntax}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{booktabs} % For formal tables
-\usepackage{tikz}
-\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
-\usepackage{pgf-umlsd}
-\usepackage{tikz-uml}
-\usepackage{hyperref}
-\usepackage{upquote}
-\usepackage{listings}
-\usepackage{lsthaskell}
-\usepackage{xspace}
-\usepackage{enumitem}
-\usepackage{mdframed}
-\usepackage{algorithmic}
-\usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{pgfplots}
-\pgfplotsset{compat=newest}
-\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = red, %Colour of internal links
-  citecolor    = green %Colour of citations
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\definecolor{ltblue}{rgb}{0,0.4,0.4}
-\definecolor{dkblue}{rgb}{0,0.1,0.6}
-\definecolor{dkgreen}{rgb}{0,0.4,0}
-\definecolor{dkviolet}{rgb}{0.3,0,0.5}
-\definecolor{dkred}{rgb}{0.5,0,0}
-
-\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
-%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
-\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
-\definecolor{orange}{rgb}{1,0.45,0.13}		
-\definecolor{olive}{rgb}{0.17,0.59,0.20}
-\definecolor{brown}{rgb}{0.69,0.31,0.31}
-\definecolor{purple}{rgb}{0.38,0.18,0.81}
-\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
-\definecolor{lightred}{rgb}{1,0.4,0.5}
-% CSS
-\lstdefinelanguage{CSS}{
-  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},
-  sensitive=true,
-  morecomment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  morestring=[b]',
-  morestring=[b]",
-  alsoletter={:},
-  alsodigit={-}
-}
-
-% JavaScript
-\lstdefinelanguage{JavaScript}{
-  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
-  morecomment=[s]{/*}{*/},
-  morecomment=[l]//,
-  morestring=[b]",
-  morestring=[b]'
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  sensitive=true,	
-  alsoletter={<>=-},	
-  morecomment=[s]{<!-}{-->},
-  morestring=[b]'
-  tag=[s],
-  otherkeywords={
-  % General
-  >,
-  % Standard tags
-	<!DOCTYPE,
-  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
-	% body
-	</body, <body,
-	% Divs
-	</div, <div, </div>, 
-	% Paragraphs
-	</p, <p, </p>,
-	% scripts
-	</script, <script,
-  % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
-  },
-  ndkeywords={
-  % General
-  =,
-  % HTML attributes
-  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
-  % SVG attributes
-  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
-  % properties
-  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
-	% CSS3 properties
-  transform:, -moz-transform:, -webkit-transform:,
-  animation:, -webkit-animation:,
-  transition:,  transition-duration:, transition-property:, transition-timing-function:,
-  }
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  tagstyle=\color{blue},
-  markfirstintag=true,
-  sensitive=true,
-  alsoletter={<>=-},	
-  morecomment=[s]{<!--}{-->},
-  % tag=[s],
-  %% morestring=[b]'',
-  morestring=[b]',
-  ndkeywords={
-    % General
-    =,
-    % HTML attributes
-    id=, class= 
-  }
-}
-
-\lstdefinestyle{htmlcssjs} {%
-  % General design
-  backgroundcolor=\color{editorGray},
-  basicstyle={\scriptsize\ttfamily},   
-  frame=tb,
-  % line-numbers
-  xleftmargin={0.75cm},
-  numbers=left,
-  stepnumber=1,
-  firstnumber=1,
-  numberfirstline=true,	
-  % Code design
-  identifierstyle=\color{black},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywordstyle=\color{editorGreen}\bfseries,
-  stringstyle=\color{editorOcher}\ttfamily,
-  commentstyle=\color{brown}\ttfamily,
-  % Code
-  language=JavaScript,
-  alsolanguage=HTML5,
-  alsodigit={.:;},	
-  tabsize=2,
-  showtabs=false,
-  showspaces=false,
-  showstringspaces=false,
-  extendedchars=true,
-  breaklines=true,
-  escapechar=|c
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\listfiles % used to output the versions of all files being used by the latex
-
-\newcommand{\Server}{\emph{Server}\xspace}
-\newcommand{\Client}{\emph{Client}\xspace}
-\newcommand{\User}{\emph{User}\xspace}
-\newcommand{\Validator}{\emph{Validator}\xspace}
-\newcommand{\thenBr}{\text{then}}
-\newcommand{\elseBr}{\text{else}}
-\newcommand{\inFor}{\text{inFor}}
-\newcommand{\inWhile}{\text{while}}
-\newcommand{\un}[1]{\underline{#1}}
-\newcommand{\Random}{\mathbb{R}}
-\newcommand{\Genetic}{\mathbb{G}}
-\newcommand{\RGenetic}{\mathbb{G}_{10}}
-
-% Copyright
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-%% \acmYear{1997}                  
-%% \copyrightyear{2016}
-
-%% \acmPrice{15.00}
-
-\begin{document}
-\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
-
-\author{Alexander Elyasov}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands} 
-}
-\email{a.elyasov@uu.nl}
-
-\author{Wishnu Prasetya}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{s.w.b.prasetya@uu.nl}
-
-\author{Jurriaan Hage}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-  \country{The Netherlands} 
-}
-\email{j.hage@uu.nl}
-
-\begin{abstract}
-As of 2017 JavaScript and Node.js continue to stay the most prevalent technologies according to the Stack Overflow developers survey.
-Nevertheless, existing JS testing frameworks are still lacking any support for such a vital step in test automation as the generation of input data.
-To address this problem, we present a novel \textbf{J}avascript \textbf{E}volutionary-based testing framework with \textbf{D}OM as an \textbf{I}input, called \textbf{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state.
-We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
- It has shown that the \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage on all experimental subjects with the average 19 seconds of execution time per branch.
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Software and its engineering~Software testing and debugging}
-\ccsdesc[300]{Software and its engineering~Search-based software engineering}
-
-\keywords{JavaScript, search-based testing, branch coverage}
-
-\maketitle
-
-\section{Introduction}
-\label{sec.intro}
-
-According to a Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the fifth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
-It is used through all technology stack web, back-ends and mobile.
-Such a tremendous ever increasing JS success is happening thanks to the extensive dynamic features of the language, JS permissiveness and native browser support.
-On the other hand, JS applications are error-prone~\cite{why}, hard to analyze~\cite{why} and test~\cite{why}.
-Therefore, it is not surprising that year after year we hear new stories\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}} about another critical bug being found in a web application by Facebook, Twitter etc.
-
-%% Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.
-
-%% Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.
-
-The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
-These frameworks support testing at various levels: unit, integration and functional.
-The survey also indicated relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
-As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite of this effort, test data generation continues to be not properly addressed by any of the widely used testing frameworks.
-The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of JS faults are DOM-related and occur in JS code, and not in HTML or CSS.
-This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
-Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{mao2016sapienz}.
-In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript.
-Our work makes the following contributions:
-\begin{enumerate}[leftmargin=5mm]
-\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-\item We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency...
-\end{enumerate}
-
-The paper is structured as follows: In Section~\ref{sec.example}, we present a motivating example illustrating the challenges of generating test data for JS.
-The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} present empirical validation, whereas Section~\ref{sec.disc} discusses future work and validity threats.
-We discuss related work in Section~\ref{sec:related.work} and conclude the paper in Section~\ref{sec:concl}.
-
-Another empirical work~\cite{richards2010analysis}.
-
-%% --------------------------------------------------------------------
-\section{Motivating Example}
-\label{sec.example}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
-function isGameFinished() {
-  var obj = document.getElementById('sudoku'); |c \label{isGameFinished.getSudoku} |c
-  var subDivs = obj.getElementsByTagName('DIV'); |c \label{isGameFinished.getDivs} |c
-  var allOk = true;
-  for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
-    if (subDivs[no].className.indexOf('sudokuSquare') >= 0 |c \label{isGameFinished.if1.begin} |c 
-        && !subDivs[no].style.backgroundColor) { 
-      var spans = subDivs[no].getElementsByTagName('SPAN');
-      if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
-        allOk = false; |c \label{isGameFinished.unfinished} |c
-        break; 
-      }
-    }
-  } |c \label{isGameFinished.outFor} |c
-}
-\end{lstlisting}
-  \caption{JS function \texttt{isGameFinished.js} from sudoku}
-  \label{code.isGameFinished}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-                                 <div></div>                           
-  </div>                        </div> 
- </body>                       </body>    
-</html>                       </html>
-
-<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-   <div class='sudokuSquare'>    <div class='sudokuSquare'>
-    <span></span>                 <span></span> 
-    <span></span>                 <span>TEST</span>
-   </div>                        </div> 
-  </div>                        </div>
- </body>                       </body>
-</html>                       </html>
-  \end{lstlisting}
-  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
-  \label{fig.isGameFinished.tests}
-\end{figure}
-
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from a web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
-This function checks the validity of a sudoku solution given by a user.
-First, we find a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, we collect all its child DIVs (line~\ref{isGameFinished.getDivs}).
-Each DIV element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) and consists of two SPANs.
-First span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
-Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal SPAN values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
-
-Suppose now that we would like to unit test this function in isolation to the rest of the application.
-We aim to maximize the branch coverage as a common testing criteria~\cite{why.this.common}.
-That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
-We assume that DOM is the only global variable that can be referenced in the body of the FUT.
-So in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
-
-%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
-
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together deliver the full coverage of the FUT.
-Let us look now at how following the structure of the FUT in Figure~\ref{code.isGameFinished}, we can construct the $T4$ test covering the $(10,11)$ branch.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{DIV} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this $div$ to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the $div$ consists of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
-The resulted test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
-
-As we have just seen, even for such a relatively simple example, the construction procedure of a test input is far from trivial because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with the gazillion of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and, at the same time, it is easiest to implement.
-It greatly saves the developers from unexpected regression and puts a safety belt around the application.
-
-%% --------------------------------------------------------------------
-\section{Test Generation Framework}
-\label{sec.framework}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t!]
-  \centering 
-  \begin{sequencediagram}[font=\scriptsize]
-
-    \renewcommand\unitfactor{0.35}
-    \newinst{user}{\textbf{User}}
-    \newinst{server}{\textbf{Server}}
-    \newinst[1]{validator}{\textbf{Validator}}
-    \newinst{client}{\textbf{Client}}
-
-    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
-      \end{call}
-
-      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
-      \end{call}
-
-      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
-      \end{call}
-
-      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
-          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
-          \end{call}
-          \prelevel
-        \end{sdblock}
-
-        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
-            \end{call}
-
-            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
-            \end{callself}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
-          \end{callself}
-          \prelevel
-        \end{sdblock}
-        \mess{server}{best fitness}{user}
-
-      \end{sdblock}
-    \end{call}
-  \end{sequencediagram}
-  \caption{The architecture of the test framework}
-  \label{fig.framework.architect} 
-\end{figure}
-
-Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses the genetic engine for test generation.
-The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-\Server is the key component of the whole framework.
-It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}.
-Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactic correctness and reports back the set of identified errors.
-\Server rejects the document if any errors were revealed and generates a new one until the generated document has no errors anymore.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate the native browser API calls.
-
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
-Let us give a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random data generation, genetic phase, logging etc.
-Experimentally, we have found an optimal set of input configurations that was used across all experimental objects in Section~\ref{sec.evaluation}.
-This data is processed by the \Server during the \emph{Initialization Phase}.
-As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{ifun}, and the signature (\emph{sig}).
-\Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
-Depends on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
-the limit on the number of generation attempts.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate $p$ according to the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
-The execution trace along with some supplementary information about the execution are sent back to the \Server, where the final \emph{fitness value} is computed.
-The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-If a new HTML document is produced somewhere in the genetic phase, it has to be first approved by the \Validator.
-At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are exercised, the algorithm reaches the end.
-In the follow up two sections, we elaborate on the details of each individual phase of our test generation framework.
-
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
-
-During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing.
-The main steps of this phase are illustrated by Algorithm~\ref{alg.init}.
-Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info.
-Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName},
-which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT.
-Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants.
-Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure.
-Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
-
-\subsubsection{Supported Types}
-\label{sub.sec.sup.types}
-
-\begin{figure}[t!]
-\setlength{\grammarparsep}{3pt}
-\small
-\begin{grammar}
-
-<JS Type Annotation> ::= /*t <Signature> */
-
-<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
-
-<DOM> ::= \texttt{dom}
-
-<Type Signature> ::= <Type> | <Type> : <Type Signature>
-
-<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
-
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
-
-<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
-\end{grammar}
-\caption{Grammar of supported JS type annotations}
-\label{fig.js.type.annot}
-\end{figure}
-One assumption made in the paper is the availability of type signatures for JS functions.
-We believe in the legitimacy of such a request due to the following observations.
-First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity.
-Second, there has been an active work on the JS type inference done both in academia~\cite{kristensen2017type} and industry, e.g.
-Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.
-
-The grammar of the JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures those which refer to the global DOM and the ``ordinary'' JS type signatures.
-The functions of the former signature expect some \texttt{dom} argument to be passed as the first implicit parameter for the function call.
-Whereas ordinary JS signature is a non-zero sequence of the JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
-
-\subsubsection{Instrumentation}
-\label{sub.sec.instrument}
-
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \emph{trace} in line~\ref{isGameFinished.instr.trace} is an array of labels corresponding to the sequence of executed program statements.
-All statements have to be traced because each one, in theory, can rise an exception.
-The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations for the consecutive for-loop.
-If no exact bound can be computed, we set it to one.
-The \texttt{branchDistance} map tracks the distances to the deviated branches according to the translation formulae~\cite{tracey1998automated}.
-
-%TODO: maybe expand this section with the JS type casting for branch distance computation
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function isGameFinished() {
- trace.push(2); |c \label{isGameFinished.instr.trace} |c
- var obj = document.getElementById("sudoku");
- trace.push(3);
- var subDivs = obj.getElementsByTagName("DIV");
- trace.push(4);
- var allOk = true;
- loopMap[5] = function () { |c \label{isGameFinished.instr.loopMap} |c
-   var no = 0;
-   if (subDivs.length || subDivs.length == 0) {
-     return Math.abs(no - subDivs.length);
-   }
-   return 1;
- }();
- trace.push(5);
- for (var no = 0; no < subDivs.length; no++) {
-  trace.push(6);
-  trace.push(7);
-  if (subDivs[no].className.indexOf("sudokuSquare") >= 0 &&
-      !subDivs[no].style.backgroundColor) {
-   trace.push(8);
-   branchDistance.push({ 
-    label: 7, 
-    distance: Math.min(
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + _K_, 
-     absZero(subDivs[no].style.backgroundColor))
-   });
-   trace.push(9);
-   var spans = subDivs[no].getElementsByTagName("SPAN");
-   trace.push(10);
-   if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(11);
-    branchDistance.push({
-     label: 10,
-     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-    });
-    trace.push(12);
-    allOk = false;
-    break;
-   } else {
-     trace.push(14);
-     branchDistance.push({label: 10,distance: _K_});
-   }
-  } else {
-   trace.push(15);
-   branchDistance.push({
-    label: 7,
-    distance: 
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + 
-     absNegZero(subDivs[no].style.backgroundColor)
-   });
-  }
- }
- trace.push(5);
- trace.push(-1);
-}
-\end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
-  \label{code.isGameFinished.instr}
-\end{figure}
-
-\subsection{Genetic Phase}
-\label{sub.sec.genetic.phase}
-
-\begin{algorithm}[!t]
-  \caption{Genetic Phase}
-  \label{alg.gen}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{
-    $config$ is a GA configuration file\\
-    $b_n$ is a target branch of FUT\\
-    $(cfg, branches, cinfo, ifun, sig)$ output of Algorithm~\ref{alg.init}
-  }
-  \Output{
-     $(f^*, p^*)$ the best population candidate and its fitness score
-  }
-  \Fn{$Genetic(b_n, cfg, cinfo, config, ifun, sig)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M,size_{H}) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
-    $target \longleftarrow b_n$\label{alg.gen.init.target}\; 
-    $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
-    $historyConverged \longleftarrow true$\;
-    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
-      $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\; 
-      $history \longleftarrow \emptyset$\label{alg.gen.init.history}\; 
-      $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
-      \Repeat{$isPerfect(f^*) \vee historyConverged \vee (i > size_G)$}{\label{alg.gen.loop.begin}
-        $scoredPop \longleftarrow \emptyset$\;
-        $history \longleftarrow history \cup archive$\;
-        \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
-          $args \longleftarrow CoerceArguments(p, sig)$\label{alg.gen.make.args}\;
-          $(tr, d_B, d_L, dyncinfo) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
-          $f \longleftarrow Score(target, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
-          $cinfo \longleftarrow cinfo \cup dyncinfo$\label{alg.gen.eval.end}\;
-          $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        }
-        $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
-        $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
-        $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
-        $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
-        $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
-        $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
-        $i \longleftarrow i + 1$\;
-        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
-      }\label{alg.gen.loop.end}
-      $target \longleftarrow NewTarget(branches, b_n)$\label{alg.gen.new.target}\;
-    }\label{alg.gen.converged.loop.end}
-    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
-  }
-\end{algorithm}
-
-The heart of our test data generation framework is in the \emph{Genetic Phase}.
-Though, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, but has been extended with the concept of the \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we take a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
-The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
-
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ equal to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged or the generations limit has not been reached.
-The \emph{archive} variable stores the most fitted population candidates observed so far, and the \emph{history} variables records all archives during the generation process.
-These variables both are empty in the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
-
-The initial population has $size_P$ elements, and it is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found or the history has converged or the generation limit $size_G$ has been reached.
-But first, we need to score the current population lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
-Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
-Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
-Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
-This gives us 4-tuple consisting of an execution trace ($tr$), branch ($d_B$) and loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
-The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
-Collected dynamic constants \emph{dyncinfo} are merged with the existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}).
-And the $combo$ is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
-The fitness value of that element defines if a perfect candidate is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
-
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{ga.flag.problem.or.survey}.
-For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it occasionally.
-In such situation, we find ourselves being trapped on a flat space, with a small unreliable chance to escape.
-In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
-At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
-If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
-It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
-Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
-In practice, we only consider the target extensions upto the length of two.
-
-The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
-In the rest of this section, we reveal the implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our main focus in those sections is on the generation and transformation of HTML documents.
-
-\begin{table}
-  \caption{Genetic Operation for the JS Types}
-  \label{tbl.gen.oper.js.types}
-    \footnotesize
-  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
-    \toprule
-    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
-    \hline
-    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
-    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
-    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
-    Random    & Array  & array of a respective type upto length five\\
-    \hline
-    Crossover & Bool   & pick at random one out of two given booleans \\
-    Crossover & Int    & pick at random one out of two given integers\\
-    Crossover & Float  & pick at random one out of two given floats\\
-    Crossover & String & pick at random one out of two single point crossovers\\
-    Crossover & Array  & similar crossover operator as for strings\\
-    \hline
-    Mutation  & Bool   & flip the boolean constant\\
-    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
-    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
-    Mutation  & String & random string, remove char or apply pred(suc) char\\
-    Mutation  & Array  & Mutate a random element in array according to its type\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsubsection{Random HTML Generation}
-\label{sub.sub.sec.random.html}
-
-\begin{figure}[t]
-  \begin{haskell}
-instance Arbitrary Html where
-  arbitrary = evalStateT generateHTML defaultState
-
-generateHTML :: GenHtmlState |c \label{ref.generateHTML.begin} |c
-generateHTML = do
-  state <- get |c \label{ref.generateHTML.getState} |c   
-  let d = getDepth state |c \label{ref.generateHTML.getDepth} |c
-  if d == 0
-  then lift \dollar return \dollar toHtml "HTML" |c \label{ref.generateHTML.returnString} |c
-  else do put state{depth = d - 1} |c \label{ref.generateHTML.updateState} |c
-           head <- generateHEAD |c \label{ref.generateHTML.newHead} |c
-           body <- generateBODY |c \label{ref.generateHTML.newBody} |c
-           lift\dollar return \dollar docTypeHtml \dollar head >> body |c \label{ref.generateHTML.end} |c
-
-data Tag = HTML | HEAD | BODY | ...
-type Context = CFlow | CMetadata | ...
-data HtmlState = |c \label{ref.HtmlState.begin} |c
-  HtmlState { depth    :: Int,           degree  :: Int    
-             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
-             , tags    :: [Tag],         ids     :: [String]
-             , classes :: [String] } |c \label{ref.HtmlState.end} |c
-type GenState s = StateT s Gen |c \label{ref.GenState} |c
-type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
-  \end{haskell}
-  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
-  \label{fig.html.arb.def}
-\end{figure}
-
-We want to generate HTML according to the WHATWG\footnote{\url{https://html.spec.whatwg.org}} specification.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-The recent HTML5 standard defines more than hundred of tags and attributes which both have to comply with extremely complex logic to constitute a syntactically valid HTML.
-Browsers are usually tolerant to syntactic errors in HTML.
-They will silently fix them and display the page anyway.
-
-In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because, as we have mentioned early, the complexity of HTML and the lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} highlights that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) describes the internal state of \texttt{Html} in the generation.
-The state is composed of the following components:
-\begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of HTML 
-\item \texttt{ctx} is the current value of the HTML content model stack 
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
-\end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag should be defined as the value of the \texttt{GenHtmlState} type.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
-First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
-Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the new contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
-
-\subsubsection{Genetic HTML Operations}
-\label{sub.sub.sec.genetic.oper}
-
-In essence, HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for the \emph{expression trees} in genetic programming.
-
-\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
-
-\textbf{HTML Mutations} are of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
-The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
-The \emph{DropTree} mutation removes the whole sub-tree at a randomly chosen node.
-\emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
-Currently, we instantiated the \emph{ShuffleAttributes} mutation for only for tho types \emph{class} and \emph{id}.
-In total, this gives us four mutations to chose from in order to evolve an Html document.
-
-\subsubsection{Fitness Function}
-\label{sub.sub.sec.fitness.fun}
-
-The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating a valid input data.
-The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
-without premature exception.
-Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
-\[
-\textit{fit}(n) = \text{approach level} +
-\begin{cases}
- 1/2 * (\frac{\text{branch distance}}{1 + \text{branch distance}}) & \text{if no exception}\\
- 1                                  &  \text{otherwise}
-\end{cases}
-\]
-Final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
-\[
-\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
-\]
-Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
- \[
-\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
-\]
-
-The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
-the node caused the deviation.
-Since any node can potentially be exceptional, they all contribute to the approach level in addition to the conditional branches.
-Loops have to treated in a special way because we need to estimate the maximum number of iterations.
-In the case of for-loop, at run-time we can always provide an exact bound.
-For while-loops, we assume that it has to be passed at least once.
-The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
-
-\subsubsection{Limitations}
-\label{sub.sub.sec.limit}
-
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
-%% --------------------------------------------------------------------
-\section{Empirical Evaluation}
-\label{sec.evaluation}
-%% --------------------------------------------------------------------
-
-In order to evaluate the feasibility of our test framework adoption in practice, we conducted an empirical evaluation on a set of case-studies described in Section~\ref{sub.sec.case.studies}.
-All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which play the role of our baseline, is \emph{Random} ($\Random$).
-Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is the \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On one hand, the smaller window size forces the GA to converge faster and early discovers the stagnation on a flat space.
-On the other hand, the small window can lead to a premature archive convergence, which prevents the right genetic combination from been triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose it to report in the paper.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{fraser2011evosuite}.
-
-\begin{table}
-  \caption{Genetic Algorithm Configurations}
-  \label{tbl.gen.config}
-    \scriptsize
-  \begin{tabular}{l|r|r|r}
-    \toprule
-    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
-    \hline
-    Population size                   & 50  & 50  & 50  \\
-    Archive size                      & 1   & 25  & 25  \\
-    Maximum number of generations     & 200 & 200 & 200 \\
-    Crossover rate                    & 0   & 0.5 & 0.5 \\
-    Mutation rate                     & 0   & 0.5 & 0.5 \\
-    History window size               & -   & -   & 10  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-By carrying the evaluation, we would like to address the following research questions:
-\begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
-Which testing algorithm is the most effective?
-How the effectiveness changes with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost of one iteration?
-\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
-\end{description}
-
-\subsection{Case Studies}
-\label{sub.sec.case.studies}
-
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless number of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation.
-Before selection, the source code of a potential case-study has to be scrutinized which is time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
-Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}} to increase the presence of primitive (browserless) JS code.
-For each case-study application, we identified several JS functions that are suitable for our testing framework.
-In the end, our evaluation set included both primitive and DOM related JS functions.
-
-For the sake of space, we chose to exclude from the follow up presentation the branches and functions which coverage time was less than two seconds.
-In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
-This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the aforementioned case studies with the results presented in Section~\ref{sub.sec.eval.results}.
-
-\setlength\tabcolsep{0.6pt}
-\begin{table}[t]
-  \caption{Summary of the Case-Studies}
-  \label{tbl.case.studies}
-  %\resizebox{\textwidth}{!}{
-    \scriptsize
-  \begin{tabular}{l|l|p{3.1cm}|c|c|c|c|c|c|c|c}
-    \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & (dom)           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & (dom)         & 8  & 0 & 2 & 1 & + & + & + & - \\
-    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & + & - & + & - \\
-    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
-    \hline
-    phormer    & toggleInfo & (dom,string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
-    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
-    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
-    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
-    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
-    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
-    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
-    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
-    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
-    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
-    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & (dom,[int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
-    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
-    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
-    \hline
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
-    %% \hline
-    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
-    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
-    \bottomrule
-  \end{tabular}
-%}
-\end{table}
-
-\subsection{Results}
-\label{sub.sec.eval.results}
-
-\setlength\tabcolsep{.98pt}
-\begin{table}[!t]
-  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
-  \label{tbl.stats}
-    \scriptsize
-    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
-      \toprule
-      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{2-10} % \!:\!
-                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \midrule
-    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \textbf{newGame}*   
-                             & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \textbf{revealAll}*  
-                             & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-    \textbf{shuffleBoard}*   
-                             & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \hline
-   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \hline
-   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \hline
-   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \hline
-   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-   \midrule
-    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
-    \bottomrule
-   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \hline
-    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \hline
-    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
-    \midrule
-    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
-    %% \midrule
-    %% \midrule
-    \bottomrule
-    \bottomrule  
-    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-To study the effectiveness and efficiency of our test generation framework, including three test algorithms Random~($\Random$), Genetic~($\Genetic$) and Genetic with Restart~($\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
-In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ according to the algorithm type $\Random$, $\Genetic$ and $\RGenetic$.
-Next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-Inline with the function name, we also present accumulated statistics for the function as a whole.
-Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function.
-
-According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
-We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with the respective the CC 13, 14 and 16.
-Table~\ref{tbl.stats.sum} summarizes the total results of the experiment such as coverage, execution time per branch and significance.
-
-\begin{table}[!t]
-  \caption{Result Summary (L - large, M - medium, S - small)}
-  \label{tbl.stats.sum}
-    \footnotesize
-    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
-      \toprule
-      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
-      \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{8-16}
-                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
-      \midrule
-      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
-      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
-      \midrule
-      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
-Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The values in Table~\ref{tbl.stats} highlighted as $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
-The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
-branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of genetic approach~($\Genetic$), it may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
-We encountered three of such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines strengths of both algorithms genetic and random.
-It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only manged to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
-branch $(69,71)$ of the \emph{initBricks} function.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
-  }
-}
-
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig.budget.progress}
-\end{figure}
-
-Additionally, we would like to investigate how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time depended.
-E.g.
-running tests inside IDE should be fast; as part of the CI cycle we may afford a large waiting time; regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ starts to transcend $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
-  }
-}
-
-\paragraph{\textbf{RQ2 (efficiency).}}
- To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
-Based on this information, we suggest an estimate on the execution time of the testing framework.
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
-
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=950,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        restrict y to domain*=0:1350, % Cut values off at 14
-        visualization depends on=rawy\as\rawy, % Save the unclipped values
-        after end axis/.code={ % Draw line indicating break
-          \draw [ultra thick, white, decoration={snake, amplitude=1pt}, decorate] (rel axis cs:0,1.05) -- (rel axis cs:1,1.05);
-        },
-        nodes near coords={%
-          \pgfmathprintnumber{\rawy}% Print unclipped values
-        },
-        every node near coord/.append style={rotate=90,anchor=west,font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,270) (isGameFinished*,220) (newGame*,14) (revealAll*,50) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,514) (isValidVISA,95) (initShields*,5) (brickJiggler*,8) (doPaddlePower*,15)  (initBricks*,2379) (do\_draw,625) (prob\_gamma,710)};
-      \addplot[fill=red] coordinates {(helpMe*,47)  (isGameFinished*,30)  (newGame*,9)  (revealAll*,44) (shuffleBoard*,26) (toggleInfo*,7) (isValidCard,8)   (isValidVISA,3)  (initShields*,5) (brickJiggler*,4) (doPaddlePower*,140) (initBricks*,474) (do\_draw,1295) (prob\_gamma,84)};
-      \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Overall test generation time per function.}
-  \label{fig.gen.time.comp}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
+  \begin{tikzpicture}[scale=0.9,rotate=-90]
     \begin{axis}[
@@
         width=11cm,height=3.3cm,
-        bar width=3pt,
+        bar width=4pt,
         enlarge x limits=0.05,
@@
         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
+        %xtick=data,
         nodes near coords,
@@
         clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
+        % x tick label style={rotate=90,anchor=east,font=\footnotesize\bfseries},
+        xticklabels={,,},
         y tick label style={font=\footnotesize}
@@
   \end{tikzpicture}
-  \caption{Speed of test generation measured as $t/i$}
-    \label{fig.get.cost}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with the 7 and 25 seconds per branch.
-For simple functions, the $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
-In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch 19, 39 and 88 seconds, respectively. 
-  }
-}
-
-Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
-This information is useful when configuring the maximal generation limit.
-The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures the speed of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus not rising exceptions, and at the same time, it consists of 40 LOC.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
-  }
-}
-
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs comparing to $\Genetic$.
-Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases globally and 67\% on the difficult functions.  
-  }
-}
-
-\paragraph{\textbf{Threats to Validity}}
-The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Though, the branch coverage is a common criteria used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
-Reaching a target branch is only part of the problem, we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles disseminating in exceptions.
-Using a stronger oracle for validation is future work.
-Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent unnecessary data explosion.
-Additional measure that could be taken is applying a minimization procedure, aka \emph{delta debugging}, to the GA result.
-
-Initial GA configuration introduces the threat to the \emph{internal validity} of our empirical evaluation.
-The parameters we used are quite standard for similar SBST frameworks, e.g.
-EvoSuite.
-Though, not reported in the paper, we performed preliminary assessment of various GA configurations, which confirmed our final decision.
-
-The threat of \emph{conclusion validity} can be affected by the GA stochastic nature.
-This risk was addressed by repeating the experiment 50 times and performing statistical analysis of the significance and effect size.
-We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
-
-The \emph{external validity} deals with the threat of generalization of our results due to manual selection of the experimental subjects.
-To mitigate this fact, we picked the subjects either from previously used in related research or found in open source.
-Of course, those subjects still have to met the constrains of our testing approach.
-So, further research is required in both increasing the power of our framework and extending the validation set.
-
-%% --------------------------------------------------------------------
-\section{Related and Future Work}
-\label{sec:related.work}
-%% --------------------------------------------------------------------
-
-The last two decades were fruitful in the amount of work dedicates to the analysis and web applications and JavaScript, in particular.
-The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around two main questions:
-\begin{enumerate*}
-\item test data generation for JS functions interacting with the DOM, and
-\item the application of search-based techniques for that problem.
-\end{enumerate*}
-
-\subsection{Test Data Generation for JavaScript}
-
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect constant info and feed it to the random generation.
-We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} proposes to use feedback-directed random testing for generating TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing concolic testing or type inconsistency analysis~\cite{pradel2015typedevil}.
-It suffers from typical for the symbolic analysis problems such as the handing of arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtains DOM fixtures for the FUT.
-Combined with Jalangi it can be used for both primitive and DOM test data generation.
-As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
-Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as solid alternative for program testing.
-In fact both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discoverers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-
-\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the JS \emph{Proxies} in order to collect type related information.
-
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-
-\cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-\cite{ma2015grt} guided random testing
-
-\cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-\cite{jquery2014}
-
-ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-Information-flow security for JS~\cite{hedin2012information}.
-
-Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Search-Based Test Data Generation}
-\label{sub.sec.search.based}
-
-Despite of the practical popularity of JavaScript, the only recorded in the literature attempt of adopting search-based testing for JS unit testing was done by Alshraideh~\cite{alshraideh2008complete}.
-It uses GA for branch and mutation coverage, but only deals with the limited input types booleans, integers and strings; and provides validation based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports array and DOM types, with suggest reasonable validation with the discussion of significance and effect size.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-In this paper we dealt with the generation and evolution of DOM which is an example of tree-like data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim to improve test coverage of the XML-aware Java programs.
-To generate random document, it may rely on existing XML schema, or generate document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, which is difficult to comply.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for mutation and crossover.
-Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
-
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of SBST research~\cite{mcminn2011search}.
-Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage.
-That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
-coverage vs.
-test-suite length.
-Another direction of future work is adjusting out tool for mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That would also help us to judge about the fault revealing ability of \emph{JEDI} based on the number of killed mutants.
-As we said early in this section, SBST techniques can benefit from symbolic analysis~\cite{baars2011symbolic}.
-
-\section{Conclusions}
-\label{sec:concl}
-This paper
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{icse2018.bib}
-
-\end{document}

### 2018-05-11 doc/issre2018/introduction.tex
Near final version of the issre 2018 paper

--- 2018-05-07 doc/icse2018/issta2018.tex
@@
-\documentclass[sigconf,review]{acmart}
-
-\usepackage[inline]{enumitem}
-\usepackage{tablefootnote}
-\usepackage{syntax}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{booktabs} % For formal tables
-\usepackage{tikz}
-\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
-\usepackage{pgf-umlsd}
-\usepackage{tikz-uml}
-\usepackage{hyperref}
-\usepackage{upquote}
-\usepackage{listings}
-\usepackage{lsthaskell}
-\usepackage{xspace}
-\usepackage{enumitem}
-\usepackage{mdframed}
-\usepackage{algorithmic}
-\usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{pgfplots}
-\pgfplotsset{compat=newest}
-\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = red, %Colour of internal links
-  citecolor    = green %Colour of citations
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\definecolor{ltblue}{rgb}{0,0.4,0.4}
-\definecolor{dkblue}{rgb}{0,0.1,0.6}
-\definecolor{dkgreen}{rgb}{0,0.4,0}
-\definecolor{dkviolet}{rgb}{0.3,0,0.5}
-\definecolor{dkred}{rgb}{0.5,0,0}
-
-\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
-%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
-\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
-\definecolor{orange}{rgb}{1,0.45,0.13}		
-\definecolor{olive}{rgb}{0.17,0.59,0.20}
-\definecolor{brown}{rgb}{0.69,0.31,0.31}
-\definecolor{purple}{rgb}{0.38,0.18,0.81}
-\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
-\definecolor{lightred}{rgb}{1,0.4,0.5}
-% CSS
-\lstdefinelanguage{CSS}{
-  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},
-  sensitive=true,
-  morecomment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  morestring=[b]',
-  morestring=[b]",
-  alsoletter={:},
-  alsodigit={-}
-}
-
-% JavaScript
-\lstdefinelanguage{JavaScript}{
-  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
-  morecomment=[s]{/*}{*/},
-  morecomment=[l]//,
-  morestring=[b]",
-  morestring=[b]'
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  sensitive=true,	
-  alsoletter={<>=-},	
-  morecomment=[s]{<!-}{-->},
-  morestring=[b]'
-  tag=[s],
-  otherkeywords={
-  % General
-  >,
-  % Standard tags
-	<!DOCTYPE,
-  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
-	% body
-	</body, <body,
-	% Divs
-	</div, <div, </div>, 
-	% Paragraphs
-	</p, <p, </p>,
-	% scripts
-	</script, <script,
-  % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
-  },
-  ndkeywords={
-  % General
-  =,
-  % HTML attributes
-  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
-  % SVG attributes
-  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
-  % properties
-  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
-	% CSS3 properties
-  transform:, -moz-transform:, -webkit-transform:,
-  animation:, -webkit-animation:,
-  transition:,  transition-duration:, transition-property:, transition-timing-function:,
-  }
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  tagstyle=\color{blue},
-  markfirstintag=true,
-  sensitive=true,
-  alsoletter={<>=-},	
-  morecomment=[s]{<!--}{-->},
-  % tag=[s],
-  %% morestring=[b]'',
-  morestring=[b]',
-  ndkeywords={
-    % General
-    =,
-    % HTML attributes
-    id=, class= 
-  }
-}
-
-\lstdefinestyle{htmlcssjs} {%
-  % General design
-  backgroundcolor=\color{editorGray},
-  basicstyle={\scriptsize\ttfamily},   
-  frame=tb,
-  % line-numbers
-  xleftmargin={0.75cm},
-  numbers=left,
-  stepnumber=1,
-  firstnumber=1,
-  numberfirstline=true,	
-  % Code design
-  identifierstyle=\color{black},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywordstyle=\color{editorGreen}\bfseries,
-  stringstyle=\color{editorOcher}\ttfamily,
-  commentstyle=\color{brown}\ttfamily,
-  % Code
-  language=JavaScript,
-  alsolanguage=HTML5,
-  alsodigit={.:;},	
-  tabsize=2,
-  showtabs=false,
-  showspaces=false,
-  showstringspaces=false,
-  extendedchars=true,
-  breaklines=true,
-  escapechar=|c
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\listfiles % used to output the versions of all files being used by the late
-
-\newcommand{\Server}{\emph{Server}\xspace}
-\newcommand{\Client}{\emph{Client}\xspace}
-\newcommand{\User}{\emph{User}\xspace}
-\newcommand{\Validator}{\emph{Validator}\xspace}
-\newcommand{\thenBr}{\text{then}}
-\newcommand{\elseBr}{\text{else}}
-\newcommand{\inFor}{\text{inFor}}
-\newcommand{\inWhile}{\text{while}}
-\newcommand{\un}[1]{\underline{#1}}
-\newcommand{\Random}{\mathbb{R}}
-\newcommand{\Genetic}{\mathbb{G}}
-\newcommand{\RGenetic}{\mathbb{G}_{10}}
-
-% Copyright
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-%% \acmYear{1997}                  
-%% \copyrightyear{2016}
-
-%% \acmPrice{15.00}
-
-\begin{document}
-\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
-
-\author{Alexander Elyasov}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands} 
-}
-\email{a.elyasov@uu.nl}
-
-\author{Wishnu Prasetya}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{s.w.b.prasetya@uu.nl}
-
-\author{Jurriaan Hage}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{j.hage@uu.nl}
-
-\begin{abstract}
-The popularity of JavaScript is continuously growing.
-Together with HTML and CSS, it forms the core technology stack for web development.
-Because of the dynamic nature and complex interplay with HTML, JS applications are still error-prone and vulnerable.
-Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS applications interacting with the DOM has not yet been addressed.
-In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including the global DOM state.
-We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
-It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Software and its engineering~Software testing and debugging}
-\ccsdesc[300]{Software and its engineering~Search-based software engineering}
-
-\keywords{JavaScript, search-based testing, branch coverage}
-
-\maketitle
-
 %% ------------------------------------------------------------------------
@@
 This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
-%% --------------------------------------------------------------------
-\section{Motivating Example}
-\label{sec.example}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
-function isGameFinished() {
-  var obj = document.getElementById('sudoku'); |c \label{isGameFinished.getSudoku} |c
-  var subDivs = obj.getElementsByTagName('DIV'); |c \label{isGameFinished.getDivs} |c
-  var allOk = true;
-  for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
-    if (subDivs[no].className.indexOf('sudokuSquare') >= 0 |c \label{isGameFinished.if1.begin} |c 
-        && !subDivs[no].style.backgroundColor) { 
-      var spans = subDivs[no].getElementsByTagName('SPAN');
-      if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
-        allOk = false; |c \label{isGameFinished.unfinished} |c
-        break; 
-      }
-    }
-  } |c \label{isGameFinished.outFor} |c
-}
-\end{lstlisting}
-  \caption{JS function \texttt{isGameFinished.js} from sudoku}
-  \label{code.isGameFinished}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-                                 <div></div>                           
-  </div>                        </div> 
- </body>                       </body>    
-</html>                       </html>
-
-<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-   <div class='sudokuSquare'>    <div class='sudokuSquare'>
-    <span></span>                 <span></span> 
-    <span></span>                 <span>TEST</span>
-   </div>                        </div> 
-  </div>                        </div>
- </body>                       </body>
-</html>                       </html>
-  \end{lstlisting}
-  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
-  \label{fig.isGameFinished.tests}
-\end{figure}
-
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
-This function checks the validity of a sudoku solution given by a user.
-First, we find the DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, we collect all its child DIVs (line~\ref{isGameFinished.getDivs}).
-Each DIV element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) and consists of two SPANs.
-The first span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
-Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal SPAN values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
-
-Suppose now that we would like to unit test this function in isolation to the rest of the application.
-We aim to maximize the branch coverage as a common testing criteria~\cite{zhu1997software}.
-That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-The JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
-Henceforth, we assume that DOM is the only global variable that is allowed to be referred to in the body of the FUT.
-In general, in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
-
-%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
-
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together provide the full coverage of the FUT.
-Let us look now at how following the structure of the FUT in Figure~\ref{code.isGameFinished}, we can construct the $T4$ test covering the $(10,11)$ branch.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{DIV} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this $div$ to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the $div$ consists of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
-The resulting test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
-
-As we have just seen, even for such a relatively simple example, the construction procedure of a test input is far from trivial because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with a large number of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and the easiest to implement.
-It saves the developers from unexpected regressions and often documents the desired behavior of a program.
-
-%% --------------------------------------------------------------------
-\section{Test Generation Framework}
-\label{sec.framework}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t!]
-  \centering 
-  \begin{sequencediagram}[font=\scriptsize]
-
-    \renewcommand\unitfactor{0.35}
-    \newinst{user}{\textbf{User}}
-    \newinst{server}{\textbf{Server}}
-    \newinst[1]{validator}{\textbf{Validator}}
-    \newinst{client}{\textbf{Client}}
-
-    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
-      \end{call}
-
-      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
-      \end{call}
-
-      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
-      \end{call}
-
-      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
-          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
-          \end{call}
-          \prelevel
-        \end{sdblock}
-
-        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
-            \end{call}
-
-            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
-            \end{callself}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
-          \end{callself}
-          \prelevel
-        \end{sdblock}
-        \mess{server}{best fitness}{user}
-
-      \end{sdblock}
-    \end{call}
-  \end{sequencediagram}
-  \caption{The architecture of the test framework}
-  \label{fig.framework.architect} 
-\end{figure}
-
-Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $\mathbb{B}_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses a genetic engine for test generation.
-The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-The \Server is the key component of the  framework.
-It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}.
-Both phases will be covered in detail in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactic correctness and reports back the set of identified errors.
-\Server rejects the document if any errors were revealed and generates a new one until the generated document has no more errors.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate the native browser API calls.
-
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
-Let us take a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with a type signature.
-Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random and genetic phases, logging etc.
-Experimentally, we have found an optimal set of input configurations that was used across all experimental objects in Section~\ref{sec.evaluation}.
-This data is processed by the \Server during the \emph{Initialization Phase}.
-As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
-The \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
-Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
-the limit on the number of generation attempts.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate $p$ with the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
-The execution trace along with some supplementary information about the execution are sent back to the \Server, where the \emph{fitness value} is computed.
-The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-If a new HTML document is produced somewhere in the genetic phase, it has to be first approved by the \Validator.
-At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are covered, the algorithm reaches the end.
-Below, we elaborate on the details of each individual phase of our test generation framework.
-
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
-
-During the \emph{Initialization Phase} we analyze the FUT in order to retrieve the data required for the subsequent genetic testing.
-The main steps of this phase are described in Algorithm~\ref{alg.init}.
-Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants.
-Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods: \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName}
-These methods provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the FUT.
-The next step is to normalize the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants.
-Upon the \emph{ifun} execution this information is gathered and fed back to the fitness evaluation procedure.
-Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
-
-\subsubsection{Supported Types}
-\label{sub.sec.sup.types}
-
-\begin{figure}[t!]
-\setlength{\grammarparsep}{3pt}
-\footnotesize
-\begin{grammar}
-
-<JS Type Annotation> ::= /*t <Signature> */
-
-<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
-
-<DOM> ::= \texttt{dom}
-
-<Type Signature> ::= <Type> | <Type> : <Type Signature>
-
-<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
-
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
-
-<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
-\end{grammar}
-\caption{Grammar of supported JS type annotations}
-\label{fig.js.type.annot}
-\end{figure}
-One assumption made in the paper is the availability of type signatures for JS functions.
-We believe in the legitimacy of such a request due to the following observations.
-First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity.
-Second, there has been an active work on the JS type inference done both in academia~\cite{kristensen2017type} and industry, e.g.
-Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.
-
-The grammar of the JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures: those which refer to the global DOM and ``ordinary'' JS type signatures.
-The functions with the former kind expect some \texttt{dom} argument to be passed as the first implicit parameter of the function call.
-Whereas ordinary JS signature is a non-empty sequence of the JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
-
-\subsubsection{Instrumentation}
-\label{sub.sec.instrument}
-
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \emph{trace} in line~\ref{isGameFinished.instr.trace} is an array of labels corresponding to the sequence of executed program statements.
-All statements have to be traced because each one, in theory, can raise an exception.
-The \texttt{loopMap} map in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations of the respective for-loop.
-If no exact bound can be computed, we set it to one.
-The \texttt{branchDistance} map records the conditional distance~\cite{tracey1998automated} on the branch where the deviation from the target branch has happened.
-
-%TODO: maybe expand this section with the JS type casting for branch distance computation
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function isGameFinished() {
- trace.push(2); |c \label{isGameFinished.instr.trace} |c
- var obj = document.getElementById("sudoku");
- trace.push(3);
- var subDivs = obj.getElementsByTagName("DIV");
- trace.push(4);
- var allOk = true;
- loopMap[5] = function () { |c \label{isGameFinished.instr.loopMap} |c
-   var no = 0;
-   if (subDivs.length || subDivs.length == 0) {
-     return Math.abs(no - subDivs.length);
-   }
-   return 1;
- }();
- trace.push(5);
- for (var no = 0; no < subDivs.length; no++) {
-  trace.push(6);
-  trace.push(7);
-  if (subDivs[no].className.indexOf("sudokuSquare") >= 0 &&
-      !subDivs[no].style.backgroundColor) {
-   trace.push(8);
-   branchDistance.push({ 
-    label: 7, 
-    distance: Math.min(
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + _K_, 
-     absZero(subDivs[no].style.backgroundColor))
-   });
-   trace.push(9);
-   var spans = subDivs[no].getElementsByTagName("SPAN");
-   trace.push(10);
-   if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(11);
-    branchDistance.push({
-     label: 10,
-     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-    });
-    trace.push(12);
-    allOk = false;
-    break;
-   } else {
-     trace.push(14);
-     branchDistance.push({label: 10,distance: _K_});
-   }
-  } else {
-   trace.push(15);
-   branchDistance.push({
-    label: 7,
-    distance: 
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + 
-     absNegZero(subDivs[no].style.backgroundColor)
-   });
-  }
- }
- trace.push(5);
- trace.push(-1);
-}
-\end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
-  \label{code.isGameFinished.instr}
-\end{figure}
-
-\subsection{Genetic Phase}
-\label{sub.sec.genetic.phase}
-
-\begin{algorithm}[!t]
-  \caption{Genetic Phase}
-  \label{alg.gen}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{
-    $config$ is a GA configuration file\\
-    $b_n$ is a target branch of FUT\\
-    $(cfg, branches, cinfo, ifun, sig)$ output of Algorithm~\ref{alg.init}
-  }
-  \Output{
-     $(f^*, p^*)$ the best population candidate and its fitness score
-  }
-  \Fn{$Genetic(b_n, cfg, cinfo, config, ifun, sig)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M,size_{H}) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
-    $target \longleftarrow b_n$\label{alg.gen.init.target}\; 
-    $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
-    $historyConverged \longleftarrow true$\;
-    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
-      $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\; 
-      $history \longleftarrow \emptyset$\label{alg.gen.init.history}\; 
-      $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
-      \Repeat{$isPerfect(f^*) \vee historyConverged \vee (i > size_G)$}{\label{alg.gen.loop.begin}
-        $scoredPop \longleftarrow \emptyset$\;
-        $history \longleftarrow history \cup archive$\;
-        \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
-          $args \longleftarrow CoerceArguments(p, sig)$\label{alg.gen.make.args}\;
-          $(tr, d_B, d_L, dyncinfo) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
-          $f \longleftarrow Score(target, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
-          $cinfo \longleftarrow cinfo \cup dyncinfo$\label{alg.gen.eval.end}\;
-          $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        }
-        $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
-        $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
-        $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
-        $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
-        $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
-        $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
-        $i \longleftarrow i + 1$\;
-        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
-      }\label{alg.gen.loop.end}
-      $target \longleftarrow NewTarget(branches, b_n)$\label{alg.gen.new.target}\;
-    }\label{alg.gen.converged.loop.end}
-    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
-  }
-\end{algorithm}
-
-The heart of our test data generation framework is in the \emph{Genetic Phase}.
-Although, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, it has been extended with the concept of  \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we take a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
-The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
-
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ equal to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged, or the generations limit has not been reached.
-The \emph{archive} variable stores the most fit population candidates observed so far, and the \emph{history} variable records all archives during the generation process.
-These variables both are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
-
-The initial population has $size_P$ elements, and it is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found, or the history has converged, or the generation limit $size_G$ has been reached.
-But first, we need to score the current population (lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}).
-Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
-Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
-Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
-This gives us a 4-tuple consisting of an execution trace ($tr$), branch ($d_B$), loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
-The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
-Collected dynamic constants \emph{dyncinfo} are merged with the existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) in $combo$.
-And it is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
-If $f^*$ is a \emph{perfect} candidate, the solution is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
-
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{mcminn2004search}.
-For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it accidentally.
-In such a situation, we find ourselves being trapped on a flat space, with a small chance to escape.
-In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
-At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
-If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
-It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
-Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
-In practice, we only consider extensions upto length two.
-
-The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
-In the rest of this section, we provide implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and the fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our main focus here is on the generation and transformation of HTML documents.
-
-\begin{table}
-  \caption{Genetic Operation for the JS Types}
-  \label{tbl.gen.oper.js.types}
-    \footnotesize
-  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
-    \toprule
-    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
-    \hline
-    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
-    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
-    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
-    Random    & Array  & array of a respective type upto length five\\
-    \hline
-    Crossover & Bool   & pick at random one out of two given booleans \\
-    Crossover & Int    & pick at random one out of two given integers\\
-    Crossover & Float  & pick at random one out of two given floats\\
-    Crossover & String & pick at random one out of two single point crossovers\\
-    Crossover & Array  & similar crossover operator as for strings\\
-    \hline
-    Mutation  & Bool   & flip the boolean constant\\
-    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
-    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
-    Mutation  & String & random string, remove char or apply pred(suc) char\\
-    Mutation  & Array  & Mutate a random element in array according to its type\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsubsection{Random HTML Generation}
-\label{sub.sub.sec.random.html}
-
-\begin{figure}[t]
-  \begin{haskell}
-instance Arbitrary Html where
-  arbitrary = evalStateT generateHTML defaultState
-
-generateHTML :: GenHtmlState |c \label{ref.generateHTML.begin} |c
-generateHTML = do
-  state <- get |c \label{ref.generateHTML.getState} |c   
-  let d = getDepth state |c \label{ref.generateHTML.getDepth} |c
-  if d == 0
-  then lift \dollar return \dollar toHtml "HTML" |c \label{ref.generateHTML.returnString} |c
-  else do put state{depth = d - 1} |c \label{ref.generateHTML.updateState} |c
-           head <- generateHEAD |c \label{ref.generateHTML.newHead} |c
-           body <- generateBODY |c \label{ref.generateHTML.newBody} |c
-           lift\dollar return \dollar docTypeHtml \dollar head >> body |c \label{ref.generateHTML.end} |c
-
-data Tag = HTML | HEAD | BODY | ...
-type Context = CFlow | CMetadata | ...
-data HtmlState = |c \label{ref.HtmlState.begin} |c
-  HtmlState { depth    :: Int,           degree  :: Int    
-             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
-             , tags    :: [Tag],         ids     :: [String]
-             , classes :: [String] } |c \label{ref.HtmlState.end} |c
-type GenState s = StateT s Gen |c \label{ref.GenState} |c
-type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
-  \end{haskell}
-  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
-  \label{fig.html.arb.def}
-\end{figure}
-
-We want to generate HTML according to the WHATWG\footnote{\url{https://html.spec.whatwg.org}} specification.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-The recent HTML5 standard defines more than a hundred of tags and attributes which both have to comply with extremely complex logic to constitute  syntactically valid HTML.
-Browsers are usually tolerant to syntactic errors in HTML.
-They will silently fix them and display the page anyway.
-
-In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because the complexity of HTML and the lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} shows that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) represents the internal state of \texttt{Html}.
-The state is composed of the following components:
-\begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of the generated HTML 
-\item \texttt{ctx} is the current value of the HTML content model stack 
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
-\end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag is the value of the \texttt{GenHtmlState} type.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
-First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
-Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
-
-\subsubsection{Genetic HTML Operations}
-\label{sub.sub.sec.genetic.oper}
-
-In essence, an HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for \emph{expression trees} in genetic programming.
-
-\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
-
-\textbf{HTML Mutations} belong to one of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
-The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
-The \emph{DropTree} mutation removes the whole sub-tree at a randomly chosen node.
-\emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
-Currently, we instantiated the \emph{ShuffleAttributes} mutation only for the types \emph{class} and \emph{id}.
-In total, this gives us four mutations to choose from in order to evolve an HTML document.
-
-\subsubsection{Fitness Function}
-\label{sub.sub.sec.fitness.fun}
-
-The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating valid input data.
-The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
-without premature exception.
-Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-The FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
-\[
-\textit{fit}(n) = \text{approach level} +
-\begin{cases}
- 1/2 * (\frac{\text{branch distance}}{1 + \text{branch distance}}) & \text{if no exception}\\
- 1                                  &  \text{otherwise}
-\end{cases}
-\]
-The final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
-\[
-\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
-\]
-Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
- \[
-\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
-\]
-
-The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
-the node causing the deviation.
-Since any node can potentially be exceptional, they all contribute to the approach level, in addition to the conditional branches.
-Loops have to be treated in a special way because we need to estimate the maximum number of iterations.
-In the case of a for-loop, at run-time we can always provide an exact bound.
-For while-loops, we assume that it has to be passed at least once.
-The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
-
-\subsubsection{Limitations}
-\label{sub.sub.sec.limit}
-
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
-%% --------------------------------------------------------------------
-\section{Empirical Evaluation}
-\label{sec.evaluation}
-%% --------------------------------------------------------------------
-
-In order to evaluate the feasibility of our test framework, we conducted an empirical evaluation on a set of case-studies (see Section~\ref{sub.sec.case.studies}).
-All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which plays the role of our baseline, is \emph{Random} ($\Random$).
-Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is important to note  that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic Algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On the one hand, the smaller window size forces the GA to converge faster and quickly discovers stagnation on a flat space.
-On the other hand, the small window can lead to premature archive convergence, which prevents the right genetic combination from being triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose to report only that case in the paper.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{fraser2011evosuite}.
-
-\begin{table}
-  \caption{Genetic Algorithm Configurations}
-  \label{tbl.gen.config}
-    \scriptsize
-  \begin{tabular}{l|r|r|r}
-    \toprule
-    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
-    \hline
-    Population size                   & 50  & 50  & 50  \\
-    Archive size                      & 1   & 25  & 25  \\
-    Maximum number of generations     & 200 & 200 & 200 \\
-    Crossover rate                    & 0   & 0.5 & 0.5 \\
-    Mutation rate                     & 0   & 0.5 & 0.5 \\
-    History window size               & -   & -   & 10  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-By carrying the evaluation, we would like to answer the following research questions:
-\begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
-Which testing algorithm is the most effective?
-How does effectiveness change with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost per iteration?
-\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
-\item[\textbf{RQ4 (comparison):}] What is the branch coverage of \emph{Confix}?
-\end{description}
-
-\subsection{Case Studies}
-\label{sub.sec.case.studies}
-
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless numbers of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to native DOM manipulation.
-Before selection, the source code of a potential case-study has to be scrutinized which is a time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
-Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We added additional case-study \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} to increase the presence of primitive (browserless) JS code.
-For each case-study application, we identified several JS functions that are suitable for our testing framework.
-In the end, our evaluation set included both primitive and DOM related JS functions.
-
-For the sake of space, we chose to exclude from the following presentation the branches and functions the coverage time of which was less than two seconds.
-In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
-This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the case studies in ~Table~\ref{tbl.case.studies}.
-
-\setlength\tabcolsep{0.6pt}
-\begin{table}[t]
-  \caption{Summary of the Case-Studies}
-  \label{tbl.case.studies}
-  %\resizebox{\textwidth}{!}{
-    \scriptsize
-  \begin{tabular}{l|l|p{3.1cm}|c|c|c|c|c|c|c|c}
-    \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & (dom)           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & (dom)         & 8  & 0 & 2 & 1 & + & + & + & - \\
-    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & + & - & + & - \\
-    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
-    \hline
-    phormer    & toggleInfo & (dom,string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
-    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
-    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
-    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
-    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
-    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
-    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
-    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
-    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
-    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
-    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & (dom,[int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
-    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
-    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
-    \hline
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
-    %% \hline
-    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
-    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
-    \bottomrule
-  \end{tabular}
-%}
-\end{table}
-
-\subsection{Results}
-\label{sub.sec.eval.results}
-
-\setlength\tabcolsep{.98pt}
-\begin{table}[!t]
-  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
-  \label{tbl.stats}
-    \scriptsize
-    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
-      \toprule
-      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{2-10} % \!:\!
-                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \midrule
-    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \textbf{newGame}*   
-                             & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \textbf{revealAll}*  
-                             & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-    \textbf{shuffleBoard}*   
-                             & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \hline
-   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \hline
-   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \hline
-   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \hline
-   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-   \midrule
-    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
-    \bottomrule
-   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \hline
-    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \hline
-    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
-    \midrule
-    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
-    %% \midrule
-    %% \midrule
-    \bottomrule
-    \bottomrule  
-    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-To study the effectiveness and efficiency of our test generation framework ($\Random$, $\Genetic$ and $\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
-In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ one for each algorithm.
-The next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-To the right of the function name, we also present accumulated statistics for the function as a whole.
-Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function.
-
-According to the industry standard~\cite{bray1997c4}, functions with a CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
-We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with CC's of 13, 14 and 16 respectively.
-Table~\ref{tbl.stats.sum} summarizes the results of the experiment such as coverage, execution time per branch and significance.
-
-\begin{table}[!t]
-  \caption{Result Summary (L - large, M - medium, S - small)}
-  \label{tbl.stats.sum}
-    \footnotesize
-    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
-      \toprule
-      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
-      \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{8-16}
-                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
-      \midrule
-      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
-      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
-      \midrule
-      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
-Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The underlined values in Table~\ref{tbl.stats} like $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
-The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
-branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of the genetic approach, $\Genetic$ may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
-We encountered three such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines the strengths of both $\Random$ and $\Genetic$.
-It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only managed to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
-branch $(69,71)$ of the \emph{initBricks} function.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
-  }
-}
-
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig.budget.progress}
-\end{figure}
-
-Additionally, we have investigated how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time dependent.
-E.g.
-running tests inside an IDE should be fast; as part of the CI cycle we may afford a larger waiting time; regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ overtakes $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
-  }
-}
-
-\paragraph{\textbf{RQ2 (efficiency).}}
- To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
-Based on this information, we suggest an estimate on the execution time of the testing framework.
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum of 40\%~(\emph{newGame}) and a maximum of 510\%~(\emph{isValidCard}).
-
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=950,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        restrict y to domain*=0:1350, % Cut values off at 14
-        visualization depends on=rawy\as\rawy, % Save the unclipped values
-        after end axis/.code={ % Draw line indicating break
-          \draw [ultra thick, white, decoration={snake, amplitude=1pt}, decorate] (rel axis cs:0,1.05) -- (rel axis cs:1,1.05);
-        },
-        nodes near coords={%
-          \pgfmathprintnumber{\rawy}% Print unclipped values
-        },
-        every node near coord/.append style={rotate=90,anchor=west,font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,270) (isGameFinished*,220) (newGame*,14) (revealAll*,50) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,514) (isValidVISA,95) (initShields*,5) (brickJiggler*,8) (doPaddlePower*,15)  (initBricks*,2379) (do\_draw,625) (prob\_gamma,710)};
-      \addplot[fill=red] coordinates {(helpMe*,47)  (isGameFinished*,30)  (newGame*,9)  (revealAll*,44) (shuffleBoard*,26) (toggleInfo*,7) (isValidCard,8)   (isValidVISA,3)  (initShields*,5) (brickJiggler*,4) (doPaddlePower*,140) (initBricks*,474) (do\_draw,1295) (prob\_gamma,84)};
-      \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Overall test generation time per function.}
-  \label{fig.gen.time.comp}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=4,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,1.24) (isGameFinished*,0.83) (newGame*,0.78) (revealAll*,0.83) (shuffleBoard*,1.93) (toggleInfo*,1) (isValidCard,0.51) (isValidVISA,0.47) (initShields*,0.83) (brickJiggler*,1.14) (doPaddlePower*,0.79)  (initBricks*,1.68) (do\_draw,2.33) (prob\_gamma,0.35)};
-      \addplot[fill=red] coordinates {(helpMe*,0.77)  (isGameFinished*,0.94)  (newGame*,0.81)  (revealAll*,1) (shuffleBoard*,1.73) (toggleInfo*,1) (isValidCard,0.38)   (isValidVISA,0.38)  (initShields*,0.83) (brickJiggler*,0.67) (doPaddlePower*,0.69) (initBricks*,0.8) (do\_draw,3.38) (prob\_gamma,0.52)};
-      \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Speed of test generation measured as $t/i$}
-    \label{fig.get.cost}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with  7 and 25 seconds per branch.
-For simple functions, $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
-In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch of 19, 39 and 88 seconds, respectively. 
-  }
-}
-
-Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
-This information is useful when configuring the maximal generation limit.
-The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures the speed of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost of the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus never rising exceptions, and at the same time, it consists of 40 LOC.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second on average for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse 1.4 seconds.
-  }
-}
-
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs relative to $\Genetic$.
-Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases generally across the board and 67\% on the difficult functions.  
-  }
-}
-
-\paragraph{\textbf{RQ4 (comparison).}} Authors of \emph{Confix}~\cite{amin:ase15} have proposed three test generation strategies: 
-\begin{enumerate*}[label=(\roman*)]
-  \item only use \emph{Confix},
-  \item combine with \emph{Jalangi}~\cite{sen2013jalangi}, and
-  \item combine with manual input. 
-\end{enumerate*}
-They reported a relative increase of 2\% and 19\% in branch coverage of the second and third strategies, respectively, over the first one. Even though,
-
-The mix with manual showed 19\% increase  the best result, it is not objectively suitable for the comparison with the fully automated technique, like \emph{JEDI}.
-Unfortunately, the open source version of the \emph{Confix} we found~\footnote{\url{confix}} online does not provide actual integration with \emph{Jalangi}.
-Neither, the paper~\cite{amin:ase15} highlights any technical details of the integration.
-Also it only gave 2\% of improvement relative to
-
-\paragraph{\textbf{Threats to Validity}}
-The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Although, the branch coverage is a common criterion used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
-Reaching a target branch is only part of the problem: we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles leading to exceptions.
-Using a stronger oracle for validation is future work.
-Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent on unnecessary data explosion.
-Additional measures that could be applied is a minimization procedure, aka \emph{delta debugging}~\cite{misherghi2006hdd}, to the GA result.
-
-Initial GA configuration introduces a threat to the \emph{internal validity} of our empirical evaluation.
-The parameters we used are quite standard for similar SBST frameworks, e.g.
-EvoSuite.
-Although, not reported in the paper, we did perform a preliminary assessment of various GA configurations, which confirmed our final decision.
-
-The threat of \emph{conclusion validity} can be affected by the stochastic nature.
-This risk was addressed by repeating the experiment of GA 50 times and performing a statistical analysis of the significance and effect size.
-We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
-
-The \emph{external validity} deals with the threat of generalization of our results due to the manual selection of the experimental subjects.
-To mitigate this fact, we selected the subjects either from previous  related research or found in open source.
-Of course, those subjects still have to meet the constraints of our testing approach.
-So, further research is required in both increasing the power of our framework and extending the validation set.
-
-%% --------------------------------------------------------------------
-\section{Related and Future Work}
-\label{sec:related.work}
-%% --------------------------------------------------------------------
-
-The last two decades have been fruitful in the amount of work dedicates to the analysis of web applications and JavaScript, in particular.
-The state-of-the-art in this field including static and dynamic analysis of JS, as well as the test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around the two main questions:
-\begin{enumerate*}
-\item test data generation for JS functions interacting with the DOM, and
-\item the application of search-based techniques for that problem.
-\end{enumerate*}
-
-\subsection{Test Data Generation for JavaScript}
-
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect info about constant and feeds this data to the random generation.
-In comparison, our approach is the genetic generation.
-Additionally, we not only rely on the static information but also perform dynamic analysis to collect the run-time data.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} propose to use feedback-directed random testing for generation of TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing \emph{concolic testing} or {type inconsistency} analysis~\cite{pradel2015typedevil}.
-It suffers from common for the symbolic analysis problems such reasoning about arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtain DOM fixtures for the FUT.
-Combined with Jalangi, it can be used both for the generation of primitive data and DOM.
-As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
-Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS functions without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as a solid alternative for program testing.
-In fact, both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information for identifying potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011}, they extended the analysis with the abstractions able reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discovers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-
-\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the help the JS \emph{Proxies} in order to collect type related information.
-
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-
-%% \cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-%% \cite{ma2015grt} guided random testing
-
-%% \cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-%% \cite{jquery2014}
-
-%% ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-%% Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-%% Information-flow security for JS~\cite{hedin2012information}.
-
-%% Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-%% Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-%% Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-%% Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-%% DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Search-Based Test Data Generation}
-\label{sub.sec.search.based}
-
-Despite of the practical popularity of JavaScript, we have only encountered one work by Alshraideh~\cite{alshraideh2008complete} attempting to apply SBST to JavaScript.
-It uses GA for test generation with the goal cover all branches or kill all mutants, but it only deals with the limited input types such as booleans, integers and strings; and the provided validation is only based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports \emph{array} and \emph{DOM}, and conducts reasonable empirical validation with the discussion of significance and effect size.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-In this paper we deal with the generation and evolution of DOM which is an example of \emph{tree-like} data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim of improving test coverage of the XML-aware Java programs.
-To generate a random document, it may either rely on the  existing XML schema, or generate the document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, with extensive validation requirements.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for the mutation and crossover.
-Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
-
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of the SBST research~\cite{mcminn2011search}.
-Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a particular branch, we would like to have the set of tests maximizing the program coverage.
-That is, our solution is a vector of candidates which has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
-coverage vs.
-test-suite length.
-Another direction of future work is re-targeting out tool towards mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.
-
-% -----------------------
-Our test generation strategy is \emph{goal-oriented}~\cite{korel1992dynamic}, i.e.
-it tries to find an execution leading to a goal (statement) regardless of a concrete path taken.
-We uses control flow graph to identify implicit dependencies between nodes.
-
-The \emph{chaining approach}~\cite{ferguson1996chaining} uses data dependency to form the sequences of statements preceding the execution of a search target. 
-% -----------------------
-
-\section{Conclusions}
-\label{sec:concl}
-
-In this paper we have introduced a novel JS unit testing framework, called \emph{JEDI}, which uses search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{icse2018.bib}
-
-\end{document}

### 2018-05-11 doc/issre2018/issre2018.tex
Near final version of the issre 2018 paper

--- 2018-01-30 doc/icse2018/icse2018.tex
@@
-\documentclass[sigconf,review,anonymous]{acmart}
-
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+%\usepackage{cite}
+\usepackage[noadjust]{cite}
+\renewcommand{\citepunct}{,\penalty\citepunctpenalty\,}
+\renewcommand{\citedash}{--}% optionally
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
 \usepackage[inline]{enumitem}
@@
 \usepackage{longtable}
-\usepackage{subcaption}
+% \usepackage{subcaption}
+% \usepackage{subfig}
 \usepackage{pgfplots}
@@
 }
+
+\ifCLASSOPTIONcompsoc 
+\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+\else
+\usepackage[caption=false,font=footnotesize]{subfig}
+\fi
 
@@
 \newcommand{\RGenetic}{\mathbb{G}_{10}}
+\newcommand{\Confix}{\emph{Confix}\xspace}
+\newcommand{\Jalangi}{\emph{Jalangi}\xspace}
+\newcommand{\Jedi}{\emph{JEDI}\xspace}
 
-% Copyright
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\begin{document}
 
-% DOI
-%\acmDOI{10.475/123_4}
+\title{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM
+\thanks{Identify applicable funding agency here. If none, delete this.}
+}
 
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-%% \acmYear{1997}                  
-%% \copyrightyear{2016}
-
-%% \acmPrice{15.00}
-
-\begin{document}
-\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
-
-\author{Alexander Elyasov}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands} 
+\author{
+\IEEEauthorblockN{Alexander Elyasov}
+\IEEEauthorblockA{\textit{Utrecht University} \\
+Utrecht, The Netherlands \\
+a.elyasov@uu.nl}
+\and
+\IEEEauthorblockN{Wishnu Prasetya}
+\IEEEauthorblockA{\textit{Utrecht University} \\
+Utrecht, The Netherlands \\
+s.w.b.prasetya@uu.nl}
+\and
+\IEEEauthorblockN{Jurriaan Hage}
+\IEEEauthorblockA{\textit{Utrecht University} \\
+Utrecht, The Netherlands \\
+j.hage@uu.nl}
 }
-\email{a.elyasov@uu.nl}
-
-\author{Wishnu Prasetya}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{s.w.b.prasetya@uu.nl}
-
-\author{Jurriaan Hage}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-  \country{The Netherlands} 
-}
-\email{j.hage@uu.nl}
-
-\begin{abstract}
-As of 2017 JavaScript and Node.js continue to stay the most prevalent technologies according to the Stack Overflow developers survey.
-Nevertheless, existing JS testing frameworks are still lacking any support for such a vital step in test automation as the generation of input data.
-To address this problem, we present a novel \textbf{J}avascript \textbf{E}volutionary-based testing framework with \textbf{D}OM as an \textbf{I}input, called \textbf{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state.
-We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
- It has shown that the \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage on all experimental subjects with the average 19 seconds of execution time per branch.
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Software and its engineering~Software testing and debugging}
-\ccsdesc[300]{Software and its engineering~Search-based software engineering}
-
-\keywords{JavaScript, search-based testing, branch coverage}
 
@@
 
-\section{Introduction}
-\label{sec.intro}
+\begin{abstract}
+The popularity of JavaScript is continuously growing.
+Together with HTML and CSS, it forms the core technology stack for web development.
+Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable.
+Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS applications interacting with the DOM has not yet been addressed.
+In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
+In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including the global DOM state.
+We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
+It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
+\end{abstract}
 
-According to a Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the fifth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
-It is used through all technology stack web, back-ends and mobile.
-Such a tremendous ever increasing JS success is happening thanks to the extensive dynamic features of the language, JS permissiveness and native browser support.
-On the other hand, JS applications are error-prone~\cite{why}, hard to analyze~\cite{why} and test~\cite{why}.
-Therefore, it is not surprising that year after year we hear new stories\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}} about another critical bug being found in a web application by Facebook, Twitter etc.
+\begin{IEEEkeywords}
+JavaScript, search-based testing, branch coverage
+\end{IEEEkeywords}
 
-%% Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.
+\input{introduction}
+\input{example}
+\input{framework}
+\input{evaluation}
+\input{related-work}
+\input{conclusions}
 
-%% Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.
-
-The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
-These frameworks support testing at various levels: unit, integration and functional.
-The survey also indicated relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
-As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite of this effort, test data generation continues to be not properly addressed by any of the widely used testing frameworks.
-The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of JS faults are DOM-related and occur in JS code, and not in HTML or CSS.
-This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
-Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{mao2016sapienz}.
-In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript.
-Our work makes the following contributions:
-\begin{enumerate}[leftmargin=5mm]
-\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-\item We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency...
-\end{enumerate}
-
-The paper is structured as follows: In Section~\ref{sec.example}, we present a motivating example illustrating the challenges of generating test data for JS.
-The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} present empirical validation, whereas Section~\ref{sec.disc} discusses future work and validity threats.
-We discuss related work in Section~\ref{sec:related.work} and conclude the paper in Section~\ref{sec:concl}.
-
-Another empirical work~\cite{richards2010analysis}.
-
-%% --------------------------------------------------------------------
-\section{Motivating Example}
-\label{sec.example}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
-function isGameFinished() {
-  var obj = document.getElementById('sudoku'); |c \label{isGameFinished.getSudoku} |c
-  var subDivs = obj.getElementsByTagName('DIV'); |c \label{isGameFinished.getDivs} |c
-  var allOk = true;
-  for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
-    if (subDivs[no].className.indexOf('sudokuSquare') >= 0 |c \label{isGameFinished.if1.begin} |c 
-        && !subDivs[no].style.backgroundColor) { 
-      var spans = subDivs[no].getElementsByTagName('SPAN');
-      if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
-        allOk = false; |c \label{isGameFinished.unfinished} |c
-        break; 
-      }
-    }
-  } |c \label{isGameFinished.outFor} |c
-}
-\end{lstlisting}
-  \caption{JS function \texttt{isGameFinished.js} from sudoku}
-  \label{code.isGameFinished}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-                                 <div></div>                           
-  </div>                        </div> 
- </body>                       </body>    
-</html>                       </html>
-
-<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-   <div class='sudokuSquare'>    <div class='sudokuSquare'>
-    <span></span>                 <span></span> 
-    <span></span>                 <span>TEST</span>
-   </div>                        </div> 
-  </div>                        </div>
- </body>                       </body>
-</html>                       </html>
-  \end{lstlisting}
-  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
-  \label{fig.isGameFinished.tests}
-\end{figure}
-
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from a web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
-This function checks the validity of a sudoku solution given by a user.
-First, we find a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, we collect all its child DIVs (line~\ref{isGameFinished.getDivs}).
-Each DIV element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) and consists of two SPANs.
-First span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
-Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal SPAN values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
-
-Suppose now that we would like to unit test this function in isolation to the rest of the application.
-We aim to maximize the branch coverage as a common testing criteria~\cite{why.this.common}.
-That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
-We assume that DOM is the only global variable that can be referenced in the body of the FUT.
-So in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
-
-%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
-
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together deliver the full coverage of the FUT.
-Let us look now at how following the structure of the FUT in Figure~\ref{code.isGameFinished}, we can construct the $T4$ test covering the $(10,11)$ branch.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{DIV} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this $div$ to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the $div$ consists of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
-The resulted test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
-
-As we have just seen, even for such a relatively simple example, the construction procedure of a test input is far from trivial because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with the gazillion of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and, at the same time, it is easiest to implement.
-It greatly saves the developers from unexpected regression and puts a safety belt around the application.
-
-%% --------------------------------------------------------------------
-\section{Test Generation Framework}
-\label{sec.framework}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t!]
-  \centering 
-  \begin{sequencediagram}[font=\scriptsize]
-
-    \renewcommand\unitfactor{0.35}
-    \newinst{user}{\textbf{User}}
-    \newinst{server}{\textbf{Server}}
-    \newinst[1]{validator}{\textbf{Validator}}
-    \newinst{client}{\textbf{Client}}
-
-    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
-      \end{call}
-
-      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
-      \end{call}
-
-      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
-      \end{call}
-
-      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
-          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
-          \end{call}
-          \prelevel
-        \end{sdblock}
-
-        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
-            \end{call}
-
-            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
-            \end{callself}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
-          \end{callself}
-          \prelevel
-        \end{sdblock}
-        \mess{server}{best fitness}{user}
-
-      \end{sdblock}
-    \end{call}
-  \end{sequencediagram}
-  \caption{The architecture of the test framework}
-  \label{fig.framework.architect} 
-\end{figure}
-
-Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses the genetic engine for test generation.
-The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-\Server is the key component of the whole framework.
-It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}.
-Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactic correctness and reports back the set of identified errors.
-\Server rejects the document if any errors were revealed and generates a new one until the generated document has no errors anymore.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate the native browser API calls.
-
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
-Let us give a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random data generation, genetic phase, logging etc.
-Experimentally, we have found an optimal set of input configurations that was used across all experimental objects in Section~\ref{sec.evaluation}.
-This data is processed by the \Server during the \emph{Initialization Phase}.
-As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{ifun}, and the signature (\emph{sig}).
-\Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
-Depends on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
-the limit on the number of generation attempts.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate $p$ according to the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
-The execution trace along with some supplementary information about the execution are sent back to the \Server, where the final \emph{fitness value} is computed.
-The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-If a new HTML document is produced somewhere in the genetic phase, it has to be first approved by the \Validator.
-At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are exercised, the algorithm reaches the end.
-In the follow up two sections, we elaborate on the details of each individual phase of our test generation framework.
-
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
-
-During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing.
-The main steps of this phase are illustrated by Algorithm~\ref{alg.init}.
-Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info.
-Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName},
-which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT.
-Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants.
-Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure.
-Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
-
-\subsubsection{Supported Types}
-\label{sub.sec.sup.types}
-
-\begin{figure}[t!]
-\setlength{\grammarparsep}{3pt}
-\small
-\begin{grammar}
-
-<JS Type Annotation> ::= /*t <Signature> */
-
-<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
-
-<DOM> ::= \texttt{dom}
-
-<Type Signature> ::= <Type> | <Type> : <Type Signature>
-
-<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
-
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
-
-<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
-\end{grammar}
-\caption{Grammar of supported JS type annotations}
-\label{fig.js.type.annot}
-\end{figure}
-One assumption made in the paper is the availability of type signatures for JS functions.
-We believe in the legitimacy of such a request due to the following observations.
-First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity.
-Second, there has been an active work on the JS type inference done both in academia~\cite{kristensen2017type} and industry, e.g.
-Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.
-
-The grammar of the JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures those which refer to the global DOM and the ``ordinary'' JS type signatures.
-The functions of the former signature expect some \texttt{dom} argument to be passed as the first implicit parameter for the function call.
-Whereas ordinary JS signature is a non-zero sequence of the JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
-
-\subsubsection{Instrumentation}
-\label{sub.sec.instrument}
-
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \emph{trace} in line~\ref{isGameFinished.instr.trace} is an array of labels corresponding to the sequence of executed program statements.
-All statements have to be traced because each one, in theory, can rise an exception.
-The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations for the consecutive for-loop.
-If no exact bound can be computed, we set it to one.
-The \texttt{branchDistance} map tracks the distances to the deviated branches according to the translation formulae~\cite{tracey1998automated}.
-
-%TODO: maybe expand this section with the JS type casting for branch distance computation
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function isGameFinished() {
- trace.push(2); |c \label{isGameFinished.instr.trace} |c
- var obj = document.getElementById("sudoku");
- trace.push(3);
- var subDivs = obj.getElementsByTagName("DIV");
- trace.push(4);
- var allOk = true;
- loopMap[5] = function () { |c \label{isGameFinished.instr.loopMap} |c
-   var no = 0;
-   if (subDivs.length || subDivs.length == 0) {
-     return Math.abs(no - subDivs.length);
-   }
-   return 1;
- }();
- trace.push(5);
- for (var no = 0; no < subDivs.length; no++) {
-  trace.push(6);
-  trace.push(7);
-  if (subDivs[no].className.indexOf("sudokuSquare") >= 0 &&
-      !subDivs[no].style.backgroundColor) {
-   trace.push(8);
-   branchDistance.push({ 
-    label: 7, 
-    distance: Math.min(
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + _K_, 
-     absZero(subDivs[no].style.backgroundColor))
-   });
-   trace.push(9);
-   var spans = subDivs[no].getElementsByTagName("SPAN");
-   trace.push(10);
-   if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(11);
-    branchDistance.push({
-     label: 10,
-     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-    });
-    trace.push(12);
-    allOk = false;
-    break;
-   } else {
-     trace.push(14);
-     branchDistance.push({label: 10,distance: _K_});
-   }
-  } else {
-   trace.push(15);
-   branchDistance.push({
-    label: 7,
-    distance: 
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + 
-     absNegZero(subDivs[no].style.backgroundColor)
-   });
-  }
- }
- trace.push(5);
- trace.push(-1);
-}
-\end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
-  \label{code.isGameFinished.instr}
-\end{figure}
-
-\subsection{Genetic Phase}
-\label{sub.sec.genetic.phase}
-
-\begin{algorithm}[!t]
-  \caption{Genetic Phase}
-  \label{alg.gen}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{
-    $config$ is a GA configuration file\\
-    $b_n$ is a target branch of FUT\\
-    $(cfg, branches, cinfo, ifun, sig)$ output of Algorithm~\ref{alg.init}
-  }
-  \Output{
-     $(f^*, p^*)$ the best population candidate and its fitness score
-  }
-  \Fn{$Genetic(b_n, cfg, cinfo, config, ifun, sig)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M,size_{H}) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
-    $target \longleftarrow b_n$\label{alg.gen.init.target}\; 
-    $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
-    $historyConverged \longleftarrow true$\;
-    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
-      $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\; 
-      $history \longleftarrow \emptyset$\label{alg.gen.init.history}\; 
-      $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
-      \Repeat{$isPerfect(f^*) \vee historyConverged \vee (i > size_G)$}{\label{alg.gen.loop.begin}
-        $scoredPop \longleftarrow \emptyset$\;
-        $history \longleftarrow history \cup archive$\;
-        \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
-          $args \longleftarrow CoerceArguments(p, sig)$\label{alg.gen.make.args}\;
-          $(tr, d_B, d_L, dyncinfo) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
-          $f \longleftarrow Score(target, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
-          $cinfo \longleftarrow cinfo \cup dyncinfo$\label{alg.gen.eval.end}\;
-          $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        }
-        $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
-        $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
-        $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
-        $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
-        $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
-        $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
-        $i \longleftarrow i + 1$\;
-        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
-      }\label{alg.gen.loop.end}
-      $target \longleftarrow NewTarget(branches, b_n)$\label{alg.gen.new.target}\;
-    }\label{alg.gen.converged.loop.end}
-    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
-  }
-\end{algorithm}
-
-The heart of our test data generation framework is in the \emph{Genetic Phase}.
-Though, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, but has been extended with the concept of the \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we take a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
-The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
-
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ equal to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged or the generations limit has not been reached.
-The \emph{archive} variable stores the most fitted population candidates observed so far, and the \emph{history} variables records all archives during the generation process.
-These variables both are empty in the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
-
-The initial population has $size_P$ elements, and it is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found or the history has converged or the generation limit $size_G$ has been reached.
-But first, we need to score the current population lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
-Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
-Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
-Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
-This gives us 4-tuple consisting of an execution trace ($tr$), branch ($d_B$) and loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
-The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
-Collected dynamic constants \emph{dyncinfo} are merged with the existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}).
-And the $combo$ is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
-The fitness value of that element defines if a perfect candidate is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
-
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{ga.flag.problem.or.survey}.
-For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it occasionally.
-In such situation, we find ourselves being trapped on a flat space, with a small unreliable chance to escape.
-In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
-At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
-If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
-It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
-Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
-In practice, we only consider the target extensions upto the length of two.
-
-The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
-In the rest of this section, we reveal the implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our main focus in those sections is on the generation and transformation of HTML documents.
-
-\begin{table}
-  \caption{Genetic Operation for the JS Types}
-  \label{tbl.gen.oper.js.types}
-    \footnotesize
-  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
-    \toprule
-    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
-    \hline
-    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
-    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
-    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
-    Random    & Array  & array of a respective type upto length five\\
-    \hline
-    Crossover & Bool   & pick at random one out of two given booleans \\
-    Crossover & Int    & pick at random one out of two given integers\\
-    Crossover & Float  & pick at random one out of two given floats\\
-    Crossover & String & pick at random one out of two single point crossovers\\
-    Crossover & Array  & similar crossover operator as for strings\\
-    \hline
-    Mutation  & Bool   & flip the boolean constant\\
-    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
-    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
-    Mutation  & String & random string, remove char or apply pred(suc) char\\
-    Mutation  & Array  & Mutate a random element in array according to its type\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsubsection{Random HTML Generation}
-\label{sub.sub.sec.random.html}
-
-\begin{figure}[t]
-  \begin{haskell}
-instance Arbitrary Html where
-  arbitrary = evalStateT generateHTML defaultState
-
-generateHTML :: GenHtmlState |c \label{ref.generateHTML.begin} |c
-generateHTML = do
-  state <- get |c \label{ref.generateHTML.getState} |c   
-  let d = getDepth state |c \label{ref.generateHTML.getDepth} |c
-  if d == 0
-  then lift \dollar return \dollar toHtml "HTML" |c \label{ref.generateHTML.returnString} |c
-  else do put state{depth = d - 1} |c \label{ref.generateHTML.updateState} |c
-           head <- generateHEAD |c \label{ref.generateHTML.newHead} |c
-           body <- generateBODY |c \label{ref.generateHTML.newBody} |c
-           lift\dollar return \dollar docTypeHtml \dollar head >> body |c \label{ref.generateHTML.end} |c
-
-data Tag = HTML | HEAD | BODY | ...
-type Context = CFlow | CMetadata | ...
-data HtmlState = |c \label{ref.HtmlState.begin} |c
-  HtmlState { depth    :: Int,           degree  :: Int    
-             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
-             , tags    :: [Tag],         ids     :: [String]
-             , classes :: [String] } |c \label{ref.HtmlState.end} |c
-type GenState s = StateT s Gen |c \label{ref.GenState} |c
-type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
-  \end{haskell}
-  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
-  \label{fig.html.arb.def}
-\end{figure}
-
-We want to generate HTML according to the WHATWG\footnote{\url{https://html.spec.whatwg.org}} specification.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-The recent HTML5 standard defines more than hundred of tags and attributes which both have to comply with extremely complex logic to constitute a syntactically valid HTML.
-Browsers are usually tolerant to syntactic errors in HTML.
-They will silently fix them and display the page anyway.
-
-In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because, as we have mentioned early, the complexity of HTML and the lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} highlights that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) describes the internal state of \texttt{Html} in the generation.
-The state is composed of the following components:
-\begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of HTML 
-\item \texttt{ctx} is the current value of the HTML content model stack 
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
-\end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag should be defined as the value of the \texttt{GenHtmlState} type.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
-First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
-Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the new contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
-
-\subsubsection{Genetic HTML Operations}
-\label{sub.sub.sec.genetic.oper}
-
-In essence, HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for the \emph{expression trees} in genetic programming.
-
-\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
-
-\textbf{HTML Mutations} are of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
-The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
-The \emph{DropTree} mutation removes the whole sub-tree at a randomly chosen node.
-\emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
-Currently, we instantiated the \emph{ShuffleAttributes} mutation for only for tho types \emph{class} and \emph{id}.
-In total, this gives us four mutations to chose from in order to evolve an Html document.
-
-\subsubsection{Fitness Function}
-\label{sub.sub.sec.fitness.fun}
-
-The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating a valid input data.
-The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
-without premature exception.
-Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
-\[
-\textit{fit}(n) = \text{approach level} +
-\begin{cases}
- 1/2 * (\frac{\text{branch distance}}{1 + \text{branch distance}}) & \text{if no exception}\\
- 1                                  &  \text{otherwise}
-\end{cases}
-\]
-Final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
-\[
-\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
-\]
-Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
- \[
-\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
-\]
-
-The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
-the node caused the deviation.
-Since any node can potentially be exceptional, they all contribute to the approach level in addition to the conditional branches.
-Loops have to treated in a special way because we need to estimate the maximum number of iterations.
-In the case of for-loop, at run-time we can always provide an exact bound.
-For while-loops, we assume that it has to be passed at least once.
-The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
-
-\subsubsection{Limitations}
-\label{sub.sub.sec.limit}
-
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
-%% --------------------------------------------------------------------
-\section{Empirical Evaluation}
-\label{sec.evaluation}
-%% --------------------------------------------------------------------
-
-In order to evaluate the feasibility of our test framework adoption in practice, we conducted an empirical evaluation on a set of case-studies described in Section~\ref{sub.sec.case.studies}.
-All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which play the role of our baseline, is \emph{Random} ($\Random$).
-Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is the \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On one hand, the smaller window size forces the GA to converge faster and early discovers the stagnation on a flat space.
-On the other hand, the small window can lead to a premature archive convergence, which prevents the right genetic combination from been triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose it to report in the paper.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{fraser2011evosuite}.
-
-\begin{table}
-  \caption{Genetic Algorithm Configurations}
-  \label{tbl.gen.config}
-    \scriptsize
-  \begin{tabular}{l|r|r|r}
-    \toprule
-    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
-    \hline
-    Population size                   & 50  & 50  & 50  \\
-    Archive size                      & 1   & 25  & 25  \\
-    Maximum number of generations     & 200 & 200 & 200 \\
-    Crossover rate                    & 0   & 0.5 & 0.5 \\
-    Mutation rate                     & 0   & 0.5 & 0.5 \\
-    History window size               & -   & -   & 10  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-By carrying the evaluation, we would like to address the following research questions:
-\begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
-Which testing algorithm is the most effective?
-How the effectiveness changes with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost of one iteration?
-\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
-\end{description}
-
-\subsection{Case Studies}
-\label{sub.sec.case.studies}
-
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless number of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation.
-Before selection, the source code of a potential case-study has to be scrutinized which is time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
-Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}} to increase the presence of primitive (browserless) JS code.
-For each case-study application, we identified several JS functions that are suitable for our testing framework.
-In the end, our evaluation set included both primitive and DOM related JS functions.
-
-For the sake of space, we chose to exclude from the follow up presentation the branches and functions which coverage time was less than two seconds.
-In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
-This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the aforementioned case studies with the results presented in Section~\ref{sub.sec.eval.results}.
-
-\setlength\tabcolsep{0.6pt}
-\begin{table}[t]
-  \caption{Summary of the Case-Studies}
-  \label{tbl.case.studies}
-  %\resizebox{\textwidth}{!}{
-    \scriptsize
-  \begin{tabular}{l|l|p{3.1cm}|c|c|c|c|c|c|c|c}
-    \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & (dom)           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & (dom)         & 8  & 0 & 2 & 1 & + & + & + & - \\
-    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & + & - & + & - \\
-    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
-    \hline
-    phormer    & toggleInfo & (dom,string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
-    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
-    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
-    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
-    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
-    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
-    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
-    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
-    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
-    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
-    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & (dom,[int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
-    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
-    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
-    \hline
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
-    %% \hline
-    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
-    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
-    \bottomrule
-  \end{tabular}
-%}
-\end{table}
-
-\subsection{Results}
-\label{sub.sec.eval.results}
-
-\setlength\tabcolsep{.98pt}
-\begin{table}[!t]
-  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
-  \label{tbl.stats}
-    \scriptsize
-    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
-      \toprule
-      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{2-10} % \!:\!
-                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \midrule
-    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \textbf{newGame}*   
-                             & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \textbf{revealAll}*  
-                             & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-    \textbf{shuffleBoard}*   
-                             & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \hline
-   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \hline
-   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \hline
-   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \hline
-   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-   \midrule
-    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
-    \bottomrule
-   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \hline
-    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \hline
-    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
-    \midrule
-    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
-    %% \midrule
-    %% \midrule
-    \bottomrule
-    \bottomrule  
-    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-To study the effectiveness and efficiency of our test generation framework, including three test algorithms Random~($\Random$), Genetic~($\Genetic$) and Genetic with Restart~($\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
-In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ according to the algorithm type $\Random$, $\Genetic$ and $\RGenetic$.
-Next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-Inline with the function name, we also present accumulated statistics for the function as a whole.
-Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function.
-
-According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
-We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with the respective the CC 13, 14 and 16.
-Table~\ref{tbl.stats.sum} summarizes the total results of the experiment such as coverage, execution time per branch and significance.
-
-\begin{table}[!t]
-  \caption{Result Summary (L - large, M - medium, S - small)}
-  \label{tbl.stats.sum}
-    \footnotesize
-    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
-      \toprule
-      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
-      \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{8-16}
-                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
-      \midrule
-      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
-      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
-      \midrule
-      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
-Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The values in Table~\ref{tbl.stats} highlighted as $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
-The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
-branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of genetic approach~($\Genetic$), it may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
-We encountered three of such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines strengths of both algorithms genetic and random.
-It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only manged to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
-branch $(69,71)$ of the \emph{initBricks} function.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
-  }
-}
-
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig.budget.progress}
-\end{figure}
-
-Additionally, we would like to investigate how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time depended.
-E.g.
-running tests inside IDE should be fast; as part of the CI cycle we may afford a large waiting time; regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ starts to transcend $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
-  }
-}
-
-\paragraph{\textbf{RQ2 (efficiency).}}
- To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
-Based on this information, we suggest an estimate on the execution time of the testing framework.
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
-
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=950,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        restrict y to domain*=0:1350, % Cut values off at 14
-        visualization depends on=rawy\as\rawy, % Save the unclipped values
-        after end axis/.code={ % Draw line indicating break
-          \draw [ultra thick, white, decoration={snake, amplitude=1pt}, decorate] (rel axis cs:0,1.05) -- (rel axis cs:1,1.05);
-        },
-        nodes near coords={%
-          \pgfmathprintnumber{\rawy}% Print unclipped values
-        },
-        every node near coord/.append style={rotate=90,anchor=west,font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,270) (isGameFinished*,220) (newGame*,14) (revealAll*,50) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,514) (isValidVISA,95) (initShields*,5) (brickJiggler*,8) (doPaddlePower*,15)  (initBricks*,2379) (do\_draw,625) (prob\_gamma,710)};
-      \addplot[fill=red] coordinates {(helpMe*,47)  (isGameFinished*,30)  (newGame*,9)  (revealAll*,44) (shuffleBoard*,26) (toggleInfo*,7) (isValidCard,8)   (isValidVISA,3)  (initShields*,5) (brickJiggler*,4) (doPaddlePower*,140) (initBricks*,474) (do\_draw,1295) (prob\_gamma,84)};
-      \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Overall test generation time per function.}
-  \label{fig.gen.time.comp}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=4,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,1.24) (isGameFinished*,0.83) (newGame*,0.78) (revealAll*,0.83) (shuffleBoard*,1.93) (toggleInfo*,1) (isValidCard,0.51) (isValidVISA,0.47) (initShields*,0.83) (brickJiggler*,1.14) (doPaddlePower*,0.79)  (initBricks*,1.68) (do\_draw,2.33) (prob\_gamma,0.35)};
-      \addplot[fill=red] coordinates {(helpMe*,0.77)  (isGameFinished*,0.94)  (newGame*,0.81)  (revealAll*,1) (shuffleBoard*,1.73) (toggleInfo*,1) (isValidCard,0.38)   (isValidVISA,0.38)  (initShields*,0.83) (brickJiggler*,0.67) (doPaddlePower*,0.69) (initBricks*,0.8) (do\_draw,3.38) (prob\_gamma,0.52)};
-      \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Speed of test generation measured as $t/i$}
-    \label{fig.get.cost}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with the 7 and 25 seconds per branch.
-For simple functions, the $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
-In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch 19, 39 and 88 seconds, respectively. 
-  }
-}
-
-Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
-This information is useful when configuring the maximal generation limit.
-The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures the speed of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus not rising exceptions, and at the same time, it consists of 40 LOC.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
-  }
-}
-
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs comparing to $\Genetic$.
-Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases globally and 67\% on the difficult functions.  
-  }
-}
-
-\paragraph{\textbf{Threats to Validity}}
-The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Though, the branch coverage is a common criteria used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
-Reaching a target branch is only part of the problem, we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles disseminating in exceptions.
-Using a stronger oracle for validation is future work.
-Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent unnecessary data explosion.
-Additional measure that could be taken is applying a minimization procedure, aka \emph{delta debugging}, to the GA result.
-
-Initial GA configuration introduces the threat to the \emph{internal validity} of our empirical evaluation.
-The parameters we used are quite standard for similar SBST frameworks, e.g.
-EvoSuite.
-Though, not reported in the paper, we performed preliminary assessment of various GA configurations, which confirmed our final decision.
-
-The threat of \emph{conclusion validity} can be affected by the GA stochastic nature.
-This risk was addressed by repeating the experiment 50 times and performing statistical analysis of the significance and effect size.
-We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
-
-The \emph{external validity} deals with the threat of generalization of our results due to manual selection of the experimental subjects.
-To mitigate this fact, we picked the subjects either from previously used in related research or found in open source.
-Of course, those subjects still have to met the constrains of our testing approach.
-So, further research is required in both increasing the power of our framework and extending the validation set.
-
-%% --------------------------------------------------------------------
-\section{Related and Future Work}
-\label{sec:related.work}
-%% --------------------------------------------------------------------
-
-The last two decades were fruitful in the amount of work dedicates to the analysis and web applications and JavaScript, in particular.
-The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around two main questions:
-\begin{enumerate*}
-\item test data generation for JS functions interacting with the DOM, and
-\item the application of search-based techniques for that problem.
-\end{enumerate*}
-
-\subsection{Test Data Generation for JavaScript}
-
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect constant info and feed it to the random generation.
-We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} proposes to use feedback-directed random testing for generating TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing concolic testing or type inconsistency analysis~\cite{pradel2015typedevil}.
-It suffers from typical for the symbolic analysis problems such as the handing of arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtains DOM fixtures for the FUT.
-Combined with Jalangi it can be used for both primitive and DOM test data generation.
-As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
-Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as solid alternative for program testing.
-In fact both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discoverers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-
-\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the JS \emph{Proxies} in order to collect type related information.
-
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-
-\cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-\cite{ma2015grt} guided random testing
-
-\cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-\cite{jquery2014}
-
-ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-Information-flow security for JS~\cite{hedin2012information}.
-
-Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Search-Based Test Data Generation}
-\label{sub.sec.search.based}
-
-Despite of the practical popularity of JavaScript, the only recorded in the literature attempt of adopting search-based testing for JS unit testing was done by Alshraideh~\cite{alshraideh2008complete}.
-It uses GA for branch and mutation coverage, but only deals with the limited input types booleans, integers and strings; and provides validation based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports array and DOM types, with suggest reasonable validation with the discussion of significance and effect size.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-In this paper we dealt with the generation and evolution of DOM which is an example of tree-like data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim to improve test coverage of the XML-aware Java programs.
-To generate random document, it may rely on existing XML schema, or generate document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, which is difficult to comply.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for mutation and crossover.
-Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
-
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of SBST research~\cite{mcminn2011search}.
-Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage.
-That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
-coverage vs.
-test-suite length.
-Another direction of future work is adjusting out tool for mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That would also help us to judge about the fault revealing ability of \emph{JEDI} based on the number of killed mutants.
-As we said early in this section, SBST techniques can benefit from symbolic analysis~\cite{baars2011symbolic}.
-
-\section{Conclusions}
-\label{sec:concl}
-This paper
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{icse2018.bib}
+\bibliographystyle{IEEEtran}
+\bibliography{issre2018}
 

### 2018-05-11 doc/issre2018/related-work.tex
Near final version of the issre 2018 paper

%% --------------------------------------------------------------------
\section{Related and Future Work}
\label{sec:related.work}
%% --------------------------------------------------------------------

The last two decades have been highly productive for the research in JS testing and analysis~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}. We discuss the state-of-the-art in JS testing clustering the works by the underlying technique: feedback-directed random generation~\cite{heidegger2010contract,heidegger2012jscontest,kristensen2017type}, symbolic~\cite{tanida2014automatic,saxena2010symbolic} and concolic~\cite{sen2013jalangi,amin:ase15} execution, static~\cite{tajs2009,dom2011} and dynamic~\cite{andreasen2017survey} analysis, formal verification~\cite{gardner2008local,lerner2012modeling,gardner2012towards}, search-based testing~\cite{alshraideh2008complete}, and the whole web application testing~\cite{alshahwan2011automated,mesbah2012invariant,milani2014leveraging}.

Guided by the developer's provided type annotation, \emph{JSContest}~\cite{heidegger2010contract} generates random input for a JS function with the goal to verify the conformance of \emph{type} or \emph{access permission}~\cite{heidegger2012jscontest} contracts. It constructs test inputs out statically collected constants. In comparison, our genetic-based approach can handle interactions with the DOM, and also leverages dynamic information. $TS_{TEST}$~\cite{kristensen2017type} is the feedback-directed random testing tool for checking the conformance of TypeScript declaration files with the respective JS libraries. It supports generics but still lacks DOM generation.

%% cite heidegger2010dom

\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be instantiated for \emph{concolic testing} or {type inconsistency} analysis~\cite{pradel2015typedevil} but it does not DOM. \emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in construct DOM fixtures. However, it could reinforce \Jalangi with the capability of DOM modeling. As our evaluation has shown, \Confix can not find solutions for programs with complex data dependency. SymJS~\cite{tanida2014automatic} employs symbolic execution for JS unit-test generation but again missing symbolic stubs for DOM API.

%% Another \cite{saxena2010symbolic} symbolic execution tool

Jensen et al.~\cite{tajs2009} proposed a static analysis framework \emph{TAJS} for JS type inference. Later they extend the analysis to support reasoning about HTML DOM and browser API~\cite{dom2011}. \emph{TAJS} is able to point to a dead code, type violation and references to \emph{undefined} values.

Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles. Gardener et al.~\cite{gardner2012towards} tries to esteblish formal versification framework for JS including part of the DOM specification~\cite{gardner2008local}.

Alshraideh~\cite{alshraideh2008complete} is the only attempt to employ GA for JS test data generation. But the work deals with the functions of primitive type, without DOM, and has no not been empirically validated. Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique. DOM is an instance of \emph{tree-like} data structure. \emph{XMLMATE}~\cite{havrikov2014xmlmate} is an XML test generation tool build on top \emph{EvoSuite} with the aim of improving test coverage of the XML-aware Java programs. To generate a random document, it either relies on the  existing XML schema, or generates the document from scratch. In some sense, DOM specification can be thought of a complex XML schema, with extensive validation requirements. One distinction of our approach is the use of program analysis for data generation. Both tools have similar philosophy for the mutation and crossover. Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.

In contrast with the early presented techniques, the whole web application testing requires the application to be fully functional. This enables test generation based on crawling~\cite{mesbah2012invariant} and can be combined with the developer's written tests~\cite{milani2014leveraging}. \emph{Artemis}~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application. It discovers new tests by generating sequences of executable events and monitoring they effect on the state of the application. Biagiola et al.~\cite{biagiola2017search} proposed to use \emph{page objects} to generate navigation path and input data with by exploiting search-based approach. \emph{JSEFT}~\cite{mirshokraie2015jseft} leverages dynamic execution to generate JS unit test including fixtures captured at run-time. The generated test can be compeented with DOM-dependent assertions produced by \emph{Atrina}~\cite{icst16}.

\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the help the JS \emph{Proxies} in order to collect type related information.

\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.

%% \cite{ma2015grt} guided random testing

%% \cite{mao2016sapienz} Multi-objective automated testing for Android application

%% \cite{jquery2014}

%% ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.

%% Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.

%% Information-flow security for JS~\cite{hedin2012information}.

%% Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}

%% Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.

%% Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.

%% Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.

%% DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.

%% Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of the SBST research~\cite{mcminn2011search}. Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.

%% % -----------------------
%% Our test generation strategy is \emph{goal-oriented}~\cite{korel1992dynamic}, i.e. it tries to find an execution leading to a goal (statement) regardless of a concrete path taken. We uses control flow graph to identify implicit dependencies between nodes.

%% The \emph{chaining approach}~\cite{ferguson1996chaining} uses data dependency to form the sequences of statements preceding the execution of a search target.
% -----------------------

\subsection{Future Work}
\label{subsec.fut.work}

One likely direction for the future extension of \emph{JEDI} is \emph{the whole test suite generation}~\cite{fraser2013whole}. Such problems usually incur multi-objective optimization~\cite{lakhotia2007multi,panichella2017lips}, e.g. trade-off between coverage and test-suite length.

Another direction of future work is re-targeting out tool towards mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}. That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.

Similar to \cite{baars2011symbolic, galeotti2013improving}, it could be worth to combine search-based generation with concolic (symbolic) execution, e.g. investigate the integration of \Jedi with \Jalangi.

We plan to validate \Jedi on a larger set of examples. Towards this goal, we have to extend our framework with the support of such input types as user-defined classes and high-order functions. The first extension is straightforward since any class can be described as the collection of the types of class fields. To generate functions as inputs we could employ approach similar to QuickCheck~\cite{koopman2006automatic}.

%% Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process:
%% \begin{enumerate}
%% \item ability to assign static types to input parameters
%% \item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
%% \item no support for recursion
%% \item doesn't perform inter-procedural analysis
%% \item no support for JS frameworks
%% \item no reference to global variables and functions
%% \item limited support of DOM API
%% \end{enumerate}

### 2018-05-14 doc/issre2018/evaluation.tex
Final edits of the paper

@@
 
-By carrying the evaluation, we would like to answer the following research questions:
+By carrying out the evaluation, we would like to answer the following research questions:
 \begin{description}
@@
 
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
+Being one of the most popular programming languages for web development, there are ample open source JS projects on the Web.
 JS applications are written with the help of countless numbers of specialized libraries, and greatly vary in size, complexity and coding style.
@@
 To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our framework on the case studies in Table~\ref{tbl.case.studies}.
-For the sake of space, we omitted from the following presentation the functions and branches with the coverage time less than two seconds.
+For the sake of space, we omitted from the following presentation the functions and branches with a coverage time of less than two seconds.
 In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
@@
 To study the effectiveness and efficiency of our test generation framework, we exercised each algorithm ($\Random$, $\Genetic$ and $\RGenetic$) against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
+Due to the probabilistic nature of the test generation process, the experiments have been repeated 50 times to achieve statistical significance.
 Table~\ref{tbl.stats} summarizes the evaluation results.
@@
 Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The underlined values in Table~\ref{tbl.stats} like $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
+The underlined values in Table~\ref{tbl.stats} like $\underline{200}$ indicate branches which were not covered by the respective algorithms.
 The main reason for the random generation~($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
@@
 It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only managed to outperform $\Random$ and cover the three problematic branches above, but it generally improved the results of $\Genetic$, e.g.
+As our evaluation has shown, $\RGenetic$ not only managed to outperform $\Random$ and cover the three problematic branches above, but it has generally improved the results of $\Genetic$, e.g.
 branch $(69,71)$ of the \emph{initBricks} function.\\
@@
 
-Additionally, we have investigated how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time dependent.
+Additionally, we have investigated how the coverage progresses with the change of time budget assigned per branch.
+This experiment models different time dependent testing scenarios, used in practice.
 E.g.
 running tests inside an IDE should be fast; as part of the continuous integration we may afford a longer waiting time; and regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across budget categories from 5 to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
+Figure~\ref{fig.budget.progress} illustrates the progress of the algorithms across budget categories from 5 to 150 seconds per branch.
+Random test generation consistently underperforms the genetic one across all budget categories by at least a factor of two.
 Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
+Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ perform equally at the rate of 45\%.
 When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ overtakes $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
+But when the budget rises to 30 seconds, $\RGenetic$ overtakes $\Genetic$ and the distance between them continues growing further with the budget increase (starting from 120 seconds).\\
 \framebox{
@@
 \textbf{RQ2 (efficiency):} To answer this question, we compare the actual execution time of our test generation algorithms.
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
+The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time differs for each algorithm at the function level.
 There are two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
@@
 Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with  7 and 25 seconds per branch.
-For simple functions, the $\Genetic$ performance was quite close to $\RGenetic$, only 9 seconds, but for difficult functions it was two times slower.
+For simple functions, the performance of $\Genetic$ was quite close to $\RGenetic$, only 9 seconds, but for difficult functions it was two times slower.
 In all categories, $\Random$ was much slower than both genetic alternatives.\\
@@
 Another question related to the efficiency is the computational cost of one iteration of each algorithm.
-It useful to know in order to choose the generation limit.
+It is useful to know in order to choose the generation limit.
 The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
@@
   \parbox[t][0.7cm]{0.95\linewidth}{
-    On average, one algorithm iteration took one second for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse 1.4 seconds.
+    On average, one algorithm iteration took one second for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse at 1.4 seconds.
   }
@@
 Thus, the higher the value in the $_{\Genetic}^{\Random}$ column, indicates that $\Random$ is slower comparison with $\Genetic$.
-Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
+Depending on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
 \framebox{
@@
 \end{enumerate*}
-Even though, the third strategy outperformed pure \Confix by 19\%, it is not suitable for an objective comparison with a fully automated technique, like \Jedi.
+Even though the third strategy outperformed pure \Confix by 19\%, it is not suitable for an objective comparison with a fully automated technique, like \Jedi.
 On the other hand, the combination with \Jalangi could be used for the evaluation, but it only improved branch coverage by 2\%, and the \Confix version available online~\cite{confixgit} has no actual integration with \Jalangi.
-Thus we had to fall back on the plain \Confix test generation, results are present in Figure~\ref{tbl.confix.compare}.
-\Jedi seeks for a normal program termination during test generation, which is a stronger coverage criterion in comparison with only reaching a target branch provided by \Confix.\\
+Thus we had to fall back on plain \Confix test generation; results are present in Figure~\ref{tbl.confix.compare}.
+In comparison with \Jedi, \Confix does not search for a test input in terms of a \emph{strong} coverage, i.e.
+it only tries to reach a target branch neglecting the normal termination.
+But even in terms of \emph{weak} coverage, it showed the complete coverage in 2 out 10 cases.\\
 \framebox{
   \parbox[t][0.65cm]{0.95\linewidth}{
-Although, \Confix performs much faster (under 10 seconds), it is unable to reach hard to cover branches.
+Although, \Confix performs much faster (under 10 seconds), it is unable to cover hard branches, which \Jedi can.
   }
@@
 To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent on unnecessary data explosion.
-Additional measures that could be applied is a minimization procedure, aka \emph{delta debugging}~\cite{misherghi2006hdd}, to the GA result.
+Additional measure that could be applied is a minimization procedure, aka \emph{hierarchical delta debugging}~\cite{misherghi2006hdd} and its variations~\cite{herfert2017automatically}, to the GA result.
 
@@
 Of course, those subjects still have to meet the constraints of our testing approach.
-So, further research is required in both increasing the power of our framework and extending the validation set.
+So, further research is required both to increase the power of our framework and extend the validation set.

### 2018-05-14 doc/issre2018/example.tex
Final edits of the paper

@@
       && !subDivs[no].style.backgroundColor) {
-      var spans = subDivs[no].getElementsByTagName('SPAN');
+   var spans=subDivs[no].getElementsByTagName('SPAN');
    if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
     allOk = false; //target |c \label{isGameFinished.unfinished} |c
-        break;}}}} |c \label{isGameFinished.outFor} |c
+    break;
+   }
+  }
+ } |c \label{isGameFinished.outFor} |c
+  return allOk;
+}
 \end{lstlisting}
@@
 Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}~\cite{sudoku}.
-This function validates a sudoku solution given by a user.
-First, it finds a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, it collects all the child \emph{divs} (line~\ref{isGameFinished.getDivs}).
-Each \emph{div} element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}), and consists of two \emph{spans}.
-The first \emph{span} contains a user input, whereas the second one (hidden by default) stores an expected value for that sudoku square.
-Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
+This function checks if a given sudoku solution is valid.
+First, it locates a DOM element \texttt{obj} representing the game field (line~\ref{isGameFinished.getSudoku}).
+Then, it collects all children \emph{DIV} elements of \texttt{obj} (line~\ref{isGameFinished.getDivs}).
+Each \emph{DIV} corresponds to an input square of the game (line~\ref{isGameFinished.if1.begin}) and consists of two \emph{SPAN} tags.
+The first \emph{SPAN} contains the value entered by the player, whereas the second one (hidden by default) stores the expected (correct) value for that square.
+In the for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate through the whole collection of the input squares.
+Once, we encounter a square with two unequal values (line~\ref{isGameFinished.if2.begin}), we terminate the loop and call the game unfinished (line~\ref{isGameFinished.unfinished}), otherwise finished.
 
-Suppose now that we would like to unit test this function in isolation to the rest of the application.
+Suppose now that we would like to unit test this function.
 We aim to maximize the branch coverage as a common testing criteria~\cite{zhu1997software}.
@@
 In general, in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
+The tests should be decoupled from the application's HTML.
+Moreover, such HTML could still be under active development.
+Thus, the developers have to complement test with DOM fixtures.
 
@@
 
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together provide the full coverage of the FUT.
-Let us take a look at how to construct the \texttt{T4} test, which covers the branch $(10,11)$, by following the structure of the FUT.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with an id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{div} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this \emph{div} to be of the class \textquotesingle\texttt{square}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the \emph{div} consists of two \emph{span} elements whose \emph{innerHtml} values are not equal.
+Figure~\ref{fig.isGameFinished.tests} exhibits four tests that together provide the full branch coverage of the FUT.
+Let us, for example, take a look at how we can reach the target branch $(10,11)$.
+Line~\ref{isGameFinished.getSudoku} expects the DOM to have an element with an id \textquotesingle\texttt{sudoku}\textquotesingle.
+In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, this element should have at least one child \emph{DIV} tag.
+The first if-condition in line~\ref{isGameFinished.if1.begin} requires each \emph{DIV} element to be of the class \textquotesingle\texttt{square}\textquotesingle\, and do not have a background color.
+The second if-condition (line~\ref{isGameFinished.if2.begin}) implies that the \emph{DIV} should consist of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
 The resulting test \texttt{T4} in Figure~\ref{fig.isGameFinished.tests} meets all the above conditions.
 
-As we have just observed, even for such a relatively simple example, the test data generation can be far from trivial procedure because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with a large number of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
+As we have just witnessed, even for such a relatively simple example, the test data generation can be far from trivial procedure because it requires the deep understanding of the program semantics.
+In practice, web developers often have to deal with third-party code, including a large number of JS libraries freely available on the GitHub, which are commonly untested and poorly documented.
 At the same time, unit testing is the most fundamental level of testing and the easiest to implement.
-It saves the developers from unexpected regressions and often documents the desired behavior of a program.
+It saves the code from unexpected regressions and often documents the desired behavior of a program.
+Thus, in industry unit testing has became a standard practice in web development.

### 2018-05-14 doc/issre2018/introduction.tex
Final edits of the paper

@@
 It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million).
-Such an ever increasing JS success can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}.
+The success of JS can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}.
 On the other hand, due to of implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}.
-Thus, it is not surprising that once in a while critical bugs manage to break through~\cite{bugstories2017} into the web applications by Facebook, Twitter etc.
+Thus, it is not surprising that once in a while critical bugs manage to break through~\cite{bugstories2017} even into the web applications of major companies such as Facebook, Twitter etc.
 
-Systematic unit testing is basic and, at the same time, the most effective technique for improving software quality.
-In practice, there are numerous of JS frameworks --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc.
---- intended to assist developers with the automation of various unit testing activities such as design, execution and monitoring.
+Systematic unit testing is a basic and, at the same time, the most effective technique for improving software quality~\cite{martin2009clean}.
+There exist numerous JS frameworks on the market --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc.
+--- intended to assist web developers with the automation of various  activities such as the design, execution and monitoring of unit tests.
 Despite the apparent abundance of the JS testing tools, the developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements.
-One of such areas is \emph{test data generation}.
-It pursues the goal of maximizing the test coverage by exercising the function under test (FUT) with different input parameters.
+One of the missing steps on the way to complete JS test automation is \emph{the generation of test data}.
+It pursues the goal of maximizing test coverage by exercising the function under test (FUT) with various input parameters.
 Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.
 
-Generally, the problem of test data generation has been under an active study for the past three decades.
+Generally, the problem of test data generation has been actively studied for the past three decades.
 In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the whole web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
-Out of those tools, only \emph{Confix} tries to construct a sufficient DOM fixture by translating native browser API calls into logical constraints.
-However, in the empirical evaluation~\cite{amin:ase15}, Confix only reached about 50\% in \emph{branch coverage} on the selected subjects.
-At the same time, search-based techniques have shown prominent results in achieving high branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications.
+Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints.
+However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reached about 50\% \emph{branch coverage} on the selected subjects.
+At the same time, search-based techniques have shown prominent results in successfully achieving higher branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications.
 But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of the search-based approach.
@@
 Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
-\item Our test generation algorithm, called ``genetic with restart'', is trying to escape search plateau by restarting GA with a new target.
-Because the full-fledged JS data flow analysis~\cite{jang2009points} is hard to reach, the new target is chosen purely based on the preceding control flow behaviour in contrast with more popular techniques~\cite{ferguson1996chaining}.
+\item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target.
+In contrast with the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly reachable.
 \item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results.
 The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
-Moreover, we showed that on the selected subjects \emph{JEDI} outperforms \emph{Confix} ....
+Moreover, we show that out of 10 functions where \emph{JEDI} achieved complete branch coverage, \emph{Confix} only covered 32\% on average.
 \end{enumerate}
@@
 The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} presents empirical validation and indicates the validity threats.
+Section~\ref{sec.evaluation} presents empirical validation and the validity threats.
 Related and future work are discussed in Section~\ref{sec:related.work}.

### 2018-05-14 doc/issre2018/related-work.tex
Final edits of the paper

@@
 The last two decades have been highly productive for the research in JS testing and analysis~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-We discuss the state-of-the-art in JS testing clustering the works by the underlying technique: feedback-directed random generation~\cite{heidegger2010contract,heidegger2012jscontest,kristensen2017type}, symbolic~\cite{tanida2014automatic,saxena2010symbolic} and concolic~\cite{sen2013jalangi,amin:ase15} execution, static~\cite{tajs2009,dom2011} and dynamic~\cite{andreasen2017survey} analysis, formal verification~\cite{gardner2008local,lerner2012modeling,gardner2012towards}, search-based testing~\cite{alshraideh2008complete}, and the whole web application testing~\cite{alshahwan2011automated,mesbah2012invariant,milani2014leveraging}.
+Discussing the state-of-the-art in JS testing we cluster the works, by the underlying technique, into the following categories: feedback-directed random generation~\cite{heidegger2010contract,heidegger2012jscontest,kristensen2017type}, symbolic~\cite{tanida2014automatic,saxena2010symbolic} and concolic~\cite{sen2013jalangi,amin:ase15} execution, static~\cite{tajs2009,dom2011} and dynamic~\cite{andreasen2017survey} analysis, formal verification~\cite{gardner2008local,lerner2012modeling,gardner2012towards}, search-based generation~\cite{alshraideh2008complete}, and whole web application testing~\cite{alshahwan2011automated,mesbah2012invariant,milani2014leveraging}.
 
-Guided by the developer's provided type annotation, \emph{JSContest}~\cite{heidegger2010contract} generates random input for a JS function with the goal to verify the conformance of \emph{type} or \emph{access permission}~\cite{heidegger2012jscontest} contracts.
-It constructs test inputs out statically collected constants.
-In comparison, our genetic-based approach can handle interactions with the DOM, and also leverages dynamic information.
-$TS_{TEST}$~\cite{kristensen2017type} is the feedback-directed random testing tool for checking the conformance of TypeScript declaration files with the respective JS libraries.
-It supports generics but still lacks DOM generation.
+Guided by developer's type annotations, \emph{JSContest} generates random inputs for JS functions with the goal to verify the conformance to the \emph{type}~\cite{heidegger2010contract} and \emph{access permission}~\cite{heidegger2012jscontest} contracts.
+In comparison with our genetic approach, it does not leverage dynamic information to construct test inputs, only static one, and ignores the DOM interactions.
+$TS_{TEST}$~\cite{kristensen2017type} employs the feedback-directed random generation for conformance checking of TypeScript declarations with the respective JS libraries.
+It supports generics, but cannot generate DOM.
 
@@
 
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be instantiated for \emph{concolic testing} or {type inconsistency} analysis~\cite{pradel2015typedevil} but it does not DOM.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in construct DOM fixtures.
-However, it could reinforce \Jalangi with the capability of DOM modeling.
-As our evaluation has shown, \Confix can not find solutions for programs with complex data dependency.
-SymJS~\cite{tanida2014automatic} employs symbolic execution for JS unit-test generation but again missing symbolic stubs for DOM API.
+\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be instantiated for \emph{concolic testing} and \emph{type inconsistency analysis}~\cite{pradel2015typedevil}, but it does not support DOM.
+\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constraint solver in order to construct a DOM fixture.
+It can reinforce \Jalangi with the capability of DOM modeling.
+However, as our evaluation has shown, \Confix cannot resolve hard to cover branches.
+\emph{SymJS}~\cite{tanida2014automatic} employs symbolic execution for JS unit-test generation but again has no symbolic stubs for the DOM API.
 
@@
 Jensen et al.~\cite{tajs2009} proposed a static analysis framework \emph{TAJS} for JS type inference.
-Later they extend the analysis to support reasoning about HTML DOM and browser API~\cite{dom2011}.
+Later the analysis was extended to support reasoning about the HTML DOM and browser API~\cite{dom2011}.
 \emph{TAJS} is able to point to a dead code, type violation and references to \emph{undefined} values.
+A review of dynamic analysis techniques ofr JS can be found in a recently published survey~\cite{andreasen2017survey} by Andreasen et al.
 
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-Gardener et al.~\cite{gardner2012towards} tries to esteblish formal versification framework for JS including part of the DOM specification~\cite{gardner2008local}.
+Lerner~\cite{lerner2012modeling} formally models the event behavior in the DOM to establish testing oracles.
+Gardener et al.~\cite{gardner2012towards} presents a formal verification framework for JS, which can deal with some parts the DOM specification~\cite{gardner2008local}.
 
-Alshraideh~\cite{alshraideh2008complete} is the only attempt to employ GA for JS test data generation.
-But the work deals with the functions of primitive type, without DOM, and has no not been empirically validated.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-DOM is an instance of \emph{tree-like} data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is an XML test generation tool build on top \emph{EvoSuite} with the aim of improving test coverage of the XML-aware Java programs.
-To generate a random document, it either relies on the  existing XML schema, or generates the document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, with extensive validation requirements.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for the mutation and crossover.
+Alshraideh~\cite{alshraideh2008complete} is the first work suggesting to use GA for JS test data generation.
+But the implementation is limited to primitive types such as numbers and strings, and does not report on empirical validation.
+Moreover, it does not support the generation of arrays and DOM.
+Recently, SBST has been applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
+\emph{XMLMATE}~\cite{havrikov2014xmlmate} is the only search-based tool we have encountered that can produce \emph{tree-like} structures such as XML.
+It is built on top of \emph{EvoSuite} with the aim of improving the test coverage of the XML-aware Java programs.
+To generate a random document, it either relies on an existing XML schema, or generates the document from scratch.
+Both tools have a similar approach for the mutation and crossover.
+One distinguishing feature of our approach is the use of program analysis to facilitate DOM generation.
 Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
 
-In contrast with the early presented techniques, the whole web application testing requires the application to be fully functional.
+In contrast with the techniques discussed so far, whole web application testing requires the application to be fully functional.
 This enables test generation based on crawling~\cite{mesbah2012invariant} and can be combined with the developer's written tests~\cite{milani2014leveraging}.
-\emph{Artemis}~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discovers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-Biagiola et al.~\cite{biagiola2017search} proposed to use \emph{page objects} to generate navigation path and input data with by exploiting search-based approach.
+\emph{Artemis}~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web applications.
+It discovers new tests by generating the sequences of executable events and monitoring how they effect the application state.
+Biagiola et al.~\cite{biagiola2017search} propose to use existing \emph{page objects} to produce navigation paths and input data by exploiting the search-based approach.
 \emph{JSEFT}~\cite{mirshokraie2015jseft} leverages dynamic execution to generate JS unit test including fixtures captured at run-time.
-The generated test can be compeented with DOM-dependent assertions produced by \emph{Atrina}~\cite{icst16}.
+The generated test can be complemented with the DOM-dependent assertions produced by \emph{Atrina}~\cite{icst16}.
 
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the help the JS \emph{Proxies} in order to collect type related information.
+%% \emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the help the JS \emph{Proxies} in order to collect type related information.
 
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
+%% \emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
 
@@
 
-One likely direction for the future extension of \emph{JEDI} is \emph{the whole test suite generation}~\cite{fraser2013whole}.
+One likely direction for the future extension of \emph{JEDI} is \emph{whole test suite generation}~\cite{fraser2013whole}.
 Such problems usually incur multi-objective optimization~\cite{lakhotia2007multi,panichella2017lips}, e.g.
-trade-off between coverage and test-suite length.
+a trade-off between coverage and test-suite length.
 
-Another direction of future work is re-targeting out tool towards mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
+Another direction of future work is re-targeting our tool towards mutation-driven generation of unit tests and oracles, similar to~\cite{fraser2012mutation}.
 That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.

### 2018-06-29 doc/issre2018/conclusions.tex

--- 2018-01-30 doc/icse2018/icse2018.tex
@@
-\documentclass[sigconf,review,anonymous]{acmart}
-
-\usepackage[inline]{enumitem}
-\usepackage{tablefootnote}
-\usepackage{syntax}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{booktabs} % For formal tables
-\usepackage{tikz}
-\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
-\usepackage{pgf-umlsd}
-\usepackage{tikz-uml}
-\usepackage{hyperref}
-\usepackage{upquote}
-\usepackage{listings}
-\usepackage{lsthaskell}
-\usepackage{xspace}
-\usepackage{enumitem}
-\usepackage{mdframed}
-\usepackage{algorithmic}
-\usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{pgfplots}
-\pgfplotsset{compat=newest}
-\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = red, %Colour of internal links
-  citecolor    = green %Colour of citations
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\definecolor{ltblue}{rgb}{0,0.4,0.4}
-\definecolor{dkblue}{rgb}{0,0.1,0.6}
-\definecolor{dkgreen}{rgb}{0,0.4,0}
-\definecolor{dkviolet}{rgb}{0.3,0,0.5}
-\definecolor{dkred}{rgb}{0.5,0,0}
-
-\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
-%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
-\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
-\definecolor{orange}{rgb}{1,0.45,0.13}		
-\definecolor{olive}{rgb}{0.17,0.59,0.20}
-\definecolor{brown}{rgb}{0.69,0.31,0.31}
-\definecolor{purple}{rgb}{0.38,0.18,0.81}
-\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
-\definecolor{lightred}{rgb}{1,0.4,0.5}
-% CSS
-\lstdefinelanguage{CSS}{
-  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},
-  sensitive=true,
-  morecomment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  morestring=[b]',
-  morestring=[b]",
-  alsoletter={:},
-  alsodigit={-}
-}
-
-% JavaScript
-\lstdefinelanguage{JavaScript}{
-  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
-  morecomment=[s]{/*}{*/},
-  morecomment=[l]//,
-  morestring=[b]",
-  morestring=[b]'
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  sensitive=true,	
-  alsoletter={<>=-},	
-  morecomment=[s]{<!-}{-->},
-  morestring=[b]'
-  tag=[s],
-  otherkeywords={
-  % General
-  >,
-  % Standard tags
-	<!DOCTYPE,
-  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
-	% body
-	</body, <body,
-	% Divs
-	</div, <div, </div>, 
-	% Paragraphs
-	</p, <p, </p>,
-	% scripts
-	</script, <script,
-  % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
-  },
-  ndkeywords={
-  % General
-  =,
-  % HTML attributes
-  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
-  % SVG attributes
-  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
-  % properties
-  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
-	% CSS3 properties
-  transform:, -moz-transform:, -webkit-transform:,
-  animation:, -webkit-animation:,
-  transition:,  transition-duration:, transition-property:, transition-timing-function:,
-  }
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  tagstyle=\color{blue},
-  markfirstintag=true,
-  sensitive=true,
-  alsoletter={<>=-},	
-  morecomment=[s]{<!--}{-->},
-  % tag=[s],
-  %% morestring=[b]'',
-  morestring=[b]',
-  ndkeywords={
-    % General
-    =,
-    % HTML attributes
-    id=, class= 
-  }
-}
-
-\lstdefinestyle{htmlcssjs} {%
-  % General design
-  backgroundcolor=\color{editorGray},
-  basicstyle={\scriptsize\ttfamily},   
-  frame=tb,
-  % line-numbers
-  xleftmargin={0.75cm},
-  numbers=left,
-  stepnumber=1,
-  firstnumber=1,
-  numberfirstline=true,	
-  % Code design
-  identifierstyle=\color{black},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywordstyle=\color{editorGreen}\bfseries,
-  stringstyle=\color{editorOcher}\ttfamily,
-  commentstyle=\color{brown}\ttfamily,
-  % Code
-  language=JavaScript,
-  alsolanguage=HTML5,
-  alsodigit={.:;},	
-  tabsize=2,
-  showtabs=false,
-  showspaces=false,
-  showstringspaces=false,
-  extendedchars=true,
-  breaklines=true,
-  escapechar=|c
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\listfiles % used to output the versions of all files being used by the latex
-
-\newcommand{\Server}{\emph{Server}\xspace}
-\newcommand{\Client}{\emph{Client}\xspace}
-\newcommand{\User}{\emph{User}\xspace}
-\newcommand{\Validator}{\emph{Validator}\xspace}
-\newcommand{\thenBr}{\text{then}}
-\newcommand{\elseBr}{\text{else}}
-\newcommand{\inFor}{\text{inFor}}
-\newcommand{\inWhile}{\text{while}}
-\newcommand{\un}[1]{\underline{#1}}
-\newcommand{\Random}{\mathbb{R}}
-\newcommand{\Genetic}{\mathbb{G}}
-\newcommand{\RGenetic}{\mathbb{G}_{10}}
-
-% Copyright
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-%% \acmYear{1997}                  
-%% \copyrightyear{2016}
-
-%% \acmPrice{15.00}
-
-\begin{document}
-\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
-
-\author{Alexander Elyasov}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands} 
-}
-\email{a.elyasov@uu.nl}
-
-\author{Wishnu Prasetya}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{s.w.b.prasetya@uu.nl}
-
-\author{Jurriaan Hage}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-  \country{The Netherlands} 
-}
-\email{j.hage@uu.nl}
-
-\begin{abstract}
-As of 2017 JavaScript and Node.js continue to stay the most prevalent technologies according to the Stack Overflow developers survey.
-Nevertheless, existing JS testing frameworks are still lacking any support for such a vital step in test automation as the generation of input data.
-To address this problem, we present a novel \textbf{J}avascript \textbf{E}volutionary-based testing framework with \textbf{D}OM as an \textbf{I}input, called \textbf{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state.
-We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
- It has shown that the \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage on all experimental subjects with the average 19 seconds of execution time per branch.
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Software and its engineering~Software testing and debugging}
-\ccsdesc[300]{Software and its engineering~Search-based software engineering}
-
-\keywords{JavaScript, search-based testing, branch coverage}
-
-\maketitle
-
-\section{Introduction}
-\label{sec.intro}
-
-According to a Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the fifth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
-It is used through all technology stack web, back-ends and mobile.
-Such a tremendous ever increasing JS success is happening thanks to the extensive dynamic features of the language, JS permissiveness and native browser support.
-On the other hand, JS applications are error-prone~\cite{why}, hard to analyze~\cite{why} and test~\cite{why}.
-Therefore, it is not surprising that year after year we hear new stories\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}} about another critical bug being found in a web application by Facebook, Twitter etc.
-
-%% Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.
-
-%% Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.
-
-The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
-These frameworks support testing at various levels: unit, integration and functional.
-The survey also indicated relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
-As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite of this effort, test data generation continues to be not properly addressed by any of the widely used testing frameworks.
-The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of JS faults are DOM-related and occur in JS code, and not in HTML or CSS.
-This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
-Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{mao2016sapienz}.
-In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript.
-Our work makes the following contributions:
-\begin{enumerate}[leftmargin=5mm]
-\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-\item We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency...
-\end{enumerate}
-
-The paper is structured as follows: In Section~\ref{sec.example}, we present a motivating example illustrating the challenges of generating test data for JS.
-The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} present empirical validation, whereas Section~\ref{sec.disc} discusses future work and validity threats.
-We discuss related work in Section~\ref{sec:related.work} and conclude the paper in Section~\ref{sec:concl}.
-
-Another empirical work~\cite{richards2010analysis}.
-
-%% --------------------------------------------------------------------
-\section{Motivating Example}
-\label{sec.example}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
-function isGameFinished() {
-  var obj = document.getElementById('sudoku'); |c \label{isGameFinished.getSudoku} |c
-  var subDivs = obj.getElementsByTagName('DIV'); |c \label{isGameFinished.getDivs} |c
-  var allOk = true;
-  for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
-    if (subDivs[no].className.indexOf('sudokuSquare') >= 0 |c \label{isGameFinished.if1.begin} |c 
-        && !subDivs[no].style.backgroundColor) { 
-      var spans = subDivs[no].getElementsByTagName('SPAN');
-      if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
-        allOk = false; |c \label{isGameFinished.unfinished} |c
-        break; 
-      }
-    }
-  } |c \label{isGameFinished.outFor} |c
-}
-\end{lstlisting}
-  \caption{JS function \texttt{isGameFinished.js} from sudoku}
-  \label{code.isGameFinished}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-                                 <div></div>                           
-  </div>                        </div> 
- </body>                       </body>    
-</html>                       </html>
-
-<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-   <div class='sudokuSquare'>    <div class='sudokuSquare'>
-    <span></span>                 <span></span> 
-    <span></span>                 <span>TEST</span>
-   </div>                        </div> 
-  </div>                        </div>
- </body>                       </body>
-</html>                       </html>
-  \end{lstlisting}
-  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
-  \label{fig.isGameFinished.tests}
-\end{figure}
-
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from a web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
-This function checks the validity of a sudoku solution given by a user.
-First, we find a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, we collect all its child DIVs (line~\ref{isGameFinished.getDivs}).
-Each DIV element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) and consists of two SPANs.
-First span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
-Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal SPAN values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
-
-Suppose now that we would like to unit test this function in isolation to the rest of the application.
-We aim to maximize the branch coverage as a common testing criteria~\cite{why.this.common}.
-That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
-We assume that DOM is the only global variable that can be referenced in the body of the FUT.
-So in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
-
-%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
-
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together deliver the full coverage of the FUT.
-Let us look now at how following the structure of the FUT in Figure~\ref{code.isGameFinished}, we can construct the $T4$ test covering the $(10,11)$ branch.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{DIV} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this $div$ to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the $div$ consists of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
-The resulted test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
-
-As we have just seen, even for such a relatively simple example, the construction procedure of a test input is far from trivial because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with the gazillion of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and, at the same time, it is easiest to implement.
-It greatly saves the developers from unexpected regression and puts a safety belt around the application.
-
-%% --------------------------------------------------------------------
-\section{Test Generation Framework}
-\label{sec.framework}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t!]
-  \centering 
-  \begin{sequencediagram}[font=\scriptsize]
-
-    \renewcommand\unitfactor{0.35}
-    \newinst{user}{\textbf{User}}
-    \newinst{server}{\textbf{Server}}
-    \newinst[1]{validator}{\textbf{Validator}}
-    \newinst{client}{\textbf{Client}}
-
-    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
-      \end{call}
-
-      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
-      \end{call}
-
-      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
-      \end{call}
-
-      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
-          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
-          \end{call}
-          \prelevel
-        \end{sdblock}
-
-        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
-            \end{call}
-
-            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
-            \end{callself}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
-          \end{callself}
-          \prelevel
-        \end{sdblock}
-        \mess{server}{best fitness}{user}
-
-      \end{sdblock}
-    \end{call}
-  \end{sequencediagram}
-  \caption{The architecture of the test framework}
-  \label{fig.framework.architect} 
-\end{figure}
-
-Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses the genetic engine for test generation.
-The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-\Server is the key component of the whole framework.
-It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}.
-Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactic correctness and reports back the set of identified errors.
-\Server rejects the document if any errors were revealed and generates a new one until the generated document has no errors anymore.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate the native browser API calls.
-
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
-Let us give a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random data generation, genetic phase, logging etc.
-Experimentally, we have found an optimal set of input configurations that was used across all experimental objects in Section~\ref{sec.evaluation}.
-This data is processed by the \Server during the \emph{Initialization Phase}.
-As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{ifun}, and the signature (\emph{sig}).
-\Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
-Depends on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
-the limit on the number of generation attempts.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate $p$ according to the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
-The execution trace along with some supplementary information about the execution are sent back to the \Server, where the final \emph{fitness value} is computed.
-The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-If a new HTML document is produced somewhere in the genetic phase, it has to be first approved by the \Validator.
-At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are exercised, the algorithm reaches the end.
-In the follow up two sections, we elaborate on the details of each individual phase of our test generation framework.
-
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
-
-During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing.
-The main steps of this phase are illustrated by Algorithm~\ref{alg.init}.
-Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info.
-Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName},
-which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT.
-Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants.
-Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure.
-Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
-
-\subsubsection{Supported Types}
-\label{sub.sec.sup.types}
-
-\begin{figure}[t!]
-\setlength{\grammarparsep}{3pt}
-\small
-\begin{grammar}
-
-<JS Type Annotation> ::= /*t <Signature> */
-
-<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
-
-<DOM> ::= \texttt{dom}
-
-<Type Signature> ::= <Type> | <Type> : <Type Signature>
-
-<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
-
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
-
-<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
-\end{grammar}
-\caption{Grammar of supported JS type annotations}
-\label{fig.js.type.annot}
-\end{figure}
-One assumption made in the paper is the availability of type signatures for JS functions.
-We believe in the legitimacy of such a request due to the following observations.
-First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity.
-Second, there has been an active work on the JS type inference done both in academia~\cite{kristensen2017type} and industry, e.g.
-Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.
-
-The grammar of the JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures those which refer to the global DOM and the ``ordinary'' JS type signatures.
-The functions of the former signature expect some \texttt{dom} argument to be passed as the first implicit parameter for the function call.
-Whereas ordinary JS signature is a non-zero sequence of the JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
-
-\subsubsection{Instrumentation}
-\label{sub.sec.instrument}
-
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \emph{trace} in line~\ref{isGameFinished.instr.trace} is an array of labels corresponding to the sequence of executed program statements.
-All statements have to be traced because each one, in theory, can rise an exception.
-The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations for the consecutive for-loop.
-If no exact bound can be computed, we set it to one.
-The \texttt{branchDistance} map tracks the distances to the deviated branches according to the translation formulae~\cite{tracey1998automated}.
-
-%TODO: maybe expand this section with the JS type casting for branch distance computation
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function isGameFinished() {
- trace.push(2); |c \label{isGameFinished.instr.trace} |c
- var obj = document.getElementById("sudoku");
- trace.push(3);
- var subDivs = obj.getElementsByTagName("DIV");
- trace.push(4);
- var allOk = true;
- loopMap[5] = function () { |c \label{isGameFinished.instr.loopMap} |c
-   var no = 0;
-   if (subDivs.length || subDivs.length == 0) {
-     return Math.abs(no - subDivs.length);
-   }
-   return 1;
- }();
- trace.push(5);
- for (var no = 0; no < subDivs.length; no++) {
-  trace.push(6);
-  trace.push(7);
-  if (subDivs[no].className.indexOf("sudokuSquare") >= 0 &&
-      !subDivs[no].style.backgroundColor) {
-   trace.push(8);
-   branchDistance.push({ 
-    label: 7, 
-    distance: Math.min(
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + _K_, 
-     absZero(subDivs[no].style.backgroundColor))
-   });
-   trace.push(9);
-   var spans = subDivs[no].getElementsByTagName("SPAN");
-   trace.push(10);
-   if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(11);
-    branchDistance.push({
-     label: 10,
-     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-    });
-    trace.push(12);
-    allOk = false;
-    break;
-   } else {
-     trace.push(14);
-     branchDistance.push({label: 10,distance: _K_});
-   }
-  } else {
-   trace.push(15);
-   branchDistance.push({
-    label: 7,
-    distance: 
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + 
-     absNegZero(subDivs[no].style.backgroundColor)
-   });
-  }
- }
- trace.push(5);
- trace.push(-1);
-}
-\end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
-  \label{code.isGameFinished.instr}
-\end{figure}
-
-\subsection{Genetic Phase}
-\label{sub.sec.genetic.phase}
-
-\begin{algorithm}[!t]
-  \caption{Genetic Phase}
-  \label{alg.gen}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{
-    $config$ is a GA configuration file\\
-    $b_n$ is a target branch of FUT\\
-    $(cfg, branches, cinfo, ifun, sig)$ output of Algorithm~\ref{alg.init}
-  }
-  \Output{
-     $(f^*, p^*)$ the best population candidate and its fitness score
-  }
-  \Fn{$Genetic(b_n, cfg, cinfo, config, ifun, sig)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M,size_{H}) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
-    $target \longleftarrow b_n$\label{alg.gen.init.target}\; 
-    $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
-    $historyConverged \longleftarrow true$\;
-    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
-      $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\; 
-      $history \longleftarrow \emptyset$\label{alg.gen.init.history}\; 
-      $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
-      \Repeat{$isPerfect(f^*) \vee historyConverged \vee (i > size_G)$}{\label{alg.gen.loop.begin}
-        $scoredPop \longleftarrow \emptyset$\;
-        $history \longleftarrow history \cup archive$\;
-        \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
-          $args \longleftarrow CoerceArguments(p, sig)$\label{alg.gen.make.args}\;
-          $(tr, d_B, d_L, dyncinfo) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
-          $f \longleftarrow Score(target, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
-          $cinfo \longleftarrow cinfo \cup dyncinfo$\label{alg.gen.eval.end}\;
-          $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        }
-        $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
-        $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
-        $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
-        $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
-        $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
-        $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
-        $i \longleftarrow i + 1$\;
-        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
-      }\label{alg.gen.loop.end}
-      $target \longleftarrow NewTarget(branches, b_n)$\label{alg.gen.new.target}\;
-    }\label{alg.gen.converged.loop.end}
-    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
-  }
-\end{algorithm}
-
-The heart of our test data generation framework is in the \emph{Genetic Phase}.
-Though, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, but has been extended with the concept of the \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we take a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
-The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
-
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ equal to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged or the generations limit has not been reached.
-The \emph{archive} variable stores the most fitted population candidates observed so far, and the \emph{history} variables records all archives during the generation process.
-These variables both are empty in the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
-
-The initial population has $size_P$ elements, and it is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found or the history has converged or the generation limit $size_G$ has been reached.
-But first, we need to score the current population lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
-Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
-Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
-Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
-This gives us 4-tuple consisting of an execution trace ($tr$), branch ($d_B$) and loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
-The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
-Collected dynamic constants \emph{dyncinfo} are merged with the existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}).
-And the $combo$ is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
-The fitness value of that element defines if a perfect candidate is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
-
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{ga.flag.problem.or.survey}.
-For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it occasionally.
-In such situation, we find ourselves being trapped on a flat space, with a small unreliable chance to escape.
-In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
-At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
-If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
-It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
-Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
-In practice, we only consider the target extensions upto the length of two.
-
-The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
-In the rest of this section, we reveal the implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our main focus in those sections is on the generation and transformation of HTML documents.
-
-\begin{table}
-  \caption{Genetic Operation for the JS Types}
-  \label{tbl.gen.oper.js.types}
-    \footnotesize
-  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
-    \toprule
-    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
-    \hline
-    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
-    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
-    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
-    Random    & Array  & array of a respective type upto length five\\
-    \hline
-    Crossover & Bool   & pick at random one out of two given booleans \\
-    Crossover & Int    & pick at random one out of two given integers\\
-    Crossover & Float  & pick at random one out of two given floats\\
-    Crossover & String & pick at random one out of two single point crossovers\\
-    Crossover & Array  & similar crossover operator as for strings\\
-    \hline
-    Mutation  & Bool   & flip the boolean constant\\
-    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
-    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
-    Mutation  & String & random string, remove char or apply pred(suc) char\\
-    Mutation  & Array  & Mutate a random element in array according to its type\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsubsection{Random HTML Generation}
-\label{sub.sub.sec.random.html}
-
-\begin{figure}[t]
-  \begin{haskell}
-instance Arbitrary Html where
-  arbitrary = evalStateT generateHTML defaultState
-
-generateHTML :: GenHtmlState |c \label{ref.generateHTML.begin} |c
-generateHTML = do
-  state <- get |c \label{ref.generateHTML.getState} |c   
-  let d = getDepth state |c \label{ref.generateHTML.getDepth} |c
-  if d == 0
-  then lift \dollar return \dollar toHtml "HTML" |c \label{ref.generateHTML.returnString} |c
-  else do put state{depth = d - 1} |c \label{ref.generateHTML.updateState} |c
-           head <- generateHEAD |c \label{ref.generateHTML.newHead} |c
-           body <- generateBODY |c \label{ref.generateHTML.newBody} |c
-           lift\dollar return \dollar docTypeHtml \dollar head >> body |c \label{ref.generateHTML.end} |c
-
-data Tag = HTML | HEAD | BODY | ...
-type Context = CFlow | CMetadata | ...
-data HtmlState = |c \label{ref.HtmlState.begin} |c
-  HtmlState { depth    :: Int,           degree  :: Int    
-             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
-             , tags    :: [Tag],         ids     :: [String]
-             , classes :: [String] } |c \label{ref.HtmlState.end} |c
-type GenState s = StateT s Gen |c \label{ref.GenState} |c
-type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
-  \end{haskell}
-  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
-  \label{fig.html.arb.def}
-\end{figure}
-
-We want to generate HTML according to the WHATWG\footnote{\url{https://html.spec.whatwg.org}} specification.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-The recent HTML5 standard defines more than hundred of tags and attributes which both have to comply with extremely complex logic to constitute a syntactically valid HTML.
-Browsers are usually tolerant to syntactic errors in HTML.
-They will silently fix them and display the page anyway.
-
-In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because, as we have mentioned early, the complexity of HTML and the lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} highlights that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) describes the internal state of \texttt{Html} in the generation.
-The state is composed of the following components:
-\begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of HTML 
-\item \texttt{ctx} is the current value of the HTML content model stack 
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
-\end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag should be defined as the value of the \texttt{GenHtmlState} type.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
-First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
-Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the new contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
-
-\subsubsection{Genetic HTML Operations}
-\label{sub.sub.sec.genetic.oper}
-
-In essence, HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for the \emph{expression trees} in genetic programming.
-
-\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
-
-\textbf{HTML Mutations} are of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
-The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
-The \emph{DropTree} mutation removes the whole sub-tree at a randomly chosen node.
-\emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
-Currently, we instantiated the \emph{ShuffleAttributes} mutation for only for tho types \emph{class} and \emph{id}.
-In total, this gives us four mutations to chose from in order to evolve an Html document.
-
-\subsubsection{Fitness Function}
-\label{sub.sub.sec.fitness.fun}
-
-The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating a valid input data.
-The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
-without premature exception.
-Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
-\[
-\textit{fit}(n) = \text{approach level} +
-\begin{cases}
- 1/2 * (\frac{\text{branch distance}}{1 + \text{branch distance}}) & \text{if no exception}\\
- 1                                  &  \text{otherwise}
-\end{cases}
-\]
-Final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
-\[
-\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
-\]
-Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
- \[
-\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
-\]
-
-The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
-the node caused the deviation.
-Since any node can potentially be exceptional, they all contribute to the approach level in addition to the conditional branches.
-Loops have to treated in a special way because we need to estimate the maximum number of iterations.
-In the case of for-loop, at run-time we can always provide an exact bound.
-For while-loops, we assume that it has to be passed at least once.
-The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
-
-\subsubsection{Limitations}
-\label{sub.sub.sec.limit}
-
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
-%% --------------------------------------------------------------------
-\section{Empirical Evaluation}
-\label{sec.evaluation}
-%% --------------------------------------------------------------------
-
-In order to evaluate the feasibility of our test framework adoption in practice, we conducted an empirical evaluation on a set of case-studies described in Section~\ref{sub.sec.case.studies}.
-All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which play the role of our baseline, is \emph{Random} ($\Random$).
-Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is the \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On one hand, the smaller window size forces the GA to converge faster and early discovers the stagnation on a flat space.
-On the other hand, the small window can lead to a premature archive convergence, which prevents the right genetic combination from been triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose it to report in the paper.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{fraser2011evosuite}.
-
-\begin{table}
-  \caption{Genetic Algorithm Configurations}
-  \label{tbl.gen.config}
-    \scriptsize
-  \begin{tabular}{l|r|r|r}
-    \toprule
-    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
-    \hline
-    Population size                   & 50  & 50  & 50  \\
-    Archive size                      & 1   & 25  & 25  \\
-    Maximum number of generations     & 200 & 200 & 200 \\
-    Crossover rate                    & 0   & 0.5 & 0.5 \\
-    Mutation rate                     & 0   & 0.5 & 0.5 \\
-    History window size               & -   & -   & 10  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-By carrying the evaluation, we would like to address the following research questions:
-\begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
-Which testing algorithm is the most effective?
-How the effectiveness changes with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost of one iteration?
-\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
-\end{description}
-
-\subsection{Case Studies}
-\label{sub.sec.case.studies}
-
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless number of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation.
-Before selection, the source code of a potential case-study has to be scrutinized which is time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
-Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}} to increase the presence of primitive (browserless) JS code.
-For each case-study application, we identified several JS functions that are suitable for our testing framework.
-In the end, our evaluation set included both primitive and DOM related JS functions.
-
-For the sake of space, we chose to exclude from the follow up presentation the branches and functions which coverage time was less than two seconds.
-In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
-This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the aforementioned case studies with the results presented in Section~\ref{sub.sec.eval.results}.
-
-\setlength\tabcolsep{0.6pt}
-\begin{table}[t]
-  \caption{Summary of the Case-Studies}
-  \label{tbl.case.studies}
-  %\resizebox{\textwidth}{!}{
-    \scriptsize
-  \begin{tabular}{l|l|p{3.1cm}|c|c|c|c|c|c|c|c}
-    \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & (dom)           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & (dom)         & 8  & 0 & 2 & 1 & + & + & + & - \\
-    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & + & - & + & - \\
-    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
-    \hline
-    phormer    & toggleInfo & (dom,string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
-    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
-    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
-    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
-    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
-    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
-    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
-    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
-    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
-    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
-    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & (dom,[int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
-    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
-    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
-    \hline
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
-    %% \hline
-    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
-    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
-    \bottomrule
-  \end{tabular}
-%}
-\end{table}
-
-\subsection{Results}
-\label{sub.sec.eval.results}
-
-\setlength\tabcolsep{.98pt}
-\begin{table}[!t]
-  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
-  \label{tbl.stats}
-    \scriptsize
-    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
-      \toprule
-      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{2-10} % \!:\!
-                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \midrule
-    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \textbf{newGame}*   
-                             & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \textbf{revealAll}*  
-                             & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-    \textbf{shuffleBoard}*   
-                             & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \hline
-   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \hline
-   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \hline
-   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \hline
-   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-   \midrule
-    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
-    \bottomrule
-   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \hline
-    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \hline
-    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
-    \midrule
-    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
-    %% \midrule
-    %% \midrule
-    \bottomrule
-    \bottomrule  
-    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-To study the effectiveness and efficiency of our test generation framework, including three test algorithms Random~($\Random$), Genetic~($\Genetic$) and Genetic with Restart~($\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
-In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ according to the algorithm type $\Random$, $\Genetic$ and $\RGenetic$.
-Next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-Inline with the function name, we also present accumulated statistics for the function as a whole.
-Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function.
-
-According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
-We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with the respective the CC 13, 14 and 16.
-Table~\ref{tbl.stats.sum} summarizes the total results of the experiment such as coverage, execution time per branch and significance.
-
-\begin{table}[!t]
-  \caption{Result Summary (L - large, M - medium, S - small)}
-  \label{tbl.stats.sum}
-    \footnotesize
-    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
-      \toprule
-      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
-      \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{8-16}
-                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
-      \midrule
-      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
-      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
-      \midrule
-      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
-Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The values in Table~\ref{tbl.stats} highlighted as $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
-The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
-branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of genetic approach~($\Genetic$), it may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
-We encountered three of such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines strengths of both algorithms genetic and random.
-It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only manged to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
-branch $(69,71)$ of the \emph{initBricks} function.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
-  }
-}
-
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig.budget.progress}
-\end{figure}
-
-Additionally, we would like to investigate how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time depended.
-E.g.
-running tests inside IDE should be fast; as part of the CI cycle we may afford a large waiting time; regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ starts to transcend $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
-  }
-}
-
-\paragraph{\textbf{RQ2 (efficiency).}}
- To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
-Based on this information, we suggest an estimate on the execution time of the testing framework.
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
-
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=950,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        restrict y to domain*=0:1350, % Cut values off at 14
-        visualization depends on=rawy\as\rawy, % Save the unclipped values
-        after end axis/.code={ % Draw line indicating break
-          \draw [ultra thick, white, decoration={snake, amplitude=1pt}, decorate] (rel axis cs:0,1.05) -- (rel axis cs:1,1.05);
-        },
-        nodes near coords={%
-          \pgfmathprintnumber{\rawy}% Print unclipped values
-        },
-        every node near coord/.append style={rotate=90,anchor=west,font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,270) (isGameFinished*,220) (newGame*,14) (revealAll*,50) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,514) (isValidVISA,95) (initShields*,5) (brickJiggler*,8) (doPaddlePower*,15)  (initBricks*,2379) (do\_draw,625) (prob\_gamma,710)};
-      \addplot[fill=red] coordinates {(helpMe*,47)  (isGameFinished*,30)  (newGame*,9)  (revealAll*,44) (shuffleBoard*,26) (toggleInfo*,7) (isValidCard,8)   (isValidVISA,3)  (initShields*,5) (brickJiggler*,4) (doPaddlePower*,140) (initBricks*,474) (do\_draw,1295) (prob\_gamma,84)};
-      \addplot[fill=yellow] coordinates {(helpMe*,56)  (isGameFinished*,43)  (newGame*,10) (revealAll*,53) (shuffleBoard*,29) (toggleInfo*,6) (isValidCard,10)  (isValidVISA,2)  (initShields*,3) (brickJiggler*,3) (doPaddlePower*,16) (initBricks*,415) (do\_draw,334) (prob\_gamma,81)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Overall test generation time per function.}
-  \label{fig.gen.time.comp}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=4,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,1.24) (isGameFinished*,0.83) (newGame*,0.78) (revealAll*,0.83) (shuffleBoard*,1.93) (toggleInfo*,1) (isValidCard,0.51) (isValidVISA,0.47) (initShields*,0.83) (brickJiggler*,1.14) (doPaddlePower*,0.79)  (initBricks*,1.68) (do\_draw,2.33) (prob\_gamma,0.35)};
-      \addplot[fill=red] coordinates {(helpMe*,0.77)  (isGameFinished*,0.94)  (newGame*,0.81)  (revealAll*,1) (shuffleBoard*,1.73) (toggleInfo*,1) (isValidCard,0.38)   (isValidVISA,0.38)  (initShields*,0.83) (brickJiggler*,0.67) (doPaddlePower*,0.69) (initBricks*,0.8) (do\_draw,3.38) (prob\_gamma,0.52)};
-      \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Speed of test generation measured as $t/i$}
-    \label{fig.get.cost}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with the 7 and 25 seconds per branch.
-For simple functions, the $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
-In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch 19, 39 and 88 seconds, respectively. 
-  }
-}
-
-Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
-This information is useful when configuring the maximal generation limit.
-The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures the speed of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus not rising exceptions, and at the same time, it consists of 40 LOC.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
-  }
-}
-
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs comparing to $\Genetic$.
-Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases globally and 67\% on the difficult functions.  
-  }
-}
-
-\paragraph{\textbf{Threats to Validity}}
-The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Though, the branch coverage is a common criteria used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
-Reaching a target branch is only part of the problem, we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles disseminating in exceptions.
-Using a stronger oracle for validation is future work.
-Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent unnecessary data explosion.
-Additional measure that could be taken is applying a minimization procedure, aka \emph{delta debugging}, to the GA result.
-
-Initial GA configuration introduces the threat to the \emph{internal validity} of our empirical evaluation.
-The parameters we used are quite standard for similar SBST frameworks, e.g.
-EvoSuite.
-Though, not reported in the paper, we performed preliminary assessment of various GA configurations, which confirmed our final decision.
-
-The threat of \emph{conclusion validity} can be affected by the GA stochastic nature.
-This risk was addressed by repeating the experiment 50 times and performing statistical analysis of the significance and effect size.
-We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
-
-The \emph{external validity} deals with the threat of generalization of our results due to manual selection of the experimental subjects.
-To mitigate this fact, we picked the subjects either from previously used in related research or found in open source.
-Of course, those subjects still have to met the constrains of our testing approach.
-So, further research is required in both increasing the power of our framework and extending the validation set.
-
-%% --------------------------------------------------------------------
-\section{Related and Future Work}
-\label{sec:related.work}
-%% --------------------------------------------------------------------
-
-The last two decades were fruitful in the amount of work dedicates to the analysis and web applications and JavaScript, in particular.
-The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around two main questions:
-\begin{enumerate*}
-\item test data generation for JS functions interacting with the DOM, and
-\item the application of search-based techniques for that problem.
-\end{enumerate*}
-
-\subsection{Test Data Generation for JavaScript}
-
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect constant info and feed it to the random generation.
-We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} proposes to use feedback-directed random testing for generating TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing concolic testing or type inconsistency analysis~\cite{pradel2015typedevil}.
-It suffers from typical for the symbolic analysis problems such as the handing of arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtains DOM fixtures for the FUT.
-Combined with Jalangi it can be used for both primitive and DOM test data generation.
-As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
-Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as solid alternative for program testing.
-In fact both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discoverers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-
-\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the JS \emph{Proxies} in order to collect type related information.
-
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-
-\cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-\cite{ma2015grt} guided random testing
-
-\cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-\cite{jquery2014}
-
-ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-Information-flow security for JS~\cite{hedin2012information}.
-
-Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Search-Based Test Data Generation}
-\label{sub.sec.search.based}
-
-Despite of the practical popularity of JavaScript, the only recorded in the literature attempt of adopting search-based testing for JS unit testing was done by Alshraideh~\cite{alshraideh2008complete}.
-It uses GA for branch and mutation coverage, but only deals with the limited input types booleans, integers and strings; and provides validation based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports array and DOM types, with suggest reasonable validation with the discussion of significance and effect size.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-In this paper we dealt with the generation and evolution of DOM which is an example of tree-like data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim to improve test coverage of the XML-aware Java programs.
-To generate random document, it may rely on existing XML schema, or generate document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, which is difficult to comply.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for mutation and crossover.
-Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
-
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of SBST research~\cite{mcminn2011search}.
-Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage.
-That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
-coverage vs.
-test-suite length.
-Another direction of future work is adjusting out tool for mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That would also help us to judge about the fault revealing ability of \emph{JEDI} based on the number of killed mutants.
-As we said early in this section, SBST techniques can benefit from symbolic analysis~\cite{baars2011symbolic}.
-
 \section{Conclusions}
 \label{sec:concl}
-This paper
 
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{icse2018.bib}
-
-\end{document}
+In this paper we have introduced a novel JS unit testing framework, called \emph{JEDI}, which uses search-based techniques for generating test data.
+Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
+We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
+Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
+The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.

### 2018-06-29 doc/issre2018/framework.tex

@@
 Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $\mathbb{B}_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application, which uses under the hood a genetic engine, for test generation.
+Our JS testing framework, called \emph{JEDI}, is a client-server application, which under the hood uses a genetic engine for test generation.
 The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
 The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-The \Server is the key component of the  framework, responsible for the \emph{Initialization} and \emph{Genetic Phases}, covered in detail in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
+The \Server is the key component of the  framework.
+It is responsible for the \emph{Initialization} and \emph{Genetic Phases}, which are covered in detail in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase}, respectively.
 
-Each newly constructed HTML document has to be assessed by the \Validator~\cite{htmlvalidator} that checks its syntactic correctness and reports back any identified errors.
-The document generation process is repeated by the \Server until there are no errors revealed.
+Each newly constructed HTML document has to be assessed by the \Validator~\cite{htmlvalidator}.
+It checks the document for syntactic correctness and reports back any identified errors.
+The document generation process is repeated by the \Server until there are no more errors revealed.
 \Client is a \emph{Node.js}~\cite{nodejs} application that is mainly responsible for the execution of the JS code.
@@
 As an input for our testing framework, \User has to provide a JS file \emph{fun.js} that contains a FUT \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that sets various control parameters for the random and genetic phases, logging etc.
-Experimentally, we have found an optimal configuration that was consistently used in the experimental evaluation in Section~\ref{sec.evaluation}.
+Additionally, \User specifies a configuration file \emph{config} that sets various control parameters for the random and genetic generation, logging and so on.
+Experimentally, we have found an optimal configuration that we consistently used in the experimental evaluation in Section~\ref{sec.evaluation}.
 Once all the data are processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
@@
 Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework triggers the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework begins with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criteria is achieved, e.g.
+For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
+Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criteria is achieved, e.g.
 the limit on the number of generation attempts.
-Any HTML document produced during the genetic phase has to be first approved by the \Validator.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate solution $p$ with the type signature \emph{sig}, and invokes the instrumented JS function as \emph{ifun(p)}.
+Any HTML document produced during the genetic phase should be approved by the \Validator.
+Each candidate in the population is evaluated in \emph{Evaluation Loop} by \Client.
+First, the candidate solution $p$ is matched with the type signature \emph{sig}.
+Then, the instrumented function \emph{ifun} is called (\emph{ifun(p)}).
 The execution trace along with some auxiliary information is sent back to the \Server, where the final \emph{fitness value} is computed.
@@
 Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants, e.g.
-numeric and string literals.
-Additionally, we monitor the calls to such DOM API methods as \texttt{getElementsByTagName}, \texttt{getElementById}, and \texttt{getElementsByClassName}.
-These methods provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the FUT.
+In order to maximize the chances of generating the fittest candidate, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants such as numeric and string literals.
+Additionally, we monitor the calls to the functions \texttt{getElementsByTagName}, \texttt{getElementById}, and \texttt{getElementsByClassName} and other DOM API methods.
+They provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the FUT.
 The next step is to normalize the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
 transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) for run-time data collection about the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants.
-Upon the \emph{ifun} execution this information is gathered and fed back to the fitness evaluation procedure.
-Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
+We instrument the FUT (line~\ref{alg.init.instr}) in order to collect at run-time the values of the execution trace, \emph{the approach level}, \emph{the branch and loop distances} (explained later), and the constants.
+Upon the \emph{ifun} execution this information will be gathered and fed back to the fitness evaluation procedure.
+Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and return all branches of the FUT (line~\ref{alg.init.get.branches}).
 
@@
 We assume the FUT is equipped with the type signature.
-The legitimacy of such a requirement can be confirmed by the popularity of \emph{TypeScript}~\cite{typescript}, and advances in the JS type inference \emph{Flow}~\cite{flow}.
+The legitimacy of such requirement can be confirmed by the popularity of \emph{TypeScript}~\cite{typescript}, and advances in the JS type inference, e.g.
+\emph{Flow}~\cite{flow}.
 The supported grammar of type annotations is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
+Each type annotation is a signature expressed as a specialized JS type comment (\texttt{/*t...*/}).
 We distinguish between two kinds of signatures: with the reference to the global DOM and ``ordinary'' JS type signatures.
@@
 %% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-%% \subsubsection{Instrumentation}
-%% \label{sub.sec.instrument}
+\subsubsection{Instrumentation}
+\label{sub.sec.instrument}
 
-%% Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
+Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
 The global variable \texttt{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT.
@@
 
-%% %TODO: maybe expand this section with the JS type casting for branch distance computation
+%TODO: maybe expand this section with the JS type casting for branch distance computation
 
-%% \begin{figure}[!t]
-%%   \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-%% function isGameFinished() {
-%%  trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
-%%  trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
-%%  var allOk = true;
-%%  loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
-%%    var no = 0;
-%%    if (subDivs.length || subDivs.length == 0) {
-%%      return Math.abs(no - subDivs.length);
-%%    }; return 1}();
-%%  trace.push(3);
-%%  for (var no = 0; no < subDivs.length; no++) {
-%%   trace.push(4);
-%%   if (subDivs[no].className.indexOf("square") >= 0 &&
-%%       !subDivs[no].style.backgroundColor) {
-%%    trace.push(5); branchDistance.push({ label: 3,
-%%     distance: Math.min(
-%%      abs(subDivs[no].className.indexOf("square"),0)+_K_
-%%      absZero(subDivs[no].style.backgroundColor))
-%%    });
-%%    trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
-%%    trace.push(7);
-%%    if (spans[0].innerHTML != spans[1].innerHTML) {
-%%     trace.push(8); branchDistance.push({ label: 7,
-%%      distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-%%     });
-%%     allOk = false; break;
-%%    } else {
-%%    trace.push(9);branchDistance.push({label:7,distance:_K_});
-%%    }
-%%   } else {
-%%    trace.push(10); branchDistance.push({ label: 3,
-%%     distance:
-%%      abs(subDivs[no].className.indexOf("square"), 0) +
-%%      absNegZero(subDivs[no].style.backgroundColor)
-%%    });}}
-%%  trace.push(-1);
-%% }
-%% \end{lstlisting}
-%%   \caption{Instrumented version of \texttt{isGameFinished.js} }
-%%   \label{code.isGameFinished.instr}
-%% \end{figure}
+\begin{figure}[!t]
+  \tiny
+  \begin{lstlisting}[style=htmlcssjs,language=JavaScript,basicstyle={\tiny\ttfamily}]
+function isGameFinished() {
+ trace.push(1);var obj = document.getElementById("sudoku"); |c \label{isGameFinished.instr.trace} |c
+ trace.push(2);var subDivs = obj.getElementsByTagName("DIV");
+ var allOk = true;
+ loopMap[3] = function () { |c \label{isGameFinished.instr.loopMap} |c
+   var no = 0;
+   if (subDivs.length || subDivs.length == 0) {
+     return Math.abs(no - subDivs.length);
+   }; return 1}();
+ trace.push(3);
+ for (var no = 0; no < subDivs.length; no++) {
+  trace.push(4);
+  if (subDivs[no].className.indexOf("square") >= 0 &&
+      !subDivs[no].style.backgroundColor) {
+   trace.push(5); branchDistance.push({ label: 3,
+    distance: Math.min(
+     abs(subDivs[no].className.indexOf("square"),0)+_K_
+     absZero(subDivs[no].style.backgroundColor))
+   });
+   trace.push(6);var spans=subDivs[no].getElementsByTagName("SPAN");
+   trace.push(7);
+   if (spans[0].innerHTML != spans[1].innerHTML) {
+    trace.push(8); branchDistance.push({ label: 7,
+     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
+    });
+    allOk = false; break;
+   } else {
+   trace.push(9);branchDistance.push({label:7,distance:_K_});
+   }
+  } else {
+   trace.push(10); branchDistance.push({ label: 3,
+    distance:
+     abs(subDivs[no].className.indexOf("square"), 0) +
+     absNegZero(subDivs[no].style.backgroundColor)
+   });}}
+ trace.push(-1); return allOK;
+}
+\end{lstlisting}
+  \caption{Instrumented version of \texttt{isGameFinished.js} }
+  \label{code.isGameFinished.instr}
+\end{figure}
 
@@
         $i \longleftarrow i + 1$\;
-        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
+        $historyConverged \longleftarrow isConverged(history, size_H)$ \label{alg.gen.has.converged}\;
       }\label{alg.gen.loop.end}
@@
 Although, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, it has been extended with the concept of \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we specify a configuration file \emph{config}, a target branch $b_n$ of the FUT, and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
+As an input, we pass a configuration file \emph{config}, a target branch $b_n$ of the FUT, and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
 The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
@@
 The \emph{archive} variable stores the most fit population candidates observed so far, and the \emph{history} variable records all the archives during the generation process.
-The two variables are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
+These variables are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
 
-The initial population of $size_P$ is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
+The initial population of the $size_P$ elements is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
 In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate is found, or the history is converged, or the generation limit $size_G$ is reached.
@@
 Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
-Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
+Thus, it should be coerced according to the type signature $sig$ (line~\ref{alg.gen.make.args}).
 Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
@@
 It is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
+Then, the scored population together with the current archive are sorted by fitness value, and the top $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
+The first element of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
 If $f^*$ is a \emph{perfect} candidate, the solution is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
+Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as an output.
 
-However, ff during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
 At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
@@
 In some cases, we get insufficient guidance from a fitness function because the FUT contains \emph{flag variables}~\cite{baresel2004evolutionary}, nested predicates~\cite{mcminn2005testability}, or unstructured control flow~\cite{hierons2005branch}.
-Researches have devised several techniques, such as \emph{chaining approach}~\cite{ferguson1996chaining,mcminn2006evolutionary} and \emph{testability transformation}~\cite{korel2005data}, to overcome with these problems.
-The common idea behind of these techniques is to incorporate data dependency into the search.
+Researches have devised several techniques, such as \emph{chaining approach}~\cite{ferguson1996chaining,mcminn2006evolutionary} and \emph{testability transformation}~\cite{korel2005data}, to overcome these problems.
+The common idea behind of those techniques is to incorporate data dependency into the search.
 In our case, such an analysis for JS is hard to implement~\cite{jang2009points}.
-So we decided to build our search algorithm purely on the knowledge about control-flow dependencies.
-The downside of this idea is the lack of precision, i.e some of the node sequences are fruitless to tackle.
+So we decided to build our search algorithm purely on the knowledge of the control flow dependencies.
+The downside of this approach is the lack of precision, i.e some of the node sequences are fruitless to test.
 Nevertheless, it was sufficient to find solutions for our experimental subjects.
 
-The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
+The genetic operations applied to the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
 In the rest of this section, we provide implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and the fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
@@
 We want to generate HTML according to the WHATWG~\cite{htmlspec} specification.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
+HTML is an XML-family markup language that uses special \emph{tags} and \emph{attributes} to describe document structures on the Web.
 The recent HTML5 standard defines more than a hundred of tags and attributes which both have to comply with extremely complex logic to constitute  syntactically valid HTML.
@@
 Our search target is a specific branch of the FUT that we want to cover.
-As a dynamically typed language, JS does not statically guarantee for an object that its accessed field or method are defined.
-Thus, such a behaviour can only be known at run-time and will eventually result into an exception.
-We have to assume that every statement of the FUT can rise an exception leading to the deviation from the target.
+As a dynamically typed language, JS does not provide any static guarantees that an accessed field or a called method for an object are defined.
+Thus, such behaviour can only be known at run-time and may eventually rise an exception.
+Thus, we have to assume that every statement of the FUT, in theory, can rise an exception leading to the deviation from the target.
 We consider a test input as \emph{valid} only if it leads the FUT to a \emph{normal termination}, i.e.

### 2018-06-29 doc/issre2018/graph-generation-time.tex

--- 2018-01-30 doc/icse2018/icse2018.tex
@@
-\documentclass[sigconf,review,anonymous]{acmart}
+  \begin{tikzpicture}[scale=0.9,rotate=-90]
 
-\usepackage[inline]{enumitem}
-\usepackage{tablefootnote}
-\usepackage{syntax}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{booktabs} % For formal tables
-\usepackage{tikz}
-\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
-\usepackage{pgf-umlsd}
-\usepackage{tikz-uml}
-\usepackage{hyperref}
-\usepackage{upquote}
-\usepackage{listings}
-\usepackage{lsthaskell}
-\usepackage{xspace}
-\usepackage{enumitem}
-\usepackage{mdframed}
-\usepackage{algorithmic}
-\usepackage{longtable}
-\usepackage{subcaption}
-\usepackage{pgfplots}
-\pgfplotsset{compat=newest}
-\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = red, %Colour of internal links
-  citecolor    = green %Colour of citations
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\definecolor{ltblue}{rgb}{0,0.4,0.4}
-\definecolor{dkblue}{rgb}{0,0.1,0.6}
-\definecolor{dkgreen}{rgb}{0,0.4,0}
-\definecolor{dkviolet}{rgb}{0.3,0,0.5}
-\definecolor{dkred}{rgb}{0.5,0,0}
-
-\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
-%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
-\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
-\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
-\definecolor{orange}{rgb}{1,0.45,0.13}		
-\definecolor{olive}{rgb}{0.17,0.59,0.20}
-\definecolor{brown}{rgb}{0.69,0.31,0.31}
-\definecolor{purple}{rgb}{0.38,0.18,0.81}
-\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
-\definecolor{lightred}{rgb}{1,0.4,0.5}
-% CSS
-\lstdefinelanguage{CSS}{
-  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},
-  sensitive=true,
-  morecomment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  morestring=[b]',
-  morestring=[b]",
-  alsoletter={:},
-  alsodigit={-}
-}
-
-% JavaScript
-\lstdefinelanguage{JavaScript}{
-  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
-  morecomment=[s]{/*}{*/},
-  morecomment=[l]//,
-  morestring=[b]",
-  morestring=[b]'
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  sensitive=true,	
-  alsoletter={<>=-},	
-  morecomment=[s]{<!-}{-->},
-  morestring=[b]'
-  tag=[s],
-  otherkeywords={
-  % General
-  >,
-  % Standard tags
-	<!DOCTYPE,
-  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
-	% body
-	</body, <body,
-	% Divs
-	</div, <div, </div>, 
-	% Paragraphs
-	</p, <p, </p>,
-	% scripts
-	</script, <script,
-  % More tags...
-  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
-  },
-  ndkeywords={
-  % General
-  =,
-  % HTML attributes
-  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
-  % SVG attributes
-  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
-  % properties
-  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
-	% CSS3 properties
-  transform:, -moz-transform:, -webkit-transform:,
-  animation:, -webkit-animation:,
-  transition:,  transition-duration:, transition-property:, transition-timing-function:,
-  }
-}
-
-\lstdefinelanguage{HTML5}{
-  language=html,
-  tagstyle=\color{blue},
-  markfirstintag=true,
-  sensitive=true,
-  alsoletter={<>=-},	
-  morecomment=[s]{<!--}{-->},
-  % tag=[s],
-  %% morestring=[b]'',
-  morestring=[b]',
-  ndkeywords={
-    % General
-    =,
-    % HTML attributes
-    id=, class= 
-  }
-}
-
-\lstdefinestyle{htmlcssjs} {%
-  % General design
-  backgroundcolor=\color{editorGray},
-  basicstyle={\scriptsize\ttfamily},   
-  frame=tb,
-  % line-numbers
-  xleftmargin={0.75cm},
-  numbers=left,
-  stepnumber=1,
-  firstnumber=1,
-  numberfirstline=true,	
-  % Code design
-  identifierstyle=\color{black},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywordstyle=\color{editorGreen}\bfseries,
-  stringstyle=\color{editorOcher}\ttfamily,
-  commentstyle=\color{brown}\ttfamily,
-  % Code
-  language=JavaScript,
-  alsolanguage=HTML5,
-  alsodigit={.:;},	
-  tabsize=2,
-  showtabs=false,
-  showspaces=false,
-  showstringspaces=false,
-  extendedchars=true,
-  breaklines=true,
-  escapechar=|c
-}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\listfiles % used to output the versions of all files being used by the latex
-
-\newcommand{\Server}{\emph{Server}\xspace}
-\newcommand{\Client}{\emph{Client}\xspace}
-\newcommand{\User}{\emph{User}\xspace}
-\newcommand{\Validator}{\emph{Validator}\xspace}
-\newcommand{\thenBr}{\text{then}}
-\newcommand{\elseBr}{\text{else}}
-\newcommand{\inFor}{\text{inFor}}
-\newcommand{\inWhile}{\text{while}}
-\newcommand{\un}[1]{\underline{#1}}
-\newcommand{\Random}{\mathbb{R}}
-\newcommand{\Genetic}{\mathbb{G}}
-\newcommand{\RGenetic}{\mathbb{G}_{10}}
-
-% Copyright
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ISSTA 2018]{ACM SIGSOFT International Symposium on Software Testing and Analysis}{16-22 July, 2018}{Amsterdam, The Netherlands}
-%% \acmYear{1997}                  
-%% \copyrightyear{2016}
-
-%% \acmPrice{15.00}
-
-\begin{document}
-\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}
-
-\author{Alexander Elyasov}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands} 
-}
-\email{a.elyasov@uu.nl}
-
-\author{Wishnu Prasetya}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-}
-\email{s.w.b.prasetya@uu.nl}
-
-\author{Jurriaan Hage}
-\affiliation{%
-  \institution{Utrecht University, The Netherlands}
-  \country{The Netherlands} 
-}
-\email{j.hage@uu.nl}
-
-\begin{abstract}
-As of 2017 JavaScript and Node.js continue to stay the most prevalent technologies according to the Stack Overflow developers survey.
-Nevertheless, existing JS testing frameworks are still lacking any support for such a vital step in test automation as the generation of input data.
-To address this problem, we present a novel \textbf{J}avascript \textbf{E}volutionary-based testing framework with \textbf{D}OM as an \textbf{I}input, called \textbf{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state.
-We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
- It has shown that the \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage on all experimental subjects with the average 19 seconds of execution time per branch.
-\end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10011074.10011784</concept_id>
-<concept_desc>Software and its engineering~Search-based software engineering</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Software and its engineering~Software testing and debugging}
-\ccsdesc[300]{Software and its engineering~Search-based software engineering}
-
-\keywords{JavaScript, search-based testing, branch coverage}
-
-\maketitle
-
-\section{Introduction}
-\label{sec.intro}
-
-According to a Stack Overflow survey\footnote{\url{https://insights.stackoverflow.com/survey/2017}} run in 2017 across developers, JavaScript has been recognized for the fifth time in row as the most commonly used programming language with Node.js as the most commonly used technology.
-It is used through all technology stack web, back-ends and mobile.
-Such a tremendous ever increasing JS success is happening thanks to the extensive dynamic features of the language, JS permissiveness and native browser support.
-On the other hand, JS applications are error-prone~\cite{why}, hard to analyze~\cite{why} and test~\cite{why}.
-Therefore, it is not surprising that year after year we hear new stories\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}} about another critical bug being found in a web application by Facebook, Twitter etc.
-
-%% Common mistakes JS developers do\footnote{\url{https://www.toptal.com/javascript/10-most-common-javascript-mistakes}}.
-
-%% Notable errors in 2017\footnote{\url{https://www.fastcompany.com/40505226/the-year-that-software-bugs-ate-the-world}}.
-
-The state of JS 2017 survey~\footnote{\url{https://stateofjs.com/}} contains an extensive list of testing frameworks including Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma and QUnit.
-These frameworks support testing at various levels: unit, integration and functional.
-The survey also indicated relatively low satisfaction rate of the current state of JS testing tools, scoring only 3.2 out of 5.
-As result, new testing frameworks such as Cypress and Storybook are constantly appearing to improve the situation.
-But despite of this effort, test data generation continues to be not properly addressed by any of the widely used testing frameworks.
-The research community has actively been working towards making progress in this direction introducing such tools as Artemis~\cite{artemis2011}, JSConTest~\cite{heidegger2010contract}, Crawljax~\cite{mesbah2012crawling}, JSeft~\cite{mirshokraie2015jseft} and Jalangi~\cite{sen2013jalangi}.
-A recent study of client-side JS bugs~\cite{ocariza2017study} has shown that the majority (68\%) of JS faults are DOM-related and occur in JS code, and not in HTML or CSS.
-This fact indicates that yet a better testing approach is needed when it comes to unit testing of JS.
-
-Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{mao2016sapienz}.
-In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript.
-Our work makes the following contributions:
-\begin{enumerate}[leftmargin=5mm]
-\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-\item We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency...
-\end{enumerate}
-
-The paper is structured as follows: In Section~\ref{sec.example}, we present a motivating example illustrating the challenges of generating test data for JS.
-The architecture of the \emph{JEDI} testing framework is explained in Section~\ref{sec.framework}.
-Section~\ref{sec.evaluation} present empirical validation, whereas Section~\ref{sec.disc} discusses future work and validity threats.
-We discuss related work in Section~\ref{sec:related.work} and conclude the paper in Section~\ref{sec:concl}.
-
-Another empirical work~\cite{richards2010analysis}.
-
-%% --------------------------------------------------------------------
-\section{Motivating Example}
-\label{sec.example}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-/*t dom */
-function isGameFinished() {
-  var obj = document.getElementById('sudoku'); |c \label{isGameFinished.getSudoku} |c
-  var subDivs = obj.getElementsByTagName('DIV'); |c \label{isGameFinished.getDivs} |c
-  var allOk = true;
-  for (var no = 0; no < subDivs.length; no++) { |c \label{isGameFinished.inFor.begin} |c
-    if (subDivs[no].className.indexOf('sudokuSquare') >= 0 |c \label{isGameFinished.if1.begin} |c 
-        && !subDivs[no].style.backgroundColor) { 
-      var spans = subDivs[no].getElementsByTagName('SPAN');
-      if (spans[0].innerHTML != spans[1].innerHTML) { |c \label{isGameFinished.if2.begin} |c
-        allOk = false; |c \label{isGameFinished.unfinished} |c
-        break; 
-      }
-    }
-  } |c \label{isGameFinished.outFor} |c
-}
-\end{lstlisting}
-  \caption{JS function \texttt{isGameFinished.js} from sudoku}
-  \label{code.isGameFinished}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs, language=HTML5]
-<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-                                 <div></div>                           
-  </div>                        </div> 
- </body>                       </body>    
-</html>                       </html>
-
-<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
-<html>                        <html>
- <body>                        <body>
-  <div id='sudoku'>             <div id='sudoku'>
-   <div class='sudokuSquare'>    <div class='sudokuSquare'>
-    <span></span>                 <span></span> 
-    <span></span>                 <span>TEST</span>
-   </div>                        </div> 
-  </div>                        </div>
- </body>                       </body>
-</html>                       </html>
-  \end{lstlisting}
-  \caption{Input DOM arguments for \texttt{isGameFinished.js}}
-  \label{fig.isGameFinished.tests}
-\end{figure}
-
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from a web game \emph{sudoku}\footnote{\url{http://www.dhtmlgoodies.com/scripts/game_sudoku/game_sudoku.html}}.
-This function checks the validity of a sudoku solution given by a user.
-First, we find a DOM element representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, we collect all its child DIVs (line~\ref{isGameFinished.getDivs}).
-Each DIV element corresponds to a sudoku input square (line~\ref{isGameFinished.if1.begin}) and consists of two SPANs.
-First span contains a user input, whereas the second one, which is hidden by default, stores the expected value for that sudoku square.
-Inside of a for-loop in lines~\ref{isGameFinished.inFor.begin}-\ref{isGameFinished.outFor}, we iterate over the whole collection of input squares.
-Once, we find a square with two unequal SPAN values (line~\ref{isGameFinished.if2.begin}), the loop is terminated and the game is considered unfinished (line~\ref{isGameFinished.unfinished}) and finished otherwise.
-
-Suppose now that we would like to unit test this function in isolation to the rest of the application.
-We aim to maximize the branch coverage as a common testing criteria~\cite{why.this.common}.
-That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
-JS function takes \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as the DOM state.
-We assume that DOM is the only global variable that can be referenced in the body of the FUT.
-So in order to produce a complete test for our function we have to construct both an appropriate DOM and input arguments.
-
-%Our program has the following branches: $(6,15)$, $(6,7)$, $(7,9)$, $(7,14)$, $(10,11)$, $(10,13)$, $(16,17)$, $(16,18)$. Four tests in
-
-Figure~\ref{fig.isGameFinished.tests} presents four tests that together deliver the full coverage of the FUT.
-Let us look now at how following the structure of the FUT in Figure~\ref{code.isGameFinished}, we can construct the $T4$ test covering the $(10,11)$ branch.
-Line~\ref{isGameFinished.getSudoku} expects the input DOM to have an element with the id \textquotesingle\texttt{sudoku}\textquotesingle.
-In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, that element should have at least one child \emph{DIV} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires this $div$ to be of the class \textquotesingle\texttt{sudokuSquare}\textquotesingle\ and also have no background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) expects that the $div$ consists of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
-The resulted test $T4$ is shown in Figure~\ref{fig.isGameFinished.tests} and meets all the above conditions.
-
-As we have just seen, even for such a relatively simple example, the construction procedure of a test input is far from trivial because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with the gazillion of the JS frameworks and libraries freely available on the GitHub whose code is commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and, at the same time, it is easiest to implement.
-It greatly saves the developers from unexpected regression and puts a safety belt around the application.
-
-%% --------------------------------------------------------------------
-\section{Test Generation Framework}
-\label{sec.framework}
-%% --------------------------------------------------------------------
-
-\begin{figure}[t!]
-  \centering 
-  \begin{sequencediagram}[font=\scriptsize]
-
-    \renewcommand\unitfactor{0.35}
-    \newinst{user}{\textbf{User}}
-    \newinst{server}{\textbf{Server}}
-    \newinst[1]{validator}{\textbf{Validator}}
-    \newinst{client}{\textbf{Client}}
-
-    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
-      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
-      \end{call}
-
-      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
-      \end{call}
-
-      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}       
-      \end{call}
-
-      \begin{sdblock}{\textbf{Genetic Loop}}{\scriptsize \hspace{8mm}$\text{branch} \in \text{branches}'$}
-        \begin{sdblock}{\textbf{Random Loop}}{\scriptsize errors > 0}
-          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
-          \end{call}
-          \prelevel
-        \end{sdblock}
-
-        \begin{sdblock}{\textbf{Fitness Loop}}{\scriptsize (fitness $\neq$ 0) $\vee$ gen.limit}
-
-          \begin{sdblock}{\textbf{Evaluation Loop}}{\scriptsize p $\in$ pop}
-            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
-            \end{call}
-
-            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
-            \end{callself}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Crossover Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{sdblock}{\textbf{Mutation Loop}}{\scriptsize errors > 0}
-            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
-            \end{call}
-            \prelevel
-          \end{sdblock}
-
-          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
-          \end{callself}
-          \prelevel
-        \end{sdblock}
-        \mess{server}{best fitness}{user}
-
-      \end{sdblock}
-    \end{call}
-  \end{sequencediagram}
-  \caption{The architecture of the test framework}
-  \label{fig.framework.architect} 
-\end{figure}
-
-Given a JS function $f$ and a set of branches $\mathbb{B}_f$, the ultimate goal of the testing framework is to find input arguments for $f$ that cover all branches from $B_f$.
-Our JS testing framework, called \emph{JEDI}, is a client-server application which under the hood uses the genetic engine for test generation.
-The general workflow of the framework is depicted as a sequence diagram in Figure~\ref{fig.framework.architect}.
-The diagram consists of the four interacting components \User, \Server, \Validator, and \Client.
-\Server is the key component of the whole framework.
-It is responsible for the \emph{Initialization Phase} and the \emph{Genetic Phase}.
-Both phases will be covered in details in Section~\ref{sub.sec.init.phase} and \ref{sub.sec.genetic.phase} respectively.
-
-Each newly constructed HTML document has to be processed by the \Validator\footnote{\url{https://validator.w3.org/nu/}} which checks its syntactic correctness and reports back the set of identified errors.
-\Server rejects the document if any errors were revealed and generates a new one until the generated document has no errors anymore.
-\Client is a \emph{Node.js}\footnote{\url{https://nodejs.org/en/}} application that is mainly responsible for the execution of the JS code.
-We use the \emph{jsdom}\footnote{\url{https://github.com/tmpvar/jsdom}} library to model the virtual DOM and simulate the native browser API calls.
-
-\begin{algorithm}[t!]
-  \caption{Initialization Phase}
-  \label{alg.init}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{JS file $fun.js$ with FUT and type annotation }
-  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
-  \Fn{$Initialize(fun.js)$}{
-
-    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
-    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
-    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
-    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
-    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
-    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
-    \Return{$(cfg, branches, cinfo, ifun, sig)$}
-    }
-\end{algorithm}
-
-Let us give a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide the JS file \emph{fun.js} that contains the function under test (FUT) \emph{fun} annotated with the type signature.
-Additionally, \User specifies a configuration file \emph{config} that defines various parameters for random data generation, genetic phase, logging etc.
-Experimentally, we have found an optimal set of input configurations that was used across all experimental objects in Section~\ref{sec.evaluation}.
-This data is processed by the \Server during the \emph{Initialization Phase}.
-As an output, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{ifun}, and the signature (\emph{sig}).
-\Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
-Depends on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
-For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a certain termination criteria is achieved, e.g.
-the limit on the number of generation attempts.
-Each candidate in the population has to be evaluated in \emph{Evaluation Loop} by \Client.
-It matches the candidate $p$ according to the type signature \emph{sig} and invokes the instrumented JS function on it: \emph{ifun(p)}.
-The execution trace along with some supplementary information about the execution are sent back to the \Server, where the final \emph{fitness value} is computed.
-The new population is constructed by combining the results of the \emph{Crossover} and \emph{Mutation Loops}.
-If a new HTML document is produced somewhere in the genetic phase, it has to be first approved by the \Validator.
-At the end of the \emph{Fitness Loop}, the candidate with the ``best'' fitness value is reported back to the \User.
-Once all the branches are exercised, the algorithm reaches the end.
-In the follow up two sections, we elaborate on the details of each individual phase of our test generation framework.
-
-\subsection{Initialization Phase}
-\label{sub.sec.init.phase}
-
-During the \emph{Initialization Phase} we analyze the FUN in order to retrieve the data required for the consecutive genetic testing.
-The main steps of this phase are illustrated by Algorithm~\ref{alg.init}.
-Given a FUT \emph{fun.js} as an input, we parse the function and its type signature in line~\ref{alg.init.parse.fun.sig}.
-In order to maximize the chances of generating the fittest candidate in the genetic phase, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect constant info.
-Such constants include the numeric and string literals, as well as the arguments to the following DOM API methods \texttt{getElementsByTagName}, \texttt{getElementById}, \texttt{getElementsByClassName}, and \texttt{getElementsByName},
-which respectively signify the reference to the \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} encountered in the FUT.
-Next step is normalizing the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
-transform \emph{if-then} branches into \emph{if-then-else}.
-We instrument the FUT (line~\ref{alg.init.instr}) in order to collect the run-time data such as the execution trace, the approach level, the branch and loop distances, and the constants.
-Upon the $ifun$ execution this information is gathered and fed back to the fitness evaluation procedure.
-Finally, we construct the control-flow graph (line~\ref{alg.init.build.cfg}) and identify all branches of the FUT (line~\ref{alg.init.get.branches}).
-
-\subsubsection{Supported Types}
-\label{sub.sec.sup.types}
-
-\begin{figure}[t!]
-\setlength{\grammarparsep}{3pt}
-\small
-\begin{grammar}
-
-<JS Type Annotation> ::= /*t <Signature> */
-
-<Signature> ::= <DOM> : <Type Signature> | <Type Signature>
-
-<DOM> ::= \texttt{dom}
-
-<Type Signature> ::= <Type> | <Type> : <Type Signature>
-
-<Type> ::= <Void Type> | <Primitive Type> | <Array Type>
-
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
-
-<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
-\end{grammar}
-\caption{Grammar of supported JS type annotations}
-\label{fig.js.type.annot}
-\end{figure}
-One assumption made in the paper is the availability of type signatures for JS functions.
-We believe in the legitimacy of such a request due to the following observations.
-First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity.
-Second, there has been an active work on the JS type inference done both in academia~\cite{kristensen2017type} and industry, e.g.
-Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.
-
-The grammar of the JS type annotations supported by our test generation framework is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature embedded into a specialized JS type comment (\texttt{/*t...*/}).
-We distinguish between two kinds of signatures those which refer to the global DOM and the ``ordinary'' JS type signatures.
-The functions of the former signature expect some \texttt{dom} argument to be passed as the first implicit parameter for the function call.
-Whereas ordinary JS signature is a non-zero sequence of the JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
-
-\subsubsection{Instrumentation}
-\label{sub.sec.instrument}
-
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \emph{trace} in line~\ref{isGameFinished.instr.trace} is an array of labels corresponding to the sequence of executed program statements.
-All statements have to be traced because each one, in theory, can rise an exception.
-The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} approximates the potential number of iterations for the consecutive for-loop.
-If no exact bound can be computed, we set it to one.
-The \texttt{branchDistance} map tracks the distances to the deviated branches according to the translation formulae~\cite{tracey1998automated}.
-
-%TODO: maybe expand this section with the JS type casting for branch distance computation
-
-\begin{figure}[t]
-  \begin{lstlisting}[style=htmlcssjs,language=JavaScript]
-function isGameFinished() {
- trace.push(2); |c \label{isGameFinished.instr.trace} |c
- var obj = document.getElementById("sudoku");
- trace.push(3);
- var subDivs = obj.getElementsByTagName("DIV");
- trace.push(4);
- var allOk = true;
- loopMap[5] = function () { |c \label{isGameFinished.instr.loopMap} |c
-   var no = 0;
-   if (subDivs.length || subDivs.length == 0) {
-     return Math.abs(no - subDivs.length);
-   }
-   return 1;
- }();
- trace.push(5);
- for (var no = 0; no < subDivs.length; no++) {
-  trace.push(6);
-  trace.push(7);
-  if (subDivs[no].className.indexOf("sudokuSquare") >= 0 &&
-      !subDivs[no].style.backgroundColor) {
-   trace.push(8);
-   branchDistance.push({ 
-    label: 7, 
-    distance: Math.min(
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + _K_, 
-     absZero(subDivs[no].style.backgroundColor))
-   });
-   trace.push(9);
-   var spans = subDivs[no].getElementsByTagName("SPAN");
-   trace.push(10);
-   if (spans[0].innerHTML != spans[1].innerHTML) {
-    trace.push(11);
-    branchDistance.push({
-     label: 10,
-     distance: abs(spans[0].innerHTML, spans[1].innerHTML)
-    });
-    trace.push(12);
-    allOk = false;
-    break;
-   } else {
-     trace.push(14);
-     branchDistance.push({label: 10,distance: _K_});
-   }
-  } else {
-   trace.push(15);
-   branchDistance.push({
-    label: 7,
-    distance: 
-     abs(subDivs[no].className.indexOf("sudokuSquare"), 0) + 
-     absNegZero(subDivs[no].style.backgroundColor)
-   });
-  }
- }
- trace.push(5);
- trace.push(-1);
-}
-\end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
-  \label{code.isGameFinished.instr}
-\end{figure}
-
-\subsection{Genetic Phase}
-\label{sub.sec.genetic.phase}
-
-\begin{algorithm}[!t]
-  \caption{Genetic Phase}
-  \label{alg.gen}
-  \algsetup{linenosize=\tiny}
-  \scriptsize
-  \DontPrintSemicolon
-  \SetAlgoVlined
-  \SetKwInOut{Input}{Input}
-  \SetKwInOut{Output}{Output}
-  \SetKwInOut{Require}{Require}
-  \SetKwProg{Fn}{Function}{}{}
-  \Input{
-    $config$ is a GA configuration file\\
-    $b_n$ is a target branch of FUT\\
-    $(cfg, branches, cinfo, ifun, sig)$ output of Algorithm~\ref{alg.init}
-  }
-  \Output{
-     $(f^*, p^*)$ the best population candidate and its fitness score
-  }
-  \Fn{$Genetic(b_n, cfg, cinfo, config, ifun, sig)$}{
-    $(size_P, size_A, size_G, rate_C, rate_M,size_{H}) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
-    $target \longleftarrow b_n$\label{alg.gen.init.target}\; 
-    $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
-    $historyConverged \longleftarrow true$\;
-    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
-      $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\; 
-      $history \longleftarrow \emptyset$\label{alg.gen.init.history}\; 
-      $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
-      \Repeat{$isPerfect(f^*) \vee historyConverged \vee (i > size_G)$}{\label{alg.gen.loop.begin}
-        $scoredPop \longleftarrow \emptyset$\;
-        $history \longleftarrow history \cup archive$\;
-        \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
-          $args \longleftarrow CoerceArguments(p, sig)$\label{alg.gen.make.args}\;
-          $(tr, d_B, d_L, dyncinfo) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
-          $f \longleftarrow Score(target, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
-          $cinfo \longleftarrow cinfo \cup dyncinfo$\label{alg.gen.eval.end}\;
-          $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
-        }
-        $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
-        $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
-        $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
-        $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
-        $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
-        $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
-        $i \longleftarrow i + 1$\;
-        $historyConverged \longleftarrow hasConverged(history, size_H)$\label{alg.gen.has.converged}\;
-      }\label{alg.gen.loop.end}
-      $target \longleftarrow NewTarget(branches, b_n)$\label{alg.gen.new.target}\;
-    }\label{alg.gen.converged.loop.end}
-    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
-  }
-\end{algorithm}
-
-The heart of our test data generation framework is in the \emph{Genetic Phase}.
-Though, the main workflow of the underlying genetic algorithm (GA) is fairly standard~\cite{poli2008field}, but has been extended with the concept of the \emph{archive convergence} (Algorithm~\ref{alg.gen}).
-As an input, we take a configuration file \emph{config}, a target branch $b_n$ of the FUT (which we would like to cover), and a tuple of supplementary parameters computed by Algorithm~\ref{alg.init}.
-The output consists of the ``best'' fitness score $f^*$ achieved by the population candidate $p^*$.
-
-First, we read the \emph{config} file (line~\ref{alg.gen.read.config}) and retrieve the following GA configuration parameters: a population size  ($size_P$), an archive size ($size_A$), the number of generations ($size_G$), crossover ($rate_C$) and mutation ($rate_M$) rates respectively, and a history window size ($size_H$).
-We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ equal to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged or the generations limit has not been reached.
-The \emph{archive} variable stores the most fitted population candidates observed so far, and the \emph{history} variables records all archives during the generation process.
-These variables both are empty in the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
-
-The initial population has $size_P$ elements, and it is randomly generated out of the constants from \emph{cinfo} (line~\ref{alg.gen.random.gen}).
-In the loop~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}, this population is evolved until either a perfect candidate has been found or the history has converged or the generation limit $size_G$ has been reached.
-But first, we need to score the current population lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}.
-Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
-Thus, it should to be coerced respectively to the type signature $sig$ (line~\ref{alg.gen.make.args}).
-Afterwards, the instrumented function \emph{ifun} can be called with the coerced arguments $args$ (line~\ref{alg.gen.call.ifun}).
-This gives us 4-tuple consisting of an execution trace ($tr$), branch ($d_B$) and loop distances ($d_L$), and the set of dynamic constants (\emph{dyncinfo}) collected at the run-time.
-The next step is actually computing the fitness value for $p$ (line~\ref{alg.gen.eval}).
-Collected dynamic constants \emph{dyncinfo} are merged with the existing constant pool (line~\ref{alg.gen.eval.end}).
-Eventually, the scored population is combined with the archive (line~\ref{alg.gen.get.combo}).
-And the $combo$ is used for crossover (line~\ref{alg.gen.cross}) and mutation (line~\ref{alg.gen.mut}) steps in order to form the new population (line~\ref{alg.gen.new.pop}).
-Then, the scored population together with the current archive are sorted by the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}).
-The element at the top of the archive is the fittest candidate (line~\ref{alg.gen.archive.head}) of the current population.
-The fitness value of that element defines if a perfect candidate is found (line~\ref{alg.gen.loop.end}).
-Eventually, the tuple $(f^*, p^*)$ is returned by the algorithm (line~\ref{alg.gen.return}) as solution.
-
-In some cases, when we do not get enough guidance from a fitness function, the genetic algorithm converges to a local minimum~\cite{ga.flag.problem.or.survey}.
-For example, if one branch is dominated by another, the coverage of the former depends on the coverage of the latter.
-Unless this relation is encoded in the fitness function somehow, we can not learn about it occasionally.
-In such situation, we find ourselves being trapped on a flat space, with a small unreliable chance to escape.
-In order to overcome this problem, we propose a novel --- to the best of our knowledge --- solution based on the idea of \emph{archive convergence}.
-If during a certain history window, the fitness values of the respective archives have converged to a fixed point, we deem the whole history converged and restart the genetic search with a new search target.
-At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
-If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
-It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
-Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
-In practice, we only consider the target extensions upto the length of two.
-
-The genetic operations used for the primitive JS types and arrays are summarized in Table~\ref{tbl.gen.oper.js.types}.
-In the rest of this section, we reveal the implementation details of random generation in Section~\ref{sub.sub.sec.random.html}, crossover and mutation in Section~\ref{sub.sub.sec.genetic.oper}, and fitness function in Section~\ref{sub.sub.sec.fitness.fun}.
-Our main focus in those sections is on the generation and transformation of HTML documents.
-
-\begin{table}
-  \caption{Genetic Operation for the JS Types}
-  \label{tbl.gen.oper.js.types}
-    \footnotesize
-  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
-    \toprule
-    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
-    \hline
-    Random    & Bool   & choose at random \{\texttt{true}, \texttt{false}\} \\
-    Random    & Int    & choose at random [-10, 10] or constants with the ratio 4:1\\
-    Random    & Float  & choose at random [-10.0, 10.0] or constants with the ratio 4:1\\
-    Random    & String & >5 chars from $\texttt{[a-zA-Z0-9]}$ or constants with the ratio 4:1\\
-    Random    & Array  & array of a respective type upto length five\\
-    \hline
-    Crossover & Bool   & pick at random one out of two given booleans \\
-    Crossover & Int    & pick at random one out of two given integers\\
-    Crossover & Float  & pick at random one out of two given floats\\
-    Crossover & String & pick at random one out of two single point crossovers\\
-    Crossover & Array  & similar crossover operator as for strings\\
-    \hline
-    Mutation  & Bool   & flip the boolean constant\\
-    Mutation  & Int    & random integer, $\pm 1$ or $\pm 10$\\
-    Mutation  & Float  & random float, $\pm 0.1$, $\pm 1$ or $\pm 10$\\
-    Mutation  & String & random string, remove char or apply pred(suc) char\\
-    Mutation  & Array  & Mutate a random element in array according to its type\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsubsection{Random HTML Generation}
-\label{sub.sub.sec.random.html}
-
-\begin{figure}[t]
-  \begin{haskell}
-instance Arbitrary Html where
-  arbitrary = evalStateT generateHTML defaultState
-
-generateHTML :: GenHtmlState |c \label{ref.generateHTML.begin} |c
-generateHTML = do
-  state <- get |c \label{ref.generateHTML.getState} |c   
-  let d = getDepth state |c \label{ref.generateHTML.getDepth} |c
-  if d == 0
-  then lift \dollar return \dollar toHtml "HTML" |c \label{ref.generateHTML.returnString} |c
-  else do put state{depth = d - 1} |c \label{ref.generateHTML.updateState} |c
-           head <- generateHEAD |c \label{ref.generateHTML.newHead} |c
-           body <- generateBODY |c \label{ref.generateHTML.newBody} |c
-           lift\dollar return \dollar docTypeHtml \dollar head >> body |c \label{ref.generateHTML.end} |c
-
-data Tag = HTML | HEAD | BODY | ...
-type Context = CFlow | CMetadata | ...
-data HtmlState = |c \label{ref.HtmlState.begin} |c
-  HtmlState { depth    :: Int,           degree  :: Int    
-             , ctx     :: Stack Context, tagFreq :: [(Int, Tag)] 
-             , tags    :: [Tag],         ids     :: [String]
-             , classes :: [String] } |c \label{ref.HtmlState.end} |c
-type GenState s = StateT s Gen |c \label{ref.GenState} |c
-type GenHtmlState = GenState HtmlState Html |c \label{ref.GenHtmlState} |c
-  \end{haskell}
-  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
-  \label{fig.html.arb.def}
-\end{figure}
-
-We want to generate HTML according to the WHATWG\footnote{\url{https://html.spec.whatwg.org}} specification.
-HTML is an XML-family markup language that uses special tags and attributes to describe document structures on the Web.
-The recent HTML5 standard defines more than hundred of tags and attributes which both have to comply with extremely complex logic to constitute a syntactically valid HTML.
-Browsers are usually tolerant to syntactic errors in HTML.
-They will silently fix them and display the page anyway.
-
-In order to support the variability of HTML content, we have developed an eDSL that prescribes the generation of syntactically valid HTML.
-This was a challenge on its own because, as we have mentioned early, the complexity of HTML and the lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
-With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} highlights that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) describes the internal state of \texttt{Html} in the generation.
-The state is composed of the following components:
-\begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of HTML 
-\item \texttt{ctx} is the current value of the HTML content model stack 
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
-\end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag should be defined as the value of the \texttt{GenHtmlState} type.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to its specification\footnote{\url{https://html.spec.whatwg.org/multipage/semantics.html\#the-html-element}}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
-First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
-Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the new contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
-
-\subsubsection{Genetic HTML Operations}
-\label{sub.sub.sec.genetic.oper}
-
-In essence, HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for the \emph{expression trees} in genetic programming.
-
-\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
-
-\textbf{HTML Mutations} are of the three categories: \emph{NewTree}, \emph{DropTree}, and \emph{ShuffleAttributes}.
-The \emph{NewTree} mutation simply generates a new tree based on a given state of the constant pool.
-The \emph{DropTree} mutation removes the whole sub-tree at a randomly chosen node.
-\emph{ShuffleAttributes} re-assigns all attributes of a given type on a tree.
-Currently, we instantiated the \emph{ShuffleAttributes} mutation for only for tho types \emph{class} and \emph{id}.
-In total, this gives us four mutations to chose from in order to evolve an Html document.
-
-\subsubsection{Fitness Function}
-\label{sub.sub.sec.fitness.fun}
-
-The success of any search-based algorithm heavily relies on the right choice of the fitness function (FF) that guides the evolution process.
-Our search target is a specific branch of the function under test that we want to cover by generating a valid input data.
-The input is \emph{valid} only if it leads the program to a \emph{normal termination}, i.e.
-without premature exception.
-Our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}\cite{arcuri2010does}.
-\[
-\textit{fit}(n) = \text{approach level} +
-\begin{cases}
- 1/2 * (\frac{\text{branch distance}}{1 + \text{branch distance}}) & \text{if no exception}\\
- 1                                  &  \text{otherwise}
-\end{cases}
-\]
-Final FF ($\textit{fit}^*$) is an ordered pair of the FFs of the respective nodes.   
-\[
-\textit{fit}^*(n_b, n_x) = (\textit{fit}(n_b), \textit{fit}(n_x))
-\]
-Similarly, this definition can be extended to an arbitrary sequence of CFG nodes $(n_1, n_2, \ldots, n_k)$:
- \[
-\textit{fit}^*(n_1, n_2, \ldots, n_k) = (\textit{fit}(n_1), \textit{fit}(n_2), \ldots, \textit{fit}(n_k))
-\]
-
-The approach level is an integer value that indicates how many conditions should be met in order to reach the \emph{problem node}, i.e.
-the node caused the deviation.
-Since any node can potentially be exceptional, they all contribute to the approach level in addition to the conditional branches.
-Loops have to treated in a special way because we need to estimate the maximum number of iterations.
-In the case of for-loop, at run-time we can always provide an exact bound.
-For while-loops, we assume that it has to be passed at least once.
-The branch condition is a rational value from 0 to 1, which measures the deviation explicitly in the problem node and it is computed according to the formulae~\cite{tracey1998automated}.
-
-\subsubsection{Limitations}
-\label{sub.sub.sec.limit}
-
-Currently, our framework imposes certain explicit constraints on the kind of JS functions it is able to process: 
-\begin{enumerate}
-\item ability to assign static types to input parameters 
-\item no support for the \emph{Object} type, heterogeneous arrays and high-order functions
-\item no support for recursion
-\item doesn't perform inter-procedural analysis
-\item no support for JS frameworks
-\item no reference to global variables and functions
-\item limited support of DOM API     
-\end{enumerate}
-
-%% --------------------------------------------------------------------
-\section{Empirical Evaluation}
-\label{sec.evaluation}
-%% --------------------------------------------------------------------
-
-In order to evaluate the feasibility of our test framework adoption in practice, we conducted an empirical evaluation on a set of case-studies described in Section~\ref{sub.sec.case.studies}.
-All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm.
-The first version, which play the role of our baseline, is \emph{Random} ($\Random$).
-Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch.
-It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation.
-The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}.
-The last version is the \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
-On one hand, the smaller window size forces the GA to converge faster and early discovers the stagnation on a flat space.
-On the other hand, the small window can lead to a premature archive convergence, which prevents the right genetic combination from been triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose it to report in the paper.
-Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
-\emph{EvoSuite}~\cite{fraser2011evosuite}.
-
-\begin{table}
-  \caption{Genetic Algorithm Configurations}
-  \label{tbl.gen.config}
-    \scriptsize
-  \begin{tabular}{l|r|r|r}
-    \toprule
-    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
-    \hline
-    Population size                   & 50  & 50  & 50  \\
-    Archive size                      & 1   & 25  & 25  \\
-    Maximum number of generations     & 200 & 200 & 200 \\
-    Crossover rate                    & 0   & 0.5 & 0.5 \\
-    Mutation rate                     & 0   & 0.5 & 0.5 \\
-    History window size               & -   & -   & 10  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-By carrying the evaluation, we would like to address the following research questions:
-\begin{description}
-\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework?
-Which testing algorithm is the most effective?
-How the effectiveness changes with the budget per branch?
-\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost of one iteration?
-\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
-\end{description}
-
-\subsection{Case Studies}
-\label{sub.sec.case.studies}
-
-Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless number of specialized libraries, and greatly vary in size, complexity and coding style.
-Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation.
-Before selection, the source code of a potential case-study has to be scrutinized which is time consuming and labor intensive process.
-Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}.
-Both of these works address the problem of testing of JS application with the reference to the browser DOM.
-We introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}} to increase the presence of primitive (browserless) JS code.
-For each case-study application, we identified several JS functions that are suitable for our testing framework.
-In the end, our evaluation set included both primitive and DOM related JS functions.
-
-For the sake of space, we chose to exclude from the follow up presentation the branches and functions which coverage time was less than two seconds.
-In all those cases, the three algorithms studied here have shown equally good results by finding a solution within the first iteration --- random generation.
-This left us with only 7 case studies contributing to the total number of 14 functions  shown in~Table~\ref{tbl.case.studies}.
-For each function, we reported the following software metrics\footnote{\url{http://jsmeter.info/} is the tool used for measuring JS code statistics}: lines of code~(\textbf{LOC}), number of branches~(\textbf{BR}), depth~(\textbf{D}), and cyclomatic complexity~(\textbf{CC}).
-The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulate with \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.
-To answer the research questions posed in the beginning of Section~\ref{sec.evaluation}, we evaluated our test generation framework on the aforementioned case studies with the results presented in Section~\ref{sub.sec.eval.results}.
-
-\setlength\tabcolsep{0.6pt}
-\begin{table}[t]
-  \caption{Summary of the Case-Studies}
-  \label{tbl.case.studies}
-  %\resizebox{\textwidth}{!}{
-    \scriptsize
-  \begin{tabular}{l|l|p{3.1cm}|c|c|c|c|c|c|c|c}
-    \toprule
-    \textbf{case-study} & \textbf{function} & \textbf{type signature} & \textbf{LOC} & \textbf{BR} & \textbf{D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
-    \hline
-    sudoku     & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
-    sudoku     & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & + & + & + & + \\
-    sudoku     & newGame & (dom)           & 9  & 1 & 2 & 2 & + & + & + & + \\
-    sudoku     & revealAll & (dom)         & 8  & 0 & 2 & 1 & + & + & + & - \\
-    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
-    sudoku     & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & + & - & + & - \\
-    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
-    \hline
-    phormer    & toggleInfo & (dom,string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
-    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
-    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
-    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
-    hotel RS   & isValidCard & ([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
-    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
-    hotel RS   & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
-    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
-    \hline
-    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
-    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
-    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
-    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
-    apophis    & initShields & (dom,[int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
-    \hline
-    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
-    bingbong   & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
-    bingbong   & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & + & + & - & - \\
-    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
-    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
-    \hline
-    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
-    %% \hline
-    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
-    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\ 
-    \hline
-    mathjs     & prob\_gamma & (float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
-    \bottomrule
-  \end{tabular}
-%}
-\end{table}
-
-\subsection{Results}
-\label{sub.sec.eval.results}
-
-\setlength\tabcolsep{.98pt}
-\begin{table}[!t]
-  \caption{Statistics of experimental results for three testing algorithms $\Random$, $\Genetic$ and $\RGenetic$ (time $t$ is in seconds; \underline{200} indicates branch is not covered; (-) means the data is insignificant).}
-  \label{tbl.stats}
-    \scriptsize
-    \begin{tabular}{l|ccc|ccc|ccc|ccc|ccc}
-      \toprule
-      \multirow{2}{*}{\textbf{NAME}} &   \multicolumn{3}{c|}{$m_{\Random}$} & \multicolumn{3}{c|}{$m_{\Genetic}$} & \multicolumn{3}{c|}{$m_{\RGenetic}$} & \multirow{2}{*}{$\frac{t_{\Random}}{t_{\Genetic}}$} &  \multirow{2}{*}{$\frac{t_{\Random}}{t_{\RGenetic}}$} & \multirow{2}{*}{$\frac{t_{\Genetic}}{t_{\RGenetic}}$}   & \multirow{2}{*}{\hfil $_{\Genetic}^{\Random}$} &  \multirow{2}{*}{\hfil $_{\RGenetic}^{\Random}$} & \multirow{2}{*}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{2-10} % \!:\!
-                             & $i$      & $t$  & $t/i$     & $i$& $t$&$t/i$             &$i$ &$t$ &$t/i$               &      &       &        &      &       &      \\
-      \midrule
-    \textbf{helpMe}*         & 218      & 270  & 1.24      & 61 & 47 & 0.77             & 62 & 56 & 0.9                & 5.74 & 4.82  & 0.84   &      &      &       \\
-    $(3,4,\inFor)$           & 4        & 4    & 1         & 5  & 3  & 0.6              & 8  & 6  & 0.75               & 1.33 & 0.67  & 0.5    & - & 0.39 & 0.37  \\
-    $(5,6,\thenBr)$          & 4        & 5    & 1.25      & 8  & 6  & 0.75             & 7  & 5  & 0.71               & 0.83 & 1     & 1.2    & - & -  & -  \\
-    $(5,15,\elseBr)$         & 121      & 156  & 1.29      & 24 & 21 & 0.86             & 23 & 24 & 1.04               & 7.43 & 6.5   & 0.88   & 0.87 & 0.86 & -  \\
-    $(9,10,\thenBr)$         & 85       & 101  & 1.19      & 18 & 14 & 0.78             & 19 & 17 & 0.89               & 7.21 & 5.94  & 0.82   & 0.98 & 0.95 & -  \\
-    $(9,14,\elseBr)$         & 4        & 4    & 1         & 6  & 4  & 0.67             & 5  & 4  & 0.8                & 1    & 1     & 1      & - & - & -  \\
-    \hline                                                                                                          
-    \textbf{isGameFinished}* & 264      & 220  & 0.83      & 32 & 30 & 0.94             & 43 & 43 & 1                  & 7.33 & 5.12  & 0.7    &      &      &        \\
-    $(7,8,\thenBr)$          & 37       & 30   & 0.81      & 8  & 8  & 1                & 12 & 13 & 1.08               & 3.75 & 2.31  & 0.62   & -  & 0.66 & -   \\
-    $(10,11,\thenBr)$        & \un{200} & 167  & 0.84      & 11 & 10 & 0.91             & 10 & 11 & 1.1                & 16.7 & 15.18 & 0.91   & 0.88 & 0.96 & -   \\
-    $(10,14,\elseBr)$        & 25       & 21   & 0.84      & 11 & 11 & 1                & 19 & 18 & 0.95               & 1.91 & 1.17  & 0.61   & - & - & -   \\
-    \hline
-    \textbf{newGame}*   
-                             & 18       & 14   & 0.78      & 11 & 9  & 0.81             & 10 & 10 & 1                  & 1.56 & 1.4   & 0.9    &      &      &      \\
-    $(6,7,\thenBr)$          & 16       & 12   & 0.75      & 9  & 7  & 0.78             & 8  & 8  & 1                  & 1.71 & 1.5   & 0.88   & 0.64 & 0.65 & -  \\
-    \hline
-    \textbf{revealAll}*  
-                             & 60       & 50   & 0.83      & 44 & 44 & 1                & 47 & 53 & 1.13               & 1.14 & 0.94  & 0.83   &      &      &        \\
-    $(2,3,\inFor)$           & 25       & 20   & 0.8       & 24 & 24 & 1                & 24 & 27 & 1.13               & 0.83 & 0.74  & 0.89   & - & - & -  \\
-    $(4,5,\inFor)$           & 35       & 30   & 0.86      & 20 & 20 & 1                & 23 & 26 & 1.13               & 1.5  & 1.15  & 0.77   & 0.62 & -   &  0.37  \\
-    \hline
-    \textbf{shuffleBoard}*   
-                             & 15       & 29   & 1.93      & 15 & 26 & 1.73             & 17 & 29 & 1.71               & 1.12 & 1     & 0.9    &      &      &       \\
-    $(13,14,\thenBr)$        & 5        & 10   & 2         & 5  & 9  & 1.8              & 6  & 10 & 1.67               & 1.11 & 1     & 0.9    & - & - & -  \\
-    $(17,18,\thenBr)$        & 5        & 10   & 2         & 5  & 10 & 2                & 6  & 11 & 1.83               & 1    & 0.91  & 0.91   & - & - & -   \\
-    \hline
-   \textbf{toggleInfo}*      & 6        & 6    & 1         & 7  & 7 & 1                 & 9 & 6   & 0.66               & 0.86  & 1     & 1.17  &    &      &       \\
-    $(6,7,\thenBr)$          & 2        & 2    & 1         & 3  & 3 & 1                 & 5 & 3   & 0.6                & 0.67  & 0.67  & 1     & 0.37 & 0.36 & -  \\
-    \hline
-   \textbf{isValidCard}      & 1001     & 514  & 0.51      & 21 & 8 & 0.38              & 21 & 10 & 0.48               & 64.25 & 51.4  & 0.8    &   &   &       \\
-    $(3,6,\elseBr)$          & \un{200} & 103  & 0.52      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51.5  & 51.5  & 1      & 1 & 1 & -   \\
-    $(7,8,\inFor)$           & \un{200} & 103  & 0.52      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 103   & 51.5  & 0.5    & 1 & 1 & -  \\
-    $(10,11,\thenBr)$        & \un{200} & 102  & 0.51      & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 51    & 51    & 1      & 1 & 1 & -  \\
-    $(10,13,\elseBr)$        & \un{200} & 106  & 0.53      & 4  & 1 & 0.25              & 4  & 2  & 0.5                & 106   & 53    & 0.5    & 1 & 1 & -  \\
-    $(14,15,\inFor)$         & \un{200} & 100  & 0.5       & 4  & 2 & 0.5               & 4  & 2  & 0.5                & 50    & 50    & 1      & 1 & 1 & -  \\
-    \hline
-   \textbf{isValidVISA}      & 201      & 95   & 0.47      & 8  & 3 & 0.38              & 8  & 2  & 0.25               & 31.67 & 47.5  & 1.5    &   &   &       \\
-    $(2,3,\thenBr)$          & \un{200} & 95   & 0.48      & 7  & 3 & 0.43              & 7  & 2  & 0.29               & 31.67 & 47.5  & 1.5    & 1 & 1 & -  \\
-    \hline
-   \textbf{initShields}*     & 6        & 5    & 0.83      & 6  & 5 & 0.83              & 6  & 3  & 0.5                & 1      & 1.67 & 1.67   &      &      &       \\
-    $(2,3,\inFor)$           & 6        & 5    & 0.83      & 6  & 4 & 0.67              & 6  & 3  & 0.5                & 1.25   & 1.67 & 1.33   & 0.83 & 0.84 & -  \\
-    \hline
-   \textbf{brickJiggler}*    & 7        & 8    & 1.14      & 6  & 4 & 0.67              & 4  & 3  & 0.75               & 2      & 2.67 & 1.33   &      &      &       \\
-    $(2,3,\thenBr)$          & 6        & 7    & 1.17      & 5  & 3 & 0.6               & 3  & 2  & 0.67               & 2.33   & 3.5  & 1.5    & 0.83 & 0.85 & -  \\
-    \hline
-   \textbf{doPaddlePower}*   & 19       & 15   & 0.79      & 204  & 140 & 0.69          & 25 & 16  & 0.64              & 0.11   & 0.94 & 8.75   &       &      &      \\
-    $(10,11,\thenBr)$        & 16       & 12   & 0.75      & \un{200} & 136 & 0.68      & 22 & 13  & 0.59              & 0.09   & 0.92 & 10.46  &  0.02 & - & 0.94 \\
-   \midrule
-    \textbf{TOTAL (simple)}          & 1816      & 1226 & 0.68      & 415 & 323 & 0.78          & 252 & 231 & 0.92              & 3.8    & 5.31  & 1.4       &   &   &    \\  
-    \bottomrule
-   \textbf{initBricks}*      & 1418     & 2379 & 1.68      & 593  & 474 & 0.8           & 422 & 415 & 0.98             & 5.02   & 5.73  & 1.14   &      &      &       \\
-    $(6,7,\thenBr)$          & 2        & 3    & 1.5       & 5    & 4   & 0.8           & 3   & 3   & 1                & 0.75   & 1     & 1.33   & - & -  & -   \\
-    $(6,10,\elseBr)$         & 15       & 23   & 1.53      & 6    & 6   & 1             & 6   & 6   & 1                & 3.83   & 3.83  & 1      & 0.87 & 0.83 & -   \\
-    $(11,12,\thenBr)$        & \un{200} & 317  & 1.59      & 14   & 12  & 0.86          & 17  & 15  & 0.88             & 26.41  & 21.13 & 0.8    & 0.93 & 0.91 & -  \\
-    $(11,15,\elseBr)$        & 18       & 30   & 1.67      & 6    & 6   & 1             & 6   & 6   & 1                & 5      & 5     & 1      & 0.89 & 0.86 & -  \\
-    $(16,17,\thenBr)$        & \un{200} & 324  & 1.62      & 17   & 14  & 0.82          & 17  & 16  & 0.94             & 23.14  & 20.25 & 0.88   & 0.96 & 0.96 & -  \\
-    $(16,20,\elseBr)$        & 25       & 40   & 1.6       & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.71   & 5.71  & 1      & 0.89 & 0.86 & -  \\
-    $(21,22,\thenBr)$        & \un{200} & 310  & 1.55      & 14   & 13  & 0.93          & 17  & 17  & 1                & 23.85  & 18.24 & 0.76   & 0.94 & 0.9  & 0.36  \\
-    $(21,25,\elseBr)$        & 26       & 41   & 1.58      & 7    & 7   & 1             & 8   & 7   & 0.88             & 5.86   & 5.86  & 1      & 0.94 & 0.87 & -  \\
-    $(29,30,\thenBr)$        & \un{200} & 330  & 1.65      & 66   & 58  & 0.88          & 74  & 70  & 0.95             & 5.69   & 4.71  & 0.83   & 0.82 & 0.88 & -   \\
-    $(29,37,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & - & - & -  \\
-    $(38,39,\thenBr)$        & 185      & 328  & 1.77      & 85   & 67  & 0.79          & 48  & 44  & 0.92             & 4.9    & 7.45  & 1.52   & 0.87 & 0.88 & -  \\
-    $(38,46,\elseBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & 0.64 & - & -  \\
-    $(47,48,\thenBr)$        & 187      & 336  & 1.8       & \un{200} & 141 & 0.7       & 127 & 131 & 1.03             & 2.38   & 2.56  & 1.08   & 0.8  & 0.8  & -  \\
-    $(47,55,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.66 & 0.61 & -  \\
-    $(56,57,\thenBr)$        & 109      & 198  & 1.82      & 50   & 43  & 0.86          & 49  & 47  & 0.96             & 4.6    & 4.21  & 0.91   & 0.76 & 0.75 & -   \\
-    $(56,64,\elseBr)$        & 2        & 4    & 2         & 3    & 3   & 1             & 3   & 4   & 1.33             & 1.33   & 1     & 0.75   & 0.64 & 0.61 & -  \\
-    $(69,70,\thenBr)$        & 2        & 4    & 2         & 3    & 4   & 1.33          & 3   & 4   & 1.33             & 1      & 1     & 1      & - & - & -  \\
-    $(69,71,\elseBr)$        & 41       & 81   & 1.98      & 95   & 84  & 0.88          & 27  & 26  & 0.96             & 0.96   & 3.12  & 3.23   & - & 0.68 & 0.61  \\
-    \hline
-    \textbf{do\_draw}        & 268      & 625  & 2.33      & 383  & 1295 & 3.38         & 124 & 334 & 2.69             & 0.48   & 1.87  & 3.88   &      &      &       \\
-    $(6,7,\thenBr)$          & 8        & 19   & 2.38      & 6    & 25   & 4.1          & 7   & 20  & 2.86             & 0.76   & 0.95  & 1.25   & - & -  &  0.62 \\
-    $(8,9,\thenBr)$          & 10       & 23   & 2.3       & 6    & 17   & 2.83         & 7   & 21  & 3                & 1.35   & 1.1   & 0.81   & 0.63 & 0.62 &  - \\
-    $(8,11,\elseBr)$         & 144      & 343  & 2.39      & 17   & 51   & 3            & 19  & 57  & 3                & 6.73   & 6.02  & 0.89   & 0.91 & 0.91 &  - \\
-    $(44,45,\thenBr)$        & 57       & 144  & 2.5       & \un{200} & 681  & 3.4      & 40  & 111 & 2.78             & 0.21   & 1.3   & 6.14   & 0.16 & - &  0.89 \\
-    $(48,49,\thenBr)$        & 26       & 68   & 2.61      & 137  & 492  & 3.59         & 34  & 97  & 2.85             & 0.14   & 0.7   & 5.07   & 0.24 & - &  0.74 \\
-    \hline
-    \textbf{prob\_gamma}     & 2006     & 710  & 0.35      & 163 & 84   & 0.52          & 162 & 81  & 0.5              & 8.45   & 8.77  & 1.04   &  &   &        \\
-    $(4,5,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,7,\thenBr)$          & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(6,9,\elseBr)$          & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(10,11,\thenBr)$        & \un{200} & 72   & 0.36      & 62  & 42   & 0.68          & 61  & 40  & 0.66             & 1.71   & 1.8   & 1.05   & 1 & 1 &  -  \\
-    $(10,13,\elseBr)$        & \un{200} & 71   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 71     & 71    & 1      & 1 & 1 &  -  \\
-    $(16,17,\inWhile)$       & \un{200} & 70   & 0.35      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 70     & 70    & 1      & 1 & 1 &  -  \\
-    $(20,21,\thenBr)$        & \un{200} & 70   & 0.35      & 6   & 2    & 0.33          & 6   & 3   & 0.5              & 35     & 23.33 & 0.67   & 1 & 1 &  -  \\
-    $(20,23,\elseBr)$        & \un{200} & 72   & 0.36      & 2   & 1    & 0.5           & 2   & 1   & 0.5              & 72     & 72    & 1      & 1 & 1 &  -  \\
-    $(30,31,\thenBr)$        & \un{200} & 72   & 0.36      & 53  & 23   & 0.43          & 52  & 22  & 0.42             & 3.13   & 3.27  & 1.05   & 1 & 1 &  -  \\
-    $(34,35,\thenBr)$        & \un{200} & 72   & 0.36      & 24  & 10   & 0.42          & 25  & 10  & 0.4              & 7.2    & 7.2   & 1      & 1 & 1 &  -  \\
-    \midrule
-    \textbf{TOTAL (diff.)}           & 3692     & 3714 & 1         & 1139 & 1853 & 1.63         & 708 & 830 & 1.17             & 2      & 4.47  & 2.23   &   &   &    \\
-    %% \midrule
-    %% \midrule
-    \bottomrule
-    \bottomrule  
-    \textbf{TOTAL (global)} & 5507      & 4940 & 0.9       & 1554 & 2176 & 1.4          & 966 & 1061 & 1.1             & 2.27   & 4.66  & 2.05       &   &   &    \\  
-    \bottomrule
-    \end{tabular}
-\end{table}
-
-To study the effectiveness and efficiency of our test generation framework, including three test algorithms Random~($\Random$), Genetic~($\Genetic$) and Genetic with Restart~($\RGenetic$), we exercised each algorithm against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments were repeated 50 times to achieve statistical significance.
-Table~\ref{tbl.stats} contains results of our evaluation.
-For each algorithm, we computed the following median values per branch: the number of iterations~($i$), time in seconds~($t$), and their ratio~($t/i$).
-In the table, these values are grouped into three columns $m_{\Random}$, $m_{\Genetic}$ and $m_{\RGenetic}$ according to the algorithm type $\Random$, $\Genetic$ and $\RGenetic$.
-Next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-Inline with the function name, we also present accumulated statistics for the function as a whole.
-Because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function.
-
-According to the industry standard~\cite{bray1997c4}, functions with the CC below 10 are considered easy to test, and above 10 present a reasonable challenge.
-We call the functions of the first type ``simple'', and ``difficult'' otherwise.
-The three functions \emph{initBricks}, \emph{do_draw} and \emph{prob_gamma} at the bottom of Table~\ref{tbl.case.studies} are difficult with the respective the CC 13, 14 and 16.
-Table~\ref{tbl.stats.sum} summarizes the total results of the experiment such as coverage, execution time per branch and significance.
-
-\begin{table}[!t]
-  \caption{Result Summary (L - large, M - medium, S - small)}
-  \label{tbl.stats.sum}
-    \footnotesize
-    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
-      \toprule
-      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
-      \cline{2-16}
-                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
-      \cline{8-16}
-                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
-      \midrule
-      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
-      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
-      \midrule
-      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
-      \bottomrule
-    \end{tabular}
-\end{table}
-
-\paragraph{\textbf{RQ1 (effectiveness).}} To answer this question, we report on the branch coverage achieved by each testing algorithm in our empirical study.
-Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
-The values in Table~\ref{tbl.stats} highlighted as $\underline{200}$ indicate branches which on average were not covered by the respective algorithms.
-The main reason for the random generation ($\Random$) to fail is the large size of the search space and the lack of any feedback in the generation process, e.g.
-branch $(10,11)$ of the \emph{isGameFinished} function.
-In the case of genetic approach~($\Genetic$), it may get stuck at a plateau because the fitness function does not provide sufficient heuristic information, whereas $\Random$ can escape the plateau by chance.
-We encountered three of such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-Those three examples motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines strengths of both algorithms genetic and random.
-It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
-As our evaluation has shown, $\RGenetic$ not only manged to cover the three problematic branches and outperform $\Random$, but it also improved some of the genetic search results, e.g.
-branch $(69,71)$ of the \emph{initBricks} function.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
-  }
-}
-
-\begin{figure}[!t]
-  \begin{tikzpicture}[scale=0.5]
-    \begin{axis}[
-        xlabel={Time budget per branch (seconds)},
-        ylabel={Number of covered branches},
-        xmin=0, xmax=150,
-        ymin=10, ymax=58,
-        xtick={0,5,10,30,60,90,120,150,180},
-        ytick={0,10,20,30,40,50},
-        legend pos=south east,
-        ymajorgrids=true,
-        % xmajorgrids=true,
-        grid style=dashed,
-        label style={font=\huge}
-      ]
-
-      \addplot[
-        color=blue,
-        mark=square*,
-      ] coordinates {
-        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
-      }; 
-      \addplot[
-        color=red,
-        mark=triangle*,
-      ]  coordinates {
-        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
-      };
-      \addplot[
-        color=yellow,
-        mark=*,
-      ]   coordinates {
-        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
-      };
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Progress of the branch coverage given fix time budget per branch}
-    \label{fig.budget.progress}
-\end{figure}
-
-Additionally, we would like to investigate how the coverage progresses with the increase of budget assigned per branch.
-This experiment models different testing scenarios, used in practice, which are time depended.
-E.g.
-running tests inside IDE should be fast; as part of the CI cycle we may afford a large waiting time; regression testing over night may take hours.
-Figure~\ref{fig.budget.progress} illustrates the progress of algorithms across various budget categories from 5 to 150 seconds per branch.
-Random test generation consistently underperforms the genetic one across all budget categories by at least factor of two.
-Eventually, it converges around 52\% coverage.
-Given 5 seconds per branch, both $\Genetic$ and $\RGenetic$ equally perform at the rate of 45\%.
-When the budget increases towards 10 seconds, $\Genetic$ slightly outperforms $\RGenetic$, 60\% against 63\% respectively.
-But when the budget rises to 30 seconds, $\RGenetic$ starts to transcend $\Genetic$ and the distance between them keeps growing further with the budget increase (starting from 120 seconds).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-Our recommendation is to use $\Genetic$ for rapid testing during development, and later in integration testing switch to $\RGenetic$ since it is able to reach harder to cover branches.
-  }
-}
-
-\paragraph{\textbf{RQ2 (efficiency).}}
- To answer this question, we compare the actual execution time shown by our test algorithms in the experiments.
-Based on this information, we suggest an estimate on the execution time of the testing framework.
-The bar chart in Figure~\ref{fig.gen.time.comp} illustrates how the median coverage time varies for each algorithm at the function level.
-There are only two cases, \emph{revealAll} and \emph{doPaddlePower} out of 14, where $\Random$ just slightly outperformed $\RGenetic$ by 6\%, and two more cases \emph{shuffleBoard} and \emph{toggleInfo}, where they performed equally.
-In all other cases, $\RGenetic$ significantly outperformed $\Random$ by minimum 40\%~(\emph{newGame}) and maximum 510\%~(\emph{isValidCard}).
-
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[scale=0.8]
     \begin{axis}[
@@
         width=11cm,height=3.3cm,
-        bar width=3pt,
+        bar width=4pt,
         enlarge x limits=0.05,
-        legend style={at={(0.05,1.1)},anchor=north west,font=\footnotesize,legend columns=-1},
+        legend style={rotate=45,anchor=north west,font=\footnotesize,legend columns=-1,at={(0.05,1.1)}},
         legend cell align={left},
@@
         clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
+        x tick label style={rotate=90,anchor=east,font=\footnotesize\bfseries},
         y tick label style={font=\footnotesize}
@@
   \end{tikzpicture}
-  \caption{Overall test generation time per function.}
-  \label{fig.gen.time.comp}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{tikzpicture}[scale=0.8]
-    \begin{axis}[
-        every axis plot post/.style={/pgf/number format/fixed},
-        ybar,
-        ymin=0,ymax=4,
-        width=11cm,height=3.3cm,
-        bar width=3pt,
-        enlarge x limits=0.05,
-        legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-        legend cell align={left},
-        ylabel={time (sec.)},
-        symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-        xtick=data,
-        nodes near coords,
-        every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-        % every node near coord/.append style={font=\footnotesize},
-        axis lines*=left,
-        clip=false,
-        x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-        y tick label style={font=\footnotesize}
-      ]
-      \addplot[fill=blue] coordinates {(helpMe*,1.24) (isGameFinished*,0.83) (newGame*,0.78) (revealAll*,0.83) (shuffleBoard*,1.93) (toggleInfo*,1) (isValidCard,0.51) (isValidVISA,0.47) (initShields*,0.83) (brickJiggler*,1.14) (doPaddlePower*,0.79)  (initBricks*,1.68) (do\_draw,2.33) (prob\_gamma,0.35)};
-      \addplot[fill=red] coordinates {(helpMe*,0.77)  (isGameFinished*,0.94)  (newGame*,0.81)  (revealAll*,1) (shuffleBoard*,1.73) (toggleInfo*,1) (isValidCard,0.38)   (isValidVISA,0.38)  (initShields*,0.83) (brickJiggler*,0.67) (doPaddlePower*,0.69) (initBricks*,0.8) (do\_draw,3.38) (prob\_gamma,0.52)};
-      \addplot[fill=yellow] coordinates {(helpMe*,0.9)  (isGameFinished*,1)  (newGame*,1) (revealAll*,1.13) (shuffleBoard*,1.71) (toggleInfo*,0.66) (isValidCard,0.48)  (isValidVISA,0.25)  (initShields*,0.5) (brickJiggler*,0.75) (doPaddlePower*,0.64) (initBricks*,0.98) (do\_draw,2.69) (prob\_gamma,0.5)};
-      \legend{$\Random$,$\Genetic$,$\RGenetic$}
-    \end{axis}
-  \end{tikzpicture}
-  \caption{Speed of test generation measured as $t/i$}
-    \label{fig.get.cost}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \begin{tikzpicture}[scale=0.8]
-%%     \begin{axis}[
-%%         every axis plot post/.style={/pgf/number format/fixed},
-%%         ybar,
-%%         ymin=0,ymax=135,
-%%         width=11cm,height=3.3cm,
-%%         bar width=3pt,
-%%         enlarge x limits=0.05,
-%%         legend style={at={(0.05,1.2)},anchor=north west,font=\footnotesize,legend columns=-1},
-%%         legend cell align={left},
-%%         ylabel={time (sec.)},
-%%         symbolic x coords={helpMe*,isGameFinished*,newGame*,revealAll*,shuffleBoard*,toggleInfo*,isValidCard,isValidVISA,initShields*,brickJiggler*,doPaddlePower*,initBricks*,do\_draw,prob\_gamma},
-%%         xtick=data,
-%%         nodes near coords,
-%%         every node near coord/.append style={rotate=90, anchor=west, font=\footnotesize},
-%%         % every node near coord/.append style={font=\footnotesize},
-%%         axis lines*=left,
-%%         clip=false,
-%%         x tick label style={rotate=45,anchor=east,font=\footnotesize\bfseries},
-%%         y tick label style={font=\footnotesize}
-%%       ]
-%%       \addplot[fill=blue] coordinates {(helpMe*,54) (isGameFinished*,44) (newGame*,4.7) (revealAll*,25) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,85.7) (isValidVISA,47.5) (initShields*,5) (brickJiggler*,4) (doPaddlePower*,3.75)  (initBricks*,132.16) (do\_draw,28.5) (prob\_gamma,44.4)};
-
-%%       \addplot[fill=red] coordinates {(helpMe*,9.4)  (isGameFinished*,6)  (newGame*,3)  (revealAll*,22) (shuffleBoard*,3.25) (toggleInfo*,1.75) (isValidCard,1.33)   (isValidVISA,1.5)  (initShields*,4) (brickJiggler*,2) (doPaddlePower*,35) (initBricks*,26.33) (do\_draw,58.9) (prob\_gamma,5.25)};
-
-%%       \addplot[fill=yellow] coordinates {(helpMe*,11.2)  (isGameFinished*,8.6)  (newGame*,3.3) (revealAll*,26.5) (shuffleBoard*,3.6) (toggleInfo*,1.5) (isValidCard,1.66)  (isValidVISA,1)  (initShields*,3) (brickJiggler*,1.5) (doPaddlePower*,4) (initBricks*,23.1) (do\_draw,15.18) (prob\_gamma,5.1)};
-%%       \legend{$\Random$,$\Genetic$,$\RGenetic$}
-%%     \end{axis}
-%%   \end{tikzpicture}
-%%   \caption{Average generation time per branch}
-%%     \label{fig.gen.time.branch}
-%% \end{figure}
-
-Looking separately at the average execution time for \emph{simple} and \emph{difficult} functions in Table~\ref{tbl.stats.sum}, we conclude that $\RGenetic$ was the fastest algorithm in both cases with the 7 and 25 seconds per branch.
-For simple functions, the $\Genetic$'s performance was quite close to $\RGenetic$, only 9 seconds, but was two times slower for difficult functions.
-In all categories, $\Random$ was much slower than both genetic alternatives.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch 19, 39 and 88 seconds, respectively. 
-  }
-}
-
-Another question, related to the efficiency of our framework, is the computational cost of one iteration of the algorithm.
-This information is useful when configuring the maximal generation limit.
-The cost, shown in column $t/i$ in Table~\ref{tbl.stats}, is calculated as the relation between the execution time and the number of generations, i.e.
-it measures the speed of one iteration.
-Figure~\ref{fig.get.cost} presents the cost comparison of three algorithms across all functions in our study.
-On the one hand, the cost of one iteration depends on the population size, 50 candidates in our case.
-On the other hand, it also depends on the length of the execution trace produced during the evaluation of a candidate, because longer traces increase the computation cost the fitness function.
-Premature program termination due to exceptions leads to short traces, whereas loops and program size in the general contribute to the longer traces.
-For example, the \emph{do_draw} function produces long traces because it only operates with the primitive types thus not rising exceptions, and at the same time, it consists of 40 LOC.
-In our evaluation we observed that the iteration cost varied between 0.25 and 3.59 seconds.\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Globally, one algorithm iteration took one second for $\Random$ and $\RGenetic$, with $\Genetic$ performing worse 1.4 seconds.
-  }
-}
-
-\paragraph{\textbf{RQ3 (significance).}} Because our testing framework is randomized by nature, we need to conduct statistical analysis to test the \emph{significance} and \emph{effect size} of our the performance results.
-This analysis is based on the coverage time in 50 executions, produced by each test algorithm $\Random$, $\Genetic$ and $\RGenetic$.
-Following recommendations on the assessment of randomized algorithms~\cite{arcuri2011practical}, we use the non-parametric Mann-Whitney U-test~\cite{mann1947test} and the Vargha-Delaney $\hat{A}_{12}$ statistics~\cite{vargha2000critique} for measuring statistical significance ($\alpha=0.05$) and effect size, respectively.
-In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-For example, the higher the value in the $_{\Genetic}^{\Random}$ column, the slower $\Random$ performs comparing to $\Genetic$.
-Depends on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
-\setlength{\fboxsep}{1mm}
-\fbox{%
-  \parbox{8.2cm}{
-    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases globally and 67\% on the difficult functions.  
-  }
-}
-
-\paragraph{\textbf{Threats to Validity}}
-The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time.
-Though, the branch coverage is a common criteria used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy.
-Reaching a target branch is only part of the problem, we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles disseminating in exceptions.
-Using a stronger oracle for validation is future work.
-Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent unnecessary data explosion.
-Additional measure that could be taken is applying a minimization procedure, aka \emph{delta debugging}, to the GA result.
-
-Initial GA configuration introduces the threat to the \emph{internal validity} of our empirical evaluation.
-The parameters we used are quite standard for similar SBST frameworks, e.g.
-EvoSuite.
-Though, not reported in the paper, we performed preliminary assessment of various GA configurations, which confirmed our final decision.
-
-The threat of \emph{conclusion validity} can be affected by the GA stochastic nature.
-This risk was addressed by repeating the experiment 50 times and performing statistical analysis of the significance and effect size.
-We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.
-
-The \emph{external validity} deals with the threat of generalization of our results due to manual selection of the experimental subjects.
-To mitigate this fact, we picked the subjects either from previously used in related research or found in open source.
-Of course, those subjects still have to met the constrains of our testing approach.
-So, further research is required in both increasing the power of our framework and extending the validation set.
-
-%% --------------------------------------------------------------------
-\section{Related and Future Work}
-\label{sec:related.work}
-%% --------------------------------------------------------------------
-
-The last two decades were fruitful in the amount of work dedicates to the analysis and web applications and JavaScript, in particular.
-The state-of-the-art in this field including JS static and dynamic analysis, as well as test generation is captured by the following surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Therefore, we would like to organize our discussion of related work around two main questions:
-\begin{enumerate*}
-\item test data generation for JS functions interacting with the DOM, and
-\item the application of search-based techniques for that problem.
-\end{enumerate*}
-
-\subsection{Test Data Generation for JavaScript}
-
-The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation.
-Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM.
-It performs static analysis to collect constant info and feed it to the random generation.
-We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution.
-Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.
-More recently, Kristensen et al.~\cite{kristensen2017type} proposes to use feedback-directed random testing for generating TypeScript tests based on the provided type annotations.
-
-\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be employed, for example, for implementing concolic testing or type inconsistency analysis~\cite{pradel2015typedevil}.
-It suffers from typical for the symbolic analysis problems such as the handing of arrays and loops.
-\emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constrain solver in order to obtains DOM fixtures for the FUT.
-Combined with Jalangi it can be used for both primitive and DOM test data generation.
-As it has been shown early by Baars et al.~\cite{baars2011symbolic}, search-based testing can greatly benefit from symbolic analysis.
-Following this approach, we could try to combine \emph{JEDI} with \emph{Confix} to achieve better results.
-Tanida~\cite{tanida2014automatic} implemented pure symbolic test generation for JS without the DOM interaction.
-
-Static analysis is a powerful technique commonly used as solid alternative for program testing.
-In fact both techniques can benefit from one another.
-For such weakly typed and dynamic languages as JavaScript employing static analysis to infer types can be an invaluable source of information to identify potential bugs or even guarantee their absence.
-Jensen et al.~\cite{tajs2009} presented such an analysis for JavaScript using abstract interpretation.
-In the follow-up work~\cite{dom2011} they extended the analysis with the abstractions to reason about HTML DOM and browser API.
-Given step let the authors to carry static analysis at the level of complete web application (JavaScript + HTML).
-Artemis~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web application.
-It discoverers new tests by generating sequences of executable events and monitoring they effect on the state of the application.
-
-\emph{Atrina}~\cite{icst16} uses existing DOM-dependent assertions complemented with the inferred ones to accompany unit tests generated by \emph{JSEFT}~\cite{mirshokraie2015jseft}.
-
-\emph{Flycatcher}~\cite{de2012automatic} generates tests by instrumenting a program with the JS \emph{Proxies} in order to collect type related information.
-
-\emph{$JS_{DEP}$}~\cite{sung2016static} proposes a constraint-based static analysis for learning dependencies between DOM-events, which can help to prune the sequence of tests consisting of the web-application events.
-Lerner~\cite{lerner2012modeling} define formal model of event behavior in the DOM to establish testing oracles.
-
-\cite{alshahwan2011automated} automated web application testing using search based software techniques.
-
-\cite{ma2015grt} guided random testing
-
-\cite{mao2016sapienz} Multi-objective automated testing for Android application
-
-\cite{jquery2014}
-
-ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.
-
-Salable dynamic analysis framework for JS based on shadow executions~\cite{create.citation}.
-
-Information-flow security for JS~\cite{hedin2012information}.
-
-Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}
-
-Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.
-
-Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.
-
-Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.
-
-DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.
-
-\subsection{Search-Based Test Data Generation}
-\label{sub.sec.search.based}
-
-Despite of the practical popularity of JavaScript, the only recorded in the literature attempt of adopting search-based testing for JS unit testing was done by Alshraideh~\cite{alshraideh2008complete}.
-It uses GA for branch and mutation coverage, but only deals with the limited input types booleans, integers and strings; and provides validation based on one trivial example --- \emph{the triangle program}.
-On the contrary, our work additionally supports array and DOM types, with suggest reasonable validation with the discussion of significance and effect size.
-Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-
-In this paper we dealt with the generation and evolution of DOM which is an example of tree-like data structure.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim to improve test coverage of the XML-aware Java programs.
-To generate random document, it may rely on existing XML schema, or generate document from scratch.
-In some sense, DOM specification can be thought of a complex XML schema, which is difficult to comply.
-One distinction of our approach is the use of program analysis for data generation.
-Both tools have similar philosophy for mutation and crossover.
-Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.
-
-Starting from the seminal survey of search-based test data generation~\cite{mcminn2004search}, there has been an active growth in the number of SBST research~\cite{mcminn2011search}.
-Powered by the works of Wegener et at.~\cite{wegener2001evolutionary} on structural test generation, and Tonella~\cite{tonella2004evolutionary} on evolutionary class testing, it resulted in the development of EvoSuite~\cite{fraser2011evosuite} --- evolutionary framework for Java test generation.
-
-One likely direction for the future extension of \emph{JEDI} is the whole test suite generation.
-Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage.
-That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage.
-Usually, such problems incur multi-objective optimization~\cite{lakhotia2007multi}, e.g.
-coverage vs.
-test-suite length.
-Another direction of future work is adjusting out tool for mutation-driven generation of unit tests and oracles, similar to the line of work~\cite{fraser2012mutation}.
-That would also help us to judge about the fault revealing ability of \emph{JEDI} based on the number of killed mutants.
-As we said early in this section, SBST techniques can benefit from symbolic analysis~\cite{baars2011symbolic}.
-
-\section{Conclusions}
-\label{sec:concl}
-This paper
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{icse2018.bib}
-
-\end{document}

### 2018-06-29 doc/issre2018/issre2018.tex

@@
 \and
-\IEEEauthorblockN{Wishnu Prasetya}
+\IEEEauthorblockN{I.S.W.B Prasetya}
 \IEEEauthorblockA{\textit{Utrecht University} \\
@@
 The popularity of JavaScript is continuously growing.
-Together with HTML and CSS, it forms the core technology stack for web development.
+Together with HTML and CSS, it is the core technology for modern web development.
 Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable.
-Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS applications interacting with the DOM has not yet been addressed.
+Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS code interacting with the DOM has not yet been addressed.
 In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.

### 2018-08-11 doc/issre2018/introduction.tex
Preparing camera ready: introduction

@@
 The success of JS can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}.
-On the other hand, due to of implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}.
-Thus, it is not surprising that once in a while critical bugs manage to break through~\cite{bugstories2017} even into the web applications of major companies such as Facebook, Twitter etc.
+On the other hand, due to implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}.
+Thus, it is not surprising that once in a while critical bugs manage to make it into web applications of major companies such as Facebook, Twitter etc~\cite{bugstories2017}.
 
@@
 --- intended to assist web developers with the automation of various  activities such as the design, execution and monitoring of unit tests.
-Despite the apparent abundance of the JS testing tools, the developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements.
+Despite the apparent abundance of the JS testing tools, developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements.
 One of the missing steps on the way to complete JS test automation is \emph{the generation of test data}.
@@
 
-Generally, the problem of test data generation has been actively studied for the past three decades.
-In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the whole web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
+The problem of test data generation has been actively studied for the past three decades.
+In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the complete web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
 Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints.
-However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reached about 50\% \emph{branch coverage} on the selected subjects.
+However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reaches about 50\% \emph{branch coverage} on the selected subjects.
 At the same time, search-based techniques have shown prominent results in successfully achieving higher branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications.
-But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of the search-based approach.
-In this paper we are breaching this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-We can summarize our contributions as follows:
+But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of search-based approach.
+In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
+We summarize our contributions as follows:
 \begin{enumerate}[leftmargin=5mm]
@@
 \item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target.
-In contrast with the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly reachable.
-\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
+In contrast to the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly achievable.
+\item Based on the case studies found in two related papers~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results.
+The validation shows the effectiveness of the framework in covering target branches with a reasonable efficiency.
 Moreover, we show that out of 10 functions where \emph{JEDI} achieved complete branch coverage, \emph{Confix} only covered 32\% on average.

### 2018-08-11 doc/issre2018/issre2018.tex
Preparing camera ready: introduction

@@
 \begin{abstract}
-The popularity of JavaScript is continuously growing.
+The popularity of JavaScript is enormous.
 Together with HTML and CSS, it is the core technology for modern web development.
 Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable.
-Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS code interacting with the DOM has not yet been addressed.
-In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
-In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including the global DOM state.
+Despite active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS code interacting with the DOM has not yet been addressed.
+In this paper, we present a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
+In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function in combination with the global DOM state.
 We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.

### 2018-08-12 doc/issre2018/conclusions.tex
Working on camera-ready. Fixed all comments by Doatse.

@@
 Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
+We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateaus by restarting search with a new target.
 Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.

### 2018-08-12 doc/issre2018/evaluation.tex
Working on camera-ready. Fixed all comments by Doatse.

@@
 On the other hand, the small window can lead to premature archive convergence, which prevents the right genetic combination from being triggered.
-We have experimented with two different windows of size 5 and 10.
-But since the latter one ($\RGenetic$) showed the best performance over all, we chose to report only that case in the paper.
+We have experimented with the windows of size 5 and 10.
+But since the latter one ($\RGenetic$) showed the best performance over all, we chose to report only that case here.
 Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
@@
 Being one of the most popular programming languages for web development, there are ample open source JS projects on the Web.
-JS applications are written with the help of countless numbers of specialized libraries, and greatly vary in size, complexity and coding style.
+JS applications are written with the help of countless specialized libraries, and greatly vary in size, complexity and coding style.
 Moreover, some popular JS web-frameworks, such as jQuery and React~\cite{todomvc}, implement their own API for DOM manipulation.
@@
 To study the effectiveness and efficiency of our test generation framework, we exercised each algorithm ($\Random$, $\Genetic$ and $\RGenetic$) against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments have been repeated 50 times to achieve statistical significance.
+Due to the probabilistic nature of the test generation process, the experiments have been repeated 50 times to achieve statistical significance~\cite{arcuri2011practical}.
 Table~\ref{tbl.stats} summarizes the evaluation results.
@@
 \textbf{RQ1 (effectiveness)}: To answer this question, we measure the branch coverage achieved by each test generation algorithm.
-Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm can not guarantee finding a solution.
+Given a fixed limit on the number of test iterations, 200 in our case, a search algorithm cannot guarantee finding a solution.
 The underlined values in Table~\ref{tbl.stats} like $\underline{200}$ indicate branches which were not covered by the respective algorithms.
@@
 So, an exceptional program termination leads to short traces, whereas loops tend to produce longer traces.
-For example, the \emph{do_draw} function has long traces because it only operates with the primitive types thus never rising exceptions, and at the same time, it consists of 40 LOC.
+For example, the \emph{do_draw} function has long traces because it only operates with the primitive types thus never rises exceptions, and at the same time, it consists of 40 LOC.
 In our evaluation, the iteration cost varied between 0.25 and 3.59 seconds.\\
@@
 In Table~\ref{tbl.stats} the three columns to the right show the $\hat{A}_{12}$ values for all algorithm combinations, where this value is significant and '-' otherwise.
-Thus, the higher the value in the $_{\Genetic}^{\Random}$ column, indicates that $\Random$ is slower comparison with $\Genetic$.
+Thus, the higher the value in the $_{\Genetic}^{\Random}$ column, indicates that $\Random$ is slower in comparison with $\Genetic$.
 Depending on the actual $\hat{A}_{12}$ value, the effect size can be small (0.56), medium (0.64), and large (0.71).\\
@@
 Reaching a target branch is only part of the problem: we also need an oracle to discriminate the program's output.
-In this paper, we strike for so called ``natural'' oracles leading to exceptions.
+In this paper, we rely on so called ``natural'' oracles leading to exceptions.
 Using a stronger oracle for validation is future work.
 Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.
-To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent on unnecessary data explosion.
+To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent data explosion.
 Additional measure that could be applied is a minimization procedure, aka \emph{hierarchical delta debugging}~\cite{misherghi2006hdd} and its variations~\cite{herfert2017automatically}, to the GA result.

### 2018-08-12 doc/issre2018/example.tex
Working on camera-ready. Fixed all comments by Doatse.

@@
 Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}~\cite{sudoku}.
-This function checks if a given sudoku solution is valid.
+This function checks if a candidate sudoku solution is valid.
 First, it locates a DOM element \texttt{obj} representing the game field (line~\ref{isGameFinished.getSudoku}).
@@
 Suppose now that we would like to unit test this function.
-We aim to maximize the branch coverage as a common testing criteria~\cite{zhu1997software}.
+We aim to maximize the branch coverage as a common testing criterion~\cite{zhu1997software}.
 That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
@@
 As we have just witnessed, even for such a relatively simple example, the test data generation can be far from trivial procedure because it requires the deep understanding of the program semantics.
-In practice, web developers often have to deal with third-party code, including a large number of JS libraries freely available on the GitHub, which are commonly untested and poorly documented.
+In practice, web developers often have to deal with third-party code, including a large number of JS libraries freely available on GitHub, which are commonly untested and poorly documented.
 At the same time, unit testing is the most fundamental level of testing and the easiest to implement.
 It saves the code from unexpected regressions and often documents the desired behavior of a program.
-Thus, in industry unit testing has became a standard practice in web development.
+Thus, in industry unit testing has become a standard practice in web development.

### 2018-08-12 doc/issre2018/framework.tex
Working on camera-ready. Fixed all comments by Doatse.

@@
 Let us take a closer look at the sequence of interactions in Figure~\ref{fig.framework.architect}.
-As an input for our testing framework, \User has to provide a JS file \emph{fun.js} that contains a FUT \emph{fun} annotated with the type signature.
+As an input for our testing framework, \User has to provide a JS file \emph{fun.js} that contains a FUT \emph{fun} annotated with its type signature.
 Additionally, \User specifies a configuration file \emph{config} that sets various control parameters for the random and genetic generation, logging and so on.
 Experimentally, we have found an optimal configuration that we consistently used in the experimental evaluation in Section~\ref{sec.evaluation}.
-Once all the data are processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), the instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
+Once all data have been processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), an instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
 Then, the \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
@@
 For each branch, our framework enters the \emph{Genetic Loop (Phase)}.
-Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criteria is achieved, e.g.
+Inside of this phase, the framework starts with a randomly generated population (\emph{Random Loop}), and continues to evolve that population (\emph{Fitness Loop}) until either a perfect entity is found or a termination criterion is achieved, e.g.
 the limit on the number of generation attempts.
@@
 Additionally, we monitor the calls to the functions \texttt{getElementsByTagName}, \texttt{getElementById}, and \texttt{getElementsByClassName} and other DOM API methods.
-They provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the FUT.
+They provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the body of the FUT.
 The next step is to normalize the FUT before applying any instrumentation (line~\ref{alg.init.transform.ast}), e.g.
@@
 
-We assume the FUT is equipped with the type signature.
+We assume the FUT is equipped with its type signature.
 The legitimacy of such requirement can be confirmed by the popularity of \emph{TypeScript}~\cite{typescript}, and advances in the JS type inference, e.g.
@@
     $i \longleftarrow 0 $\label{alg.gen.iter.count}\;
-    $historyConverged \longleftarrow true$\;
-    \Repeat{$\neg historyConverged \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
+    \Repeat{$isPerfect(f^*) \vee (i > size_G)$}{\label{alg.gen.converged.loop.begin}
       $archive \longleftarrow \emptyset$\label{alg.gen.init.archive}\;
       $history \longleftarrow \emptyset$\label{alg.gen.init.history}\;
+      $historyConverged \longleftarrow false$\;
       $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
@@
 We start with the initial target $b_n$ (line~\ref{alg.gen.init.target}) and the iteration counter $i$ set to 0 (line~\ref{alg.gen.iter.count}).
-We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either the history has not converged, or the generations limit has not been exceeded.
-The \emph{archive} variable stores the most fit population candidates observed so far, and the \emph{history} variable records all the archives during the generation process.
+We run the genetic search for the target branch (lines~\ref{alg.gen.converged.loop.begin}-\ref{alg.gen.converged.loop.end}) until either a perfect candidate is found, or the generations limit has been exceeded.
+The \emph{archive} variable stores the fittest population candidates observed so far, and the \emph{history} variable records all the archives during the generation process.
 These variables are empty at the beginning of the evolution (line~\ref{alg.gen.init.archive} and~\ref{alg.gen.init.history} respectively).
@@
 But first, we need to score the current population (lines~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}).
-Each candidate $p$ of the population $pop$ represents a concrete substitution for the arguments of the FUT.
+Each candidate $p$ of the population $pop$ represents a concrete value instance for the arguments of the FUT.
 Thus, it should be coerced according to the type signature $sig$ (line~\ref{alg.gen.make.args}).
@@
 Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their combination (line~\ref{ref.generateHTML.end}).
+Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their composition (line~\ref{ref.generateHTML.end}).
 
@@
 Our search target is a specific branch of the FUT that we want to cover.
-As a dynamically typed language, JS does not provide any static guarantees that an accessed field or a called method for an object are defined.
-Thus, such behaviour can only be known at run-time and may eventually rise an exception.
-Thus, we have to assume that every statement of the FUT, in theory, can rise an exception leading to the deviation from the target.
+As a dynamically typed language, JS does not provide any static guarantees that the field access or method call are defined operations on an object.
+So such behaviour can only be known at run-time and may eventually give rise to an exception.
+Thus, we have to assume that every statement of the FUT, in theory, can produce an exception leading to the deviation from the target.
 We consider a test input as \emph{valid} only if it leads the FUT to a \emph{normal termination}, i.e.
@@
 Therefore, our initial search target is an ordered pair of the CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node.
-The FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and normalized \emph{branch distance}~\cite{arcuri2010does}.
+The FF for a CFG node is traditionally defined~\cite{arcuri2010does} as a combination of the \emph{approach level} and normalized \emph{branch distance}.
 \begin{equation}

### 2018-08-12 doc/issre2018/related-work.tex
Working on camera-ready. Fixed all comments by Doatse.

@@
 Guided by developer's type annotations, \emph{JSContest} generates random inputs for JS functions with the goal to verify the conformance to the \emph{type}~\cite{heidegger2010contract} and \emph{access permission}~\cite{heidegger2012jscontest} contracts.
-In comparison with our genetic approach, it does not leverage dynamic information to construct test inputs, only static one, and ignores the DOM interactions.
+In comparison with our genetic approach, it does not leverage dynamic information to construct test inputs, only static ones, and ignores the DOM interactions.
 $TS_{TEST}$~\cite{kristensen2017type} employs the feedback-directed random generation for conformance checking of TypeScript declarations with the respective JS libraries.
@@
 Later the analysis was extended to support reasoning about the HTML DOM and browser API~\cite{dom2011}.
-\emph{TAJS} is able to point to a dead code, type violation and references to \emph{undefined} values.
+\emph{TAJS} is able to point to dead code, type violation and references to \emph{undefined} values.
 A review of dynamic analysis techniques ofr JS can be found in a recently published survey~\cite{andreasen2017survey} by Andreasen et al.
@@
 \emph{Artemis}~\cite{artemis2011} is a feedback-directed random testing tool for JavaScript web applications.
-It discovers new tests by generating the sequences of executable events and monitoring how they effect the application state.
+It discovers new tests by generating the sequences of executable events and monitoring how they affect the application state.
 Biagiola et al.~\cite{biagiola2017search} propose to use existing \emph{page objects} to produce navigation paths and input data by exploiting the search-based approach.
@@
 
-Another direction of future work is re-targeting our tool towards mutation-driven generation of unit tests and oracles, similar to~\cite{fraser2012mutation}.
+Another direction of future work is re-targeting our tool towards mutation-driven generation of unit tests and oracles~\cite{fraser2012mutation}.
 That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.
@@
 The first extension is straightforward since any class can be described as the collection of the types of class fields.
-To generate functions as inputs we could employ approach similar to QuickCheck~\cite{koopman2006automatic}.
+To generate functions as inputs we could employ an approach similar to QuickCheck~\cite{koopman2006automatic}.
 

### 2018-08-14 doc/issre2018/conclusions.tex
Prepared camera ready

--- 2018-06-29 doc/issre2018/conclusions.tex
@@
 
-In this paper we have introduced a novel JS unit testing framework, called \emph{JEDI}, which uses search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.
-We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
-Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results.
-The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency.
+In this paper we have introduced a novel search-based JS unit testing framework, called \emph{JEDI}.
+Notably, our framework is able to generate an arbitrary DOM inputs that are syntactically valid and compliant with the recent HTML5 specification.
+We present a test generation algorithm, called ``genetic with restart'', which is capable of escaping plateaus by concretizing the search target.
+Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation followed by the significance study, which has confirmed the effectiveness and efficiency of our framework in branch coverage testing.

### 2018-08-14 doc/issre2018/evaluation.tex
Prepared camera ready

@@
 All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3.
-We have created three different instances of the JS testing framework --- each one is based on a slight variation of the underlying genetic algorithm.
+We have created three different instances of the JS testing framework --- each one is based on a slight variation of the underlying GA.
 The first version, which plays the role of our baseline, is \emph{Random} ($\Random$).
@@
 The last version is \emph{Genetic with Restart} ($\RGenetic$).
-It is based on the genetic Algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
+It is based on Algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window.
 On the one hand, the smaller window size forces the GA to converge faster and quickly discovers stagnation.
@@
 Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework.
-The initial setup for genetic algorithm is similar to other frameworks, e.g.
+The initial setup for the GA is similar to other frameworks, e.g.
 \emph{EvoSuite}~\cite{fraser2011evosuite}.
@@
 To study the effectiveness and efficiency of our test generation framework, we exercised each algorithm ($\Random$, $\Genetic$ and $\RGenetic$) against all branches of the functions in Table~\ref{tbl.case.studies}.
-Due to the probabilistic nature of the test generation process, the experiments have been repeated 50 times to achieve statistical significance~\cite{arcuri2011practical}.
+Due to the probabilistic nature of the test generation process~\cite{arcuri2011practical}, the experiments have been repeated 50 times to achieve statistical significance.
 Table~\ref{tbl.stats} summarizes the evaluation results.
@@
 The next group of columns $t_{\Random}/t_{\Genetic}$, $t_{\Random}/t_{\RGenetic}$ and $t_{\Genetic}/t_{\RGenetic}$ presents the relative performance of each pair of the testing algorithm $(\Random,\Genetic)$, $(\Random,\RGenetic)$, and $(\Genetic,\RGenetic)$ respectively.
-To the right of the function name, we also present accumulated statistics for the function as a whole\footnote{because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
-see the \emph{toggleInfo} function}
+To the right of the function name, we also present accumulated statistics\footnote{because of the missing branches, the function's summary may not be equal to the sum of the branches, e.g.
+see the \emph{toggleInfo} function}.
 
@@
 We encountered three such cases in our study: branches $(10,11)$, $(47,48)$ and $(45,45)$ of the function \emph{doPaddlePower}, \emph{initBricks} and \emph{do_draw}, respectively.
-They motivated us to introduce the genetic algorithm with restart ($\RGenetic$) which combines the strengths of both $\Random$ and $\Genetic$.
+They motivated us to introduce the GA with restart ($\RGenetic$) which combines the strengths of both $\Random$ and $\Genetic$.
 It leverages the genetic search while the fitness continues to improve, and restarts the search with a new target, when the fitness suboptimally converges.
@@
 
-\textbf{RQ4 (comparison):} We evaluated \Confix\ as the only available alternative for the generation of DOM fixtures.
-In \cite{amin:ase15} the authors have proposed three strategies for test generation based on:
-\begin{enumerate*}[label=(\roman*)]
-  \item \emph{Confix} entirely,
-  \item \emph{Jalangi}~\cite{sen2013jalangi} combination, and
-  \item semi-manual approach.
-\end{enumerate*}
-Even though the third strategy outperformed pure \Confix by 19\%, it is not suitable for an objective comparison with a fully automated technique, like \Jedi.
-On the other hand, the combination with \Jalangi could be used for the evaluation, but it only improved branch coverage by 2\%, and the \Confix version available online~\cite{confixgit} has no actual integration with \Jalangi.
-Thus we had to fall back on plain \Confix test generation; results are present in Figure~\ref{tbl.confix.compare}.
-In comparison with \Jedi, \Confix does not search for a test input in terms of a \emph{strong} coverage, i.e.
-it only tries to reach a target branch neglecting the normal termination.
-But even in terms of \emph{weak} coverage, it showed the complete coverage in 2 out 10 cases.\\
+\textbf{RQ4 (comparison):} We evaluate \Confix~\cite{amin:ase15} as the only available alternative for the generation of DOM fixtures.
+The authors suggest that \Confix\ achieves higher branch and statement coverage by being combined with \Jalangi~\cite{sen2013jalangi} --- a concolic test generation tool for JS --- which is able to produce test inputs for JS arguments of primitive types.
+However, the available online implementation of \Confix~\cite{confixgit} has no actual integration with \Jalangi.
+Thus we have to fall back on plain \Confix test generation.
+
+Experimental results are presented in Figure~\ref{tbl.confix.compare}.
+We report both \emph{weak} (reach the target branch) and \emph{strong} (reach the branch and terminate normally) coverage.
+\Confix test generation is guided by the weak coverage in contrast with the strong coverage of \Jedi.
+In all experimental subjects except one (\jsID{isGameFinished}), \Confix poorly performs simply due to an inability to produce appropriate input arguments.
+However, in the case of \jsID{isGameFinished}, which requires no inputs, it still fails to reach deeply nested branches because of imprecise symbolic representation.
+In particular, it cannot interpret the expression on line~\ref{isGameFinished.if1.begin} in Figure~\ref{code.isGameFinished}:
+%% following expression:
+\begin{center}
+\begin{lstlisting}[style=htmlcssjs,language=JavaScript,basicstyle={\footnotesize\ttfamily},backgroundcolor=\color{white},frame=none,numbers=none,xleftmargin={0.2cm}]
+subDivs[no].className.indexOf('sudokuSquare') >= 0
+\end{lstlisting}
+\end{center}
+This is not a principal constraint, but to be fully addressed, \Confix should model an extensive library of built-in JS functions.
+\Jedi mitigates this constraint by substituting observed string literals as conceivable class names, which are additionally evolved thanks to crossover and mutation operators.
+We admit, however, that some constructs, e.g.
+jQuery, are supported by Confix but not by Jedi.\\
 \framebox{
-  \parbox[t][0.65cm]{0.95\linewidth}{
-Although, \Confix performs much faster (under 10 seconds), it is unable to cover hard branches, which \Jedi can.
+  \parbox[t][1.5cm]{0.95\linewidth}{
+In a nutshell, the choice between a concolic and search-based approach is a trade-off between a labour-intensive modelling effort and long execution time, respectively, where both can reinforce each other.
   }
@@
 \textbf{Threats to Validity:}
-The \emph{construct validity} threat comes from the choice of measurements: branch coverage and execution time.
-Although, the branch coverage is a common criterion used in practice, the actual fault finding capability is a stronger indication of testing adequacy.
+The \emph{construct validity} threat is due to the choice of measurements: branch coverage and execution time.
+Although, the branch coverage is a common criterion used in practice, the fault finding capability is a stronger indication of testing adequacy.
 Reaching a target branch is only part of the problem: we also need an oracle to discriminate the program's output.
-In this paper, we rely on so called ``natural'' oracles leading to exceptions.
-Using a stronger oracle for validation is future work.
+In this paper, we rely on so called ``natural'' oracles such as exceptions.
+%Using a stronger oracle for validation is future work.
 Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time.

### 2018-08-14 doc/issre2018/example.tex
Prepared camera ready

@@
-%% --------------------------------------------------------------------
+%%% --------------------------------------------------------------------
 \section{Motivating Example}
@@
 
-Let us consider the JS function \texttt{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}~\cite{sudoku}.
+Let us consider the JS function \jsID{isGameFinished} in Figure~\ref{code.isGameFinished} taken from the web game \emph{sudoku}~\cite{sudoku}.
 This function checks if a candidate sudoku solution is valid.
-First, it locates a DOM element \texttt{obj} representing the game field (line~\ref{isGameFinished.getSudoku}).
-Then, it collects all children \emph{DIV} elements of \texttt{obj} (line~\ref{isGameFinished.getDivs}).
+First, it locates a DOM element \jsID{obj} representing the game field (line~\ref{isGameFinished.getSudoku}).
+Then, it collects all children \emph{DIV} elements of \jsID{obj} (line~\ref{isGameFinished.getDivs}).
 Each \emph{DIV} corresponds to an input square of the game (line~\ref{isGameFinished.if1.begin}) and consists of two \emph{SPAN} tags.
@@
 We aim to maximize the branch coverage as a common testing criterion~\cite{zhu1997software}.
-That is, for each individual branch of the function under test (FUT) \texttt{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
+That is, for each individual branch of the function under test (FUT) \jsID{isGameFinished}, we need to construct a test input that covers the branch and leads to the normal termination of the FUT.
 A JS function can take \emph{explicit} input arguments (in our case none), but it can also accept \emph{implicit} arguments such as a DOM state.
@@
 Let us, for example, take a look at how we can reach the target branch $(10,11)$.
-Line~\ref{isGameFinished.getSudoku} expects the DOM to have an element with an id \textquotesingle\texttt{sudoku}\textquotesingle.
+Line~\ref{isGameFinished.getSudoku} expects the DOM to have an element with the id \textquotesingle\jsID{sudoku}\textquotesingle.
 In order to enter the for-loop in line~\ref{isGameFinished.inFor.begin}, this element should have at least one child \emph{DIV} tag.
-The first if-condition in line~\ref{isGameFinished.if1.begin} requires each \emph{DIV} element to be of the class \textquotesingle\texttt{square}\textquotesingle\, and do not have a background color.
-The second if-condition (line~\ref{isGameFinished.if2.begin}) implies that the \emph{DIV} should consist of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
-The resulting test \texttt{T4} in Figure~\ref{fig.isGameFinished.tests} meets all the above conditions.
+The first if-condition in line~\ref{isGameFinished.if1.begin} requires each \emph{DIV} element to be of the class \textquotesingle\jsID{square}\textquotesingle\, and do not have a background color.
+The second if-condition (line~\ref{isGameFinished.if2.begin}) implies that the \emph{DIV} element should consist of two \emph{SPAN} elements whose \emph{innerHtml} values are not equal.
+The resulting test \jsID{T4} in Figure~\ref{fig.isGameFinished.tests} meets all the above conditions.
 
@@
 In practice, web developers often have to deal with third-party code, including a large number of JS libraries freely available on GitHub, which are commonly untested and poorly documented.
-At the same time, unit testing is the most fundamental level of testing and the easiest to implement.
-It saves the code from unexpected regressions and often documents the desired behavior of a program.
-Thus, in industry unit testing has become a standard practice in web development.
+At the same time, unit testing is the most fundamental and easiest to implement type of testing.
+It saves the code from unexpected regressions and documents the desired behavior of a program.
+Thus, in industry unit testing has become a standard development practice.

### 2018-08-14 doc/issre2018/framework.tex
Prepared camera ready

@@
 Once all data have been processed by the \Server in \emph{Initialization Phase}, we get back the following information about \emph{fun}: the control flow graph (\emph{cfg}), the complete list of its branches (\emph{branches}), the constant info (\emph{cinfo}), an instrumented version \emph{fun} (\emph{ifun}), and the signature (\emph{sig}).
-Then, the \Server sends a \texttt{POST} request with \emph{ifun} and \emph{sig} to the \Client.
+Then, the \Server sends a \jsID{POST} request with \emph{ifun} and \emph{sig} to the \Client.
 Depending on the configured execution mode, the \Server either asks the \User to select a \emph{target} branch or covers all branches one by one in a fixed order.
@@
 In order to maximize the chances of generating the fittest candidate, in line~\ref{alg.init.collect.info} we perform static analysis of the FUT with the purpose to collect information about constants such as numeric and string literals.
-Additionally, we monitor the calls to the functions \texttt{getElementsByTagName}, \texttt{getElementById}, and \texttt{getElementsByClassName} and other DOM API methods.
+Additionally, we monitor the calls to the functions \jsID{getElementsByTagName}, \jsID{getElementById}, and \jsID{getElementsByClassName} and other DOM API methods.
 They provide the information about \emph{tags}, \emph{ids}, \emph{classes} and \emph{names} referred from the body of the FUT.
@@
 
-<Signature> ::= \texttt{dom} : <Type Signature> | <Type Signature>
+<Signature> ::= \jsID{dom} : <Type Signature> | <Type Signature>
 
@@
 
-<Primitive Type> ::= \texttt{bool} | \texttt{int} | \texttt{float} | \texttt{string}
+<Primitive Type> ::= \jsID{bool} | \jsID{int} | \jsID{float} | \jsID{string}
 
@@
 The supported grammar of type annotations is shown in Figure~\ref{fig.js.type.annot}.
-Each type annotation is a signature expressed as a specialized JS type comment (\texttt{/*t...*/}).
+Each type annotation is a signature expressed as a specialized JS type comment (\jsID{/*t...*/}).
 We distinguish between two kinds of signatures: with the reference to the global DOM and ``ordinary'' JS type signatures.
-The former kind expects the \texttt{dom} terminal to be in place of the first parameter of the function call.
+The former kind expects the \jsID{dom} terminal to be in place of the first parameter of the function call.
 Whereas an ordinary JS signature is a non-empty sequence of the JS types.
-The type can be \emph{Void}, \emph{Primitive} (\texttt{bool}, \texttt{int}, \texttt{float}, \texttt{string}) or \emph{Array} (recursive homogeneous array type).
+The type can be \emph{Void}, \emph{Primitive} (\jsID{bool}, \jsID{int}, \jsID{float}, \jsID{string}) or \emph{Array} (recursive homogeneous array type).
 
-%% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-%%        LEFT OUT DUE TO LACK OF SPACE
-%% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 \subsubsection{Instrumentation}
@@
 
-Figure~\ref{code.isGameFinished.instr} presents the \texttt{isGameFinished} function after instrumentation.
-The global variable \texttt{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT.
+The instrumented version of the FUT is shown in Figure~\ref{code.isGameFinished.instr}.
+The global variable \jsID{trace} in line~\ref{isGameFinished.instr.trace} records the sequence of executed statements of the FUT.
 We have to trace all the statements because each one, in theory, can rise an exception.
-The \texttt{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} captures the upper bound for the number for-loop iterations.
+The \jsID{loopMap} variable in line~\ref{isGameFinished.instr.loopMap} captures the upper bound for the number for-loop iterations.
 If the exact bound is unknown, it is set to one.
-The \texttt{branchDistance} variable, computed for the \emph{problem node}, contains the distance~\cite{tracey1998automated} from the target branch.
+The \jsID{branchDistance} variable, computed for the \emph{problem node}, contains the distance~\cite{tracey1998automated} from the target branch.
 
@@
 \end{lstlisting}
-  \caption{Instrumented version of \texttt{isGameFinished.js} }
+  \caption{Instrumented version of \jsID{isGameFinished.js} }
   \label{code.isGameFinished.instr}
@@
 At the end of the evolution loop (line~\ref{alg.gen.has.converged}), we verify the convergence of the history within the window of $size_H$.
-If that condition is true (line~\ref{alg.gen.loop.end}), the genetic algorithm is restarted with a new search target.
-It consists of the original branch $b_n$ prefixed with a new branch $b$ from which $b_n$ depends on (line~\ref{alg.gen.new.target}).
-Every time the history converges, we produce a new search target by eventually exhausting all possible executions leading to $b_n$.
+If it has converged (line~\ref{alg.gen.loop.end}), the GA is restarted with a new search target, which is composed of the original branch $b_n$ prefixed with a branch $b$ on which $b_n$ depends (line~\ref{alg.gen.new.target}).
+This process is exhaustively repeated to test all possible executions leading to $b_n$.
 In practice, we only consider extensions upto length two.
@@
     Random    & Float  & choose (4:1) at random [-10.0, 10.0] or constants\\
-    Random    & String & $>5$ chars from $\texttt{[a-zA-Z0-9]}$ or constants (4:1)\\
+    Random    & String & $>5$ chars from $\jsID{[a-zA-Z0-9]}$ or constants (4:1)\\
     Random    & Array  & array of a respective type upto length five\\
@@
   \end{haskell}
-  \caption{The \texttt{Arbitrary} instance for the \texttt{Html} data type}
+  \caption{The \jsID{Arbitrary} instance for the \jsID{Html} data type}
   \label{fig.html.arb.def}
@@
 This was a challenge on its own because the complexity of HTML and the lack of formal specification.
-Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \texttt{Arbitrary} instance for the \texttt{Html} data type.
+Our language is inspired by QuickCheck~\cite{claessen2011quickcheck} and essentially employs it to define an \jsID{Arbitrary} instance for the \jsID{Html} data type.
 With some technical details left out for the sake of simplicity, Figure~\ref{fig.html.arb.def} shows that definition.
-The data type \texttt{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) represents the internal state of \texttt{Html}.
+The data type \jsID{HtmlState} (lines~\ref{ref.HtmlState.begin}--\ref{ref.HtmlState.end}) represents the internal state of \jsID{Html}.
 The state is composed of the following components:
 \begin{itemize}
-\item \texttt{depth} and \texttt{degree} specify respectively the maximum depth and node degree of the generated HTML
-\item \texttt{ctx} is the current value of the HTML content model stack
-\item \texttt{tagFreq} provides statistical information about the frequency of tags in HTML
-\item \texttt{tags}, \texttt{ids} and \texttt{classes} are the initial set of respective HTML elements used for random generation.
+\item \jsID{depth} and \jsID{degree} specify respectively the maximum depth and node degree of the generated HTML
+\item \jsID{ctx} is the stack of HTML contexts
+\item \jsID{tagFreq} provides statistical information about the frequency of tags in HTML
+\item \jsID{tags}, \jsID{ids} and \jsID{classes} are the initial set of respective HTML elements used for random generation.
 \end{itemize}
-Combined with the random generation monad \texttt{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \texttt{Html} (line~\ref{ref.GenHtmlState}).
-Each HTML tag is the value of the \texttt{GenHtmlState} type.
-Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \texttt{<html>} tag.
-According to the specification~\cite{htmlspec}, the tag is composed of the \texttt{<head>} tag followed by the \texttt{<body>} tag.
+Combined with the random generation monad \jsID{Gen}, this state is wrapped into a state monad transformer~\cite{jones1995functional} (line~\ref{ref.GenState}) which returns the randomly generated \jsID{Html} (line~\ref{ref.GenHtmlState}).
+Each HTML tag is the value of the \jsID{GenHtmlState} type.
+Lines~\ref{ref.generateHTML.begin}--\ref{ref.generateHTML.end} give an example of the content generation for the \jsID{<html>} tag.
+According to the specification~\cite{htmlspec}, the tag is composed of the \jsID{<head>} tag followed by the \jsID{<body>} tag.
 First, we store the state of HTML generation and retrieve the current the depth (lines~\ref{ref.generateHTML.getState} and \ref{ref.generateHTML.getDepth} respectively).
 Then, if the depth is zero, we immediately return a string literal (line~\ref{ref.generateHTML.returnString}).
-Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \texttt{head} (line~\ref{ref.generateHTML.newHead}) and \texttt{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their composition (line~\ref{ref.generateHTML.end}).
+Otherwise, we decrease the current depth by one (line~\ref{ref.generateHTML.updateState}), generate the contents for \jsID{head} (line~\ref{ref.generateHTML.newHead}) and \jsID{body} (line~\ref{ref.generateHTML.newBody}), and return, finally, their composition (line~\ref{ref.generateHTML.end}).
 
@@
 
-In essence, an HTML document is a labeled tree with \emph{tags} instead of nodes and \emph{attributes} as labels.
-Therefore, the crossover and mutations are defined similar to those operators for \emph{expression trees} in genetic programming.
+In essence, an HTML document is a labeled tree, where nodes are \emph{tags} and labels are \emph{attributes}.
+So, crossover and mutations are defined similar to those operators for \emph{expression trees} in genetic programming.
 
-\textbf{HTML Crossover} takes two HTML tree candidates, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
+\textbf{HTML Crossover} takes two documents, randomly picks a node in the first one, and replaces the respective sub-tree by a randomly selected sub-tree from the second candidate.
 

### 2018-08-14 doc/issre2018/introduction.tex
Prepared camera ready

@@
 
-According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript has been recognized for the sixth time in row as the most commonly used programming language.
+According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript (JS) has been recognized for the sixth time in row as the most commonly used programming language.
 It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million).
-The success of JS can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}.
-On the other hand, due to implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}.
-Thus, it is not surprising that once in a while critical bugs manage to make it into web applications of major companies such as Facebook, Twitter etc~\cite{bugstories2017}.
+The success of JS can be explained by its native browsers support, and the rise in popularity of the JS runtime environment \emph{Node.js}.
+On the other hand, JS applications are error-prone~\cite{frolin:TSE16} and challenging to test and analyze~\cite{mesbah2015advances,andreasen2017survey,sun2017analysis} due to such language features as implicit type conversion, lack of static types, and extensive support of dynamic constructs~\cite{richards2010analysis}.
+Thus, it is not surprising that once in a while critical bugs manage to make it into web applications of major companies such as Facebook, Twitter etc.~\cite{bugstories2017}.
 
-Systematic unit testing is a basic and, at the same time, the most effective technique for improving software quality~\cite{martin2009clean}.
-There exist numerous JS frameworks on the market --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc.
---- intended to assist web developers with the automation of various  activities such as the design, execution and monitoring of unit tests.
-Despite the apparent abundance of the JS testing tools, developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements.
+Systematic unit testing is a basic and, at the same time, the most effective technique for improving software quality~\cite{martin2009clean}. There exist numerous JS frameworks on the market
+--- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc. ---
+intended to assist web developers with the automation of various  activities such as the design, execution and monitoring of unit tests.
+Despite the apparent abundance of the JS testing tools, developers satisfaction  is still relatively low~\cite{stateJS2017} (3.2 out of 5), indicating there is a room for improvements.
 One of the missing steps on the way to complete JS test automation is \emph{the generation of test data}.
@@
 The problem of test data generation has been actively studied for the past three decades.
-In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the complete web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
+In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\mbox{\emph{JSContest}}~\cite{heidegger2010contract}), and the analysis of the complete web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}).
 Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints.
@@
 But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of search-based approach.
-In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
+In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
 We summarize our contributions as follows:
@@
 \item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data.
-Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
+Notably, our testing framework is able to generate an arbitrary DOM input (including \emph{tags} and \emph{attributes}), which is syntactically valid and compliant with the recent HTML5 specification.
 \item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target.

### 2018-08-14 doc/issre2018/issre2018.tex
Prepared camera ready

@@
 \usepackage{tikz-uml}
-\usepackage{hyperref}
+\usepackage[bookmarks=false]{hyperref}
 \usepackage{upquote}
@@
 
+\newcommand{\jsID}[1]{\texttt{\small #1}}
 \newcommand{\Server}{\emph{Server}\xspace}
@@
 \title{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM
-\thanks{Identify applicable funding agency here. If none, delete this.}
+%\thanks{Identify applicable funding agency here. If none, delete this.}
 }
@@
 \begin{abstract}
-The popularity of JavaScript is enormous.
+The popularity of JavaScript (JS) is enormous.
 Together with HTML and CSS, it is the core technology for modern web development.
@@
 Despite active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS code interacting with the DOM has not yet been addressed.
-In this paper, we present a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
+In this paper, we present a \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
 In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function in combination with the global DOM state.
@@
 \begin{IEEEkeywords}
-JavaScript, search-based testing, branch coverage
+JavaScript, DOM, search-based testing, branch coverage, genetic algorithm
 \end{IEEEkeywords}

### 2018-08-14 doc/issre2018/related-work.tex
Prepared camera ready

@@
 
-The last two decades have been highly productive for the research in JS testing and analysis~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
-Discussing the state-of-the-art in JS testing we cluster the works, by the underlying technique, into the following categories: feedback-directed random generation~\cite{heidegger2010contract,heidegger2012jscontest,kristensen2017type}, symbolic~\cite{tanida2014automatic,saxena2010symbolic} and concolic~\cite{sen2013jalangi,amin:ase15} execution, static~\cite{tajs2009,dom2011} and dynamic~\cite{andreasen2017survey} analysis, formal verification~\cite{gardner2008local,lerner2012modeling,gardner2012towards}, search-based generation~\cite{alshraideh2008complete}, and whole web application testing~\cite{alshahwan2011automated,mesbah2012invariant,milani2014leveraging}.
+The last two decades have been highly productive for the research in JS testing and analysis as revealed by these recent surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
+The JS testing research can be clustered, by the choice of underlying technique, into the following categories: feedback-directed random generation~\cite{heidegger2010contract,heidegger2012jscontest,kristensen2017type}, symbolic~\cite{tanida2014automatic,saxena2010symbolic} and concolic~\cite{sen2013jalangi,amin:ase15} execution, static~\cite{tajs2009,dom2011} and dynamic~\cite{andreasen2017survey} analysis, formal verification~\cite{gardner2008local,lerner2012modeling,gardner2012towards}, search-based generation~\cite{alshraideh2008complete}, and whole web application testing~\cite{alshahwan2011automated,mesbah2012invariant,milani2014leveraging}.
+Let us discuss each separate group of works.
 
@@
 However, as our evaluation has shown, \Confix cannot resolve hard to cover branches.
-\emph{SymJS}~\cite{tanida2014automatic} employs symbolic execution for JS unit-test generation but again has no symbolic stubs for the DOM API.
+\emph{SymJS}~\cite{tanida2014automatic} employs symbolic execution for JS unit testing, but again it has no symbolic stubs for the DOM API.
 
@@
 Jensen et al.~\cite{tajs2009} proposed a static analysis framework \emph{TAJS} for JS type inference.
-Later the analysis was extended to support reasoning about the HTML DOM and browser API~\cite{dom2011}.
+Later the analysis was extended to support reasoning about the DOM and browser API~\cite{dom2011}.
 \emph{TAJS} is able to point to dead code, type violation and references to \emph{undefined} values.
-A review of dynamic analysis techniques ofr JS can be found in a recently published survey~\cite{andreasen2017survey} by Andreasen et al.
+A comprehensive review of JS dynamic analysis techniques can be found in a recently published survey~\cite{andreasen2017survey} by Andreasen et al.
 
-Lerner~\cite{lerner2012modeling} formally models the event behavior in the DOM to establish testing oracles.
+Lerner~\cite{lerner2012modeling} formally models the events behaviors in the DOM to establish testing oracles.
 Gardener et al.~\cite{gardner2012towards} presents a formal verification framework for JS, which can deal with some parts the DOM specification~\cite{gardner2008local}.
@@
 Alshraideh~\cite{alshraideh2008complete} is the first work suggesting to use GA for JS test data generation.
-But the implementation is limited to primitive types such as numbers and strings, and does not report on empirical validation.
-Moreover, it does not support the generation of arrays and DOM.
+But the implementation is limited to primitive types such as numbers and strings (no arrays and DOM), and does not report an empirical validation.
 Recently, SBST has been applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.
-\emph{XMLMATE}~\cite{havrikov2014xmlmate} is the only search-based tool we have encountered that can produce \emph{tree-like} structures such as XML.
-It is built on top of \emph{EvoSuite} with the aim of improving the test coverage of the XML-aware Java programs.
-To generate a random document, it either relies on an existing XML schema, or generates the document from scratch.
+\emph{XMLMATE}~\cite{havrikov2014xmlmate} is the only search-based tool we have encountered that can produce \emph{tree-like} structures.
+It leverages \emph{EvoSuite} as the search-based engine in order to produce an XML input for the testing of Java programs.
+For random generation, it either relies on an existing XML schema, or generates the document from scratch.
 Both tools have a similar approach for the mutation and crossover.
@@
 
-One likely direction for the future extension of \emph{JEDI} is \emph{whole test suite generation}~\cite{fraser2013whole}.
+One likely direction for the future extension of \Jedi is \emph{whole test suite generation}~\cite{fraser2013whole}.
 Such problems usually incur multi-objective optimization~\cite{lakhotia2007multi,panichella2017lips}, e.g.
-a trade-off between coverage and test-suite length.
+a trade-off between coverage and test suite length.
 
-Another direction of future work is re-targeting our tool towards mutation-driven generation of unit tests and oracles~\cite{fraser2012mutation}.
-That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.
+Another future direction is the mutation testing\cite{fraser2012mutation}, which should help to evaluate the fault revealing capability of \Jedi.
 
-Similar to \cite{baars2011symbolic, galeotti2013improving}, it could be worth to combine search-based generation with concolic (symbolic) execution, e.g.
-investigate the integration of \Jedi with \Jalangi.
+Search-based testing can be strengthened with concolic execution~\cite{baars2011symbolic, galeotti2013improving}. For example, it worth of investigation how to integrate \Jalangi into \Jedi.
 
-We plan to validate \Jedi on a larger set of examples.
-Towards this goal, we have to extend our framework with the support of such input types as user-defined classes and high-order functions.
-The first extension is straightforward since any class can be described as the collection of the types of class fields.
+We plan to conduct larger evaluation of \Jedi.
+Therefore, the framework should be extended to support user-defined objects and high-order functions.
+The first requirement is straightforward since an object can be described as the collection of fields.
 To generate functions as inputs we could employ an approach similar to QuickCheck~\cite{koopman2006automatic}.

### 2018-10-09 doc/issre2018/presentation/issre18_slides.tex
Added presentation for issre 2018.

\documentclass{beamer}
\usepackage[utf8]{inputenc}
%\usepackage[latin1]{inputenc}
\usepackage{pifont}   %% tick and times symbols
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{tabulary}
\usepackage{savesym}
\savesymbol{checkmark}
\usepackage{dingbat}
\usepackage{tabu}
\usepackage{listingsutf8}
%\usepackage{listings}
\usepackage{tikz} 
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{color, colortbl}
%\usepgfplotslibrary{clickable}
\usetikzlibrary{shapes.callouts, decorations.text, decorations.pathreplacing, arrows.meta, automata, positioning, shapes.geometric}
\usepackage{hyperref}
%\usepackage{multimedia}
%\usepackage{media9}
\usepackage{multirow}
\usepackage{numprint} % provides rounding of float numbers 
\usepackage{pdfpages}
\usepackage{adjustbox}
\usepackage{pgf-umlsd}
\usepackage{algorithmic}
\usepackage[titlenotnumbered, linesnumbered]{algorithm2e}
\usepackage{booktabs} % For formal tables
\usetheme{uucs}
\setbeamercovered{invisible}

\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = uuyblue, %Colour for external hyperlinks
  linkcolor    = uuyred, %Colour of internal links
  citecolor    = uuygreen %Colour of citations
}

\newcommand{\Random}{\mathbb{R}}
\newcommand{\Genetic}{\mathbb{G}}
\newcommand{\RGenetic}{\mathbb{G}_{10}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{ltblue}{rgb}{0,0.4,0.4}
\definecolor{dkblue}{rgb}{0,0.1,0.6}
\definecolor{dkgreen}{rgb}{0,0.4,0}
\definecolor{dkviolet}{rgb}{0.3,0,0.5}
\definecolor{dkred}{rgb}{0.5,0,0}

\definecolor{lightgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{darkgray}{rgb}{0.4, 0.4, 0.4}
%\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\definecolor{editorGray}{rgb}{0.95, 0.95, 0.95}
\definecolor{editorOcher}{rgb}{1, 0.5, 0} % #FF7F00 -> rgb(239, 169, 0)
\definecolor{editorGreen}{rgb}{0, 0.5, 0} % #007C00 -> rgb(0, 124, 0)
\definecolor{orange}{rgb}{1,0.45,0.13}		
\definecolor{olive}{rgb}{0.17,0.59,0.20}
\definecolor{brown}{rgb}{0.69,0.31,0.31}
\definecolor{purple}{rgb}{0.38,0.18,0.81}
\definecolor{lightblue}{rgb}{0.1,0.57,0.7}
\definecolor{lightred}{rgb}{1,0.4,0.5}
% CSS
\lstdefinelanguage{CSS}{
  keywords={color,background-image:,margin,padding,font,weight,display,position,top,left,right,bottom,list,style,border,size,white,space,min,width, transition:, transform:, transition-property, transition-duration, transition-timing-function},	
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]",
  alsoletter={:},
  alsodigit={-}
}

% JavaScript
\lstdefinelanguage{JavaScript}{
  morekeywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, for},
  morecomment=[s]{/*}{*/},
  morecomment=[l]//,
  morestring=[b]",
  morestring=[b]'
}

\lstdefinelanguage{HTML5}{
  language=html,
  sensitive=true,	
  alsoletter={<>=-},	
  morecomment=[s]{<!-}{-->},
  morestring=[b]'
  tag=[s],
  otherkeywords={
  % General
  >,
  % Standard tags
	<!DOCTYPE,
  </html, <html, <head, <title, </title, <style, </style, <link, </head, <meta, />,
	% body
	</body, <body,
	% Divs
	</div, <div, </div>, 
	% Paragraphs
	</p, <p, </p>,
	% scripts
	</script, <script,
  % More tags...
  <canvas, /canvas>, <svg, <rect, <animateTransform, </rect>, </svg>, <video, <source, <iframe, </iframe>, </video>, <image, </image>, <header, </header, <article, </article
  },
  ndkeywords={
  % General
  =,
  % HTML attributes
  charset=, src=, id=, width=, height=, style=, type=, rel=, href=,
  % SVG attributes
  fill=, attributeName=, begin=, dur=, from=, to=, poster=, controls=, x=, y=, repeatCount=, xlink:href=,
  % properties
  margin:, padding:, background-image:, border:, top:, left:, position:, width:, height:, margin-top:, margin-bottom:, font-size:, line-height:,
	% CSS3 properties
  transform:, -moz-transform:, -webkit-transform:,
  animation:, -webkit-animation:,
  transition:,  transition-duration:, transition-property:, transition-timing-function:,
  }
}

\lstdefinelanguage{HTML5}{
  language=html,
  tagstyle=\color{blue},
  markfirstintag=true,
  sensitive=true,
  alsoletter={<>=-},	
  morecomment=[s]{<!--}{-->},
  % tag=[s],
  %% morestring=[b]'',
  morestring=[b]',
  ndkeywords={
    % General
    =,
    % HTML attributes
    id=, class= 
  }
}

\lstdefinestyle{htmlcssjs} {%
  % General design
  backgroundcolor=\color{editorGray},
  basicstyle={\scriptsize\ttfamily},   
  %frame=tb,
  % line-numbers
  xleftmargin={0.75cm},
  numbers=left,
  stepnumber=1,
  firstnumber=1,
  numberfirstline=true,	
  % Code design
  identifierstyle=\color{black},
  keywordstyle=\color{blue}\bfseries,
  ndkeywordstyle=\color{editorGreen}\bfseries,
  stringstyle=\color{editorOcher}\ttfamily,
  commentstyle=\color{brown}\ttfamily,
  % Code
  language=JavaScript,
  alsolanguage=HTML5,
  alsodigit={.:;},	
  tabsize=2,
  showtabs=false,
  showspaces=false,
  showstringspaces=false,
  extendedchars=true,
  breaklines=true,
  escapechar=|c
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[ISSRE]{Test Data Generation for JavaScript Functions that Interact with the DOM}
\author[Elyasov et al.]{Alexander Elyasov, Wishnu Prasetya, \textbf{Jurriaan Hage}}
\institute[Universities Utrecht and Valencia]{
Utrecht University, The Netherlands \\ \texttt{alex.elyasov@gmail.com}
}
\date[ISSRE '18]{ISSRE '18, Memphis, TN, US}

\begin{document}
\frontmatter

\begin{frame}
  \titlepage
\end{frame}

\mainmatter

\begin{frame}
  \frametitle{Outline}
  %\transduration{10}
  \tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}{StackOverflow Developer Survey}

  \footnotesize
  \begin{itemize}
    \item For the sixth year in a row, \emph{JavaScript} is the most commonly used programming language
    \item \emph{Node.js} and \emph{AngularJS} continue to be the most commonly used technologies, with \emph{React} also important to many developers
  \end{itemize}

  \begin{columns}
    \column{.5\textwidth}{
      \centering
      \includegraphics[scale=0.2]{JS_Popular.png}
    }

    \column{.5\textwidth}{
      \centering
      \includegraphics[scale=0.2]{NodeJS_Popular.png}
    }
  \end{columns}

  \begin{tikzpicture}[overlay]
    \draw[uuxred,line width=0.3mm] (0.2,3.3) rectangle (4.2,3.05);
    \draw[uuxred,line width=0.3mm] (6,3.3) rectangle (10,2.55);
  \end{tikzpicture}

\end{frame}

\begin{frame}{The State of JavaScript Testing}

  \begin{itemize}
    \item There exist numerous JS frameworks on the market:
      \begin{itemize}
        \item structure: Mocha, Jasmine
        \item assertions: Chai
        \item mocks and spies: Sinon
        \item coverage: Istanbul
        \item reporting: Karma
      \end{itemize}
   \item Developers report a relatively low happiness score with the state of testing tools
  \end{itemize}

  \centering{
    \includegraphics[width=10cm]{Unhappy_Devs.png}
  }
\end{frame}

\begin{frame}{Goal}
  \centering{
      \includegraphics[width=7cm]{make.png}
  }
\end{frame}

\begin{frame}{Eureka!}
  \centering{
    \includegraphics[width=7cm]{solution.png}
  }
\end{frame}

\begin{frame}{Test Input Generation}
  \begin{block}{Available techniques}
    \begin{itemize}
    \item concolic execution: \emph{Jalangi} and \emph{Confix}
    \item random generation: \emph{JSContest}
    \item static and dynamic analysis: \emph{Artemis}
    \item crawling: \emph{Crawljax}   
  \end{itemize}
  \end{block}

  \begin{block}{Input types}
    \begin{itemize}
      \item primitive types: numbers and strings
      \item collections: arrays
      \item objects
      \item DOM (focus of this paper)
      \item functions  
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Solution}

  \emph{JEDI}: \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput

  \begin{block}{Contributions}
    \begin{itemize}
  \item implemented JEDI
  \item test generation algorithm
  \item  evaluation
    \end{itemize}
  \end{block}
\end{frame}

\section{Motivation Example}

\begin{frame}{Sudoku}
  \centering{
    \includegraphics[width=7cm]{sudoku.png}
  }
\end{frame}

\begin{frame}[fragile]{isGameFinished}

\begin{figure}
  \centering
  \begin{lstlisting}[style=htmlcssjs,language=JavaScript,basicstyle={\tiny\ttfamily}]
/*t dom */
function isGameFinished() {
  var obj = document.getElementById('sudoku'); 
  var subDivs = obj.getElementsByTagName('DIV'); 
  var allOk = true;
  for (var no = 0; no < subDivs.length; no++) { 
    if (subDivs[no].className.indexOf('square') >= 0 
        && !subDivs[no].style.backgroundColor) {
      var spans=subDivs[no].getElementsByTagName('SPAN');
      if (spans[0].innerHTML != spans[1].innerHTML) { 
       allOk = false; //target 
       break;
      }
    }
  } 
  return allOk;
}
  \end{lstlisting}
\end{figure}

\end{frame}

\begin{frame}[fragile]{DOM Tests}

\begin{figure}
  \begin{lstlisting}[style=htmlcssjs,language=HTML5,basicstyle={\tiny\ttfamily}]
<!-- T1: (5,5) -->            <!-- T2: (5,6), (7,15) -->
<html>                        <html>
 <body>                        <body>
  <div id='sudoku'>             <div id='sudoku'>
                                 <div></div>
  </div>                        </div>
 </body>                       </body>
</html>                       </html>

<!-- T3: (7,8), (10,14) -->   <!-- T4: (7,8), (10,11) -->
<html>                        <html>
 <body>                        <body>
  <div id='sudoku'>             <div id='sudoku'>
   <div class='square'>          <div class='square'>
    <span></span>                 <span></span>
    <span></span>                 <span>TEST</span>
   </div>                        </div>
  </div>                        </div>
 </body>                       </body>
</html>                       </html>
  \end{lstlisting}
\end{figure}

\pause

  \begin{tikzpicture}[overlay]
    \draw[uuxred,line width=0.4mm] (4.5,4.1) rectangle (9,1);
  \end{tikzpicture}

\end{frame}

\begin{frame}[fragile]{T4 Explained}
\begin{adjustbox}{width=10cm}     \begin{lstlisting}[style=htmlcssjs,language=JavaScript,basicstyle={\tiny\ttfamily},mathescape=true]
/*t dom */
function isGameFinished() {
  var obj = document.getElementById('sudoku');   // $\mbox{\leftpointright}$ <div id='sudoku'>
  var subDivs = obj.getElementsByTagName('DIV'); // $\mbox{\leftpointright}$ <div class='square'>
  var allOk = true;
  for (var no = 0; no < subDivs.length; no++) { 
    if (subDivs[no].className.indexOf('square') >= 0  // $\mbox{\leftpointright}$ class='square'
        && !subDivs[no].style.backgroundColor) {
      var spans=subDivs[no].getElementsByTagName('SPAN');//$\mbox{\leftpointright}$ <span></span>
      // $\mbox{\leftpointright}$ <span>TEST</span>
      if (spans[0].innerHTML != spans[1].innerHTML) { 
       allOk = false; //target 
       break;
      }
    }
  } 
  return allOk;
}
  \end{lstlisting}
  \end{adjustbox}
\end{frame}

\section{Test Generation Framework}

\begin{frame}{Initialization Phase}
  \begin{figure}[!t]
  \centering
\tikzset{
  % add this style to all tikzpicture environments
  every picture/.append style={
    % enable scaling of nodes
    transform shape,
    % set scale factor
    scale=0.7
  }
}
  \begin{sequencediagram}[font=\footnotesize]

    \renewcommand\unitfactor{0.6}
    \newinst{user}{\textbf{User}}
    \newinst[1]{server}{\textbf{Server}}
    \newinst[4]{validator}{\textbf{Validator}}
    \newinst[1]{client}{\textbf{Client}}

    \begin{call}{user}{fun.js + config}{server}{\textbf{end}}
      \begin{call}{server}{Initialize(fun.js)}{server}{(cfg, branches, cinfo, ifun, sig)}
      \end{call}

      \begin{call}{server}{POST /init \{ifun, sig\}}{client}{status}
      \end{call}

      \begin{call}{server}{Select(branches)}{user}{$\text{branches}'$}
      \end{call}

    \end{call}
  \end{sequencediagram}
\end{figure}

\end{frame}

\begin{frame}{Algorithm I: Initialization Phase}
\begin{algorithm}[H]
  %% \algsetup{linenosize=\tiny} %% COMMENTED OUT IN PHD
  \footnotesize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Input{JS file $fun.js$ with FUT and type annotation }
  \Output{Tuple $(cfg, branches, cinfo, ifun, sig)$}
  \Fn{$Initialize(fun.js)$}{

    $(ast, sig) \longleftarrow ParseFuncAndSig(fun.js)$\label{alg.init.parse.fun.sig}\;
    $cinfo \longleftarrow GetConstantInfo(ast)$\label{alg.init.collect.info}\;
    $nast \longleftarrow NormalizeAST(ast)$\label{alg.init.transform.ast}\;
    $ifun \longleftarrow Instrument(nast)$\label{alg.init.instr}\;
    $cfg \longleftarrow BuildCFG(nast)$\label{alg.init.build.cfg}\;
    $branches \longleftarrow GetBranches(cfg)$\label{alg.init.get.branches}\;
    \Return{$(cfg, branches, cinfo, ifun, sig)$}
    }
\end{algorithm}
\end{frame}

\begin{frame}{Supported Types}
\begin{block}{Type Annotation}
  /*t dom : bool : int : float : string : [int]  */
\end{block}
\begin{itemize}
\item primitive types: bool, int, float, sting
\item arrays
\item DOM
\item could be extended to objects
\end{itemize}
\end{frame}

\begin{frame}{Instrumentation}
\begin{itemize}
  \item \emph{trace} records the sequence of executed statements of the FUT
  \item \emph{branchDistance} contains the distance from the target branch
  \item \emph{loopMap} captures the upper bound for the number for-loop iterations  
\end{itemize}
\end{frame}

\begin{frame}{Genetic Phase}
\begin{figure}[!t]
  \centering
\tikzset{
  % add this style to all tikzpicture environments
  every picture/.append style={
    % enable scaling of nodes
    transform shape,
    % set scale factor
    scale=0.4
  }
}
  \begin{sequencediagram}[font=\normalsize]

    \renewcommand\unitfactor{0.55}
    \newinst{user}{\textbf{User}}
    \newinst[1]{server}{\textbf{Server}}
    \newinst[7]{validator}{\textbf{Validator}}
    \newinst[1]{client}{\textbf{Client}}

      \begin{sdblock}{\textbf{Genetic Loop}}{\small \hspace{8mm}$\text{branch} \in \text{branches}'$}
        \begin{sdblock}{\textbf{Random Loop}}{\small errors $>$ 0}
          \begin{call}{server}{pop = Random(cinfo, config)}{validator}{errors}
          \end{call}
          %\prelevel
        \end{sdblock}

        \begin{sdblock}{\textbf{Fitness Loop}}{\small (fitness $\neq$ 0) $\vee$ gen.limit}

          \begin{sdblock}{\textbf{Evaluation Loop}}{\small p $\in$ pop}
            \begin{call}{server}{POST /genetic \{p\}}{client}{response = ifun(p: sig)}
            \end{call}

            \begin{callself}{server}{Evaluate(branch, cfg, response)}{fitness}
            \end{callself}
            % \prelevel
          \end{sdblock}

          \begin{sdblock}{\textbf{Crossover Loop}}{\small errors $>$ 0}
            \begin{call}{server}{cross = Crossover(cinfo, pop)}{validator}{errors}
            \end{call}
            %\prelevel
          \end{sdblock}

          \begin{sdblock}{\textbf{Mutation Loop}}{\small errors $>$ 0}
            \begin{call}{server}{mut = Mutation(cinfo, pop)}{validator}{errors}
            \end{call}
            %\prelevel
          \end{sdblock}

          \begin{callself}{server}{pop = cross $\cup$ mut}{pop}
          \end{callself}
          %\prelevel
        \end{sdblock}
        \mess{server}{best fitness}{user}

      \end{sdblock}
  \end{sequencediagram}
\end{figure}
\end{frame}

\begin{frame}{HTML Generation}
  \begin{block}{Random}
    \begin{itemize}
      \item DSL for the generation of syntactically valid HTML documents composed of arbitrary \emph{tags} and \emph{attributes}
      \item multiple options for the parameterization: tree width and depth, tags frequency, etc.  
    \end{itemize} 
  \end{block}

  \begin{block}{GA operations}
    \begin{itemize}
      \item \emph{crossover} two HTML trees at a randomly chosen node
      \item HTML tree \emph{mutations}: \textit{NewTree}, \textit{DropTree} and \textit{ShuffleAttributes} (e.g. 'id' and 'class') 
    \end{itemize}
  \end{block}

  \end{frame}

\begin{frame}{Fitness Function (FF)}
\scriptsize
\begin{block}{FF for a node}
\begin{equation*}
F(n) = \textit{approach\_level} +
\begin{cases}
 1/2 * (\frac{\textit{branch\_distance}}{1 + \textit{branch\_distance}}) & \text{if no exception}\\
 1                                  & \text{otherwise}
\end{cases}
\end{equation*}
\begin{itemize}
  \item \emph{approach\_level} is the number of decision nodes between the target and the problem node (in JS every node can be exceptional)
  \item \emph{branch\_distance} measures the deviation explicitly in the problem node
\end{itemize}
\end{block}

\begin{block}{FF for a node sequence}
  \begin{equation*}
F^*(n_b, n_x) = (F(n_b), F(n_x))
\end{equation*}
\begin{itemize}
\item $n_b$ is a target branch node
\item $n_x$ is a terminal exit node
\item Can be generalized to: $F^*(n_1, n_2, \ldots, n_k) = (F(n_1), F(n_2), \ldots, F(n_k))$
\end{itemize}
\end{block}

\end{frame}

\begin{frame}{GA with Restart}
\begin{block}{Problem}
GA sometimes reaches a local minimum and stagnates due to flag variables, nested predicates, or unstructured control flow.
\end{block}
\begin{itemize}
  \item Common solution it to incorporate data dependency into the search, e.g. \emph{chaining approach}~\cite{ferguson1996chaining}
  \item Our approach is CFG-based because JS is a dynamic language which is hard to analyze for data dependency
  \item We suggest to restart GA with a new target when the fitness progress stops during a configured \emph{history window}
  \item The \emph{new target} consists of the original target prefixed by a dominating CFG node  
\end{itemize}
\end{frame}

\section{Empirical Evaluation}

\begin{frame}{Genetic Algorithm Configurations}

\begin{block}{Variations of Generation Algorithms}
\begin{itemize}
\item $\Random$  random
\item $\Genetic$  pure genetic
\item $\RGenetic$ genetic with restart
\end{itemize}

\end{block}

\begin{table}[!t]
  \footnotesize
  \centering
  \begin{tabular}{l|r|r|r}
    \toprule
    \textbf{Parameter Name} &$\Random$&$\Genetic$ &$\RGenetic$ \\
    \hline
    Population size                   & 50  & 50  & 50  \\
    Archive size                      & 1   & 25  & 25  \\
    Maximum number of generations     & 200 & 200 & 200 \\
    Crossover rate                    & 0   & 0.5 & 0.5 \\
    Mutation rate                     & 0   & 0.5 & 0.5 \\
    History window size               & -   & -   & 10  \\
    \bottomrule
  \end{tabular}
\end{table}
\end{frame}

\begin{frame}{Case Studies}
\setlength\tabcolsep{3pt}
\begin{table}[!t]
  %\resizebox{\textwidth}{!}{
    \tiny
    \centering
  \begin{tabular}{l|l|c|c|c|c|c|c|c|c}
    \toprule
    \textbf{case-study} & \textbf{function} & \textbf{loc} & \textbf{c} & \textbf{d} & \textbf{cc} & \textbf{dom} & \textbf{id} & \textbf{tag} & \textbf{class} \\
    \hline
    sudoku     & helpMe(int,int)    & 14 & 2 & 3 & 3 & + & + & + & - \\
    sudoku     & isGameFinished()    & 10 & 3 & 3 & 4 & + & + & + & + \\
    sudoku     & newGame()           & 9  & 1 & 2 & 2 & + & + & + & + \\
    sudoku     & revealAll()         & 8  & 0 & 2 & 1 & + & + & + & - \\
    %% sudoku     & - & showCell & (dom)          & 8  & 0 & 0 & 1 & + & + & + & - \\
    sudoku     & shuffleBoard(int,int)      & 23 & 2 & 3 & 3 & + & - & + & - \\
    %% sudoku     & - & switchLevel & (dom,bool)  & 10 & 1 & 2 & 2 & + & - & + & - \\
    \hline
    phormer    & toggleInfo(string)                                                     & 16 & 3 & 1 & 4 & + & + & - & - \\
    %% \multirow{2}{*}{phormer}    & \multirow{2}{*}{-} & \multirow{2}{*}{update} & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &   &   &   &   &   &   & \\
    %%            &   &        &                                                                      & 35 & 5 & 3 & 6 & + & + & - & - \\
    %% phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & + & + & - & - \\
    \hline
    %% hotel RS   & - & RequiredField & (dom,[string])  & 11 & 2 & 2 & 5 & + & + & - & - \\
    hotel RS   & isValidCard([int])           & 17 & 2 & 2 & 5 & - & - & - & - \\
    %% hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & - & - & - & - \\
    hotel RS   & isValidVISA([int])           & 6  & 3 & 1 & 6 & - & - & - & - \\
    %% hotel RS   & - & validateNumber & (dom,string)   & 7  & 1 & 1 & 4 & + & + & - & - \\
    \hline
    %% apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & + & + & - & -\\
    %% apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & + & + & - & - \\
    %% apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & - & - & - & - \\
    %% apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & + & + & - & - \\
    apophis    & initShields([int],int,int)                                              & 6  & 0 & 1 & 1 & + & + & - & -\\
    \hline
    bingbong   & brickJiggler(int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
    bingbong   & doPaddlePower(int,int)                            & 15 & 2  & 1 & 3  & + & + & - & - \\
    bingbong   & initBricks(int,[int],[int],[int],[int],int,[string])                         & 70 & 12 & 4 & 13 & + & + & - & - \\
    %% bingbong   & - & drawLevel & (dom,int,int,int,int)                        & 22 & 2  & 3 & 3  & + & + & - & - \\
    %% bingbong   & - & goPing & (dom,int,int,int)                               & 12 & 2  & 2 & 3  & + & + & - & - \\
    \hline
    burncanvas & do\_draw(int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & - & - & - & - \\
    %% \hline
    %% cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & -  & -  & - & - \\
    %% cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & -  & -  & - & - \\
    \hline
    mathjs     & prob\_gamma(float)                                   & 57 & 8  & 2 & 16 & - & - & - & - \\
    \bottomrule
  \end{tabular}
%}
\end{table}

\begin{itemize}
\item if $\text{CC} < 10$ then the function is \emph{easy to test} else \emph{difficult} 
\end{itemize}

\end{frame}

\begin{frame}{Research Questions}
\begin{description}
\item[RQ1] What is the branch coverage?
\item[RQ2] What is the coverage time per branch?
\item[RQ3] Are the results statistically significant?
\item[RQ4] What is the branch coverage of \emph{Confix}?
\end{description}
\end{frame}

\section{Results}

\begin{frame}{RQ1: What is the branch coverage?}

  \begin{table}
    \footnotesize
    \caption{Branch coverage (\%)}
    \begin{tabular}{c|ccc}
      \toprule
      \textbf{TYPE}  & $\Random$  & $\Genetic$ & $\RGenetic$\\
        \midrule
      \textbf{simple (23)}    & 79 & 97 & 100  \\
      \textbf{difficult (33)} & 58 & 94 & 100 \\
      \midrule
      \textbf{global (56)}    & 63 & 95 & 100 \\
      \bottomrule
    \end{tabular}
  \end{table}

  \begin{block}{}
    Across all subjects, the $\RGenetic$ algorithm achieved 100\% branch coverage, with $\Genetic$ in the second place with 95\% coverage, and, finally, $\Random$ with  63\% coverage.
  \end{block}

\end{frame}

\begin{frame}{RQ1: Branch Coverage Progress}
  \begin{tikzpicture}[scale=0.9]
    \begin{axis}[
        xlabel={Time budget per branch (seconds)},
        ylabel={Number of covered branches},
        width=10cm,height=6.6cm,
        xmin=0, xmax=150,
        ymin=10, ymax=58,
        xtick={0,5,10,30,60,90,120,150,180},
        ytick={0,10,20,30,40,50},
        legend pos=south east,
        ymajorgrids=true,
        % xmajorgrids=true,
        grid style=dashed,
        label style={font=\small}
      ]

      \addplot[
        color=blue,
        mark=square*,
      ] coordinates {
        (5,13) (10,15) (30,25) (60,28) (90,29) (120,30) (150,31)
      };
      \addplot[
        color=red,
        mark=triangle*,
      ]  coordinates {
        (5,27) (10,37) (30,48) (60,52) (90,54) (120,54) (150,54)
      };
      \addplot[
        color=yellow,
        mark=*,
      ]   coordinates {
        (5,27) (10,35) (30,50) (60,54) (90,55) (120,56) (150,58)
      };
      \legend{$\Random$,$\Genetic$,$\RGenetic$}

    \end{axis}
  \end{tikzpicture}

  \begin{block}{}
    $\Genetic$ could be more suitable for rapid testing during development, whereas $\RGenetic$ for integration
  \end{block}

\end{frame}

\begin{frame}{RQ2: What is the coverage time per branch?}

  \begin{table}
    \footnotesize
    \centering
    \caption{Average execution time per brunch (sec.)}
    \begin{tabular}{c|ccc}
      \toprule
      \textbf{TYPE} & $\Random$ & $\Genetic$ & $\RGenetic$ \\
      \midrule
      \textbf{simple (23)}    & 37  & 9  & 7   \\
      \textbf{difficult (33)} & 112 & 56 & 25  \\
      \midrule
      \textbf{global (56)}    & 88  & 39 & 19  \\
      \bottomrule
    \end{tabular}
  \end{table}

\begin{block}{}
  $\RGenetic$ outperformed both $\Genetic$ and $\Random$ with an average execution time per branch of 19, 39 and 88 seconds, respectively.
\end{block}

\begin{block}{}
    On average, one algorithm iteration took one second for $\Random$ and $\RGenetic$, $\Genetic$ performed somewhat worse at 1.4 seconds.
\end{block}

\end{frame}

\begin{frame}{RQ3: Are the results statistically significant?}
  \footnotesize
  \begin{table}
     \scriptsize
     \centering
     %\caption{Significance and effect size}
     \begin{tabular}{c|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
      \toprule
      \multirow{2}{*}{\textbf{TYPE}} & \multicolumn{3}{c|}{$\Random / \Genetic$} & \multicolumn{3}{c|}{$\Random / \RGenetic$} & \multicolumn{3}{c}{$\Genetic / \RGenetic$} \\
      \cline{2-10}
      %\hline
                              & L  & M  & S  & L  & M  & S  & L & M & S \\
      \midrule
      \textbf{simple (23)}    & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
      \textbf{difficult (33)} & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
      \midrule
      \textbf{global (56)}    & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
      \bottomrule
    \end{tabular}
\end{table}

\begin{itemize}
  \item Use the non-parametric Mann-Whitney U-test and the Vargha-Delaney $\hat{A}_{12}$ statistics for measuring statistical significance ($\alpha=0.05$) and effect size~\cite{arcuri2011practical}
    \item L - large  (0.71), M - medium (0.64), S - small (0.56)
\end{itemize}

\begin{block}{}
    Both $\Genetic$ and $\RGenetic$ largely outperform $\Random$ in 50\% cases generally across the board and 67\% on the difficult functions.
\end{block}
\end{frame}

\begin{frame}{RQ4: What is the branch coverage of Confix?}
\begin{table}
  \scriptsize
  \setlength\tabcolsep{2pt}
    \begin{tabular}{c|l|c|c|c|c|c}
      \toprule
      \textbf{case-study} & \textbf{function} & \textbf{\#BR} & \textbf{\#C (weak)} & \textbf{\#C (strong)} & \textbf{\#tests} & \textbf{time (sec.)} \\
      \hline
      sudoku & helpMe          & 5  & 4 (80\%)  & 4 (80\%)  & 2 & 5 \\
      sudoku & isGameFinished  & 5  & 2 (40\%)  & 2 (40\%)  & 2 & 5 \\
      sudoku & newGame         & 3  & 3 (100\%) & 3 (100\%) & 4 & 6 \\
      sudoku & revealAll       & 2  & 2 (100\%) & 0 (0\%)   & 6 & 11 \\
      sudoku & shuffleBoard    & 7  & 5 (71\%)  & 0 (0\%)   & 2 & 5  \\
      \hline
      phormer & toogleInfo     & 4  & 2 (50\%)  & 2 (50\%)  & 3 & 5 \\
      \hline
      apophis & initShields    & 1  & 0 (0\%)   & 0 (0\%)   & 1 & 6 \\
      \hline
      bingbong & brickJiggler  & 2  & 0 (0\%)   & 0 (0\%)   & 1  & 3 \\
      bingbong & doPaddlePower & 4  & 2 (50\%)  & 2 (50\%)  & 1  & 4 \\
      bingbong & initBricks    & 18 & 3 (17\%)  & 0 (0\%) & 1  & 3 \\
      \bottomrule
    \end{tabular}
\end{table}
\begin{block}{}
The choice between a concolic and search-based approach is a trade-off between a labour-intensive modelling and execution time, respectively, where both can reinforce each other.
\end{block}

\end{frame}

\begin{frame}{Threats to Validity}
\begin{itemize}
  \item \emph{construct validity}: measured only branch coverage and execution time
    \begin{itemize}
      \item it doesn't indicate fault finding capability
      \item use only ``natural'' oracles such as exception
      \item ignore test case size
    \end{itemize}    
  \item \emph{internal validity}: choice of the initial GA configuration 
  \item \emph{conclusion validity}: stochastic nature of the experiment
  \item \emph{external validity}: limited set of experimental subjects 
\end{itemize}
\end{frame}

\section{Future Work and Conclusions}

\begin{frame}{Future Work}
\begin{itemize}
  \item the whole test suite generation based on multi-objective optimization to balance coverage and test suite size~\cite{panichella2017lips}
    \item mutation driven test generation~\cite{fraser2012mutation}; should allow us to evaluate fault finding capability
    \item combine search-based with concolic test generation for JavaScript, e.g. integrate \emph{Jalangi}~\cite{sen2013jalangi} and~\emph{Confix}~\cite{amin:ase15}
      \item conduct large evaluation of \emph{JEDI}; it requires the extension of arbitrary input objects and functional arguments~\cite{claessen2011quickcheck, selakovic2018test}
\end{itemize}
\end{frame}

\begin{frame}{Conclusions}
  \begin{itemize}
    \item introduced a novel search-based JS unit testing framework, called \emph{JEDI}, which is able to generate arbitrary DOM inputs
     \item presented a test generation algorithm ---``genetic with restart''; it is capable of escaping plateaus by concretizing the search target
     \item conduced an empirical validation followed by the significance study, which has confirmed the effectiveness and efficiency of our framework in branch coverage testing

  \end{itemize}
\end{frame}

\begin{frame}[t,allowframebreaks]{References}
\tiny
\bibliographystyle{alpha}
\bibliography{issre2018}
\end{frame}

\begin{frame}{The End}
\begin{center}
  \vspace{-2em}
  \emph{Thanks for attention!}\\
  \vspace{1em}
  \emph{Questions?}\\
  \vspace{2em}
  %% \href{http://www.facebook.com/FITTESTproject}{\includegraphics[height=1.5cm,keepaspectratio]{pict/logo/facebook}}~%
  %% \href{https://plus.google.com/112865571538811672642}{\includegraphics[height=1.5cm,keepaspectratio]{pict/logo/gplus}}~%
  \href{https://github.com/aelyasov/JSDomTest}{\includegraphics[height=1.5cm,keepaspectratio]{pict/logo/git}}%
\end{center}
\end{frame}

\end{document}

### 2018-10-09 doc/issre2018/presentation/pict/ShoppingCart1_files/api.js

@@ -1,0 +1,7 @@
+var gapi=window.gapi=window.gapi||{};gapi._bs=new Date().getTime();(function(){var f=encodeURIComponent,g=window,k=decodeURIComponent,m="push",n="test",s="shift",t="replace",x="length",A="split",B="join";var C=g,D=document,aa=C.location,ba=function(){},ca=/\[native code\]/,F=function(a,b,c){return a[b]=a[b]||c},da=function(a){for(var b=0;b<this[x];b++)if(this[b]===a)return b;return-1},ea=function(a){a=a.sort();for(var b=[],c=void 0,d=0;d<a[x];d++){var e=a[d];e!=c&&b[m](e);c=e}return b},G=function(){var a;if((a=Object.create)&&ca[n](a))a=a(null);else{a={};for(var b in a)a[b]=void 0}return a},H=F(C,"gapi",{});var I;I=F(C,"___jsl",G());F(I,"I",0);F(I,"hel",10);var J=function(){var a=aa.href,b;if(I.dpo)b=I.h;else{b=I.h;var c=RegExp("([#].*&|[#])jsh=([^&#]*)","g"),d=RegExp("([?#].*&|[?#])jsh=([^&#]*)","g");if(a=a&&(c.exec(a)||d.exec(a)))try{b=k(a[2])}catch(e){}}return b},fa=function(a){var b=F(I,"PQ",[]);I.PQ=[];var c=b[x];if(0===c)a();else for(var d=0,e=function(){++d===c&&a()},h=0;h<c;h++)b[h](e)},K=function(a){return F(F(I,"H",G()),a,G())};var L=F(I,"perf",G()),M=F(L,"g",G()),ga=F(L,"i",G());F(L,"r",[]);G();G();var N=function(a,b,c){var d=L.r;"function"===typeof d?d(a,b,c):d[m]([a,b,c])},P=function(a,b,c){b&&0<b[x]&&(b=O(b),c&&0<c[x]&&(b+="___"+O(c)),28<b[x]&&(b=b.substr(0,28)+(b[x]-28)),c=b,b=F(ga,"_p",G()),F(b,c,G())[a]=(new Date).getTime(),N(a,"_p",c))},O=function(a){return a[B]("__")[t](/\./g,"_")[t](/\-/g,"_")[t](/\,/g,"_")};var R=G(),S=[],T=function(a){throw Error("Bad hint"+(a?": "+a:""));};S[m](["jsl",function(a){
[…]

### 2018-10-09 doc/issre2018/presentation/pict/ShoppingCart1_files/mainjs-v8.js

@@ -1,0 +1,3773 @@
+//SETTING UP OUR POPUP
+//0 means disabled; 1 means enabled;
+var popupStatus = 0;
+var toppp=0;
+function loadPopup()
+{
+	if(popupStatus==0)
+	{
+		$("#msgbox_window").css('width','962px');
+		$("#backgroundPopup").css({ "height": "100%" });
+		$("#backgroundPopup").show('fade');
+		$("#msgbox_window").show('fade');
+		centerPopup();
+		popupStatus = 1;
+	}
+}
+
+function disablePopup()
+{
+	if(popupStatus==1){
+		$("#backgroundPopup").hide('fade');
+		$("#msgbox_window").hide('fade');
+		popupStatus = 0;
+		$('#backgroundPopup,#msgbox_window').remove();
+	}
+}
+
+function centerPopup()
+{
+	var windowWidth = $(window).width();
+	var windowHeight = $(window).height();
+	var popupHeight = $("#msgbox_window").height();
+	var popupWidth = $("#msgbox_window").width();
+	$("#msgbox_window").css({
+		"position": "absolute",
+		"top": toppp,
+		"left": (windowWidth-popupWidth)/2+document.body.scrollLeft
+	});
+	//only need force for IE6
+	$("#backgroundPopup").css({ "height": windowHeight+document.body.scrollTop, "filter": "alpha(opacity=40)" });
+}
+
+function scrollTOP() {
+     $('html, body').animate({
+         scrollTop: 100
+     }, 1000);            
+}
+
+// cookies (cookies0.js)
+function setCookie2(name, value, expires, path, domain, secure)
+	{
+	if (!expires)
+		expires=365;
+	var today = new Date();
+	var expires2 = new Date(today.getTime()+1000*60*60*24*expires);
+	document.cookie= name + "=" + escape(value) +
+		((expires) ? "; expires=" + expires2.toGMTString() : "") +
+		((path) ? "; path=" + path : "; path=/") +
+		((domain) ? "; domain=" + domain : "; domain=.dreamstime.com") +
+		((secure) ? "; secure" : "");
+	}
+
+function setCookie(name, value, expires, path, domain, secure)
+	{
[…]

### 2018-10-09 doc/issre2018/presentation/pict/ShoppingCart1_files/plusone.js

@@ -1,0 +1,47 @@
+var gapi=window.gapi=window.gapi||{};gapi._bs=new Date().getTime();(function(){var aa=encodeURIComponent,k=window,ba=Object,q=document,ca=Array,da=parseInt,r=String,ea=decodeURIComponent;function fa(a,b){return a.type=b}
+var ga="appendChild",s="push",t="test",ha="shift",ia="exec",ja="width",ka="slice",v="replace",la="getElementById",ma="concat",na="charAt",oa="JSON",x="indexOf",pa="nodeName",qa="match",y="createElement",z="setAttribute",ra="type",sa="bind",ta="getTime",ua="getElementsByTagName",A="substr",B="toString",D="length",E="prototype",F="split",G="location",H="style",va="removeChild",I="call",K="getAttribute",wa="protocol",xa="charCodeAt",L="href",M="substring",ya="documentMode",za="action",N="apply",Aa="attributes",
+O="parentNode",Ba="update",Ca="height",P="join",Da="toLowerCase",Ea=this,Fa=function(a,b,c){return a[I][N](a[sa],arguments)},Ga=function(a,b,c){if(!a)throw Error();if(2<arguments[D]){var d=ca[E][ka][I](arguments,2);return function(){var c=ca[E][ka][I](arguments);ca[E].unshift[N](c,d);return a[N](b,c)}}return function(){return a[N](b,arguments)}},Ha=function(a,b,c){Ha=Function[E][sa]&&-1!=Function[E][sa][B]()[x]("native code")?Fa:Ga;return Ha[N](null,arguments)};
[…]

### 2018-10-09 doc/issre2018/introduction.tex
Changed git ignore and removed some clutter

@@
 But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of search-based approach.
-In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}.
+In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}~\cite{jedi}.
 We summarize our contributions as follows:

### 2018-10-09 doc/issre2018/presentation/pict/ShoppingCart1_files/addthis_widget.js

@@ -1,2 +1,0 @@
-/* (c) 2008-2014 AddThis, Inc */
-if(!((window._atc||{}).ver)){var _atd="www.addthis.com/",_atr=window.addthis_cdn||"//s7.addthis.com/",_euc=encodeURIComponent,_duc=decodeURIComponent,_atc={dbg:0,rrev:1400772893,dr:0,ver:250,loc:0,enote:"",cwait:500,bamp:0.25,camp:1,csmp:0.0001,damp:1,famp:1,pamp:0.1,abmp:0.5,sfmp:-1,tamp:1,plmp:1,stmp:1,vamp:1,cscs:1,ohmp:0,ltj:1,xamp:1,abf:!!window.addthis_do_ab,qs:0,cdn:0,rsrcs:{bookmark:_atr+"static/r07/bookmark041.html",atimg:_atr+"static/r07/atimg041.html",countercss:_atr+"static/r07/counter014.css",counterIE67css:_atr+"static/r07/counterIE67004.css",counter:_atr+"static/r07/counter017.js",core:_atr+"static/r07/core131.js",wombat:_atr+"static/r07/bar026.js",wombatcss:_atr+"static/r07/bar012.css",qbarcss:_atr+"bannerQuirks.css",fltcss:_atr+"static/r07/floating010.css",barcss:_atr+"static/r07/banner006.css",barjs:_atr+"static/r07/banner004.js",contentcss:_atr+"static/r07/content008.css",contentjs:_atr+"static/r07/content022.js",layersjs:_atr+"static/r07/layers049.js",layerscss:_atr+"static/r07/layers040.css",layersiecss:_atr+"static/r07/layersIE6007.css",layersdroidcss:_atr+"static/r07/layersdroid004.css",warning:_atr+"static/r07/warning000.html",ssojs:_atr+"static/r07/ssi005.js",ssocss:_atr+"static/r07/ssi004.css",peekaboocss:_atr+"static/r07/peekaboo002.css",overlayjs:_atr+"static/r07/overlay005.js",widget32css:_atr+"static/r07/widgetbig060.css",widget32whitecss:_atr+"widgetbigwhite.css",widget20css:_atr+"static/r07/widgetmed010.css",widgetcss:_atr+"static/r07/widget120.css",widgetIE67css:_atr+"static/r07/widgetIE67006.css",widgetpng:"//s7.addthis.com/static/r07/widget060.gif",embed:_atr+"static/r07/embed010.js
[…]

### 2018-10-09 doc/issre2018/presentation/pict/ShoppingCart1_files/api.js

@@ -1,7 +1,0 @@
-var gapi=window.gapi=window.gapi||{};gapi._bs=new Date().getTime();(function(){var f=encodeURIComponent,g=window,k=decodeURIComponent,m="push",n="test",s="shift",t="replace",x="length",A="split",B="join";var C=g,D=document,aa=C.location,ba=function(){},ca=/\[native code\]/,F=function(a,b,c){return a[b]=a[b]||c},da=function(a){for(var b=0;b<this[x];b++)if(this[b]===a)return b;return-1},ea=function(a){a=a.sort();for(var b=[],c=void 0,d=0;d<a[x];d++){var e=a[d];e!=c&&b[m](e);c=e}return b},G=function(){var a;if((a=Object.create)&&ca[n](a))a=a(null);else{a={};for(var b in a)a[b]=void 0}return a},H=F(C,"gapi",{});var I;I=F(C,"___jsl",G());F(I,"I",0);F(I,"hel",10);var J=function(){var a=aa.href,b;if(I.dpo)b=I.h;else{b=I.h;var c=RegExp("([#].*&|[#])jsh=([^&#]*)","g"),d=RegExp("([?#].*&|[?#])jsh=([^&#]*)","g");if(a=a&&(c.exec(a)||d.exec(a)))try{b=k(a[2])}catch(e){}}return b},fa=function(a){var b=F(I,"PQ",[]);I.PQ=[];var c=b[x];if(0===c)a();else for(var d=0,e=function(){++d===c&&a()},h=0;h<c;h++)b[h](e)},K=function(a){return F(F(I,"H",G()),a,G())};var L=F(I,"perf",G()),M=F(L,"g",G()),ga=F(L,"i",G());F(L,"r",[]);G();G();var N=function(a,b,c){var d=L.r;"function"===typeof d?d(a,b,c):d[m]([a,b,c])},P=function(a,b,c){b&&0<b[x]&&(b=O(b),c&&0<c[x]&&(b+="___"+O(c)),28<b[x]&&(b=b.substr(0,28)+(b[x]-28)),c=b,b=F(ga,"_p",G()),F(b,c,G())[a]=(new Date).getTime(),N(a,"_p",c))},O=function(a){return a[B]("__")[t](/\./g,"_")[t](/\-/g,"_")[t](/\,/g,"_")};var R=G(),S=[],T=function(a){throw Error("Bad hint"+(a?": "+a:""));};S[m](["jsl",function(a){
[…]

### 2018-10-09 doc/issre2018/presentation/pict/ShoppingCart1_files/lightbox-v13.js

@@ -1,1311 +1,0 @@
-if ($) {
-
-  function lightbox_vars() {
-    lightbox_vars.selectors = {};
-    lightbox_vars.callqueue = lightbox_vars.callqueue || [];
-    lightbox_vars.cookies = lightbox_vars.cookies || {};
-    lightbox_vars.timeouts = lightbox_vars.timeouts || {};
-    lightbox_vars.images = lightbox_vars.images || [];
-    lightbox_vars.images_info = lightbox_vars.images_info || {};
-    lightbox_vars.delimgs = lightbox_vars.delimgs || {};
-    lightbox_vars.preloadedimgs = lightbox_vars.preloadedimgs || {};
-  }
-
-  function $lightbox(selector) {
-    if (!lightbox_vars.selectors[selector]) {
-      lightbox_vars.selectors[selector] = $(selector);
-    }
-    return lightbox_vars.selectors[selector];
-  }
-
-  function lightbox_setDirectCookie(name, value, path, domain) {
-    name = "lb" + name;
-    path = path || "/";
-    domain = domain || "dreamstime.com";
-    document.cookie = name + "=" + escape(value) +
-                      "; path=" + escape(path) +
-                      "; domain=" + escape(domain);
-  }
-
-  function lightbox_deleteDirectCookie(name, path, domain) {
-    name = "lb" + name;
-    path = path || "/";
-    domain = domain || "dreamstime.com";
-    document.cookie = name + "=" +
-                      "; path=" + escape(path) +
-                      "; domain=" + escape(domain) +
-                      "; expires=Thu, 01-Jan-70 00:00:01 GMT";
-  }
-
-  function lightbox_getCookie(name) {
-    return lightbox_vars.cookies[name];
-  }
-
-  function lightbox_loadCookies() {
-    var cookies = ["cartL", "cartT", "cartW", "cartV", "cartCollapsed", "cartScroll", "cartResized", "dockCartR", "dockCartB"];
-    for (var i = 0; i < cookies.length; i++) {
-      lightbox_vars.cookies[cookies[i]] = getCookie("lb" + cookies[i]);
-    }
-  }
-
-  function lightbox_saveCookies() {
-    for (var name in lightbox_vars.cookies) {
-      value = lightbox_vars.cookies[name];
-      if (value == null) {
-        lightbox_deleteDirectCookie(name);
-      } else {
-        lightbox_setDirectCookie(name, value);
-      }
-    }
-  }
-
-  function lightbox_setCookie(name, value) {
[…]

### 2018-10-09 doc/issre2018/presentation/pict/ShoppingCart1_files/mainjs-v8.js

@@ -1,3773 +1,0 @@
-//SETTING UP OUR POPUP
-//0 means disabled; 1 means enabled;
-var popupStatus = 0;
-var toppp=0;
-function loadPopup()
-{
-	if(popupStatus==0)
-	{
-		$("#msgbox_window").css('width','962px');
-		$("#backgroundPopup").css({ "height": "100%" });
-		$("#backgroundPopup").show('fade');
-		$("#msgbox_window").show('fade');
-		centerPopup();
-		popupStatus = 1;
-	}
-}
-
-function disablePopup()
-{
-	if(popupStatus==1){
-		$("#backgroundPopup").hide('fade');
-		$("#msgbox_window").hide('fade');
-		popupStatus = 0;
-		$('#backgroundPopup,#msgbox_window').remove();
-	}
-}
-
-function centerPopup()
-{
-	var windowWidth = $(window).width();
-	var windowHeight = $(window).height();
-	var popupHeight = $("#msgbox_window").height();
-	var popupWidth = $("#msgbox_window").width();
-	$("#msgbox_window").css({
-		"position": "absolute",
-		"top": toppp,
-		"left": (windowWidth-popupWidth)/2+document.body.scrollLeft
-	});
-	//only need force for IE6
-	$("#backgroundPopup").css({ "height": windowHeight+document.body.scrollTop, "filter": "alpha(opacity=40)" });
-}
-
-function scrollTOP() {
-     $('html, body').animate({
-         scrollTop: 100
-     }, 1000);            
-}
-
-// cookies (cookies0.js)
-function setCookie2(name, value, expires, path, domain, secure)
-	{
-	if (!expires)
-		expires=365;
-	var today = new Date();
-	var expires2 = new Date(today.getTime()+1000*60*60*24*expires);
-	document.cookie= name + "=" + escape(value) +
-		((expires) ? "; expires=" + expires2.toGMTString() : "") +
-		((path) ? "; path=" + path : "; path=/") +
-		((domain) ? "; domain=" + domain : "; domain=.dreamstime.com") +
-		((secure) ? "; secure" : "");
-	}
-
-function setCookie(name, value, expires, path, domain, secure)
-	{
[…]

### 2018-10-09 doc/issre2018/presentation/pict/ShoppingCart1_files/plusone.js

@@ -1,47 +1,0 @@
-var gapi=window.gapi=window.gapi||{};gapi._bs=new Date().getTime();(function(){var aa=encodeURIComponent,k=window,ba=Object,q=document,ca=Array,da=parseInt,r=String,ea=decodeURIComponent;function fa(a,b){return a.type=b}
-var ga="appendChild",s="push",t="test",ha="shift",ia="exec",ja="width",ka="slice",v="replace",la="getElementById",ma="concat",na="charAt",oa="JSON",x="indexOf",pa="nodeName",qa="match",y="createElement",z="setAttribute",ra="type",sa="bind",ta="getTime",ua="getElementsByTagName",A="substr",B="toString",D="length",E="prototype",F="split",G="location",H="style",va="removeChild",I="call",K="getAttribute",wa="protocol",xa="charCodeAt",L="href",M="substring",ya="documentMode",za="action",N="apply",Aa="attributes",
-O="parentNode",Ba="update",Ca="height",P="join",Da="toLowerCase",Ea=this,Fa=function(a,b,c){return a[I][N](a[sa],arguments)},Ga=function(a,b,c){if(!a)throw Error();if(2<arguments[D]){var d=ca[E][ka][I](arguments,2);return function(){var c=ca[E][ka][I](arguments);ca[E].unshift[N](c,d);return a[N](b,c)}}return function(){return a[N](b,arguments)}},Ha=function(a,b,c){Ha=Function[E][sa]&&-1!=Function[E][sa][B]()[x]("native code")?Fa:Ga;return Ha[N](null,arguments)};
[…]
